### 2018-09-07 paper.tex
Initial ShareLaTeX Import

\documentclass[aps, prb, showpacs, twocolumn, notitlepage, superscriptaddress]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb,amscd,bm,dsfont,wasysym,mathrsfs,latexsym,psfrag,accents,mathtools}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{dcolumn}
\usepackage{float}
\usepackage{color}
\usepackage{xcolor}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{boldline}
\usepackage[normalem]{ulem}
\input{preamble}

\begin{document}

\title{Landau quantization of nearly degenerate bands}

\author{Chong Wang}\affiliation{Institute for Advanced Study, Tsinghua University, Beijing 100084, China}
\author{Wenhui Duan}\affiliation{Institute for Advanced Study, Tsinghua University, Beijing 100084, China}\affiliation{Department of Physics and State Key Laboratory of Low-Dimensional Quantum Physics, Tsinghua University, Beijing 100084, China}\affiliation{Collaborative Innovation Center of Quantum Matter, Tsinghua University, Beijing 100084, China}
\author{Leonid Glazman}\affiliation{
Department of Physics, Yale University, New Haven, Connecticut 06520, USA}
\author{A. Alexandradinata}\affiliation{
Department of Physics, Yale University, New Haven, Connecticut 06520, USA}

\begin{abstract}
\textbf{[abstract needs revamp]}
 In the semiclassical theory of Landau levels, a Bloch electron is driven by a magnetic field  along constant-energy band contours  (in quasimomentum space) known as orbits. We introduce a quantization rule for Landau levels of nearly degenerate orbits which are split by spin-orbit coupling. The average area $S$ of two spin-orbit-split orbits is assumed much larger than the difference in areas ($\delta S$), and also much larger than the inverse square of the magnetic length ($\lmt$). By treating both $\delta S/S$ and $1/l^2S$ as small parameters with finite ratio $l^2\delta S$, our perspective diverges from and generalizes previous semiclassical theories.  $l^2\delta S$ is the dimensionless measure of the field-induced hybridization between spin-orbit-split orbits; we allow for $l^2\delta S$ to be comparable with the Zeeman coupling. In the opposing regimes $l^2\delta S {{\ll}} 1$  and $l^2\delta S{\gg}1$, we recover the known Onsager-Lifshitz-Roth rules for nondegenerate and degenerate orbits, respectively.  In the absence of crystallographic symmetry, three real parameters are needed to tune a degeneracy between two Landau levels which have been split by the spin-orbit and Zeeman interactions. Here, we identify symmetry classes for which such degeneracies can be tuned by varying a single parameter, which might be the magnitude or orientation of the field, or a bias voltage in tunneling spectroscopy.  We demonstrate the utility of our rule for the Rashba 2DEG (for which an in-plane Zeeman field can induce a type-II Dirac point), Dresselhaus spin-orbit-coupled systems, and the angular magnetoresistance oscillations of semiconductor bilayer heterostructures.      
\end{abstract}
\date{\today}

% We demonstrate the utility of our rule for quasidegenerate orbits which  touch at isolated (type-II Dirac) points, as well as for orbits which (nearly) touch at \emph{all points} along their trajectory. In the former case, a wavepacket follows each spin-orbit-split orbit adiabatically, except at localized regions where quantum  tunneling (known as magnetic breakdown) is appreciable; in the latter case, adiabaticity is irrelevant and the orbits are completely reconstructed by the field.

%Magnetic breakdown is the phenomenon of quantum tunneling between semiclassical orbits; conventionally, the tunneling region is localized to \emph{isolated}  points   in momentum space, as exemplified by saddle- or Dirac points. Here, we introduce a qualitatively distinct form of tunneling that is delocalized over the entire orbit. Such nonlocal breakdown occurs wherever two orbits nearly touch at \emph{all points} along their trajectory, as exemplified in solids by the spin-orbit splitting of spin-degenerate energy bands. We formulate the Bohr-Sommerfeld quantization rules that are predictive of Landau levels in the presence of nonlocal breakdown. We propose the experimental signature to be an aperiodic beating in quantum oscillations of the magnetization or resistivity, which contrasts with the periodic beating that is well-known for two decoupled orbits.

%By accounting for all dynamical and geometric phases induced by this spin-splitting, our work extends the known Onsager-Lifshitz-Roth rules for nondegenerate and degenerate orbits.

\maketitle

\section{Introduction}

%Semiclassical theory is predictive of Landau levels for solids in a weak magnetic field $B$. This theory has been extended to describe quantum tunneling between two orbits which intersect at \emph{isolated} points. Examples of such isolated points include saddle and type-II Dirac points, where tunneling respectively occurs between orbits of the same band (known as intraband magnetic breakdown) and between orbits of distinct bands (interband breakdown). As $B {\rightarrow} 0$, tunneling is localized to an arbitrarily small neighborhood of such isolated points, and occurs with half probability for the saddlepoint, and with unit probability for the  Dirac point.\footnote{If orbits nearly intersect, tunneling occurs with a probability that asymptotically $\sim e^{-c/B}$, where $c$ is field-independent;[Blount] as a  rule of thumb, this probability ${\sim} 1$ if the \emph{minimal} separation of the two orbits in $\bk$-space is of order of the inverse magnetic length.}

%This work introduces a qualitatively distinct form of tunneling that occurs between two orbits which nearly touch at \emph{all} points along their trajectory. This is exemplified in solids by energy bands that are split on a scale $\Delta$ due to spin-orbit coupling, as illustrated in Fig. \ref{fig:orbits} for the Rashba model of a two dimensional (2D) electron gas. Generally, the probability of tunneling on any interval of the orbit in reciprocal space \emph{vanishes} in proportion with the length of the interval. Yet the net probability of tunneling over the entire orbit is generically ${\sim} 1$, if $\Delta$ is of order the cyclotron energy. Such tunneling that is delocalized over the entire orbit may be referred to as nonlocal breakdown, in contrast with the localized breakdown that occurs at saddle and Dirac points.

%In this work, we study quasidegenerate orbits and formulate Bohr-Sommerfield quantization rule for them. We find the tunneling between the orbits can be described by a propagator and compare the quantization rule to Landau levels from exact diagonalization. Finally, we discuss experimental signatures of such tunneling.

In the absence of magnetic breakdown, semiclassical quantization rules are well-known for Landau levels of  both nondegenerate [Onsager, Lifshitz] and degenerate [Roth, Mikitik, Topoferm, 100page] energy bands.  Our work generalizes these rules to nearly-degenerate bands, whose orbits are split in $\bk$-space with a differential area  $\delta S$ that is much less than the average area $S$ of the orbits; we shall refer to $\delta S/S{\ll}1$ as the \textit{quasidegeneracy} condition. Quasidegenerate orbits commonly originate from spin-orbit-splitting of energy bands in noncentrosymmetric solids. We provide an illustrative model of  a 2DEG with Rashba spin-orbit coupling:
\begin{equation}
H_R=\frac{{\hbar^2} k^2}{2m}+\alpha  (k_{x}\sigma_{y}-k_{y}\sigma_{x}).\label{eq:Rashba-Hamiltonian}
\end{equation}
At energies much greater than $m\alpha^2$, the differential area of the two spin-orbit-split orbits [see Fig. \ref{fig:orbits}(a)] is much smaller than their average area:\footnote{The expressions for $\delta S$ and $S$ in \q{deltaSvsS} are asymptotically valid  for $E{\gg}m\alpha^2$.}
\e{\delta S = 2\pi k_E \f{2\alpha m}{\hbar} \ll  S =\pi k_E^2; \;\; k_{E}:=\f{\sqrt{2m E}}{\hbar} .\la{deltaSvsS}}
$S$ is equivalently the area of the circular, constant-energy contour in the absence of spin-orbit coupling ($\alpha{=}0$).

Throughout this work we will treat both $\delta S/S$ and $1/l^2S$  as small parameters with finite ratio $l^2\delta S$ \textbf{[define magnetic length]}. Our perspective diverges from and generalizes previous semiclassical theories [Kohn, Blount, Roth, Wannier, Fredkin, Niu, Mikitik, topoferm, 100page] having only a single small parameter ($B$).

$(l^2\delta S)^{-1}$ is a measure of the field-induced hybridization of the quasidegenerate orbits, and shall be called the hybridization parameter. 
In the regime that $l^2\delta S$ is much greater than the Zeeman interaction, we expect that the Onsager-Lifshitz quantization rules apply independently to the two concentric (but decoupled) orbits. In the opposite regime, we should recover the known quantization rule for degenerate orbits. [topoferm, 100p, roth, mikitik] Our goal is to present a unifying rule that interpolates smoothly between the two known regimes.

\section{Quantization Rule\label{sec:qtznrules}}

Let us heuristically argue for the form of such a rule; a more pedagogical and rigorous approach is elaborated in App. \ref{app:quantizationruleproof}. We consider independent electrons described (at zero field) by a translation-invariant Hamiltonian: $\hat{H}_0{+}\delta \hat{H}$. This decomposition is such that energy bands of $\hat{H}_0$ are $D$-fold degenerate at every crystal wavevector $\bk$, while $\delta \hat{H}$ is a weak perturbation that lifts this degeneracy at generic $\bk$. For conceptual simplicity, we focus on $D{=}2$ spin degeneracy, and postpone the general formulation for $D{\geq}2$ to Appendix \ref{app:quantizationruleproof}.  $\hat{H}_0$ is commonly exemplified by  the Schr\"odinger Hamiltonian, and $\delta H$ by a non-centrosymmetric spin-orbit interaction; alternatively, $\hat{H}_0$ may be a centrosymmetric Pauli Hamiltonian (complete with spin-orbit coupling), while $\delta H$ describes a lattice deformation that breaks the spatial-inversion symmetry.

% The quantum theory of a Bloch electron in a magnetic field is based on the noncommutivity of the kinematic quasimomentum operators:[onsager, lifshitz]

Let us apply a magnetic field, and first consider the spin-degenerate Landau levels obtained by neglecting both $\delta H$ and the Zeeman splitting. In the  semiclassical description,  we are interested in  field-induced dynamics within a low-energy degenerate band of $\hat{H}_0$ with  dispersion $\var(\bk)$, e.g., $\var(\bk){=}\hbar^2 \bk^2/2m{+}O(k^4)$ in the Rashba model.    Landau quantization is well-known to derive from the Peierls substitution $\var(\bk){\rightarrow}\var(\bK)$,[Peierls] with   the kinematic quasimomentum operator   $\boldsymbol{K}{:}{=}\boldsymbol{k}{+}(e/\hbar) \boldsymbol{A}(i\nabla_{\boldsymbol{k}})$ and $\boldsymbol{A}(\br)$ being the electromagnetic vector potential. Assuming that the field is aligned in the ${-}z$ direction, $[K_x,K_y]{=}i\lmt$ with the magnetic length $l{:}{=}\sqrt{\hbar/{eB}}$. The semiclassical solution corresponds to  cyclotron revolutions of an electron around a constant-energy contour of $\var(\bk)$ [see Fig. \ref{fig:orbits}(b)]]; this contour, equipped with an orientation given by the equation of motion ($ \hbar dk_{\alpha}/dt {=} \lmt \epsilon_{\ab}\partial \var/\partial k_{\beta} $, with $\epsilon_{xy}{=}{-}\epsilon_{yx}{=}1$), shall be referred as the zeroth-order orbit $\frako_0$.  In this work, we focus only on closed orbits which do not wrap 
non-contractibly around the Brillouin torus.

%(in $\bk$ space)  defined at zero spin-orbit coupling [$\alpha{=}0$; see Fig. \ref{fig:orbits}(b)]. This cyclotron motion obeys the equation of motion:  $ \hbar dk_{\alpha}/dt = \lmt \epsilon_{\ab}\partial \var/\partial k_{\beta} $, with $\epsilon_{xy}{=}{-}\epsilon_{yx}{=}1$. The spin-orbit-free band contour, equipped with an orientation given by the equation of motion, shall be referred as the zeroth-order orbit $\frako_0$. In this work, we focus only on orbits which are closed, i.e., orbits that do not cross the Brillouin-zone edge.

%$T_c:=2\pi\hbar/\var_c$

The quantization rule for Landau levels reflects the single-valuedness of the semiclassical (WKB) wavefunction over $\frako_0$,[Berry, Mount] i.e.,  the phase accumulated by an electron (over one cyclotron period $T_c$) is an integer multiple of $2\pi$: $(l^2S(E){+}\gamma)/2\pi{\in}\Z$. The leading-order phase   involves the classical action $S{:}{=}-\int_{0}^{T_c} k_x \dot{k}_y dt$  corresponding to $(K_x,K_y)$;[mount] $S$ has a dual interpretation as the signed area (in $\bk$-space) enclosed by $\frako_0$, as illustrated in Fig. \ref{fig:orbits}(b). $\gamma$ is a subleading Maslov correction [caustic] that generally equals $\pi$ times the rotation number $r$ of $\frako_0$ (i.e., the number of rotations made by the tangent vector over one cycle);[100page] for orbits that are deformable to a circle,  $r{=}{\pm} 1$. In the zeroth-order  solution, all Landau levels are spin-degenerate with a level spacing 
\e{ \var_c:=\f{2\pi}{l^2|\partial S/\partial E|}:=\f{\hbar^2}{ml^2}:=\f{h}{T_c}. \la{def:cyclotron}} 
Here, $\var_c$ and $T_c$ are respectively the cyclotron energy and period of the zeroth-order orbit, and $m$ is the effective mass. Henceforth, `degeneracy of Landau levels' should be understood as a spin degeneracy.

%rather than the ever-present macroscopic degeneracy associated to the cyclotron motion of a single species of fermions.

To the first order, $\delta H$ and the Zeeman interaction  induce a subleading phase offset ($\lambda_a$) which generically differs for the two orthogonal spinor states (labelled $a{=}1,2$):
\begin{equation}
l^2S(E)+\lambda_a(E,B)+\gamma=2\pi n,\as  n\in \mathbb{Z},\;a=1,2. \label{eq:rule}
\end{equation}
This implies that the spin-degeneracy of Landau levels is split   by  $\var_c|\lambda_1{-}\lambda_2|/2\pi$. The phase offsets $\lambda_a$ can be viewed as Floquet quasienergies of a time-periodic, perturbative Hamiltonian ($\calh$) that governs the dynamics of the spinor wavefunction.  $\lambda_a$ is obtained  from  eigenvalues $\{e^{i\lambda_a}\}_{a=1}^2$ of a time-evolution propagator -- the time-ordered exponential 
\begin{equation}
\A{:}{=}\overline{\exp}\left[-\frac{i}{\hbar}\int_0^{T_c} \calh(\bk(t)) dt\right],
\label{eq:prop}
\end{equation} 
with $\bk(t){\in}\frako_0$ a periodic function determined by the semiclassical equation of motion.   $\calh$ has the two-by-two matrix form:
\begin{equation}
  \calh=\delta \var +B\bigg(M_z -g_s\mu_{B}\f{s_z}{\hbar} + e\epsilon_{\alpha\beta}\mathfrak{X}_{\beta}v_{\alpha}\bigg):=\delta \var+B\calm,\label{eq:H1}
\end{equation}
$\delta \var$ is the projection of $\delta H$ to the quasidegenerate band associated to $\var(\bk)$, e.g., $\delta \var{=}\alpha(k_x\sigma_y{-}k_y\sigma_x)$ in the Rashba model. In the basis of energy-split bands (which we label by  ${+}$ and $-$ for the outer and inner orbit respectively),\footnote{We remark that the quantization rule is invariant under basis transformations within the degenerate band subspace (See App. \ref{app:quantizationruleproof}); this may be exploited for efficient  numerical computations.} $\delta \var$ is a diagonal matrix whose diagonal entries ($\delta \var_+,\delta \var_-$) are related to  the hybridization parameter:\footnote{The neglected term on the right-hand side of  \q{spinsplitwkb} is smaller (than the kept term) by a factor $\delta v_{\pm}/v$, which is the relative change in band speed $v=|\boldsymbol{v}|=\hbar^{-1}|\partial \var/\partial \bk|$ induced by the spin-orbit coupling. This factor is assumed to be small.  For example in the Rashba model, $\delta v_{\pm}/v=m\alpha/\hbar k_E{\sim}\delta S/S{\ll}1$.}   
\e{\int_0^{T_c} (\delta \var_+{-}\delta \var_-) \frac{dt}{\hbar} \approx l^2\delta S. \la{spinsplitwkb}}
%In the  Rashba model,   $\delta \var_{\pm}(E){=}{\pm} (\alpha/\hbar)\sqrt{2mE}$ is independent of $\bk$ due to a continuous rotational symmetry of $H_R$. \\

%the wavepacket;  $g_s{\approx}2$ is the free-electron $g$-factor and $\mu_B$ the Bohr magneton.[100page] 
%Spin in $z$ direction is represented by $s_z=\hbar\sigma_z/2$ \textbf{[detail]}.

The remaining terms in \q{eq:H1} describe a generalized Zeeman interaction $B\calm$ which is the first-order-in-$B$ correction to the Peierls-Onsager Hamiltonian $\var(\bK)$.[kohn,blount,roth] Included in this interaction is the Zeeman coupling to the spin ($g_s\mu_Bs_z/\hbar$) and orbital ($M_z$) magnetic moment of the quasidegenerate band; the latter  is expressible in terms of matrix elements of the velocity operator \textbf{[please insert definition of v from below eq 3 in topoferm]}:
\e{
M_z=\f{ie\hbar}{2}\sum_l'\f{v_{x,ml}v_{y,ln}-v_{y,ml}v_{x,ln}}{\epsilon_m-\epsilon_l}. \la{eq:orbitalmoment}
}
Here, the summation in $l$ does not include the two quasidegenerate bands.  There is finally a geometric contribution to the Zeeman interaction, which involves the two-by-two non-Abelian Berry connection  as well as the  zeroth-order band velocity: 
\e{\mathfrak{X}_{\beta,mn}{=}i\braket{u_m}{\partial u_n/\partial k_{\beta}},  \;\;v_{\alpha}:= \red{\f{1}{\hbar}}\p{\var}{k_{\alpha}},\la{berryconn}}
with $\{u_n\}_{n=1}^2$ the periodic component of Bloch functions in the quasidegenerate band. 
%which provides a geometric characterization of band wavefunctions along $\frako_0$.\\
%All matrix elements in \qq{eq:prop}{eq:orbitalmoment} are evaluated with wavefunctions of $\hat{H}_0$.

\qq{eq:rule}{berryconn} allow us to determine $\lambda_{1,2}$ to the lowest order  in $1/l^2S$ and $\delta S/S$, and for arbitrary values of $l^2\delta S$ and $||B\calm||/\delta \var_{\pm}$.

%It will be useful to separate $B$-independent and $B$-dependent terms in \q{eq:H1}; the latter we denote as $B\calm$, with $\calm$ having the dimension of a magnetic moment. Let us explain each term in the order of its appearance.\\

\begin{figure}
\includegraphics[width=0.9\columnwidth]{orbits.png}
\caption{(a) \textbf{[some axes will be helpful]} Solid (resp.\ dashed) lines respectively illustrate the band dispersion of an electron gas with (resp.\ without) Rashba spin-orbit coupling.  The oriented circles illustrate the spin-orit-split orbits for a magnetic field pointing to $-z$ direction. \textbf{[might replace Delta with $2\alpha k_E$ at some point]} (b) The zeroth-order orbit $\frako_0$ is indicated by a dashed circle with area $S$; $\delta S$ is the differential area  between two spin-orbit-split orbits. The spin texture is indicated by purple arrows.\label{fig:orbits}}
\end{figure}

\subsection{Recovering the Onsager-Lifshitz-Roth quantization rules in two limits}\la{sec:recoveronsager}

It is useful to compare $\delta \var$ with $B\calm$ in the basis of energy-split bands (labelled $\pm$): in the two regimes where one dominates over the other, \qq{eq:rule}{berryconn} reduce to the known Onsager-Lifshitz-Roth rules for (i) two independent, nondegenerate orbits, and for (ii) degenerate orbits.  \\

%\footnote{Though the adiabatic limit does not exist for orbits that exactly intersect at type-II Dirac points, these orbits are nevertheless describable by our quantization rule, as exemplified in the case studies of \s{sec:inplanezeeman} and \s{sec:rotsymmbreakdown}.}}

\noi{i} If $|\var_+{-}\var_-|$ is everywhere (along $\frako_0$) much greater than $B|\calm_{+-}|$, then an electron would undergo adiabatic (band-conserving) dynamics[nenciu] along two independent, nondegenerate orbits. Such an adiabatic regime always exists as $B{\rightarrow} 0$ for quasidegenerate orbits that do not intersect, e.g, at a type-II Dirac point, which is the subject of the case studies in \s{sec:inplanezeeman} and \s{sec:rotsymmbreakdown}.
By  neglecting  $B\calm_{+-}$ in favor of intraband elements,  $\cala$ reduces to a diagonal matrix with  diagonal entries ($e^{i\lambda_{\pm}}$) given by:
\e{\lambda_{\sma{\pm}} = \int_0^{T_c}\calh_{\sma{\pm\pm}}dt=\pm \tf1{2}l^2\delta S +B\int_0^{T_c}\calm_{\sma{\pm\pm}}dt.  \la{phaseindependentorbit}} 
In the second equality, we have applied \q{spinsplitwkb} and assumed that 
 $\delta \var$ is traceless (this assumption is  valid for splittings of a spin degeneracy\footnote{The Pauli spin-orbit coupling term ${\propto} \bs{\cdot} (\bE {\times} \bp)$ (that is derived from the non-relativistic limit of the Dirac equation) is  traceless in any spin-symmetric  (pseudo-)spinor basis.  Viewing the spin-orbit coupling as a small parameter in degenerate perturbation theory, the lowest-order splitting of any spin-degenerate energy level is always symmetric about the zeroth-order energy. This follows because the zeroth-order, spin-symmetric wavefunctions (associated to a spin-degenerate level) are tensor products of spin and spatial wavefunctions: $\ket{\Psi_{\pm}}{:}{=}\ket{{\pm}\hat{n}}{\otimes} \ket{\psi}$ with $\hat{n}$ a unit vector and  $\bs{\cdot} \hat{n} \ket{{\pm}\hat{n}}{=}{\pm}\ket{\pm \hat{n}}$. Hence, $\braopket{\Psi_{\pm}}{\bs{\cdot} (\bE {\times} \bp)}{\Psi_{\pm}}{=}{\pm}\hat{n}\cdot\braopket{\psi}{\bE {\times} \bp}{\psi}$. \textbf{Please generalize above proof to the case where H0 already includes centrosymmetric SOC. }}).  \q{eq:rule}, combined with \q{phaseindependentorbit}, may be identified as the Onsager-Lifshitz rule[onsager,lifshitz] for  two independent, nondegenerate orbits of areas $S{\pm}\delta S$, and with subleading phase corrections that were first identified by Roth[rothII].\footnote{We remark that \q{phaseindependentorbit} neglects the contribution by band $-$ to the orbital moment of band $+$: $\delta M_z=il^{-2}\epsilon_{\ab}(\delta \var_+-\delta \var_-)\mathfrak{X}^{\alpha}_{+-}\mathfrak{X}^{\beta}_{-+}$. $\mathfrak{X}^{\alpha}_{+-}$, being an off-diagonal matrix element of the position operator, is generically of order a lattice constant $a$. We then estimate $\int_0^{T_c} B\delta M_z dt/\hbar=O(a^2 \delta S )$, which is negligible compared to $l^2\delta S/2$. Note also that the single-band orbital moment simply vanishes in some symmetry classes of orbits.[100page] } The perturbative inclusion of $B\calm_{\sma{+-}}$ results in  a correction to $\lambda_{\pm}$ [cf.\ \q{phaseindependentorbit}] that is expressible as a power series in $B$, with a leading term proportional to $B$; this will be confirmed in a subsequent case study [cf.\ \q{lambdasmallB}] and applied to understand beatings in quantum-oscillatory phenomena in  \s{sec:qo}.    \\

%the hybridization parameter  $(l^2\delta S)^{-1}$ with the interband matrix elements of the generalized Zeeman interaction $\mathbb{Z}_{+-}{:}{=}B\int_0^{T_c}|\calm_{+-}|dt/\hbar$,  where \qq{eq:rule}{eq:H1} reduce to the known Onsager-Lifshitz-Roth rules for (i) two independent, nondegenerate orbits, and for (ii) degenerate orbits.  \\

%\noi{i} Let us consider the zero-hybridization limit ($l^2\delta S{\gg}1$) for two spin-orbit-split orbits that do not exactly intersect (e.g., at a type-II Dirac point\footnote{Though the adiabatic limit does not exist for orbits that exactly intersect at type-II Dirac points, these orbits are nevertheless describable by our quantization rule, as exemplified in the case studies of \s{sec:inplanezeeman} and \s{sec:rotsymmbreakdown}.}).

\noi{ii} Let us consider the opposite regime where the Zeeman splitting due to $B\calm$ is much greater than $(\delta \var_+{-}\delta\var_-)$. \qq{eq:rule}{berryconn}, with $\calh{\approx}B\calm$, may then be identified with the quantization rule (formulated previously by us [topoferm,100page]) for degenerate orbits of any symmetry.\footnote{An equivalent but less general formulation was proposed earlier in [RothII] and [Mikitik,Sharlai] for centrosymmetric solids with time-reversal symmetry (at zero field). For comparison, it should be emphasized that \qq{eq:rule}{berryconn} applies to solids of any symmetry, including magnetically-ordered solids.}

%The competition between $B\calm$ and $\delta \epsilon$ decides 
%whether the spin-orbit-split energy bands are nontrivially hybridized by the magnetic field. More precisely, the competition is between $\delta \epsilon$ and the inter-band matrix elements of $B\calm$; the former (resp.\ latter) is always dominant for sufficiently weak (resp.\ large) field, as  we will illustrate in the case study of \s{sec:Rashba}.

%This leading dependence originates from $\A$ being generated by $\delta \var T_c {\propto}1/B$ [cf.\ \qq{eq:prop}{eq:H1}].

%One motivation for the form of \q{eq:rule} is a separation of scales for different components of

%Separating the semiclassical phase (acquired by a spinor wavepacket over one cyclotron period) into multiple components [as in \q{eq:rule}] may be motivated as a separation of scales. 
% in absolute magnitude, the rate of variation of $\partial l^2S$ (with respect to $E$ and $B$) is also much greater.

%Such non-analyticities might originate from saddle- or II-Dirac points of the zero-field Hamiltonian \textit{without} spin-orbit coupling.

%is estimated to be $\sim\epsilon_c E/\Delta$, much larger than cyclotron energy $\epsilon_c$ due to $\Delta\ll E$. Therefore, the dependence of $\lambda_a$ on $E$ is also weak.

The quantization rule, summarized by \qq{eq:rule}{berryconn}, is the technical accomplishment of this work; the remainder of this work is focused on unpacking its physical implications. We will first demonstrate the utility of our rule in case studies where the adiabatic approximation is invalid, and $\delta \epsilon$ competes with $B\calm$. There are two conceptually different ways in which the adiabatic approximation may fail: (i) if the spin-split orbits are  symmetric under continuous rotations (as they are for the Rashba 2DEG), then adiabaticity may be lost over the entire orbit [cf.\ \s{sec:Rashba}]. (ii) For asymmetric spin-split orbits, adiabaticity may be lost in the vicinity of a single isolated point, where orbits intersect at a type-II Dirac point [cf.\ \s{sec:inplanezeeman}]. 
In \s{sec:llquasideg}, we investigate how many real parameters are required to tune $\lambda_1{=}\lambda_2$ (mod $2\pi$), which would imply a (near) degeneracy of Landau levels.

%In the absence of symmetry, three real parameters 
%certain symmetries  reduce the number of tuning parameters to one, as  will be investigated in \s{sec:llquasideg}.

\section{Case study: Rashba 2DEG with arbitrarily-oriented fields}

%We begin with some preliminary remarks that apply to all case studies in this work. Our chosen studies are modeled (in zero field) by $\bk{\cdot}\bp$ Hamiltonians which are expanded (to quadratic order) about a high-symmetry wavevector ($\bk$). Our model Hamiltonians are written in a (pseudo-)spinor basis, i.e., they are two-dimensional at each $\bk$ [as exemplified by \q{eq:Rashba-Hamiltonian}]; this is the minimal dimension needed to model quasidegenerate orbits.

%Any (pseudo-)spinor Hamiltonian can be  decomposed, at each $\bk$, into traceful ($\var(\bk)$) and traceless ($\delta \var$) components. We operationally identify the traceful component as the zeroth-order band Hamiltonian (with spin $\text{SU}(2)$ symmetry), and the traceless component as the spin-orbit term; the former produces spin-degenerate energy bands, and the latter splits the degeneracy. This identification has a microscopic justification: the Pauli spin-orbit coupling term  (that is derived from the non-relativistic limit of the Dirac equation) is  traceless in any spin-symmetric  (pseudo-)spinor basis.\footnote{The Pauli spin-orbit term is proportional to  $ \bs{\cdot} (\bE {\times} \bp)$. Viewing the spin-orbit coupling as a small parameter in degenerate perturbation theory, the lowest-order splitting of any spin-degenerate energy level is always symmetric about the zeroth-order energy. This follows because the zeroth-order, spin-symmetric wavefunctions (associated to a spin-degenerate level) are tensor products of spin and spatial wavefunctions: $\ket{\Psi_{\pm}}{:}{=}\ket{{\pm}\hat{n}}{\otimes} \ket{\psi}$ with $\hat{n}$ a unit vector and  $\bs{\cdot} \hat{n} \ket{{\pm}\hat{n}}{=}{\pm}\ket{\pm \hat{n}}$. Hence, $\braopket{\Psi_{\pm}}{\bs{\cdot} (\bE {\times} \bp)}{\Psi_{\pm}}{=}{\pm}\hat{n}\cdot\braopket{\psi}{\bE {\times} \bp}{\psi}$. } $H_0$ determines the zeroth-order orbit $\frako_0$ (and associated action $S$ and cyclotron energy $\var_c$). $H_{so}$ is simply identified with $\delta \var$, the spin-orbit term in the effective Hamiltonian $\calh$. One useful implication of this discussion is that $\delta \var$ is traceless.

\subsection{2DEG with Rashba and Dresselhaus spin-orbit interactions}\label{sec:Rashba}

%[ denoted by $\ket{u_{\pm,\bk}}=(1,\pm e^{i\theta_{\bk}})^t$ with $k e^{i\theta_{\bk}}=k_y+ik_x$ ]

%basis of spin-orbit-split energy  bands (defined at zero field),

We will first apply our rule to the Landau levels of the Rashba model [cf.\ \q{eq:Rashba-Hamiltonian}], for which analytic expressions exist for verification; shortly after we will demonstrate the utility of our quantization rule for the 2DEG with both Rashba and Dresselhaus spin-orbit interactions, for which there exists no known analytic closed-form solution.

For simplicity, we assume that the Pauli matrices in \q{eq:Rashba-Hamiltonian} correspond to spin: $s_i{=}\hbar \sigma_i/2$. Let us evaluate the effective Hamiltonian $\calh(\bk)$  along the cyclotron trajectory $\frako_0$ with radius $k$. In the  energy basis of the Rashba Hamiltonian $H_R$ [cf.\ \q{eq:Rashba-Hamiltonian}], 
\e{\calh(\bk)=\alpha k\tau_z{+}\f{g_s}{2}\mu_{\sma{B}}B\tau_x \red{-} \f{eB\red{\hbar}}{2m} (\tau_x-I) \epsilon_{\alpha\beta} k_{\red{\alpha}}\nabla_{\red{\beta}}\theta,\la{rashbaeffham}}
where $\tau_i$ are a new set of Pauli matrices with $\tau_z{=}{+} 1$ and ${-}1$ corresponding to the outer and inner orbits, respectively \red{[I switched the sign in the equation above to emphasize the sign difference.]}. $e^{i\theta_{\bk}}{=}(ik_x{-}k_y)/k$ is the angle of the in-plane spin-orbit field $({-}\alpha k_y,\alpha k_x,0)$, which winds once over $\frako_0$; the spin of our basis vectors likewise winds, in parallel (or anti-parallel) alignment with this field (see Fig. (\ref{fig:orbits})(b)). Terms proportional to the rate of spin rotation  ($\nabk \theta$) originate from the  non-abelian Berry connection. The first term of  $\calh$ corresponds to the spin-orbit-induced splitting of the energy-degenerate bands;
the remaining terms may be interpreted as B-induced deformations of the bands.   It is well-known that the Zeeman term tends to polarize spin in the direction ($\vec{z}$) of $\bB$; remarkably, the non-abelian Berry term   also has a polarizing effect, but with opposite sign. These two effects completely cancel for free electrons ($m{=}m_0$), but not generically in band systems. The orbital moment term $B M_z$, which generally couples the two-band subspace (of interest) to all other bands, is absent in any simplified two-band model.
%Observe that  that $\calh$ is actually time-independent, which originates from a  that is unbroken by the field (aligned with the rotational axis). Consequently,

Due to the continuous rotational symmetry of $H_R$, $\nabk \theta$ has magnitude $1/k$ and lies tangential to $\frako_0$; consequently, $\calh$ is constant along $\frako_0$, and the propagator simplifies to $\cala{=}e^{{-}i\calh T_c}$ without time-ordering, and the phase corrections to the quantization rule are simply the eigenvalues of $\calh$ multiplied by $T_c$:
\begin{equation}
\lambda_{\pm}=\pm\f1{2}\sqrt{({l^2\delta S})^2+\pi^2(g_{\sma{\text{eff}}}-2)^2}+\pi. \label{eq:Rashba-lambda}
\end{equation}
This is a function of the differential action $\delta S$ [cf.\ \q{deltaSvsS}] and  the effective  $g$-factor ($g_{\sma{\text{eff}}}{:}{=}g_sm/m_0$), which is the free-electron $g$-factor multiplied with the ratio of  effective ($m$) and free-electron ($m_0$) masses. The standalone $\pi$ term is the single-band Berry phase associated to the winding of $\theta_{\bk}$ by ${\pm}2\pi$. The two quantities under the square root originate from the spin-orbit energy splitting $\delta \var$ and the inter-band matrix elements of $B\calm$ (in the basis of zero-field bands).

In the weak-hybridization regime: $l^2\delta S {>}\pi(g_{\sma{\text{eff}}}{-}2)$, we may expand \q{eq:Rashba-lambda} as a Laurent series in $B$:
\e{\lambda_{\pm}= \pm \f{l^2\delta S}{2} +\pi \pm \f{\pi^2}{4}\f{(g_{\sma{\text{eff}}}-2)^2}{l^2\delta S} + O(B^2). \la{lambdasmallB}}
\q{eq:rule}, combined with the first two terms on the right-hand-side of \q{lambdasmallB}, may alternatively be derived from 
the standard Onsager-Lifshitz rules for two independent orbits, with a common $\pi$ Berry-phase correction for each orbit:\footnote{The intra-band Zeeman and orbital-moment couplings vanish due spacetime-inversion symmetry.[topoferm]} $l^2(S{\pm}\delta S)/2\pi {\in}\Z$. Higher-order terms in \q{lambdasmallB} reflect the field-induced hybridization of the spin-orbit-split orbits.

In the strong-hybridization regime: $l^2\delta S {\ll}\pi(g_{\sma{\text{eff}}}{-}2)$, $\lambda_{\pm}{\approx}{\pm}\pi g_{\sma{\text{eff}}} /2$ mod $2\pi$, which corresponds to the Zeeman splitting of Landau levels by $g_{s}\mu_BB$, in the \textit{absence} of the spin-orbit interaction.

%In the case of free electrons ($m{=}m_0$), we recover  an elementary result in quantum mechanics -- that all levels (except the lowest) are spin-degenerate due to the equality of cyclotron and Zeeman energies.

%Eq. (\ref{eq:prop}) interpolates smoothly between the quantization rules for degenerate and independent orbits.

%For $\delta\epsilon=0$, Eq. (\ref{eq:prop}) is exactly the propagator for degenerate bands in Ref. [100p].

%If $\delta\epsilon$ dominates over all other terms in \q{eq:H1}, tunneling matrix elements between energy bands may be neglected. That is to say, the propagator is well-approximated by a diagonal matrix in the basis of energy bands; each diagonal element corresponds to the phase offset for an independent orbit.

%To better appreciate this, 
%$\A$ has the form:
%\begin{equation}
%\A=\overline{\exp}[i\oint_\frako_0\left(\begin{array}{cc}
%-\alpha l^{2}mk_F+\frac{1}{2} & -\frac{1}{2}+\frac{g'_s}{4}\\
%-\frac{1}{2}+\frac{g'_s}{4}& \alpha l^{2}mk_F+\frac{1}{2}
%\end{array}\right)d\theta],\label{eq:Rashba-prop}
%\end{equation}
%where $\theta$ is a polar angle parametrizing the cyclotron orbit, and $g_s'{:}{=}g_{s} m/m_0$ is an effective $g$ factor weighted by the ratio of the effective mass $m$ over the free-electron mass $m_0$. Off-diagonal elements of $\A$ induce inter-band tunneling, and are contributed by the Berry connection (the term $-1/2$) and the Zeeman coupling  ($g_s'/4$). That both terms are $k$-independent originate from the continuous rotational symmetry (in $z$ direction) of the Rashba Hamiltonian. 
%Diagonalizing Eq. (\ref{eq:Rashba-prop}), we obtain subleading order correction to quantization rule as

%The two quantities under the square root reflect a competition between intra- and inter-band matrix elements. The latter reflects a quantum interference between the Zeeman coupling and the non-abelian Berry connection, which is captured by our quasidegenerate quantization rule but absent in the standard Onsager-Lifshitz rules for independent orbits. To appreciate this, suppose we employ the standard rules[roth,100page] and properly account for the Zeeman coupling, the orbital moment, and the single-band Berry phase. The  Zeeman coupling  modifies the zero-field energy bands in two ways: it enlarges the spin-orbit-induced energy gap as $\Delta {\rightarrow} \Delta'{:}{=} \sqrt{(\Delta)^2{+}(g_s\mu_BB)^2}$, and it tilts the spin (along either orbit) out of the xy-plane. For $\Delta'{\gg}\var_c$, we may treat each Zeeman-deformed orbit as independent, and the corresponding Onsager-Lifshitz quantization rules are 
%\e{ l^2S\pm \lambda'_{\pm} = 2n(\pi+1/2), \;\text{with}\;   \lambda'_{\pm}:=\pm 2\pi \Delta'/\var_c{+}\pi.}
%The first component of $\lambda'$ is simply the modification of the WKB phase $l^2\delta S'$ due to both spin-orbit and Zeeman couplings; the second component is  the sum (${=}\pi$)[Fuchs,topoferm] encodes the single-band Berry phase and the orbital moment. A comparison of $\lambda_{\pm}$ with $\lambda'_{\pm}$ shows that the former has an extra $1/2$ under the square root [cf.\ \q{eq:Rashba-lambda}], which originates from the off-diagonal element of the non-abelian Berry connection. In other words, the standard Onsager-Lifshitz rules neglects the aforementioned quantum interference. This interference is completely destructive for free electrons ($m{=}m_0$), but not generically in band systems.

%\footnote{We have further assumed here that basis functions of $\mathcal{H}_R$ are eigenstates of spin operator $s_z$, which also need not be true in band systems. }

Our quantization rule [\q{eq:rule} with \q{eq:Rashba-lambda}] may be compared with the  exact Landau-level spectrum of the Peierls-substituted Hamiltonian $H_R(\bK)$. The exact levels are given implicitly by
\e{
&n_{\pm}=\frac{l^2S}{2\pi}+\frac{l^2\delta S}{16\pi}\f{\delta S}{S}\lin 
&\pm\f1{2}\sqrt{\bigg(\frac{l^2\delta S}{8\pi}\f{\delta S}{S}\bigg)^2+(l^2\delta S)^2+\pi^2(g_{\sma{\text{eff}}}-2)^2},\label{eq:Rashba-exact}}
with the functional forms of $\delta S(E)$ and $S(E)$ provided in \q{deltaSvsS};  $n_{+}{\ge} 1$ and $n_-{\ge} 0$ here are integer-valued labels for two distinct sets of levels.  In the quasidegenerate regime ($E{\gg}m\alpha^2$), terms involving $\delta S/S$ may be neglected and \q{eq:Rashba-exact} reduces to our quantization rule with $\lambda_{\pm}$ given by \q{eq:Rashba-lambda}.

Our quantization rule equally has utility where no closed-form analytic expression exists for the spectrum. Such is the case when we introduce a Dresselhaus spin-orbit coupling:
\begin{equation}
 H_{RD}(\bk)=\frac{{\hbar^2}k^2}{2m}+\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+\beta(k_{x}\sigma_{x}-k_{y}\sigma_{y}).\la{hamRD}
\end{equation}
In Fig. \ref{fig:RD}(b), a comparison is made between the Landau levels obtained from exact numerical diagonalization of $H_{RD}(\bK)$ (by standard techniques reviewed in App. \ref{sec:numerical}) and those obtained from the quantization rule. The difference in energies  does not exceed $2\%$ of $\var_c$ [cf.\ \fig{fig:RD}(d)] for various choices of the spin-orbit parameters $(\alpha,\beta)$.
Larger differences are positively correlated with 
$l^2\delta S^2/S$ (with $\delta S$ depending on both $\alpha$ and $\beta$), as shown in Fig. \ref{fig:RD}(c); see also \q{eq:Rashba-exact}, which analytically demonstrates how terms involving $l^2\delta S^2/S$ modifies the quantization rule in the case $\beta=0$.

In \s{sec:llquasideg} we will further motivate the study of $H_{RD}$ by investigating the prevalence of Landau-level degeneracies.

%\red{Equation \ref{eq:Rashba-exact} indicates the error of quantization rule is mainly contributed by high order terms, such as terms proportional to $l^2 \delta S^2/S$. We plot in Fig. \ref{fig:RD}(c) $l^2 \delta S^2/S$, showing a strong positive correlation between $l^2 \delta S^2/S$ and error of quantization rules.

%For a last numerical comparison, we plotted in Fig. \ref{fig:RD} (b) the Landau-level spectrum at fixed $\alpha$ and $\beta$

%For fixed $\alpha$ and $\beta$, Landau fan diagrams are presented in Fig. \ref{fig:RD} (b), showing perfect match at relatively large magnetic field and slight deviation in smaller magnetic field between quantization rule and exact Landau levels.

%A typical constant energy contour of the band structure is shown in Fig. \ref{fig:errors} (a), where Dresselhaus SOC breaks continous rotational symmetry to two fold rotational symmetry. There are no known analytic closed-form solutions to the magnetic Hamiltonian $H_{RD}(\bK)$ obtained by Peierls subtitution of $H_{RD}(\bk)$; however $H_{RD}(\bK)$ can be numerically diagonalized by standard techniques that are reviewed in App. \ref{sec:numerical}. The difference between $\lambda$ calculated by numerical diagonalization and by Eq. \ref{eq:prop} are shown in Fig. \ref{fig:errors} (c), where good agreement can be observed. $\Delta/\epsilon_c$ of corresponding parameter range is presented in Fig. \ref{fig:errors}(b).

%$\lambda$ extracted from from Eq. (\ref{eq:Rashba-exact}) is consistent with what we have obtained in Eq. (\ref{eq:Rashba-lambda}).

%It is instructive to consider what we would have obtained if we ignore the tunneling between the quasidegenerate orbits. Without tunneling, the quantization rule gives Eq. (\ref{eq:Rashba-exact}) with $(1/2-g_s'/4)^2$ missing under the square root. This difference is only relevant when $\epsilon_s$ is small enough such that this term dominates the square root, i.e., in the quasidegenerate range.

\begin{figure}
\includegraphics[width=1.0\columnwidth]{RD.png}
% alpha=0.05
% beta=0.02
% m=0.01
\caption{Rashba-Dresselhaus model. (a) Typical cyclotron orbits. (b) Comparison of Landau levels calculated by Eq. (\ref{eq:rule}) (black lines) and numerical diagonalization of the Peierls-Onsager Hamiltonian  $H_{RD}(\bK)$ (red dots). Parameters: $\alpha=0.05$(eV$\cdot$\AA), $m=0.01$($\hbar^2$/eV$\cdot$\AA$^2$), $\beta=0.02~(0.04)$(eV$\cdot$\AA) for left (right) panels. $B$ is measured from 2.9 and 1.6T respectively and is in unit $10^{-2}$T. (c-d) For various spin-orbit parameters $(\alpha,\beta)$ of the Rashba-Dresselhaus model and various field strength (satisfying $l^2S(E)\gg 1$), we plot in (c) the hybridization parameter $l^2\delta S(E)$ for fixed energy $(E=0.4$eV${\gg}m\alpha^2)$. For a single Landau level that lies closest to the chosen $E$, we plot in (d) $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$, where $\epsilon_\text{rule}$ is determined by Eq. (\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian  $H_{RD}(\bK)$. Parameters: $m=0.01$($\hbar^2$/eV$\cdot$\AA$^2$). Units: $\alpha$($10^{-2}$eV$\cdot$\AA), $\beta$($10^{-2}$eV$\cdot$\AA), $Z$($10^{-3}$eV), $l^2 S$($10^2$).\label{fig:RD}}
\end{figure}

\subsection{Rashba 2DEG with in-plane Zeeman field}\la{sec:inplanezeeman}

Our next case study involves orbits that (nearly) touch at a type-II Dirac point -- an asymmetric variant of the conventional Dirac point (as will be introduced below). Quantum tunneling localized to a type-II Dirac point  (in short, II-Dirac point) is known to be mathematically equivalent to  Landau-Zener breakdown, with the electric force replaced by the Lorentz force. [Blount, Obrien, AALG] First, we will demonstrate how we recover Landau-Zener dynamics in the weak-hybridization regime  of \qq{eq:rule}{eq:H1}.

%With intermediate hybridization , including the regime where Landau-Zener dynamics is non-applicable and breakdown is nonlocal.

We begin again with the Rashba model of a rotationally-symmetric Dirac cone. To convert this Dirac point to its asymmetric variant, 
let us introduce a Zeeman coupling to an in-plane magnetic field $B_\parallel$:
\e{ 
H_{RZ}=\f{{\hbar^2}k^{2}}{2m}+\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+\zpar\sigma_{y}, \la{eq:RZ-Hamiltonian}}
with $\zpar{:}{=}{g_s}\mu_B B_{\parallel}/2$.
While this field breaks both time-reversal ($T$) and two-fold rotational ($C_2$) symmetries, the composition $C_2T$ is preserved as $\sigma_x H^*_{RZ}(\bk)\sigma_x{=}H_{RZ}(\bk),$ which constrains spin to lie in-plane at each $\bk$. In this symmetry class, Dirac nodes are irremovable but movable   in two-dimensional $\bk$-space. The in-plane Zeeman field has the dual effect of  moving the Dirac node  to the position:
\begin{eqnarray}
\bar{k}_x & = & -\frac{\zpar}{\alpha},\;\bar{k}_y=0,\;\epsilon_{0}=\frac{{\hbar^2}\zpar^{2}}{2m\alpha^2},\label{whereisdiracpoint}
\end{eqnarray}
and tilting the Dirac cone. To observe this tilt, consider the linearized Hamiltonian in the vicinity of this node: 
\e{
H & =\alpha\left[\left(\sigma_y-\frac{{\hbar^2}\zpar}{m\alpha^2}\right)\delta k_{x}-\delta k_{y}\sigma_{x}\right]+\epsilon_{0}.}
When $|\hbar^2\zpar|>|m\alpha^2|$, the Dirac cone tilts over in the $x$ direction, leading to a Lifshitz transition  of the constant-energy band contours -- from circular to hyperbolic (in the linearized approximation), as illustrated in Fig. \ref{fig:RZ}(c). An over-tilted Dirac cone shall be referred to as type-II. Our case study of a II-Dirac point  connects  two electron-like  pockets [cf.\ \fig{fig:RZ}(a)], and  differs from previous case studies [Obrien, AALG] that connect an electron- and hole-like pocket.

\begin{figure}
\includegraphics[width=1.0\columnwidth]{RZ.png}
\caption{(a) Trefoille-shaped cyclotron orbit for the Rashba-Zeeman model at the energy of the Dirac point. The orbit is drawn over the  {spin-orbit field} ($d_x,d_y$) of the Hamiltonian $H_{RZ}{=}d_0(\bk)I{+}d_x(\bk)\sigma_x{+}d_y(\bk)\sigma_y$, with $d_j$ obtainable from \q{eq:RZ-Hamiltonian}. The wavefunction along the inner (resp.\ outer) component of the trefoille orbit has its pseudospin aligned parallel (resp.\ anti-parallel) to the spin-orbit field. (b) Black dashed lines illustrate a zeroth-order approximation of the Landau levels (assuming Klein tunneling); the leading-order correction is indicated by red lines. The Dirac point lies at $10$meV, at which energy first order correction vanishes in Eq. (\ref{RZfirstorderE}). Parameters: $m$: 0.02$\hbar^2$/eV$\cdot$\AA$^2$, $\alpha$: 0.05eV$\cdot$\AA, $Z_\parallel$: 0.001eV. (c) For various configuration ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in (c) the hybridization parameter $l^2S(E)$ where $E$ is chosen as the energy of the Landau level nearest to the type-II Dirac point, i.e., closest to $\epsilon_0$ in Eq. (\ref{whereisdiracpoint}). We only plotted in region where $0.4<\epsilon_0<1.0$(eV).\red{[Note to Aris: the reason of choosing $\epsilon_0>0.4$ is I want to make sure $l^2S\gg 1$; the reason of choosing $\epsilon_0<1.0$ is Dirac point lying at high energy requires too much harmonics in numerical diagonalization. This requirement is equivalent to $\sqrt{0.8m}\alpha/\hbar<Z<\sqrt{2m}\alpha/\hbar$, corresponding to the boundaries of the plot in (c) and (d).]} (d) $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ corresponding to the parameter configurations in (c), where $\epsilon_\text{rule}$ is determined by Eq. (\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RZ}(\bK)$. Parameters: $m$: 0.01$\hbar^2$/eV$\cdot$\AA$^2$, $l=100$\AA. \label{fig:RZ}}
\end{figure}

In addition to the in-plane field, let us also apply an out-of-plane field $B_{\perp}$, with associated magnetic length $\lper{=}\sqrt{\hbar/eB_{\perp}}$, cyclotron energy $\var^{\sma{\perp}}_c{:}{=}\hbar^2/m\lper^2{:}{=}\hbar \omega_c^{\sma{\perp}}{:}{=}h/T_c^{\sma{\perp}}$ and Zeeman coupling to the spin magnetic moment:  $\zper{:}{=}{g_s}\mu_B B_{\perp}/2$. It is assumed that $\lper^2S$ is large, where $S$ is the area of the zeroth-order orbit (with effective mass $m$). For energies much greater than $m\alpha^2$ and $\zpar$, the quasidegeneracy condition is met: $\delta S{\ll}S$, hence we may apply the quantization rule of \qq{eq:rule}{eq:H1} in the subsequent analysis.

As alluded to in \s{sec:qtznrules}, the adiabatic limit of two independent orbits does not exist if the two spin-orbit-split orbits exactly intersect at a II-Dirac point. To investigate this failure of adiabaticity, let us study the Landau levels at energies close to the II-Dirac point ($\epsilon_0$). We focus first on the regime where, on average (over $\frako_0$), the energy splitting $|\delta \var_+{-}\delta \var_-|$ (due to both  spin-orbit and in-plane Zeeman interactions) is much greater than the interband, out-of-plane Zeeman interaction $B_{\perp}|\calm_{\pm}|$. This implies that the split orbits do not appreciably hybridize -- except in the vicinity of the II-Dirac point where orbits (nearly) touch. Near this II-Dirac point, the dynamics of a two-component wavepacket is described 
 by the effective Hamiltonian
\e{
\calh = \alpha k_{E} \,\omega^{\sma{\perp}}_c t\,\sigma_x+(Z_\parallel-\alpha k_{E})\sigma_y-Z_\perp\sigma_z,\la{effhamIIDirac}
}
with $k_E{=}\sqrt{2mE}/\hbar$ and  $t$ a time variable which parametrizes the zeroth-order orbit:
$\bk(t){=}({-}k_E \cos \omega_c^{\sma{\perp}} t, k_E \sin \omega_c^{\sma{\perp}} t ).$ 
$\calh$ above has been linearized with respect to  $t$, which vanishes in the vicinity of the Dirac point. The eigenbasis of $\sigma_x$ corresponds to two diabatic levels with characteristic slope $v_d{:}{=}\alpha k_E\omega^{\sma{\perp}}_c$; near $t{=}0$, the diabatic levels anticross  due to the hybridization terms ${\propto}\sigma_y,\sigma_z$. Generally, the probability of tunneling across the hybridization-induced barrier is  $\rho^2{=}\exp(-2\pi\barmu)$, with $\barmu{=}{E_g}^2/{2v_d \hbar}$ and $E_g$ the energy gap at the center of the anticrossing;[Landau and lifshitz, Wittig] in this context,
\e{\barmu=\frac{Z_\perp^2+(Z_\parallel-\alpha k_{E})^2}{2\alpha k_{E}\var^{\sma{\perp}}_c}, \la{mu1}}
with $2\alpha k_E$ the spin-orbit splitting at energy $E$ [cf.\ \fig{fig:orbits}(a)]. In the absence of the out-of-plane Zeeman coupling ($Z_\perp{=}0$), $\bar{\mu}$ would vanish at the energy of the II-Dirac point -- leading to unit-probability Klein tunneling, as was first proposed by [Obrien] in a different model realization of the II-Dirac point. However, with a proper account of $Z_\perp$, we find instead that $\bar{\mu}$ has a nonvanishing minimum: $\bar{\mu}_{\sma{\text{min}}}{:}{=} (m/m_0)(Z_\perp/2\alpha k_{E})$, which is a product of the dimensionless effective mass and the ratio of the out-of-plane Zeeman splitting over the spin-orbit splitting. This minimum is practically negligible for  semiconductor heterostructures with $m{\ll}m_0$, but may be relevant in heavy-fermion systems.

To determine the Landau levels, one needs not just the probability for tunneling but also the phase of the probability amplitude. The full information is encoded in a scattering matrix [AALG]
\e{\mathbb{S}=\matrixtwo{\tau e^{i\barphi}}{-\rho}{\rho}{\tau e^{-i\barphi}},\;\rho=e^{-\pi\barmu},\;\tau=\sqrt{1-\rho^{2}}\la{scattmat}}
which is a connection formula that matches the two-component semiclassical (WKB) wavefunction across the Dirac point. $\mathbb{S}$ in \q{scattmat} has been expressed in the basis of spin-split energy bands, so  the diagonal elements of $\mathbb{S}$ are amplitudes for intraband (adiabatic) transmission; the phase of this amplitude is $\barphi{:}{=}\barmu{-}\barmu\ln\barmu{+}\text{arg}[\Gamma(i\barmu)]{+}\pi/4$ with $\Gamma$ the gamma function.

Away from the II-Dirac point, a semiclassical wavepacket undergoes adiabatic (band-conserving) dynamics. The time-ordered, coherent process of interband tunneling and adiabatic dynamics is described by the propagator:
\e{{\A}= \matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}} \diagmatrix{e^{i\tilde{\lambda}_+}}{e^{i\tilde{\lambda}_-}}. \la{propinplanezeeman}}
$\tilde{\lambda}_{\pm}$ is the slowly-varying semiclassical phase [cf.\ \s{sec:slowvariation}]  acquired by adiabatic transport along the spin-split orbit (denoted $+$ and $-$ for outer and inner orbit respectively). $\tilde{\lambda}_{\pm}$ is generated by  $\H_{\pm \pm}$ and has the same form as \q{phaseindependentorbit}, with $B\int_0^{T_c}\calm_{\sma{\pm\pm}}dt$ equal (in this model) to the single-band Berry phase ($\phi_{\pm}^B$) of orbit $\pm$. At energies far above the Dirac point  ($|E{-}\epsilon_0|{\gg}|Z_{\perp}|$) where the Zeeman interaction is negligible, both orbits encircle the Dirac point and hence $\phi_{\pm}^B{\approx}{\pm}\pi$; far below the Dirac point, neither orbit encircles the Dirac point, leading to $\phi_{\pm}^B{\approx}0$. At intermediate energies, $\phi_{+}^B$ (resp.\ $\phi_{-}^B$) is a continuous and increasing (resp.\ decreasing) function of energy, as supported by the Bloch-sphere argument in Fig. \ref{fig:blochsphere}.

%{=}\int_{\sma{0}}^{\sma{T_c}}\calh_{jj}dt/\hbar$ is the cyclotron integral of the corresponding diagonal element of the effective Hamiltonian (in the energy-band basis). $\delta \Omega_{\pm}{=}{\pm}l^2\delta S/2$ plus a field-independent geometric phase (equal to the angle swept by the in-plane spin-orbit field $(\bk^2/2m_2{-}\mu,wk_x,0)$ along the spin-split trajectory; cf.\ discussion in \s{sec:Rashba}).

\begin{figure}
\includegraphics[width=0.8\columnwidth]{blochsphere.png}
\caption{Change of Berry phase across the Zeeman-coupling-gapped Dirac point for inner [(a)] and outer [(b)] orbit. Berry phases can be calculated as half the solid angle enclosed by the corresponding loop on the Bloch sphere. The directions of the loops are indicated by black arrows and the black arrow outside of the sphere indicates increasing energy, where green lines correspond to $\epsilon_0$ in Eq. (\ref{whereisdiracpoint}).\label{fig:blochsphere}}
\end{figure}

Our quantization rule [\qq{eq:rule}{eq:H1}], with $\A$ having the form of \q{propinplanezeeman}, may be equivalently expressed as
\e{
\text{cos}\left[\frac{\Omega_{-}+\Omega_{+}}{2}\right]=\tau\,\text{cos}\left[\frac{\Omega_{-}-\Omega_{+}}{2}+\bar{\varphi}\right], \lin
\ins{with}\;\Omega_{\pm}=l^2 (S\pm \delta S/2)+\phi_{\pm}^B +\gamma_{\pm}, \la{coscos}
}
$\Omega_{\pm}$ is the complete phase acquired by a wavepacket in adiabatically traversing orbit $\pm$, i.e., $\Omega$ sums both rapidly- and slowly-varying components of the semiclassical phase [cf.\ \s{sec:slowvariation}], as well as the quantum Maslov correction ($\gamma_{\pm}{=}\pi$) for circular orbits. A quantization rule analogous to \q{coscos} was previously derived by us for a II-Dirac point that intermediates an electron- and hole-like orbit [AALG].

%Let us first investigate the minimal- and maximal-tunneling limits for \q{coscos}. At energies away from the Dirac point ($E{\neq}\epsilon_0$) and in the limit $B{\rightarrow}0$, Landau-Zener tunneling is negligible ($\tau{\rightarrow}1,\bar{\varphi}{\rightarrow}0$), and \q{coscos} simplifies to the Onsager-Lifshitz-Roth rules ($\Omega_{\pm}/2\pi{\in}\Z$) for  two independent orbits.

In the limit $B{\rightarrow}0$ (equivalently, $\bar{\mu}{\rightarrow} \infty$), Landau-Zener tunneling is negligible ($\tau{\rightarrow}1,\bar{\varphi}{\rightarrow}0$), and \q{coscos} simplifies to the Onsager-Lifshitz-Roth rules ($\Omega_{\pm}/2\pi{\in}\Z$) for  two independent orbits. This simplification occurs even at the energy of the Dirac point, where  the intraband amplitude $\tau$ has a nonvanishing minimum with respect to energy: $\tau_{\sma{\text{min}}}{\approx}\sqrt{2\pi\bar{\mu}_{\sma{\text{min}}}}$, due to the out-of-plane Zeeman coupling.

For any nonzero field, $0{<}\tau{<}1$ implies that the two incommensurate harmonics $(\Omega_+{\pm}\Omega_-)$ in \q{coscos} compete to produce a quasirandom Landau-level spectrum [kaganovslutskin]. That is to say, the spectrum is disordered on the scale of nearest-neighbor level spacings but has longer-ranged correlations. To appreciate this, let us analyze the Landau levels (near the Dirac point) perturbatively in the small parameter $\tau$. To zeroth order, \q{coscos} reduces to\footnote{ Here, we have neglected $|\phi^B_{+}{+}\phi^B_{-}|$, which is approximately half the relative angle $\theta$ between two incoming trajectories that meet at the II-Dirac point. $\theta/2\pi=?$ \textbf{[please express in terms of Hamiltonian parameters]} and is of order $\delta S/S$. To the accuracy of our quasidegenerate perturbation theory,  $|\phi^B_{+}{+}\phi^B_{-}|$ is therefore negligible compared to the leading term $2l^2S$ in \q{trefoillerule}. } 
\e{2l^2S(E_n^0)+\pi\approx 2\pi n \rightarrow \{E_n^0(B)\}_{n\in\Z}.\label{trefoillerule}} 
 This may be interpreted as a quantization rule for a trefoille-shaped orbit with net action $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels, as plotted with dashed lines in Fig.\ \ref{fig:RZ}(b), are  periodic in $E{\rightarrow}E{+}\pi/l^2(\partial S/\partial E)$ and in $l^2{\rightarrow}l^2{+}\pi/S$. Both periods are approximately half that of either disconnected spin-orbit-split orbit, in the assumed quasidegenerate regime $\delta S{\ll}S$. The $\pi$ correction in \q{trefoillerule} is the Berry phase associated to a $2\pi$ rotation of the wavefunction spin over a single trefoille orbit, as illustrated in Fig. \ref{fig:RZ}(a). The Maslov phase, which is generally equal to $\pi$ times the rotation number of an orbit (i.e., the number of rotations made by a tangent vector over one cycle)[100page], is trivially $2\pi$ for the trefoille orbit.

%To appreciate this, consider the regime $\rho^2{\lesssim}1$, where a single harmonic (corresponding to the trefoille orbit) is dominant. Viewing $\tau{=}\sqrt{1{-}\rho^2}$ as a small parameter, the zeroth-order Landau levels $E_n^0(B)$ [as obtained from \q{trefoillerule}] has been shown to be periodic in $E$ and $l^2$ (on short scales associated to the large-action trefoille orbit).

To recapitulate, $E_n^0(B)$ [cf.\ \q{trefoillerule}] exhibits a periodicity on short scales associated to the large action of the trefoille orbit. This small-scale periodicity is lost due to  finite-$\tau$ corrections, yet a longer-range correlation (associated to the smaller differential action $\delta S$ between spin-split orbits) persists, as shown by the first-order-in-$\tau$ correction:\footnote{The general form of this perturbative calculation can be found in Sec. IX-E of [100page]. } 
\e{&\delta E_n(B) =  \f{(-1)^{n+1}}{2\pi} \tau \var_c \cos\bigg(\f{l^2\delta S}{{2}}+\f{\phi_+^B-\phi_-^B}{2}-\bar{\varphi}\bigg) \lin
    &\substack{\sma{Z_{\perp}{\rightarrow}0}\\=} \f{(-1)^{n+1}}{4\sqrt{2\pi}}  \var_c \f{(E-\epsilon_0)l}{\alpha\epsilon_0^{3/2}}\cos\bigg(\f{l^2\delta S}{{2}}-\bar{\varphi}\bigg),\label{RZfirstorderE}}
with the right-hand side (of each line) evaluated at $E_n^0(B)$. The second line of \q{RZfirstorderE} is more practically useful where $m{\ll}m_0$.

%If the out-of-plane Zeeman coupling $\zper$ were zero, $\tau$ vanishes as $|E{-}\epsilon_0|$ in the limit $E{\rightarrow}\epsilon_0$, hence $\delta E_n{\propto}\tau \text{sign}[\epsilon_0-E]$ would be analytic in $B$. However,  nonzero $\zper$ implies that $\tau$ approaches a constant $(\sqrt{2\pi \bar{\mu}_{\sma{\text{min}}}})$ as $E{\rightarrow}\epsilon_0$, leading to a non-analyticity  in $B$ as the Landau level crosses the Dirac point energy. \textbf{[I am not sure that higher-order-in-B corrections may restore analyticity, let's check this numerically]}\red{[I found no evidence of non-analyticity across the Dirac point. Eq. (\ref{RZfirstorderE}) is actually discontinuous across Dirac point, while Eq. (\ref{coscos}) is obviously continuous]}

%$\calh$ above is only defined for $|t|{\ll}T^{\sma{\perp}}_c$. 
%$\calh$ is simplest to interpret in the language of Landau-Zener dynamics:  
%$V_0{:}{=}\sqrt{(Z_\parallel-\alpha k_F)^2{+}Z_{\perp}^2}{>}0$,

%While tunneling that is localized to type-II Dirac points have been analyzed as a Landau-Zener problem [maxim,beenakker] and is solvable with generalized

\textbf{[Rest of section needs work]
} In the regime of quasidegenerate orbits ($\Delta/E{\ll}1$) with intermediate adiabaticity ($\Delta/\epsilon_c{\sim}1$),  our quantization rule \qq{eq:rule}{eq:H1} remains valid but the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}. We may anyway simulate $\cala$ numerically, and compare the semiclassically-obtained Landau levels with the exact solution of $H_{RZ}(\boldsymbol{K})$ (see Fig. \ref{fig:RZ} (c-d)). This exact solution is obtained by large-scale numerical diagonalization [appendix], since (to our knowledge) there exists no analytic solution for generic values of $\alpha,\zpar$ and $B$. \textbf{[Say a few words about the comparison]}

For the special case of $\alpha=0$, the spectra of $H_{RZ}(\boldsymbol{K})$ and  $\mathcal{A}[\mathfrak{o}]$ are both exactly soluble, leading to identical Landau levels with phase offset $\lambda_{\pm}=\pm 2\pi ml^2\sqrt{Z^2+g_s'^2/16m^2l^4}$.\textbf{[Let's be more specific about the form of the spectrum.]}

%The above quantization rule is not applicable in the nonlocal-breakdown regime ($\Delta/\epsilon_c\sim1$). The appropriate rule is summarized in \qq{eq:rule}{eq:H1}, with $\delta \var$ encoding the change in band energies due to the spin-orbit coupling ($\sim \alpha$) and the in-plane Zeeman coupling ($\sim Z$); $\alpha,Z$ and $B$ are considered  small parameters.

% Thus quasidegenerate quantization rule produces exact solution without Rashba spin-orbit coupling. After Rashba spin-orbit coupling is switched on, no analytic solution of $H_{RZ}(\boldsymbol{K})$ is known to our knowledge. Again, exact Landau levels are solved numerically and are compared with quantization rules (see Fig. \ref{fig:errors} (d-f)). Although $\alpha\ne 0$ in Fig. \ref{fig:errors} (f), accuracy of quantization rules is still largely independent of the choice of $Z$.

\section{Single-parameter tuning of Landau-Level quasidegeneracies}\label{sec:llquasideg}

Is there a relation between eigenvalue-degeneracies of  $\A$ and degeneracies of Landau levels? Suppose the propagator $\A$ were degenerate at $(\bar{E},\bar{B})$, i.e., $\lambda_+(\bar{E},\bar{B})=\lambda_-(\bar{E},\bar{B})$ mod $2\pi$. Generically, $(\bar{E},\bar{B})$ is not \emph{simultaneously} a solution of the quantization rule in \q{eq:rule}. That is to say, $\bar{E}$ is not generically the energy of a Landau level at field $\bar{B}$. To obtain a Landau level, we may tune either $E$ or $B$   away from $(\bar{E},\bar{B})$, and  utilize that  $\lambda_{\pm}$ are slowly-varying functions of $(E,B)$ compared to $l^2S(E)$:
\e{\left|l^2\p{S}{E}\right| \gg \left|\p{\lambda_a}{E}\right|,\, \left|S\right| \gg \left|\p{\lambda_a}{l^2}\right|;} 
these inequalities are guaranteed by the quasidegeneracy condition ($\delta S{\ll}S$) and the smoothness of $S(E)$, as we quantify in \app{sec:slowvariation}.  For fixed $\bar{B}$, we are therefore guaranteed to find two Landau levels (denoted $E_{\pm}$) in close proximity to $\bar{E}$, with a splitting of order:
\e{ \f{E_{+}-E_-}{\var_c}\bigg|_{\bar{B}} = \order\left( \f{\partial \lambda_a/\partial E}{l^2\partial  S/\partial E}  \right)\ll 1.\la{llquasideg}}
Alternatively, we may fix $\bar{E}$ and investigate how Landau levels disperse as a function of $B$; the analog of \q{llquasideg}  is the existence of two Landau levels (denoted $l^2_{\pm}$) in close proximity to $\bar{l}^2$, with a splitting of order:
\e{  \f{l^2_{+}-l^2_-}{T_{\sma{1/B}}}\bigg|_{\bar{E}} = O\left( \f{\partial \lambda_a/\partial l^2}{S} \right)\ll 1,\as T_{\sma{1/B}}:=\f{2\pi}{S(E)}.\la{llquasidegB} }
$\partial \lambda_a/\partial l^2$ has been estimated in \s{sec:slowvariation}, and
$T_{\sma{1/B}}$ above is the period of quantum oscillations (in the absence of spin-orbit coupling). To recapitulate, for every exact degeneracy of $\cala$, there must exist, in close proximity, a pair of Landau levels which are exactly degenerate, or nearly degenerate in the sense of \qq{llquasideg}{llquasidegB}. Such Landau levels will be called \textit{quasidegenerate}.

%where $\order(\ldots)$ denotes the order in magnitude of the largest argument; $m_0$ here is the free-electron mass, $m{=}\hbar^2|\partial S/\partial E|/2\pi$ the effective mass.

In the absence of any symmetry,  the ``non-crossing theorem'' [von Neumann,wigner] states that eigenvalue-degeneracies of complex Hamiltonians are attained by tuning three real parameters; this non-crossing rule applies also to Landau-level degeneracies of the Peierls-Onsager Hamiltonian. \textbf{[Questionable: the original theorem was proven for finite-dimensional Hamiltonians]} Henceforth it should be understood that any parameter we refer to is real, rather than complex. Here, we would prove a stronger statement: in the absence of symmetry, a non-crossing rule also applies to Landau-level quasidegeneracies. Equivalently, we would show that eigenvalue-degeneracies of the unitary propagator [cf. \q{eq:prop}] are attainable by tuning three parameters. Indeed, any two-by-two unitary  can be decomposed as $\A{=}e^{i\phi}{\cal \bar{A}}$, where ${\cal \bar{A}}{\in}\text{SU}(2)$ has eigenvalues $\{e^{i\bar{\lambda}},e^{-i\bar{\lambda}}\}$ which completely determine $\delta \lambda$. Suppose ${\cal \bar{A}}$ is parametrized by $d$ independent real numbers  $\{R_1,\ldots,R_{d}\}{:}{=}\bR $ which are tunable in experiments or on paper. The condition of degeneracy (det$[{\cal \bar{A}}(\bR){\pm}I]{=}0$) defines a set of manifolds in $\bR$-space which are henceforth referred to as degeneracy manifolds. The codimension of the degeneracy manifold  is defined as $d$ minus the dimension of said manifold; intuitively, this codimension is the number of linearly-independent parameters needed to fine-tune a degeneracy. Henceforth, we adopt the shorthand that \textit{codimension} always refers to a codimension of a degeneracy manifold (the exact manifold is to be inferred from the context). In the canonical parametrization of $\text{SU}(2)$ over the three-sphere $S^3$: 
\e{{\cal \bar{A}}{=}\matrixtwo{R_1{+}iR_2}{R_3{+}iR_4}{{-}R_3{+}iR_4}{R_1{-}iR_2},\as \sum_{j=1}^4R_j^2{=}1,  \la{s3}}
${\cal \bar{A}}{=}{+}I$ (resp.\ ${=}{-}I$) lie on a point which we refer to as the north pole (resp.\ south pole); both points have codimension three in $S^3$. If special unitaries were uniformly distributed over $S^3$, then encountering a spectral degeneracy for a randomly-selected special unitary would be an exceedingly rare event -- three parameters need be tuned to find either pole on $S^3$,  i.e., the codimension of degeneracy manifold is three. If only one  or two  parameters (in $\{R_1,\ldots,R_4\}$)  can be tuned, then in general we should not expect a degeneracy.

%, which may be viewed as imposing a $U(1){\times}U(1)$ symmetry.\footnote{$\cala$ commutes with any diagonal unitary matrix, with diagonal entries equal to two arbitrary $U(1)$ phase factors.} T

It is well-known that symmetry may reduce codimension. The conceptually-simplest example is the approximate symmetry of band conservation, which has been described in \s{sec:qtznrules}. The salient fact to recall is that  $\cala$ becomes diagonal ($R_3{=}R_4{=}0$) in the basis of energy bands. The phase of $R_1{+}iR_2$ is then the single parameter  to tune $\cala{=}{\pm}I$, i.e., the codimension is unity.
From \q{phaseindependentorbit} we deduce that phase[$R_1{\pm}iR_2]{=}{\pm} l^2\delta S/2$ plus corrections which are field-independent, hence degeneracies of $\cala$ occur with a periodicity (in $l^2$) of $2\pi/\delta S$. This periodicity  has a dual interpretation  in real space -- as a periodic increment of a single flux quantum for  the differential magnetic flux (between the two spin-split orbits).

We may ask if these weak-field degeneracies (based on approximate band-conservation symmetry) persist in the strong-field regime where the adiabatic approximation breaks down. If there is no exact symmetry that persists at finite field, we have shown in the above demonstration [cf.\ \q{s3}] that the codimension is three, hence we should not expect robust degeneracies by tuning $B$ alone. Our next tasks are to identify the exact symmetries which persist in the presence of a finite magnetic field, and to identify which of the exact symmetries result in a reduced codimension.

\red{[Needs to introduce the symmetries more gently]} Since the magnetic field is odd under time reversal, and behaves as a pseudovector under spatial transformations, we deduce that exact symmetries (denoted $g$) are only of two types: either (i) $g$  preserves both the direction of time and the orientation of cyclotron orbits (in the 2D $\bk$-space perpendicular to $B$), or (ii) $g$ inverts both said objects. (i) is exemplified by a rotational symmetry with the rotational axis aligned parallel to the field, and (ii) by the composition  of time reversal $T$ and a spatial reflection $\mathfrak{r}_x$ (with reflection axis perpendicular to $B$)\red{[???, We only have two classes now?]}.

One of our main results is that  rotational symmetry (of both discrete and continuous types) enforces unit codimension. This will be demonstrated by two  case studies in \s{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}; the first study describes a Rashba-Dresselhaus 2DEG where the adiabatic approximation breaks down at all points along the semiclassical orbit; in the second study, the adiabatic approximation breaks down only in the vicinity of type-II Dirac points \textbf{[might mention angular oscillations]}.

In comparison, the composed symmetry $T\mathfrak{r}_x$ enforces a codimension of two. This result, in addition to a comprehensive codimension analysis of all relevant symmetry classes, is presented in \s{sec:tenfold}.

%owing to a spacetime-inversion symmetry that simultaneous inverts space and time: $(\br,t){\rightarrow}({-}\br,{-}t)$, the zero-field Bloch Hamiltonian is Kramers-degenerate at each wavevector. However, this same symmetry is broken in the presence of a magnetic field, and therefore does \textit{not} reduce codimension in the Landau-level problem.

\subsection{Rashba-Dresselhaus 2DEG}\la{sec:singleparameterrashba}

We return to the Rashba model absent Dresselhaus spin-orbit coupling and in-plane Zeeman field.  Owing to a continuous rotational symmetry (denoted $\mathfrak{c}_{\infty}$), $\calh(\bk)$ is a constant along the circular zeroth-order orbit [cf.\ \q{rashbaeffham}], and the propagator simplifies to $\A{=}$exp$[{-}i\calh T_c/\hbar]$. The latter is expressible in the exponential form  $\A =\exp[-i2\pi(r_1\tau_x{+}r_2\tau_z)]$, with $(r_1,r_2){=}(g_s'/4-1/2,-\alpha k_{\red{F}}ml^2\red{+1/2})\in\R^2$. In this two-dimensional parameter space, all degeneracies occur along circles of radius $\sqrt{r_1^2+r_2^2}{=}\red{j}/2$ with $\red{j}$ a nonnegative integer; half the circles ($\red{j}$ even) correspond to $\A=I$, and the other half to $\A=-I$. Except for $\red{j}=0$, all degeneracy manifolds have unit codimension, and can be tuned by varying $B$ alone (with fixed $g_s'$); these manifolds are analogous to line nodes (of Hamiltonian degeneracies) in 2D $\bk$-space -- a topic of recent interest. That tuning $\red{j}{=}0$ requires two parameters can be understood from an elementary result in quantum mechanics: taking $\alpha{=}0$ \textit{and} $m=m_0$, we recover the Zeeman-split Landau levels of a free electron gas without spin-orbit coupling; all levels (except the lowest) are spin-degenerate owing to the equality of the Zeeman and cyclotron energies. [LandauLifshitzstatphysI]   In this exactly-soluble model [cf.\ \q{eq:Rashba-exact}], all  degeneracies ($\red{j} \ge 0$) of $\A$ correspond to exact Landau-level degeneracies, rather than the near degeneracies described by \qq{llquasideg}{llquasidegB}.

\begin{figure}
\includegraphics[width=1.0\columnwidth]{dgn.png}
\caption{Degenerate manifold of Rashba-Dresselhaus model. (a) degeneracy manifold of $\A=-I$; (b) degeneracy manifold of $\A=I$. Units: $\alpha l^2$($400$eV$\cdot$\AA$^3$), $\beta$($400$eV$\cdot$\AA$^3$), $g_s'$(10). Parameters are $m=0.01\hbar^2$/(eV$\cdot$\AA$^2$) and $E=0.4$eV. \red{[For 3D pictures, I always put units in caption since there's no room for them in the pictures.]}\label{fig:dgn}}
\end{figure}

The Rashba model suffers from an oversimplification -- continuous rotational symmetry is not a symmetry of solids. That is to say, it does not belong in any (magnetic) space group. It is possible for $\mathfrak{c}_{\infty}$-symmetric models to approximate Hamiltonians with a discrete, order-$n$ rotational symmetry (denoted $\mathfrak{c}_N$) \red{[Let's use capital N in $\mathfrak{c}_N$ since N coincides with order]}.  To what extent are Landau-level degeneracies (of $\mathfrak{c}_{\infty}$-symmetric systems) robust when $\mathfrak{c}_{\infty}$ is perturbatively reduced to $\mathfrak{c}_N$? Our general answer is out of every $N$ degeneracies of $\A$, $N-1$ of them are robust. \textbf{[results for n=3,4,6 must be checked]}.

While full proof of the above claim is delegated to App. \ref{app:codimension}, let us illustrate the simplest example $N=2$ by introducing the Dresselhaus spin-orbit term ($\propto \beta$) into the Rashba model [cf.\ \q{hamRD}]. This has the desired effect of reducing $\mathfrak{c}_{\infty}$ to a discrete $\mathfrak{c}_2$ symmetry. Since $\A$ depends on $\alpha,\beta,l$ only through $\alpha l^2$ and $\beta l^2$, we consider the three-dimensional parameter space $(\alpha l^2,\beta l^2,g_s')\in \mathbb{R}^3$. If a  line node (in the $\beta{=}0$ plane) were perturbatively stable to finite $\beta$, then it would be embedded in a two-dimensional degeneracy hypersurface of $\mathbb{R}^3$; if the planar line node were unstable, this embedding does not happen, i.e., the planar line node is simply a line node in $\mathbb{R}^3$. Our numerical study shows that half the planar line nodes (corresponding to $\A{=}I$) are stable, while the other half ($\A{=}{-}I$) destabilizes. In $\mathbb{R}^3$, we then have pairs of line nodes and hypersurfaces enclosed by increasingly larger pairs of line nodes and hypersurfaces, as illustrated in Fig. \ref{fig:dgn}.

To understand this pattern of stabilities, consider  the effective Hamiltonian $\calh$ in momentum independent basis (rather than spin-split basis used before)
\e{\calh=\alpha (k_{x}\sigma_{y}{-}k_{y}\sigma_{x})+\beta (k_{x}\sigma_{x}{-}k_{y}\sigma_{y})-\tf{g_s}{2}\mu_{B}B\sigma_z;}
with the Pauli matrices corresponding to spin operators. The two-fold rotational symmetry 
\e{\calh(\bk)=\sigma_z\calh(-\bk)\sigma_z, \;\: \bk(t)=-\bk\big(t+\tf{T_c}{2}\big)\in \frako_0,}
implies that the propagator over the time interval $[T_c/2,0]$ is symmetry-related to that over $[T_c,T_c/2]$:
\e{\A=\A_{T_c\leftarrow T_c/2}\A_{T_c/2\leftarrow 0}=\sigma_z{\A}_{T_c/2\leftarrow 0}\sigma_z {\A}_{T_c/2\leftarrow 0}.\la{eq:sigmazconstraint}}
The tracelessness of $\calh$ (at each $\bk$) implies that  ${\A}_{\sma{T_c/2\leftarrow 0}}$  has unit determinant. 
Utilizing the canonical parametrization for this $\text{SU}(2)$ matrix [Eq. (\ref{s3}) with ${\cal \bar{A}}$ replaced by ${\A}_{\sma{T_c/2\leftarrow 0}}$], we derive 
\e{
{\A}={\cal \bar{A}}=\matrixtwo{1{-}2R_2(R_2{-}iR_1)}{2iR_2(R_3{+}iR_4)}{{-}2iR_2(R_3{-}iR_4)}{1{-}2R_2(R_2{+}iR_1)} \label{proprashba}
}
with $\sum_{j=1}^4R_j^2{=}1$. We deduce from \q{proprashba} that $R_2{=}0$ is a necessary and sufficient condition for ${\cal \bar{A}}{=}I$. The corresponding degeneracy manifold is therefore a  unit-codimensional hypersurface which includes the free-electron limit: $\bR{=}(1,0,0,0)$. \red{[Discussion: I really hate introducing new symbols.]} \fig{fig:dgn}(b) illustrates the same hypersurface plotted with a different choice of coordinates: $(\alpha l^2,\beta l^2,g_s')$. On the other hand, ${\cal \bar{A}}{=}{-}I$ occurs if and only if $\bR{=}(0,1,0,0)$ -- a point in $\bR$-space. If $C_2$ were the only symmetry, then three parameters would be needed to tune ${\cal \bar{A}}{=}{-}I$. Generally, additional symmetry further constrains $\bR$, which may effectively reduce the number of tuning parameters.  This explains why the ${\cal \bar{A}}{=}{-}I$ manifolds, as plotted in Fig. \fig{fig:dgn}(a)], are line nodes instead of point nodes: these line nodes lie in either the $\alpha{=}0$ or the $\beta{=}0$ plane, both of which are $\mathfrak{c}_{\infty}$-symmetric.\footnote{To complete the explanation, \textbf{speculative:} the space of $C_{\infty}$-symmetric unitaries lie on lines in $\bR$-space that intersect $\bR{=}(0,1,0,0)$ [the point node]. A singular coordinate transformation to $\br$-space maps these $C_{inf}$-symmetric lines to $\mathfrak{c}_{inf}$-symmetric planes, and the point node to a line node.}

\subsection{Rotational symmetric magnetic breakdown}\la{sec:rotsymmbreakdown}

\begin{figure}
\includegraphics[width=1.0\columnwidth]{Cn-breakdown.png}
\caption{Cyclotron orbits for $\mathfrak{c}_2$-symmetric [(a)] and $\mathfrak{c}_3$-symmetric [(b)] breakdown. Bottom right inset of (a) presents an enlarged view of breakdown junction, where purple rectangle has area $S_{\sma{\square}}$.\label{fig:Cn-breakdown}}
\end{figure}

Quasidegenerate orbits feature tunneling everywhere along the cyclotron orbit and therefore demand a quantization rule that incorporates both tunneling and single band evolution of wave packets. Sometimes, the coherent evolution of wave packets and tunneling can be decoupled in the quantization rule in weak field limit, as exemplified by magnetic breakdown in Rashba-Zeeman model in Sec. \ref{sec:inplanezeeman}. Let us further explore single-parameter tunability of Landau-level quasidegeneracies in this limit by introducing a rotational symmetric Hamiltonian with isolated breakdown junctions at several isolated $\bk$ points. Besides being a useful toy model, this Hamiltonian provides some insights of stability of Landau-level quasidegeneracies by perturbing from two otherwise independent orbits.

We introduce a $\mathfrak{c}_2$-symmetric analog of the Rashba-Zeeman model:
\e{H=\f{\red{\hbar^2}k^2}{2m_1}+ \bigg(\f{\red{\hbar^2}k^2}{2m_2}-\mu\bigg)\sigma_z +wk_y\sigma_x,\la{modelC2breakdown}}
where $0<m_1{\ll}m_2,0<\mu$. For simplicity, we interpret the Pauli matrices as  spin operators, and the two right-most terms of  \q{modelC2breakdown} as a spin-orbit coupling. The $\mathfrak{c}_2$ symmetry manifests as $\sz H(\bk)\sz{=}H({-}\bk)$, and relates 
two Dirac points at
\e{\bar{k}_x = \pm\sqrt{2m_2\mu}/\red{\hbar},\;\bar{k}_y=0,\;\epsilon_{0}=\frac{m_2}{m_1}\mu.}
In the vicinity of either point, the  Hamiltonian has the linearized form 
\e{H_{\pm} =\pm \red{\hbar}\sqrt{\f{2\mu}{m_2}}\bigg(\frac{m_2}{m_1}+\sz\bigg)\delta k_x+w\delta k_{y}\sx+\epsilon_0, \la{linearHam2}}
from which we deduce that both Dirac points are  type-II if $m_1{<}m_2$; this condition is henceforth assumed.\footnote{Actually we will impose the stronger condition $m_1{\ll}m_2$, to ensure that the relative change in band velocity (due to the spin-orbit coupling) is small. This is a consistency requirement of our WKB theory, as explained in \app{app:quantizationruleproof}.}

%; near each point the orbits are well approximated by two hyperbolic arms
%$\phi_j{=}\int_{\sma{0}}^{\sma{T_c}}\calh_{jj}dt/\hbar$ is simply the cyclotron integral of the corresponding diagonal element of the effective Hamiltonian.

At energies close to the Dirac point ($E{-}\epsilon_0 {\ll} wm_2(2E/m_1)^{\sma{1/2}}$ \red{[need checking]}), there are two concentric orbits which (nearly) touch at both Dirac points, as illustrated in Fig. \ref{fig:Cn-breakdown} (a). Just as in \q{spinsplitwkb}, we define $\Delta$ as the spin-orbit splitting energy (averaged over the zeroth-order orbit with effective mass $m_1$). In the weak-field regime where $\var_c{=}\red{\hbar^2}/m_1l^2{\ll}\Delta$, interband tunneling is localized to the vicinities of the two II-Dirac points, and occurs with the Landau-Zener probability:
\e{\rho^2=e^{-2\pi\bar{\mu}}, \; \bar{\mu}=\f{\big(Z_{\perp}^2+(m_1/m_2)^2(E-\epsilon_0)^2\big)l^2}{2w\sqrt{2E/m_1}}. }
Elsewhere, a semiclassical wavepacket undergoes adiabatic (band-conserving) dynamics. For the upper half ($k_y>0$) of the diagram Fig. \ref{fig:Cn-breakdown}(a), this adiabatic evolution is described by a diagonal unitary matrix in the basis of energy bands; each diagonal entry encodes the slowly-varying semiclassical phase due to $\H$ ($\lambda_a'$ \red{[Let's use $\lambda_j'$ instead of $\delta_\lambda$. The latter is confusing because $\lambda_a\sim l^2 \delta S$. It would be quite confusing if we also let $\delta\lambda_a\sim l^2\delta S$]}) acquired along a spin-split trajectory to the \red{top}. In more detail, $\lambda_{\pm}'{=}{\pm}l^2\delta S/4$ up to a field-independent geometric phase \footnote{due to this field-independent phase, it is not necessary that $\delta\lambda_+=-\delta\lambda_-$}; the latter is equal to half the angle swept by the in-plane spin-orbit field $(0,wk_x,\bk^2/2m_2{-}\mu)$ along the spin-split trajectory; cf.\ discussion in \s{sec:Rashba} \red{[Are we really talking about open Berry phase here?]}.  
The time-evolution propagator  describes the time-ordered, coherent process of interband tunneling (as described by the scattering matrix of \q{scattmat})
 and adiabatic dynamics:
\e{\A&=\red{e^{i\f{\lambda_+'+\lambda_-'}{2}}}\times\nonumber\\
&\left(\matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}}\red{\diagmatrix{e^{i\f{\lambda_+'-\lambda_-'}{2}}}{e^{i\f{\lambda_-'-\lambda_+'}{2}}}} \right)^2. \la{propC2breakdown}}
The two scattering matrices for both Dirac points are identical by $\mathfrak{c}_2$ symmetry; so are the two diagonal propagators corresponding to the left and right halves of the adiabatic dynamics.

$\rho{=}0$  describes the adiabatic limit of two independent orbits with differential action $\delta S$. As described earlier in \s{sec:llquasideg}, degeneracies of $\cala$ occur with a periodicity (in $l^2$) of $2\pi/\delta S$, which corresponds to a periodic increment of a single flux quantum for  the differential magnetic flux (between the two spin-split orbits in real space). 
%The degeneracies alternate between $\cala{=}I$ and ${-}I$ on the B axis, hence the subset of degeneracies corresponding to $\cala{=}I$ (or ${-}I$) occur with a period of  $4\pi/\delta S$ (or two flux quanta).

%occurs if and only if $\rho{=}0$ and  $\exp[i(\delta \lambda_+{+}\bar{\varphi})]$ is real, while

Let us investigate the fate of these degeneracies as $\rho$ increases. While asymmetric interband tunneling generically destabilizes all degeneracies, we will demonstrate that two-fold-symmetric interband tunneling destabilizes only half of them. Indeed, the necessary condition for $\A\propto I$ is \e{\tau\cos(\f{\lambda_+'{+}\lambda_-'}{2}+\bar{\varphi})=\pm 1,0.\la{c2breakdowndgncondition}}
for $\rho{>}0$, only 0 in Eq. (\ref{c2breakdowndgncondition}) is possible, destabilizing half of the degeneracies. \footnote{Notice cosine function reaches 0 twice in a period}

Eq. (\ref{c2breakdowndgncondition}) with $0$ on the right hand side is the condition for destructive interference of the two Feynman paths that contribute to interband tunneling (as illustrated in \red{[Fig]}); this occurs with a period  of   $4\pi /\delta S$ (or two flux quanta). To appreciate this, consider that  for $(\lambda_+'{+}\lambda_-')/2$ to vary by $\pi$, $l^2$ must vary by $4\pi/\delta S$. On the other hand, the field dependence of the scattering phase is comparatively negligible: for $\bar{\varphi}(\bar{\mu})$ to vary  $\sim 1$, the Landau-Zener parameter $\bar{\mu}$ must vary by $\sim 1$;\footnote{See Fig.\ 10 in 100page} moreover, $2\pi\barmu{:}{=} (2\pi/8) l^2S_{\sma{\square}}$ with  $S_{\sma{\square}}$ the area of the rectangle inscribed between the two hyperbolic arms  (see inset of Fig. \ref{fig:Cn-breakdown} (a)); clearly $S_{\sma{\square}}{\ll}\delta S$.

%$2\pi\bar{\mu}{\sim}l^2 S_{\sma{\square}}/8$ where $S_{\sma{\square}}$ is much smaller than $\delta S$ [see inset of Fig. \ref{fig:Cn-breakdown}(a)].

%The periodicity (in $l^2$) of the destructive interference has a dual interpretation  in real space -- as a periodic increment of \textit{two} flux quanta for  the differential magnetic flux (between the two spin-split orbits).\footnote{To clarify, band-conserving orbits do not generically describe the dynamics -- except at fine-tuned fields associated to destructive interference of interband tunneling.}

%This  provides yet another  illustration of the general statement proposed in \s{sec:singleparameterrashba}: due to two-fold rotational symmetry, half the degeneracies have unit codimension, and the other half has codimension two.

An analogous model with $\mathfrak{c}_3$-related II-Dirac points  is illustrated in Fig. \ref{fig:Cn-breakdown}(b). The corresponding propagator $\A$ has a form analogous to \q{propC2breakdown} -- but with $(\cdot)^2$ replaced by $(\cdot)^3$, and with $\lambda_\pm'{=}\pm l^2\delta S/4$ replaced by $\pm l^2\delta S/6$ (plus a field-dependent geometric correction). The degeneracy condition is accordingly modified as $\tau\cos[(\lambda_+'{+}\lambda_-')/2{+}\bar{\varphi}]=\pm 1,\pm 1/2$. For nonzero tunneling ($\rho {>}0$), only $\pm 1/2$ is reachable where, of every three degeneracies that exist in the adiabatic limit ($\rho=0$), only two persist. $\tau=1/2$ marks a critical point where all degeneracies coalesce pairwise (on the $B$ axis) and annihilate. It is not hard to imagine the claim made in Sec. \ref{sec:singleparameterrashba} remains true: out of every $N$ degeneracies, $N-1$ of them are stable against $\mathfrak{c}_N$-symmetric breakdown (see App. \ref{app:codimension} for a proof).
%$\cala{=}{\pm} I$ is attained if and only if  $\tau \cos(\delta \lambda_+{+}\bar{\varphi}){=}{\mp}1/2$.

%There then are no more $B$-tunable degeneracies beyond a critical field where  $\tau{<}1/2$.

%In the zero-tunneling limit ($\rho{=}0$), the condition for degeneracy (of $\cala$) is that $\exp[i(\phi_+{+}\bar{\varphi})]$ is a sixth root of unity -- the periodicity in $l^2$ corresponds to a single quantum of differential magnetic flux.

\textbf{A different realization of two-fold symmetric breakdown: angular magnetoresistance oscillations.}

\subsection{The ten-fold table for symmetry constrained codimensions}\la{sec:tenfold}

\begin{table}
\begin{tabular*}{\columnwidth}{l@{\extracolsep{\fill}}ccccc}
\hlineB{2.0}
             & $u$ & $s$ & quasi. & $g$ & codim.\\
\hline
$\forall \bk \in \frako_0$, $g\circ \bk=\bk$ & 0 & 0 & $\surd$ & $\breve{g}\propto I$ & 3  \\
    &  &  & & $\breve{g}\not\propto I$ & 1 \\
    & 0 & 1 & & $g^2=1$ & 1  \\
    &  &  & & $g^2=-1$ & 3  \\
$|g\circ \frako_0| = |\frako_0|$ & 0 & 0 & $\surd$ & - & 1   \\
$\exists \bk \in \frako_0, g\circ \bk\ne\bk$    & 0 & 1 & & - & 1   \\
    & 1 & 0 & & $\breve{g} \propto \sigma_z$ & 2  \\
    &  &  & & $\breve{g} \not\propto \sigma_z$ & 0  \\
    & 1 & 1 & $\surd$ & $g^2=1$ & 2  \\
    &  &  & & $g^2=-1$ & 0  \\
$|g\circ \frako_0| \ne |\frako_0|$ & 0 & 0 & $\surd$ & - & 3 \\
    & 0 & 1 & & - & 3 \\
    & 1 & 0 & & - & 3 \\
    & 1 & 1 & $\surd$ & - & 3 \\
\hlineB{2.0}
\end{tabular*}
\caption{Codimensions of degeneracy manifold of two-by-two propagator $\A$ under constraints of different type of symmetries. The first column defines how the symmetry act on the cyclotron orbit, where $g\circ \bk$ (resp. $g\circ\frako$) is the image of $\bk$ (resp. $\frako$) under the the action of $g$. $|g\circ \frako=\frako|$ indicates the image of the orbit coincides with itself, regardless of orientation of the orbit. The next two columns are intrinsic properties of $g$. $u=0$ (resp. $u=1$) indicates the symmetry is a proper (resp. improper) transformation of the plane of the cyclotron orbit ($k_z=\text{constant}$). $g$ of $u=0$ (resp. $u=1$) does not flip (resp. flips) the orientation of the cyclotron orbit. $s=0$ (resp. $s=1$) indicates the symmetry is unitary (resp. antiunitary). In magnetic groups, antiunitary symmetry operations contain time reversal symmetry. The fourth column indicates whether this symmetry class applies to quasidegenerate propagator $\A$. For the five classes not applicable here, they are useful for Landau levels of fully degenerate bands, as discussed in Sec. \ref{sec:discussion}. The fifth column specifies additional conditions (on the representation of $g$) which are necessary to obtain a unique answer for codimension. $\breve{g}$ is the diagonalized, unitary matrix representation of $g$ in the degenerate subspace. The last column is codimension of the degeneracy manifold.\label{table:codimension}}
\end{table}

Sec. \ref{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown} illustrate that rotational symmetry imposes constraints on $\A$ and reduces codimension of its degeneracy manifold. This reduction of codimension is not limited to rotational symmetry.

Since magnetic field $B$ is applied externally, it does not change under the action of any symmetry operation. Hence any symmetry relevant in current context must keep $k_x-k_y$ plane untouched. By definition, $\A$ is a path-ordered exponential along the cyclotron orbit of the two-by-two Hamiltonian $\H$ and $\H$ is composed of a scalar $\delta\epsilon$ and a pseudovector $B\mathcal{M}$. Whether the symmetry $g$ transforms the cyclotron orbit to itself (denoted as $|g\circ\frako_0|=|\frako_0|$) or not ($|g\circ\frako_0|\ne|\frako_0|$) determines whether a self constraint can be imposed on $\A$. The former case can be again divided into two types, one for $g$ mapping every $\bk$ on the orbit to itself and one for at least one $\bk$ on the orbit being mapped to another point. Moreover, whether $g$ preserves the direction of cyclotron orbit (denoted as $u(g)=0$) or not (denoted as $u(g)=1$) indicates whether the path-order in $\A$ needs to be inversed. Besides the transformation of orbits, the transformation of $\H$ is also significant in determining the transformation of $\A$. As a scalar, $\delta\epsilon$ remains intact under the action of $g$ while in contrast $\mathcal{M}$ changes to $(-1)^{u+s}\mathcal{M}$, with $s(g)=0$ (resp. $s(g)=1$) denoting $g$ being unitary (resp. antiunitary). For $\H$ transforming consistently under $g$, $u+s=0, 2$ is required. The indicators defined above classifies symmetry operations into ten and only ten classes, presented in table \ref{table:codimension}.

With detailed codimension analysis delegated to App. \ref{app:codimension}, we present the result in table \ref{table:codimension}. To obtain a unique answer for codimension in some of the symmetry classes, we have to specify certain conditions for the symmetry representation: for $g$ that does not invert time ($s{=}0$), we specify certain conditions on  $\breve{g}$, the \emph{diagonalized} matrix representation  of $g$; for $g$ that inverts time  ($s{=}1$), we specify if the antiunitary representation of $g$ squares to $+I$ or $-I$.  Codimension 0, 1, 2 and 3 can be readily recognized in table \ref{table:codimension}. $T\mathfrak{r}_{x,\boldsymbol{c}/2}$ ($\mathfrak{r}_{x,\boldsymbol{c}/2}$ is glide plane translating in $z$ direction for half a lattice vector after flipping $x$ direction) at $k_z=\pi$ is an example of codimension 0, corresponding to class-6 (the 6th class in the table) \red{[Notice that I changed the name of the class. I begin to think class II-A bears more similarity to class-I and the original classification is not natural. Therefore, I abandoned the I, II-A and II-B. Do you agree?]} with condition $g^2=-1$. Due to similar reasons as Kramer's degeneracy, Landau-level quasidegeneracy are guaranteed for arbitrary parameter choice. Rotational symmetry belonging to class-3 has codimension 1, as confirmed by numerical study and arguments in Sec. \ref{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}. Codimension 2 is exemplified by $T\mathfrak{r}_x$ ($\mathfrak{r}_x$ is reflection in $x$ direction) belong to class-6 with $g^2=1$. Class-1 symmetries with $\breve{g}\propto I$, acting effectively as identity operator, imposes no constraints on $\A$ and thus no reduction in codimension.

\textbf{[for classes with codimension less than three, please give physical intuition and examples of symmetries where possible. For example, I-1 with breveg not proportional to identity merely reflects that different representations of a unitary symmetry do not hybridize at any point along orbit. give mirror symmetry as example.]}

\red{[need to define stable or robust]} Codimension 1 does not imply every degeneracy is robust, which is a stronger statement than degeneracy manifold can be found by tuning a parameter. If degeneracy manifold contains distinct components of different codimension, every degeneracy being robust implies all these components having codimension 1, which is generally not the case, as exemplified by rotational symmetry discussed in Sec. \ref{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}. Table \ref{table:codimension} only lists the smallest codimension, which is the number of parameters needed to find a degeneracy.

%We end this section by a general discussion of free parameters that is most tunable in experiments. In transport experiments, magnetic field $B$ is generally tunable; in tunneling spectroscopy experiments, both $B$ and bias voltage $E$ is tunable. If codimension of degeneracy is 1, as constrained by two types of symmetries in Table \ref{table:codimension}, Landau level degeneracies can be found by tuning either $B$ or $E$. We have argued in Sec. \ref{sec:qtznrules} that $\lambda_a$ varies slowly with respect to $B$ and $E$. Hence an \textit{aperiodic} beating pattern is expected by tuning either $B$ or $E$.

\section{Magnetic quantum Oscillations}\label{sec:qo}

We have shown that by tuning a single parameter $B$, Landau level quasidegeneracies can be found for some symmetry classes. In this section, we study how Landau level quasidegeneracies are reflected on magnetic quantum oscillations and more generally, possible implications of $\lambda_a$ on the oscillation pattern.

Traditionally, quantum oscillations of thermodynamic and transport quantities are best understood for nondegenerate orbits in the absence of breakdown; they originate from the periodic (in $1/B$) depopulation of discrete Landau levels as $B$ is ramped up. For spin-degenerate orbits in the absence of breakdown, it is the depopulation of every second Landau level that is periodic. With magnetic breakdown at isolated points, the harmonic content of quantum oscillations generically includes multiple periods corresponding to distinct orbits. A distinctive feature of spin-split bands is that quantum oscillations are generically aperiodic.

%In 2D electron systems, analysis of quantum oscillations is subtle since oscillations of the chemical potential may change the oscillating behaviour qualitatively. Therefore,

We will separately analyze the oscillations of two types of 2D electron systems distinguished by experimental environment: where (i) chemical potential is kept constant and (ii) particle density is kept constant. To analyze quantum oscillations in case (i), it is advantageous to have a Lifshitz-Kosevich-type formula so that Fourier-like components may be separately analyzed. Lifshitz-Kosevich formula have been derived in the absence of breakdown, and in the presence of magnetic breakdown at isolated points [Kaganov, lifshitz]; here we report that a Lifshitz-Kosevich formula also exists for coupled spin-split bands:\footnote{This formula corrects a factor of two in our previous work [topofermi].} In particular, for de Hass-van Alphen (dHvA) oscillation, the oscillatory component of the magnetization has the form
\begin{equation}
\delta M=-\frac{1}{2\pi}\frac{k_BT}{B}S\sum_{a=1}^D\sum_{r=1}^{\infty}e^{-\frac{r\pi}{\omega_c\tau}}\frac{\text{sin}[r(l^2S+\lambda_a+\gamma_a)]}{\text{sinh}(2\pi^2rk_BT/(\hbar\omega_c))},\label{eq:LK}
\end{equation}
where the argument of the sinuisoidal functions involve quantities from our generalized quantization rule, $T$ is temperature and $\tau$ is Dingle scattering lifetime. All the quantities on the right handside of Eq. (\ref{eq:LK}) are evaluated at Fermi energy. For 3D systems, Lifshitz-Kosevich formula is in a similar form, presented in Ref. [topoferm]. If temperature is large compared to the cyclotron frequency and/or $1/\tau$ is large, it is well-known that only the lowest harmonics ($r\sim 1$) are observable. If right handside of Eq. (\ref{eq:LK}) is contributed by two orbits, the most important oscillating part is the sum of two sine functions and $\lambda_a$ there determines whether the two sine functions are added constructively ($\delta \lambda=0$, corresponding to Landau level quasidegeneracy) or destructively ($\delta\lambda=\pi$). $\delta\lambda$ here is defined as $\delta\lambda:=|\lambda_1-\lambda_2| \mod 2\pi$. This interference phenomenon has been studied previously for spin splitting factor [topofermi], where $\lambda$ is field independent. For quasi-degenerate bands, $\lambda$ here is field dependent. Since $\lambda$ varies slowly with respect to magnetic field compared to leading term $l^2S$, a beating pattern is expected. Generically, $\delta \lambda$ nonlinearly depends on $l^2$, leading to an \textit{aperiodic} beating in the dHvA oscillation. Figure \ref{fig:qo} (a) shows the evolution of $\delta\lambda$ with respect to magnetic field for various parameters of Rashba-Dresselhaus system. Whenever $\delta\lambda$ reaches $\pi$ (resp. $0$), a beating node (resp. antinode) is expected.

%surface states of 3D solids (insulators and metals, of both trivial and topological categories), as well as (ii) 2DEG in semiconductor heterostructures or 2D materials on substrates. Quantum oscillations of the chemical potential are generically negligible in case (i),

% \footnote{Suppose $\mu$ is the field-dependent chemical potential of a 3D solid with surface states. Since $\mu$ is an intensive quantity, it may be approximated by the chemical potential $\mu'$ corresponding to the same 3D solid but with periodic boundary conditions in three independent directions. If said solid is an insulator, $\mu'$ would depend smoothly on $B$; if said solid is a metal, the quantum oscillations of $\mu'$ have negligible amplitude so long as the Fermi surface is not highly anisotropic.[lifshitz,kosevich] } and non-negligible in case (ii).

As will be shown below, for quantum oscillations in case (ii), $\delta\lambda$ also governs the oscillation pattern. For concreteness we consider Schubnikov-de Haas (SdH) oscillations of the conductivity. With the assumption of constant particle density, period of quantum oscillation without magnetic breakdown is solely determined by particle number density $n_e$ as $e/n_eh$ [Vinter]. Minimum of conductivity occurs right at the point when one Landau level is completed depopulated, i.e., when the chemical potential jumps. However, these minimums may be smeared out by temperature or disorder. Whether the minimums are vulnerable to smearing depends on the Landau level gap, i.e., the magnitude of the jump of chemical potential. Larger Landau level gap prevents the conduction minimum from being smeared out and thus corresponds to oscillation of larger magnitude. This Landau level gap is governed by $\delta\lambda$. We plot in Fig. \ref{fig:qo} (b) lower panel chemical potential oscillation with respect to $1/B$ under the assumption of zero energy and zero Landau level broadening where $\delta\lambda{\approx}2\pi$, $\delta\lambda{\approx}3\pi/2$, $\delta\lambda{\approx}\pi$ respectively; the corresponding Landau-level dispersions are obtained from exact diagonalization and plotted in upper panel of Fig. \ref{fig:qo} (b). As expected, close to Landau level quasidegeneracy ($\delta\lambda\approx 0$), half of the oscillations are smeared out and the oscillation period has effectively doubled. This behavior is further confirmed by the oscillation of chemical potential plotted in lower left plot of Fig. \ref{fig:qo} (b). As a contrast, middle column of Fig \ref{fig:qo} (b) shows Landau levels and chemical potential oscillation for $\delta\lambda\approx 3\pi/2$, when quantum oscillation are expected to exhibit large and small oscillations. For $\delta\lambda\approx\pi$, the two sets of Landau levels are equally spaced and quantum oscillation are expected to reveal the particle density of the system. Therefore, for 2D fixed particle density systems, both oscillation period and oscillation magnitude are beating \textit{aperiodically} with respect to magnetic field.

It is well known that quantum oscillations from two independent cyclotron orbits (but with similar area in reciprocal space) may also exhibit periodic beatings. This is due to Landau levels corresponding to the two orbits may also cross approximately (with a splitting $\sim e^{-c/B}$). Such crossings are not so surprising, and merely reflect that distinct orbits are essentially uncoupled; this is very much analogous to the crossing of levels having different symmetry eigenvalues. In contrast, for weakly spin-split bands, the two orbits are strongly coupled by tunneling, hence there are no obvious `symmetry eigenvalues'; nevertheless crossings exist and are tunable by $B$. The hybridization of the two sets of Landau levels destroy the periodic nature of approximate crossings and is reflected in an \emph{aperiodic} beating pattern.
\textbf{
[We should say that experimental groups (e.g. Das) have already been fitting the beating in oscillations to cos(Laurent series in B), with phenomenological coefficients. Here we provide the microscopic derivation of these coefficients.  ]}

% Another distinction: for localized breakdown, crossings occur only at $B\approx 0$, while for nonlocal breakdown they recur aperiodically  at fields denoted $B_n$. The recurrence interval for $1/B_n$ is much larger than the period of quantum oscillations, leading to an aperiodic beating effect in the quantum oscillations.

\begin{figure}
\includegraphics[width=1.0\columnwidth]{qo.png}
\caption{Quantum oscillation of Rashba-Dresselhaus system. (a) Evolution of $\delta\lambda$ with respect to field for different value of $\beta$. Horizontal grey lines are $\delta\lambda=\pi$. Upper panel of (b): Landau levels near fields indicated by vertical grey lines in right panel of (a) at $\beta=0.02$eV$\cdot$\AA, corresponding to $\delta\lambda=2\pi$, $\delta\lambda=3\pi/2$ and $\delta\lambda=\pi$ respectively. The line of $\beta=0.02$eV$\cdot$\AA~is indicated by a black arrow in (a). Lower panel (b): Oscillations of chemical potentials corresponding to upper panel. Fixed partical number density is assumed. In this figure, other parameters are $m=0.01$/(eV$\cdot$\AA$^2$), $\alpha=0.05$eV$\cdot$\AA~and $E=0.4$eV.
\label{fig:qo}}
\end{figure}

\section{Discussion and outlook}\la{sec:discussion}

Landau level quasidegeneracy is not limited to quasidegenerate bands. For degenerate bands, a similar definition is applicable: \red{[need to check]}
\e{ \f{E_{1}-E_2}{\var_c}\bigg|_{\bar{B}} = O\left(\f{\var_c}{E} \right). } Landau levels of degenerate bands are characterized by a propagator $\A'$ similar to Eq. (\ref{eq:prop}) [100p]. Codimension analysis can be carried out similarly and the results are presented in table \ref{table:codimension}. Unlike $\A$, all ten classes of symmetries impose constraints on $\A'$ and thus entries not applicable to $\A$ are useful for $\A'$. For spin-split bands, $\lambda$ depends strongly on the $B$ field for quasidegenerate orbits; for degenerate orbits, the $B$-dependence of $\lambda$ is relatively weaker, i.e., of higher power in the small parameter $B$ [Roth, Niu, Fuchs]. A more useful tuning parameter in the latter case would be the bias voltage in tunneling spectroscopy experiments.

We have assumed in the above sections that the two-fold quasidegeneracy is due to small SOC. More generally, two-fold degenerate bands can be perturbed into quasidegenerate bands by symmetry breaking. From this viewpoint, our previous assumption of small SOC breaks continuous spin rotational symmetry which protects the degeneracy of spin up and spin down states. Other common symmetry operations capable of protecting two fold degeneracy are $T\mathfrak{i}$ and $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$ at $k_z=\pi$, where $T$ is time reversal symmetry; $\mathfrak{i}$ is inversion symmetry and $\mathfrak{c}_{2z,\boldsymbol{c}/2}$ is two-fold screw rotation in $z$ direction. Table \ref{table:codimension} is applicable to quasidegenerate bands ($\A$) perturbed from degenerate bands protected by all the three symmetries and degenerate bands ($\A'$) due to $T\mathfrak{i}$ or $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$. For degenerate bands protected by continuous spin rotation, codimension is at most 1 since $\A'$ is diagonal in spin basis. Codimension analysis without assumption of degenerate bands being protected by the three symmetries are presented in App. \ref{app:codimension}, where codimensions of Landau level quasidegeneracy for possibly fine tuned degenerate/quasidegenerate bands can be found.

\begin{table}
\begin{tabular*}{\columnwidth}{l@{\extracolsep{\fill}}ccc}
\hlineB{2.0}
 symmetry  & origin of degen. & $\breve{g}\propto$ \\
\hline 
 $\mathfrak{t} \mathfrak{r}_x^n \mathfrak{r}_z^m$ & $T\mathfrak{i}$ & $\sigma_z$ \\
  $\mathfrak{t} \mathfrak{r}_x^n \mathfrak{r}_z^m$ & continuous spin rotation & $\sigma_z$ \\
 $\mathfrak{r}_z$, $\mathfrak{r}_x$, $\mathfrak{r}_{x,\boldsymbol{c}/2}\mathfrak{r}_z$ & $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$ & $I$ \\
$\mathfrak{r}_{x,\boldsymbol{c}/2}$, $\mathfrak{r}_x \mathfrak{r}_z$  & $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$ & $\sigma_z$ \\
\hlineB{2.0}
\end{tabular*}
\caption{Two by two sewing matrices for reflections and glide planes. The second column specifies the origin of two fold degeneracy. Glide operation in $x$ or $y$ direction is irrelevant; for example, $\mathfrak{r}_x$ and $\mathfrak{r}_{x,\boldsymbol{b/2}}$ share the same entry. $x$ and $y$ are equivalent; for example, $\mathfrak{r}_x$ and $\mathfrak{r}_y$ share the same entry. $\mathfrak{t}$ is (arbitrary) translation. When the two-fold degeneracy is protected by $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$, $k_z=\pi$ is assumed.\label{table:sewing-matrix}}
\end{table}

Table \ref{table:codimension} has introduced diagonalized representation matrix $\breve{g}$ and has used it to obtain a definite answer for codimension for some classes. Fortunately, in most cases, $\breve{g}$ can be calculated without knowing the wave functions of the bands. In addition, symmetry operations whose sewing matrices are needed are mostly reflections (for example, reflection in $x$ direction $\mathfrak{r}_x$) and glide planes (for example, $\mathfrak{r}_{x,\boldsymbol{c}/2}$ where $\boldsymbol{c}$ is lattice vector in $z$ direction). Therefore, for convenience, we presented in table \ref{table:sewing-matrix} sewing matrix for common reflections, glide planes and combination of them. In most scenarios, given the space group, table \ref{table:codimension} and \ref{table:sewing-matrix} are adequate to determine the codimension of Landau level quasidegeneracy.

% Our conclusion that spin-degenerate Landau levels may be obtained by tuning a single parameter  may seem to contradict a theorem by Wigner and von Neumann that states the codimension of degeneracies of a complex Hermitian matrix is three; in our context this matrix is the Peierls-Onsager Hamiltonian whose spectrum corresponds to Landau levels. This theorem leads to the famous ``no-crossing rule" in physics, which states that generically there are no crossings of energy levels of Hamiltonians defined over  one- or two-dimensional parameter spaces. To reconcile our findings with this theorem, one should recognize that any energy level obtained from a semiclassical quantization rule is only asymptotically accurate (in powers of $B$, and the spin-orbit coupling). A degeneracy obtained from this approximation scheme may in principle be split on a scale of order $\var_c^2/E$ or $\var_c\var_s/E$; in principle, the approximation can be improved order by order. This distinction between asymptotically-accurate and exact degeneracies  affords a reconciliation with the Wigner-von Neumann theorem, but should  not typically be resolvable in experiments  due to the broadening effects of  temperature and disorder-induced scattering.

\textbf{[comment on higher-order-in-B corrections to lambda, which will lead at ultra-high fields to landau-level quasidegeneracies]}

%In summary, we have developed a theory to calculate landau levels in the case of quasidegenerate orbits. This theory is asymtotically correct with small $k$ space splitting and works equally well if there are band touchings between the two quasidegenerate orbits. Aperiodic beating pattern in quantum oscillation is predicted to be observed in such systems.

\begin{acknowledgments}

We are grateful to Nicholas Read and Judith H\"oller for clarifying notions related to codimensions of matrix degeneracies. 
We acknowledge support by  the Yale Postdoctoral Prize Fellowship (AA), NSF DMR Grant No.\ 1603243 (LG),  the Ministry of Science and Technology of China, Grant No.\ 2016YFA0301001 (CW and WD), and the National Natural Science Foundation of China, Grants No.\ 11674188 and 11334006 (CW and WD). This work was performed in part at Aspen Center for Physics, which is supported by National Science Foundation grant PHY-1607611.
\end{acknowledgments}

\bibliography{paper}

%\part{Supplementary Material}

\appendix

\section{Review of effective Hamiltonian}\label{app:revieweffham}

Effective Hamiltonian lies in the heart of semiclassical theory. The leading order term (with respect to $B$) of effective Hamiltonian in momentum representation can be obtained by Peierls substitution of crystal momentum $\boldsymbol{k}$: $\boldsymbol{k}\to\boldsymbol{K}=\boldsymbol{k}+\frac{e}{\hbar}\boldsymbol{A}(i\nabla_{\boldsymbol{k}})$ in zero field band structure $H_{0}(\boldsymbol{K}):=\epsilon(\boldsymbol{k})$, where $\boldsymbol{A}$ is vector potential. Components of $\boldsymbol{K}$ do not commute with each other, thus substituting $\boldsymbol{k}$ to $\boldsymbol{K}$ is performed in a Weyl-symmetric manner that can be formally done using Fourier transformation. Wave functions in momentum representation are represented as $\phi=\sum_{\boldsymbol{k}}f_{\boldsymbol{k}}\psi_{\boldsymbol{k}}$, where $\psi_{\boldsymbol{k}}$ is modified Bloch wave function whose specific form is presented in [Roth]. The effective Hamiltonian then acts on $f_{\boldsymbol{k}}$, changing Shr\"odinger equation to:
\begin{equation}
(H(\boldsymbol{K})-E)f_{\boldsymbol{k}}=0.\label{eq:schrodinger}
\end{equation}
Subleading order term of effective Hamiltonian $H_{1}(\boldsymbol{K})$ is also obtained by substituting $\boldsymbol{k}$ to $\boldsymbol{K}$ in $H_{1}(\boldsymbol{k})$, where $H_{1}(\boldsymbol{k})$ encodes information of non-Abelian Berry phase, orbital magnetization and Zeeman energy. Assuming a magnetic field $B$ in $-z$ direction,
\begin{equation}
H_{1}(\boldsymbol{k})=eB\epsilon^{\alpha\beta}\mathfrak{X}^{\beta}v^{\alpha}+BM^{z}-g\mu_{B}B\sigma^{z}
\end{equation}
where $[\mathfrak{X}^{\alpha}]_{nm}=i\langle u_{n\boldsymbol{k}}|\partial_{k^{\alpha}}u_{m\boldsymbol{k}}\rangle$ is Berry connection, $[v^{\alpha}]_{nm}=\frac{1}{\hbar}\delta_{nm}\partial_{k^{\alpha}}\epsilon$ is band velocity, $M^{z}$ is orbital magnetization, $g\approx 2$ is the free-electron g-factor and $\mu_{B}$ is the Bohr magneton. Eq. (\ref{eq:schrodinger}) can be solved by WKB approximation. To the leading order, solution of Eq. (\ref{eq:schrodinger}) is Zilberman function
\begin{equation}
f_{k}=\frac{c}{\sqrt{|v^{x}|}}e^{ik_{0}^{x}k^{y}l^{2}}e^{-il^{2}\int k^{x}dk^{y}}\delta_{k_{0}^{x}k^{x}},
\end{equation}
where $c$ is an arbitrary constant and the integration is performed along constant energy contours. $k^x$ is a constant of motion in Landau gauge, which is why a $\delta_{k_{0}^{x}k^{x}}$ appears in Zilberman function.

\section{Proof of quasi-degenerate quantization rule\label{app:quantizationruleproof}}

\textbf{Give some motivation for why we might care about quasidegeneracy greater than two. E.g, new fermions, accidental degeneracies, mirror planes??}

Since $\delta S=0$ without $\alpha\mathcal{W}$, $\alpha$ is proportional to $\delta S$ up to linear order. A good example is Rashba Hamiltonian in the main text, where $\delta S=4\pi m\alpha\sqrt{2m\epsilon}+\text{O}(\alpha^2).$  Thus 
\begin{equation}
\mathcal{H}=
\mathcal{H}_0+\delta S \mathcal{W}'+\text{O}(\delta S^2),
\end{equation}
where $\delta S \mathcal{W}'=\alpha \mathcal{W}$.
We seek a generalized quantization condition of the form 
\begin{equation}
l^{2}S+\lambda_{a}+\gamma=2\pi n.
\end{equation}
In previously-studied quantization rules for non-degenerate and degenerate band subspaces, $\lambda$ is field-independent and of order one. The additional small parameter in quasi-degenerate magnetotransport allows to formulate a dimensionless quantity that is of order one: $l^2\delta S$. We therefore posit a field-dependent $\lambda$ that is  of order $\text{O}(1,l^2\delta S)$.

To obtain a quantization rule up to order $\text{O}(1,l^2\delta S)$, we need to formulate an effective Hamiltonian that is accurate to $\text{O}(l^{-2},\delta S)$.  Following the
idea of [Roth], it is not difficult to verify this effective Hamiltonian for a specific band is 
\begin{align}
H &= H_{0,0}+H_{1,0}+H_{0,1}+\text{o}(l^{-2}, \delta S),\\
H_{0, 0}&=\epsilon_0(\boldsymbol{K}),\\
[H_{0, 1}]_{nm}&=\delta S [\mathcal{W}'(\boldsymbol{K})]_{nm} = \alpha [\mathcal{W}(\boldsymbol{K})]_{nm},
\end{align}
where $\epsilon_0$ is band dispersion of $\mathcal{H}$ and $H_{1,0}(\boldsymbol{k})$ is still Eq. (\ref{eq:H1}) evaluated in the absence of $\alpha\mathcal{W}$. $\text{o}$ here is small-o notation

We now group the  terms in effective Hamiltonian as $\tilde{H_0}=H_{0,0}$ and $\tilde{H}_{1}:=H_{1,0}+H_{0,1}$. The Schr\"odinger equation is now
\begin{equation}
(\tilde{H}_{0}(\boldsymbol{K})+\tilde{H}_{1}(\boldsymbol{K})-E)f=\text{o}(l^{-2}, \delta S).
\end{equation}
Similar to what is done in [100page], we seek the solution to the Schr\"odinger equation using superposition\textbf{[strange way to put it]} of Zilberman-Fischbeck functions
\begin{equation}
\boldsymbol{f}=A\boldsymbol{f}^{0},
\end{equation}
where 
\begin{equation}
f_{a}^{0}=c_{a}\frac{1}{\sqrt{|v_0^{x}|}}e^{ik_{0}^{x}k^{y}l^{2}}e^{-il^{2}\int k^{x}dk^{y}}\delta_{k_{0}^{x}k^{x}}.
\end{equation}
$A$ is a square matrix with the assumption $A_{ab}$ is of order $O(1,l^2\delta S)$. Following section V of [100page], we have:
\begin{widetext}
\begin{equation}
[H_{0}(\boldsymbol{K})]_{ab}A_{bc}f_{c}^{0}=A_{ac}\epsilon_0(\boldsymbol{K})f_{c}^{0}+il^{-2}\partial_{y}A_{ac}\hbar v_0^{x}f_{c}^{0}+\text{o}(l^{-2}, \delta S),
\end{equation}
and
\begin{equation}
[\tilde{H}_{1}(\boldsymbol{K})]_{ab}A_{bc}f_{c}^{0}=[\tilde{H}_{1}]_{ab}A_{bc}f_{c}^{0}+\text{o}(l^{-2}, \delta S).
\end{equation}
\textbf{[Let's clarify at what wavevector tildeH1 is supposed to be evaluated. Let's also write out explicitly the next order term in B10, which is proportional to the spin-orbit-induced change in the band velocity. At two points in the paper, I said that the relative change in velocity must be small, so here it will be justified. ]}
\end{widetext}

Sch\"rodinger equation then becomes 
\begin{equation}
il^{-2}\partial_{y}A_{ac}\hbar v^{x}f_{c}^{0}+[\tilde{H}_{1}]_{ab}A_{bc}f_{c}^{0}=\text{o}(l^{-2}, \delta S).
\end{equation}
We want the above equation to hold for any $\mathbf{c}$, so 
\begin{equation}
\hbar\partial_{y}A_{ac}=il^{2}[v^{x\nu}]^{-1}[\tilde{H}_{1}]_{ab}A{}_{bc},
\end{equation}
thus
\begin{equation}
A=\overline{\text{exp}}[il^{2}\int\frac{\tilde{H}_{1}}{\hbar v_0^{x}}dk^{y}].
\end{equation}
$\lambda_{a}$ are again given by eigenphases of propagator $A$ along a complete orbit
\begin{equation}
\mathcal{A}[\mathfrak{o}]=\overline{\exp}[il^{2}\oint_{\mathfrak{o}}\frac{\tilde{H}_{1}}{\hbar v_0^{x}}dk^{y}].
\end{equation}

\section{Consistency conditions for our quantization rule}\la{sec:slowvariation}

The following are consistency conditions for our quantization rule:
\e{ |l^2S| \gg |\lambda_a|,\, \left|l^2\p{S}{E}\right| \gg \left|\p{\lambda_a}{E}\right|,\, \left|S\right| \gg \left|\p{\lambda_a}{l^2}\right|.} 
Due to the latter two inequalities, we shall refer to $\lambda_{a}$ as \textit{slowly-varying} (with respect to $E$ and $B$), in comparison with the rapidly-varying $l^2S$. To appreciate the difference in scales, consider that for $\lambda_a$ to change by $2\pi$ due to a variation $l^2$ (at fixed energy), we estimate [in the weak-field regime; cf.\ \q{phaseindependentorbit}] that $l^2$ must change on the scale of $2\pi/\delta S$; this scale is much greater than the period of quantum oscillations ($T_{1/B}{:}{=}2\pi/ S$), by our assumption of quasidegeneracy. Analogously, for $\lambda_a$ to vary by $2\pi$ due to a variation of $E$ (at fixed field) by $\delta E$, we estimate [from \q{phaseindependentorbit}] that $\delta E {\sim} 2\pi/l^2 (\partial \delta S/\partial E)$, which is generically much larger than the cyclotron energy $\epsilon_c{=}2\pi/l^2 (\partial  S/\partial E)$. In the strong-field regime (where $\delta \var$ may be neglected from \q{eq:H1}), $\lambda_a$ is independent of $B$ (to the accuracy of our semiclassical theory\textbf{[add footnote to describe higher order corrections]}), and depends on $E$ solely through the slow variation of $\calm$.  In the absence of symmetry, we  estimate 
\e{\p{\lambda_{a}}{E}=\order\left(\f{g_s}{m_0}\p{m}{E},\f{\partial^2S/\partial E^2}{\partial S/\partial E} \right)\ll \f{2\pi}{\var_c},} 
where $\order(a,b)$ is defined as the order of magnitude of either $a$ or $b$ (whichever is larger), $m_0$ is the free-electron mass, and $m{=}\hbar^2(\partial S/\partial E)/2\pi$ the effective mass. The first argument of $\order$ originates from the energy dependence of the effective g-factor (with $g_s$ the free-electron g-factor, and $m/m_0$ the dimensionless effective mass); the second argument accounts for possible non-analyticities in the area of $\frako_0$, which may originate from saddle- or II-Dirac points in the zeroth-order band Hamiltonian.

\section{Existence of Landau-level quasidegeneracy}\la{sec:proofLLquasideg}

This appendix demonstrates that, if a degeneracy of $\cala$ [$e^{i\lambda_+}{=}e^{i\lambda_-}$] occurs at $(\bar{E},\bar{B})$, there exists two Landau levels in close proximity to $(\bar{E},\bar{B})$ which satisfy the quasidegeneracy conditions defined in \qq{llquasideg}{llquasidegB}.

To begin, it is useful to define
\e{ \calq_{\pm}(E,B):= \f1{2\pi}\left(l^2S +\lambda_{\pm} -\gamma \right)}
such that the quantization rule \q{eq:rule} is satisfied if $\calq_{\pm}(E,B){\in}\Z$. 
Generically, either of $m_{\pm}:=\calq_{\pm}(\bar{E},\bar{B})\in \R$ is not integer-valued, but 
\e{\big(\calq_{+}-\calq_{-}\big)\bigg|_{\bar{E},\bar{B}}=\f{\lambda_+-\lambda_-}{2\pi}\bigg|_{\bar{E},\bar{B}} \in \Z. \la{diffinteger}} 
Let $n_{\pm}$ be the closest integer to $m_{\pm}$ (this implies $|n_{\pm}-m_{\pm}|<1$).  From \q{diffinteger}, we deduce that $n_+-m_+$ is equal to $n_--m_-$; this quantity is henceforth denoted as $r:= n_{\pm}-m_{\pm}$, and  $\calq_{\pm}(\bar{E},\bar{B}){+}r{\in} \Z$.

Let us first tackle \q{llquasideg}. We define $E_{\pm}$ such that $\calq_{\pm}(E_{\pm},\bar{B}){=}\calq_{\pm}(\bar{E},\bar{B}){+}r{\in} \Z$. Since  $\lambda_{\pm}$ is a slowly varying function of $E$ relative to $l^2S$, $|E_{\pm}{-}\bar{E}|/\var_c{\approx} |r|{<}1$, with the cyclotron energy $\var_c=2\pi/l^2|\partial S/\partial E|$ evaluated at $(\bar{E},\bar{B})$. Let us denote $O':=\partial O/\partial E$ evaluated at $(\bar{E},\bar{B})$. We estimate
\e{\f{E_+-E_-}{\var_c} \approx &\; \f{r}{\var_c}\left(\f1{\calq'_+}-\f1{\calq'_-}\right)\approx  \f{r}{2\pi}\var_c \left( \lambda'_- -\lambda'_+\right). \la{estimate}}
What is left is to estimate $\lambda_{\pm}'$, which we have accomplished in \s{sec:qtznrules} in both weak- and strong-field regimes. Combining our estimates for $\lambda'$ with \q{estimate}, we  arrive at \q{llquasideg}.

%From \s{sec:qtznrules}, we know that for sufficiently weak field ($\var_c\ll \Delta$), $\lambda_{\pm}'\approx \pm l^2\delta S'/2$. For $\var_c\gg \Delta$, $\lambda_{\pm}'$ is determined by the energy dependence of the field-dependent terms in the effective Hamiltonian $\calh$.

Let us next tackle \q{llquasidegB}. It is most convenient at this point to change variables from $B\rightarrow l^2$ (the square of the magnetic length). Let us  define   $l^2_{\pm}$ such that $\calq_{\pm}(\bar{E},l^2_{\pm}){=}\calq_{\pm}(\bar{E},l^2_{\pm}){+}r{\in} \Z$. We denote  $\dot{O}:=\partial O/\partial(l^2)$ evaluated at $(\bar{E},\bar{B})$, and estimate
\e{\f{l^2_+-l^2_-}{T_{\sma{1/B}}} \approx  \f{r }{2\pi}T_{\sma{1/B}} \left( \dot{\lambda}_- -\dot{\lambda}_+\right)=O\left(\f{\delta S}{S}\bigg|_{\bar{E}}\right). \la{estimateB}}
The order-of-magnitude estimate is obtained in the limit $\var_c\ll \Delta$, where $\lambda_{\pm}\approx \pm l^2\delta S/2$ [cf.\ \q{phaseindependentorbit}]. In the opposite limit $\Delta\gg \var_c$, $\lambda_{\pm}$ is independent of $B$ within the accuracy of our semiclassical theory.

\section{Codimension of Landau level quasidegeneracy}\la{app:codimension}

In this appendix, we expose mathematical details of symmetry analysis of the quasidegenerate propagator $\A$ and derive symmetry constrained codimension of degeneracy manifold. We restrict our analysis to two-by-two $\A$.

\begin{table*}[t]
\begin{tabular*}{2\columnwidth}{l@{\extracolsep{\fill}}ccccccc}
\hlineB{2}
             & $u$ & $s$ & symmetry constraint & $\det{\A}$ & $\breve{g}$ & codimension \\
\hline
(I) $\forall \bk \in \frako$, $g\circ \bk=\bk$ & 0 & 0 & $\A=\breve{g}\A\breve{g}^{-1}$ & - & $\breve{g}\propto I$ & 3  \\
&  &  &  & - & $\breve{g} \not\propto I$ & 1  \\
& 0 & 1 & $\A=\breve{g}\A^*\breve{g}^{-1}$ & 1 & $(\breve{g}K)^2=I$ & 1 \\
&  &  &  & 1 & $(\breve{g}K)^2=-I$ & 3 \\
&  &  &  & -1 & $(\breve{g}K)^2=I$ & $\infty$ \\
&  &  &  & -1 & $(\breve{g}K)^2=-I$ & $\times$ \\
(II-A) $|g\circ \frako| = |\frako|$ & 0 & 0 & $\A=\breve{g}(g^{L-1}\circ\bk_0)\prod_{i=0}^{L-1} \A_{1/L}$ & - & - & 1 \\
$\exists \bk \in \frako, g\circ \bk\ne\bk$ & 0 & 1 & $\A=\breve{g}(g^{L-1}\circ\bk_0)\prod_{i=0}^{L-1} K^i\A_{1/L}K^i$ & - & $L=N$ & 1 \\
& & & & 1 & $L\ne N$ & 1 \\
& & & & -1 & $L\ne N$, $(\breve{g}K)^2=I$ & $\infty$ \\
& & & & -1 & $L\ne N$, $(\breve{g}K)^2=-I$ & $\times$ \\
& 1 & 0 & $\A=\breve{g}\A^\dagger\breve{g}^{-1}$ & 1 &$\breve{g} \propto \sigma_z$& 2\\
& & & & 1 &$\breve{g} \not\propto \sigma_z$ & 0\\
& & & & -1 &$\breve{g} \propto I$ & 2\\
& & & & -1 &$\breve{g} \not\propto I$& 0\\
& 1 & 1 & $\A=\breve{g}\A^T\breve{g}^{-1}$ & - & $(\breve{g}K)^2=I$ & 2 \\
& & & & - & $(\breve{g}K)^2\ne I$ & 0 \\
(II-B) $|g\circ \frako| \ne |\frako|$ & 0 & 0 & $\A_2=\breve{g}\A_1\breve{g}^{-1}$ & - & - & 3 \\
& 0 & 1 & $\A_2=\breve{g}\A_1^*\breve{g}^{-1}$ & - & - & 3\\
& 1 & 0 & $\A_2=\breve{g}\A_1^\dagger\breve{g}^{-1}$ & - & - & 3\\
& 1 & 1 & $\A_2=\breve{g}\A_1^T\breve{g}^{-1}$ & - & - & 3 & \\
\hlineB{2}
\end{tabular*}
\caption{ \textbf{[for II-A-1, you might replace product with a power, and breveg by a phase factor; it looks a little disconcerting that L-1 is specially chosen in the argument. ]} Codimensions of degeneracy manifold of $\A$ or $\A'$ under constraints of different type of symmetries. Most of the symmetry constraints on $\A$ are reproduced from Ref. [100p] except for the first two classes in type II-A, where a special gauge is chosen. $\infty$ in the codimension column denotes that eigenvalues of $\A$ cannot be degenerate; $\times$ denotes an entry where we cannot self-consistently impose the symmetry constraint and the conditions on det$\A$ and $\breve{g}$ for a two-by-two unitary $\A$. In the second to last column, $\breve{g}$ is either chosen to be diagonal or off-diagonal \label{table:fullcodimension}}
\end{table*}

Since direction of external magnetic field is fixed (pointing to $-z$ direction in our convention), only symmetry operators mapping $z$ to $\pm z$ are relevant for cyclotron orbits. These symmetry operators can be classified into ten and only ten classes [100p]. The classification is based several indicators of symmetry operator $g$, namely $u(g)=0~(1)$ representing $g$ is a proper (improper) rotation of the cyclotron orbit and $s(g)=0~(1)$ representing $g$ is unitary (antiunitary). However, unlike Ref. [100p], only five out of ten symmetry classes impose constraints on $\A$. This reduction of relevant symmetry classes is due to components of $\calh$ transforming differently under symmetry operations. $\delta\epsilon$ transforms as a scalar but orbital moment and spin transforms as a pseudovector. The five symmetry classes are tabulated in Table \ref{table:codimension} in the main text. Here we calculate codimension of degeneracy manifold for all the ten classes since the other five classes are relevant for quantization rule of degenerate bands.

Sewing matrix is necessary to express the constraints on the propagator $\A$. \red{For a symmetry operator $\hat{g}$ acting on wave functions as $\hat{g}|\psi(\br)\rangle=|\psi(g^{-1}\br)\rangle$ [Really need to introduce $\check{g}$?]}, the sewing matrix $\breve{g}$ is defined as 
\e{
   \breve{g}_{nm} = \langle u_{n,g\circ\bk}|\hat{g}(\bk)|u_{m,\bk} \rangle K^{s(g)}.
}
Here, $K$ is complex conjugation; $\hat{g}(\bk)=e^{-i\bk\cdot\hat{\br}}\hat{g}e^{i\bk\cdot\hat{\br}}$; $g\circ\bk$ is the image of $\bk$ under the action of $g$; $n$ and $m$ \textbf{[m=1,2,n=1,2]} runs over the degenerate subspace. Diagonalized representation matrix of unitary $\hat{g}$ introduced in the main text is sewing matrix in a special gauge, so we use the same symbol $\breve{g}$. \textbf{[introduce what this gauge freedom is, and what are gauge-invariant quantities]}

Sewing matrix is needed to express symmetry constraints since there is an ambiguity in choosing the basis of degenerate subspace. Therefore, it can be drastically simplified if a good basis is chosen. \textbf{[give equation for how breveg is transformed with a different gauge choice]} Generally, we have the following rules for two-by-two sewing matrix:
\begin{itemize}
\item If $g\circ\bk\ne\bk$, $\breve{g}(\bk)$ can be transformed into identity matrix by a gauge transformation.
\item If $g\circ\bk=\bk$ and $\hat{g}$ is unitary, $\breve{g}(\bk)$ can be transformed into a diagonal matrix by a gauge transformation.
\item If $g\circ\bk=\bk$ and $\hat{g}$ is antiunitary, $\breve{g}(\bk)$ can be transformed into an off-diagonal matrix (diagonal terms are 0) by a gauge transformation.  For the special case of $\hat{g}$ that is order-2, $\breve{g}$ can be transformed into either $\sigma_z$  or $i\sigma_y$. We define order $N$ of $g$ as the smallest positive integer fulfilling $g^N$ is identity, $2\pi$ rotation, lattice translation or products of them. \textbf{[this definition of order should be moved up to above paragraphs where you introduce basic manipulations of sewing matrix]}
\end{itemize}
The first two claims are obvious \textbf{[it's only obvious once you give the equation for gauge-transform of breveg]} and the last claim can be verified by a direction calculation showing diagonal terms can be eliminated by a gauge transformation no matter what $\breve{g}$ is at the beginning. \textbf{[add this last proof in separate appendix]}

The symmetry constraints on $\A$ expressed using sewing matrix is presented in Ref. [100p] and reproduced in Table \ref{table:fullcodimension} for convenience. Generally, these constraints are derived using the following relation
\e{
&\A[g\circ \bk_f\leftarrow g\circ \bk_i] \nonumber\\
&=e^{i\phi}\breve{g}(\bk_f)K^{s(g)}\A[\bk_f\leftarrow \bk_i]K^{s(g)}\breve{g}^{-1}(\bk_i),\label{eq:propsymm}
}
\textbf{[define K to the power]} where $\A[\bk_f\leftarrow \bk_i]$ is a segment of the propagator from $\bk_i$ to $\bk_f$ along the cyclotron orbit. $e^{i\phi}$ is a phase factor that appears for $g$ that is a nonsymmorphic element; however this phase always drops out[100page] for closed orbits and will be neglected in the subsequent analysis.

For four of  the ten classes (class II-B), the symmetry relates the propagators of distinct and disconnected orbits, but each propagator (corresponding to one orbit) is itself unconstrained.  Therefore, the codimensions are still 3 \textbf{[must be careful in presentation, how do we distinguish orbit degeneracies from the spin degeneracies that is the focus of this work]}. For the other six classes, a case by case study is needed.

The symmetry constraints in Table \ref{table:fullcodimension} can be divided into two types: (i) the first two rows of class II-A and (ii) other rows. For symmetry constraints of type (i), the full propagator is decomposed into products of $L$ (whose meaning will be explained below) segments of the propagator. These segments are related to one another by sewing matrix. Therefore, we parametrize the first segment of the propagator $\A_{1/L}$ as
\e{
\A_{1/L} = e^{i\theta}\matrixtwo{\alpha}{\beta}{-\beta^*}{\alpha^*}, |\alpha|^2+|\beta|^2=1.\label{eq:paramA1/N}
}
Then we calculate the full propagator $\A$ and figure out how many parameters is needed to tune $\A$ such that $\A$ is proportional to identity, which is codimension of degeneracy manifold. For symmetry constraints of type (ii), $\A$ fulfills an equation expressed with sewing matrix at the base point of $\A$ (denoted as $\bk_0$). Therefore, we parametrize the propagator as
\e{
\A = e^{i\theta}\matrixtwo{\alpha}{\beta}{-\beta^*}{\alpha^*}, |\alpha|^2+|\beta|^2=1.
}
and look for how many free parameters are left after the symmetry constraint is imposed, which is codimension of degeneracy manifold.

\paragraph*{class I-1} According to the general rules of sewing matrix, the sewing matrix $\breve{g}$ can be made diagonal by a gauge transformation
\e{
\breve{g} = \matrixtwo{e^{i\phi_1}}{0}{0}{e^{i\phi_2}}.
}
In this gauge, the symmetry constraints are expressed as 
\e{
\matrixtwo{\alpha}{\beta}{-\beta^*}{\alpha^*}=\matrixtwo{\alpha}{e^{i(\phi_1-\phi_2)}\beta}{-e^{-i(\phi_1-\phi_2)}\beta^*}{\alpha^*}.
}
Therefore, unless $\breve{g}$ is proportional to identity, $\beta=0$ and the only free variable is the phase of $\alpha$.

\paragraph*{class I-2}
By a gauge transformation, the sewing matrix $\breve{g}$ can be made off-diagonal
\e{
\breve{g} = \matrixtwo{0}{1}{\pm 1}{0}.
}
In this gauge, the symmetry constraints are expressed as (notice that $\det(\A)=\pm 1$ in this class \textbf{[this should not be inserted as a casual remark, please formalize]})
\e{
\det({\A})\matrixtwo{\alpha}{\beta}{-\beta^*}{\alpha^*}=\matrixtwo{\alpha}{\mp\beta}{\pm \beta^*}{\alpha^*}.
}
This immediately gives corresponding rows in table. \ref{table:fullcodimension}.

\paragraph*{class II-A-3 and class II-A-4} Calculation of codimensions for the two classes follow the same pattern as class I and is therefore omitted here.

\paragraph*{class II-A-1} In this class \textbf{[not just this class, also II-A-2]}, the full propagator can be constructed from $1/L$ of it, where $L$ is the smallest positive integer fulfilling $g^L\circ \bk_0=\bk_0$. Here, $\bk_0$ is the base point of $\A$. In this class, $L=N$. A good example in this class is $\mathfrak{c}_{Nz}$, $N$-fold rotation in z direction.\textbf{ [give the more general expression first before you perform your gauge transform]} Generally, by gauge transformation at $g^n\circ \bk_0$, $\breve{g}(g^n\circ \bk_0)$ can be transformed to identity for $0 \le n < N-1$ and the full propagator is
\e{
\A=\breve{g}(g^{N-1}\circ\bk_0)\prod_{i=0}^{N-1} \A_{1/N}
}
where 
\e{
\breve{g}(g^{N-1}\circ\bk_0)=\prod_{n=0}^{N-1} \breve{g}(g^n\circ\bk_0)
}
is a constant phase factor determined by the group multiplication rule. For example if $g$ is an $N$-fold rotation,  the phase factor is $+1$ (resp.\ $-1$) for an integer-spin (resp.\ half-integer-spin) representation. Therefore, the central object is
$\prod_{i=0}^{N-1} \A_{1/N}$. We take $N=2$ as an example. Using the parametrization in Eq. (\ref{eq:paramA1/N}),
\e{
\A_{1/N}^2=e^{2i\theta}\matrixtwo{\alpha^2-|\beta|^2}{\beta(\alpha+\alpha^*)}{-\beta^*(\alpha+\alpha^*)}{\alpha^{*2}-|\beta|^2}.
}
For $\A_{1/N}^2 \propto I$, the sufficient and necessary condition is $\text{Re}(\alpha)=0,\pm 1$, where tuning $\text{Re}(\alpha)=0$ requires only one parameter while tuning $\text{Re}(\alpha)=\pm 1$ requires three parameters.

For crystallographic spacetime symmetries, $N$ may also equal 3, 4 or 6. It is straightforward to prove in a similar manner that in these cases, degeneracies of $\A$ lie at $\text{Re}(\alpha)=\cos(n\pi/N)$, with $n\in\mathbb{Z}$. Except for $\text{Re}(\alpha)=\pm 1$, all degeneracy manifolds have codimension 1. In the Sec. \ref{sec:llquasideg}, we construct $\mathfrak{c}_N$ models by perturbing from $\mathfrak{c}_\infty$ Rashba model and by coupling two otherwise independent orbits by magnetic breakdown. In both constructions, $\A_{1/N}$ can be written in some gauge choice as
\e{
	\A_{1/N}=e^{i\theta}\matrixtwo{e^{i\lambda}}{0}{0}{e^{-i\lambda}}
}
before perturbation is turned on. $\lambda$ evolves monotonically with respect to $B$ and sweeps through $n\pi/N$ where degeneracies of $\A$ are expected. $e^{i\lambda}$ hits $\pm 1$ once in every $N$ degeneracies and therefore the other $n-1$ degenerates are stable, i.e., have codimension 1.

\paragraph*{class II-A-2} In class II-A-1, $L=N$ is guaranteed. However, in class II-A-2, this is generally not true. For symmetry operations still respecting $L=N$, the codimension calculation is similar to what is done in class II-A-1. The only example of $L\ne N$ is $T\mathfrak{c}_{6z,n\boldsymbol{c}/6}$ ($n\in{0,1,2,3,4,5}$), where $L=3$ and $N=6$. We write $g=T\mathfrak{c}_{6z,n\boldsymbol{c}/6}$ and $h=g^3$. By gauge transformation, it is possible to make $\breve{g}(\bk_0)=\breve{g}(g\circ\bk_0)=I$ and $\breve{h}(\bk_0)=\breve{g}(g^2\circ \bk_0)\equiv\breve{h}$. In this gauge, $\breve{h}(g\circ\bk_0)=h^*$. Therefore,
\e{
\A=\breve{h}\A_{1/L}\A_{1/L}^*\A_{1/L}
}
and $\A_{1/L}$ is constrained due to $h$ as 
\e{
\A_{1/L}=\breve{h}^* \A_{1/L} \breve{h}^{-1}.\label{eq:TC6A1/L}
}
Since $h$ is of order two, $\breve{h}$ can either be chosen as $\sigma_x$ or $i\sigma_y$. Then we immediately get $\det \A_{1/L} = \pm 1$. We first study the case $\breve{h}=\sigma_x$. If $\det \A_{1/L} = 1$, we parametrize $\det \A_{1/L}$ as in Eq. (\ref{eq:paramA1/N}) with $\theta=0$. From Eq. (\ref{eq:TC6A1/L}), we get $\beta=0$ and thus 
\e{
\A = \matrixtwo{0}{\alpha^*}{\alpha}{0}
}
and eigenphases of $\A$ are fixed to $0$ and $\pi$. If $\det{\A_{1/L}}=-1$, $\theta=\pi/2$ in Eq.(\ref{eq:paramA1/N}) and we obtain
\e{
\A = \matrixtwo{\beta^{*3}}{0}{0}{\beta^3}
}
and the codimension is 1. If $h=i\sigma_y$, from the fourth entry of class I-2, we deduce $\det \A_{1/L}=1$. Choosing the parametrization in Eq. (\ref{eq:paramA1/N}) with $\theta=0$, we compute the codimension to be 1.

In the main text, we focus on degenerate bands whose degeneracy is protected by continuous spin rotational symmetry (i.e., no SOC) or antiunitary symmetry $g$ with $g\circ \bk=\bk$ and $g^2=-1$. For the former case, we have argued in the main text that $\det{\A}=1$ if $\det{\A}$ is quantized; for the latter case, we have presented in table \ref{table:fullcodimension} $\det{\A}=1$ (Notice $g$ belongs to class I-2). Therefore, we safely ignore $\det{\A}=-1$ entries in table \ref{table:fullcodimension} and obtain table \ref{table:codimension} in the main text. \textbf{[more general argument?:  if we’re concerned with spinful orbits, and in symmetry classes where u+s=1, delta var is traceless, hence det A=+1.]
}
\section{Two-by-two sewing matrix of antiunitary symmetry operator can be made off-diagonal}

We parametrize $\breve{g}$ as
\begin{equation}
\breve{g}=e^{i\theta}\left(\begin{array}{cc}
\alpha & \beta\\
-\beta^{*} & \alpha^{*}
\end{array}\right),
\end{equation}
and $V$ by
\begin{equation}
V=e^{i\phi}\left(\begin{array}{cc}
a & b\\
-b^{*} & a^{*}
\end{array}\right),
\end{equation}
\begin{widetext}
then 
\begin{align}
\breve{g} & \to V^{\dagger}\breve{g}V^{*}\\
 & =e^{i(\theta-2\phi)}\left(\begin{array}{cc}
a^{*} & -b\\
b^{*} & a
\end{array}\right)\left(\begin{array}{cc}
\alpha & \beta\\
-\beta^{*} & \alpha^{*}
\end{array}\right)\left(\begin{array}{cc}
a^{*} & b^{*}\\
-b & a
\end{array}\right)\\
 & =e^{i(\theta-2\phi)}\left(\begin{array}{cc}
a^{*2}\alpha+a^{*}b\beta^{*}-a^{*}b\beta+b^{2}\alpha^{*} & a^{*}b^{*}\alpha+bb^{*}\beta^{*}+aa^{*}\beta-ab\alpha^{*}\\
\cdots & \cdots
\end{array}\right).
\end{align}
\end{widetext}
Parametrizing $a=a_{1}+ia_{2}$, $b=b_{1}+ib_{2}$, $\alpha=\alpha_{1}+i\alpha_{2}$
and $\beta=\beta_{1}+i\beta_{2}$, we first remove the imaginary part
of $a^{*}b^{*}\alpha+bb^{*}\beta^{*}+aa^{*}\beta-ab\alpha^{*}$. If
we take both $a$ and $b$ to be real, we want
\begin{align*}
0 & =2ab\alpha_{2}-b^{2}\beta_{2}+a^{2}\beta_{2}\\
2ab\alpha_{2} & =(b^{2}-a^{2})\beta_{2}\\
2b\sqrt{1-b^{2}}\alpha_{2} & =(2b^{2}-1)\beta_{2}.
\end{align*}
This is always possible since $2b\sqrt{1-b^{2}}/(2b^{2}-1)$ can take
any real value for $b\in[-1,1]$. Therefore, we can safely assume
$\beta$ is real since a preliminary transformation can remove its
imaginary part. Then we want
\begin{align*}
0 & =a^{*2}\alpha+a^{*}b\beta^{*}-a^{*}b\beta+b^{2}\alpha^{*}\\
(a_{1}-ia_{2})^{2}(\alpha_{1}+i\alpha_{2}) & =-(b_{1}+ib_{2})^{2}(\alpha_{1}-i\alpha_{2})\\
(a_{1}^{2}-a_{2}^{2}-2ia_{1}a_{2})(\alpha_{1}+i\alpha_{2}) & =-(b_{1}^{2}-b_{2}^{2}+2ib_{1}b_{2})(\alpha_{1}-i\alpha_{2}).
\end{align*}
Real and imaginary part of the above equation are
\[
(a_{1}^{2}-a_{2}^{2})\alpha_{1}+2a_{1}a_{2}\alpha_{2}=-(b_{1}^{2}-b_{2}^{2})\alpha_{1}-2b_{1}b_{2}\alpha_{2}
\]
and 
\[
(a_{1}^{2}-a_{2}^{2})\alpha_{2}-2a_{1}a_{2}\alpha_{1}=(b_{1}^{2}-b_{2}^{2})\alpha_{2}-2b_{1}b_{2}\alpha_{1}.
\]
Therefore
\[
\frac{\alpha_{2}}{\alpha_{1}}=-\frac{(a_{1}^{2}-a_{2}^{2})+(b_{1}^{2}-b_{2}^{2})}{2a_{1}a_{2}+2b_{1}b_{2}}=\frac{2a_{1}a_{2}-2b_{1}b_{2}}{(a_{1}^{2}-a_{2}^{2})-(b_{1}^{2}-b_{2}^{2})},
\]
equivalent to
\[
|a|=|b|=\frac{\sqrt{2}}{2}
\]
and 
\[
\frac{\alpha_{2}}{\alpha_{1}}=-\frac{(a_{1}^{2}-a_{2}^{2})+(b_{1}^{2}-b_{2}^{2})}{2a_{1}a_{2}+2b_{1}b_{2}}.
\]
This can always be satisfied. For example, we can always take $b=1/2+i/2$
and the above equation becomes
\[
\frac{\alpha_{2}}{\alpha_{1}}=\frac{(2a_{2}^{2}-1/2)}{2a_{2}\sqrt{1/2-a_{2}^{2}}+1/2},
\]
which is always possible since $\frac{(2a_{2}^{2}-1/2)}{2a_{2}\sqrt{1/2-a_{2}^{2}}+1/2}$
can take any value.

\section{Method of numerical diagonalization}\la{sec:numerical}

The techniques for solving $\mathcal{H}_R(\bK)$ in \textbf{[eq]} is standard, but we describe it here since it is also used in numerical diagonalization of other Hamiltonians below with no closed analytic solutions. This technique relies on the fact that the commutation relation $[K_x,K_y]=il^{-2}$ bears similarity to that of position operator and momentum operator of simple harmonic oscillators. Therefore, $K_x$ and $K_y$ can be organized into creation and annihilation operators
\begin{align}
\begin{split}
K_x=&l^{-1}(a+a^\dagger)/\sqrt{2},\\
K_y=&-il^{-1}(a-a^\dagger)/\sqrt{2}.
\end{split}
\end{align}
Under this transformation, $\mathcal{H}_R(\bK)$ is transformed to
\begin{align}
\begin{split}
\mathcal{H}_{R}(\boldsymbol{K})=&\frac{1}{ml^2}(a^{\dagger}a+\frac{1}{2})
\\&+\sqrt{2}\alpha l^{-1}\left(\begin{array}{cc}
0 & -ia^{\dagger}\\
ia & 0
\end{array}\right)
-\frac{g_s'\sigma^z}{4ml^2},
\end{split}\label{eq:Rashba-ho}
\end{align}
where Zeeman coupling is already added. Eq. (\ref{eq:Rashba-ho}) have solutions in the form of $(c_1|n+1\rangle,c_2|n\rangle)$ where $c_1$ and $c_2$ are some constants and $|n\rangle$ labels the eigenstate of $a^\dagger a$.

\textbf{[combine this with above]
}Electron spectrum of this Hamiltonian in magnetic field is not exactly solvable to our knowledge. Yet multiband Peierls substitution is still applicable and the system can still be mapped into two coupled harmonic oscillators similar to Eq. (\ref{eq:Rashba-ho}). This Hamiltonian is infinite dimensional and can be diagonalized by cutting off at a high occupation number.

\section{Dimension of degeneracy manifolds}\la{app:nullity}

Any $SU(2)$ matrix can be expressed as ${\cal \bar{A}}= e^{i\br\cdot \bsigma}$ with $\br=(x,y,z)$ a real three vector and $\bsigma=(\sigma_x,\sigma_y,\sigma_z)$ the vector of Pauli matrices. The condition for degeneracy can be expressed as
\e{ 0=D^{\pm}=\det[{\cal \bar{A}}\pm I] = 2(1\pm \cos r)\in \R, \as r:=|\br|. \la{semipos}}
Parametrizing  ${\cal \bar{A}}(\bR)$ with $\bR$ a real $d$-vector, we define the partial derivatives
\e{  D^{\pm}_j:= \p{D^{\pm}}{ R_j}\in \R, \as D^{\pm}_{ij}:= \p{^2D^{\pm}}{ R_i\partial R_j} \in \R.  }
$D^{\pm}_{ij}$, also known as the Hessian matrix, is real and symmetric.

Let us prove that $D^{\pm}_j$ vanishes (for all $j$) when evaluated on the degeneracy manifold.  We express $D^{\pm}$ as the characteristic polynomial det$[{\cal \bar{A}}-\zeta I]$ evaluated at $\zeta=\mp 1$:
\e{ D^{\pm}(\bR)=c_0(\bR)(\mp 1-\zeta_1(\bR))(\mp 1-\zeta_2(\bR)) }
where $\zeta_j$ are the unimodular eigenvalues of ${\cal \bar{A}}$. In this form it is clear that
the first derivatives of $D^{\pm}$ vanish when $\zeta_1=\zeta_2=\pm 1$.

To alternatively derive the vanishing of $D^{\pm}_j$ where $D^{\pm}{=}0$, we may apply that  $D^{\pm}\in [0,4]$ [derived from \q{semipos}]. As an implication, consider a small displacement $\delta \bR$ away from  a point $\bR_0$  on the degeneracy manifold $D^{+}=0$:
\e{ D^+(\bR_0+\delta \bR)\eq  \f1{2} \sum_{i,j=1}^d\delta R_i D^{+}_{ij}(\bR_0) \delta R_j + O(\delta R_i^3) \lin 
\eq \f1{2}\sum_{j=1}^d c^2_j h_j + O(\delta R_i^3).\la{taylor}} 
Since $D^{\pm}$ is a semipositive definite function, it must be that $\sum_{ij}\delta R_i D^{+}_{ij}(\bR_0) \delta R_j\geq 0$ for any $\delta \bR$, i.e., the Hessian must be semipositive definite on the degeneracy manifold. In the last equality of \q{taylor}, we decomposed $\delta \bR=\sum_jc_j\bv_j$ into the real, orthonormal eigenvectors $\bv_j$ of $D^{+}_{ij}(\bR_0)$ with corresponding real eigenvalues $h_j$; note $h_j\geq 0$. We see that if $\bR_0+\delta \bR$ lies on the degeneracy manifold (i.e., $D^+(\bR_0+\delta \bR)=0$),  $\delta \bR$ must lie in the null space of $D^{+}_{ij}(\bR_0)$. This implies that the dimension of the degeneracy manifold is bounded by the dimension of this null space (i.e., the nullity).

To illustrate these degeneracy manifolds for $\bR=\br=(r_1,r_2,r_3)$ a real three-vector, and $\hat{r}_i:=r_i/r$ 
\e{ D^{\pm}_j = \mp 2\sin (r) \hat{r}_i, \as D^{\pm}_{ij}= \f{\sin r}{r}\big(\delta_{ij}-\hat{r}_i\hat{r}_j\big)+\hat{r}_i\hat{r}_j\cos r.}
The degeneracy manifolds are given by $r=n\pi$ with $n\in \Z$. In particular, $D^{\pm}_{ij}(\bze)$ is the identity matrix, which is consistent with $n=0$ manifold being a point; $D^{\pm}_{ij}(\pi,0,0)$ is a diagonal matrix with only a single nonzero entry ($-1$), which is consistent with the $n=1$ manifold being a two-sphere.
\section{Reducing nonlocal magnetic breakdown to local magnetic breakdown}
We take Rashba-Zeeman model as an example, revealing that quantization rule for nonlocal magnetic breakdown, in the limit of $\Delta\gg\epsilon_c$, becomes quantization rule for local magnetic breakdown.

In the limit of $\Delta\gg\epsilon_c$, the two orbits become nondegenerate everywhere except for the type II Dirac point. It is natural to decompose the propagator into two parts
\begin{equation}
\A = \A_2\A_1,
\end{equation}
where $\A_1:=\A[t_-\leftarrow t_+]$ encodes information of cyclotron motion from leaving the vicinity of the Dirac point (denoted as $t_+$) to entering the vicinity of the Dirac point again (denoted as $t_-$) and $\A_2:=\A[t_+\leftarrow t_-]$ encodes information of cyclotron passing the vicinity of the Dirac point. Notice that we have written down $\A$ (and $\A_1$, $\A_2$) in constant basis since $\calh$ diverges near the Dirac point if expressed in the energy band basis. $t_+-t_-\ll T_c$ due to the smallness of the Dirac point. A gauge transformation expresses $\A_1$ in the energy basis
\begin{equation}
V_+^\dagger\A V_+ = V_+^\dagger\A_2V_-V_-^\dagger\A_1V_+,
\end{equation}
where $V_\pm=V(\bk(t_\pm))$. We emphasize that while $V_-^\dagger\A_1V_+$ can be understand as $\A_1$ in energy basis, $V_+^\dagger\A_2V_-$ cannot due to the divergence of single band Berry connection at Dirac point. Since $\Delta\gg\epsilon_c$, diagonal terms of $\A_1$ is much larger than off-diagonal terms such that to the lowest order off diagonal terms can be neglected. Therefore, 
\begin{equation}
\A_1\approx\matrixtwo{\delta \Omega_1}{0}{0}{\delta \Omega_2},
\end{equation}
where $\delta\Omega_{1(2)}$ is the semiclassical phase accumulated from $t_+$ to $t_-$ besides $l^2 S$ by the two bands.

The other part $\mathcal{S}:=V_+^\dagger\A_2V_-$ is a standard Landau-Zener problem, as will be shown below. In the constant basis, 
\begin{equation}
\calh(t)=\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+Z_\parallel\sigma_{y}-Z_\perp\sigma_{z},
\end{equation}
where $k_x=-k_F \cos(\omega_c t)$ and $k_y=k_F \sin(\omega_c t)$. Since $t_+-t_-\ll T_c$, we can keep only the linear terms in $t$,
\begin{equation}
\calh(t)\approx\alpha k_F \omega_c t\sigma_x+(Z_\parallel-\alpha k_F)\sigma_y-Z_\perp\sigma_z.
\end{equation}
It is now obvious that $\mathcal{S}$ is a Landau-Zener problem: $\alpha k_F \omega_c t\sigma_x$ is linear in time; $(Z_\parallel-\alpha k_F)\sigma_y-Z_\perp\sigma_z$ is time independent; columns of $V_-$ and $V_+$ are approximately eigenvectors of $\sigma_x$. Therefore, $\mathcal{S}$ takes the form of a magnetic junction scattering matrix with
\e{\mu=\frac{ml^2(Z_\perp^2+(Z_\parallel-\alpha k_F)^2)}{2\alpha k_F}.}

Generally, $\mu$ should diverge at type I-type II Dirac point transition point, which is not the case in the above equation. Therefore, $\mu$ in the above equation is only an approximate result.

The quantization rule is now
\e{
\det\left[e^{il^2S}\mathcal{S}\matrixtwo{\delta \Omega_1}{0}{0}{\delta \Omega_2}-I\right]=0,
}
giving rise to cos-cos quantization condition.

We now compare $\mu$ derived here and $\mu$ defined in [AALG]. In [AALG], $Z_\perp$ was ignored and
\e{
\mu = \f{(k_F^2/2m-Z_\parallel^2/2m\alpha^2)^2l^2}{2\alpha^2[\,(Z_\parallel/m\alpha^2)^2-1\,]^{3/2}}.
}
If $Z/m\alpha^2$ is large, i.e., deep in type II Dirac point regime, we can ignore the 1 in the denominator,
\e{
\mu &\approx \f{ml^2(\alpha^2 k_F^2-Z_\parallel^2)^2}{8Z_\parallel^3}\\
 &= \f{ml^2(\alpha k_F-Z_\parallel)^2(\alpha k_F+Z_\parallel)^2}{8Z_\parallel^3}.
}
For tunneling effect to be significant, $Z\approx \alpha k_F$, therefore,
\e{
\mu \approx \f{ml^2(\alpha k_F-Z_\parallel)^2}{2\alpha k_F},
}
consistent with $\mu$ derived with $\A$.

\section{Fixing discontinuity in magnetic breakdown with Zeeman coupling}

For the II-Dirac point in the main text, if Zeeman coupling is taken into account, the Dirac point is gapped:
\e{
H &= (\sigma_y-a)k_x-k_y\sigma_x-\lambda\sigma_z\\
 &:= H_0+H_Z.
}
where $\lambda$ is considered as a small parameter and $a>1$. Eigenvalue of $H$ is 
\e{
\epsilon_\pm&=-a k_x \pm\sqrt{k_x^2+k_y^2+\lambda^2}\\
&:=-a k_x \pm\Delta
} and eigenvectors are
\begin{equation}
\psi_\pm=\f{1}{\sqrt{2\Delta(\Delta\pm\lambda)}}\left(
\begin{array}{c}
-\lambda\mp\Delta\\
-k_y+ik_x
\end{array}
\right).
\end{equation}

The Berry connection for lower band is 
\e{
A_x&=\f{k_y}{2\Delta(\Delta+\lambda)},\\
A_y&=-\f{k_x}{2\Delta(\Delta+\lambda)}.
}

Constant energy contours are now described by a hyperbola

\e{
(k_x+\f{a\epsilon}{a^2-1})^2-\f{k_y^2}{a^2-1}=\f{1}{a^2-1}[\lambda^2+(\frac{a^2}{(a^2-1)^2}-1)\epsilon]
}

For a general hyperbola
\e{
\f{(kx+b)^2}{c^2}-\f{k_y^2}{d^2}=1,
}
the lower branch is 
\e{
k_x = -a\sqrt{1+\frac{k_y^2}{b^2}}-c
}
and Berry phase is
\e{
\phi&=\int A_xdk_x+A_ydk_y\\
&=\int dk_y (\f{k_y}{2\Delta(\Delta+\lambda)}\f{-ak_y}{b\sqrt{b^2+k_y^2}}-\f{k_x}{2\Delta(\Delta+\lambda)}).
}

\end{document}

### 2018-09-09 paper.tex
Updates from ShareLaTeX
progress

@@
 \textbf{A different realization of two-fold symmetric breakdown: angular magnetoresistance oscillations.}
+\red{[I begin to question this again.
+In my previous understanding, the in-plane magnetic field changes the band structure while the out-of-plane magnetic field produces LLs.
+Now I believe the in-plane magnetic field cannot be simply understood simply as a change in band structures.
+Therefore, I am not quite sure whether it is related to magnetic breakdown.]}
 
@@
 Since magnetic field $B$ is applied externally, it does not change under the action of any symmetry operation.
-Hence any symmetry relevant in current context must keep $k_x-k_y$ plane untouched.
+Hence any symmetry relevant in current context must keep $k_x$-$k_y$ plane untouched.
 By definition, $\A$ is a path-ordered exponential along the cyclotron orbit of the two-by-two Hamiltonian $\H$ and $\H$ is composed of a scalar $\delta\epsilon$ and a pseudovector $B\mathcal{M}$.

### 2018-09-11 paper.tex
progress

@@
 \ref{fig:orbits}(a)] is much smaller than their average area:\footnote{The expressions for $\delta S$ and $S$ in \q{deltaSvsS} are asymptotically valid for $E{\gg}m\alpha^2$.}
-\e{\delta S = 2\pi k_E \f{2\alpha m}{\hbar} \ll  S =\pi k_E^2; \;\; k_{E}:=\f{\sqrt{2m E}}{\hbar} .\la{deltaSvsS}}
+\e{\delta S = 2\pi k_E \f{2\alpha m}{\hbar^2} \ll S =\pi k_E^2; \;\; k_{E}:=\f{\sqrt{2m E}}{\hbar} .\la{deltaSvsS}}
 $S$ is equivalently the area of the circular, constant-energy contour in the absence of spin-orbit coupling ($\alpha{=}0$).
 
-Throughout this work we will treat both $\delta S/S$ and $1/l^2S$  as small parameters with finite ratio $l^2\delta S$ \textbf{[define magnetic length]}.
-Our perspective diverges from and generalizes previous semiclassical theories [Kohn, Blount, Roth, Wannier, Fredkin, Niu, Mikitik, topoferm, 100page] having only a single small parameter ($B$).
+Semiclassical quantization rules work in semiclassical regime where magnetic length $l=\sqrt{\hbar/eB}$ is much larger than characteristic length of cyclotron motion in $\bk$-space, i.e., $1/l^2 S\ll 1$.
+This condition is assumed by previous semiclassical theories.
+[Kohn, Blount, Roth, Wannier, Fredkin, Niu, Mikitik, topoferm, 100page] As a generalization, we will treat $\delta S/S$ as an extra small parameters throughout this work with finite ratio $l^2\delta S$.
 
 $(l^2\delta S)^{-1}$ is a measure of the field-induced hybridization of the quasidegenerate orbits, and shall be called the hybridization parameter. 
-In the regime that $l^2\delta S$ is much greater than the Zeeman interaction, we expect that the Onsager-Lifshitz quantization rules apply independently to the two concentric (but decoupled) orbits.
+In the regime that $l^2\delta S$ is much greater than the Zeeman interaction \red{[Zeeman interaction?
+Why not just 1.]}, we expect that the Onsager-Lifshitz quantization rules apply independently to the two concentric (but decoupled) orbits.
 In the opposite regime, we should recover the known quantization rule for degenerate orbits.
@@
 This decomposition is such that energy bands of $\hat{H}_0$ are $D$-fold degenerate at every crystal wavevector $\bk$, while $\delta \hat{H}$ is a weak perturbation that lifts this degeneracy at generic $\bk$.
-For conceptual simplicity, we focus on $D{=}2$ spin degeneracy, and postpone the general formulation for $D{\geq}2$ to Appendix \ref{app:quantizationruleproof}.
-$\hat{H}_0$ is commonly exemplified by  the Schr\"odinger Hamiltonian, and $\delta H$ by a non-centrosymmetric spin-orbit interaction; alternatively, $\hat{H}_0$ may be a centrosymmetric Pauli Hamiltonian (complete with spin-orbit coupling), while $\delta H$ describes a lattice deformation that breaks the spatial-inversion symmetry.
+For conceptual simplicity, we focus on $D{=}2$ spin degeneracy, and postpone the general formulation for $D{\geq}2$ to App.
+\ref{app:quantizationruleproof}.
+$\hat{H}_0$ is commonly exemplified by  the Schr\"odinger Hamiltonian, and $\delta H$ by a non-centrosymmetric spin-orbit interaction; alternatively, $\hat{H}_0$ may be a centrosymmetric Pauli Hamiltonian (with spin-orbit coupling), while $\delta H$ describes a lattice deformation that breaks the spatial-inversion symmetry.
 
@@
 Let us apply a magnetic field, and first consider the spin-degenerate Landau levels obtained by neglecting both $\delta H$ and the Zeeman splitting.
-In the  semiclassical description,  we are interested in  field-induced dynamics within a low-energy degenerate band of $\hat{H}_0$ with  dispersion $\var(\bk)$, e.g., $\var(\bk){=}\hbar^2 \bk^2/2m{+}O(k^4)$ in the Rashba model.
-Landau quantization is well-known to derive from the Peierls substitution $\var(\bk){\rightarrow}\var(\bK)$,[Peierls] with   the kinematic quasimomentum operator   $\boldsymbol{K}{:}{=}\boldsymbol{k}{+}(e/\hbar) \boldsymbol{A}(i\nabla_{\boldsymbol{k}})$ and $\boldsymbol{A}(\br)$ being the electromagnetic vector potential.
-Assuming that the field is aligned in the ${-}z$ direction, $[K_x,K_y]{=}i\lmt$ with the magnetic length $l{:}{=}\sqrt{\hbar/{eB}}$.
+In the  semiclassical description,  we are interested in  field-induced dynamics within a low-energy degenerate band of $\hat{H}_0$ with  dispersion $\var(\bk)$, e.g., $\var(\bk){=}\hbar^2 k^2/2m{+}\order(k^4)$ \red{[What is contained in this $\order(k^4)$?]}in the Rashba model.
+Landau quantization is well-known to derive from the Peierls substitution $\var(\bk){\rightarrow}\var(\bK)$, [Peierls] with the kinematic quasimomentum operator   $\boldsymbol{K}{:}{=}\boldsymbol{k}{+}(e/\hbar) \boldsymbol{A}(i\nabla_{\boldsymbol{k}})$ and $\boldsymbol{A}(\br)$ being the electromagnetic vector potential.
+Assuming that the field is aligned in the ${-}z$ direction, $[K_x,K_y]{=}i\lmt$.
 The semiclassical solution corresponds to  cyclotron revolutions of an electron around a constant-energy contour of $\var(\bk)$ [see Fig.
@@
 
-To the first order, $\delta H$ and the Zeeman interaction  induce a subleading phase offset ($\lambda_a$) which generically differs for the two orthogonal spinor states (labelled $a{=}1,2$):
+To the first order, $\delta \hat{H}$ and the Zeeman interaction induce a subleading phase offset ($\lambda_a$) which generically differs for the two orthogonal spinor states (labelled $a{=}1,2$):
 \begin{equation}
@@
 In the basis of energy-split bands (which we label by  ${+}$ and $-$ for the outer and inner orbit respectively),\footnote{We remark that the quantization rule is invariant under basis transformations within the degenerate band subspace (See App.
-\ref{app:quantizationruleproof}); this may be exploited for efficient  numerical computations.} $\delta \var$ is a diagonal matrix whose diagonal entries ($\delta \var_+,\delta \var_-$) are related to  the hybridization parameter:\footnote{The neglected term on the right-hand side of  \q{spinsplitwkb} is smaller (than the kept term) by a factor $\delta v_{\pm}/v$, which is the relative change in band speed $v=|\boldsymbol{v}|=\hbar^{-1}|\partial \var/\partial \bk|$ induced by the spin-orbit coupling.
+\ref{app:quantizationruleproof}); this may be exploited for efficient numerical computations.} $\delta \var$ is a diagonal matrix whose diagonal entries ($\delta \var_+,\delta \var_-$, corresponding to outer and inner orbit respectively; $\delta \var_+<\delta \var_-$) are related to the hybridization parameter:\footnote{The neglected term on the right-hand side of  \q{spinsplitwkb} is smaller (than the kept term) by a factor $\delta v_{\pm}/v$, which is the relative change in band speed $v=|\boldsymbol{v}|=\hbar^{-1}|\partial \var/\partial \bk|$ induced by the spin-orbit coupling.
 This factor is assumed to be small.
 For example in the Rashba model, $\delta v_{\pm}/v=m\alpha/\hbar k_E{\sim}\delta S/S{\ll}1$.}
-\e{\int_0^{T_c} (\delta \var_+{-}\delta \var_-) \frac{dt}{\hbar} \approx l^2\delta S. \la{spinsplitwkb}}
+\e{-\int_0^{T_c} (\delta \var_+{-}\delta \var_-) \frac{dt}{\hbar} \approx l^2\delta S. \la{spinsplitwkb}}
 %In the  Rashba model,   $\delta \var_{\pm}(E){=}{\pm} (\alpha/\hbar)\sqrt{2mE}$ is independent of $\bk$ due to a continuous rotational symmetry of $H_R$. \\
@@
 
-The remaining terms in \q{eq:H1} describe a generalized Zeeman interaction $B\calm$ which is the first-order-in-$B$ correction to the Peierls-Onsager Hamiltonian $\var(\bK)$.[kohn,blount,roth] Included in this interaction is the Zeeman coupling to the spin ($g_s\mu_Bs_z/\hbar$) and orbital ($M_z$) magnetic moment of the quasidegenerate band; the latter  is expressible in terms of matrix elements of the velocity operator \textbf{[please insert definition of v from below eq 3 in topoferm]}:
-\e{
-M_z=\f{ie\hbar}{2}\sum_l'\f{v_{x,ml}v_{y,ln}-v_{y,ml}v_{x,ln}}{\epsilon_m-\epsilon_l}. \la{eq:orbitalmoment}
+The remaining terms in \q{eq:H1} describe a generalized Zeeman interaction $B\calm$ which is the first-order-in-$B$ correction to the Peierls-Onsager Hamiltonian $\var(\bK)$.[kohn,blount,roth] Included in this interaction is the Zeeman coupling to the spin ($g_s\mu_Bs_z/\hbar$) and orbital ($M_z$) magnetic moment of the quasidegenerate band; the latter is expressible in terms of matrix elements of the velocity operator $\boldsymbol{\Pi}$ between Bloch wave functions $\psi_{n\bk}$ $\boldsymbol{\Pi}_{mn}=i\langle\psi_m|[\hat{H}, \hat{\boldsymbol{r}}]|\psi_n\rangle/\hbar$:
+\e{
+M_z=\f{ie\hbar}{2}\sum_l'\f{\Pi_{x,ml}\Pi_{y,ln}-\Pi_{y,ml}\Pi_{x,ln}}{\epsilon_m-\epsilon_l}. \la{eq:orbitalmoment}
 }
@@
 
-\qq{eq:rule}{berryconn} allow us to determine $\lambda_{1,2}$ to the lowest order  in $1/l^2S$ and $\delta S/S$, and for arbitrary values of $l^2\delta S$ and $||B\calm||/\delta \var_{\pm}$.
+\qq{eq:rule}{berryconn} allow us to determine $\lambda_{1,2}$ to the lowest order  in $1/l^2S$ and $\delta S/S$, and for arbitrary values of $l^2\delta S$ and $|B\calm|/\delta \var_{\pm}$.
 
@@
 By  neglecting  $B\calm_{+-}$ in favor of intraband elements,  $\cala$ reduces to a diagonal matrix with  diagonal entries ($e^{i\lambda_{\pm}}$) given by:
-\e{\lambda_{\sma{\pm}} = \int_0^{T_c}\calh_{\sma{\pm\pm}}dt=\pm \tf1{2}l^2\delta S +B\int_0^{T_c}\calm_{\sma{\pm\pm}}dt.  \la{phaseindependentorbit}} 
+\e{\lambda_{\sma{\pm}} = -\int_0^{T_c}\calh_{\sma{\pm\pm}}\f{dt}{\hbar}=\pm \f{1}{2}l^2\delta S - B\int_0^{T_c}\calm_{\sma{\pm\pm}}\f{dt}{\hbar}.  \la{phaseindependentorbit}} 
 In the second equality, we have applied \q{spinsplitwkb} and assumed that 
@@
 In the  energy basis of the Rashba Hamiltonian $H_R$ [cf.\ \q{eq:Rashba-Hamiltonian}],
-\e{\calh(\bk)=\alpha k\tau_z{+}\f{g_s}{2}\mu_{\sma{B}}B\tau_x \red{-} \f{eB\red{\hbar}}{2m} (\tau_x-I) \epsilon_{\alpha\beta} k_{\red{\alpha}}\nabla_{\red{\beta}}\theta,\la{rashbaeffham}}
+\e{\calh(\bk)=-\alpha k\tau_z{+}\f{g_s}{2}\mu_{\sma{B}}B\tau_x \red{-} \f{eB\hbar}{2m} (\tau_x-I) \epsilon_{\alpha\beta} k_{\red{\alpha}}\nabla_{\red{\beta}}\theta,\la{rashbaeffham}}
 where $\tau_i$ are a new set of Pauli matrices with $\tau_z{=}{+} 1$ and ${-}1$ corresponding to the outer and inner orbits, respectively \red{[I switched the sign in the equation above to emphasize the sign difference.]}.
@@
 It is well-known that the Zeeman term tends to polarize spin in the direction ($\vec{z}$) of $\bB$; remarkably, the non-abelian Berry term   also has a polarizing effect, but with opposite sign.
-These two effects completely cancel for free electrons ($m{=}m_0$), but not generically in band systems.
+These two effects completely cancel for free electrons ($m{=}m_0$, with $m_0$ being free electron mass.), but not generically in band systems.
 The orbital moment term $B M_z$, which generally couples the two-band subspace (of interest) to all other bands, is absent in any simplified two-band model.
@@
 
-Due to the continuous rotational symmetry of $H_R$, $\nabk \theta$ has magnitude $1/k$ and lies tangential to $\frako_0$; consequently, $\calh$ is constant along $\frako_0$, and the propagator simplifies to $\cala{=}e^{{-}i\calh T_c}$ without time-ordering, and the phase corrections to the quantization rule are simply the eigenvalues of $\calh$ multiplied by $T_c$:
+Due to the continuous rotational symmetry of $H_R$, $\nabk \theta$ has magnitude $1/k$ and lies tangential to $\frako_0$; consequently, $\calh$ is constant along $\frako_0$, and the propagator simplifies to $\cala{=}e^{{-}i\calh T_c/\hbar}$ without time-ordering, and the phase corrections to the quantization rule are simply the eigenvalues of $\calh$ multiplied by $T_c$:
 \begin{equation}
@@
 
-In the weak-hybridization regime: $l^2\delta S {>}\pi(g_{\sma{\text{eff}}}{-}2)$, we may expand \q{eq:Rashba-lambda} as a Laurent series in $B$:
-\e{\lambda_{\pm}= \pm \f{l^2\delta S}{2} +\pi \pm \f{\pi^2}{4}\f{(g_{\sma{\text{eff}}}-2)^2}{l^2\delta S} + O(B^2). \la{lambdasmallB}}
+In the weak-hybridization regime: $l^2\delta S  \gg \pi|g_{\text{eff}}{-}2|$, we may expand \q{eq:Rashba-lambda} as a Laurent series in $B$:
+\e{\lambda_{\pm}= \pm \f{l^2\delta S}{2} +\pi \pm \f{\pi^2}{4}\f{(g_{\text{eff}}-2)^2}{l^2\delta S} + O(B^2). \la{lambdasmallB}}
 \q{eq:rule}, combined with the first two terms on the right-hand-side of \q{lambdasmallB}, may alternatively be derived from 
@@
 
-In the strong-hybridization regime: $l^2\delta S {\ll}\pi(g_{\sma{\text{eff}}}{-}2)$, $\lambda_{\pm}{\approx}{\pm}\pi g_{\sma{\text{eff}}} /2$ mod $2\pi$, which corresponds to the Zeeman splitting of Landau levels by $g_{s}\mu_BB$, in the \textit{absence} of the spin-orbit interaction.
+In the strong-hybridization regime: $l^2\delta S {\ll}\pi(g_{\text{eff}}{-}2)$, $\lambda_{\pm}{\approx}{\pm}\pi g_{\text{eff}} /2$ mod $2\pi$, which corresponds to the Zeeman splitting of Landau levels by $g_{s}\mu_BB$, in the \textit{absence} of the spin-orbit interaction.
 
@@
 \ref{sec:numerical}) and those obtained from the quantization rule.
-The difference in energies  does not exceed $2\%$ of $\var_c$ [cf.\ \fig{fig:RD}(d)] for various choices of the spin-orbit parameters $(\alpha,\beta)$.
+The difference in energies  does not exceed $2\%$ of $\var_c$ [cf.\ \fig{fig:RD}(c)] for various choices of the spin-orbit parameters $(\alpha,\beta)$.
 Larger differences are positively correlated with 
 $l^2\delta S^2/S$ (with $\delta S$ depending on both $\alpha$ and $\beta$), as shown in Fig.
-\ref{fig:RD}(c); see also \q{eq:Rashba-exact}, which analytically demonstrates how terms involving $l^2\delta S^2/S$ modifies the quantization rule in the case $\beta=0$.
+\ref{fig:RD}(d); see also \q{eq:Rashba-exact}, which analytically demonstrates how terms involving $l^2\delta S^2/S$ modifies the quantization rule in the case $\beta=0$.
 
@@
 (\ref{eq:rule}) (black lines) and numerical diagonalization of the Peierls-Onsager Hamiltonian  $H_{RD}(\bK)$ (red dots).
-Parameters: $\alpha=0.05$(eV$\cdot$\AA), $m=0.01$($\hbar^2$/eV$\cdot$\AA$^2$), $\beta=0.02~(0.04)$(eV$\cdot$\AA) for left (right) panels.
-$B$ is measured from 2.9 and 1.6T respectively and is in unit $10^{-2}$T.
-(c-d) For various spin-orbit parameters $(\alpha,\beta)$ of the Rashba-Dresselhaus model and various field strength (satisfying $l^2S(E)\gg 1$), we plot in (c) the hybridization parameter $l^2\delta S(E)$ for fixed energy $(E=0.4$eV${\gg}m\alpha^2)$.
-For a single Landau level that lies closest to the chosen $E$, we plot in (d) $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$, where $\epsilon_\text{rule}$ is determined by Eq.
+Parameters for (b): $\alpha=0.05$(eV$\cdot$\AA), $m=0.01$($\hbar^2$/eV$\cdot$\AA$^2$), $\beta=0.02~(0.04)$(eV$\cdot$\AA) for left (right) panels.
+$B$ is measured from 2.9 and 1.0T respectively and is in unit $10^{-2}$T.
+(c) For various spin-orbit parameters $(\alpha,\beta)$ of the Rashba-Dresselhaus model and various field strength (satisfying $l^2S(E)\gg 1$), we plot  $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that lies closest to energy $E=0.4eV$, where $\epsilon_\text{rule}$ is determined by Eq.
 (\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian  $H_{RD}(\bK)$.
-Parameters: $m=0.01$($\hbar^2$/eV$\cdot$\AA$^2$).
+We also plot in (d) $l^2\delta S^2/S$, which has a strong positive relation with error in (c).
+Parameters for (c-d): $m=0.01$($\hbar^2$/eV$\cdot$\AA$^2$).
 Units: $\alpha$($10^{-2}$eV$\cdot$\AA), $\beta$($10^{-2}$eV$\cdot$\AA), $Z$($10^{-3}$eV), $l^2 S$($10^2$).\label{fig:RD}}
@@
 (b) Black dashed lines illustrate a zeroth-order approximation of the Landau levels (assuming Klein tunneling); the leading-order correction is indicated by red lines.
-The Dirac point lies at $10$meV, at which energy first order correction vanishes in Eq.
-(\ref{RZfirstorderE}).
-Parameters: $m$: 0.02$\hbar^2$/eV$\cdot$\AA$^2$, $\alpha$: 0.05eV$\cdot$\AA, $Z_\parallel$: 0.001eV.
-(c) For various configuration ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in (c) the hybridization parameter $l^2S(E)$ where $E$ is chosen as the energy of the Landau level nearest to the type-II Dirac point, i.e., closest to $\epsilon_0$ in Eq.
-(\ref{whereisdiracpoint}).
-We only plotted in region where $0.4<\epsilon_0<1.0$(eV).\red{[Note to Aris: the reason of choosing $\epsilon_0>0.4$ is I want to make sure $l^2S\gg 1$; the reason of choosing $\epsilon_0<1.0$ is Dirac point lying at high energy requires too much harmonics in numerical diagonalization.
-This requirement is equivalent to $\sqrt{0.8m}\alpha/\hbar<Z<\sqrt{2m}\alpha/\hbar$, corresponding to the boundaries of the plot in (c) and (d).]} (d) $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ corresponding to the parameter configurations in (c), where $\epsilon_\text{rule}$ is determined by Eq.
+The Dirac point lies at $10$meV.
+Parameters for (b): $m$: 0.02$\hbar^2$/eV$\cdot$\AA$^2$, $\alpha$: 0.05eV$\cdot$\AA, $Z_\parallel$: 0.001eV.
+(c) A sketch of cyclotron orbits of Rashba Hamiltonian with in-plane magnetic field.
+(d) For various configurations ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in left panel $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that is closest to $\epsilon_0$ in Eq.
+(\ref{whereisdiracpoint}), where $\epsilon_\text{rule}$ is determined by Eq.
 (\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RZ}(\bK)$.
-Parameters: $m$: 0.01$\hbar^2$/eV$\cdot$\AA$^2$, $l=100$\AA.
+Corresponding $l^2 \delta S^2/S$ are plotted in right panel.
+We only plotted in region where $0.4<\epsilon_0<1.0$(eV).\footnote{$l^2S\gg 1$ is assured by requiring $\epsilon_0>0.4$; the reason of choosing $\epsilon_0<1.0$ is Dirac point lying at high energy requires too much harmonics in numerical diagonalization.
+This requirement is equivalent to $\sqrt{0.8m}\alpha/\hbar<Z<\sqrt{2m}\alpha/\hbar$, corresponding to the boundaries of the plots in (d).} Parameters for (d): $m$: 0.01$\hbar^2$/eV$\cdot$\AA$^2$, $l=100$\AA.
 \label{fig:RZ}}

### 2018-09-12 paper.tex
Updates from ShareLaTeX

@@
 
-The remaining terms in \q{eq:H1} describe a generalized Zeeman interaction $B\calm$ which is the first-order-in-$B$ correction to the Peierls-Onsager Hamiltonian $\var(\bK)$.[kohn,blount,roth] Included in this interaction is the Zeeman coupling to the spin ($g_s\mu_Bs_z/\hbar$) and orbital ($M_z$) magnetic moment of the quasidegenerate band; the latter is expressible in terms of matrix elements of the velocity operator $\boldsymbol{\Pi}$ between Bloch wave functions $\psi_{n\bk}$ $\boldsymbol{\Pi}_{mn}=i\langle\psi_m|[\hat{H}, \hat{\boldsymbol{r}}]|\psi_n\rangle/\hbar$:
+The remaining terms in \q{eq:H1} describe a generalized Zeeman interaction $B\calm$ which is the first-order-in-$B$ correction to the Peierls-Onsager Hamiltonian $\var(\bK)$.[kohn,blount,roth] Included in this interaction is the Zeeman coupling to the spin ($g_s\mu_Bs_z/\hbar$) and orbital ($M_z$) magnetic moment of the quasidegenerate band; the latter is expressible in terms of matrix elements of the velocity operator $\boldsymbol{\Pi}_{mn}=i\langle\psi_m|[\hat{H}, \hat{\boldsymbol{r}}]|\psi_n\rangle/\hbar$ between Bloch wave functions $\psi_{n\bk}$:
 \e{
@@
 An over-tilted Dirac cone shall be referred to as type-II.
-Our case study of a II-Dirac point  connects  two electron-like  pockets [cf.\ \fig{fig:RZ}(a)], and  differs from previous case studies [Obrien, AALG] that connect an electron- and hole-like pocket.
+Our case study of a II-Dirac point  connects  two electron-like  pockets [cf.\ \fig{fig:RZ}(a,c)], and  differs from previous case studies [Obrien, AALG] that connect an electron- and hole-like pocket.
 
@@
 $\tilde{\lambda}_{\pm}$ is the slowly-varying semiclassical phase [cf.\ \s{sec:slowvariation}]  acquired by adiabatic transport along the spin-split orbit (denoted $+$ and $-$ for outer and inner orbit respectively).
-$\tilde{\lambda}_{\pm}$ is generated by  $\H_{\pm \pm}$ and has the same form as \q{phaseindependentorbit}, with $B\int_0^{T_c}\calm_{\sma{\pm\pm}}dt$ equal (in this model) to the single-band Berry phase ($\phi_{\pm}^B$) of orbit $\pm$.
+$\tilde{\lambda}_{\pm}$ is generated by  $\H_{\pm \pm}$ and has the same form as \q{phaseindependentorbit}, with $B\int_0^{T_c}\calm_{\pm\pm}dt/\hbar$ equal (in this model) to the single-band Berry phase ($\phi_{\pm}^B$) of orbit $\pm$.
 At energies far above the Dirac point  ($|E{-}\epsilon_0|{\gg}|Z_{\perp}|$) where the Zeeman interaction is negligible, both orbits encircle the Dirac point and hence $\phi_{\pm}^B{\approx}{\pm}\pi$; far below the Dirac point, neither orbit encircles the Dirac point, leading to $\phi_{\pm}^B{\approx}0$.
@@
 }
-$\Omega_{\pm}$ is the complete phase acquired by a wavepacket in adiabatically traversing orbit $\pm$, i.e., $\Omega$ sums both rapidly- and slowly-varying components of the semiclassical phase [cf.\ \s{sec:slowvariation}], as well as the quantum Maslov correction ($\gamma_{\pm}{=}\pi$) for circular orbits.
+$\Omega_{\pm}$ is the complete phase acquired by a wavepacket in adiabatically traversing orbit $\pm$, i.e., $\Omega$ sums both rapidly- and slowly-varying components of the semiclassical phase [\red{cf.\ \s{sec:slowvariation}}], as well as the quantum Maslov correction ($\gamma_{\pm}{=}\pi$) for circular orbits.
 A quantization rule analogous to \q{coscos} was previously derived by us for a II-Dirac point that intermediates an electron- and hole-like orbit [AALG].
@@
 \ref{fig:RZ}(a).
-The Maslov phase, which is generally equal to $\pi$ times the rotation number of an orbit (i.e., the number of rotations made by a tangent vector over one cycle)[100page], is trivially $2\pi$ for the trefoille orbit.
+The Maslov phase, which is generally equal to $\pi$ times the rotation number of an orbit, is trivially $2\pi$ for the trefoille orbit.
 

### 2018-09-14 paper.tex
Updates from ShareLaTeX

@@
 \end{equation}
-This implies that the spin-degeneracy of Landau levels is split   by  $\var_c|\lambda_1{-}\lambda_2|/2\pi$.
+This implies that the spin-degeneracy of Landau levels is split   by approximately  $\var_c|\lambda_1{-}\lambda_2|/2\pi$.
 The phase offsets $\lambda_a$ can be viewed as Floquet quasienergies of a time-periodic, perturbative Hamiltonian ($\calh$) that governs the dynamics of the spinor wavefunction.
@@
 $\delta \var$ is the projection of $\delta H$ to the quasidegenerate band associated to $\var(\bk)$, e.g., $\delta \var{=}\alpha(k_x\sigma_y{-}k_y\sigma_x)$ in the Rashba model.
-In the basis of energy-split bands (which we label by  ${+}$ and $-$ for the outer and inner orbit respectively),\footnote{We remark that the quantization rule is invariant under basis transformations within the degenerate band subspace (See App.
+In the basis of energy-split bands (which we label by ${+}$ and $-$ for bands corresponding to the outer and inner orbit respectively),\footnote{We remark that the quantization rule is invariant under basis transformations within the degenerate band subspace (See App.
 \ref{app:quantizationruleproof}); this may be exploited for efficient numerical computations.} $\delta \var$ is a diagonal matrix whose diagonal entries ($\delta \var_+,\delta \var_-$, corresponding to outer and inner orbit respectively; $\delta \var_+<\delta \var_-$) are related to the hybridization parameter:\footnote{The neglected term on the right-hand side of  \q{spinsplitwkb} is smaller (than the kept term) by a factor $\delta v_{\pm}/v$, which is the relative change in band speed $v=|\boldsymbol{v}|=\hbar^{-1}|\partial \var/\partial \bk|$ induced by the spin-orbit coupling.
@@
 We begin again with the Rashba model of a rotationally-symmetric Dirac cone. To convert this Dirac point to its asymmetric variant, 
-let us introduce a Zeeman coupling to an in-plane magnetic field $B_\parallel$:
+let us introduce a Zeeman coupling to an in-plane magnetic field $B_\parallel$ (parallel to the $+y$ direction):
 \e{ 
@@
 Parameters for (b): $m$: 0.02$\hbar^2$/eV$\cdot$\AA$^2$, $\alpha$: 0.05eV$\cdot$\AA, $Z_\parallel$: 0.001eV.
-(c) A sketch of cyclotron orbits of Rashba Hamiltonian with in-plane magnetic field.
+(c)\textbf{ Can we add axes E vs kx vs ky for main figure, and another set of axes kx vs ky for inset?} A sketch of cyclotron orbits of Rashba Hamiltonian with in-plane magnetic field.
 (d) For various configurations ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in left panel $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that is closest to $\epsilon_0$ in Eq.
@@
 This requirement is equivalent to $\sqrt{0.8m}\alpha/\hbar<Z<\sqrt{2m}\alpha/\hbar$, corresponding to the boundaries of the plots in (d).} Parameters for (d): $m$: 0.01$\hbar^2$/eV$\cdot$\AA$^2$, $l=100$\AA.
-\label{fig:RZ}}
+\textbf{please choose formatting such that footnote is at the back} \label{fig:RZ}}
 \end{figure}
@@
 $\calh$ above has been linearized with respect to  $t$, which vanishes in the vicinity of the Dirac point.
-The eigenbasis of $\sigma_x$ corresponds to two diabatic levels with characteristic slope $v_d{:}{=}\alpha k_E\omega^{\sma{\perp}}_c$; near $t{=}0$, the diabatic levels anticross  due to the hybridization terms ${\propto}\sigma_y,\sigma_z$.
+The eigenbasis of $\sigma_x$ corresponds to two diabatic levels with characteristic slope $v_d{:}{=}\alpha k_E\omega^{\sma{\perp}}_c$; near $t{=}0$, the diabatic levels anticross  due to the hybridization terms proportional to $\sigma_{y,z}$.
 Generally, the probability of tunneling across the hybridization-induced barrier is  $\rho^2{=}\exp(-2\pi\barmu)$, with $\barmu{=}{E_g}^2/{2v_d \hbar}$ and $E_g$ the energy gap at the center of the anticrossing;[Landau and lifshitz, Wittig] in this context,
@@
 \e{{\A}= \matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}} \diagmatrix{e^{i\tilde{\lambda}_+}}{e^{i\tilde{\lambda}_-}}. \la{propinplanezeeman}}
-$\tilde{\lambda}_{\pm}$ is the slowly-varying semiclassical phase [cf.\ \s{sec:slowvariation}]  acquired by adiabatic transport along the spin-split orbit (denoted $+$ and $-$ for outer and inner orbit respectively).
-$\tilde{\lambda}_{\pm}$ is generated by  $\H_{\pm \pm}$ and has the same form as \q{phaseindependentorbit}, with $B\int_0^{T_c}\calm_{\pm\pm}dt/\hbar$ equal (in this model) to the single-band Berry phase ($\phi_{\pm}^B$) of orbit $\pm$.
+$\tilde{\lambda}_{\pm}$ is generated by $\H_{\pm \pm}$ and has the same form as \q{phaseindependentorbit}, with $B\int_0^{T_c}\calm_{\pm\pm}dt/\hbar$ equal (in this model) to the single-band Berry phase ($\phi_{\pm}^B$) of band $\pm$ on $\frako_0$.
 At energies far above the Dirac point ($|E{-}\epsilon_0|{\gg}|Z_{\perp}|$) where the Zeeman interaction is negligible, both orbits encircle the Dirac point and hence $\phi_{\pm}^B{\approx}{\pm}\pi$; far below the Dirac point, neither orbit encircles the Dirac point, leading to $\phi_{\pm}^B{\approx}0$.
@@
 \includegraphics[width=0.8\columnwidth]{blochsphere.png}
-\caption{Change of Berry phase across the Zeeman-coupling-gapped Dirac point for inner [(a)] and outer [(b)] orbit.
-Berry phases can be calculated as half the solid angle enclosed by the corresponding loop on the Bloch sphere.
+\caption{Energy dependence of the Berry phase for inner [(a)] and outer [(b)] orbit.
+The Berry phase equals half the solid angle enclosed by the corresponding loop on the Bloch sphere \textbf{[loop must be explained, right-hand rule explained]}.
 The directions of the loops are indicated by black arrows and the black arrow outside of the sphere indicates increasing energy, where green lines correspond to $\epsilon_0$ in Eq.
-(\ref{whereisdiracpoint}).\label{fig:blochsphere}}
+(\ref{whereisdiracpoint}) \textbf{This figure is problematic because only the red loop is shown, while for the other loops the audience is left guessing.
+Perhaps it is best to separate one bloch sphere into three smaller spheres, such that each smaller sphere has only one loop.
+We might also show the analog of Fig 3a for energy above and below Dirac point.}.\label{fig:blochsphere}}
 \end{figure}
@@
 }
-$\Omega_{\pm}$ is the complete phase acquired by a wavepacket in adiabatically traversing orbit $\pm$, i.e., $\Omega$ sums both rapidly- and slowly-varying components of the semiclassical phase [\red{cf.\ \s{sec:slowvariation}}], as well as the quantum Maslov correction ($\gamma_{\pm}{=}\pi$) for circular orbits.
+$\Omega_{\pm}$ is the phase acquired by an electron in adiabatically traversing orbit $\pm$; the quantum Maslov correction $\gamma_{\pm}{=}\pi$ for circular orbits.
 A quantization rule analogous to \q{coscos} was previously derived by us for a II-Dirac point that intermediates an electron- and hole-like orbit [AALG].
@@
 To appreciate this, let us analyze the Landau levels (near the Dirac point) perturbatively in the small parameter $\tau$.
-To zeroth order, \q{coscos} reduces to\footnote{ Here, we have neglected $|\phi^B_{+}{+}\phi^B_{-}|$, which is approximately half the relative angle $\theta$ between two incoming trajectories that meet at the II-Dirac point.
-$\theta/2\pi=?$ \textbf{[please express in terms of Hamiltonian parameters]} and is of order $\delta S/S$.
-To the accuracy of our quasidegenerate perturbation theory,  $|\phi^B_{+}{+}\phi^B_{-}|$ is therefore negligible compared to the leading term $2l^2S$ in \q{trefoillerule}.
-}
-\e{2l^2S(E_n^0)+\pi\approx 2\pi n \rightarrow \{E_n^0(B)\}_{n\in\Z}.\label{trefoillerule}} 
+To zeroth order, \q{coscos} reduces to\footnote{Notice that $\phi_+ + \phi_-=0$ since for any two band model, Berry phases of the two bands cancel on the same orbit ($\frako_0$ here).}
+\e{2l^2S(E_n^0)+\pi = 2\pi n \rightarrow \{E_n^0(B)\}_{n\in\Z}.\label{trefoillerule}} 
  This may be interpreted as a quantization rule for a trefoille-shaped orbit with net action $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels, as plotted with dashed lines in Fig.\ \ref{fig:RZ}(b), are  periodic in $E{\rightarrow}E{+}\pi/l^2(\partial S/\partial E)$ and in $l^2{\rightarrow}l^2{+}\pi/S$.
@@
 \e{&\delta E_n(B) = \f{(-1)^{n+1}}{2\pi} \tau \var_c \cos\bigg(\f{l^2\delta S}{{2}}+\f{\phi_+^B-\phi_-^B}{2}-\bar{\varphi}\bigg) \lin
-    &\substack{\sma{Z_{\perp}{\rightarrow}0}\\=} \f{(-1)^{n+1}}{4\sqrt{2\pi}}  \var_c \f{(E-\epsilon_0)l}{\alpha\epsilon_0^{3/2}}\cos\bigg(\f{l^2\delta S}{{2}}-\bar{\varphi}\bigg),\label{RZfirstorderE}}
-with the right-hand side (of each line) evaluated at $E_n^0(B)$. The second line of \q{RZfirstorderE} is more practically useful where $m{\ll}m_0$.
-
-%If the out-of-plane Zeeman coupling $\zper$ were zero, $\tau$ vanishes as $|E{-}\epsilon_0|$ in the limit $E{\rightarrow}\epsilon_0$, hence $\delta E_n{\propto}\tau \text{sign}[\epsilon_0-E]$ would be analytic in $B$.
-However,  nonzero $\zper$ implies that $\tau$ approaches a constant $(\sqrt{2\pi \bar{\mu}_{\sma{\text{min}}}})$ as $E{\rightarrow}\epsilon_0$, leading to a non-analyticity  in $B$ as the Landau level crosses the Dirac point energy.
-\textbf{[I am not sure that higher-order-in-B corrections may restore analyticity, let's check this numerically]}\red{[I found no evidence of non-analyticity across the Dirac point.
-Eq.
-(\ref{RZfirstorderE}) is actually discontinuous across Dirac point, while Eq.
-(\ref{coscos}) is obviously continuous]}
-
-%$\calh$ above is only defined for $|t|{\ll}T^{\sma{\perp}}_c$. 
-%$\calh$ is simplest to interpret in the language of Landau-Zener dynamics:  
-%$V_0{:}{=}\sqrt{(Z_\parallel-\alpha k_F)^2{+}Z_{\perp}^2}{>}0$,
-
-%While tunneling that is localized to type-II Dirac points have been analyzed as a Landau-Zener problem [maxim,beenakker] and is solvable with generalized
+    &\substack{\sma{Z_{\perp}{\rightarrow}0}\\ \approx} \f{(-1)^{n+1}}{4\sqrt{2\pi}}  \var_c \f{(E-\epsilon_0)l}{\alpha(\epsilon_0/Z_{\parallel})^{3/2}}\cos\bigg(\f{l^2\delta S}{{2}}-\bar{\varphi}\bigg),\label{RZfirstorderE}}
+with the right-hand side (of each line) evaluated at $E_n^0(B)$. The second line of \q{RZfirstorderE} has greater utility where $m{\ll}m_0$.
 
@@
 
-\section{Single-parameter tuning of Landau-Level quasidegeneracies}\label{sec:llquasideg}
-
-Is there a relation between eigenvalue-degeneracies of  $\A$ and degeneracies of Landau levels?
+\section{Tuning the spin-degeneracy of Landau Levels}\label{sec:llquasideg}
+
+We have argued in \s{sec:qtznrules} that the subleading corrections ($\lambda_{1,2}$) to the quantization rule [cf.\ \q{eq:rule}] generically lift the spin-degeneracy of Landau levels -- the level splitting is approximately $\var_c(\lambda_1{-}\lambda_2)/2\pi$.
+Conversely, Landau levels are approximately spin-degenerate if $\lambda_1{=}\lambda_2$ (mod $2\pi$); this non-generic scenario may require fine-tuning of the Peierls-Onsager Hamiltonian.
+
+In \s{sec:relatedegeneracies}, we will describe the precise relation between eigenvalue-degeneracies of  $\A$ and (near) degeneracies of Landau levels.
+We then ask how many tunable real parameters are necessary to fine-tune an eigenvalue-degeneracy of $\A$.
+Our answer is either $0,1,2$ or $3$, depending on the symmetry class of the orbit.
+Before providing this general answer in \s{sec:tenfold}, we will first develop physical intuition by studying two models [cf.\ \s{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}] where only one tunable parameter is needed -- this can be the B field itself.
+Finally, the experimental implications of single- and double-parameter tuning of Landau-level crossings are discussed in \s{sec:qo}.
+
+\subsection{Relating the eigenvalue-degeneracy of $\A$ to the spin-degeneracy of Landau levels}\la{sec:relatedegeneracies}
+
 Suppose the propagator $\A$ were degenerate at $(\bar{E},\bar{B})$, i.e., $\lambda_+(\bar{E},\bar{B})=\lambda_-(\bar{E},\bar{B})$ mod $2\pi$.
@@
 
-In the absence of any symmetry,  the ``non-crossing theorem'' [von Neumann,wigner] states that eigenvalue-degeneracies of complex Hamiltonians are attained by tuning three real parameters; this non-crossing rule applies also to Landau-level degeneracies of the Peierls-Onsager Hamiltonian.
-\textbf{[Questionable: the original theorem was proven for finite-dimensional Hamiltonians]} Henceforth it should be understood that any parameter we refer to is real, rather than complex.
-Here, we would prove a stronger statement: in the absence of symmetry, a non-crossing rule also applies to Landau-level quasidegeneracies.
-Equivalently, we would show that eigenvalue-degeneracies of the unitary propagator [cf.
-\q{eq:prop}] are attainable by tuning three parameters.
-Indeed, any two-by-two unitary  can be decomposed as $\A{=}e^{i\phi}{\cal \bar{A}}$, where ${\cal \bar{A}}{\in}\text{SU}(2)$ has eigenvalues $\{e^{i\bar{\lambda}},e^{-i\bar{\lambda}}\}$ which completely determine $\delta \lambda$.
+%In the absence of any symmetry,  the ``non-crossing theorem'' [von Neumann,wigner] states that eigenvalue-degeneracies of complex Hamiltonians are attained by tuning three real parameters; this non-crossing rule applies also to Landau-level degeneracies of the Peierls-Onsager Hamiltonian.
+\textbf{[Questionable: the original theorem was proven for finite-dimensional Hamiltonians]}  Here, we would prove a stronger statement:
+
+%a non-crossing rule also applies to Landau-level quasidegeneracies. Equivalently, we would show that
+
+In the absence of symmetry,  eigenvalue-degeneracies of the unitary propagator [cf.
+\q{eq:prop}] are attainable by tuning three real parameters.
+Analogously, it is well known (as the non-crossing rule in quantum theory[von Neumann,wigner]) that eigenvalue-degeneracies of complex, finite-dimensional matrix Hamiltonians are also attainable by tuning three real parameters.
+ To prove the non-crossing rule for two-by-two unitaries, we begin by decomposing any such matrix as $\A{=}e^{i\phi}{\cal \bar{A}}$, such that  ${\cal \bar{A}}{\in}\text{SU}(2)$ being equal to $\pm I$ is a necessary and sufficient condition for an eigenvalue-degeneracy of $\A$.
 Suppose ${\cal \bar{A}}$ is parametrized by $d$ independent real numbers  $\{R_1,\ldots,R_{d}\}{:}{=}\bR $ which are tunable in experiments or on paper.
-The condition of degeneracy (det$[{\cal \bar{A}}(\bR){\pm}I]{=}0$) defines a set of manifolds in $\bR$-space which are henceforth referred to as degeneracy manifolds.
+Then ${\cal \bar{A}}(\bR){=}{\pm}I$ defines a set of manifolds in $\bR$-space which are henceforth referred to as degeneracy manifolds.
 The codimension of the degeneracy manifold  is defined as $d$ minus the dimension of said manifold; intuitively, this codimension is the number of linearly-independent parameters needed to fine-tune a degeneracy.
-Henceforth, we adopt the shorthand that \textit{codimension} always refers to a codimension of a degeneracy manifold (the exact manifold is to be inferred from the context).
+Here and henceforth, we adopt the shorthand that real parameters will just be referred to as parameters, and \textit{codimension} always refers to a codimension of a degeneracy manifold.
 In the canonical parametrization of $\text{SU}(2)$ over the three-sphere $S^3$:
@@
 \red{[Needs to introduce the symmetries more gently]} Since the magnetic field is odd under time reversal, and behaves as a pseudovector under spatial transformations, we deduce that exact symmetries (denoted $g$) are only of two types: either (i) $g$  preserves both the direction of time and the orientation of cyclotron orbits (in the 2D $\bk$-space perpendicular to $B$), or (ii) $g$ inverts both said objects.
-(i) is exemplified by a rotational symmetry with the rotational axis aligned parallel to the field, and (ii) by the composition  of time reversal $T$ and a spatial reflection $\mathfrak{r}_x$ (with reflection axis perpendicular to $B$)\red{[???, We only have two classes now?]}.
+(i) is exemplified by a rotational symmetry with the rotational axis aligned parallel to the field, and (ii) by the composition  of time reversal $T$ and a spatial reflection $\mathfrak{r}_x$ (with reflection axis perpendicular to $B$).
 
@@
 It would be quite confusing if we also let $\delta\lambda_a\sim l^2\delta S$]}) acquired along a spin-split trajectory to the \red{top}.
-In more detail, $\lambda_{\pm}'{=}{\pm}l^2\delta S/4$ up to a field-independent geometric phase \footnote{due to this field-independent phase, it is not necessary that $\delta\lambda_+=-\delta\lambda_-$}; the latter is equal to half the angle swept by the in-plane spin-orbit field $(0,wk_x,\bk^2/2m_2{-}\mu)$ along the spin-split trajectory; cf.\ discussion in \s{sec:Rashba} \red{[Are we really talking about open Berry phase here?]}.
+In more detail, $\lambda_{\pm}'{=}{\pm}l^2\delta S/4$ up to a field-independent geometric phase \footnote{due to this field-independent phase, it is not necessary that $\delta\lambda_+=-\delta\lambda_-$}.
 The time-evolution propagator  describes the time-ordered, coherent process of interband tunneling (as described by the scattering matrix of \q{scattmat})
  and adiabatic dynamics:
-\e{\A&=\red{e^{i\f{\lambda_+'+\lambda_-'}{2}}}\times\nonumber\\
+\e{\A&=\red{e^{i(\lambda_+'+\lambda_-')}}\times\nonumber\\
 &\left(\matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}}\red{\diagmatrix{e^{i\f{\lambda_+'-\lambda_-'}{2}}}{e^{i\f{\lambda_-'-\lambda_+'}{2}}}} \right)^2.
@@
 
-\section{Magnetic quantum Oscillations}\label{sec:qo}
+\subsection{Magnetic quantum Oscillations}\label{sec:qo}
 

### 2018-09-15 paper.tex
Updates from ShareLaTeX

@@
 \includegraphics[width=0.9\columnwidth]{orbits.png}
-\caption{(a) \textbf{[some axes will be helpful]} Solid (resp.\ dashed) lines respectively illustrate the band dispersion of an electron gas with (resp.\ without) Rashba spin-orbit coupling.
+\caption{(a) Solid (resp.\ dashed) lines respectively illustrate the band dispersion of an electron gas with (resp.\ without) Rashba spin-orbit coupling.
 The oriented circles illustrate the spin-orit-split orbits for a magnetic field pointing to $-z$ direction.
-\textbf{[might replace Delta with $2\alpha k_E$ at some point]} (b) The zeroth-order orbit $\frako_0$ is indicated by a dashed circle with area $S$; $\delta S$ is the differential area  between two spin-orbit-split orbits.
+(b) The zeroth-order orbit $\frako_0$ is indicated by a dashed circle with area $S$; $\delta S$ is the differential area  between two spin-orbit-split orbits.
 The spin texture is indicated by purple arrows.\label{fig:orbits}}

### 2018-09-16 paper.tex
Updates from ShareLaTeX

@@
 \e{\calh(\bk)=-\alpha k\tau_z{+}\f{g_s}{2}\mu_{\sma{B}}B\tau_x \red{-} \f{eB\hbar}{2m} (\tau_x-I) \epsilon_{\alpha\beta} k_{\red{\alpha}}\nabla_{\red{\beta}}\theta,\la{rashbaeffham}}
-where $\tau_i$ are a new set of Pauli matrices with $\tau_z{=}{+} 1$ and ${-}1$ corresponding to the outer and inner orbits, respectively \red{[I switched the sign in the equation above to emphasize the sign difference.]}.
+where $\tau_i$ are a new set of Pauli matrices with $\tau_z{=}{+} 1$ and ${-}1$ corresponding to the outer and inner orbits, respectively.
 $e^{i\theta_{\bk}}{=}(ik_x{-}k_y)/k$ is the angle of the in-plane spin-orbit field $({-}\alpha k_y,\alpha k_x,0)$, which winds once over $\frako_0$; the spin of our basis vectors likewise winds, in parallel (or anti-parallel) alignment with this field (see Fig.
@@
 We have argued in \s{sec:qtznrules} that the subleading corrections ($\lambda_{1,2}$) to the quantization rule [cf.\ \q{eq:rule}] generically lift the spin-degeneracy of Landau levels -- the level splitting is approximately $\var_c(\lambda_1{-}\lambda_2)/2\pi$.
-Conversely, Landau levels are approximately spin-degenerate if $\lambda_1{=}\lambda_2$ (mod $2\pi$); this non-generic scenario may require fine-tuning of the Peierls-Onsager Hamiltonian.
+Conversely, Landau levels are approximately spin-degenerate if $\lambda_1{=}\lambda_2$ (mod $2\pi$) -- this degeneracy condition for the eigenvalues of $\A$ may require fine-tuning of the Peierls-Onsager Hamiltonian.
 
 In \s{sec:relatedegeneracies}, we will describe the precise relation between eigenvalue-degeneracies of  $\A$ and (near) degeneracies of Landau levels.
-We then ask how many tunable real parameters are necessary to fine-tune an eigenvalue-degeneracy of $\A$.
-Our answer is either $0,1,2$ or $3$, depending on the symmetry class of the orbit.
-Before providing this general answer in \s{sec:tenfold}, we will first develop physical intuition by studying two models [cf.\ \s{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}] where only one tunable parameter is needed -- this can be the B field itself.
-Finally, the experimental implications of single- and double-parameter tuning of Landau-level crossings are discussed in \s{sec:qo}.
-
-\subsection{Relating the eigenvalue-degeneracy of $\A$ to the spin-degeneracy of Landau levels}\la{sec:relatedegeneracies}
-
-Suppose the propagator $\A$ were degenerate at $(\bar{E},\bar{B})$, i.e., $\lambda_+(\bar{E},\bar{B})=\lambda_-(\bar{E},\bar{B})$ mod $2\pi$.
+We then ask how many tunable real parameters are needed to attain an eigenvalue-degeneracy of $\A$.
+Our answer is  $3$ in the absence of symmetry, as discussed in \s{sec:introducecodimension}; the answer may reduce to $0,1$ or $2$ depending on the symmetry class of the orbit, as will be explained in \s{sec:tenfold}.
+Before this general symmetry classification,  we will first develop physical intuition by studying two rotationally-symmetric models [cf.\ \s{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}] where only one tunable parameter is needed -- this can be the $B$ field itself.
+Finally, the experimental implications of single- and double-parameter tuning of Landau-level degeneracies are discussed in \s{sec:qo}.
+
+\subsection{Relating the eigenvalue-degeneracy of $\A$ to the quasidegeneracy of Landau levels}\la{sec:relatedegeneracies}
+
+Suppose the propagator $\A$ were degenerate at $(\bar{E},\bar{B})$, i.e., $\lambda_1(\bar{E},\bar{B})=\lambda_2(\bar{E},\bar{B})$ mod $2\pi$.
 Generically, $(\bar{E},\bar{B})$ is not \emph{simultaneously} a solution of the quantization rule in \q{eq:rule}.
@@
 To obtain a Landau level, we may tune either $E$ or $B$   away from $(\bar{E},\bar{B})$, and  utilize that  $\lambda_{\pm}$ are slowly-varying functions of $(E,B)$ compared to $l^2S(E)$:
-\e{\left|l^2\p{S}{E}\right| \gg \left|\p{\lambda_a}{E}\right|,\, \left|S\right| \gg \left|\p{\lambda_a}{l^2}\right|;} 
-these inequalities are guaranteed by the quasidegeneracy condition ($\delta S{\ll}S$) and the smoothness of $S(E)$, as we quantify in \app{sec:slowvariation}.
-For fixed $\bar{B}$, we are therefore guaranteed to find two Landau levels (denoted $E_{\pm}$) in close proximity to $\bar{E}$, with a splitting of order:
-\e{ \f{E_{+}-E_-}{\var_c}\bigg|_{\bar{B}} = \order\left( \f{\partial \lambda_a/\partial E}{l^2\partial  S/\partial E}  \right)\ll 1.\la{llquasideg}}
-Alternatively, we may fix $\bar{E}$ and investigate how Landau levels disperse as a function of $B$; the analog of \q{llquasideg}  is the existence of two Landau levels (denoted $l^2_{\pm}$) in close proximity to $\bar{l}^2$, with a splitting of order:
-\e{  \f{l^2_{+}-l^2_-}{T_{\sma{1/B}}}\bigg|_{\bar{E}} = O\left( \f{\partial \lambda_a/\partial l^2}{S} \right)\ll 1,\as T_{\sma{1/B}}:=\f{2\pi}{S(E)}.\la{llquasidegB} }
-$\partial \lambda_a/\partial l^2$ has been estimated in \s{sec:slowvariation}, and
-$T_{\sma{1/B}}$ above is the period of quantum oscillations (in the absence of spin-orbit coupling).
-To recapitulate, for every exact degeneracy of $\cala$, there must exist, in close proximity, a pair of Landau levels which are exactly degenerate, or nearly degenerate in the sense of \qq{llquasideg}{llquasidegB}.
-Such Landau levels will be called \textit{quasidegenerate}.
+\e{l^2\left|\p{S}{E}\right| \gg \left|\p{\lambda_a}{E}\right|,\, \left|S\right| \gg \left|\p{\lambda_a}{l^2}\right|;} 
+these inequalities are guaranteed by the quasidegeneracy condition ($\delta S{\ll}S$) and the smoothness of $S(E)$, as shown in \app{sec:slowvariation}.
+For fixed $\bar{B}$, we are therefore guaranteed to find a number (of order one) of paired Landau levels  in close proximity to $\bar{E}$, with each pair having an energetic splitting of order:
+\e{ \bigg|\f{E_{1}-E_2}{\var_c}\bigg|_{B=\bar{B}} = \order\left( \f{\partial \lambda_a/\partial E}{\bar{l}^2\partial  S/\partial E}  \right)\ll 1.\la{llquasideg}}
+Alternatively, we may fix $\bar{E}$ and investigate how Landau levels disperse as a function of $B$; the analog of \q{llquasideg}  is the existence of paired Landau levels in close proximity to $\bar{l}^2$, with a splitting of order:
+\e{  \bigg|\f{l^2_{+}-l^2_-}{T_{{l^2}}}\bigg|_{E=\bar{E}} = O\left( \f{1}{S}\p{\lambda_a}{l^2} \right)\ll 1,\;\; T_{{l^2}}:=\f{2\pi}{S(\bar{E})}.\la{llquasidegB} }
+$\partial \lambda_a/\partial l^2$ is estimated in \app{sec:slowvariation}, and
+$T_{l^2}$ above is the period of quantum oscillations (in the absence of spin-orbit coupling).
+To recapitulate, for every exact degeneracy of $\cala$, there must exist, in close proximity, a number of paired Landau levels which are exactly degenerate, or nearly degenerate in the sense of \qq{llquasideg}{llquasidegB}.
+Each such pair of Landau levels will be called \textit{quasidegenerate}.
 
@@
 
-In the absence of symmetry,  eigenvalue-degeneracies of the unitary propagator [cf.
+\subsection{Codimension analysis in the absence of symmetry}\la{sec:introducecodimension}
+
+In the absence of symmetry,  eigenvalue-degeneracies of the unitary propagator $\A$ [cf.
 \q{eq:prop}] are attainable by tuning three real parameters.
@@
  To prove the non-crossing rule for two-by-two unitaries, we begin by decomposing any such matrix as $\A{=}e^{i\phi}{\cal \bar{A}}$, such that  ${\cal \bar{A}}{\in}\text{SU}(2)$ being equal to $\pm I$ is a necessary and sufficient condition for an eigenvalue-degeneracy of $\A$.
-Suppose ${\cal \bar{A}}$ is parametrized by $d$ independent real numbers  $\{R_1,\ldots,R_{d}\}{:}{=}\bR $ which are tunable in experiments or on paper.
-Then ${\cal \bar{A}}(\bR){=}{\pm}I$ defines a set of manifolds in $\bR$-space which are henceforth referred to as degeneracy manifolds.
-The codimension of the degeneracy manifold  is defined as $d$ minus the dimension of said manifold; intuitively, this codimension is the number of linearly-independent parameters needed to fine-tune a degeneracy.
-Here and henceforth, we adopt the shorthand that real parameters will just be referred to as parameters, and \textit{codimension} always refers to a codimension of a degeneracy manifold.
 In the canonical parametrization of $\text{SU}(2)$ over the three-sphere $S^3$:
-\e{{\cal \bar{A}}{=}\matrixtwo{R_1{+}iR_2}{R_3{+}iR_4}{{-}R_3{+}iR_4}{R_1{-}iR_2},\as \sum_{j=1}^4R_j^2{=}1,  \la{s3}}
-${\cal \bar{A}}{=}{+}I$ (resp.\ ${=}{-}I$) lie on a point which we refer to as the north pole (resp.\ south pole); both points have codimension three in $S^3$.
-If special unitaries were uniformly distributed over $S^3$, then encountering a spectral degeneracy for a randomly-selected special unitary would be an exceedingly rare event -- three parameters need be tuned to find either pole on $S^3$,  i.e., the codimension of degeneracy manifold is three.
+\e{{\cal \bar{A}}{=}\matrixtwo{R_1{+}iR_2}{R_3{+}iR_4}{{-}R_3{+}iR_4}{R_1{-}iR_2},\;\; \sum_{j=1}^4R_j^2{=}1,\;\; R_j\in \mathbb{R},  \la{s3}}
+${\cal \bar{A}}{=}{\pm}I$ lie on distinct points of $S^3$, and are attainable by tuning three real parameters: $R_3{=}R_4{=}0$, and the phase of $R_1{+}iR_2$ must equal $0$ or $\pi$.
+The conclusion that three parameters need be tuned remains valid for any  non-singular\footnote{By `non-singular parametrization', we mean a set of parameters related to those in \q{s3} by a non-singular coordinate transformation.} parametrization of SU$(2)$.
+
+%If special unitaries were uniformly distributed over $S^3$, then encountering a spectral degeneracy for a randomly-selected special unitary would be an exceedingly rare event -- three parameters need be tuned to find either pole on $S^3$,  i.e., the codimension of degeneracy manifold is three.
 If only one  or two  parameters (in $\{R_1,\ldots,R_4\}$)  can be tuned, then in general we should not expect a degeneracy.
 
+ To generalize the above discussion, let us parametrize ${\cal \bar{A}}$ by $d$ independent real numbers  $\{R_1,\ldots,R_{d}\}{:}{=}\bR $;  ${\cal \bar{A}}(\bR){=}{\pm}I$ defines a set of manifolds in $\bR$-space which we refer to as degeneracy manifolds; in the above example, these manifolds comprise two points on $S^3$.
+The codimension of the degeneracy manifold  is defined as $d$ minus the dimension of said manifold; alternatively stated, the codimension is the number of linearly-independent parameters needed to fine-tune a degeneracy.
+Here and henceforth, we adopt the shorthand that  \textit{parameters} will always refer to real parameters, and \textit{codimension} always refers to a codimension of a degeneracy manifold.
+
 %, which may be viewed as imposing a $U(1){\times}U(1)$ symmetry.\footnote{$\cala$ commutes with any diagonal unitary matrix, with diagonal entries equal to two arbitrary $U(1)$ phase factors.} T
 
-It is well-known that symmetry may reduce codimension.
-The conceptually-simplest example is the approximate symmetry of band conservation, which has been described in \s{sec:qtznrules}.
-The salient fact to recall is that  $\cala$ becomes diagonal ($R_3{=}R_4{=}0$) in the basis of energy bands.
-The phase of $R_1{+}iR_2$ is then the single parameter  to tune $\cala{=}{\pm}I$, i.e., the codimension is unity.
-From \q{phaseindependentorbit} we deduce that phase[$R_1{\pm}iR_2]{=}{\pm} l^2\delta S/2$ plus corrections which are field-independent, hence degeneracies of $\cala$ occur with a periodicity (in $l^2$) of $2\pi/\delta S$.
-This periodicity  has a dual interpretation  in real space -- as a periodic increment of a single flux quantum for  the differential magnetic flux (between the two spin-split orbits).
-
-We may ask if these weak-field degeneracies (based on approximate band-conservation symmetry) persist in the strong-field regime where the adiabatic approximation breaks down.
-If there is no exact symmetry that persists at finite field, we have shown in the above demonstration [cf.\ \q{s3}] that the codimension is three, hence we should not expect robust degeneracies by tuning $B$ alone.
-Our next tasks are to identify the exact symmetries which persist in the presence of a finite magnetic field, and to identify which of the exact symmetries result in a reduced codimension.
-
-\red{[Needs to introduce the symmetries more gently]} Since the magnetic field is odd under time reversal, and behaves as a pseudovector under spatial transformations, we deduce that exact symmetries (denoted $g$) are only of two types: either (i) $g$  preserves both the direction of time and the orientation of cyclotron orbits (in the 2D $\bk$-space perpendicular to $B$), or (ii) $g$ inverts both said objects.
-(i) is exemplified by a rotational symmetry with the rotational axis aligned parallel to the field, and (ii) by the composition  of time reversal $T$ and a spatial reflection $\mathfrak{r}_x$ (with reflection axis perpendicular to $B$).
-
-One of our main results is that  rotational symmetry (of both discrete and continuous types) enforces unit codimension.
-This will be demonstrated by two  case studies in \s{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}; the first study describes a Rashba-Dresselhaus 2DEG where the adiabatic approximation breaks down at all points along the semiclassical orbit; in the second study, the adiabatic approximation breaks down only in the vicinity of type-II Dirac points \textbf{[might mention angular oscillations]}.
-
-In comparison, the composed symmetry $T\mathfrak{r}_x$ enforces a codimension of two.
-This result, in addition to a comprehensive codimension analysis of all relevant symmetry classes, is presented in \s{sec:tenfold}.
+It is well-known that symmetry may reduce codimension.[wigner,von neumann] The conceptually-simplest example is the approximate symmetry of band conservation, which exists in the adiabatic regime [cf.\ \s{sec:qtznrules}].
+Recall from \q{phaseindependentorbit} that  $\cala$ becomes diagonal ($R_3{=}R_4{=}0$) in the basis of energy bands,
+with phase[$R_1{\pm}iR_2]{=}{\pm} l^2\delta S/2$ plus field-independent corrections. Since this  phase alone  can be  tuned to attain $\cala{=}{\pm}I$, the codimension is unity.
+As a function of $l^2$, we deduce that Landau-level quasi-crossings occur  with a periodicity of $2\pi/\delta S$.
+This periodicity  has a dual interpretation  in real space -- as a periodic increment of a single flux quantum for  the differential magnetic flux (between the two split orbits).
+
+We may ask if these quasi-crossings (based on band-conservation symmetry) persist at stronger fields where adiabaticity breaks down.
+If no symmetry persists at finite field, then the codimension is three [cf.\ \q{s3}], hence Landau-level quasi-crossings should not generically be found by varying $B$ alone.
+
+At finite field (assumed to be homogeneous in space and time), any remnant  symmetry (denoted $g$) must preserve the component of the magnetic moment in the direction of  $\bB$.
+The magnetic moment is odd under time reversal, and behaves as a pseudovector under spatial transformations.[sakurai] Therefore, either (i) $g$  preserves both the direction of time and the magnetic moment, or (ii) $g$ inverts both said objects.
+(i) is exemplified by a rotational symmetry with the rotational axis aligned parallel to the field, and (ii) by the composition  of time reversal $T$ and a spatial reflection $\mathfrak{r}_x$ (with reflection axis perpendicular to $\vec{B}$).
+
+One of our main results is that  rotational symmetry (of both discrete and continuous types) results in degeneracy manifolds with unit codimension.
+This will be demonstrated by two  case studies: the Rashba 2DEG in \s{sec:singleparameterrashba}, and a model with II-Dirac points in \ref{sec:rotsymmbreakdown}.
+In contrast,  $T\mathfrak{r}_x$ results in manifolds with codimension two.
+The latter result, in addition to a comprehensive codimension analysis for all symmetry classes, is presented in \s{sec:tenfold}.
+
+%The first study describes a Rashba-Dresselhaus 2DEG where the adiabatic approximation breaks down at all points along the semiclassical orbit; in the second study, the adiabatic approximation breaks down only in the vicinity of type-II Dirac points.
 
@@
 
-\subsection{Rashba-Dresselhaus 2DEG}\la{sec:singleparameterrashba}
-
-We return to the Rashba model absent Dresselhaus spin-orbit coupling and in-plane Zeeman field.
-Owing to a continuous rotational symmetry (denoted $\mathfrak{c}_{\infty}$), $\calh(\bk)$ is a constant along the circular zeroth-order orbit [cf.\ \q{rashbaeffham}], and the propagator simplifies to $\A{=}$exp$[{-}i\calh T_c/\hbar]$.
-The latter is expressible in the exponential form  $\A =\exp[-i2\pi(r_1\tau_x{+}r_2\tau_z)]$, with $(r_1,r_2){=}(g_s'/4-1/2,-\alpha k_{\red{F}}ml^2\red{+1/2})\in\R^2$.
-In this two-dimensional parameter space, all degeneracies occur along circles of radius $\sqrt{r_1^2+r_2^2}{=}\red{j}/2$ with $\red{j}$ a nonnegative integer; half the circles ($\red{j}$ even) correspond to $\A=I$, and the other half to $\A=-I$.
-Except for $\red{j}=0$, all degeneracy manifolds have unit codimension, and can be tuned by varying $B$ alone (with fixed $g_s'$); these manifolds are analogous to line nodes (of Hamiltonian degeneracies) in 2D $\bk$-space -- a topic of recent interest.
-That tuning $\red{j}{=}0$ requires two parameters can be understood from an elementary result in quantum mechanics: taking $\alpha{=}0$ \textit{and} $m=m_0$, we recover the Zeeman-split Landau levels of a free electron gas without spin-orbit coupling; all levels (except the lowest) are spin-degenerate owing to the equality of the Zeeman and cyclotron energies.
-[LandauLifshitzstatphysI]   In this exactly-soluble model [cf.\ \q{eq:Rashba-exact}], all  degeneracies ($\red{j} \ge 0$) of $\A$ correspond to exact Landau-level degeneracies, rather than the near degeneracies described by \qq{llquasideg}{llquasidegB}.
+\subsection{Unit codimension for the Rashba 2DEG}\la{sec:singleparameterrashba}
+
+To exemplify the role of rotational symmetry in reducing codimension,
+we return to the Rashba model [cf.\ \q{eq:Rashba-Hamiltonian}] absent Dresselhaus spin-orbit coupling and in-plane Zeeman field.
+Owing to a continuous rotational symmetry (denoted $\mathfrak{c}_{\infty}$), $\calh(\bk)$ is a constant along the circular zeroth-order orbit [cf.\ \q{rashbaeffham}], and therefore the propagator simplifies to $\A{=}$exp$[{-}i\calh T_c/\hbar]$.
+The latter is expressible in the exponential form:
+\e{\A =e^{-i2\pi(r_1\tau_x{+}r_2\tau_z)}, \;\;(r_1,r_2){=}\bigg(\f{g_{\sma{\text{eff}}}}{4}-\f1{2},\f1{2}-\f{\alpha k_{{E}}}{\var_c}\bigg).\notag} 
+All degeneracies occur along circles of radius $\sqrt{r_1^2+r_2^2}{=}{j}/2$, with ${j}$ a nonnegative even (resp.\ positive odd) integer for  $\A{=}I$ (resp.\ $\A{=}{-}I$).
+In this exactly-soluble model [cf.\ \q{eq:Rashba-exact}], all  degeneracies (${j} {\ge} 0$) of $\A$ correspond to exact Landau-level degeneracies, rather than the near degeneracies described by \qq{llquasideg}{llquasidegB}.
+
+That the ${j}{=}0$ manifold has codimension two can be understood from an elementary result in quantum mechanics: taking $\alpha{=}0$ \textit{and} $m{=}m_0$, we recover the Zeeman-split Landau levels of a free electron gas without spin-orbit coupling; all levels (except the lowest) are spin-degenerate owing to the equality of the Zeeman and cyclotron energies.[LandauLifshitzstatphysI]   All other manifolds ($j{>}0$) have unit codimension, and can be tuned by varying $B$ alone (with fixed $g_{\sma{\text{eff}}}$); these manifolds are analogous to line nodes (of Hamiltonian degeneracies) in 2D $\bk$-space -- a topic of recent interest.[citations]
 
@@
 The Rashba model suffers from an oversimplification -- continuous rotational symmetry is not a symmetry of solids.
-That is to say, it does not belong in any (magnetic) space group.
-It is possible for $\mathfrak{c}_{\infty}$-symmetric models to approximate Hamiltonians with a discrete, order-$n$ rotational symmetry (denoted $\mathfrak{c}_N$) \red{[Let's use capital N in $\mathfrak{c}_N$ since N coincides with order]}.
-To what extent are Landau-level degeneracies (of $\mathfrak{c}_{\infty}$-symmetric systems) robust when $\mathfrak{c}_{\infty}$ is perturbatively reduced to $\mathfrak{c}_N$?
-Our general answer is out of every $N$ degeneracies of $\A$, $N-1$ of them are robust.
-\textbf{[results for n=3,4,6 must be checked]}.
-
-While full proof of the above claim is delegated to App.
-\ref{app:codimension}, let us illustrate the simplest example $N=2$ by introducing the Dresselhaus spin-orbit term ($\propto \beta$) into the Rashba model [cf.\ \q{hamRD}].
-This has the desired effect of reducing $\mathfrak{c}_{\infty}$ to a discrete $\mathfrak{c}_2$ symmetry.
-Since $\A$ depends on $\alpha,\beta,l$ only through $\alpha l^2$ and $\beta l^2$, we consider the three-dimensional parameter space $(\alpha l^2,\beta l^2,g_s')\in \mathbb{R}^3$.
+That is to say, it does not belong in any crystallographic space group.
+It is possible for $\mathfrak{c}_{\infty}$-symmetric $\bk{\cdot}\bp$ models to approximate Bloch Hamiltonians (defined over the Brillouin torus) with a discrete, order-$N$ rotational symmetry (denoted $\mathfrak{c}_N$).
+To what extent are degeneracies of $\A$ (for $\mathfrak{c}_{\infty}$-symmetric systems) robust when $\mathfrak{c}_{\infty}$ is perturbatively reduced to $\mathfrak{c}_N$?
+For each of $N{=}2,3,4$ and $6$ (the allowed values in space groups), we find that $N{-}1$ out of every $N$ degeneracies (of $\A$) are robust, as proven in App.
+\ref{app:codimension}.
+
+For illustration, let us reduce $\mathfrak{c}_{\infty}$ symmetry to  $\mathfrak{c}_2$  by adding the Dresselhaus spin-orbit term ($\propto \beta$) to the Rashba model [cf.\ \q{hamRD}].
+Since $\A$ depends on $\alpha,\beta,l$ only through $\alpha l^2$ and $\beta l^2$, we consider the three-dimensional parameter space $(\alpha l^2,\beta l^2,g_{\sma{\text{eff}}})\in \mathbb{R}^3$.
 If a  line node (in the $\beta{=}0$ plane) were perturbatively stable to finite $\beta$, then it would be embedded in a two-dimensional degeneracy hypersurface of $\mathbb{R}^3$; if the planar line node were unstable, this embedding does not happen, i.e., the planar line node is simply a line node in $\mathbb{R}^3$.
@@
 Let us further explore single-parameter tunability of Landau-level quasidegeneracies in this limit by introducing a rotational symmetric Hamiltonian with isolated breakdown junctions at several isolated $\bk$ points.
-Besides being a useful toy model, this Hamiltonian provides some insights of stability of Landau-level quasidegeneracies by perturbing from two otherwise independent orbits.
+Besides being an interesting toy model, this Hamiltonian provides some insights of stability of Landau-level quasidegeneracies by perturbing from two otherwise independent orbits.
 
@@
 Therefore, the central object is
-$\prod_{i=0}^{N-1} \A_{1/N}$. We take $N=2$ as an example. Using the parametrization in Eq. (\ref{eq:paramA1/N}),
-\e{
-\A_{1/N}^2=e^{2i\theta}\matrixtwo{\alpha^2-|\beta|^2}{\beta(\alpha+\alpha^*)}{-\beta^*(\alpha+\alpha^*)}{\alpha^{*2}-|\beta|^2}.
-}
-For $\A_{1/N}^2 \propto I$, the sufficient and necessary condition is $\text{Re}(\alpha)=0,\pm 1$, where tuning $\text{Re}(\alpha)=0$ requires only one parameter while tuning $\text{Re}(\alpha)=\pm 1$ requires three parameters.
-
-For crystallographic spacetime symmetries, $N$ may also equal 3, 4 or 6.
-It is straightforward to prove in a similar manner that in these cases, degeneracies of $\A$ lie at $\text{Re}(\alpha)=\cos(n\pi/N)$, with $n\in\mathbb{Z}$.
-Except for $\text{Re}(\alpha)=\pm 1$, all degeneracy manifolds have codimension 1.
+$\prod_{i=0}^{N-1} \A_{1/N}$. Using the parametrization in Eq. (\ref{eq:paramA1/N}), we diagonalize $A_{1/N}$ as 
+\e{
+A_{1/N} = e^{i\theta}U^{\dagger}\matrixtwo{e^{i\varphi}}{0}{0}{e^{-i\varphi}}U
+}
+with $\cos(\phi)=\text{Re}(\alpha)$.
+The sufficient and necessary condition for $A_{1/N}\propto I$ is $\text{Re}(\alpha)=\cos(n\pi/N)$, with $n\in\mathbb{Z}$.
+Tuning $\text{Re}(\alpha)=\cos(n\pi/N)$ requires only one parameter, except for $n=0$ and $n=N$, where three parameters are required.
+
 In the Sec.
 \ref{sec:llquasideg}, we construct $\mathfrak{c}_N$ models by perturbing from $\mathfrak{c}_\infty$ Rashba model and by coupling two otherwise independent orbits by magnetic breakdown.
-In both constructions, $\A_{1/N}$ can be written in some gauge choice as
-\e{
-	\A_{1/N}=e^{i\theta}\matrixtwo{e^{i\lambda}}{0}{0}{e^{-i\lambda}}
-}
-before perturbation is turned on.
-$\lambda$ evolves monotonically with respect to $B$ and sweeps through $n\pi/N$ where degeneracies of $\A$ are expected.
-$e^{i\lambda}$ hits $\pm 1$ once in every $N$ degeneracies and therefore the other $n-1$ degenerates are stable, i.e., have codimension 1.
+In both constructions, $\varphi$ evolves monotonically with respect to $B$ before perturbation are turned on.
+$\varphi$ sweeps through $n\pi/N$ where degeneracies of $\A$ are expected.
+$e^{i\varphi}$ hits $\pm 1$ once in every $N$ degeneracies and therefore the other $n-1$ degenerates are stable, i.e., have codimension 1.
 

### 2018-09-16 paper.tex
Updates from ShareLaTeX

@@
 }
-with $\cos(\phi)=\text{Re}(\alpha)$.
-The sufficient and necessary condition for $A_{1/N}\propto I$ is $\text{Re}(\alpha)=\cos(n\pi/N)$, with $n\in\mathbb{Z}$.
+with $\cos(\varphi)=\text{Re}(\alpha)$.
+The sufficient and necessary condition for $A_{1/N}^N \propto I$ is $\text{Re}(\alpha)=\cos(n\pi/N)$, with $n\in\mathbb{Z}$.
 Tuning $\text{Re}(\alpha)=\cos(n\pi/N)$ requires only one parameter, except for $n=0$ and $n=N$, where three parameters are required.
@@
 For symmetry operations still respecting $L=N$, the codimension calculation is similar to what is done in class II-A-1.
-The only example of $L\ne N$ is $T\mathfrak{c}_{6z,n\boldsymbol{c}/6}$ ($n\in{0,1,2,3,4,5}$), where $L=3$ and $N=6$.
+The only example of $L\ne N$ is $T\mathfrak{c}_{6z,n\boldsymbol{c}/6}$ ($n\in\{0,1,2,3,4,5\}$), where $L=3$ and $N=6$.
 We write $g=T\mathfrak{c}_{6z,n\boldsymbol{c}/6}$ and $h=g^3$.

### 2018-09-19 paper.tex
Updates from ShareLaTeX

@@
 In the  energy basis of the Rashba Hamiltonian $H_R$ [cf.\ \q{eq:Rashba-Hamiltonian}],
-\e{\calh(\bk)=-\alpha k\tau_z{+}\f{g_s}{2}\mu_{\sma{B}}B\tau_x \red{-} \f{eB\hbar}{2m} (\tau_x-I) \epsilon_{\alpha\beta} k_{\red{\alpha}}\nabla_{\red{\beta}}\theta,\la{rashbaeffham}}
+\e{\calh(\bk)=-\alpha k\tau_z{+}\f{g_s}{2}\mu_{\sma{B}}B\tau_x {-} \f{eB\hbar}{2m} (\tau_x-I) \epsilon_{\alpha\beta} k_{\alpha}\nabla_{\beta}\theta,\la{rashbaeffham}}
 where $\tau_i$ are a new set of Pauli matrices with $\tau_z{=}{+} 1$ and ${-}1$ corresponding to the outer and inner orbits, respectively.
@@
 Parameters for (b): $\alpha=0.05$(eV$\cdot$\AA), $m=0.01$($\hbar^2$/eV$\cdot$\AA$^2$), $\beta=0.02~(0.04)$(eV$\cdot$\AA) for left (right) panels.
-$B$ is measured from 2.9 and 1.0T respectively and is in unit $10^{-2}$T.
 (c) For various spin-orbit parameters $(\alpha,\beta)$ of the Rashba-Dresselhaus model and various field strength (satisfying $l^2S(E)\gg 1$), we plot  $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that lies closest to energy $E=0.4eV$, where $\epsilon_\text{rule}$ is determined by Eq.
@@
 Parameters for (b): $m$: 0.02$\hbar^2$/eV$\cdot$\AA$^2$, $\alpha$: 0.05eV$\cdot$\AA, $Z_\parallel$: 0.001eV.
-(c)\textbf{ Can we add axes E vs kx vs ky for main figure, and another set of axes kx vs ky for inset?} A sketch of cyclotron orbits of Rashba Hamiltonian with in-plane magnetic field.
+(c) A sketch of cyclotron orbits of Rashba Hamiltonian with in-plane magnetic field.
 (d) For various configurations ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in left panel $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that is closest to $\epsilon_0$ in Eq.
@@
 In the canonical parametrization of $\text{SU}(2)$ over the three-sphere $S^3$:
-\e{{\cal \bar{A}}{=}\matrixtwo{R_1{+}iR_2}{R_3{+}iR_4}{{-}R_3{+}iR_4}{R_1{-}iR_2},\;\; \sum_{j=1}^4R_j^2{=}1,\;\; R_j\in \mathbb{R},  \la{s3}}
-${\cal \bar{A}}{=}{\pm}I$ lie on distinct points of $S^3$, and are attainable by tuning three real parameters: $R_3{=}R_4{=}0$, and the phase of $R_1{+}iR_2$ must equal $0$ or $\pi$.
-The conclusion that three parameters need be tuned remains valid for any  non-singular\footnote{By `non-singular parametrization', we mean a set of parameters related to those in \q{s3} by a non-singular coordinate transformation.} parametrization of SU$(2)$.
+\e{{\cal \bar{A}}{=}\matrixtwo{r_1{+}ir_2}{r_3{+}ir_4}{{-}r_3{+}ir_4}{r_1{-}ir_2},\;\; \sum_{j=1}^4r_j^2{=}1,\;\; r_j\in \mathbb{R},  \la{s3}}
+${\cal \bar{A}}{=}{\pm}I$ lie on distinct points of $S^3$, and are attainable by tuning three real parameters: $r_3{=}r_4{=}0$, and the phase of $r_1{+}ir_2$ must equal $0$ or $\pi$.
+The conclusion that three parameters need be tuned remains valid for any  non-singular parametrization of SU$(2)$.
 
 %If special unitaries were uniformly distributed over $S^3$, then encountering a spectral degeneracy for a randomly-selected special unitary would be an exceedingly rare event -- three parameters need be tuned to find either pole on $S^3$,  i.e., the codimension of degeneracy manifold is three.
-If only one  or two  parameters (in $\{R_1,\ldots,R_4\}$)  can be tuned, then in general we should not expect a degeneracy.
-
- To generalize the above discussion, let us parametrize ${\cal \bar{A}}$ by $d$ independent real numbers  $\{R_1,\ldots,R_{d}\}{:}{=}\bR $;  ${\cal \bar{A}}(\bR){=}{\pm}I$ defines a set of manifolds in $\bR$-space which we refer to as degeneracy manifolds; in the above example, these manifolds comprise two points on $S^3$.
+If only one  or two  parameters (in $\{r_1,\ldots,r_4\}$)  can be tuned, then in general we should not expect a degeneracy.
+
+ To generalize the above discussion, let us parametrize ${\cal \bar{A}}$ by $d$ independent real numbers  $\{r_1,\ldots,r_{d}\}{:}{=}\br $;  ${\cal \bar{A}}(\br){=}{\pm}I$ defines a set of submanifolds in $\br$-space which we refer to as degeneracy manifolds; in the above example, these manifolds comprise two points on $S^3$.
 The codimension of the degeneracy manifold  is defined as $d$ minus the dimension of said manifold; alternatively stated, the codimension is the number of linearly-independent parameters needed to fine-tune a degeneracy.
@@
 
-It is well-known that symmetry may reduce codimension.[wigner,von neumann] The conceptually-simplest example is the approximate symmetry of band conservation, which exists in the adiabatic regime [cf.\ \s{sec:qtznrules}].
-Recall from \q{phaseindependentorbit} that  $\cala$ becomes diagonal ($R_3{=}R_4{=}0$) in the basis of energy bands,
-with phase[$R_1{\pm}iR_2]{=}{\pm} l^2\delta S/2$ plus field-independent corrections. Since this  phase alone  can be  tuned to attain $\cala{=}{\pm}I$, the codimension is unity.
+It is well-known that symmetry may reduce the codimension of Hamiltonians, e.g., an antiunitary symmetry may restrict complex Hamiltonians to real Hamiltonians, thus reducing codimension from three to two.[wigner,von neumann] In our context, an analog would be the symmetry of band conservation in the adiabatic regime [cf.\ \s{sec:qtznrules}], which restricts $\cala$ to have diagonal form  ($r_3{=}r_4{=}0$) in the basis of energy bands [cf.\ \q{phaseindependentorbit}].
+The phase of $r_1{\pm}ir_2$ equals ${\pm} l^2\delta S/2$ plus field-independent corrections.
+Since this  phase alone  can be  tuned to attain $\cala{=}{\pm}I$, the codimension is unity.
 As a function of $l^2$, we deduce that Landau-level quasi-crossings occur  with a periodicity of $2\pi/\delta S$.
@@
 
-\subsection{Unit codimension for the Rashba 2DEG}\la{sec:singleparameterrashba}
-
-To exemplify the role of rotational symmetry in reducing codimension,
-we return to the Rashba model [cf.\ \q{eq:Rashba-Hamiltonian}] absent Dresselhaus spin-orbit coupling and in-plane Zeeman field.
+\subsection{Codimension reduction for the Rashba 2DEG}\la{sec:singleparameterrashba}
+
+In this and the subsequent section [\s{sec:rotsymmbreakdown}], we will demonstrate how rotational symmetry reduces codimension in the Landau-level problem.
+Before delving into this, it is instructive to consider the conceptually-simplest analog in differential geometry: if we parametrize the 2D plane by Cartesian coordinates $(x,y){\in}\R^2$, it is apparent that two parameters must be tuned to arrive at the origin.
+If however the origin is the center of a rotation symmetry, we may instead utilize polar coordinates and tune a single parameter (the radial coordinate) to arrive at $x{=}y{=}0$.
+We see that rotational symmetry reduces the codimension of the origin from two to one.
+Here, and in the  Landau-level problem, we define codimension with respect to a \textit{symmetrically-chosen coordinates} (if symmetry exists).
+We do not require that the symmetric coordinates is globally defined, e.g., polar coordinates is singular at $x{=}y{=}0$.
+
+\subsubsection{With continuous rotational symmetry}\la{sec:ctsrot}
+
+%To exemplify the role of rotational symmetry in reducing codimension, we return to the Rashba model [cf.\ \q{eq:Rashba-Hamiltonian}] absent Dresselhaus spin-orbit coupling and in-plane Zeeman field.
 Owing to a continuous rotational symmetry (denoted $\mathfrak{c}_{\infty}$), $\calh(\bk)$ is a constant along the circular zeroth-order orbit [cf.\ \q{rashbaeffham}], and therefore the propagator simplifies to $\A{=}$exp$[{-}i\calh T_c/\hbar]$.
 The latter is expressible in the exponential form:
-\e{\A =e^{-i2\pi(r_1\tau_x{+}r_2\tau_z)}, \;\;(r_1,r_2){=}\bigg(\f{g_{\sma{\text{eff}}}}{4}-\f1{2},\f1{2}-\f{\alpha k_{{E}}}{\var_c}\bigg).\notag} 
-All degeneracies occur along circles of radius $\sqrt{r_1^2+r_2^2}{=}{j}/2$, with ${j}$ a nonnegative even (resp.\ positive odd) integer for  $\A{=}I$ (resp.\ $\A{=}{-}I$).
+%\e{\A =e^{-i2\pi(r_1\tau_1{+}r_3\tau_3)}, \;\;(r_1,r_3){=}\bigg(\f{g_{\sma{\text{eff}}}}{4}-\f1{2},\f1{2}-\f{\alpha k_{{E}}}{\var_c}\bigg).\notag} 
+%All degeneracies occur along circles of radius $\sqrt{r_1^2+r_3^2}{=}{j}/2$, with ${j}$ a nonnegative, even (resp.\ positive, odd) integer for  $\A{=}I$ (resp.\ $\A{=}{-}I$).
 In this exactly-soluble model [cf.\ \q{eq:Rashba-exact}], all  degeneracies (${j} {\ge} 0$) of $\A$ correspond to exact Landau-level degeneracies, rather than the near degeneracies described by \qq{llquasideg}{llquasidegB}.
 
-That the ${j}{=}0$ manifold has codimension two can be understood from an elementary result in quantum mechanics: taking $\alpha{=}0$ \textit{and} $m{=}m_0$, we recover the Zeeman-split Landau levels of a free electron gas without spin-orbit coupling; all levels (except the lowest) are spin-degenerate owing to the equality of the Zeeman and cyclotron energies.[LandauLifshitzstatphysI]   All other manifolds ($j{>}0$) have unit codimension, and can be tuned by varying $B$ alone (with fixed $g_{\sma{\text{eff}}}$); these manifolds are analogous to line nodes (of Hamiltonian degeneracies) in 2D $\bk$-space -- a topic of recent interest.[citations]
+%That the ${j}{=}0$ manifold has codimension two can be understood from an elementary result in quantum mechanics: taking $\alpha{=}0$ \textit{and} $m{=}m_0$, we recover the Zeeman-split Landau levels of a free electron gas without spin-orbit coupling; all levels (except the lowest) are spin-degenerate owing to the equality of the Zeeman and cyclotron energies.[LandauLifshitzstatphysI]   All other manifolds ($j{>}0$) have unit codimension, and can be reached by varying $B$ alone (with fixed $g_{\sma{\text{eff}}}$).
+
+To understand why rotational symmetry reduces codimension in the Landau-level problem, we return to the Rashba model [cf.
+\ \q{eq:Rashba-Hamiltonian}] absent Dresselhaus spin-orbit coupling and in-plane Zeeman field.
+This model has a continuous rotational symmetry (denoted $\mathfrak{c}_{\infty}$), which manifests as the constancy of $\calh(\bk){:}{=}\sum_{j=1}^3r_j\tau_j$ over the circular zeroth-order orbit [cf.\ \q{rashbaeffham}]; here, $\br{=}(r_1,r_2,r_3)$ is a real three-vector and $\{\tau_j\}$ a set of Pauli matrices.
+Consequently, the propagator  simplifies to  the exponential form:
+\e{\A{=}e^{-i2\pi\sum_{j}r_j\tau_j}, \;\;(r_1,r_3){=}\bigg(\f{g_{\sma{\ext{eff}}}}{4}{-}\f1{2},\f1{2}{-}\f{\alpha k_{\sma{E}}}{\var_c}\bigg).\la{expform}} 
+$r_2{=}0$ in the Rashba model, but nonzero $r_2$ corresponds to a symmetry-allowed deformation that we allow for greater generality -- any $SU(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}]  for some (possibly non-unique) $\br$, which are the symmetric  coordinates.
+
+%\textbf{[perhaps a footnote explaining this is a non-singular parametrization if no symmetry is imposed]}
+
+All degeneracies of $\A$ occur on spheres in $\br$-space with radii equal to an integer ($j$)  multiple of $1/2$;  ${j}$ equals a nonnegative, even (resp.\ positive, odd) integer for  $\A{=}I$ (resp.\ $\A{=}{-}I$).
+The zero-radius sphere (i.e., a point) has codimension three, as would be expected if symmetry were absent.
+This point degeneracy can be understood from an elementary result in quantum mechanics: taking $\alpha{=}r_2{=}0$ \textit{and} $m{=}m_0$, we recover the Zeeman-split Landau levels of a free electron gas without spin-orbit coupling; all levels (except the lowest) are spin-degenerate owing to the equality of the Zeeman and cyclotron energies.[LandauLifshitzstatphysI]
+
+All other spheres are unit-codimensional surfaces (known as hypersurfaces), and can be reached by varying $B$ alone.
+Equivalently stated, at fixed energy there exists a series of Landau-level quasi-crossings as a function of $B$.
+The stability of hypersurfaces rely on  $\mathfrak{c}_{\infty}$ symmetry.
+Moreover, the hypersurfaces separate $\br$-space into infinitely-many, distinct connected components, i.e., the zeroth homotopy group $\pi_0$ comprises an infinite set.
+Each hypersurface may thus be viewed as a symmetry-protected, topological defect, which separates domains in $\br$-space where Landau levels are non-quasidegenerate.
+
+This discussion is reminiscent of topological (semi)metals which host Dirac-Weyl points and/or line nodes (of Bloch-Hamiltonian degeneracies).
+Weyl points in 3D $\bk$-space have codimension three and do not require any crystallographic point-group symmetry for their stability.
+Just like Weyl points, the point degeneracy of $\A$ is associated with a nontrivial Chern number (defined as an integral of the Berry curvature\footnote{The curvature is defined with respect to a line bundle formed from the nondegenerate eigenvector of $\cala$.} over a Gaussian surface surrounding the point).
+On the other hand,  both Dirac points (in 2D $\bk$-space, e.g., graphene) and  line nodes (in 3D $\bk$-space) have codimension two, hence their existence relies on point-group symmetries.
 
@@
 \includegraphics[width=1.0\columnwidth]{dgn.png}
-\caption{Degenerate manifold of Rashba-Dresselhaus model.
-(a) degeneracy manifold of $\A=-I$; (b) degeneracy manifold of $\A=I$.
-Units: $\alpha l^2$($400$eV$\cdot$\AA$^3$), $\beta$($400$eV$\cdot$\AA$^3$), $g_s'$(10).
-Parameters are $m=0.01\hbar^2$/(eV$\cdot$\AA$^2$) and $E=0.4$eV.
-\red{[For 3D pictures, I always put units in caption since there's no room for them in the pictures.]}\label{fig:dgn}}
+\caption{Degeneracy manifolds of the Rashba-Dresselhaus model, with units: $\alpha l^2$($400$eV$\cdot$\AA$^3$), $\beta$($400$eV$\cdot$\AA$^3$), $g_{\sma{\text{eff}}}$(10), and parameters: $m=0.01\hbar^2$/(eV$\cdot$\AA$^2$) and $E=0.4$eV.
+(a) illustrates the degeneracy manifold of $\A=-I$, which lie confined to  the $\alpha{=}0$ and $\beta{=}0$ planes.
+Each $\mathfrak{c}_{\infty}$-symmetric plane contains an infinite set of concentric, circular line degeneracies.
+Every circle (except for the smallest in either plane)  intersects two other circles in an orthogonal plane, such that the entire line node is path-connected.
+(b) The degeneracy manifold of $\A{=}I$ is a path-connected hypersurface.
+\label{fig:dgn}}
 \end{figure}
 
-The Rashba model suffers from an oversimplification -- continuous rotational symmetry is not a symmetry of solids.
-That is to say, it does not belong in any crystallographic space group.
+\subsubsection{With discrete rotational symmetry}\la{sec:disrot}
+
+The Rashba model suffers from an oversimplification -- continuous rotational symmetry is not a symmetry in any crystallographic space group.
 It is possible for $\mathfrak{c}_{\infty}$-symmetric $\bk{\cdot}\bp$ models to approximate Bloch Hamiltonians (defined over the Brillouin torus) with a discrete, order-$N$ rotational symmetry (denoted $\mathfrak{c}_N$).
-To what extent are degeneracies of $\A$ (for $\mathfrak{c}_{\infty}$-symmetric systems) robust when $\mathfrak{c}_{\infty}$ is perturbatively reduced to $\mathfrak{c}_N$?
-For each of $N{=}2,3,4$ and $6$ (the allowed values in space groups), we find that $N{-}1$ out of every $N$ degeneracies (of $\A$) are robust, as proven in App.
+How robust are the above-mentioned Landau-level quasi-crossings  (over the $B$ axis) when $\mathfrak{c}_{\infty}$ symmetry is perturbatively reduced to $\mathfrak{c}_N$?
+For any  integer $N{\geq}2$, we find that $N{-}1$ of every $N$ quasi-crossings  are perturbatively stable, as proven in App.
 \ref{app:codimension}.
 
-For illustration, let us reduce $\mathfrak{c}_{\infty}$ symmetry to  $\mathfrak{c}_2$  by adding the Dresselhaus spin-orbit term ($\propto \beta$) to the Rashba model [cf.\ \q{hamRD}].
-Since $\A$ depends on $\alpha,\beta,l$ only through $\alpha l^2$ and $\beta l^2$, we consider the three-dimensional parameter space $(\alpha l^2,\beta l^2,g_{\sma{\text{eff}}})\in \mathbb{R}^3$.
-If a  line node (in the $\beta{=}0$ plane) were perturbatively stable to finite $\beta$, then it would be embedded in a two-dimensional degeneracy hypersurface of $\mathbb{R}^3$; if the planar line node were unstable, this embedding does not happen, i.e., the planar line node is simply a line node in $\mathbb{R}^3$.
+For illustration, let us reduce $\mathfrak{c}_{\infty}$ symmetry to  $\mathfrak{c}_2$  by adding the Dresselhaus spin-orbit term (${\propto} \beta$) to the Rashba model [cf.\ \q{hamRD}].
+Since $\A$ depends on $\alpha,\beta,l$ only through $\alpha l^2$ and $\beta l^2$, let us consider the three-dimensional parameter space $(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_{\sma{\text{eff}}}){\in} \mathbb{R}^3$.
+$\A{=}{\pm} I$ determines a set of concentric circles in the $\beta{=}0$ plane, as per the $\mathfrak{c}_{\infty}$-symmetric case study in \s{sec:ctsrot}.
+Moving off this plane, we find that $\A{=}I$ is satisfied in a  neighborhood of $\beta{=}0$, i.e., $\A{=}I$ defines a hypersurface in $\mathbb{R}^3$ that is illustrated in \fig{fig:dgn}(b).
+On the other hand, $\A{=}{-}I$ is not satisfied in the neighborhood of $\beta{=}0$, hence the circles associated to $\A{=}{-}I$ remain isolated as line nodes, as illustrated in \fig{fig:dgn}(a).
+To recapitulate, we have found that one of every two Landau-level crossings (those labelled by odd $j$) destabilize due to the symmetry reduction.
+\textbf{[Bonus content:consider the Berry phase of the eigenstate of A.
+Is it quantized for a symmetrically chosen loop in r space?]}
+%If a  line node (in the $\beta{=}0$ plane) were perturbatively stable to finite $\beta$, then it would be embedded in a two-dimensional degeneracy hypersurface of $\mathbb{R}^3$; if the planar line node were unstable, this embedding does not happen, i.e., the planar line node is simply a line node in $\mathbb{R}^3$.
 Our numerical study shows that half the planar line nodes (corresponding to $\A{=}I$) are stable, while the other half ($\A{=}{-}I$) destabilizes.
@@
 
-To understand this pattern of stabilities, consider  the effective Hamiltonian $\calh$ in momentum independent basis (rather than spin-split basis used before)
-\e{\calh=\alpha (k_{x}\sigma_{y}{-}k_{y}\sigma_{x})+\beta (k_{x}\sigma_{x}{-}k_{y}\sigma_{y})-\tf{g_s}{2}\mu_{B}B\sigma_z;}
-with the Pauli matrices corresponding to spin operators. The two-fold rotational symmetry 
+To demonstrate how the $\A{=}I$ hypersurface derives from $\mathfrak{c}_2$ symmetry, consider  the effective Hamiltonian $\calh$ 
+\e{\calh=\alpha (k_{x}\sigma_{y}{-}k_{y}\sigma_{x})+\beta (k_{x}\sigma_{x}{-}k_{y}\sigma_{y})-\tf{g_s}{2}\mu_{B}B\sigma_z,}
+in a momentum-independent basis where the Pauli matrices correspond to spin operators. The two-fold rotational symmetry 
 \e{\calh(\bk)=\sigma_z\calh(-\bk)\sigma_z, \;\: \bk(t)=-\bk\big(t+\tf{T_c}{2}\big)\in \frako_0,}
@@
 \e{
-{\A}={\cal \bar{A}}=\matrixtwo{1{-}2R_2(R_2{-}iR_1)}{2iR_2(R_3{+}iR_4)}{{-}2iR_2(R_3{-}iR_4)}{1{-}2R_2(R_2{+}iR_1)} \label{proprashba}
-}
-with $\sum_{j=1}^4R_j^2{=}1$.
-We deduce from \q{proprashba} that $R_2{=}0$ is a necessary and sufficient condition for ${\cal \bar{A}}{=}I$.
-The corresponding degeneracy manifold is therefore a  unit-codimensional hypersurface which includes the free-electron limit: $\bR{=}(1,0,0,0)$.
-\red{[Discussion: I really hate introducing new symbols.]} \fig{fig:dgn}(b) illustrates the same hypersurface plotted with a different choice of coordinates: $(\alpha l^2,\beta l^2,g_s')$.
-On the other hand, ${\cal \bar{A}}{=}{-}I$ occurs if and only if $\bR{=}(0,1,0,0)$ -- a point in $\bR$-space.
-If $C_2$ were the only symmetry, then three parameters would be needed to tune ${\cal \bar{A}}{=}{-}I$.
+{\A}={\cal \bar{A}}=\matrixtwo{1{-}2r_2(r_2{-}ir_1)}{2ir_2(r_3{+}ir_4)}{{-}2ir_2(r_3{-}ir_4)}{1{-}2r_2(r_2{+}ir_1)} \label{proprashba}
+}
+with $\sum_{j=1}^4r_j^2{=}1$.
+It follows that $r_2{=}0$ is a necessary and sufficient condition for ${\cal \bar{A}}{=}I$.
+The corresponding degeneracy manifold is a  path-connected hypersurface which includes the free-electron limit: $\br{=}(r_1,r_2,r_3){=}(1,0,0)$.
+\fig{fig:dgn}(b) illustrates the same hypersurface in distinct coordinates: $(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_{\sma{\text{eff}}})$.
+On the other hand, ${\cal \bar{A}}{=}{-}I$ occurs if and only if $\br{=}(0,1,0)$.
+This point is mapped to a path-connected line node confined to the  $\alpha{=}0$ and $\beta{=}0$ planes [cf.\ \fig{fig:dgn}(a)]; the difference in codimension originates from the  $\mathfrak{c}_{\infty}$ symmetry within these two planes [cf.\ \s{sec:ctsrot}], which was not accounted for in the $\mathfrak{c}_2$-symmetric analysis of \q{proprashba}.
+
+%If $C_2$ were the only symmetry, then three parameters would be needed to tune ${\cal \bar{A}}{=}{-}I$.
 Generally, additional symmetry further constrains $\bR$, which may effectively reduce the number of tuning parameters.
-This explains why the ${\cal \bar{A}}{=}{-}I$ manifolds, as plotted in Fig.
-\fig{fig:dgn}(a)], are line nodes instead of point nodes: these line nodes lie in either the $\alpha{=}0$ or the $\beta{=}0$ plane, both of which are $\mathfrak{c}_{\infty}$-symmetric.\footnote{To complete the explanation, \textbf{speculative:} the space of $C_{\infty}$-symmetric unitaries lie on lines in $\bR$-space that intersect $\bR{=}(0,1,0,0)$ [the point node].
+This explains why the ${\cal \bar{A}}{=}{-}I$ manifolds, as plotted in \fig{fig:dgn}(a)], are line nodes instead of point nodes: these line nodes lie in either the $\alpha{=}0$ or the $\beta{=}0$ plane, both of which are $\mathfrak{c}_{\infty}$-symmetric.\footnote{To complete the explanation, \textbf{speculative:} the space of $C_{\infty}$-symmetric unitaries lie on lines in $\bR$-space that intersect $\bR{=}(0,1,0,0)$ [the point node].
 A singular coordinate transformation to $\br$-space maps these $C_{inf}$-symmetric lines to $\mathfrak{c}_{inf}$-symmetric planes, and the point node to a line node.}
@@
 For example if $g$ is an $N$-fold rotation,  the phase factor is $+1$ (resp.\ $-1$) for an integer-spin (resp.\ half-integer-spin) representation.
-Therefore, the central object is
+For the purpose of determining degeneracies, we may focus on
 $\prod_{i=0}^{N-1} \A_{1/N}$. Using the parametrization in Eq. (\ref{eq:paramA1/N}), we diagonalize $A_{1/N}$ as 
@@
 Tuning $\text{Re}(\alpha)=\cos(n\pi/N)$ requires only one parameter, except for $n=0$ and $n=N$, where three parameters are required.
+\textbf{A few more details in above proof would be helpful}
 

### 2018-09-19 paper.tex
Updates from ShareLaTeX

@@
 \begin{figure}
-\includegraphics[width=0.8\columnwidth]{blochsphere.png}
-\caption{Energy dependence of the Berry phase for inner [(a)] and outer [(b)] orbit.
-The Berry phase equals half the solid angle enclosed by the corresponding loop on the Bloch sphere \textbf{[loop must be explained, right-hand rule explained]}.
-The directions of the loops are indicated by black arrows and the black arrow outside of the sphere indicates increasing energy, where green lines correspond to $\epsilon_0$ in Eq.
-(\ref{whereisdiracpoint}) \textbf{This figure is problematic because only the red loop is shown, while for the other loops the audience is left guessing.
-Perhaps it is best to separate one bloch sphere into three smaller spheres, such that each smaller sphere has only one loop.
-We might also show the analog of Fig 3a for energy above and below Dirac point.}.\label{fig:blochsphere}}
+\includegraphics[width=1.0\columnwidth]{blochsphere.png}
+\caption{Energy dependence of the Berry phase for inner (upper panel) and outer (lower panel) orbits.
+For two band models, the Berry phase equals half the solid angle enclosed by the loop swept by spin orbit field on the unit sphere.
+The solid angles are indicated by blue outlines and the energy is measured from $\epsilon_0$ in Eq.
+(\ref{whereisdiracpoint}).\label{fig:blochsphere}}
 \end{figure}

### 2018-09-19 paper.tex
progress

@@
 $(l^2\delta S)^{-1}$ is a measure of the field-induced hybridization of the quasidegenerate orbits, and shall be called the hybridization parameter. 
-In the regime that $l^2\delta S$ is much greater than the Zeeman interaction \red{[Zeeman interaction?
-Why not just 1.]}, we expect that the Onsager-Lifshitz quantization rules apply independently to the two concentric (but decoupled) orbits.
+In the regime that $l^2\delta S$ is much greater than the Zeeman interaction, we expect that the Onsager-Lifshitz quantization rules apply independently to the two concentric (but decoupled) orbits.
 In the opposite regime, we should recover the known quantization rule for degenerate orbits.
@@
 Let us apply a magnetic field, and first consider the spin-degenerate Landau levels obtained by neglecting both $\delta H$ and the Zeeman splitting.
-In the  semiclassical description,  we are interested in  field-induced dynamics within a low-energy degenerate band of $\hat{H}_0$ with  dispersion $\var(\bk)$, e.g., $\var(\bk){=}\hbar^2 k^2/2m{+}\order(k^4)$ \red{[What is contained in this $\order(k^4)$?]}in the Rashba model.
+In the  semiclassical description,  we are interested in  field-induced dynamics within a low-energy degenerate band of $\hat{H}_0$ with  dispersion $\var(\bk)$, e.g., $\var(\bk){=}\hbar^2 k^2/2m{+}\order(k^4)$ in the Rashba model.
 Landau quantization is well-known to derive from the Peierls substitution $\var(\bk){\rightarrow}\var(\bK)$, [Peierls] with the kinematic quasimomentum operator   $\boldsymbol{K}{:}{=}\boldsymbol{k}{+}(e/\hbar) \boldsymbol{A}(i\nabla_{\boldsymbol{k}})$ and $\boldsymbol{A}(\br)$ being the electromagnetic vector potential.
@@
 This requirement is equivalent to $\sqrt{0.8m}\alpha/\hbar<Z<\sqrt{2m}\alpha/\hbar$, corresponding to the boundaries of the plots in (d).} Parameters for (d): $m$: 0.01$\hbar^2$/eV$\cdot$\AA$^2$, $l=100$\AA.
-\textbf{please choose formatting such that footnote is at the back} \label{fig:RZ}}
+\textbf{[please choose formatting such that footnote is at the back]}\red{[Sorry, I haven't figured out how to do this.
+I will do this later.]} \label{fig:RZ}}
 \end{figure}
@@
 In the absence of the out-of-plane Zeeman coupling ($Z_\perp{=}0$), $\bar{\mu}$ would vanish at the energy of the II-Dirac point -- leading to unit-probability Klein tunneling, as was first proposed by [Obrien] in a different model realization of the II-Dirac point.
-However, with a proper account of $Z_\perp$, we find instead that $\bar{\mu}$ has a nonvanishing minimum: $\bar{\mu}_{\sma{\text{min}}}{:}{=} (m/m_0)(Z_\perp/2\alpha k_{E})$, which is a product of the dimensionless effective mass and the ratio of the out-of-plane Zeeman splitting over the spin-orbit splitting.
+However, with a proper account of $Z_\perp$, we find instead that $\bar{\mu}$ has a nonvanishing minimum: $\bar{\mu}_{\sma{\text{min}}}{:}{=} ( m/m_0)(Z_\perp/4\alpha k_{E})$, which is a product of the dimensionless effective mass and the ratio of the out-of-plane Zeeman splitting over the spin-orbit splitting.
 This minimum is practically negligible for  semiconductor heterostructures with $m{\ll}m_0$, but may be relevant in heavy-fermion systems.
@@
 which is a connection formula that matches the two-component semiclassical (WKB) wavefunction across the Dirac point.
-$\mathbb{S}$ in \q{scattmat} has been expressed in the basis of spin-split energy bands, so  the diagonal elements of $\mathbb{S}$ are amplitudes for intraband (adiabatic) transmission; the phase of this amplitude is $\barphi{:}{=}\barmu{-}\barmu\ln\barmu{+}\text{arg}[\Gamma(i\barmu)]{+}\pi/4$ with $\Gamma$ the gamma function.
+$\mathbb{S}$ in \q{scattmat} has been expressed in the basis of Zeeman coupling corrected energy bands, i.e., eigenvector of Eq.
+\ref{effhamIIDirac}, so the diagonal elements of $\mathbb{S}$ are amplitudes for intraband (adiabatic) transmission; the phase of this amplitude is $\barphi{:}{=}\barmu{-}\barmu\ln\barmu{+}\text{arg}[\Gamma(i\barmu)]{+}\pi/4$ with $\Gamma$ the gamma function.
 
@@
 \e{{\A}= \matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}} \diagmatrix{e^{i\tilde{\lambda}_+}}{e^{i\tilde{\lambda}_-}}. \la{propinplanezeeman}}
-$\tilde{\lambda}_{\pm}$ is generated by $\H_{\pm \pm}$ and has the same form as \q{phaseindependentorbit}, with $B\int_0^{T_c}\calm_{\pm\pm}dt/\hbar$ equal (in this model) to the single-band Berry phase ($\phi_{\pm}^B$) of band $\pm$ on $\frako_0$.
+In the basis of Zeeman coupling corrected energy bands, the band-conserving phases $\tilde{\lambda}_{\pm}$ consist of two parts: dynamical phase $l^2 \delta S$ with $\delta S$ now accounting for both spin-split and Zeeman-split area corrections, and single band Berry phases $\phi^B_\pm$ evaluated on $\frako_0$.
 At energies far above the Dirac point ($|E{-}\epsilon_0|{\gg}|Z_{\perp}|$) where the Zeeman interaction is negligible, both orbits encircle the Dirac point and hence $\phi_{\pm}^B{\approx}{\pm}\pi$; far below the Dirac point, neither orbit encircles the Dirac point, leading to $\phi_{\pm}^B{\approx}0$.
@@
 \includegraphics[width=1.0\columnwidth]{blochsphere.png}
-\caption{Energy dependence of the Berry phase for inner (upper panel) and outer (lower panel) orbits.
-For two band models, the Berry phase equals half the solid angle enclosed by the loop swept by spin orbit field on the unit sphere.
+\caption{Energy dependence of the Berry phases for inner (upper panel) and outer (lower panel) orbits.
+For two band models, the Berry phase equals half the solid angle enclosed by the loop swept by spin-orbit field on the unit sphere.
 The solid angles are indicated by blue outlines and the energy is measured from $\epsilon_0$ in Eq.
@@
 $\Omega_{\pm}$ is the phase acquired by an electron in adiabatically traversing orbit $\pm$; the quantum Maslov correction $\gamma_{\pm}{=}\pi$ for circular orbits.
+Since $\phi^B_\pm$ are evaluated both on $\frako_0$, $\phi^B_-+\phi^B_+=0$ in two band models.
 A quantization rule analogous to \q{coscos} was previously derived by us for a II-Dirac point that intermediates an electron- and hole-like orbit [AALG].
@@
 In the limit $B{\rightarrow}0$ (equivalently, $\bar{\mu}{\rightarrow} \infty$), Landau-Zener tunneling is negligible ($\tau{\rightarrow}1,\bar{\varphi}{\rightarrow}0$), and \q{coscos} simplifies to the Onsager-Lifshitz-Roth rules ($\Omega_{\pm}/2\pi{\in}\Z$) for  two independent orbits.
-This simplification occurs even at the energy of the Dirac point, where  the intraband amplitude $\tau$ has a nonvanishing minimum with respect to energy: $\tau_{\sma{\text{min}}}{\approx}\sqrt{2\pi\bar{\mu}_{\sma{\text{min}}}}$, due to the out-of-plane Zeeman coupling.
 
@@
 To appreciate this, let us analyze the Landau levels (near the Dirac point) perturbatively in the small parameter $\tau$.
-To zeroth order, \q{coscos} reduces to\footnote{Notice that $\phi_+ + \phi_-=0$ since for any two band model, Berry phases of the two bands cancel on the same orbit ($\frako_0$ here).}
+To zeroth order, \q{coscos} reduces to
 \e{2l^2S(E_n^0)+\pi = 2\pi n \rightarrow \{E_n^0(B)\}_{n\in\Z}.\label{trefoillerule}} 
@@
 
-\textbf{[Rest of section needs work]
-} In the regime of quasidegenerate orbits ($\Delta/E{\ll}1$) with intermediate adiabaticity ($\Delta/\epsilon_c{\sim}1$),  our quantization rule \qq{eq:rule}{eq:H1} remains valid but the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}.
+In the regime of quasidegenerate orbits ($\delta S/S \ll 1$) with intermediate adiabaticity ($l^2\delta S\sim 1$),  our quantization rule \qq{eq:rule}{eq:H1} remains valid but the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}.
 We may anyway simulate $\cala$ numerically, and compare the semiclassically-obtained Landau levels with the exact solution of $H_{RZ}(\boldsymbol{K})$ (see Fig.
-\ref{fig:RZ} (c-d)).
+\ref{fig:RZ} (d)).
 This exact solution is obtained by large-scale numerical diagonalization [appendix], since (to our knowledge) there exists no analytic solution for generic values of $\alpha,\zpar$ and $B$.
-\textbf{[Say a few words about the comparison]}
-
-For the special case of $\alpha=0$, the spectra of $H_{RZ}(\boldsymbol{K})$ and  $\mathcal{A}[\mathfrak{o}]$ are both exactly soluble, leading to identical Landau levels with phase offset $\lambda_{\pm}=\pm 2\pi ml^2\sqrt{Z^2+g_s'^2/16m^2l^4}$.\textbf{[Let's be more specific about the form of the spectrum.]}
+Errors of \qq{eq:rule}{eq:H1} in predicting Landau levels are less than 0.3\% of cyclotron energy in Fig.
+\ref{fig:RZ} (d).
+Similar to Rashba-Dresselhaus model, the observed errors are strongly positively related to $l^2\delta S^2/S$.
+
+For the special case of $\alpha=0$, the spectra of $H_{RZ}(\boldsymbol{K})$ and $\mathcal{A}[\mathfrak{o}]$ are both exactly soluble.
+The eigenphases of $\A$ are $\lambda_{\pm}=\pm 2\pi ml^2\sqrt{Z_\parallel^2/\hbar^4+g_\text{eff}^2/16m^2l^4}$.
+Together with Eq.
+(\ref{eq:rule}), $\lambda_\pm$ here generate exact the same Landau level spectrum as $H_{RZ}(\boldsymbol{K})$.
 
@@
 Consequently, the propagator  simplifies to  the exponential form:
-\e{\A{=}e^{-i2\pi\sum_{j}r_j\tau_j}, \;\;(r_1,r_3){=}\bigg(\f{g_{\sma{\ext{eff}}}}{4}{-}\f1{2},\f1{2}{-}\f{\alpha k_{\sma{E}}}{\var_c}\bigg).\la{expform}} 
+\e{\A{=}e^{-i2\pi\sum_{j}r_j\tau_j}, \;\;(r_1,r_3){=}\bigg(\f{g_{\sma{\text{eff}}}}{4}{-}\f1{2},\f1{2}{-}\f{\alpha k_{\sma{E}}}{\var_c}\bigg).\la{expform}} 
 $r_2{=}0$ in the Rashba model, but nonzero $r_2$ corresponds to a symmetry-allowed deformation that we allow for greater generality -- any $SU(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}]  for some (possibly non-unique) $\br$, which are the symmetric  coordinates.

### 2018-09-20 paper.tex
Updates from ShareLaTeX

@@
 $\delta \var$ is the projection of $\delta H$ to the quasidegenerate band associated to $\var(\bk)$, e.g., $\delta \var{=}\alpha(k_x\sigma_y{-}k_y\sigma_x)$ in the Rashba model.
-In the basis of energy-split bands (which we label by ${+}$ and $-$ for bands corresponding to the outer and inner orbit respectively),\footnote{We remark that the quantization rule is invariant under basis transformations within the degenerate band subspace (See App.
-\ref{app:quantizationruleproof}); this may be exploited for efficient numerical computations.} $\delta \var$ is a diagonal matrix whose diagonal entries ($\delta \var_+,\delta \var_-$, corresponding to outer and inner orbit respectively; $\delta \var_+<\delta \var_-$) are related to the hybridization parameter:\footnote{The neglected term on the right-hand side of  \q{spinsplitwkb} is smaller (than the kept term) by a factor $\delta v_{\pm}/v$, which is the relative change in band speed $v=|\boldsymbol{v}|=\hbar^{-1}|\partial \var/\partial \bk|$ induced by the spin-orbit coupling.
+In the basis of energy-split bands (which we label by ${+}$ and $-$ for bands corresponding to the outer and inner orbit respectively), $\delta \var$ is a diagonal matrix whose diagonal entries ($\delta \var_+,\delta \var_-$, corresponding to outer and inner orbit respectively; $\delta \var_+<\delta \var_-$) are related to the hybridization parameter:\footnote{The neglected term on the right-hand side of  \q{spinsplitwkb} is smaller (than the kept term) by a factor $\delta v_{\pm}/v$, which is the relative change in band speed $v=|\boldsymbol{v}|=\hbar^{-1}|\partial \var/\partial \bk|$ induced by the spin-orbit coupling.
 This factor is assumed to be small.
@@
 There is finally a geometric contribution to the Zeeman interaction, which involves the two-by-two non-Abelian Berry connection  as well as the  zeroth-order band velocity:
-\e{\mathfrak{X}_{\beta,mn}{=}i\braket{u_m}{\partial u_n/\partial k_{\beta}},  \;\;v_{\alpha}:= \red{\f{1}{\hbar}}\p{\var}{k_{\alpha}},\la{berryconn}}
+\e{\mathfrak{X}_{\beta,mn}{=}i\braket{u_m}{\partial u_n/\partial k_{\beta}},  \;\;v_{\alpha}:= \f{1}{\hbar}\p{\var}{k_{\alpha}},\la{berryconn}}
 with $\{u_n\}_{n=1}^2$ the periodic component of Bloch functions in the quasidegenerate band. 
@@
 \qq{eq:rule}{berryconn} allow us to determine $\lambda_{1,2}$ to the lowest order  in $1/l^2S$ and $\delta S/S$, and for arbitrary values of $l^2\delta S$ and $|B\calm|/\delta \var_{\pm}$.
+We remark that the quantization rule is invariant under basis transformations within the degenerate band subspace (See App.
+\ref{app:quantizationruleproof}); other basis, such as $\bk$-independent basis where Berry connections are trivial, may be more convenient in many discussions.
 
@@
 where $\tau_i$ are a new set of Pauli matrices with $\tau_z{=}{+} 1$ and ${-}1$ corresponding to the outer and inner orbits, respectively.
-$e^{i\theta_{\bk}}{=}(ik_x{-}k_y)/k$ is the angle of the in-plane spin-orbit field $({-}\alpha k_y,\alpha k_x,0)$, which winds once over $\frako_0$; the spin of our basis vectors likewise winds, in parallel (or anti-parallel) alignment with this field (see Fig.
+$e^{i\theta_{\bk}}{=}(ik_x{-}k_y)/k$ is the angle of the in-plane spin-splitting field $({-}\alpha k_y,\alpha k_x,0)$ of $H_R$, which winds once over $\frako_0$; the spin of our basis vectors likewise winds, in parallel (or anti-parallel) alignment with this field (see Fig.
 (\ref{fig:orbits})(b)).
@@
 \ref{sec:numerical}) and those obtained from the quantization rule.
-The difference in energies  does not exceed $2\%$ of $\var_c$ [cf.\ \fig{fig:RD}(c)] for various choices of the spin-orbit parameters $(\alpha,\beta)$.
-Larger differences are positively correlated with 
+Perfect match between quantization rule and exact diagonalization can be observed in the left panel of \fig{fig:RD}(b) while slight deviations are seen for smaller magnetic field.
+In \fig{fig:RD}(c) we plot the errors in energies for various choices of the spin-orbit parameters $(\alpha,\beta)$, which does not exceed $2\%$ of $\var_c$ in the plot range.
+Larger errors are positively correlated with
 $l^2\delta S^2/S$ (with $\delta S$ depending on both $\alpha$ and $\beta$), as shown in Fig.
@@
 \caption{(a) Trefoille-shaped cyclotron orbit for the Rashba-Zeeman model at the energy of the Dirac point.
-The orbit is drawn over the  {spin-orbit field} ($d_x,d_y$) of the Hamiltonian $H_{RZ}{=}d_0(\bk)I{+}d_x(\bk)\sigma_x{+}d_y(\bk)\sigma_y$, with $d_j$ obtainable from \q{eq:RZ-Hamiltonian}.
+The orbit is drawn over the  spin-splitting field ($d_x,d_y$) of the Hamiltonian $H_{RZ}{=}d_0(\bk)I{+}d_x(\bk)\sigma_x{+}d_y(\bk)\sigma_y$, with $d_j$ obtainable from \q{eq:RZ-Hamiltonian}.
 The wavefunction along the inner (resp.\ outer) component of the trefoille orbit has its pseudospin aligned parallel (resp.\ anti-parallel) to the spin-orbit field.
@@
 Corresponding $l^2 \delta S^2/S$ are plotted in right panel.
-We only plotted in region where $0.4<\epsilon_0<1.0$(eV).\footnote{$l^2S\gg 1$ is assured by requiring $\epsilon_0>0.4$; the reason of choosing $\epsilon_0<1.0$ is Dirac point lying at high energy requires too much harmonics in numerical diagonalization.
-This requirement is equivalent to $\sqrt{0.8m}\alpha/\hbar<Z<\sqrt{2m}\alpha/\hbar$, corresponding to the boundaries of the plots in (d).} Parameters for (d): $m$: 0.01$\hbar^2$/eV$\cdot$\AA$^2$, $l=100$\AA.
-\textbf{[please choose formatting such that footnote is at the back]}\red{[Sorry, I haven't figured out how to do this.
-I will do this later.]} \label{fig:RZ}}
+We only plotted in region where $0.4<\epsilon_0<1.0$(eV).\cite{RZfignote} Parameters for (d): $m$: 0.01$\hbar^2$/eV$\cdot$\AA$^2$, $l=100$\AA.
+\label{fig:RZ}}
 \end{figure}
@@
 This implies that the split orbits do not appreciably hybridize -- except in the vicinity of the II-Dirac point where orbits (nearly) touch.
-Near this II-Dirac point, the dynamics of a two-component wavepacket is described
- by the effective Hamiltonian
+In the constant basis,
+\begin{equation}
+\calh(t)=\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+Z_\parallel\sigma_{y}-Z_\perp\sigma_{z},\label{calHRZ}
+\end{equation}
+where $k_x=-k_F \cos(\omega_c t)$ and $k_y=k_F \sin(\omega_c t)$. Near the II-Dirac point, the dynamics of a two-component wavepacket is described by linearizing $\H$ with respect to $t$
 \e{
@@
 $\bk(t){=}({-}k_E \cos \omega_c^{\sma{\perp}} t, k_E \sin \omega_c^{\sma{\perp}} t ).$ 
-$\calh$ above has been linearized with respect to  $t$, which vanishes in the vicinity of the Dirac point.
 The eigenbasis of $\sigma_x$ corresponds to two diabatic levels with characteristic slope $v_d{:}{=}\alpha k_E\omega^{\sma{\perp}}_c$; near $t{=}0$, the diabatic levels anticross  due to the hybridization terms proportional to $\sigma_{y,z}$.
@@
 which is a connection formula that matches the two-component semiclassical (WKB) wavefunction across the Dirac point.
-$\mathbb{S}$ in \q{scattmat} has been expressed in the basis of Zeeman coupling corrected energy bands, i.e., eigenvector of Eq.
-\ref{effhamIIDirac}, so the diagonal elements of $\mathbb{S}$ are amplitudes for intraband (adiabatic) transmission; the phase of this amplitude is $\barphi{:}{=}\barmu{-}\barmu\ln\barmu{+}\text{arg}[\Gamma(i\barmu)]{+}\pi/4$ with $\Gamma$ the gamma function.
+$\mathbb{S}$ in \q{scattmat} has been expressed in the basis of Zeeman-corrected energy bands, i.e., eigenvectors of Eq.
+(\ref{calHRZ}), so the diagonal elements of $\mathbb{S}$ are amplitudes for intraband (adiabatic) transmission; the phase of this amplitude is $\barphi{:}{=}\barmu{-}\barmu\ln\barmu{+}\text{arg}[\Gamma(i\barmu)]{+}\pi/4$ with $\Gamma$ the gamma function.
 
@@
 \e{{\A}= \matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}} \diagmatrix{e^{i\tilde{\lambda}_+}}{e^{i\tilde{\lambda}_-}}. \la{propinplanezeeman}}
-In the basis of Zeeman coupling corrected energy bands, the band-conserving phases $\tilde{\lambda}_{\pm}$ consist of two parts: dynamical phase $l^2 \delta S$ with $\delta S$ now accounting for both spin-split and Zeeman-split area corrections, and single band Berry phases $\phi^B_\pm$ evaluated on $\frako_0$.
+In the basis of Zeeman-corrected energy bands, the adiabatic phases $\tilde{\lambda}_{\pm}$ consist of two parts: dynamical phase $l^2 \delta S'$ with $\delta S'$ now accounting for both spin-split and Zeeman-split area corrections, and single band Berry phases $\phi^B_\pm$ evaluated on $\frako_0$.
 At energies far above the Dirac point ($|E{-}\epsilon_0|{\gg}|Z_{\perp}|$) where the Zeeman interaction is negligible, both orbits encircle the Dirac point and hence $\phi_{\pm}^B{\approx}{\pm}\pi$; far below the Dirac point, neither orbit encircles the Dirac point, leading to $\phi_{\pm}^B{\approx}0$.
@@
 \caption{Energy dependence of the Berry phases for inner (upper panel) and outer (lower panel) orbits.
-For two band models, the Berry phase equals half the solid angle enclosed by the loop swept by spin-orbit field on the unit sphere.
+For two band models, the Berry phase equals half the solid angle subtended by the loop swept by spin-splitting field ($-\alpha k_y$,$Z_\parallel+\alpha k_x$,$Z_\perp$) of $\H$ in Eq.
+(\ref{calHRZ}) on the unit sphere.
+Notice that Zeeman coupling are included in spin-splitting field here.
+For lower band (outer orbit), the spin splitting field should be inverted to reflect the change in band index.
 The solid angles are indicated by blue outlines and the energy is measured from $\epsilon_0$ in Eq.
@@
 \text{cos}\left[\frac{\Omega_{-}+\Omega_{+}}{2}\right]=\tau\,\text{cos}\left[\frac{\Omega_{-}-\Omega_{+}}{2}+\bar{\varphi}\right], \lin
-\ins{with}\;\Omega_{\pm}=l^2 (S\pm \delta S/2)+\phi_{\pm}^B +\gamma_{\pm}, \la{coscos}
+\ins{with}\;\Omega_{\pm}=l^2 (S\pm \delta S'/2)+\phi_{\pm}^B +\gamma_{\pm}, \la{coscos}
 }
@@
 This exact solution is obtained by large-scale numerical diagonalization [appendix], since (to our knowledge) there exists no analytic solution for generic values of $\alpha,\zpar$ and $B$.
-Errors of \qq{eq:rule}{eq:H1} in predicting Landau levels are less than 0.3\% of cyclotron energy in Fig.
+Errors of \qq{eq:rule}{eq:H1} in predicting Landau levels are less than 0.3\% of cyclotron energy in the parameter range plotted in Fig.
 \ref{fig:RZ} (d).
-Similar to Rashba-Dresselhaus model, the observed errors are strongly positively related to $l^2\delta S^2/S$.
+Similar to Rashba-Dresselhaus model, the observed errors are strongly positively correlated with $l^2\delta S^2/S$.
 

### 2018-09-20 paper.tex
Updates from ShareLaTeX

@@
 \ref{app:quantizationruleproof}.
-$\hat{H}_0$ is commonly exemplified by  the Schr\"odinger Hamiltonian, and $\delta H$ by a non-centrosymmetric spin-orbit interaction; alternatively, $\hat{H}_0$ may be a centrosymmetric Pauli Hamiltonian (with spin-orbit coupling), while $\delta H$ describes a lattice deformation that breaks the spatial-inversion symmetry.
+$\hat{H}_0$ is commonly exemplified by  the Schr\"odinger Hamiltonian, and $\delta \hat{H}$ by a non-centrosymmetric spin-orbit interaction; alternatively, $\hat{H}_0$ may be a centrosymmetric Pauli Hamiltonian (with spin-orbit coupling), while $\delta H$ describes a lattice deformation that breaks the spatial-inversion symmetry.
 
@@
 \end{equation}
-In Fig.
-\ref{fig:RD}(b), a comparison is made between the Landau levels obtained from exact numerical diagonalization of $H_{RD}(\bK)$ (by standard techniques reviewed in App.
+In Fig.\ \ref{fig:RD}(b-d), a comparison is made between the Landau levels obtained from exact numerical diagonalization of $H_{RD}(\bK)$ (by standard techniques reviewed in App.
 \ref{sec:numerical}) and those obtained from the quantization rule.
-Perfect match between quantization rule and exact diagonalization can be observed in the left panel of \fig{fig:RD}(b) while slight deviations are seen for smaller magnetic field.
+The difference in energies tends to increase with smaller field [compare the left and right panels of   \fig{fig:RD}(b)] and shows a strong positive correlation with $l^2\delta S(\alpha,\beta)^2/S$ [compare \fig{fig:RD}(c) with \fig{fig:RD}(d)] for various choices of the spin-orbit parameters $(\alpha,\beta)$.
+This correlation may be anticipated from \q{eq:Rashba-exact}, which analytically demonstrates how terms involving $l^2\delta S^2/S$ modifies the quantization rule in the case where $\beta{=}0$.
+For our chosen parameters,  the difference in energies does not exceed $2\%$ of $\var_c$ as $l^2\delta S^2/S$ varies over $[0,0.75]$.
+
+%Perfect match between quantization rule and exact diagonalization can be observed in the left panel of \fig{fig:RD}(b) while slight deviations are seen for smaller magnetic field.
 In \fig{fig:RD}(c) we plot the errors in energies for various choices of the spin-orbit parameters $(\alpha,\beta)$, which does not exceed $2\%$ of $\var_c$ in the plot range.
 Larger errors are positively correlated with
-$l^2\delta S^2/S$ (with $\delta S$ depending on both $\alpha$ and $\beta$), as shown in Fig.
-\ref{fig:RD}(d); see also \q{eq:Rashba-exact}, which analytically demonstrates how terms involving $l^2\delta S^2/S$ modifies the quantization rule in the case $\beta=0$.
+%$l^2\delta S^2/S$ (with $\delta S$ depending on both $\alpha$ and $\beta$), as shown in Fig.
+\ref{fig:RD}(d); see also \q{eq:Rashba-exact}, which analytically demonstrates how terms involving $l^2\delta S^2/S$ modifies the quantization rule in the case of $\beta=0$.
 
@@
 Our next case study involves orbits that (nearly) touch at a type-II Dirac point -- an asymmetric variant of the conventional Dirac point (as will be introduced below).
-Quantum tunneling localized to a type-II Dirac point  (in short, II-Dirac point) is known to be mathematically equivalent to  Landau-Zener breakdown, with the electric force replaced by the Lorentz force.
-[Blount, Obrien, AALG] First, we will demonstrate how we recover Landau-Zener dynamics in the weak-hybridization regime  of \qq{eq:rule}{eq:H1}.
+Quantum tunneling localized to a type-II Dirac point  (in short, a II-Dirac point) is known to be mathematically equivalent to  Landau-Zener breakdown, with the electric force replaced by the Lorentz force.[Blount, Obrien, AALG] Here, we will demonstrate how  Landau-Zener dynamics emerge from our quantization rule [\qq{eq:rule}{eq:H1}], and explore (for the first time) how these dynamics are modified by the Zeeman effect.
+In particular, we will show that the perfect Klein tunneling predicted by O'Brien et al [OBrien] is never perfect with a proper account of the Zeeman effect.
 
@@
 \e{ 
-H_{RZ}=\f{{\hbar^2}k^{2}}{2m}+\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+\zpar\sigma_{y}, \la{eq:RZ-Hamiltonian}}
+H_{RZ}=\f{{\hbar^2}k^{2}}{2m}+\delta \var; \;\;\;\delta \var=\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+\zpar\sigma_{y}, \la{eq:RZ-Hamiltonian}}
 with $\zpar{:}{=}{g_s}\mu_B B_{\parallel}/2$.
@@
 In addition to the in-plane field, let us also apply an out-of-plane field $B_{\perp}$, with associated magnetic length $\lper{=}\sqrt{\hbar/eB_{\perp}}$, cyclotron energy $\var^{\sma{\perp}}_c{:}{=}\hbar^2/m\lper^2{:}{=}\hbar \omega_c^{\sma{\perp}}{:}{=}h/T_c^{\sma{\perp}}$ and Zeeman coupling to the spin magnetic moment:  $\zper{:}{=}{g_s}\mu_B B_{\perp}/2$.
-It is assumed that $\lper^2S$ is large, where $S$ is the area of the zeroth-order orbit (with effective mass $m$).
-For energies much greater than $m\alpha^2$ and $\zpar$, the quasidegeneracy condition is met: $\delta S{\ll}S$, hence we may apply the quantization rule of \qq{eq:rule}{eq:H1} in the subsequent analysis.
+We shall assume  $1/\lper^2S{\ll}1$, where $S$ is the area of the zeroth-order orbit (with effective mass $m$ and radius $k_E{=}\sqrt{2mE}/\hbar$).
+For energies much greater than $m\alpha^2$ and $\zpar$, the quasidegeneracy condition ($\delta S/S{\ll}1$) is met, where $\delta S$ is the differential area induced by both spin-orbit and in-plane Zeeman couplings [see \fig{fig:RZ}(a)].
+The smallness of $1/\lper^2S$ and $\delta S/S$ (with finite ratio $\lper^2\delta S$) justifies our application of the quantization rule [\qq{eq:rule}{eq:H1}],  with the effective Hamiltonian:
+\begin{equation}
+\calh(t)=\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+Z_\parallel\sigma_{y}-Z_\perp\sigma_{z}.\label{calHRZ}
+\end{equation}
+$t$ here is a time variable which parametrizes the zeroth-order orbit:
+$\bk(t){=}({-}k_E \cos \omega_c^{\sma{\perp}} t, k_E \sin \omega_c^{\sma{\perp}} t )$.
+In the momentum-independent spin basis of \q{calHRZ}, the non-Abelian Berry connection vanishes, hence the generalized Zeeman interaction $B_{\sma{\perp}}\calm$ simply reduces to the Zeeman interaction with the spin  moment: $Z_\perp\sigma_{z}$.
 
@@
 To investigate this failure of adiabaticity, let us study the Landau levels at energies close to the II-Dirac point ($\epsilon_0$).
-We focus first on the regime where, on average (over $\frako_0$), the energy splitting $|\delta \var_+{-}\delta \var_-|$ (due to both spin-orbit and in-plane Zeeman interactions) is much greater than the interband, out-of-plane Zeeman interaction $B_{\perp}|\calm_{\pm}|$.
+We focus first on the regime where, on average (over $\frako_0$), the energy splitting $|\delta \var_+{-}\delta \var_-|$ [cf.\ \q{eq:RZ-Hamiltonian}] is much greater than $Z_\perp$.
 This implies that the split orbits do not appreciably hybridize -- except in the vicinity of the II-Dirac point where orbits (nearly) touch.
-In the constant basis,
-\begin{equation}
-\calh(t)=\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+Z_\parallel\sigma_{y}-Z_\perp\sigma_{z},\label{calHRZ}
-\end{equation}
-where $k_x=-k_F \cos(\omega_c t)$ and $k_y=k_F \sin(\omega_c t)$. Near the II-Dirac point, the dynamics of a two-component wavepacket is described by linearizing $\H$ with respect to $t$
+Near this touching point (where $t{=}0$), the dynamics of a spinor electron is described by linearizing $\H$ [cf.\ \q{calHRZ}] with respect to $t$:
 \e{
@@
 }
-with $k_E{=}\sqrt{2mE}/\hbar$ and  $t$ a time variable which parametrizes the zeroth-order orbit:
-$\bk(t){=}({-}k_E \cos \omega_c^{\sma{\perp}} t, k_E \sin \omega_c^{\sma{\perp}} t ).$ 
 The eigenbasis of $\sigma_x$ corresponds to two diabatic levels with characteristic slope $v_d{:}{=}\alpha k_E\omega^{\sma{\perp}}_c$; near $t{=}0$, the diabatic levels anticross  due to the hybridization terms proportional to $\sigma_{y,z}$.
@@
 with $2\alpha k_E$ the spin-orbit splitting at energy $E$ [cf.\ \fig{fig:orbits}(a)].
-In the absence of the out-of-plane Zeeman coupling ($Z_\perp{=}0$), $\bar{\mu}$ would vanish at the energy of the II-Dirac point -- leading to unit-probability Klein tunneling, as was first proposed by [Obrien] in a different model realization of the II-Dirac point.
+In the absence of the out-of-plane Zeeman coupling ($Z_\perp{=}0$), $\bar{\mu}$ would vanish at the energy of the II-Dirac point -- leading to unit-probability Klein tunneling, as was first proposed by [Obrien] in a different model of the II-Dirac point.
 However, with a proper account of $Z_\perp$, we find instead that $\bar{\mu}$ has a nonvanishing minimum: $\bar{\mu}_{\sma{\text{min}}}{:}{=} ( m/m_0)(Z_\perp/4\alpha k_{E})$, which is a product of the dimensionless effective mass and the ratio of the out-of-plane Zeeman splitting over the spin-orbit splitting.
@@
 which is a connection formula that matches the two-component semiclassical (WKB) wavefunction across the Dirac point.
-$\mathbb{S}$ in \q{scattmat} has been expressed in the basis of Zeeman-corrected energy bands, i.e., eigenvectors of Eq.
-(\ref{calHRZ}), so the diagonal elements of $\mathbb{S}$ are amplitudes for intraband (adiabatic) transmission; the phase of this amplitude is $\barphi{:}{=}\barmu{-}\barmu\ln\barmu{+}\text{arg}[\Gamma(i\barmu)]{+}\pi/4$ with $\Gamma$ the gamma function.
-
-Away from the II-Dirac point, a semiclassical wavepacket undergoes adiabatic (band-conserving) dynamics.
-The time-ordered, coherent process of interband tunneling and adiabatic dynamics is described by the propagator:
+This formula  has been expressed in the basis of Zeeman-modified energy bands [i.e., eigenvectors of Eq.\ (\ref{calHRZ})]; diagonal (resp.\ off-diagonal) elements of $\mathbb{S}$ are amplitudes for intraband transmission (resp.\ interband tunneling).
+The phase of the intraband amplitude is $\barphi{:}{=}\barmu{-}\barmu\ln\barmu{+}\text{arg}[\Gamma(i\barmu)]{+}\pi/4$ with $\Gamma$ the gamma function.
+
+Away from the II-Dirac point, an electron undergoes adiabatic (band-conserving) dynamics.
+The time-ordered, coherent process of Landau-Zener tunneling/transmission and adiabatic dynamics is described by the propagator:
 \e{{\A}= \matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}} \diagmatrix{e^{i\tilde{\lambda}_+}}{e^{i\tilde{\lambda}_-}}. \la{propinplanezeeman}}
-In the basis of Zeeman-corrected energy bands, the adiabatic phases $\tilde{\lambda}_{\pm}$ consist of two parts: dynamical phase $l^2 \delta S'$ with $\delta S'$ now accounting for both spin-split and Zeeman-split area corrections, and single band Berry phases $\phi^B_\pm$ evaluated on $\frako_0$.
+The adiabatic phase $\tilde{\lambda}_{\pm}$ is the sum of a dynamical phase ${\pm} l^2 \delta S$ and  the single-band Berry phase $\phi^B_\pm$, for the outer ($+$) and inner ($-$) orbit respectively.
 At energies far above the Dirac point ($|E{-}\epsilon_0|{\gg}|Z_{\perp}|$) where the Zeeman interaction is negligible, both orbits encircle the Dirac point and hence $\phi_{\pm}^B{\approx}{\pm}\pi$; far below the Dirac point, neither orbit encircles the Dirac point, leading to $\phi_{\pm}^B{\approx}0$.
-At intermediate energies, $\phi_{+}^B$ (resp.\ $\phi_{-}^B$) is a continuous and increasing (resp.\ decreasing) function of energy, as supported by the Bloch-sphere argument in Fig.
+At intermediate energies, $\phi_{+}^B$ (resp.\ $\phi_{-}^B$) is a continuous and decreasing (resp.\ increasing) function of energy, as supported by the Bloch-sphere argument in Fig.
 \ref{fig:blochsphere}.
+
+%consist of two parts: dynamical phase $\lper^2 \delta S$ with $\delta S'$ now accounting for both spin-split and Zeeman-split area corrections,
 
@@
 \includegraphics[width=1.0\columnwidth]{blochsphere.png}
-\caption{Energy dependence of the Berry phases for inner (upper panel) and outer (lower panel) orbits.
-For two band models, the Berry phase equals half the solid angle subtended by the loop swept by spin-splitting field ($-\alpha k_y$,$Z_\parallel+\alpha k_x$,$Z_\perp$) of $\H$ in Eq.
-(\ref{calHRZ}) on the unit sphere.
-Notice that Zeeman coupling are included in spin-splitting field here.
-For lower band (outer orbit), the spin splitting field should be inverted to reflect the change in band index.
-The solid angles are indicated by blue outlines and the energy is measured from $\epsilon_0$ in Eq.
-(\ref{whereisdiracpoint}).\label{fig:blochsphere}}
+\caption{Energy dependence of the single-band Berry phase for inner (upper panel) and outer (lower panel) orbits, denoted $\phi_-^B$ and $\phi_+^B$ respectively.
+$\phi_{\pm}^B$  equals half the solid angle subtended by the three-vector ${\pm} \bd(\bk)$,[Berry] where  $\bd{=}({-}\alpha k_y$,$Z_\parallel{+}\alpha k_x,{-}Z_\perp$) is obtained from expressing the effective Hamiltonian [cf.\ Eq.
+(\ref{calHRZ})] as $\sum_jd_j\sigma_j$.
+The solid angles are enclosed by blue outlines and the energy is measured from $\epsilon_0$ [cf.\ Eq.
+(\ref{whereisdiracpoint})].\label{fig:blochsphere}}
 \end{figure}
@@
 \text{cos}\left[\frac{\Omega_{-}+\Omega_{+}}{2}\right]=\tau\,\text{cos}\left[\frac{\Omega_{-}-\Omega_{+}}{2}+\bar{\varphi}\right], \lin
-\ins{with}\;\Omega_{\pm}=l^2 (S\pm \delta S'/2)+\phi_{\pm}^B +\gamma_{\pm}, \la{coscos}
+\ins{with}\;\Omega_{\pm}=l^2 (S\pm \delta S/2)+\phi_{\pm}^B +\gamma_{\pm}, \la{coscos}
 }
 $\Omega_{\pm}$ is the phase acquired by an electron in adiabatically traversing orbit $\pm$; the quantum Maslov correction $\gamma_{\pm}{=}\pi$ for circular orbits.
-Since $\phi^B_\pm$ are evaluated both on $\frako_0$, $\phi^B_-+\phi^B_+=0$ in two band models.
 A quantization rule analogous to \q{coscos} was previously derived by us for a II-Dirac point that intermediates an electron- and hole-like orbit [AALG].
@@
 \e{2l^2S(E_n^0)+\pi = 2\pi n \rightarrow \{E_n^0(B)\}_{n\in\Z}.\label{trefoillerule}}
- This may be interpreted as a quantization rule for a trefoille-shaped orbit with net action $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels, as plotted with dashed lines in Fig.\ \ref{fig:RZ}(b), are  periodic in $E{\rightarrow}E{+}\pi/l^2(\partial S/\partial E)$ and in $l^2{\rightarrow}l^2{+}\pi/S$.
+To derive the above equation, we have utilized $\phi^B_-{+}\phi^B_+{=}0$, which is valid for any two-band model in the quasidegenerate regime\footnote{For two band models, Berry phases of the two bands sum up to 0 on arbitrary path}; in \fig{fig:blochsphere} this is reflected in the sum of solid angles (at fixed energy) equalling $4\pi$.
+\q{trefoillerule} may be interpreted as a quantization rule for a trefoille-shaped orbit with net action $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels, as plotted with dashed lines in Fig.\ \ref{fig:RZ}(b), are  periodic in $E{\rightarrow}E{+}\pi/l^2(\partial S/\partial E)$ and in $l^2{\rightarrow}l^2{+}\pi/S$.
 Both periods are approximately half that of either disconnected spin-orbit-split orbit, in the assumed quasidegenerate regime $\delta S{\ll}S$.
@@
 
-In the regime of quasidegenerate orbits ($\delta S/S \ll 1$) with intermediate adiabaticity ($l^2\delta S\sim 1$),  our quantization rule \qq{eq:rule}{eq:H1} remains valid but the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}.
-We may anyway simulate $\cala$ numerically, and compare the semiclassically-obtained Landau levels with the exact solution of $H_{RZ}(\boldsymbol{K})$ (see Fig.
-\ref{fig:RZ} (d)).
-This exact solution is obtained by large-scale numerical diagonalization [appendix], since (to our knowledge) there exists no analytic solution for generic values of $\alpha,\zpar$ and $B$.
-Errors of \qq{eq:rule}{eq:H1} in predicting Landau levels are less than 0.3\% of cyclotron energy in the parameter range plotted in Fig.
-\ref{fig:RZ} (d).
-Similar to Rashba-Dresselhaus model, the observed errors are strongly positively correlated with $l^2\delta S^2/S$.
-
-For the special case of $\alpha=0$, the spectra of $H_{RZ}(\boldsymbol{K})$ and $\mathcal{A}[\mathfrak{o}]$ are both exactly soluble.
-The eigenphases of $\A$ are $\lambda_{\pm}=\pm 2\pi ml^2\sqrt{Z_\parallel^2/\hbar^4+g_\text{eff}^2/16m^2l^4}$.
-Together with Eq.
-(\ref{eq:rule}), $\lambda_\pm$ here generate exact the same Landau level spectrum as $H_{RZ}(\boldsymbol{K})$.
+If the quasidegenerate orbits are appreciably hybridized ( $|\delta \var_+-\delta \var_-|{\lesssim}Z_{\perp}$ on average), our quantization rule \qq{eq:rule}{eq:H1} remains valid but the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}.
+We may anyway diagonalize $\cala$ numerically, and compare the resultant semiclassical Landau levels with the exact diagonalization of $H_{RZ}(\boldsymbol{K})$; to our knowledge, there exists no analytic solution of $H_{RZ}(\boldsymbol{K})$ for generic values of $\alpha,\zpar$ and $B_{\perp}$.
+For fixed  $B_{\perp}$ and a range of $(\alpha,\zpar)$ wherein  $l^2\delta S^2/S$ varies over $[0,0.2]$, the difference between semiclassical and exact Landau levels never exceeds  0.3\% of the cyclotron energy $\var_c$; this difference shows a strong positive correlation with $l^2\delta S^2/S$ [compare the left and right panels of Fig.\ \ref{fig:RZ} (d)], just like in the Rashba-Dresselhaus model.
+
+For the special case of $\alpha{=}0$, the spectra of $H_{RZ}(\boldsymbol{K})$ and $\mathcal{A}[\mathfrak{o}]$ are both exactly soluble, hence it is possible to verify that the exact and semiclassical Landau levels match perfectly for every level index $n$ without any approximation; the latter is obtained from our rule [Eq.\ (\ref{eq:rule})], with the eigenphases of $\A$ equal to
+\e{\lambda_{\pm}{=}{\pm} 2\pi ml^2\sqrt{\f{Z_\parallel^2}{\hbar^4}{+}\f{g_\text{eff}^2}{16m^2l^4}}.}
+
+%Together with Eq. (\ref{eq:rule}), $\lambda_\pm$ here generate exact the same Landau level spectrum as $H_{RZ}(\boldsymbol{K})$.
 
@@
 Here, and in the  Landau-level problem, we define codimension with respect to a \textit{symmetrically-chosen coordinates} (if symmetry exists).
-We do not require that the symmetric coordinates is globally defined, e.g., polar coordinates is singular at $x{=}y{=}0$.
+We do not require that the symmetric coordinates is globally defined, e.g., the polar coordinates is not well-defined where the radial coordinate vanishes.
 
@@
 \e{\A{=}e^{-i2\pi\sum_{j}r_j\tau_j}, \;\;(r_1,r_3){=}\bigg(\f{g_{\sma{\text{eff}}}}{4}{-}\f1{2},\f1{2}{-}\f{\alpha k_{\sma{E}}}{\var_c}\bigg).\la{expform}} 
-$r_2{=}0$ in the Rashba model, but nonzero $r_2$ corresponds to a symmetry-allowed deformation that we allow for greater generality -- any $SU(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}]  for some (possibly non-unique) $\br$, which are the symmetric  coordinates.
+$r_2{=}0$ in the Rashba model, but nonzero $r_2$ corresponds to a symmetry-allowed deformation that we allow for greater generality -- any $SU(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}]  for some (possibly non-unique) $\br$, which may be identified as the symmetric  coordinates.
 
@@
 
-All other spheres are unit-codimensional surfaces (known as hypersurfaces), and can be reached by varying $B$ alone.
-Equivalently stated, at fixed energy there exists a series of Landau-level quasi-crossings as a function of $B$.
-The stability of hypersurfaces rely on  $\mathfrak{c}_{\infty}$ symmetry.
-Moreover, the hypersurfaces separate $\br$-space into infinitely-many, distinct connected components, i.e., the zeroth homotopy group $\pi_0$ comprises an infinite set.
-Each hypersurface may thus be viewed as a symmetry-protected, topological defect, which separates domains in $\br$-space where Landau levels are non-quasidegenerate.
-
-This discussion is reminiscent of topological (semi)metals which host Dirac-Weyl points and/or line nodes (of Bloch-Hamiltonian degeneracies).
+All other spheres are unit-codimensional surfaces (known as hypersurfaces), whose stability rely on $\mathfrak{c}_{\infty}$ symmetry.
+These hypersurfaces separate $\br$-space into infinitely-many, distinct connected components, i.e., the zeroth homotopy group $\pi_0$ comprises an infinite set.
+Each hypersurface may thus be viewed as a symmetry-protected, topological defect, which separates domains (in $\br$-space) where Landau levels are non-quasidegenerate.
+By varying $B$ alone (at fixed energy), one then transits between different domains; each penetration of a hypersurface is accompanied by a Landau-level quasi-crossing.
+For the exactly-soluble Rashba model ($r_2{=}0$), these $\mathfrak{c}_{\infty}$-protected quasi-crossings  are consistent with (and partially explain)  the abundance of \textit{exact} level crossings in the spectrum of $H_R(\bK)$ [cf.\ \q{eq:Rashba-exact}], which would otherwise seem mysterious in face of  the Wigner-von Neuman non-crossing rule[wigner neumann].
+
+%Equivalently stated, at fixed energy there exists a series of Landau-level quasi-crossings as a function of $B$.
+
+The above discussion is reminiscent of topological (semi)metals which host Dirac-Weyl points and/or line nodes (of Bloch-Hamiltonian degeneracies).
 Weyl points in 3D $\bk$-space have codimension three and do not require any crystallographic point-group symmetry for their stability.

### 2018-09-21 paper.tex
Updates from ShareLaTeX

@@
 An over-tilted Dirac cone shall be referred to as type-II.
-Our case study of a II-Dirac point  connects  two electron-like  pockets [cf.\ \fig{fig:RZ}(a,c)], and  differs from previous case studies [Obrien, AALG] that connect an electron- and hole-like pocket.
+Our case study of a II-Dirac point  connects  two electron-like  pockets [cf.\ \fig{fig:RZ}(a,c)], and  differs from previous case studies [OBrien, AALG] that connect an electron- and hole-like pocket.
 
@@
 \includegraphics[width=1.0\columnwidth]{blochsphere.png}
-\caption{Energy dependence of the single-band Berry phase for inner (upper panel) and outer (lower panel) orbits, denoted $\phi_-^B$ and $\phi_+^B$ respectively.
-$\phi_{\pm}^B$  equals half the solid angle subtended by the three-vector ${\pm} \bd(\bk)$,[Berry] where  $\bd{=}({-}\alpha k_y$,$Z_\parallel{+}\alpha k_x,{-}Z_\perp$) is obtained from expressing the effective Hamiltonian [cf.\ Eq.
-(\ref{calHRZ})] as $\sum_jd_j\sigma_j$.
-The solid angles are enclosed by blue outlines and the energy is measured from $\epsilon_0$ [cf.\ Eq.
-(\ref{whereisdiracpoint})].\label{fig:blochsphere}}
+\caption{Solid-angle representation of  the single-band Berry phase $\phi_{\pm}^B$ for inner (subscript $-$, upper panel) and outer ($+$, lower panel) orbit, at various energies close to the Dirac point $\epsilon_0$ [cf.\ Eq.
+(\ref{whereisdiracpoint})].
+The decomposition of the effective Hamiltonian [cf.\ Eq.
+(\ref{calHRZ})] into sums of Pauli matrices ($\calh{=}\sum_jd_j\sigma_j$) defines a three-vector $\bd{=}({-}\alpha k_y$,$Z_\parallel{+}\alpha k_x,{-}Z_\perp$).
+ $\phi_{\pm}^B$  equals half the solid angle subtended by   ${\pm} \bd(\bk)$ \textbf{[I wasn't  careful about minus signs here]} as $\bk$ is varied along the outer/inner orbit.[Berry]   These angles are indicated in the figure by blue outlines.\label{fig:blochsphere}}
 \end{figure}
@@
 
-\subsection{Codimension analysis in the absence of symmetry}\la{sec:introducecodimension}
+\subsection{Codimension analysis without symmetry, and with band-conservation symmetry}\la{sec:introducecodimension}
 
@@
 
-\subsection{Rotational symmetric magnetic breakdown}\la{sec:rotsymmbreakdown}
+\subsection{Codimension reduction for 2DEG with distinct, symmetry-related II-Dirac points}\la{sec:rotsymmbreakdown}
 
@@
 \end{figure}
+
+In the adiabatic regime of two quasidegenerate orbits, we have found [in \s{sec:introducecodimension}] that the codimension for $\cala{=}{\pm} I$ is unity.
+Here we investigate how relaxing adiabaticity -- in the presence of a discrete $N$-fold rotational symmetry $\mathfrak{c}_N$  -- changes this result.
+One simple way to relax adiabaticity is to incorporate Landau-Zener tunneling at II-Dirac points.
+Since a II-Dirac cone is tilted in a special direction, a II-Dirac point cannot be the center of a rotational symmetry; the minimal model with $\mathfrak{c}_N$ symmetry thus requires $N$ distinct but symmetry-related II-Dirac points.
+For $N{=}2$, we will demonstrate that the codimension for $\cala{=}I$ remains unity, in accordance with the symmetric-coordinate analysis of \q{proprashba}; the existence of Landau-level quasi-crossings (over the B axis) will be explained in terms of the destructive interference of two tunneling Feynman paths
 
@@
 \begin{table}
-\begin{tabular*}{\columnwidth}{l@{\extracolsep{\fill}}ccccc}
+\begin{tabular*}{\columnwidth}{l@{\extracolsep{\fill}}cccccc}
 \hlineB{2.0}
-             & $u$ & $s$ & quasi. & $g$ & codim.\\
+             no. & description & $u$ & $s$ & quasi. & $g$ & codim.\\
 \hline
-$\forall \bk \in \frako_0$, $g\circ \bk=\bk$ & 0 & 0 & $\surd$ & $\breve{g}\propto I$ & 3  \\
-    &  &  & & $\breve{g}\not\propto I$ & 1 \\
-    & 0 & 1 & & $g^2=1$ & 1  \\
-    &  &  & & $g^2=-1$ & 3  \\
-$|g\circ \frako_0| = |\frako_0|$ & 0 & 0 & $\surd$ & - & 1   \\
-$\exists \bk \in \frako_0, g\circ \bk\ne\bk$    & 0 & 1 & & - & 1   \\
-    & 1 & 0 & & $\breve{g} \propto \sigma_z$ & 2  \\
-    &  &  & & $\breve{g} \not\propto \sigma_z$ & 0  \\
-    & 1 & 1 & $\surd$ & $g^2=1$ & 2  \\
-    &  &  & & $g^2=-1$ & 0  \\
-$|g\circ \frako_0| \ne |\frako_0|$ & 0 & 0 & $\surd$ & - & 3 \\
-    & 0 & 1 & & - & 3 \\
-    & 1 & 0 & & - & 3 \\
-    & 1 & 1 & $\surd$ & - & 3 \\
+1 &$\forall \bk \in \frako_0$, $g\circ \bk=\bk$  & 0 & 0 & $\surd$ & $\breve{g}\propto I$ & 3  \\
+ &    &  &  & & $\breve{g}\not\propto I$ & 1 \\
+2 &    & 0 & 1 & & $g^2=1$ & 1  \\
+ &    &  &  & & $g^2=-1$ & 3  \\
+3 & $|g\circ \frako_0| = |\frako_0|$ & 0 & 0 & $\surd$ & - & 1   \\
+4 & $\exists \bk \in \frako_0, g\circ \bk\ne\bk$    & 0 & 1 & & - & 1   \\
+5 &    & 1 & 0 & & $\breve{g} \propto \sigma_z$ & 2  \\
+ &    &  &  & & $\breve{g} \not\propto \sigma_z$ & 0  \\
+6 &    & 1 & 1 & $\surd$ & $g^2=1$ & 2  \\
+&    &  &  & & $g^2=-1$ & 0  \\
+7 & $|g\circ \frako_0| \ne |\frako_0|$ & 0 & 0 & $\surd$ & - & 3 \\
+8 &    & 0 & 1 & & - & 3 \\
+9 &    & 1 & 0 & & - & 3 \\
+10 &    & 1 & 1 & $\surd$ & - & 3 \\
 \hlineB{2.0}

### 2018-09-22 paper.tex
Updates from ShareLaTeX

@@
 (b) Black dashed lines illustrate a zeroth-order approximation of the Landau levels (assuming Klein tunneling); the leading-order correction is indicated by red lines.
-The Dirac point lies at $10$meV.
-Parameters for (b): $m$: 0.02$\hbar^2$/eV$\cdot$\AA$^2$, $\alpha$: 0.05eV$\cdot$\AA, $Z_\parallel$: 0.001eV.
+Exact Landau levels by numerical diagonalization are plotted as green dots.
+The Dirac point lies at $6.4$eV.
+Parameters for (b): $m$: 0.05$\hbar^2$/eV$\cdot$\AA$^2$, $\alpha$: 0.05eV$\cdot$\AA, $Z_\parallel$: 0.04eV.
 (c) A sketch of cyclotron orbits of Rashba Hamiltonian with in-plane magnetic field.
@@
 To investigate this failure of adiabaticity, let us study the Landau levels at energies close to the II-Dirac point ($\epsilon_0$).
-We focus first on the regime where, on average (over $\frako_0$), the energy splitting $|\delta \var_+{-}\delta \var_-|$ [cf.\ \q{eq:RZ-Hamiltonian}] is much greater than $Z_\perp$.
+We focus first on the regime where, on average (over $\frako_0$), the energy splitting $|\delta \var_+{-}\delta \var_-|$ [cf.\ \q{eq:RZ-Hamiltonian}] is much greater than $B_\perp|\calm_{\sma{+-}}|$.
 This implies that the split orbits do not appreciably hybridize -- except in the vicinity of the II-Dirac point where orbits (nearly) touch.
@@
 \e{
-\calh = \alpha k_{E} \,\omega^{\sma{\perp}}_c t\,\sigma_x+(Z_\parallel-\alpha k_{E})\sigma_y-Z_\perp\sigma_z,\la{effhamIIDirac}
+\calh = -\alpha k_{E}\omega^{\sma{\perp}}_c t\,\sigma_x+(Z_\parallel-\alpha k_{E})\sigma_y-Z_\perp\sigma_z,\la{effhamIIDirac}
 }
@@
 \e{{\A}= \matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}} \diagmatrix{e^{i\tilde{\lambda}_+}}{e^{i\tilde{\lambda}_-}}. \la{propinplanezeeman}}
-The adiabatic phase $\tilde{\lambda}_{\pm}$ is the sum of a dynamical phase ${\pm} l^2 \delta S$ and  the single-band Berry phase $\phi^B_\pm$, for the outer ($+$) and inner ($-$) orbit respectively.
+The adiabatic phase $\tilde{\lambda}_{\pm}$ is the sum of a dynamical phase ${\pm} l^2 \delta S/2$ and  the single-band Berry phase $\phi^B_\pm$, for the outer ($+$) and inner ($-$) orbit respectively.
 At energies far above the Dirac point ($|E{-}\epsilon_0|{\gg}|Z_{\perp}|$) where the Zeeman interaction is negligible, both orbits encircle the Dirac point and hence $\phi_{\pm}^B{\approx}{\pm}\pi$; far below the Dirac point, neither orbit encircles the Dirac point, leading to $\phi_{\pm}^B{\approx}0$.
@@
 This small-scale periodicity is lost due to  finite-$\tau$ corrections, yet a longer-range correlation (associated to the smaller differential action $\delta S$ between spin-split orbits) persists, as shown by the first-order-in-$\tau$ correction:\footnote{The general form of this perturbative calculation can be found in Sec.
-IX-E of [100page].
-}
+IX-E of [100page].}
 \e{&\delta E_n(B) = \f{(-1)^{n+1}}{2\pi} \tau \var_c \cos\bigg(\f{l^2\delta S}{{2}}+\f{\phi_+^B-\phi_-^B}{2}-\bar{\varphi}\bigg) \lin
     &\substack{\sma{Z_{\perp}{\rightarrow}0}\\ \approx} \f{(-1)^{n+1}}{4\sqrt{2\pi}}  \var_c \f{(E-\epsilon_0)l}{\alpha(\epsilon_0/Z_{\parallel})^{3/2}}\cos\bigg(\f{l^2\delta S}{{2}}-\bar{\varphi}\bigg),\label{RZfirstorderE}}
-with the right-hand side (of each line) evaluated at $E_n^0(B)$. The second line of \q{RZfirstorderE} has greater utility where $m{\ll}m_0$.
-
-If the quasidegenerate orbits are appreciably hybridized ( $|\delta \var_+-\delta \var_-|{\lesssim}Z_{\perp}$ on average), our quantization rule \qq{eq:rule}{eq:H1} remains valid but the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}.
+with the right-hand side (of each line) evaluated at $E_n^0(B)$.
+The second line of \q{RZfirstorderE} has greater utility where $m{\ll}m_0$.
+\red{This first order corrections of Landau levels are plotted in Fig.
+\ref{fig:RZ}(b) as red solid lines.
+The oscillation in Eq.
+(\ref{RZfirstorderE}) cannot be observed due to the smallness of $\delta S$.
+However, as expected from Eq.
+(\ref{RZfirstorderE}), first order correction have alternative signs for every Landau levels, which is confirmed by exact diagonalization [cf.
+Fig.
+\ref{fig:RZ}](b).}
+
+If the quasidegenerate orbits are appreciably hybridized ( $|\delta \var_+{-}\delta \var_-|{\lesssim}B_\perp|\calm_{\sma{+-}}|$ on average), our quantization rule \qq{eq:rule}{eq:H1} remains valid but the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}.
 We may anyway diagonalize $\cala$ numerically, and compare the resultant semiclassical Landau levels with the exact diagonalization of $H_{RZ}(\boldsymbol{K})$; to our knowledge, there exists no analytic solution of $H_{RZ}(\boldsymbol{K})$ for generic values of $\alpha,\zpar$ and $B_{\perp}$.
@@
 \caption{Cyclotron orbits for $\mathfrak{c}_2$-symmetric [(a)] and $\mathfrak{c}_3$-symmetric [(b)] breakdown.
-Bottom right inset of (a) presents an enlarged view of breakdown junction, where purple rectangle has area $S_{\sma{\square}}$.\label{fig:Cn-breakdown}}
+\textbf{[Please add dashed line indicating zeroth order orbit, and label one of the crescents by $\delta S/4$ and another by $\delta S/6$.
+It would also be good to show the energy-momentum dispersion and the orbits (the analog of Fig 3c).]} Bottom right inset of (a) presents an enlarged view of the breakdown junction, where the purple rectangle has area $S_{\sma{\square}}$.\label{fig:Cn-breakdown}}
 \end{figure}
 
-In the adiabatic regime of two quasidegenerate orbits, we have found [in \s{sec:introducecodimension}] that the codimension for $\cala{=}{\pm} I$ is unity.
-Here we investigate how relaxing adiabaticity -- in the presence of a discrete $N$-fold rotational symmetry $\mathfrak{c}_N$  -- changes this result.
-One simple way to relax adiabaticity is to incorporate Landau-Zener tunneling at II-Dirac points.
+In the adiabatic limit of two quasidegenerate orbits, we have found [in \s{sec:introducecodimension}] that the codimension for $\cala{=}{\pm} I$ is unity.
+Here we investigate how this result changes as adiabaticity is relaxed by Landau-Zener tunneling -- that respects a discrete $N$-fold rotational symmetry ($\mathfrak{c}_N$).
 Since a II-Dirac cone is tilted in a special direction, a II-Dirac point cannot be the center of a rotational symmetry; the minimal model with $\mathfrak{c}_N$ symmetry thus requires $N$ distinct but symmetry-related II-Dirac points.
-For $N{=}2$, we will demonstrate that the codimension for $\cala{=}I$ remains unity, in accordance with the symmetric-coordinate analysis of \q{proprashba}; the existence of Landau-level quasi-crossings (over the B axis) will be explained in terms of the destructive interference of two tunneling Feynman paths
-
-Quasidegenerate orbits feature tunneling everywhere along the cyclotron orbit and therefore demand a quantization rule that incorporates both tunneling and single band evolution of wave packets.
+For $N{=}2$, we will demonstrate that the codimension for $\cala{=}I$ (but not for $\cala{=}{-}I$) remains unity, in accordance with the symmetric-coordinate analysis of \q{proprashba}; the persistence of  Landau-level quasidegeneracies  (at finite tunneling probability) will be demystified in terms of the destructive interference of tunneling Feynman paths.
+For $N{=}3$, we will find that two of three Landau-level quasi-crossings are perturbatively stable against tunneling, but even these will destabilize beyond a critical tunneling strength.
+
+%Quasidegenerate orbits feature tunneling everywhere along the cyclotron orbit and therefore demand a quantization rule that incorporates both tunneling and single band evolution of wave packets.
 Sometimes, the coherent evolution of wave packets and tunneling can be decoupled in the quantization rule in weak field limit, as exemplified by magnetic breakdown in Rashba-Zeeman model in Sec.
@@
 
-We introduce a $\mathfrak{c}_2$-symmetric analog of the Rashba-Zeeman model:
-\e{H=\f{\red{\hbar^2}k^2}{2m_1}+ \bigg(\f{\red{\hbar^2}k^2}{2m_2}-\mu\bigg)\sigma_z +wk_y\sigma_x,\la{modelC2breakdown}}
-where $0<m_1{\ll}m_2,0<\mu$.
+We begin with a minimal, $\mathfrak{c}_2$-symmetric model:
+\e{H=\f{{\hbar^2}k^2}{2m_1}+ \bigg(\f{{\hbar^2}k^2}{2m_2}-\mu\bigg)\sigma_z +wk_y\sigma_x,\la{modelC2breakdown}}
+with $0{<}m_1{\ll}m_2$ and positive $\mu$.
 For simplicity, we interpret the Pauli matrices as  spin operators, and the two right-most terms of  \q{modelC2breakdown} as a spin-orbit coupling.
@@
 two Dirac points at
-\e{\bar{k}_x = \pm\sqrt{2m_2\mu}/\red{\hbar},\;\bar{k}_y=0,\;\epsilon_{0}=\frac{m_2}{m_1}\mu.}
+\e{\bar{k}_x = \pm\sqrt{2m_2\mu}/{\hbar},\;\bar{k}_y=0,\;\epsilon_{0}=\frac{m_2}{m_1}\mu.}
 In the vicinity of either point, the  Hamiltonian has the linearized form 
-\e{H_{\pm} =\pm \red{\hbar}\sqrt{\f{2\mu}{m_2}}\bigg(\frac{m_2}{m_1}+\sz\bigg)\delta k_x+w\delta k_{y}\sx+\epsilon_0, \la{linearHam2}}
-from which we deduce that both Dirac points are  type-II if $m_1{<}m_2$; this condition is henceforth assumed.\footnote{Actually we will impose the stronger condition $m_1{\ll}m_2$, to ensure that the relative change in band velocity (due to the spin-orbit coupling) is small.
+\e{H_{\pm} =\pm {\hbar}\sqrt{\f{2\mu}{m_2}}\bigg(\frac{m_2}{m_1}+\sz\bigg)\delta k_x+w\delta k_{y}\sx+\epsilon_0, \la{linearHam2}}
+from which we deduce that both Dirac points are  type-II if $m_1{<}m_2$; we further assume $m_1{\ll}m_2$ so that the quasidegeneracy condition is satisfied.
+
+%this condition is henceforth assumed.\footnote{Actually we will impose the stronger condition $m_1{\ll}m_2$, to ensure that the relative change in band velocity (due to the spin-orbit coupling) is small.
 This is a consistency requirement of our WKB theory, as explained in \app{app:quantizationruleproof}.}
@@
 
-At energies close to the Dirac point ($E{-}\epsilon_0 {\ll} wm_2(2E/m_1)^{\sma{1/2}}$ \red{[need checking]}), there are two concentric orbits which (nearly) touch at both Dirac points, as illustrated in Fig.
+% In the weak-field regime where $\var_c{=}{\hbar^2}/m_1l^2{\ll}\Delta$,
+
+At energies close to the Dirac point ($E{-}\epsilon_0 {\ll} wm_2(2E/m_1)^{\sma{1/2}}$), there are two concentric orbits which (nearly) touch at both Dirac points, as illustrated in Fig.
 \ref{fig:Cn-breakdown} (a).
-Just as in \q{spinsplitwkb}, we define $\Delta$ as the spin-orbit splitting energy (averaged over the zeroth-order orbit with effective mass $m_1$).
-In the weak-field regime where $\var_c{=}\red{\hbar^2}/m_1l^2{\ll}\Delta$, interband tunneling is localized to the vicinities of the two II-Dirac points, and occurs with the Landau-Zener probability:
-\e{\rho^2=e^{-2\pi\bar{\mu}}, \; \bar{\mu}=\f{\big(Z_{\perp}^2+(m_1/m_2)^2(E-\epsilon_0)^2\big)l^2}{2w\sqrt{2E/m_1}}. }
-Elsewhere, a semiclassical wavepacket undergoes adiabatic (band-conserving) dynamics.
-For the upper half ($k_y>0$) of the diagram Fig.
-\ref{fig:Cn-breakdown}(a), this adiabatic evolution is described by a diagonal unitary matrix in the basis of energy bands; each diagonal entry encodes the slowly-varying semiclassical phase due to $\H$ ($\lambda_a'$ \red{[Let's use $\lambda_j'$ instead of $\delta_\lambda$.
-The latter is confusing because $\lambda_a\sim l^2 \delta S$.
-It would be quite confusing if we also let $\delta\lambda_a\sim l^2\delta S$]}) acquired along a spin-split trajectory to the \red{top}.
-In more detail, $\lambda_{\pm}'{=}{\pm}l^2\delta S/4$ up to a field-independent geometric phase \footnote{due to this field-independent phase, it is not necessary that $\delta\lambda_+=-\delta\lambda_-$}.
-The time-evolution propagator  describes the time-ordered, coherent process of interband tunneling (as described by the scattering matrix of \q{scattmat})
- and adiabatic dynamics:
-\e{\A&=\red{e^{i(\lambda_+'+\lambda_-')}}\times\nonumber\\
-&\left(\matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}}\red{\diagmatrix{e^{i\f{\lambda_+'-\lambda_-'}{2}}}{e^{i\f{\lambda_-'-\lambda_+'}{2}}}} \right)^2.
+For sufficiently weak field, interband tunneling is localized near either II-Dirac point, and occurs with the Landau-Zener probability:
+\e{\rho^2=e^{-2\pi\bar{\mu}}, \; \bar{\mu}=\f{\big(Z_{\perp}^2+(m_1/m_2)^2(E-\epsilon_0)^2\big)l^2}{2w\sqrt{2E/m_1}}. \la{landauzenerc2} }
+Elsewhere, an electron undergoes adiabatic (band-conserving) dynamics.
+Due to the $\mathfrak{c}_2$ symmetry, the time-evolution propagator over the full cyclotron period is simply the square of the propagator for half the period:
+\e{\A={e^{i(\tilde{\lambda}_++\tilde{\lambda}_-)}}\left(\matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}}{\diagmatrix{e^{i\f{\tilde{\lambda}_+-\tilde{\lambda}_-}{2}}}{e^{i\f{\tilde{\lambda}_--\tilde{\lambda}_+}{2}}}} \right)^2.
 \la{propC2breakdown}}
-The two scattering matrices for both Dirac points are identical by $\mathfrak{c}_2$ symmetry; so are the two diagonal propagators corresponding to the left and right halves of the adiabatic dynamics.
-
-$\rho{=}0$  describes the adiabatic limit of two independent orbits with differential action $\delta S$.
-As described earlier in \s{sec:llquasideg}, degeneracies of $\cala$ occur with a periodicity (in $l^2$) of $2\pi/\delta S$, which corresponds to a periodic increment of a single flux quantum for  the differential magnetic flux (between the two spin-split orbits in real space).
+The half-period propagator may be taken from \qq{scattmat}{propinplanezeeman}, with  $\bar{\mu}$ here given by \q{landauzenerc2}, and  $\tilde{\lambda}_{\pm}{=}{\pm}l^2\delta S/4$ plus a field-independent geometric phase.
+
+%For the upper half ($k_y{>}0$) of Fig.
+\ref{fig:Cn-breakdown}(a), this adiabatic evolution is described by a diagonal unitary matrix in the basis of energy bands; the phase of the diagonal entry $\tilde{\lambda}_{\pm}{=}{\pm}l^2\delta S/4$ plus a field-independent geometric phase.
+The time-evolution propagator  describes the time-ordered, coherent process of Landau-Zener tunneling/transmission (as described by the scattering matrix of \q{scattmat}) and adiabatic dynamics:
+
+%The two scattering matrices for both Dirac points are identical by $\mathfrak{c}_2$ symmetry; so are the two diagonal propagators corresponding to the left and right halves of the adiabatic dynamics.
+
+% \footnote{due to this field-independent phase, it is not necessary that $\delta\lambda_+=-\delta\lambda_-$}
+
+The necessary and sufficient condition for a degeneracy of $\cala$ is \begin{align}\tau\cos\bigg(\f{\tilde{\lambda}_+{+}\tilde{\lambda}_-}{2}+\bar{\varphi}\bigg)= \begin{cases} 0, & {\A}=+I \\
+                 \pm 1, & \A =-I\end{cases}.\la{c2breakdowndgncondition}
+\end{align}
+The adiabatic limit is given by $\tau{=}1$ and $\bar{\phi}{=}0$, which leads to the satisfaction of \q{c2breakdowndgncondition} for $l^2$ equal to an integer multiple of $2\pi/\delta S$.
+As noted  in \s{sec:introducecodimension}, such a periodicity  corresponds to a differential increment of a single, magnetic flux quantum.
+
+Deviating from the adiabatic limit ($\tau{<}1$), we deduce from \q{c2breakdowndgncondition} that only $\A{=}I$ remains attainable by varying $B$; this is consistent with the codimension analysis of \q{proprashba}.
+The conditions $\A{=}I$ and $\rho{>}0$ are interpreted as a destructive interference of the two Feynman paths [illustrated in \red{[Fig]}] that an electron may take in tunneling between bands (over one cyclotron period) -- effectively, there are then two identical and independent orbits, which lead to a Landau-level quasidegeneracy.
+Such quasidegeneracies occur with  a periodicity in $l^2$ of $4\pi/\delta S$ (or two flux quanta).
+This periodicity is not affected by the additional phase $\bar{\phi}$ in the argument of the cosine function, because $\bar{\phi}$  varies on the scale  $2\pi/S_{\sma{\square}}$ [with  $S_{\sma{\square}}$ the area of the rectangle inscribed between the two hyperbolic arms  in Fig.\ \ref{fig:Cn-breakdown} (a)],\footnote{For $\bar{\varphi}(\bar{\mu})$ to vary  $\sim 1$, the Landau-Zener parameter $\bar{\mu}$ must vary by $\sim 1$;\footnote{See Fig.\ 10 in 100page} moreover, $2\pi\barmu{:}{=} (2\pi/8) l^2S_{\sma{\square}}$.[AALG]} which is much larger than
+ $4\pi/\delta S$. To recapitulate, half the Landau-level quasi-crossings (over the $B$ axis) are destabilized by tunneling; the robustness of the other half relies on $\mathfrak{c}_2$ symmetry.
+
 %The degeneracies alternate between $\cala{=}I$ and ${-}I$ on the B axis, hence the subset of degeneracies corresponding to $\cala{=}I$ (or ${-}I$) occur with a period of  $4\pi/\delta S$ (or two flux quanta).
@@
 
-Let us investigate the fate of these degeneracies as $\rho$ increases.
+%Let us investigate the fate of these degeneracies as $\rho$ increases.
 While asymmetric interband tunneling generically destabilizes all degeneracies, we will demonstrate that two-fold-symmetric interband tunneling destabilizes only half of them.
-Indeed, the necessary condition for $\A\propto I$ is \e{\tau\cos(\f{\lambda_+'{+}\lambda_-'}{2}+\bar{\varphi})=\pm 1,0.\la{c2breakdowndgncondition}}
-for $\rho{>}0$, only 0 in Eq. (\ref{c2breakdowndgncondition}) is possible, destabilizing half of the degeneracies. \footnote{Notice cosine function reaches 0 twice in a period}
-
-Eq.
+Indeed,
+
+%for $\rho{>}0$, only 0 in Eq. (\ref{c2breakdowndgncondition}) is possible, destabilizing half of the degeneracies. \footnote{Notice cosine function reaches 0 twice in a period}
+
+%Eq.
 (\ref{c2breakdowndgncondition}) with $0$ on the right hand side is the condition for destructive interference of the two Feynman paths that contribute to interband tunneling (as illustrated in \red{[Fig]}); this occurs with a period  of   $4\pi /\delta S$ (or two flux quanta).
-To appreciate this, consider that  for $(\lambda_+'{+}\lambda_-')/2$ to vary by $\pi$, $l^2$ must vary by $4\pi/\delta S$.
-On the other hand, the field dependence of the scattering phase is comparatively negligible: for $\bar{\varphi}(\bar{\mu})$ to vary  $\sim 1$, the Landau-Zener parameter $\bar{\mu}$ must vary by $\sim 1$;\footnote{See Fig.\ 10 in 100page} moreover, $2\pi\barmu{:}{=} (2\pi/8) l^2S_{\sma{\square}}$ with  $S_{\sma{\square}}$ the area of the rectangle inscribed between the two hyperbolic arms  (see inset of Fig.
-\ref{fig:Cn-breakdown} (a)); clearly $S_{\sma{\square}}{\ll}\delta S$.
 
@@
 
-An analogous model with $\mathfrak{c}_3$-related II-Dirac points  is illustrated in Fig.
+For our last illustration, we consider a II-Dirac model with $\mathfrak{c}_3$  symmetry, as   is illustrated in Fig.
 \ref{fig:Cn-breakdown}(b).
-The corresponding propagator $\A$ has a form analogous to \q{propC2breakdown} -- but with $(\cdot)^2$ replaced by $(\cdot)^3$, and with $\lambda_\pm'{=}\pm l^2\delta S/4$ replaced by $\pm l^2\delta S/6$ (plus a field-dependent geometric correction).
-The degeneracy condition is accordingly modified as $\tau\cos[(\lambda_+'{+}\lambda_-')/2{+}\bar{\varphi}]=\pm 1,\pm 1/2$.
-For nonzero tunneling ($\rho {>}0$), only $\pm 1/2$ is reachable where, of every three degeneracies that exist in the adiabatic limit ($\rho=0$), only two persist.
-$\tau=1/2$ marks a critical point where all degeneracies coalesce pairwise (on the $B$ axis) and annihilate.
-It is not hard to imagine the claim made in Sec.
-\ref{sec:singleparameterrashba} remains true: out of every $N$ degeneracies, $N-1$ of them are stable against $\mathfrak{c}_N$-symmetric breakdown (see App.
-\ref{app:codimension} for a proof).
+The corresponding propagator $\A$ has a form analogous to \q{propC2breakdown} -- but with $(\cdot)^2$ replaced by $(\cdot)^3$, and with $\tilde{\lambda}_\pm{=}\pm l^2\delta S/4$ replaced by $\pm l^2\delta S/6$ (plus a field-dependent geometric correction).
+The degeneracy condition is  modified to $\tau\cos[(\tilde{\lambda}_+{+}\tilde{\lambda}_-)/2{+}\bar{\varphi}]{=}{\pm} 1,{\pm} 1/2$.
+With nonzero tunneling ($\rho {>}0$), only $\pm 1/2$ is attainable -- this implies that of every three degeneracies that exist in the adiabatic limit, only two are perturbatively stable.
+Beyond a critical field  (defined by $\tau{=}1/2$),   all degeneracies coalesce pairwise (on the $B$ axis) and annihilate.
+
+We conclude this section with a general result that is valid for any integer $N{\geq}2$: of every $N$ quasi-crossings that exist in the adiabatic limit, $N{-}1$ of them are stable against tunneling that respects  $\mathfrak{c}_N$ symmetry.
+We prove this in App.
+\ref{app:codimension}.
 %$\cala{=}{\pm} I$ is attained if and only if  $\tau \cos(\delta \lambda_+{+}\bar{\varphi}){=}{\mp}1/2$.
@@
 
-\textbf{A different realization of two-fold symmetric breakdown: angular magnetoresistance oscillations.}
-\red{[I begin to question this again.
+\textbf{Bonus: A different realization of two-fold symmetric breakdown: angular magnetoresistance oscillations.}
+%\red{[I begin to question this again.
 In my previous understanding, the in-plane magnetic field changes the band structure while the out-of-plane magnetic field produces LLs.
@@
 \begin{equation}
-\calh(t)\approx\alpha k_F \omega_c t\sigma_x+(Z_\parallel-\alpha k_F)\sigma_y-Z_\perp\sigma_z.
+\calh(t)\approx-\alpha k_F \omega_c t\sigma_x+(Z_\parallel-\alpha k_F)\sigma_y-Z_\perp\sigma_z.
 \end{equation}

### 2018-09-23 paper.tex
Updates from ShareLaTeX

@@
 (\ref{eq:rule}) (black lines) and numerical diagonalization of the Peierls-Onsager Hamiltonian  $H_{RD}(\bK)$ (red dots).
-Parameters for (b): $\alpha=0.05$(eV$\cdot$\AA), $m=0.01$($\hbar^2$/eV$\cdot$\AA$^2$), $\beta=0.02~(0.04)$(eV$\cdot$\AA) for left (right) panels.
+Parameters for (b): $\alpha=7.5$($10^{5}$cm$\cdot \hbar$/s), $m=0.076m_e$, $\beta=3~(6)$($10^{5}$cm$\cdot \hbar$/s) for left (right) panels.
 (c) For various spin-orbit parameters $(\alpha,\beta)$ of the Rashba-Dresselhaus model and various field strength (satisfying $l^2S(E)\gg 1$), we plot  $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that lies closest to energy $E=0.4eV$, where $\epsilon_\text{rule}$ is determined by Eq.
@@
 We also plot in (d) $l^2\delta S^2/S$, which has a strong positive relation with error in (c).
-Parameters for (c-d): $m=0.01$($\hbar^2$/eV$\cdot$\AA$^2$).
-Units: $\alpha$($10^{-2}$eV$\cdot$\AA), $\beta$($10^{-2}$eV$\cdot$\AA), $Z$($10^{-3}$eV), $l^2 S$($10^2$).\label{fig:RD}}
+Parameters for (c-d): $m=0.076m_e$.
+Units: $\alpha$($1.5\times 10^{5}$cm$\cdot \hbar$/s), $\beta$($1.5\times 10^{5}$cm$\cdot \hbar$/s), $Z$($10^{-3}$eV), $l^2 S$($10^2$).\label{fig:RD}}
 \end{figure}
@@
 Corresponding $l^2 \delta S^2/S$ are plotted in right panel.
-We only plotted in region where $0.4<\epsilon_0<1.0$(eV).\cite{RZfignote} Parameters for (d): $m$: 0.01$\hbar^2$/eV$\cdot$\AA$^2$, $l=100$\AA.
+We only plotted in region where $0.4<\epsilon_0<1.0$(eV).\cite{RZfignote} Parameters for (d): $m=0.076m_e$, $l=100$\AA.
 \label{fig:RZ}}
@@
 (\ref{calHRZ})] into sums of Pauli matrices ($\calh{=}\sum_jd_j\sigma_j$) defines a three-vector $\bd{=}({-}\alpha k_y$,$Z_\parallel{+}\alpha k_x,{-}Z_\perp$).
- $\phi_{\pm}^B$  equals half the solid angle subtended by   ${\pm} \bd(\bk)$ \textbf{[I wasn't  careful about minus signs here]} as $\bk$ is varied along the outer/inner orbit.[Berry]   These angles are indicated in the figure by blue outlines.\label{fig:blochsphere}}
+ $\phi_{\pm}^B$  equals half the solid angle subtended by   ${\pm} \bd(\bk)$ as $\bk$ is varied along the outer/inner orbit.[Berry]   These angles are indicated in the figure by blue outlines.\label{fig:blochsphere}}
 \end{figure}

### 2018-09-24 paper.tex
Updates from ShareLaTeX

@@
 (\ref{eq:rule}) (black lines) and numerical diagonalization of the Peierls-Onsager Hamiltonian  $H_{RD}(\bK)$ (red dots).
-Parameters for (b): $\alpha=7.5$($10^{5}$cm$\cdot \hbar$/s), $m=0.076m_e$, $\beta=3~(6)$($10^{5}$cm$\cdot \hbar$/s) for left (right) panels.
+Parameters for (b): $\alpha=7.5$($10^{5}$cm/s$\cdot\hbar$), $m=0.076m_e$, $\beta=3~(6)$($10^{5}$cm/s$\cdot\hbar$) for left (right) panels.
 (c) For various spin-orbit parameters $(\alpha,\beta)$ of the Rashba-Dresselhaus model and various field strength (satisfying $l^2S(E)\gg 1$), we plot  $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that lies closest to energy $E=0.4eV$, where $\epsilon_\text{rule}$ is determined by Eq.
@@
 Parameters for (c-d): $m=0.076m_e$.
-Units: $\alpha$($1.5\times 10^{5}$cm$\cdot \hbar$/s), $\beta$($1.5\times 10^{5}$cm$\cdot \hbar$/s), $Z$($10^{-3}$eV), $l^2 S$($10^2$).\label{fig:RD}}
+Units: $\alpha$($1.5\times 10^{5}$cm/s$\cdot\hbar$), $\beta$($1.5\times 10^{5}$cm/s$\cdot\hbar$), $l^2 S$($10^2$).\label{fig:RD}}
 \end{figure}
@@
 The wavefunction along the inner (resp.\ outer) component of the trefoille orbit has its pseudospin aligned parallel (resp.\ anti-parallel) to the spin-orbit field.
-(b) Black dashed lines illustrate a zeroth-order approximation of the Landau levels (assuming Klein tunneling); the leading-order correction is indicated by red lines.
-Exact Landau levels by numerical diagonalization are plotted as green dots.
-The Dirac point lies at $6.4$eV.
-Parameters for (b): $m$: 0.05$\hbar^2$/eV$\cdot$\AA$^2$, $\alpha$: 0.05eV$\cdot$\AA, $Z_\parallel$: 0.04eV.
+(b) Oscillation of $\delta E_n$ [cf.
+Eq.
+(\ref{RZfirstorderE})] for even integer $n$ with respect to magnetic field calculated by Eq.
+(\ref{RZfirstorderE}) (black dashed line) and numerical diagonalization (red solid line).
+$\delta E$ is extracted at 0.45eV and the II-Dirac point is located at 0.5eV.
+Parameters for (b): $m$: 0.076$m_e$, $\alpha$: 1.5($10^{5}$cm/s$\cdot\hbar$), $Z_\parallel$: 1meV.
+Out of plane Zeeman coupling is ignored here.
 (c) A sketch of cyclotron orbits of Rashba Hamiltonian with in-plane magnetic field.
@@
 Corresponding $l^2 \delta S^2/S$ are plotted in right panel.
-We only plotted in region where $0.4<\epsilon_0<1.0$(eV).\cite{RZfignote} Parameters for (d): $m=0.076m_e$, $l=100$\AA.
-\label{fig:RZ}}
+We only plotted in region where $0.4<\epsilon_0<1.0$(eV).\cite{RZfignote}, Units: $\alpha$($1.5\times 10^{5}$cm/s$\cdot\hbar$).
+Parameters for (d): $m=0.076m_e$, $l=100$\AA.
+\label{fig:RZ}}.
 \end{figure}
@@
 We focus first on the regime where, on average (over $\frako_0$), the energy splitting $|\delta \var_+{-}\delta \var_-|$ [cf.\ \q{eq:RZ-Hamiltonian}] is much greater than $B_\perp|\calm_{\sma{+-}}|$.
-This implies that the split orbits do not appreciably hybridize -- except in the vicinity of the II-Dirac point where orbits (nearly) touch.
+Equivalently, we are in the regime where $\alpha k_{\sma{E}}{\gg}\var_c$.\footnote{The orbit-averaged energy splitting is of order $\alpha k_{\sma{E}}$ for energies near the Dirac point.
+$B_\perp|\calm_{\sma{+-}}|$ is simply the Berry contribution to the Zeeman interaction, and has the form of the right-most term in \q{rashbaeffham}; this term is of order $\var_c$.} This implies that the split orbits do not appreciably hybridize -- except in the vicinity of the II-Dirac point where orbits (nearly) touch.
 Near this touching point (where $t{=}0$), the dynamics of a spinor electron is described by linearizing $\H$ [cf.\ \q{calHRZ}] with respect to $t$:
@@
 To derive the above equation, we have utilized $\phi^B_-{+}\phi^B_+{=}0$, which is valid for any two-band model in the quasidegenerate regime\footnote{For two band models, Berry phases of the two bands sum up to 0 on arbitrary path}; in \fig{fig:blochsphere} this is reflected in the sum of solid angles (at fixed energy) equalling $4\pi$.
-\q{trefoillerule} may be interpreted as a quantization rule for a trefoille-shaped orbit with net action $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels, as plotted with dashed lines in Fig.\ \ref{fig:RZ}(b), are  periodic in $E{\rightarrow}E{+}\pi/l^2(\partial S/\partial E)$ and in $l^2{\rightarrow}l^2{+}\pi/S$.
-Both periods are approximately half that of either disconnected spin-orbit-split orbit, in the assumed quasidegenerate regime $\delta S{\ll}S$.
+\q{trefoillerule} may be interpreted as a quantization rule for a trefoille-shaped orbit with net area $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels are periodic in $E{\rightarrow}E{+}\pi/l^2(\partial S/\partial E)$ and in $l^2{\rightarrow}l^2{+}\pi/S$.
+Both periods are approximately half that of either disconnected  orbit, in the assumed quasidegenerate regime $\delta S{\ll}S$.
 The $\pi$ correction in \q{trefoillerule} is the Berry phase associated to a $2\pi$ rotation of the wavefunction spin over a single trefoille orbit, as illustrated in Fig.
@@
 
-To recapitulate, $E_n^0(B)$ [cf.\ \q{trefoillerule}] exhibits a periodicity on short scales associated to the large action of the trefoille orbit.
-This small-scale periodicity is lost due to  finite-$\tau$ corrections, yet a longer-range correlation (associated to the smaller differential action $\delta S$ between spin-split orbits) persists, as shown by the first-order-in-$\tau$ correction:\footnote{The general form of this perturbative calculation can be found in Sec.
+To recapitulate, $E_n^0(B)$ [cf.\ \q{trefoillerule}] exhibits a periodicity on short scales associated to the large area of the trefoille orbit.
+This short-scale periodicity is lost due to  finite-$\tau$ corrections, yet a longer-range correlation (associated to the smaller differential action $\delta S$ between spin-split orbits) persists, as shown by the first-order-in-$\tau$ correction:\footnote{The general form of this perturbative calculation can be found in Sec.
 IX-E of [100page].}
 \e{&\delta E_n(B) = \f{(-1)^{n+1}}{2\pi} \tau \var_c \cos\bigg(\f{l^2\delta S}{{2}}+\f{\phi_+^B-\phi_-^B}{2}-\bar{\varphi}\bigg) \lin
-    &\substack{\sma{Z_{\perp}{\rightarrow}0}\\ \approx} \f{(-1)^{n+1}}{4\sqrt{2\pi}}  \var_c \f{(E-\epsilon_0)l}{\alpha(\epsilon_0/Z_{\parallel})^{3/2}}\cos\bigg(\f{l^2\delta S}{{2}}-\bar{\varphi}\bigg),\label{RZfirstorderE}}
-with the right-hand side (of each line) evaluated at $E_n^0(B)$.
-The second line of \q{RZfirstorderE} has greater utility where $m{\ll}m_0$.
-\red{This first order corrections of Landau levels are plotted in Fig.
-\ref{fig:RZ}(b) as red solid lines.
-The oscillation in Eq.
-(\ref{RZfirstorderE}) cannot be observed due to the smallness of $\delta S$.
-However, as expected from Eq.
-(\ref{RZfirstorderE}), first order correction have alternative signs for every Landau levels, which is confirmed by exact diagonalization [cf.
-Fig.
-\ref{fig:RZ}](b).}
-
-If the quasidegenerate orbits are appreciably hybridized ( $|\delta \var_+{-}\delta \var_-|{\lesssim}B_\perp|\calm_{\sma{+-}}|$ on average), our quantization rule \qq{eq:rule}{eq:H1} remains valid but the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}.
+    &\approx \f{(-1)^{n+1}}{4\sqrt{2\pi}}  \var_c \f{(E-\epsilon_0)l}{\alpha(\epsilon_0/Z_{\parallel})^{3/2}}\cos\bigg(\f{l^2\delta S}{{2}}-\bar{\varphi}\bigg),\label{RZfirstorderE}}
+with the right-hand side (of each line) evaluated at $E{=}E_n^0(B)$.
+The second line is an approximation for $Z_{\perp}{\rightarrow}0$, and has greater utility where $m{\ll}m_0$.
+\red{Eq.
+(\ref{RZfirstorderE}) are compared with numerical diagonalization Fig.
+\ref{fig:RZ}(b) with even integers $n$.}
+
+%( $|\delta \var_+{-}\delta \var_-|{\lesssim}B_\perp|\calm_{\sma{+-}}|$ on average)
+
+If the quasidegenerate orbits are appreciably hybridized ($\alpha k_{\sma{E}}{\lesssim}\var_c$), our quantization rule \qq{eq:rule}{eq:H1} remains valid but the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}.
 We may anyway diagonalize $\cala$ numerically, and compare the resultant semiclassical Landau levels with the exact diagonalization of $H_{RZ}(\boldsymbol{K})$; to our knowledge, there exists no analytic solution of $H_{RZ}(\boldsymbol{K})$ for generic values of $\alpha,\zpar$ and $B_{\perp}$.
@@
 
-For the special case of $\alpha{=}0$, the spectra of $H_{RZ}(\boldsymbol{K})$ and $\mathcal{A}[\mathfrak{o}]$ are both exactly soluble, hence it is possible to verify that the exact and semiclassical Landau levels match perfectly for every level index $n$ without any approximation; the latter is obtained from our rule [Eq.\ (\ref{eq:rule})], with the eigenphases of $\A$ equal to
-\e{\lambda_{\pm}{=}{\pm} 2\pi ml^2\sqrt{\f{Z_\parallel^2}{\hbar^4}{+}\f{g_\text{eff}^2}{16m^2l^4}}.}
+%For the special case of $\alpha{=}0$, the spectra of $H_{RZ}(\boldsymbol{K})$ and $\mathcal{A}[\mathfrak{o}]$ are both exactly soluble, hence it is possible to verify that the exact and semiclassical Landau levels match perfectly for every level index $n$ without any approximation; the latter is obtained from our rule [Eq.\ (\ref{eq:rule})], with the eigenphases of $\A$ equal to
+%\e{\lambda_{\pm}{=}{\pm} 2\pi ml^2\sqrt{\f{Z_\parallel^2}{\hbar^4}{+}\f{g_\text{eff}^2}{16m^2l^4}}.}
 
@@
 $\partial \lambda_a/\partial l^2$ is estimated in \app{sec:slowvariation}, and
-$T_{l^2}$ above is the period of quantum oscillations (in the absence of spin-orbit coupling).
+$T_{l^2}$ above is the period (in $l^2$) of quantum oscillations -- in the absence of spin-orbit coupling.
 To recapitulate, for every exact degeneracy of $\cala$, there must exist, in close proximity, a number of paired Landau levels which are exactly degenerate, or nearly degenerate in the sense of \qq{llquasideg}{llquasidegB}.
@@
 Analogously, it is well known (as the non-crossing rule in quantum theory[von Neumann,wigner]) that eigenvalue-degeneracies of complex, finite-dimensional matrix Hamiltonians are also attainable by tuning three real parameters.
- To prove the non-crossing rule for two-by-two unitaries, we begin by decomposing any such matrix as $\A{=}e^{i\phi}{\cal \bar{A}}$, such that  ${\cal \bar{A}}{\in}\text{SU}(2)$ being equal to $\pm I$ is a necessary and sufficient condition for an eigenvalue-degeneracy of $\A$.
+ To prove the non-crossing rule for two-by-two unitaries, we begin by decomposing any such matrix as $\A{=}e^{i\phi}{\cal \bar{A}}$, with  ${\cal \bar{A}}{\in}\text{SU}(2)$.
+Then the necessary and sufficient condition for an eigenvalue-degeneracy of $\A$ is that ${\cal \bar{A}}{=}{\pm}I$.
 In the canonical parametrization of $\text{SU}(2)$ over the three-sphere $S^3$:
 \e{{\cal \bar{A}}{=}\matrixtwo{r_1{+}ir_2}{r_3{+}ir_4}{{-}r_3{+}ir_4}{r_1{-}ir_2},\;\; \sum_{j=1}^4r_j^2{=}1,\;\; r_j\in \mathbb{R},  \la{s3}}
-${\cal \bar{A}}{=}{\pm}I$ lie on distinct points of $S^3$, and are attainable by tuning three real parameters: $r_3{=}r_4{=}0$, and the phase of $r_1{+}ir_2$ must equal $0$ or $\pi$.
+${\cal \bar{A}}{=}{\pm}I$ lie on distinct points of $S^3$, and are attainable by tuning three real parameters: $r_2{=}r_3{=}r_4{=}0$.
 The conclusion that three parameters need be tuned remains valid for any  non-singular parametrization of SU$(2)$.
@@
 
-At finite field (assumed to be homogeneous in space and time), any remnant  symmetry (denoted $g$) must preserve the component of the magnetic moment in the direction of  $\bB$.
+Any symmetry $g$ that remains at finite field (assumed to be homogeneous in space and time) must preserve the component of the magnetic moment in the direction of  $\vec{B}$.
 The magnetic moment is odd under time reversal, and behaves as a pseudovector under spatial transformations.[sakurai] Therefore, either (i) $g$  preserves both the direction of time and the magnetic moment, or (ii) $g$ inverts both said objects.
@@
 We see that rotational symmetry reduces the codimension of the origin from two to one.
-Here, and in the  Landau-level problem, we define codimension with respect to a \textit{symmetrically-chosen coordinates} (if symmetry exists).
-We do not require that the symmetric coordinates is globally defined, e.g., the polar coordinates is not well-defined where the radial coordinate vanishes.
+Here, and in the  Landau-level problem, we define codimension with respect to a \textit{symmetrically-chosen coordinates} (if symmetry exists); such symmetric coordinates need not be well-defined at isolated high-symmetry points, just as the polar coordinates are not well-defined at the rotational center.
 
@@
 To understand why rotational symmetry reduces codimension in the Landau-level problem, we return to the Rashba model [cf.
-\ \q{eq:Rashba-Hamiltonian}] absent Dresselhaus spin-orbit coupling and in-plane Zeeman field.
+\ \q{eq:Rashba-Hamiltonian}] without in-plane Zeeman field.
 This model has a continuous rotational symmetry (denoted $\mathfrak{c}_{\infty}$), which manifests as the constancy of $\calh(\bk){:}{=}\sum_{j=1}^3r_j\tau_j$ over the circular zeroth-order orbit [cf.\ \q{rashbaeffham}]; here, $\br{=}(r_1,r_2,r_3)$ is a real three-vector and $\{\tau_j\}$ a set of Pauli matrices.
-Consequently, the propagator  simplifies to  the exponential form:
-\e{\A{=}e^{-i2\pi\sum_{j}r_j\tau_j}, \;\;(r_1,r_3){=}\bigg(\f{g_{\sma{\text{eff}}}}{4}{-}\f1{2},\f1{2}{-}\f{\alpha k_{\sma{E}}}{\var_c}\bigg).\la{expform}} 
-$r_2{=}0$ in the Rashba model, but nonzero $r_2$ corresponds to a symmetry-allowed deformation that we allow for greater generality -- any $SU(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}]  for some (possibly non-unique) $\br$, which may be identified as the symmetric  coordinates.
+Consequently, the propagator [cf.\ \q{eq:prop}]  simplifies to  the exponential form:
+\e{\A{=}e^{-i2\pi\sum_{j}r_j\tau_j}, \;\;\br{=}\bigg(\f{g_{\sma{\text{eff}}}}{4}{-}\f1{2},0,\f1{2}{-}\f{\alpha k_{\sma{E}}}{\var_c}\bigg).\la{expform}}
+Any $SU(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}]  for some (possibly non-unique) $\br$, with $r_2$ not necessarily zero.
+We will demonstrate codimension reduction for the general form of $\A$ (having any $\br$), with the Rashba model as a particular realization.
+
+%Nonzero $r_2$ corresponds to a symmetry-allowed deformation that we allow for greater generality -- any $SU(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}]  for some (possibly non-unique) $\br$, which may be identified as the symmetric  coordinates.
 
@@
 
-All degeneracies of $\A$ occur on spheres in $\br$-space with radii equal to an integer ($j$)  multiple of $1/2$;  ${j}$ equals a nonnegative, even (resp.\ positive, odd) integer for  $\A{=}I$ (resp.\ $\A{=}{-}I$).
-The zero-radius sphere (i.e., a point) has codimension three, as would be expected if symmetry were absent.
-This point degeneracy can be understood from an elementary result in quantum mechanics: taking $\alpha{=}r_2{=}0$ \textit{and} $m{=}m_0$, we recover the Zeeman-split Landau levels of a free electron gas without spin-orbit coupling; all levels (except the lowest) are spin-degenerate owing to the equality of the Zeeman and cyclotron energies.[LandauLifshitzstatphysI]
-
-All other spheres are unit-codimensional surfaces (known as hypersurfaces), whose stability rely on $\mathfrak{c}_{\infty}$ symmetry.
+All eigenvalue-degeneracies of $\A$ occur on spheres in $\br$-space with radii $|\br|{=}\sqrt{r_1^2{+}r_2^2{+}r_3^2}$ equal to an integer ($j$)  multiple of $1/2$;  ${j}$ is even (resp.\  odd) for  $\A{=}I$ (resp.\ $\A{=}{-}I$).
+This condition $|\br|{=}j/2$ (for any nonzero $j$) may be attained by tuning a single parameter.
+In other words,
+all nonzero-radius spheres are unit-codimensional surfaces (known as hypersurfaces), whose stability rely on $\mathfrak{c}_{\infty}$ symmetry.
 These hypersurfaces separate $\br$-space into infinitely-many, distinct connected components, i.e., the zeroth homotopy group $\pi_0$ comprises an infinite set.
@@
 
+The zero-radius sphere (i.e., a point) has codimension three, as would be expected if symmetry were absent [cf.\ \s{sec:introducecodimension}].
+This point degeneracy can be understood from an elementary result in quantum mechanics: taking $\alpha{=}r_2{=}0$ \textit{and} $m{=}m_0$, we recover the Zeeman-split Landau levels of a free electron gas without spin-orbit coupling; all levels (except the lowest) are spin-degenerate owing to the equality of the Zeeman and cyclotron energies.[LandauLifshitzstatphysI]
+
 %Equivalently stated, at fixed energy there exists a series of Landau-level quasi-crossings as a function of $B$.
 
-The above discussion is reminiscent of topological (semi)metals which host Dirac-Weyl points and/or line nodes (of Bloch-Hamiltonian degeneracies).
+%The above discussion is reminiscent of topological (semi)metals which host Dirac-Weyl points and/or line nodes (of Bloch-Hamiltonian degeneracies).
 Weyl points in 3D $\bk$-space have codimension three and do not require any crystallographic point-group symmetry for their stability.
@@
 
+The above discussion is reminiscent of topological (semi)metals which host Dirac-Weyl points and/or line nodes (of Bloch-Hamiltonian degeneracies).
+Both Dirac points (in 2D $\bk$-space, e.g., graphene) and  line nodes (in 3D $\bk$-space) are attainable by tuning two wavenumbers; the stability of such codimension-two manifolds
+ relies on crystallographic point-group symmetries.
+On the other hand,  Weyl points in 3D $\bk$-space have codimension three and do not require any  point-group symmetry for their stability.
+Just like Weyl points, the point degeneracy of $\A$ is associated with a nontrivial Chern number (defined as an integral of the Berry curvature\footnote{The curvature is defined with respect to a line bundle formed from the nondegenerate eigenvector of $\cala$.} over a Gaussian surface surrounding the point).
+
 \begin{figure}
 \includegraphics[width=1.0\columnwidth]{dgn.png}
-\caption{Degeneracy manifolds of the Rashba-Dresselhaus model, with units: $\alpha l^2$($400$eV$\cdot$\AA$^3$), $\beta$($400$eV$\cdot$\AA$^3$), $g_{\sma{\text{eff}}}$(10), and parameters: $m=0.01\hbar^2$/(eV$\cdot$\AA$^2$) and $E=0.4$eV.
+\caption{ \textbf{please switch (a) and (b) to fit chronology of presentation} Degeneracy manifolds of the Rashba-Dresselhaus model, with units: $\alpha l^2$($400$eV$\cdot$\AA$^3$), $\beta$($400$eV$\cdot$\AA$^3$), $g_{\sma{\text{eff}}}$(10), and parameters: $m=0.01\hbar^2$/(eV$\cdot$\AA$^2$) and $E=0.4$eV.
 (a) illustrates the degeneracy manifold of $\A=-I$, which lie confined to  the $\alpha{=}0$ and $\beta{=}0$ planes.
@@
 Elsewhere, an electron undergoes adiabatic (band-conserving) dynamics.
-Due to the $\mathfrak{c}_2$ symmetry, the time-evolution propagator over the full cyclotron period is simply the square of the propagator for half the period:
+Due to $\mathfrak{c}_2$ symmetry, the time-evolution propagator over the full cyclotron period is simply the square of the propagator for half the period:
 \e{\A={e^{i(\tilde{\lambda}_++\tilde{\lambda}_-)}}\left(\matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}}{\diagmatrix{e^{i\f{\tilde{\lambda}_+-\tilde{\lambda}_-}{2}}}{e^{i\f{\tilde{\lambda}_--\tilde{\lambda}_+}{2}}}} \right)^2.
@@
 
+Generalizing our rotational-symmetric case studies in
 Sec.
-\ref{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown} illustrate that rotational symmetry imposes constraints on $\A$ and reduces codimension of its degeneracy manifold.
-This reduction of codimension is not limited to rotational symmetry.
-
-Since magnetic field $B$ is applied externally, it does not change under the action of any symmetry operation.
-Hence any symmetry relevant in current context must keep $k_x$-$k_y$ plane untouched.
+\ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown}, we now present the symmetry-constrained codimensions for all ten[topoferm] symmetry classes of orbits.
+Depending on the class, the codimension is either $0,1,2$ or $3$.
+We begin by briefly reviewing the ten-fold symmetry classification of orbits in \s{sec:reviewtenfold}.
+
+%Since magnetic field $B$ is applied externally, it does not change under the action of any symmetry operation.
+
+\subsubsection{Ten-fold classification of orbits}\la{sec:reviewtenfold}
+
+Any symmetry $g$ of a space group acts on space-time as
+\begin{align}
+&g: \vectwo{\br}{t} \rightarrow \matrixtwo{\check{g}^{-1}}{0}{0}{ (-1)^{s(g)}}\vectwo{\br}{t}+\vectwo{\bdelta}{0}, \la{definesg}
+\end{align}
+with $s(g){=}0$ (resp.\ $1$) if $g$ preserves (resp.\  reverses) the arrow of time.
+$\check{g}$ is the matrix representation of $g$ in real space, and the corresponding action of  $g$ on the crystal wavevector is
+\e{\bk \rightarrow g\circ\bk := (-1)^{s(g)}\check{g}\bk. \la{gmapk}}   
+We restrict our attention to the subset of $g$ (in the space group) that preserves all field-orthogonal $\bk$-planes, where the field-induced orbits  are confined.\textbf{[might say something different about 2DEG]}
+
+%We align the z-axis of our Cartesian coordinate system parallel to the field, such that field-induced dynamics is constrained within planes of constant $k_z$.
+
+%Hence any symmetry relevant in current context must keep $k_x$-$k_y$ plane untouched.
+
+Given any orbit $\frako_0$ within a plane (given by constant-energy and $k_z$ contours all bands), we may deduce from \q{gmapk} if  $g$ maps the orbit to itself (denoted as $|g\circ\frako_0|=|\frako_0|$) or to a distinct orbit.
+Moreover, whether $g$ preserves the direction of cyclotron orbit (denoted as $u(g)=0$) or not (denoted as $u(g)=1$) indicates whether the path-ordering in $\A$ needs to be inverted.
+
+then there exists a matrix representation of $g$ that relates $\A$ to itself (if u=1) or to its inverse (if u=-1).
+
+or not ($|g\circ\frako_0|\ne|\frako_0|$) determines whether a self constraint can be imposed on $\A$.
+The former case can be again divided into two types, one for $g$ mapping every $\bk$ on the orbit to itself and one for at least one $\bk$ on the orbit being mapped to another point.
+
  By definition, $\A$ is a path-ordered exponential along the cyclotron orbit of the two-by-two Hamiltonian $\H$ and $\H$ is composed of a scalar $\delta\epsilon$ and a pseudovector $B\mathcal{M}$.
-Whether the symmetry $g$ transforms the cyclotron orbit to itself (denoted as $|g\circ\frako_0|=|\frako_0|$) or not ($|g\circ\frako_0|\ne|\frako_0|$) determines whether a self constraint can be imposed on $\A$.
-The former case can be again divided into two types, one for $g$ mapping every $\bk$ on the orbit to itself and one for at least one $\bk$ on the orbit being mapped to another point.
-Moreover, whether $g$ preserves the direction of cyclotron orbit (denoted as $u(g)=0$) or not (denoted as $u(g)=1$) indicates whether the path-order in $\A$ needs to be inversed.
  Besides the transformation of orbits, the transformation of $\H$ is also significant in determining the transformation of $\A$.
@@
 
-With detailed codimension analysis delegated to App.
+\subsubsection{Symmetry-constrained codimension for quasidegenerate orbits}\la{sec:codimquasideg}
+
+With detailed codimension analysis relegated to App.
 \ref{app:codimension}, we present the result in table \ref{table:codimension}.
 To obtain a unique answer for codimension in some of the symmetry classes, we have to specify certain conditions for the symmetry representation: for $g$ that does not invert time ($s{=}0$), we specify certain conditions on  $\breve{g}$, the \emph{diagonalized} matrix representation  of $g$; for $g$ that inverts time  ($s{=}1$), we specify if the antiunitary representation of $g$ squares to $+I$ or $-I$.
-Codimension 0, 1, 2 and 3 can be readily recognized in table \ref{table:codimension}.
 $T\mathfrak{r}_{x,\boldsymbol{c}/2}$ ($\mathfrak{r}_{x,\boldsymbol{c}/2}$ is glide plane translating in $z$ direction for half a lattice vector after flipping $x$ direction) at $k_z=\pi$ is an example of codimension 0, corresponding to class-6 (the 6th class in the table) \red{[Notice that I changed the name of the class.
@@
 Hence an \textit{aperiodic} beating pattern is expected by tuning either $B$ or $E$.
+
+\subsubsection{Symmetry-constrained codimension for exactly-degenerate orbits}\la{sec:codimexactdeg}
 

### 2018-09-29 paper.tex
Updates from ShareLaTeX

@@
 Quasidegenerate orbits commonly originate from spin-orbit-splitting of energy bands in noncentrosymmetric solids.
-We provide an illustrative model of  a 2DEG with Rashba spin-orbit coupling:
+We provide an illustrative model of a two dimensional electron gas (2DEG) with Rashba spin-orbit coupling:
 \begin{equation}
@@
 \ref{app:quantizationruleproof}.
-$\hat{H}_0$ is commonly exemplified by  the Schr\"odinger Hamiltonian, and $\delta \hat{H}$ by a non-centrosymmetric spin-orbit interaction; alternatively, $\hat{H}_0$ may be a centrosymmetric Pauli Hamiltonian (with spin-orbit coupling), while $\delta H$ describes a lattice deformation that breaks the spatial-inversion symmetry.
-
-% The quantum theory of a Bloch electron in a magnetic field is based on the noncommutivity of the kinematic quasimomentum operators:[onsager, lifshitz]
+$\hat{H}_0$ is commonly exemplified by  the Schr\"odinger Hamiltonian, and $\delta \hat{H}$ by a non-centrosymmetric spin-orbit interaction; alternatively, $\hat{H}_0$ may be a centrosymmetric Pauli Hamiltonian (with spin-orbit coupling), while $\delta \hat{H}$ describes a lattice deformation that breaks the spatial-inversion symmetry.
 
@@
 \end{equation}
-$\delta \var$ is the projection of $\delta H$ to the quasidegenerate band associated to $\var(\bk)$, e.g., $\delta \var{=}\alpha(k_x\sigma_y{-}k_y\sigma_x)$ in the Rashba model.
+$\delta \var$ is the projection of $\delta \hat{H}$ to the degenerate band subspace of $\hat{H}_0$.
 In the basis of energy-split bands (which we label by ${+}$ and $-$ for bands corresponding to the outer and inner orbit respectively), $\delta \var$ is a diagonal matrix whose diagonal entries ($\delta \var_+,\delta \var_-$, corresponding to outer and inner orbit respectively; $\delta \var_+<\delta \var_-$) are related to the hybridization parameter:\footnote{The neglected term on the right-hand side of  \q{spinsplitwkb} is smaller (than the kept term) by a factor $\delta v_{\pm}/v$, which is the relative change in band speed $v=|\boldsymbol{v}|=\hbar^{-1}|\partial \var/\partial \bk|$ induced by the spin-orbit coupling.
@@
 
-%With intermediate hybridization , including the regime where Landau-Zener dynamics is non-applicable and breakdown is nonlocal.
-
 We begin again with the Rashba model of a rotationally-symmetric Dirac cone. To convert this Dirac point to its asymmetric variant, 
@@
 The wavefunction along the inner (resp.\ outer) component of the trefoille orbit has its pseudospin aligned parallel (resp.\ anti-parallel) to the spin-orbit field.
-(b) Oscillation of $\delta E_n$ [cf.
+(b) Upper panel: a sketch of Landau level dispersion near II-Dirac point of Rashba model with in plane Zeeman field in the weak hybridization limit.
+The dashed line representing first order solution [cf.
+Eq.
+(\ref{RZfirstorderE})] oscillates around the solid line [zeroth order solution, cf.
+Eq.
+({trefoillerule})].
+Due to the smallness of $\delta S$, the oscillation should not be observable in the scale of several Landau levels.
+Therefore, We exaggerate the oscillation frequency in the sketch.
+Lower panel: oscillation of $\delta E_n$ [cf.
 Eq.
@@
 $\delta E$ is extracted at 0.45eV and the II-Dirac point is located at 0.5eV.
-Parameters for (b): $m$: 0.076$m_e$, $\alpha$: 1.5($10^{5}$cm/s$\cdot\hbar$), $Z_\parallel$: 1meV.
+Parameters for lower panel of (b): $m$: 0.076$m_e$, $\alpha$: 1.5($10^{5}$cm/s$\cdot\hbar$), $Z_\parallel$: 1meV.
 Out of plane Zeeman coupling is ignored here.
 (c) A sketch of cyclotron orbits of Rashba Hamiltonian with in-plane magnetic field.
+Inset: illustration of $S_{\sma{\square}}$ by the purple rectangle.
 (d) For various configurations ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in left panel $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that is closest to $\epsilon_0$ in Eq.
@@
 We focus first on the regime where, on average (over $\frako_0$), the energy splitting $|\delta \var_+{-}\delta \var_-|$ [cf.\ \q{eq:RZ-Hamiltonian}] is much greater than $B_\perp|\calm_{\sma{+-}}|$.
-Equivalently, we are in the regime where $\alpha k_{\sma{E}}{\gg}\var_c$.\footnote{The orbit-averaged energy splitting is of order $\alpha k_{\sma{E}}$ for energies near the Dirac point.
+Equivalently, we are in the regime where $\alpha k_{\sma{E}}{\gg}\var_c^\perp$.\footnote{The orbit-averaged energy splitting is of order $\alpha k_{\sma{E}}$ for energies near the Dirac point.
 $B_\perp|\calm_{\sma{+-}}|$ is simply the Berry contribution to the Zeeman interaction, and has the form of the right-most term in \q{rashbaeffham}; this term is of order $\var_c$.} This implies that the split orbits do not appreciably hybridize -- except in the vicinity of the II-Dirac point where orbits (nearly) touch.
@@
 with $2\alpha k_E$ the spin-orbit splitting at energy $E$ [cf.\ \fig{fig:orbits}(a)].
+$\bar{\mu}$ has an alternative interpretation as the area of rectangle inscribed between the two hyperbolic arms $S_{\sma{\square}}$, as illustrated in the inset of Fig.
+\ref{fig:RZ}(c).
 In the absence of the out-of-plane Zeeman coupling ($Z_\perp{=}0$), $\bar{\mu}$ would vanish at the energy of the II-Dirac point -- leading to unit-probability Klein tunneling, as was first proposed by [Obrien] in a different model of the II-Dirac point.
@@
 (\ref{calHRZ})] into sums of Pauli matrices ($\calh{=}\sum_jd_j\sigma_j$) defines a three-vector $\bd{=}({-}\alpha k_y$,$Z_\parallel{+}\alpha k_x,{-}Z_\perp$).
- $\phi_{\pm}^B$  equals half the solid angle subtended by   ${\pm} \bd(\bk)$ as $\bk$ is varied along the outer/inner orbit.[Berry]   These angles are indicated in the figure by blue outlines.\label{fig:blochsphere}}
+ $\phi_{\pm}^B$  equals half the solid angle subtended by   ${\mp} \bd(\bk)$ as $\bk$ is varied along the outer/inner orbit.[Berry]   These angles are indicated in the figure by blue outlines.\label{fig:blochsphere}}
 \end{figure}
@@
 To derive the above equation, we have utilized $\phi^B_-{+}\phi^B_+{=}0$, which is valid for any two-band model in the quasidegenerate regime\footnote{For two band models, Berry phases of the two bands sum up to 0 on arbitrary path}; in \fig{fig:blochsphere} this is reflected in the sum of solid angles (at fixed energy) equalling $4\pi$.
-\q{trefoillerule} may be interpreted as a quantization rule for a trefoille-shaped orbit with net area $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels are periodic in $E{\rightarrow}E{+}\pi/l^2(\partial S/\partial E)$ and in $l^2{\rightarrow}l^2{+}\pi/S$.
+\q{trefoillerule} may be interpreted as a quantization rule for a trefoille-shaped orbit with net area $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels (sketched by solid lines in the upper panel of Fig.
+\ref{fig:RZ}(b)) are periodic in $E{\rightarrow}E{+}\pi/l^2(\partial S/\partial E)$ and in $l^2{\rightarrow}l^2{+}\pi/S$.
 Both periods are approximately half that of either disconnected  orbit, in the assumed quasidegenerate regime $\delta S{\ll}S$.
@@
 
-%To appreciate this, consider the regime $\rho^2{\lesssim}1$, where a single harmonic (corresponding to the trefoille orbit) is dominant.
-Viewing $\tau{=}\sqrt{1{-}\rho^2}$ as a small parameter, the zeroth-order Landau levels $E_n^0(B)$ [as obtained from \q{trefoillerule}] has been shown to be periodic in $E$ and $l^2$ (on short scales associated to the large-action trefoille orbit).
-
 To recapitulate, $E_n^0(B)$ [cf.\ \q{trefoillerule}] exhibits a periodicity on short scales associated to the large area of the trefoille orbit.
@@
 IX-E of [100page].}
-\e{&\delta E_n(B) = \f{(-1)^{n+1}}{2\pi} \tau \var_c \cos\bigg(\f{l^2\delta S}{{2}}+\f{\phi_+^B-\phi_-^B}{2}-\bar{\varphi}\bigg) \lin
-    &\approx \f{(-1)^{n+1}}{4\sqrt{2\pi}}  \var_c \f{(E-\epsilon_0)l}{\alpha(\epsilon_0/Z_{\parallel})^{3/2}}\cos\bigg(\f{l^2\delta S}{{2}}-\bar{\varphi}\bigg),\label{RZfirstorderE}}
+\e{&\delta E_n(B) = \f{(-1)^n}{2\pi} \tau \var_c^\perp \cos\bigg(\f{l^2\delta S}{{2}}+\f{\phi_+^B-\phi_-^B}{2}-\bar{\varphi}\bigg) \lin
+    &\approx \f{(-1)^{n+1}m\alpha^2(E-\epsilon_0)(\var_c^{\perp})^{1/2}}{2\sqrt{\pi}\hbar^2
+    Z_{\parallel}^{3/2}}\cos\bigg(\f{l^2\delta S}{{2}}-\bar{\varphi}\bigg),\label{RZfirstorderE}}
 with the right-hand side (of each line) evaluated at $E{=}E_n^0(B)$.
 The second line is an approximation for $Z_{\perp}{\rightarrow}0$, and has greater utility where $m{\ll}m_0$.
-\red{Eq.
-(\ref{RZfirstorderE}) are compared with numerical diagonalization Fig.
-\ref{fig:RZ}(b) with even integers $n$.}
-
-%( $|\delta \var_+{-}\delta \var_-|{\lesssim}B_\perp|\calm_{\sma{+-}}|$ on average)
+$E_n^{(0)}+\delta E_n$ are sketched in the upper panel of Fig.
+\ref{fig:RZ}(b) as dashed lines.
+The validity of Eq.
+(\ref{RZfirstorderE}) is confirmed by a comparison between $\delta E_n$ in Eq.
+(\ref{RZfirstorderE}) and $\delta E_n$ extracted from numerical diagonalization in the lower panel of Fig.
+\ref{fig:RZ}(b).
 
@@
 
-%For the special case of $\alpha{=}0$, the spectra of $H_{RZ}(\boldsymbol{K})$ and $\mathcal{A}[\mathfrak{o}]$ are both exactly soluble, hence it is possible to verify that the exact and semiclassical Landau levels match perfectly for every level index $n$ without any approximation; the latter is obtained from our rule [Eq.\ (\ref{eq:rule})], with the eigenphases of $\A$ equal to
-%\e{\lambda_{\pm}{=}{\pm} 2\pi ml^2\sqrt{\f{Z_\parallel^2}{\hbar^4}{+}\f{g_\text{eff}^2}{16m^2l^4}}.}
-
-%Together with Eq. (\ref{eq:rule}), $\lambda_\pm$ here generate exact the same Landau level spectrum as $H_{RZ}(\boldsymbol{K})$.
-
-%The above quantization rule is not applicable in the nonlocal-breakdown regime ($\Delta/\epsilon_c\sim1$).
-The appropriate rule is summarized in \qq{eq:rule}{eq:H1}, with $\delta \var$ encoding the change in band energies due to the spin-orbit coupling ($\sim \alpha$) and the in-plane Zeeman coupling ($\sim Z$); $\alpha,Z$ and $B$ are considered  small parameters.
-
-% Thus quasidegenerate quantization rule produces exact solution without Rashba spin-orbit coupling.
-After Rashba spin-orbit coupling is switched on, no analytic solution of $H_{RZ}(\boldsymbol{K})$ is known to our knowledge.
-Again, exact Landau levels are solved numerically and are compared with quantization rules (see Fig.
-\ref{fig:errors} (d-f)).
-Although $\alpha\ne 0$ in Fig.
-\ref{fig:errors} (f), accuracy of quantization rules is still largely independent of the choice of $Z$.
-
 \section{Tuning the spin-degeneracy of Landau Levels}\label{sec:llquasideg}
 
-We have argued in \s{sec:qtznrules} that the subleading corrections ($\lambda_{1,2}$) to the quantization rule [cf.\ \q{eq:rule}] generically lift the spin-degeneracy of Landau levels -- the level splitting is approximately $\var_c(\lambda_1{-}\lambda_2)/2\pi$.
+We have argued in \s{sec:qtznrules} that the subleading corrections ($\lambda_{1,2}$) to the quantization rule [cf.\ \q{eq:rule}] generically lift the spin-degeneracy of Landau levels -- the level splitting is approximately $\var_c\delta_\lambda/2\pi$ with $\delta \lambda=|\lambda_1-\lambda_2|$.
 Conversely, Landau levels are approximately spin-degenerate if $\lambda_1{=}\lambda_2$ (mod $2\pi$) -- this degeneracy condition for the eigenvalues of $\A$ may require fine-tuning of the Peierls-Onsager Hamiltonian.
@@
 For fixed $\bar{B}$, we are therefore guaranteed to find a number (of order one) of paired Landau levels  in close proximity to $\bar{E}$, with each pair having an energetic splitting of order:
-\e{ \bigg|\f{E_{1}-E_2}{\var_c}\bigg|_{B=\bar{B}} = \order\left( \f{\partial \lambda_a/\partial E}{\bar{l}^2\partial  S/\partial E}  \right)\ll 1.\la{llquasideg}}
+\e{\bigg|\f{E_{1}-E_2}{\var_c}\bigg|_{B=\bar{B}} = \order\left( \f{\partial \lambda_a/\partial E}{\bar{l}^2\partial  S/\partial E}  \right)\ll 1,\la{llquasideg}}
+with $\bar{l}$ magnetic length of $\bar{B}$.
 Alternatively, we may fix $\bar{E}$ and investigate how Landau levels disperse as a function of $B$; the analog of \q{llquasideg}  is the existence of paired Landau levels in close proximity to $\bar{l}^2$, with a splitting of order:
-\e{  \bigg|\f{l^2_{+}-l^2_-}{T_{{l^2}}}\bigg|_{E=\bar{E}} = O\left( \f{1}{S}\p{\lambda_a}{l^2} \right)\ll 1,\;\; T_{{l^2}}:=\f{2\pi}{S(\bar{E})}.\la{llquasidegB} }
+\e{\bigg|\f{l^2_{+}-l^2_-}{T_{{l^2}}}\bigg|_{E=\bar{E}} = O\left( \f{1}{S}\p{\lambda_a}{l^2} \right)\ll 1,\;\; T_{{l^2}}:=\f{2\pi}{S(\bar{E})}.\la{llquasidegB} }
 $\partial \lambda_a/\partial l^2$ is estimated in \app{sec:slowvariation}, and
@@
 Each such pair of Landau levels will be called \textit{quasidegenerate}.
-
-%where $\order(\ldots)$ denotes the order in magnitude of the largest argument; $m_0$ here is the free-electron mass, $m{=}\hbar^2|\partial S/\partial E|/2\pi$ the effective mass.
-
-%In the absence of any symmetry,  the ``non-crossing theorem'' [von Neumann,wigner] states that eigenvalue-degeneracies of complex Hamiltonians are attained by tuning three real parameters; this non-crossing rule applies also to Landau-level degeneracies of the Peierls-Onsager Hamiltonian.
-\textbf{[Questionable: the original theorem was proven for finite-dimensional Hamiltonians]}  Here, we would prove a stronger statement:
-
-%a non-crossing rule also applies to Landau-level quasidegeneracies. Equivalently, we would show that
 
@@
 
-It is well-known that symmetry may reduce the codimension of Hamiltonians, e.g., an antiunitary symmetry may restrict complex Hamiltonians to real Hamiltonians, thus reducing codimension from three to two.[wigner,von neumann] In our context, an analog would be the symmetry of band conservation in the adiabatic regime [cf.\ \s{sec:qtznrules}], which restricts $\cala$ to have diagonal form  ($r_3{=}r_4{=}0$) in the basis of energy bands [cf.\ \q{phaseindependentorbit}].
+It is well-known that symmetry may reduce the codimension of Hamiltonians, e.g., an antiunitary symmetry may restrict complex Hamiltonians to real Hamiltonians, thus reducing codimension from three to two.[wigner,von neumann] In our context, an analog would be the symmetry of band conservation in the adiabatic regime (cf.\ \s{sec:qtznrules}), which restricts $\cala$ to have diagonal form  ($r_3{=}r_4{=}0$) in the basis of energy bands [cf.\ \q{phaseindependentorbit}].
 The phase of $r_1{\pm}ir_2$ equals ${\pm} l^2\delta S/2$ plus field-independent corrections.
@@
 We may ask if these quasi-crossings (based on band-conservation symmetry) persist at stronger fields where adiabaticity breaks down.
-If no symmetry persists at finite field, then the codimension is three [cf.\ \q{s3}], hence Landau-level quasi-crossings should not generically be found by varying $B$ alone.
-
-Any symmetry $g$ that remains at finite field (assumed to be homogeneous in space and time) must preserve the component of the magnetic moment in the direction of  $\vec{B}$.
-The magnetic moment is odd under time reversal, and behaves as a pseudovector under spatial transformations.[sakurai] Therefore, either (i) $g$  preserves both the direction of time and the magnetic moment, or (ii) $g$ inverts both said objects.
-(i) is exemplified by a rotational symmetry with the rotational axis aligned parallel to the field, and (ii) by the composition  of time reversal $T$ and a spatial reflection $\mathfrak{r}_x$ (with reflection axis perpendicular to $\vec{B}$).
-
-One of our main results is that  rotational symmetry (of both discrete and continuous types) results in degeneracy manifolds with unit codimension.
+If no symmetry remains, then the codimension is three [cf.\ \q{s3}], hence Landau-level quasi-crossings should not generically be found by varying $B$ alone.
+One of our main results is that  rotational symmetry (with rotational axis parallel to the field) results in degeneracy manifolds with unit codimension.
 This will be demonstrated by two  case studies: the Rashba 2DEG in \s{sec:singleparameterrashba}, and a model with II-Dirac points in \ref{sec:rotsymmbreakdown}.
-In contrast,  $T\mathfrak{r}_x$ results in manifolds with codimension two.
+
+%The indicators defined above classifies symmetry operations into ten and only ten classes, presented in Tab.\ \ref{table:codimension}.
+
+%In contrast,  $T\mathfrak{r}_x$ results in manifolds with codimension two.
 The latter result, in addition to a comprehensive codimension analysis for all symmetry classes, is presented in \s{sec:tenfold}.
@@
 
-In this and the subsequent section [\s{sec:rotsymmbreakdown}], we will demonstrate how rotational symmetry reduces codimension in the Landau-level problem.
+In this and the subsequent section (\s{sec:rotsymmbreakdown}), we will demonstrate how rotational symmetry reduces codimension in the Landau-level problem.
 Before delving into this, it is instructive to consider the conceptually-simplest analog in differential geometry: if we parametrize the 2D plane by Cartesian coordinates $(x,y){\in}\R^2$, it is apparent that two parameters must be tuned to arrive at the origin.
@@
 Consequently, the propagator [cf.\ \q{eq:prop}] simplifies to the exponential form:
-\e{\A{=}e^{-i2\pi\sum_{j}r_j\tau_j}, \;\;\br{=}\bigg(\f{g_{\sma{\text{eff}}}}{4}{-}\f1{2},0,\f1{2}{-}\f{\alpha k_{\sma{E}}}{\var_c}\bigg).\la{expform}}
-Any $SU(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}]  for some (possibly non-unique) $\br$, with $r_2$ not necessarily zero.
+\e{\A{=}\exp(-2\pi i\sum_{j}r_j\tau_j),\la{expform}}
+where
+\e{\br=\f{\br_0(|\br_0|+\pi)}{|\br_0|},\br_0{=}\bigg(\f{g_{\sma{\text{eff}}}}{4}{-}\f1{2},0,-\f{\alpha k_{\sma{E}}}{\var_c}\bigg).}
+Any $\text{SU}(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}] for some (possibly non-unique) $\br$, with $r_2$ not necessarily zero.
 We will demonstrate codimension reduction for the general form of $\A$ (having any $\br$), with the Rashba model as a particular realization.
 
-%Nonzero $r_2$ corresponds to a symmetry-allowed deformation that we allow for greater generality -- any $SU(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}]  for some (possibly non-unique) $\br$, which may be identified as the symmetric  coordinates.
-
-%\textbf{[perhaps a footnote explaining this is a non-singular parametrization if no symmetry is imposed]}
-
-All eigenvalue-degeneracies of $\A$ occur on spheres in $\br$-space with radii $|\br|{=}\sqrt{r_1^2{+}r_2^2{+}r_3^2}$ equal to an integer ($j$)  multiple of $1/2$;  ${j}$ is even (resp.\  odd) for  $\A{=}I$ (resp.\ $\A{=}{-}I$).
+All eigenvalue degeneracies of $\A$ occur on spheres in $\br$-space with radii $|\br|{=}\sqrt{r_1^2{+}r_2^2{+}r_3^2}$ equal to an integer ($j$)  multiple of $1/2$;  ${j}$ is even (resp.
+odd) for  $\A{=}I$ (resp.\ $\A{=}{-}I$).
 This condition $|\br|{=}j/2$ (for any nonzero $j$) may be attained by tuning a single parameter.
@@
 
-%Equivalently stated, at fixed energy there exists a series of Landau-level quasi-crossings as a function of $B$.
-
-%The above discussion is reminiscent of topological (semi)metals which host Dirac-Weyl points and/or line nodes (of Bloch-Hamiltonian degeneracies).
-Weyl points in 3D $\bk$-space have codimension three and do not require any crystallographic point-group symmetry for their stability.
-Just like Weyl points, the point degeneracy of $\A$ is associated with a nontrivial Chern number (defined as an integral of the Berry curvature\footnote{The curvature is defined with respect to a line bundle formed from the nondegenerate eigenvector of $\cala$.} over a Gaussian surface surrounding the point).
-On the other hand,  both Dirac points (in 2D $\bk$-space, e.g., graphene) and  line nodes (in 3D $\bk$-space) have codimension two, hence their existence relies on point-group symmetries.
-
 The above discussion is reminiscent of topological (semi)metals which host Dirac-Weyl points and/or line nodes (of Bloch-Hamiltonian degeneracies).
@@
 \includegraphics[width=1.0\columnwidth]{dgn.png}
-\caption{ \textbf{please switch (a) and (b) to fit chronology of presentation} Degeneracy manifolds of the Rashba-Dresselhaus model, with units: $\alpha l^2$($400$eV$\cdot$\AA$^3$), $\beta$($400$eV$\cdot$\AA$^3$), $g_{\sma{\text{eff}}}$(10), and parameters: $m=0.01\hbar^2$/(eV$\cdot$\AA$^2$) and $E=0.4$eV.
-(a) illustrates the degeneracy manifold of $\A=-I$, which lie confined to  the $\alpha{=}0$ and $\beta{=}0$ planes.
+\caption{Degeneracy manifolds of the Rashba-Dresselhaus model.
+(a) The degeneracy manifold of $\A{=}I$ is a path-connected hypersurface.
+(b) illustrates the degeneracy manifold of $\A=-I$, which lie confined to  the $\alpha{=}0$ and $\beta{=}0$ planes.
 Each $\mathfrak{c}_{\infty}$-symmetric plane contains an infinite set of concentric, circular line degeneracies.
 Every circle (except for the smallest in either plane)  intersects two other circles in an orthogonal plane, such that the entire line node is path-connected.
-(b) The degeneracy manifold of $\A{=}I$ is a path-connected hypersurface.
 \label{fig:dgn}}
@@
 How robust are the above-mentioned Landau-level quasi-crossings  (over the $B$ axis) when $\mathfrak{c}_{\infty}$ symmetry is perturbatively reduced to $\mathfrak{c}_N$?
-For any  integer $N{\geq}2$, we find that $N{-}1$ of every $N$ quasi-crossings  are perturbatively stable, as proven in App.
-\ref{app:codimension}.
-
-For illustration, let us reduce $\mathfrak{c}_{\infty}$ symmetry to  $\mathfrak{c}_2$  by adding the Dresselhaus spin-orbit term (${\propto} \beta$) to the Rashba model [cf.\ \q{hamRD}].
-Since $\A$ depends on $\alpha,\beta,l$ only through $\alpha l^2$ and $\beta l^2$, let us consider the three-dimensional parameter space $(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_{\sma{\text{eff}}}){\in} \mathbb{R}^3$.
-$\A{=}{\pm} I$ determines a set of concentric circles in the $\beta{=}0$ plane, as per the $\mathfrak{c}_{\infty}$-symmetric case study in \s{sec:ctsrot}.
-Moving off this plane, we find that $\A{=}I$ is satisfied in a  neighborhood of $\beta{=}0$, i.e., $\A{=}I$ defines a hypersurface in $\mathbb{R}^3$ that is illustrated in \fig{fig:dgn}(b).
-On the other hand, $\A{=}{-}I$ is not satisfied in the neighborhood of $\beta{=}0$, hence the circles associated to $\A{=}{-}I$ remain isolated as line nodes, as illustrated in \fig{fig:dgn}(a).
+For any  integer $N{\geq}2$, we find that $N{-}1$ of every $N$ quasi-crossings  are perturbatively stable.
+This general statement is proven in App.
+\ref{app:codimension}, and here we illustrate it for a specific model of $N{=}2$ -- we will reduce the $\mathfrak{c}_{\infty}$ symmetry of the Rashba model [cf.\ \q{hamRD}] to  $\mathfrak{c}_2$  by adding the Dresselhaus spin-orbit term (${\propto} \beta$).
+
+Since $\A$ depends on $\alpha,~\beta,~l,~E,~m$ only through $\alpha k_E /\var_c$, $\beta k_E /\var_c$ and $g_\text{eff}$, let us consider the three-dimensional parameter space $(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_{\sma{\text{eff}}}){\in} \mathbb{R}^3$.
+$\A(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_{\sma{\text{eff}}}){=}{\pm} I$ determines a set of concentric circles in the $\beta{=}0$ plane, as per the $\mathfrak{c}_{\infty}$-symmetric case study in \s{sec:ctsrot}.
+Moving off this plane, we find that $\A{=}I$ is satisfied in a  neighborhood of $\beta{=}0$, i.e., $\A{=}I$ defines a hypersurface in $\mathbb{R}^3$ that is illustrated in \fig{fig:dgn}(a).
+On the other hand, $\A{=}{-}I$ is not satisfied in the neighborhood of $\beta{=}0$, hence the circles associated to $\A{=}{-}I$ remain isolated as line nodes, as illustrated in \fig{fig:dgn}(b).
 To recapitulate, we have found that one of every two Landau-level crossings (those labelled by odd $j$) destabilize due to the symmetry reduction.
@@
 To demonstrate how the $\A{=}I$ hypersurface derives from $\mathfrak{c}_2$ symmetry, consider  the effective Hamiltonian $\calh$ 
-\e{\calh=\alpha (k_{x}\sigma_{y}{-}k_{y}\sigma_{x})+\beta (k_{x}\sigma_{x}{-}k_{y}\sigma_{y})-\tf{g_s}{2}\mu_{B}B\sigma_z,}
+\e{\calh=\alpha (k_{x}\sigma_{y}{-}k_{y}\sigma_{x})+\beta (k_{x}\sigma_{x}{-}k_{y}\sigma_{y})-\f{g_s}{2}\mu_{B}B\sigma_z,}
 in a momentum-independent basis where the Pauli matrices correspond to spin operators. The two-fold rotational symmetry 
-\e{\calh(\bk)=\sigma_z\calh(-\bk)\sigma_z, \;\: \bk(t)=-\bk\big(t+\tf{T_c}{2}\big)\in \frako_0,}
+\e{\calh(\bk)=\sigma_z\calh(-\bk)\sigma_z, \;\: \bk(t)=-\bk\big(t+\f{T_c}{2}\big)\in \frako_0,}
 implies that the propagator over the time interval $[T_c/2,0]$ is symmetry-related to that over $[T_c,T_c/2]$:
@@
 It follows that $r_2{=}0$ is a necessary and sufficient condition for ${\cal \bar{A}}{=}I$.
-The corresponding degeneracy manifold is a  path-connected hypersurface which includes the free-electron limit: $\br{=}(r_1,r_2,r_3){=}(1,0,0)$.
-\fig{fig:dgn}(b) illustrates the same hypersurface in distinct coordinates: $(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_{\sma{\text{eff}}})$.
-On the other hand, ${\cal \bar{A}}{=}{-}I$ occurs if and only if $\br{=}(0,1,0)$.
-This point is mapped to a path-connected line node confined to the  $\alpha{=}0$ and $\beta{=}0$ planes [cf.\ \fig{fig:dgn}(a)]; the difference in codimension originates from the  $\mathfrak{c}_{\infty}$ symmetry within these two planes [cf.\ \s{sec:ctsrot}], which was not accounted for in the $\mathfrak{c}_2$-symmetric analysis of \q{proprashba}.
+The corresponding degeneracy manifold is a  path-connected hypersurface, which separates $\br=(r_1,r_2,r_3,r_4)$-space into two distinct connected components.
+\textbf{[does this conclusion generalize to any N]} \fig{fig:dgn}(a) illustrates the same hypersurface in distinct coordinates: $(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_{\sma{\text{eff}}})$.
+On the other hand, ${\cal \bar{A}}{=}{-}I$ occurs if and only if $\br{=}(0,\pm 1,0,0)$.
+These two points are mapped to a path-connected line node confined to the $\alpha{=}0$ and $\beta{=}0$ planes [cf.\ \fig{fig:dgn}(b)]; the difference in codimension originates from the  $\mathfrak{c}_{\infty}$ symmetry within these two planes [cf.\ \s{sec:ctsrot}], which was not accounted for in the $\mathfrak{c}_2$-symmetric analysis of \q{proprashba}.
 
@@
 \caption{Cyclotron orbits for $\mathfrak{c}_2$-symmetric [(a)] and $\mathfrak{c}_3$-symmetric [(b)] breakdown.
-\textbf{[Please add dashed line indicating zeroth order orbit, and label one of the crescents by $\delta S/4$ and another by $\delta S/6$.
-It would also be good to show the energy-momentum dispersion and the orbits (the analog of Fig 3c).]} Bottom right inset of (a) presents an enlarged view of the breakdown junction, where the purple rectangle has area $S_{\sma{\square}}$.\label{fig:Cn-breakdown}}
+Bottom right inset of (a) presents an enlarged view of the breakdown junction, where the purple rectangle has area $S_{\sma{\square}}$.\label{fig:Cn-breakdown}}
 \end{figure}
@@
 
+%For simplicity, we interpret the Pauli matrices as  spin operators, and the two right-most terms of  \q{modelC2breakdown} as a spin-orbit coupling.
+
 We begin with a minimal, $\mathfrak{c}_2$-symmetric model:
 \e{H=\f{{\hbar^2}k^2}{2m_1}+ \bigg(\f{{\hbar^2}k^2}{2m_2}-\mu\bigg)\sigma_z +wk_y\sigma_x,\la{modelC2breakdown}}
-with $0{<}m_1{\ll}m_2$ and positive $\mu$.
-For simplicity, we interpret the Pauli matrices as  spin operators, and the two right-most terms of  \q{modelC2breakdown} as a spin-orbit coupling.
-The $\mathfrak{c}_2$ symmetry manifests as $\sz H(\bk)\sz{=}H({-}\bk)$, and relates
+with $0{<}m_1{\ll}m_2$ and positive $\mu$.  The $\mathfrak{c}_2$ symmetry manifests as $\sigma_z H(\bk)\sigma_z{=}H({-}\bk)$, and relates 
 two Dirac points at
@@
 \e{H_{\pm} =\pm {\hbar}\sqrt{\f{2\mu}{m_2}}\bigg(\frac{m_2}{m_1}+\sz\bigg)\delta k_x+w\delta k_{y}\sx+\epsilon_0, \la{linearHam2}}
-from which we deduce that both Dirac points are  type-II if $m_1{<}m_2$; we further assume $m_1{\ll}m_2$ so that the quasidegeneracy condition is satisfied.
+from which we deduce that both Dirac points are  type-II if $m_1{<}m_2$; we further assume $m_1{\ll}m_2$ so that the quasidegeneracy condition ($\delta S/S$) is satisfied.
 
@@
 
-At energies close to the Dirac point ($E{-}\epsilon_0 {\ll} wm_2(2E/m_1)^{\sma{1/2}}$), there are two concentric orbits which (nearly) touch at both Dirac points, as illustrated in Fig.
+At energies close to the Dirac point ($E{-}\epsilon_0 {\ll} wm_2(2\epsilon_0/m_1)^{\sma{1/2}}$), there are two concentric orbits which (nearly) touch at both Dirac points, as illustrated in Fig.
 \ref{fig:Cn-breakdown} (a).
@@
 
-The necessary and sufficient condition for a degeneracy of $\cala$ is \begin{align}\tau\cos\bigg(\f{\tilde{\lambda}_+{+}\tilde{\lambda}_-}{2}+\bar{\varphi}\bigg)= \begin{cases} 0, & {\A}=+I \\
+The necessary and sufficient condition for a degeneracy of $\cala$ is 
+\begin{align}
+\Delta:= \tilde{\lambda}_+{-}\tilde{\lambda}_{-}{+}2\bar{\varphi},\;\;
+\tau\cos\f{\Delta}{2}= \begin{cases} 0, & {\A}=+I \\
                  \pm 1, & \A =-I\end{cases}.\la{c2breakdowndgncondition}
 \end{align}
-The adiabatic limit is given by $\tau{=}1$ and $\bar{\phi}{=}0$, which leads to the satisfaction of \q{c2breakdowndgncondition} for $l^2$ equal to an integer multiple of $2\pi/\delta S$.
+$\Delta$ is the differential phase between two Feynman loops  that involve a single tunneling event  over one cyclotron period, as illustrated in Fig.\ \ref{fig:Cn-breakdown}(a) \textbf{[might be good to draw loops in figure using (translucent?) colors other than black]}.
+The adiabatic limit is given by $\tau{=}1$ and $\bar{\varphi}{=}0$, which leads to the satisfaction of \q{c2breakdowndgncondition} for $l^2$ equal to an integer multiple of $2\pi/\delta S$.
 As noted  in \s{sec:introducecodimension}, such a periodicity  corresponds to a differential increment of a single, magnetic flux quantum.
 
-Deviating from the adiabatic limit ($\tau{<}1$), we deduce from \q{c2breakdowndgncondition} that only $\A{=}I$ remains attainable by varying $B$; this is consistent with the codimension analysis of \q{proprashba}.
-The conditions $\A{=}I$ and $\rho{>}0$ are interpreted as a destructive interference of the two Feynman paths [illustrated in \red{[Fig]}] that an electron may take in tunneling between bands (over one cyclotron period) -- effectively, there are then two identical and independent orbits, which lead to a Landau-level quasidegeneracy.
-Such quasidegeneracies occur with  a periodicity in $l^2$ of $4\pi/\delta S$ (or two flux quanta).
-This periodicity is not affected by the additional phase $\bar{\phi}$ in the argument of the cosine function, because $\bar{\phi}$  varies on the scale  $2\pi/S_{\sma{\square}}$ [with  $S_{\sma{\square}}$ the area of the rectangle inscribed between the two hyperbolic arms  in Fig.\ \ref{fig:Cn-breakdown} (a)],\footnote{For $\bar{\varphi}(\bar{\mu})$ to vary  $\sim 1$, the Landau-Zener parameter $\bar{\mu}$ must vary by $\sim 1$;\footnote{See Fig.\ 10 in 100page} moreover, $2\pi\barmu{:}{=} (2\pi/8) l^2S_{\sma{\square}}$.[AALG]} which is much larger than
+Deviating from the adiabatic limit, we deduce from \q{c2breakdowndgncondition} that  $\A{=}I$ remains attainable by varying $B$, but $\A{=}{-}I$ is unattainable because $\tau{<}1$; this is consistent with the codimension analysis of \q{proprashba}.
+The conditions $\A{=}I$ and $\rho{>}0$ are interpreted as the destructive interference of  two, single-tunneling Feynman loops, i.e., $\Delta{=}\pi$.
+Concurrently, there is constructive interference of the Feynman loops involving zero and two tunneling events.
+The differential phase between outer and inner zero-tunneling (band-conserving) loops is simply $2\Delta{=}2\pi$ (by $\mathfrak{c}_2$ symmetry), hence Landau levels are quasidegenerate.
+Such quasidegeneracies recur as $\Delta$ advances by $2\pi$, corresponding to a periodicity in $l^2$ of $4\pi/\delta S$ (or two flux quanta).
+This periodicity is not affected by the additional phase $2\bar{\phi}$ in $\Delta$, because $\bar{\phi}$  varies on the scale  $2\pi/S_{\sma{\square}}$ \textbf{[we can't use symbols we don't define; footnotes don't count]},\footnote{For $\bar{\varphi}(\bar{\mu})$ to vary  $\sim 1$, the Landau-Zener parameter $\bar{\mu}$ must vary by $\sim 1$ [cf.\  Fig.\ 10 in 100page].
+Moreover, $2\pi\barmu{:}{=} (2\pi/8) l^2S_{\sma{\square}}$.[AALG]} which is much larger than
  $4\pi/\delta S$. To recapitulate, half the Landau-level quasi-crossings (over the $B$ axis) are destabilized by tunneling; the robustness of the other half relies on $\mathfrak{c}_2$ symmetry.
@@
 
-For our last illustration, we consider a II-Dirac model with $\mathfrak{c}_3$  symmetry, as   is illustrated in Fig.
+For our last illustration, we consider a II-Dirac model with $\mathfrak{c}_3$  symmetry, as   illustrated in Fig.
 \ref{fig:Cn-breakdown}(b).
-The corresponding propagator $\A$ has a form analogous to \q{propC2breakdown} -- but with $(\cdot)^2$ replaced by $(\cdot)^3$, and with $\tilde{\lambda}_\pm{=}\pm l^2\delta S/4$ replaced by $\pm l^2\delta S/6$ (plus a field-dependent geometric correction).
-The degeneracy condition is  modified to $\tau\cos[(\tilde{\lambda}_+{+}\tilde{\lambda}_-)/2{+}\bar{\varphi}]{=}{\pm} 1,{\pm} 1/2$.
-With nonzero tunneling ($\rho {>}0$), only $\pm 1/2$ is attainable -- this implies that of every three degeneracies that exist in the adiabatic limit, only two are perturbatively stable.
+The corresponding propagator $\A$ has a form analogous to \q{propC2breakdown} -- but with $(\cdot)^2$ replaced by $(\cdot)^3$, and with $\tilde{\lambda}_\pm{=}{\pm} l^2\delta S/4$ replaced by $\pm l^2\delta S/6$ (plus a field-independent geometric correction).
+The degeneracy condition is modified to $\tau\cos[(\tilde{\lambda}_+-\tilde{\lambda}_-)/2{+}\bar{\varphi}]{=}{\pm} 1,{\pm} 1/2$.
+With nonzero tunneling ($1/2{<}\tau {<}1$), only $\pm 1/2$ is attainable -- this implies that of every three degeneracies that exist in the adiabatic limit, only two are perturbatively stable.
 Beyond a critical field  (defined by $\tau{=}1/2$), all degeneracies coalesce pairwise (on the $B$ axis) and annihilate.
 
-We conclude this section with a general result that is valid for any integer $N{\geq}2$: of every $N$ quasi-crossings that exist in the adiabatic limit, $N{-}1$ of them are stable against tunneling that respects  $\mathfrak{c}_N$ symmetry.
+We conclude this section with a general result that is valid for any integer $N{\geq}2$: of every $N$ quasi-crossings that exist in the adiabatic limit, $N{-}1$ of them are perturbatively stable against tunneling that respects  $\mathfrak{c}_N$ symmetry.
 We prove this in App.
@@
 
-\begin{table}
-\begin{tabular*}{\columnwidth}{l@{\extracolsep{\fill}}cccccc}
+\begin{table*}
+\begin{tabular*}{\textwidth}{c@{\extracolsep{\fill}}ccccccc}
 \hlineB{2.0}
-             no. & description & $u$ & $s$ & quasi. & $g$ & codim.\\
+             class number & action on orbit & action on $\bk$ & $u$ & $s$ & quasidegenerate & $g$ & codimension\\
 \hline
-1 &$\forall \bk \in \frako_0$, $g\circ \bk=\bk$  & 0 & 0 & $\surd$ & $\breve{g}\propto I$ & 3  \\
- &    &  &  & & $\breve{g}\not\propto I$ & 1 \\
-2 &    & 0 & 1 & & $g^2=1$ & 1  \\
- &    &  &  & & $g^2=-1$ & 3  \\
-3 & $|g\circ \frako_0| = |\frako_0|$ & 0 & 0 & $\surd$ & - & 1   \\
-4 & $\exists \bk \in \frako_0, g\circ \bk\ne\bk$    & 0 & 1 & & - & 1   \\
-5 &    & 1 & 0 & & $\breve{g} \propto \sigma_z$ & 2  \\
- &    &  &  & & $\breve{g} \not\propto \sigma_z$ & 0  \\
-6 &  & 1 & 1 & $\surd$ & $g^2=1$ & 2  \\
-&  &  &  & & $g^2=-1$ & 0  \\
-7 & $|g\circ \frako_0| \ne |\frako_0|$ & 0 & 0 & $\surd$ & - & 3 \\
-8 &    & 0 & 1 & & - & 3 \\
-9 &    & 1 & 0 & & - & 3 \\
-10 &    & 1 & 1 & $\surd$ & - & 3 \\
+\multirow{2}{*}{1} & \multirow{10}{*}{$|g\circ \frako_0| = |\frako_0|$} & \multirow{4}{*}{$\forall \bk \in \frako_0$, $g\circ \bk=\bk$} & \multirow{2}{*}{0} & \multirow{2}{*}{0} & \multirow{2}{*}{$\surd$} & $\breve{g}\propto I$ & 3  \\
+ & & & & & & $\breve{g}\not\propto I$ & 1 \\
+ \cline{4-8}
+\multirow{2}{*}{2} & & & \multirow{2}{*}{0} & \multirow{2}{*}{1} & & $g^2=1$ & 1  \\
+ & & &  &  & & $g^2=-1$ & 3  \\
+ \cline{3-8}
+3 & & \multirow{6}{*}{$\exists \bk \in \frako_0, g\circ \bk\ne\bk$} & 0 & 0 & $\surd$ & - & 1   \\
+\cline{4-8}
+4 & & & 0 & 1 & & - & 1   \\
+\cline{4-8}
+\multirow{2}{*}{5} & & & \multirow{2}{*}{1} & \multirow{2}{*}{0} & & $\breve{g} \propto \sigma_z$ & 2  \\
+ & & & &  & & $\breve{g} \not\propto \sigma_z$ & 0  \\
+\cline{4-8}
+\multirow{2}{*}{6} & & & \multirow{2}{*}{1} & \multirow{2}{*}{1} & \multirow{2}{*}{$\surd$} & $g^2=1$ & 2  \\
+& & & &  & & $g^2=-1$ & 0  \\
+\hline
+7 & \multirow{4}{*}{$|g\circ \frako_0| \ne |\frako_0|$} & \multirow{4}{*}{-} & 0 & 0 & $\surd$ & - & 3 \\
+\cline{4-8}
+8 &  &  & 0 & 1 & & - & 3 \\
+\cline{4-8}
+9 &  &  & 1 & 0 & & - & 3 \\
+\cline{4-8}
+10 &  &  & 1 & 1 & $\surd$ & - & 3 \\
 \hlineB{2.0}
@@
 \caption{Codimensions of degeneracy manifold of two-by-two propagator $\A$ under constraints of different type of symmetries.
-The first column defines how the symmetry act on the cyclotron orbit, where $g\circ \bk$ (resp.
-$g\circ\frako$) is the image of $\bk$ (resp.
-$\frako$) under the the action of $g$.
-$|g\circ \frako=\frako|$ indicates the image of the orbit coincides with itself, regardless of orientation of the orbit.
-The next two columns are intrinsic properties of $g$.
-$u=0$ (resp.
-$u=1$) indicates the symmetry is a proper (resp.
-improper) transformation of the plane of the cyclotron orbit ($k_z=\text{constant}$).
-$g$ of $u=0$ (resp.
-$u=1$) does not flip (resp.
-flips) the orientation of the cyclotron orbit.
-$s=0$ (resp.
-$s=1$) indicates the symmetry is unitary (resp.
-antiunitary).
-In magnetic groups, antiunitary symmetry operations contain time reversal symmetry.
-The fourth column indicates whether this symmetry class applies to quasidegenerate propagator $\A$.
-For the five classes not applicable here, they are useful for Landau levels of fully degenerate bands, as discussed in Sec.
-\ref{sec:discussion}.
-The fifth column specifies additional conditions (on the representation of $g$) which are necessary to obtain a unique answer for codimension.
-$\breve{g}$ is the diagonalized, unitary matrix representation of $g$ in the degenerate subspace.
-The last column is codimension of the degeneracy manifold.\label{table:codimension}}
-\end{table}
+The first column is class number.
+The second and third column defines how the symmetry acts on the cyclotron orbit.
+The next two columns are intrinsic properties of $g$ (cf.
+Sec.
+\ref{sec:reviewtenfold}).
+The sixth column indicates whether this symmetry class applies to quasidegenerate propagator $\A$.
+The seventh column specifies additional conditions (on the representation of $g$) which must be imposed to uniquely determine the codimension.
+$\breve{g}$ is the diagonalized, unitary matrix representation of $g$ in the degenerate subspace of $\hat{H}_0$.
+In class 5, $\breve g$ is evaluated at $\bk$ where $g\circ\bk=\bk$.
+Symmetry operations whose sewing matrices are needed are mostly reflections and glide planes.
+For convenience, we presented in table \ref{table:sewing-matrix} sewing matrix for common reflections and glide planes.
+The last column presents codimensions of the degeneracy manifold.
+In class 2, 4 and 5, $\A$ is subject to another requirement: $\text{det}(\A)=\pm 1$ [topofermi].
+For spin degeneracy studied in current work, we assume SOC can be turned off continuously without lifting the degeneracies or increasing the degree of degenearcies.
+With this assumption, $\text{det}(\A)=1$, which is utilized to obtain the current table.
+ \label{table:codimension}}
+\end{table*}
 
 Generalizing our rotational-symmetric case studies in
-Sec.
-\ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown}, we now present the symmetry-constrained codimensions for all ten[topoferm] symmetry classes of orbits.
+Sec.\ \ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown}, we now present the symmetry-constrained codimensions for all ten[topoferm] symmetry classes of orbits.
 Depending on the class, the codimension is either $0,1,2$ or $3$.
 We begin by briefly reviewing the ten-fold symmetry classification of orbits in \s{sec:reviewtenfold}.
-
-%Since magnetic field $B$ is applied externally, it does not change under the action of any symmetry operation.
+We then study in Sec.
+\ref{sec:codimquasideg} five of the classes which is relevant to quasidegenerate orbits.
+The remaining five classes are relevant to exactly degenerate orbits, which we study in Sec.
+\ref{sec:codimexactdeg}.
 
@@
 
-Any symmetry $g$ of a space group acts on space-time as
+%%We restrict our attention to the subset of $g$ (in the space group) that preserves all field-orthogonal $\bk$-planes, where  orbits  are confined.\textbf{[might say something different about 2DEG]}
+
+Any symmetry $g$ of a field-independent, translation-invariant Hamiltonian $\hat{H}$ acts on space-time as
 \begin{align}
-&g: \vectwo{\br}{t} \rightarrow \matrixtwo{\check{g}^{-1}}{0}{0}{ (-1)^{s(g)}}\vectwo{\br}{t}+\vectwo{\bdelta}{0}, \la{definesg}
+&g: \vectwo{\br}{t} \rightarrow \matrixtwo{\check{g}}{0}{0}{ (-1)^{s(g)}}\vectwo{\br}{t}+\vectwo{\bdelta}{0}, \la{definesg}
 \end{align}
@@
 \e{\bk \rightarrow g\circ\bk := (-1)^{s(g)}\check{g}\bk. \la{gmapk}}
-We restrict our attention to the subset of $g$ (in the space group) that preserves all field-orthogonal $\bk$-planes, where the field-induced orbits  are confined.\textbf{[might say something different about 2DEG]}
-
-%We align the z-axis of our Cartesian coordinate system parallel to the field, such that field-induced dynamics is constrained within planes of constant $k_z$.
-
-%Hence any symmetry relevant in current context must keep $k_x$-$k_y$ plane untouched.
-
-Given any orbit $\frako_0$ within a plane (given by constant-energy and $k_z$ contours all bands), we may deduce from \q{gmapk} if  $g$ maps the orbit to itself (denoted as $|g\circ\frako_0|=|\frako_0|$) or to a distinct orbit.
-Moreover, whether $g$ preserves the direction of cyclotron orbit (denoted as $u(g)=0$) or not (denoted as $u(g)=1$) indicates whether the path-ordering in $\A$ needs to be inverted.
-
-then there exists a matrix representation of $g$ that relates $\A$ to itself (if u=1) or to its inverse (if u=-1).
-
-or not ($|g\circ\frako_0|\ne|\frako_0|$) determines whether a self constraint can be imposed on $\A$.
-The former case can be again divided into two types, one for $g$ mapping every $\bk$ on the orbit to itself and one for at least one $\bk$ on the orbit being mapped to another point.
-
- By definition, $\A$ is a path-ordered exponential along the cyclotron orbit of the two-by-two Hamiltonian $\H$ and $\H$ is composed of a scalar $\delta\epsilon$ and a pseudovector $B\mathcal{M}$.
- Besides the transformation of orbits, the transformation of $\H$ is also significant in determining the transformation of $\A$.
-As a scalar, $\delta\epsilon$ remains intact under the action of $g$ while in contrast $\mathcal{M}$ changes to $(-1)^{u+s}\mathcal{M}$, with $s(g)=0$ (resp.
-$s(g)=1$) denoting $g$ being unitary (resp.
-antiunitary).
-For $\H$ transforming consistently under $g$, $u+s=0, 2$ is required.
-The indicators defined above classifies symmetry operations into ten and only ten classes, presented in table \ref{table:codimension}.
-
-\subsubsection{Symmetry-constrained codimension for quasidegenerate orbits}\la{sec:codimquasideg}
-
-With detailed codimension analysis relegated to App.
-\ref{app:codimension}, we present the result in table \ref{table:codimension}.
-To obtain a unique answer for codimension in some of the symmetry classes, we have to specify certain conditions for the symmetry representation: for $g$ that does not invert time ($s{=}0$), we specify certain conditions on  $\breve{g}$, the \emph{diagonalized} matrix representation  of $g$; for $g$ that inverts time  ($s{=}1$), we specify if the antiunitary representation of $g$ squares to $+I$ or $-I$.
-$T\mathfrak{r}_{x,\boldsymbol{c}/2}$ ($\mathfrak{r}_{x,\boldsymbol{c}/2}$ is glide plane translating in $z$ direction for half a lattice vector after flipping $x$ direction) at $k_z=\pi$ is an example of codimension 0, corresponding to class-6 (the 6th class in the table) \red{[Notice that I changed the name of the class.
-I begin to think class II-A bears more similarity to class-I and the original classification is not natural.
-Therefore, I abandoned the I, II-A and II-B.
-Do you agree?]} with condition $g^2=-1$.
+Given $\hat{H}$ and the orientation of the magnetic field, electrons follow orbits (denoted $\frako$) that are confined to field-orthogonal $\bk$-planes.
+Given an orbit $\frako$, we restrict our attention to the subgroup of $\hat{H}$ that maps the orbit to itself (denoted as $|g\circ\frako|{=}|\frako|$) or to a distinct orbit ($|g\circ\frako|{\ne}|\frako|$).
+In the former mapping, we may further distinguish two cases: (a)  $g$ maps every $\bk$ on the orbit to itself, as exemplified by the composition $T\inv$ of time reversal ($T$) and spatial inversion ($\inv$)  symmetries.
+(b) There exists at least one $\bk$ on the orbit that is mapped to a distinct wavevector, e.g., time-reversal symmetry relates two wavevectors ($\bk$ and ${-}\bk$) on an orbit that encircles a time-reversal-invariant point.
+
+Lastly, we distinguish  between mappings [\q{gmapk}] that preserve  ($u(g){=}0$) or invert ($u(g){=}1$) the orientation of the orbit.
+For example, a rotation with axis parallel to the field is orientation-preserving, while a reflection with axis orthogonal to the field is orientation-inverting.
+The combination of all distinguishing criteria leads to   a ten-fold classification of orbits $\frako_0$ with $g$ symmetry, as was first presented in [topoferm] and is summarized by the ten numbered rows in \tab{table:codimension}.
+
+%In the latter case there exists no self-constraint on the propagator $\A$ [cf.\ \q{eq:prop}] due to $g$ alone, hence the codimension
+
+% preserves  ($u(g)=0$) or inverts ($u(g)=1$) the orientation of the orbit. In the latter case ($|g\circ\frako_0|\ne|\frako_0|$), no constraint exists between $\A$ and itself
+
+\subsubsection{Symmetry-constrained codimension for quasidegenerate orbits}\label{sec:codimquasideg}
+
+In the particular context of quasidegenerate bands, $\hat{H}{=}\hat{H}_0{+}\delta \hat{H}$ is the sum of a zeroth-order Hamiltonian (with spin-degenerate bands) and a symmetry-lowering perturbation.
+Given a zeroth-order orbit $\frako_0$ of $\hat{H}_0$, we  are interested in the subgroup of $\hat{H}$ that  maps $\frako_0$ to itself or to a distinct zeroth-order orbit.
+
+Of the ten classes described in \s{sec:reviewtenfold}, only five   are relevant to quasidegenerate orbits (which are split with differential area  $\delta S$ that is much less than the area of $\frako_0$).
+To identify this five, recall that the subleading corrections to our quantization rule are determined by the propagator $\A$ [cf.\ \q{eq:prop}], which is a time-ordered exponential of an effective Hamiltonian $\H{=}\delta\epsilon{+}B \mathcal{M}$ [cf.\ \q{eq:H1}]; $\H$ perturbatively encodes $\delta H$ and the Zeeman interaction, for an electron travelling over  $\frako_0$.
+Since $g$ is  a symmetry of  $\delta \hat{H}$, $\delta\epsilon$ is invariant under action of $g$.
+On the other hand, $\mathcal{M}$ is the field-parallel component of a pseudovector that is odd under time reversal,[sakurai] hence changes under $g$ to  $(-1)^{u+s}\mathcal{M}$  (plus a gauge-dependent term[100page] which is not essential to the present argument).
+Only with $u{+}s{=}0$ or $2$ would both terms in $\H$ transform consistently (invariantly) under $g$ -- this identifies the five ticked classes in Tab.\ \ref{table:codimension}.
+
+%\textit{quasidegenerate} orbits; such orbits are split with differential area  $\delta S$ that is much less than the area of the zeroth-order orbit $\frako_0$.
+We remind the reader that $\frako_0$ is determined from the field orientation and the spin-degenerate bands of $\hat{H}_0$, while $\delta S$ is further determined by a symmetry-lowering perturbation: $\hat{H}{=}\hat{H}_0{+}\delta \hat{H}$.
+
+%To recapitulate the discussion in \s{sec:reviewtenfold}, we are interested in $g$ belonging to the subgroup of $\hat{H}$ that 
+% maps $\frako_0$ to itself or to a distinct zeroth-order orbit.
+In the less-general context of quasidegenerate orbits, we shall impose additional restrictions that restrict $g$ to five of ten classes.
+
+For these five classes (labelled 1, 3, 6, 7 and 10 according to the first column of Tab.\ \ref{table:codimension}), we list their corresponding \textit{symmetry-constrained codimensions} in the right-most column of Tab.\ \ref{table:codimension}; these numbers are derived in  App.\ \ref{app:codimension}.
+To clarify, we define the $g$-constrained codimension as the minimal codimension -- among all degeneracy manifolds -- as enforced by $g$ symmetry.
+For example, we have found that two-fold rotational symmetry reduces the codimension of the $\A{=}{+}I$ manifold (to unity), but not the codimension of the $\A{=}{-}I$ manifold [cf.\ \q{proprashba}]; the rotation-constrained codimension is then unity.
+Each entry in the right-most column of Tab.\ \ref{table:codimension} equals the $g$-constrained codimension for any $g$ in that class.\textbf{[chong, please add footnote describing how the notion of symmetry-constrained codimension is useful for class 3 and 4.
+We don't need to give details, just some easy-to-read facts.]}
+
+Of the five classes only three (1, 3 and 6) potentially have symmetry-constrained codimensions that are reduced from three: these three have in common that  $|g\circ\frako_0|{=}|\frako_0|$, and therefore the propagator $\A$ [cf.\ \q{eq:prop}] is self-constrained.
+To clarify, a self-constraint relates  the propagator $\A$ [cf.\ \q{eq:prop}] to itself or to its inverse $\A^{-1}$, depending respectively on whether $u{=}0$ or $1$.
+
+%To uniquely determine the codimension in some classes,  conditions for the symmetry representation of $g$ must be specified: in class 1 for unitary $g$ that preserves the arrow of time ($s{=}0$),
+
+Class 1 groups together  spatial symmetries that preserve the arrow of time and map every $\bk$ on $\frako_0$ to itself.
+The simplest example is of $g$  a reflection symmetry with axis parallel to the field, and of  $\frako_0$ that is confined to a $g$-invariant $\bk$-plane.
+To uniquely determine the symmetry-constrained codimension in class 1, one must specify if the quasi-degenerate bands belong to identical or distinct representations of $g$.
+The symmetry-constrained codimension is reduced to unity in the latter (and only the latter) case, due to the absence of level repulsion between distinct representations of $g$ -- the corresponding quasidegeneracies of Landau levels would then be exact degeneracies, rather than the near degeneracies described by \qq{llquasideg}{llquasidegB}.
+
+%we specify certain conditions on  $\breve{g}$, the \emph{diagonalized}, two-by-two matrix representation  of $g$;
+
+Class 3 corresponds to spatial symmetries that preserve the arrow of time and the orientation of $\frako_0$, as exemplified by rotational symmetry with rotational axis parallel to the field.
+The symmetry-constrained codimension here is unity, as has been modelled in Sec.\ \ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown}.
+
+Symmetries in class 6 reverse both the arrow of time and the orientation of the orbit.
+The symmetry-constrained codimension is $2$ or $0$, depending respectively on whether the antiunitary representation of $g$ squares to $+1$ or $-1$.
+The former is exemplified by the composition $T\mathfrak{r}_{y=-x}$ of time reversal with a reflection symmetry (with reflection axis orthogonal to the field); this is a symmetry of the Rashba-Dresselhaus Hamiltonian [cf.\ \q{hamRD}]:
+\e{ g H_{RD}(k_x,k_y)g^{-1} = H(k_y,k_x),\;\; g = e^{i\sigma_z\pi/4}K,}
+with $K$ implementing complex conjugation.
+A consequence of this symmetry is that the degeneracy line node in Fig.
+\ref{fig:dgn}(b) is robust -- a property we had previously (and consistently) deduced from continuous rotational symmetry.
+An example of $g^2{=}-1$ is given by
+the composition $T\mathfrak{r}_{x,\boldsymbol{c}/2}$ of time reversal with a glide symmetry; $\mathfrak{r}_{x,\boldsymbol{c}/2}$ is itself the composition of a reflection (with axis orthogonal to the field) and half a lattice translation (parallel to the field).
+The propagator for an orbit in the Brillouin-zone boundary ($k_z{=}\pi$ plane) would then be Kramers-degenerate -- the symmetry-constrained codimension vanishes.
+
+%In the latter case, the codimension vanishes due to Kramers degeneracy.
+In the former case, the codimension is calculated to be 2, which is exemplified by $H_{RD}$ respecting $T\mathfrak{r}_{y=-x}$, with $\mathfrak{r}_{y=-x}$ being reflection transforming $x$ to $y$ and $z$ to $z$.
+
+%Therefore, codimension 2 in table \ref{table:codimension} instructs the degeneracy manifold in Fig.
+\ref{fig:dgn}(b) should be one dimensional, providing an alternative explanation of the line node in Fig.
+\ref{fig:dgn}(b).
+
+%Extensively studied in Sec.
+\ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown} is class-3 (3rd row in the table), where rotational symmetry guarantees Landau level quasidegeneracy can be expected by tuning $B$ alone.
+Class-1 presents another example of codimension 1.
+Unitary symmetry in class-1 with $\breve{g}\not\propto I$ assigns different symmetry eigenvalues to the two degenerate bands (of $\hat{H}_0$) on $\frako_0$ and forbids hybridization between them.
+Therefore, $\A$ assumes a diagonal form and admits only one free variable.
+Class-1 symmetries with $\breve{g}\propto I$, acting effectively as identity operator, impose no constraints on $\A$ and thus no reduction in codimension.
+
+%Codimension 0 is exemplified by class-6 with $g^2=-1$, where any eigenvector of $\A$ here is paired with another one due to Kramer's degeneracy.
+
+%\red{In our definition, $g$ is called a symmetry if $\hat{g}$ commutes with both $\hat{H}_0$ and $\delta \hat{H}$.
+Therefore, $\delta \epsilon$ is invariant under the action of $g$.
+For $\cal H$ to transform consistently under $g$, $g$ must preserve the magnetic moment $\mathcal{M}$.
+The magnetic moment is odd under time reversal, and behaves as a pseudovector under spatial transformations.[sakurai] Therefore, either (i) $g$ preserves the direction of time and is a proper transformation of space, or (ii) $g$ inverts the direction of time and is an improper transformation of space.} (i) is exemplified by a rotational symmetry with the rotational axis aligned parallel to the field, and (ii) by the composition  of time reversal $T$ and a spatial reflection $\mathfrak{r}_x$ (with reflection axis perpendicular to $\vec{B}$).
+%As discussed at the end of \s{sec:introducecodimension}, these classes either respect $u+s=0$ or $u+s=2$. \red{[These discussions moved to Sec. IV B]}
+
+%$T\mathfrak{r}_{x,\boldsymbol{c}/2}$ ($\mathfrak{r}_{x,\boldsymbol{c}/2}$ is glide plane translating in $z$ direction for half a lattice vector after flipping $x$ direction) at $k_z=\pi$ is an example of codimension 0, corresponding to class-6 (the 6th class in the table)  with condition $g^2=-1$.
 Due to similar reasons as Kramer's degeneracy, Landau-level quasidegeneracy are guaranteed for arbitrary parameter choice.
@@
 
-\textbf{[for classes with codimension less than three, please give physical intuition and examples of symmetries where possible.
-For example, I-1 with breveg not proportional to identity merely reflects that different representations of a unitary symmetry do not hybridize at any point along orbit.
-give mirror symmetry as example.]}
-
-\red{[need to define stable or robust]} Codimension 1 does not imply every degeneracy is robust, which is a stronger statement than degeneracy manifold can be found by tuning a parameter.
+%\red{[need to define stable or robust]} Codimension 1 does not imply every degeneracy is robust, which is a stronger statement than degeneracy manifold can be found by tuning a parameter.
 If degeneracy manifold contains distinct components of different codimension, every degeneracy being robust implies all these components having codimension 1, which is generally not the case, as exemplified by rotational symmetry discussed in Sec.
@@
 
-\subsubsection{Symmetry-constrained codimension for exactly-degenerate orbits}\la{sec:codimexactdeg}
-
-\subsection{Magnetic quantum Oscillations}\label{sec:qo}
-
-We have shown that by tuning a single parameter $B$, Landau level quasidegeneracies can be found for some symmetry classes.
-In this section, we study how Landau level quasidegeneracies are reflected on magnetic quantum oscillations and more generally, possible implications of $\lambda_a$ on the oscillation pattern.
-
-Traditionally, quantum oscillations of thermodynamic and transport quantities are best understood for nondegenerate orbits in the absence of breakdown; they originate from the periodic (in $1/B$) depopulation of discrete Landau levels as $B$ is ramped up.
-For spin-degenerate orbits in the absence of breakdown, it is the depopulation of every second Landau level that is periodic.
-With magnetic breakdown at isolated points, the harmonic content of quantum oscillations generically includes multiple periods corresponding to distinct orbits.
-A distinctive feature of spin-split bands is that quantum oscillations are generically aperiodic.
-
-%In 2D electron systems, analysis of quantum oscillations is subtle since oscillations of the chemical potential may change the oscillating behaviour qualitatively. Therefore,
-
-We will separately analyze the oscillations of two types of 2D electron systems distinguished by experimental environment: where (i) chemical potential is kept constant and (ii) particle density is kept constant.
-To analyze quantum oscillations in case (i), it is advantageous to have a Lifshitz-Kosevich-type formula so that Fourier-like components may be separately analyzed.
-Lifshitz-Kosevich formula have been derived in the absence of breakdown, and in the presence of magnetic breakdown at isolated points [Kaganov, lifshitz]; here we report that a Lifshitz-Kosevich formula also exists for coupled spin-split bands:\footnote{This formula corrects a factor of two in our previous work [topofermi].} In particular, for de Hass-van Alphen (dHvA) oscillation, the oscillatory component of the magnetization has the form
-\begin{equation}
-\delta M=-\frac{1}{2\pi}\frac{k_BT}{B}S\sum_{a=1}^D\sum_{r=1}^{\infty}e^{-\frac{r\pi}{\omega_c\tau}}\frac{\text{sin}[r(l^2S+\lambda_a+\gamma_a)]}{\text{sinh}(2\pi^2rk_BT/(\hbar\omega_c))},\label{eq:LK}
-\end{equation}
-where the argument of the sinuisoidal functions involve quantities from our generalized quantization rule, $T$ is temperature and $\tau$ is Dingle scattering lifetime.
-All the quantities on the right handside of Eq.
-(\ref{eq:LK}) are evaluated at Fermi energy.
-For 3D systems, Lifshitz-Kosevich formula is in a similar form, presented in Ref.
-[topoferm].
-If temperature is large compared to the cyclotron frequency and/or $1/\tau$ is large, it is well-known that only the lowest harmonics ($r\sim 1$) are observable.
-If right handside of Eq.
-(\ref{eq:LK}) is contributed by two orbits, the most important oscillating part is the sum of two sine functions and $\lambda_a$ there determines whether the two sine functions are added constructively ($\delta \lambda=0$, corresponding to Landau level quasidegeneracy) or destructively ($\delta\lambda=\pi$).
-$\delta\lambda$ here is defined as $\delta\lambda:=|\lambda_1-\lambda_2| \mod 2\pi$.
-This interference phenomenon has been studied previously for spin splitting factor [topofermi], where $\lambda$ is field independent.
-For quasi-degenerate bands, $\lambda$ here is field dependent.
-Since $\lambda$ varies slowly with respect to magnetic field compared to leading term $l^2S$, a beating pattern is expected.
-Generically, $\delta \lambda$ nonlinearly depends on $l^2$, leading to an \textit{aperiodic} beating in the dHvA oscillation.
-Figure \ref{fig:qo} (a) shows the evolution of $\delta\lambda$ with respect to magnetic field for various parameters of Rashba-Dresselhaus system.
-Whenever $\delta\lambda$ reaches $\pi$ (resp.
-$0$), a beating node (resp.
-antinode) is expected.
-
-%surface states of 3D solids (insulators and metals, of both trivial and topological categories), as well as (ii) 2DEG in semiconductor heterostructures or 2D materials on substrates.
-Quantum oscillations of the chemical potential are generically negligible in case (i),
-
-% \footnote{Suppose $\mu$ is the field-dependent chemical potential of a 3D solid with surface states.
-Since $\mu$ is an intensive quantity, it may be approximated by the chemical potential $\mu'$ corresponding to the same 3D solid but with periodic boundary conditions in three independent directions.
-If said solid is an insulator, $\mu'$ would depend smoothly on $B$; if said solid is a metal, the quantum oscillations of $\mu'$ have negligible amplitude so long as the Fermi surface is not highly anisotropic.[lifshitz,kosevich] } and non-negligible in case (ii).
-
-As will be shown below, for quantum oscillations in case (ii), $\delta\lambda$ also governs the oscillation pattern.
-For concreteness we consider Schubnikov-de Haas (SdH) oscillations of the conductivity.
-With the assumption of constant particle density, period of quantum oscillation without magnetic breakdown is solely determined by particle number density $n_e$ as $e/n_eh$ [Vinter].
-Minimum of conductivity occurs right at the point when one Landau level is completed depopulated, i.e., when the chemical potential jumps.
-However, these minimums may be smeared out by temperature or disorder.
-Whether the minimums are vulnerable to smearing depends on the Landau level gap, i.e., the magnitude of the jump of chemical potential.
-Larger Landau level gap prevents the conduction minimum from being smeared out and thus corresponds to oscillation of larger magnitude.
-This Landau level gap is governed by $\delta\lambda$.
-We plot in Fig.
-\ref{fig:qo} (b) lower panel chemical potential oscillation with respect to $1/B$ under the assumption of zero energy and zero Landau level broadening where $\delta\lambda{\approx}2\pi$, $\delta\lambda{\approx}3\pi/2$, $\delta\lambda{\approx}\pi$ respectively; the corresponding Landau-level dispersions are obtained from exact diagonalization and plotted in upper panel of Fig.
-\ref{fig:qo} (b).
-As expected, close to Landau level quasidegeneracy ($\delta\lambda\approx 0$), half of the oscillations are smeared out and the oscillation period has effectively doubled.
-This behavior is further confirmed by the oscillation of chemical potential plotted in lower left plot of Fig.
-\ref{fig:qo} (b).
-As a contrast, middle column of Fig \ref{fig:qo} (b) shows Landau levels and chemical potential oscillation for $\delta\lambda\approx 3\pi/2$, when quantum oscillation are expected to exhibit large and small oscillations.
-For $\delta\lambda\approx\pi$, the two sets of Landau levels are equally spaced and quantum oscillation are expected to reveal the particle density of the system.
-Therefore, for 2D fixed particle density systems, both oscillation period and oscillation magnitude are beating \textit{aperiodically} with respect to magnetic field.
-
-It is well known that quantum oscillations from two independent cyclotron orbits (but with similar area in reciprocal space) may also exhibit periodic beatings.
-This is due to Landau levels corresponding to the two orbits may also cross approximately (with a splitting $\sim e^{-c/B}$).
-Such crossings are not so surprising, and merely reflect that distinct orbits are essentially uncoupled; this is very much analogous to the crossing of levels having different symmetry eigenvalues.
-In contrast, for weakly spin-split bands, the two orbits are strongly coupled by tunneling, hence there are no obvious `symmetry eigenvalues'; nevertheless crossings exist and are tunable by $B$.
-The hybridization of the two sets of Landau levels destroy the periodic nature of approximate crossings and is reflected in an \emph{aperiodic} beating pattern.
-\textbf{
-[We should say that experimental groups (e.g.
-Das) have already been fitting the beating in oscillations to cos(Laurent series in B), with phenomenological coefficients.
-Here we provide the microscopic derivation of these coefficients.
-]}
-
-% Another distinction: for localized breakdown, crossings occur only at $B\approx 0$, while for nonlocal breakdown they recur aperiodically  at fields denoted $B_n$.
-The recurrence interval for $1/B_n$ is much larger than the period of quantum oscillations, leading to an aperiodic beating effect in the quantum oscillations.
-
-\begin{figure}
-\includegraphics[width=1.0\columnwidth]{qo.png}
-\caption{Quantum oscillation of Rashba-Dresselhaus system.
-(a) Evolution of $\delta\lambda$ with respect to field for different value of $\beta$.
-Horizontal grey lines are $\delta\lambda=\pi$.
-Upper panel of (b): Landau levels near fields indicated by vertical grey lines in right panel of (a) at $\beta=0.02$eV$\cdot$\AA, corresponding to $\delta\lambda=2\pi$, $\delta\lambda=3\pi/2$ and $\delta\lambda=\pi$ respectively.
-The line of $\beta=0.02$eV$\cdot$\AA~is indicated by a black arrow in (a).
-Lower panel (b): Oscillations of chemical potentials corresponding to upper panel.
-Fixed partical number density is assumed.
-In this figure, other parameters are $m=0.01$/(eV$\cdot$\AA$^2$), $\alpha=0.05$eV$\cdot$\AA~and $E=0.4$eV.
-\label{fig:qo}}
-\end{figure}
-
-\section{Discussion and outlook}\la{sec:discussion}
-
-Landau level quasidegeneracy is not limited to quasidegenerate bands. For degenerate bands, a similar definition is applicable: \red{[need to check]}
-\e{ \f{E_{1}-E_2}{\var_c}\bigg|_{\bar{B}} = O\left(\f{\var_c}{E} \right).
-} Landau levels of degenerate bands are characterized by a propagator $\A'$ similar to Eq.
+\subsubsection{Symmetry-constrained codimension for exactly-degenerate orbits}\label{sec:codimexactdeg}
+
+This work has mainly focused on the Landau quantization of quasidegenerate bands, which are eigenstates of the field-independent Hamiltonian $\hat{H}_0{+}\delta \hat{H}$.
+In this section we focus on higher-symmetry solids where the degeneracy-lifting perturbation $\delta \hat{H}$ is disallowed.
+$\hat{H}_0$ may or may not include spin-orbit coupling; in the former case, a crystalline point-group symmetry (e.g., $T\inv$ symmetry) is required for energy bands to be  two-fold degenerate at zero field.
+
+Given $\hat{H}_0$ and the orientation of the field, electrons of opposite spin follow exactly-overlapping orbits (denoted $\frako_0$) which are confined to field-orthogonal $\bk$-planes.
+Such overlapping orbits will be referred to as \textit{exactly-degenerate}, in contrast with quasidegenerate orbits that are split on the $\bk$-plane.
+Despite the exact degeneracy of orbits, the corresponding Landau levels are generically split by the Zeeman interaction $B\calm$.
+We may therefore ask, in complete analogy: how many tunable parameters are required to attain a Landau-level (quasi)degeneracy for exactly-degenerate orbits?
+
+%The preceding codimension analysis may be straighforwardly extended to  energy bands that are exactly $D$-fold degenerate (at every wavevector) in the absence of the field.
+For simplicity we focus on $D{=}2$ spin degeneracy, which may arise in solids with negligibl\e spin-orbit coupling, and also in spin-orbit-coupled solids with certain crystallographic point-group symmetries (e.g., $T\inv$ symmetry).
+
+We answer this question in nearly the same vein as for quasidegenerate orbits: the quantization rule for exactly-degenerate orbits[topoferm] has the same form as \qq{eq:rule}{berryconn} with $\delta \var{=}\delta S{=}0.$ An eigenvalue-degeneracy of $\A$ would also imply a Landau-level quasidegeneracy, since the analysis of \s{sec:relatedegeneracies} applies to the special case $\delta S{=}0$.
+
+There is, however, a difference in the possible symmetry classes that apply to exactly-degenerate vs quasidegenerate orbits.
+In \s{sec:codimquasideg}, we restricted ourselves to symmetries  that map the magnetic moment  $\calm$ to itself (plus a gauge-dependent term[100page]), so that both terms in $\calh{=}\delta \var{+}B\calm$ transform consistently as scalars.
+In the present context, this restriction is void because $\delta\var{=}0$, hence we \textit{also} allow for symmetries that invert the sign of $\calm$.
+
+Some $\calm$-inverting symmetries also exhibit reduced symmetry-constrained codimensions, as listed in the five \textit{unticked} classes of \tab{table:codimension}.
+As a case in point, class-2 symmetries invert time and $\calm$, and map  every wavevector (in $\frako_0$) to itself.
+The corresponding codimension is three (resp.\ one) if $g$ squares to $-1$ (resp.\ $+1$).
+The former is exemplified by $T\inv$ symmetry, and the latter by $T\rot_{2z}$ (the composition of time reversal with a two-fold rotation about the field direction).
+For an exactly-degenerate orbit $\frako$ confined to a $\rot_{2z}$-invariant plane, the wavefunction can be made real at each $\bk$ in $\frako$, and hence the associated propagator $\A$ is unitarily equivalent to a special orthogonal matrix[AA] with a single, tunable angle of rotation -- this provides an intuitive explanation for the unit codimension.
+
+%the angle of rotation associated to any SO(2) matrix then provides the single tuning parameter.
+
+The simplest example of codimension reduction by a $\calm$-preserving symmetry is that of continuous spin-rotation.
+This is a symmetry of any solid with negligible spin-orbit coupling, and results in the absence of Landau-level repulsion between different spin species [cf.\ unit symmetry-constrained codimension in class I, with non-identical symmetry eigenvalues].
+In this case the Landau-level degeneracy is exact.
+
+The detailed modelling of all ten classes of exactly-degenerate orbits is left to future work.
+We conclude this section by commenting on the tunable experimental parameters that are relevant to exactly-degenerate orbits.
+The absence of $\delta\var$  implies that the eigenvalues of $\cala$ are independent of the magnitude of $B$ [cf.\ \q{lambdasmallB} with $\delta S{=}0$].
+However, the generic anisotropy of $\calm$ (viewed as a pseudovector) suggests that we may sweep the orientation of $B$; the generic energy-dependence of $\calm$ suggests that we may tune the bias voltage in tunneling spectroscopy.
+
+%As derived in App.\ \ref{app:codimension},
+
+%Absent this restriction, all ten symmetry classes may potentially apply to exactly-degenerate orbits, but only six of ten (with $|g\circ\frako_0|{=}|\frako_0|$) may have a symmetry-reduced codimension.
+The codimensions for three of these six classes have been explained in \s{sec:codimquasideg}, so here we focus on the other three.
+
+%Landau level quasidegeneracy is not limited to quasidegenerate bands. For degenerate bands, a similar definition is applicable: \red{[need to check]}
+%\e{ \f{E_{1}-E_2}{\var_c}\bigg|_{\bar{B}} = O\left(\f{\var_c}{E} \right). }
+
+%Landau levels of degenerate bands are characterized by a propagator $\A'$ similar to Eq.
 (\ref{eq:prop}) [100p].
 Codimension analysis can be carried out similarly and the results are presented in table \ref{table:codimension}.
-Unlike $\A$, all ten classes of symmetries impose constraints on $\A'$ and thus entries not applicable to $\A$ are useful for $\A'$.
-For spin-split bands, $\lambda$ depends strongly on the $B$ field for quasidegenerate orbits; for degenerate orbits, the $B$-dependence of $\lambda$ is relatively weaker, i.e., of higher power in the small parameter $B$ [Roth, Niu, Fuchs].
-A more useful tuning parameter in the latter case would be the bias voltage in tunneling spectroscopy experiments.
-
-We have assumed in the above sections that the two-fold quasidegeneracy is due to small SOC.
+
+%Unlike $\A$, all ten classes of symmetries impose constraints on $\A'$ and thus entries not applicable to $\A$ are useful for $\A'$.
+
+%We have assumed in the above sections that the two-fold quasidegeneracy is due to small SOC.
 More generally, two-fold degenerate bands can be perturbed into quasidegenerate bands by symmetry breaking.
@@
 \hlineB{2.0}
- symmetry  & origin of degen. & $\breve{g}\propto$ \\
+ symmetry  & origin of degeneracy & $\breve{g}\propto$ \\
 \hline 
@@
 \end{tabular*}
-\caption{Two by two sewing matrices for reflections and glide planes.
-The second column specifies the origin of two fold degeneracy.
+\caption{Two by two sewing matrices for reflections (e.g., $\mathfrak{r}_x$) and glide planes (e.g., $\mathfrak{r}_{x,\boldsymbol{c}/2}$).
+The two-fold degeneracy are assumed to be protected by either spatial-time inversion symmetry ($T\mathfrak{i}$), composition of time reversal and two fold rotation symmetry ($T\mathfrak{c}_{2z,\boldsymbol{c}/2}$) at $k_z=\pi$ and continous spin rotation symmetry (i.e., negligible SOC).
 Glide operation in $x$ or $y$ direction is irrelevant; for example, $\mathfrak{r}_x$ and $\mathfrak{r}_{x,\boldsymbol{b/2}}$ share the same entry.
@@
 $\mathfrak{t}$ is (arbitrary) translation.
-When the two-fold degeneracy is protected by $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$, $k_z=\pi$ is assumed.\label{table:sewing-matrix}}
+\label{table:sewing-matrix}}
 \end{table}
 
-Table \ref{table:codimension} has introduced diagonalized representation matrix $\breve{g}$ and has used it to obtain a definite answer for codimension for some classes.
-Fortunately, in most cases, $\breve{g}$ can be calculated without knowing the wave functions of the bands.
-In addition, symmetry operations whose sewing matrices are needed are mostly reflections (for example, reflection in $x$ direction $\mathfrak{r}_x$) and glide planes (for example, $\mathfrak{r}_{x,\boldsymbol{c}/2}$ where $\boldsymbol{c}$ is lattice vector in $z$ direction).
-Therefore, for convenience, we presented in table \ref{table:sewing-matrix} sewing matrix for common reflections, glide planes and combination of them.
-In most scenarios, given the space group, table \ref{table:codimension} and \ref{table:sewing-matrix} are adequate to determine the codimension of Landau level quasidegeneracy.
+\section{Quantum-oscillatory phenomena for exactly- and quasi-degenerate orbits}\label{sec:qo}
+
+In \s{sec:qtznrules} we have presented a quantization rule [\qq{eq:rule}{berryconn}] that is applicable to both quasidegenerate ($0{<}\delta S{<}S$) orbits and exactly-degenerate ($\delta S{=}0$) orbits.
+This section explores the implication of this rule for quantum-oscillatory phenomena of the Schubnikov-de Haas (SdH) [SdH] and de Haas-van Alphen (dHvA) [dhva] types.
+In \s{sec:quantosc_equidis}, we present a generalized Lifshitz-Kosevich formula that inputs our rule and outputs quantum oscillations.
+Applying this formula in the high-temperature regime, we will prove that  destructive interference of the fundamental quantum-oscillatory harmonic may  be tuned by at most one parameter in any symmetry class; this parameter may be the magnitude ($B$) of the magnetic field for quasidegenerate orbits, but not for exactly-degenerate orbits.
+\s{sec:quantosc_quasideg} focuses on the low-temperature SdH effect for quasidegenerate orbits in symmetry classes 1 to 4 [cf.\ \tab{table:codimension}], wherein we predict a smooth crossover from period-doubled to -undoubled oscillations upon variation of $B$ (at fixed particle density).
+
+%In We have demonstrated for certain symmetry classes that Landau-level quasidegeneracies can be attained by tuning only the magnitude ($B$) of the magnetic field.
+This manifests in the Schubnikov-de Haas effect  as an aperiodic beating of the minima of conductivity (at fixed particle density), as described in \s{sec:quantosc_quasideg}.
+Analogously, it is also possible to attain quasi-equidistant Landau levels by tuning $B$; this manifests as an aperiodic, destructive interference of the fundamental quantum-oscillatory harmonic (at fixed chemical potential).
+
+\subsection{Single-parameter tunability for the destructive interference of the fundamental harmonic}\la{sec:quantosc_equidis}
+
+%and in the presence of magnetic breakdown [Kaganov, lifshitz];
+
+Lifshitz-Kosevich formulae[lifshitzkosevich] allow for a harmonic analysis of quantum oscillations, and have previously been derived for  exactly-degenerate orbits in symmetry class 1[rothII], with the generalization to all ten symmetry classes in Ref.
+[topoferm].
+A simple generalization of the derivation in [topoferm] extend the utility of these existing formulae to quasi-degenerate orbits of any symmetry.
+For example, the oscillatory component of the magnetization of 2D metals has the form
+\begin{equation}
+\delta M=-\frac{1}{2\pi}\frac{k_BT}{BS^{-1}}\sum_{a=1}^2\sum_{r=1}^{\infty}e^{-\f{r\pi}{\omega_c\tau_{\sma{D}}}} \frac{\text{sin}[r(l^2S{+}\lambda_a{+}\gamma)]}{\text{sinh}(2\pi^2rk_BT/\var_c)},\label{eq:LK}
+\end{equation}
+where the argument of the sine function involve quantities from our  quantization rule [\qq{eq:rule}{berryconn}]; $T$ is temperature and $\tau_{\sma{D}}$  the Dingle scattering lifetime.
+All the quantities on the right handside of Eq.\ (\ref{eq:LK}) are evaluated at the chemical potential.
+\q{eq:LK} corrects the analogous formula in Ref.
+[topoferm] by a factor of half.
+
+%For 3D metals, the oscillLifshitz-Kosevich formula is in a similar form, presented in Ref. [topoferm].
+
+At high temperature ($kT{\gg}\var_c$) and/or with strong disorder ($\omega_c\tau_{\sma{D}}{\ll}1$), the dominant contribution to $\delta M$ is from the fundamental harmonic ($r{=}1$), which sums two sine functions with generically distinct phase offsets $\lambda_{1,2}$.
+This summation (or interference) is constructive if $\delta \lambda{=}|\lambda_1{-}\lambda_2|{\equiv}0$, and destructive if $\delta \lambda{\equiv}\pi$  ($\equiv$ denotes an equivalence modulo $2\pi$).
+In the latter case, only even-$r$ harmonics remain.
+
+%The former is associated to Landau-level quasidegeneracies, and the latter to quasi-equidistant Landau levels with spacing ${\approx}\var_c/2$.
+
+We have shown in \s{sec:llquasideg} that  the number of tunable parameters required to attain  $\delta \lambda{\equiv}0$ ranges from $0$ to $3$; this number is a symmetry-dependent measure of Landau-level repulsion [cf.\ \tab{table:codimension}].
+As illustrated in the right-most panel of Fig 7(b), $\delta \lambda{\equiv}\pi$ is the condition  for Landau levels to be quasi-equidistant  with spacing ${\approx}\var_c/2$; since no level repulsion need be overcome,
+we expect $\delta \lambda{\equiv}\pi$ is attainable with at most one tunable parameter (in any symmetry class).
+To prove this, we return to the canonical parametrization of the SU(2) component (${\cal \bar{A}}$) of $\A$ [cf.\ \q{s3}].
+The necessary and sufficient condition for $\delta \lambda{\equiv}\pi$ is that ${\cal \bar{A}}(r_1,r_2,r_3,r_4)$ has eigenvalues $+i$ and $-i$; the latter condition is equivalent to setting $r_1{=}0$ in \q{s3} -- a condition on a single parameter.\footnote{For an alternative proof,   $\delta \lambda{\equiv}\pi$ is equivalent to ${ \bar{\cal A}}{=}Ve^{i\sigma_z\pi/2}V^{-1}$ for some unitary $V\in U(2)$.
+The manifold associated to $\delta \lambda{\equiv}\pi$ is then the space of unitary matrices  that do not commute with $e^{i\sigma_z\pi/2}$.
+The dimension of this manifold is the number of linearly-independent Hermitian generators (two) for unitaries that do not commute with $e^{i\sigma_z\pi/2}$.
+The codimension is then obtained from deducting two from the total number (three)  of linearly-independent Hermitian generators  for U(2).
+This approach of determining codimension is similar to that in [JHNR].}
+
+For exactly-degenerate orbits, the single parameter to attain destructive interference might be the chemical potential (as illustrated for the quantum oscillations of Na$_3$Bi in [topoferm]) or the orientation of the magnetic field; however $\lambda_a$ is independent of the field magnitude ($B$), as explained in \s{sec:codimexactdeg}.
+In principle, one may account for linear-in-$B$ corrections to $\lambda_a$ at stronger fields, however a quantitative theory for such corrections only exists (thus far) for non-degenerate orbits.[rothII,fischbeck,niu,fuchs]
+
+For quasidegenerate orbits,  $\lambda_a$ is expandable as a Laurent series in $B$ with leading term $1/B$ [cf.\ \q{lambdasmallB}], hence $B$ can be tuned to attain destructive interference.
+The slow variation of $\lambda_a$ compared to the action $l^2S$ [cf.\ \app{sec:slowvariation}] implies a beating pattern for the fundamental harmonic.
+In the weak-field, adiabatic regime, the antinodes of this pattern occur with period $2\pi/\delta S$ in $l^2$ [cf.\ \s{sec:introducecodimension}]; in the non-adiabatic regime, the antinodes are generically aperiodic [cf.\ \q{lambdasmallB}].
+Such beatings have been observed for semiconductor heterostructures[das,several more]; our contribution is the first quantitative theory  [summarized by the quantization rule of \qq{eq:rule}{berryconn} and the Lifshitz-Kosevich formula of \q{eq:LK}] from which one can calculate the beating pattern.
+
+\begin{figure}
+\includegraphics[width=1.0\columnwidth]{qo.png}
+\caption{Quantum oscillation of the Rashba-Dresselhaus 2DEG.
+(a) Evolution of $\delta\lambda$ with respect to the inverse field for different values of $\beta$.
+Horizontal grey lines are $\delta\lambda=\pi$.
+Upper panel of (b): Landau levels near fields indicated by vertical grey lines in right panel of (a) at $\beta=3(10^{5}$cm/s$\cdot\hbar$), corresponding to $\delta\lambda=0$, $\delta\lambda=\pi/2$ and $\delta\lambda=\pi$ respectively.
+The line of $\beta=3(10^{5}$cm/s$\cdot\hbar$) is indicated by a black arrow in (a).
+Lower panel (b): Oscillations of chemical potentials corresponding to upper panel.
+Fixed partical number density is assumed.
+In this figure, other parameters are $m=0.076m_e$, $\alpha=7.5(10^{5}$cm/s$\cdot\hbar$) and $E=0.4$eV.
+\label{fig:qo}}
+\end{figure}
+
+%For quasidegenerate orbits, the single parameter might be the magnitude ($B$) of the field.
+%Generically, $\delta \lambda$ nonlinearly depends on $l^2$, leading to an \textit{aperiodic} beating in the dHvA oscillation; in figure \ref{fig:qo} (a), Whenever $\delta\lambda$ reaches $\pi$ (resp.
+$0$), a beating node (resp.
+antinode) is expected.
+
+\subsection{Schubnikov-de Haas effect for quasidegenerate orbits in symmetry class 1-4}\la{sec:quantosc_quasideg}
+
+Let us focus on quasidegenerate orbits for which a single parameter ($B$) can be tuned to attain $\delta \lambda{\equiv}0$ (equivalently, to attain a Landau-level quasidegeneracy).
+These orbits lie in symmetry classes 1 to 4; in classes 1 and 2 further assumptions must be made about the symmetry representation, as explained in \s{sec:codimquasideg} and summarized in \tab{table:codimension}.
+
+We propose a signature for tunable quasidegeneracies in the  Schubnikov-de Haas effect at fixed particle density $n_e$, low temperature ($k_BT{\ll}\var_c$) and weak disorder ($\omega_c\tau_{\sma{D}}{\gg}1$).
+In this regime, it is known that minima of the longitudinal conductivity occur at discrete fields (denoted $B_{\nu}$)  where the filling is integer-valued;[vinter] the period of quantum oscillations is determined by the total density $n_e$ through $1/B_j{-}1/B_{j+1}{=}e/n_eh$.
+As $B$ increases through $B_j$, a Landau level is completely depopulated, leading to a periodic drop in the chemical potential ($\mu$) by the energy gap  between Landau levels, as illustrated in \fig{fig:qo}(b).
+Where $\delta\lambda{\equiv}\pi$,  Landau levels are  quasi-equidistant, hence adjacent minima (of conductivity) should be identically low.
+Where $\delta\lambda{\equiv}0$, every consecutive gap is small compared to $k_BT$ and $h/\tau_{\sma{D}}$, hence every other  minimum (of conductivity) is smeared out.[rashba] $0{\leq}\delta\lambda{\leq}{\pi}$ thus characterizes a smooth crossover between period-doubled and -undoubled oscillations, as representatively illustrated in \fig{fig:qo}(b).
+
+%This contrasts with the high-temperature, low-disorder beating discussed in  \s{sec:quantosc_equidis}, where the antinodes occur as $\delta \lambda{\equiv}\pi$.
+
+Our contribution is the exhaustive  identification of symmetry classes (1 to 4) for which such a crossover will occur.
+In particular, we are proposing that the crossover occurs for the Rashba-Dresselhaus 2DEG [cf.\ \q{hamRD}], whose quasidegenerate orbits fall into class 3.
+For this model,  Fig.\ \ref{fig:qo}(a) plots $\delta \lambda$ vs $1/B$ for various choices of the Dresselhaus coupling $\beta$.
+As expected from the codimension analysis of \s{sec:disrot}, half of the degeneracies ($\delta\lambda {\equiv}0{\equiv}2\pi$) are lifted by introducing nonzero $\beta$.
+
+%\textbf{please see if any information in paragraph below is worth merging into text above}
+%Fig.
+\ref{fig:qo}(b) lower panel presents chemical potential oscillation with respect to $1/B$ under the assumption of zero energy and zero Landau level broadening where $\delta\lambda{\approx}2\pi$, $\delta\lambda{\approx}3\pi/2$, $\delta\lambda{\approx}\pi$ respectively; the corresponding Landau-level dispersions are obtained from exact diagonalization and plotted in upper panel of Fig.
+\ref{fig:qo}(b).
+As expected, close to Landau level quasidegeneracy ($\delta\lambda\approx 0$), half of the oscillations are smeared out and the oscillation period has effectively doubled.
+This behavior is further confirmed by the oscillation of chemical potential plotted in lower left plot of Fig.
+\ref{fig:qo}(b).
+As a contrast, middle column of Fig \ref{fig:qo}(b) shows Landau levels and chemical potential oscillation for $\delta\lambda\approx 3\pi/2$, when quantum oscillation are expected to exhibit large and small oscillations.
+For $\delta\lambda\approx\pi$, the two sets of Landau levels are equally spaced and quantum oscillation are expected to reveal the particle density of the system.
+Generally, with hybridization between cyclotron orbits, we cannot expect the beating to be periodic.
+Therefore, for 2D fixed particle density systems, both oscillation period and oscillation magnitude are beating \textit{aperiodically} with respect to magnetic field.\textbf{[to say that a period is beating aperiodically is perhaps like referring to a snake as a lion, then complaining that the lion isn't snakelike]}
+
+%While the previous subsection has made no assumptions about the 
+%For spin-degenerate Landau levels, the period of quantum oscillation is solely determined by the (assumed constant) particle number density $n_e$ as $e/n_eh$ [Vinter].
+Minima of longitudinal conductivity occur at discrete fields (denoted $B_{\nu}$)  where the filling is even-integer-valued; as $B$ increases beyond $B_{\nu}$, the complete depopulation of spin-degenerate Landau levels is accompanied by a sudden drop in the chemical potential at zero temperature.
+
+%However, these minima may be smeared out by temperature or disorder.
+Whether the minimums are vulnerable to smearing depends on the Landau level gap, i.e., the magnitude of the jump of chemical potential.
+Larger Landau level gap prevents the conduction minimum from being smeared out and thus corresponds to oscillation of larger magnitude.
+This Landau level gap is governed by $\delta\lambda$.
+
+%surface states of 3D solids (insulators and metals, of both trivial and topological categories), as well as (ii) 2DEG in semiconductor heterostructures or 2D materials on substrates.
+Quantum oscillations of the chemical potential are generically negligible in case (i),
+
+% \footnote{Suppose $\mu$ is the field-dependent chemical potential of a 3D solid with surface states.
+Since $\mu$ is an intensive quantity, it may be approximated by the chemical potential $\mu'$ corresponding to the same 3D solid but with periodic boundary conditions in three independent directions.
+If said solid is an insulator, $\mu'$ would depend smoothly on $B$; if said solid is a metal, the quantum oscillations of $\mu'$ have negligible amplitude so long as the Fermi surface is not highly anisotropic.[lifshitz,kosevich] } and non-negligible in case (ii).
+
+%Traditionally, quantum oscillations of thermodynamic and transport quantities are best understood for nondegenerate orbits in the absence of breakdown; they originate from the periodic (in $1/B$) depopulation of discrete Landau levels as $B$ is ramped up.
+For spin-degenerate orbits in the absence of breakdown, it is the depopulation of every second Landau level that is periodic.
+With magnetic breakdown at isolated points, the harmonic content of quantum oscillations generically includes multiple periods corresponding to distinct orbits.
+A distinctive feature of spin-split bands is that quantum oscillations are generically aperiodic.
+
+%It is well known that quantum oscillations from two independent cyclotron orbits (but with similar area in reciprocal space) may also exhibit periodic beatings.
+This is due to Landau levels corresponding to the two orbits may also cross approximately (with a splitting $\sim e^{-c/B}$).
+Such crossings are not so surprising, and should be attributed to band conserving symmetry introduced in Sec.
+\ref{sec:introducecodimension}.
+In contrast, for weakly spin-split bands, the two orbits are strongly hybridized; nevertheless crossings exist and are tunable by $B$.
+The hybridization of the two sets of Landau levels destroy the periodic nature of approximate crossings and is reflected in an \emph{aperiodic} beating pattern.
+%merely reflect that distinct orbits are essentially uncoupled; this is very much analogous to the crossing of levels having different symmetry eigenvalues.
+In contrast, for weakly spin-split bands, the two orbits are strongly coupled by tunneling, hence there are no obvious `symmetry eigenvalues'; nevertheless crossings exist and are tunable by $B$.
+The hybridization of the two sets of Landau levels destroy the periodic nature of approximate crossings and is reflected in an \emph{aperiodic} beating pattern.
+
+% Another distinction: for localized breakdown, crossings occur only at $B\approx 0$, while for nonlocal breakdown they recur aperiodically  at fields denoted $B_n$.
+The recurrence interval for $1/B_n$ is much larger than the period of quantum oscillations, leading to an aperiodic beating effect in the quantum oscillations.
+
+\section{Discussion and outlook}\la{sec:discussion}
+
+\textbf{[work in progress]}
+Tunable parameters: B, orientation of B, bias voltage. The first is not applicable to exactly-degenerate orbits.
+For spin-split bands, $\lambda$ depends strongly on the $B$ field for quasidegenerate orbits; for degenerate orbits, the $B$-dependence of $\lambda$ is relatively weaker, i.e., of higher power in the small parameter $B$ [Roth, Niu, Fuchs].
+A more useful tuning parameter in the latter case would be the bias voltage in tunneling spectroscopy experiments.
+
+Application to $D>4$. Not uncommon to find spin-degenerate bands (in centrosymmetric solids) which are quasi-four-fold degenerate.
+
+Phase offset of quantum oscillations. Is it quantized for quasidegenerate orbits?
 
@@
 
-\textbf{[comment on higher-order-in-B corrections to lambda, which will lead at ultra-high fields to landau-level quasidegeneracies]}
-
 %In summary, we have developed a theory to calculate landau levels in the case of quasidegenerate orbits.
@@
 We are grateful to Nicholas Read and Judith H\"oller for clarifying notions related to codimensions of matrix degeneracies. 
-We acknowledge support by  the Yale Postdoctoral Prize Fellowship (AA), NSF DMR Grant No.\ 1603243 (LG),  the Ministry of Science and Technology of China, Grant No.\ 2016YFA0301001 (CW and WD), and the National Natural Science Foundation of China, Grants No.\ 11674188 and 11334006 (CW and WD).
+We acknowledge support by  the Yale Postdoctoral Prize Fellowship (AA), NSF DMR Grant No.\ 1603243 (LG),  the Ministry of Science and Technology of China, Grant No.\ 2016YFA0301001 (CW and WD), the National Natural Science Foundation of China, Grants No.\ 11674188 and 11334006 (CW and WD) and the Beijing Advanced Innovation Center for Future Chip (ICFC, CW and WD).
 This work was performed in part at Aspen Center for Physics, which is supported by National Science Foundation grant PHY-1607611.
+This work was supported in part by the Gordon and Betty Moore Foundation EPiQS Initiative through Grant No.
+GBMF4305 at the University of Illinois.
 \end{acknowledgments}
@@
 Effective Hamiltonian lies in the heart of semiclassical theory.
-The leading order term (with respect to $B$) of effective Hamiltonian in momentum representation can be obtained by Peierls substitution of crystal momentum $\boldsymbol{k}$: $\boldsymbol{k}\to\boldsymbol{K}=\boldsymbol{k}+\frac{e}{\hbar}\boldsymbol{A}(i\nabla_{\boldsymbol{k}})$ in zero field band structure $H_{0}(\boldsymbol{K}):=\epsilon(\boldsymbol{k})$, where $\boldsymbol{A}$ is vector potential.
+The leading order term (with respect to $B$) of effective Hamiltonian in momentum representation can be obtained by Peierls substitution of crystal momentum $\boldsymbol{k}$: $\boldsymbol{k}\to\boldsymbol{K}=\boldsymbol{k}+(e/\hbar)\boldsymbol{A}(i\nabla_{\boldsymbol{k}})$ in zero field band structure $\mathfrak{H}_{0}(\boldsymbol{K}):=\epsilon(\boldsymbol{k})$, where $\boldsymbol{A}$ is vector potential.
 Components of $\boldsymbol{K}$ do not commute with each other, thus substituting $\boldsymbol{k}$ to $\boldsymbol{K}$ is performed in a Weyl-symmetric manner that can be formally done using Fourier transformation.
-Wave functions in momentum representation are represented as $\phi=\sum_{\boldsymbol{k}}f_{\boldsymbol{k}}\psi_{\boldsymbol{k}}$, where $\psi_{\boldsymbol{k}}$ is modified Bloch wave function whose specific form is presented in [Roth].
+Wave functions in momentum representation are represented as $\phi=\sum_{\boldsymbol{k}}f_{\boldsymbol{k}}\psi_{\boldsymbol{k}}$, where $\psi_{\boldsymbol{k}}$ is modified Bloch wave function whose specific form is presented in Ref.
+[Roth].
 The effective Hamiltonian then acts on $f_{\boldsymbol{k}}$, changing Shr\"odinger equation to:
 \begin{equation}
-(H(\boldsymbol{K})-E)f_{\boldsymbol{k}}=0.\label{eq:schrodinger}
-\end{equation}
-Subleading order term of effective Hamiltonian $H_{1}(\boldsymbol{K})$ is also obtained by substituting $\boldsymbol{k}$ to $\boldsymbol{K}$ in $H_{1}(\boldsymbol{k})$, where $H_{1}(\boldsymbol{k})$ encodes information of non-Abelian Berry phase, orbital magnetization and Zeeman energy.
+(\mathfrak{H}(\boldsymbol{K})-E)f_{\boldsymbol{k}}=0.\label{eq:schrodinger}
+\end{equation}
+Subleading order term of effective Hamiltonian $\mathfrak{H}_{1}(\boldsymbol{K})$ is also obtained by substituting $\boldsymbol{k}$ to $\boldsymbol{K}$ in $\mathfrak{H}_{1}(\boldsymbol{k})$, where $\mathfrak{H}_{1}(\boldsymbol{k})$ encodes information of non-Abelian Berry connection, orbital moment and Zeeman energy.
 Assuming a magnetic field $B$ in $-z$ direction,
 \begin{equation}
-H_{1}(\boldsymbol{k})=eB\epsilon^{\alpha\beta}\mathfrak{X}^{\beta}v^{\alpha}+BM^{z}-g\mu_{B}B\sigma^{z}
-\end{equation}
-where $[\mathfrak{X}^{\alpha}]_{nm}=i\langle u_{n\boldsymbol{k}}|\partial_{k^{\alpha}}u_{m\boldsymbol{k}}\rangle$ is Berry connection, $[v^{\alpha}]_{nm}=\frac{1}{\hbar}\delta_{nm}\partial_{k^{\alpha}}\epsilon$ is band velocity, $M^{z}$ is orbital magnetization, $g\approx 2$ is the free-electron g-factor and $\mu_{B}$ is the Bohr magneton.
-Eq.
-(\ref{eq:schrodinger}) can be solved by WKB approximation.
-To the leading order, solution of Eq.
-(\ref{eq:schrodinger}) is Zilberman function
-\begin{equation}
-f_{k}=\frac{c}{\sqrt{|v^{x}|}}e^{ik_{0}^{x}k^{y}l^{2}}e^{-il^{2}\int k^{x}dk^{y}}\delta_{k_{0}^{x}k^{x}},
-\end{equation}
-where $c$ is an arbitrary constant and the integration is performed along constant energy contours.
-$k^x$ is a constant of motion in Landau gauge, which is why a $\delta_{k_{0}^{x}k^{x}}$ appears in Zilberman function.
-
-\section{Proof of quasi-degenerate quantization rule\label{app:quantizationruleproof}}
-
-\textbf{Give some motivation for why we might care about quasidegeneracy greater than two. E.g, new fermions, accidental degeneracies, mirror planes??}
-
-Since $\delta S=0$ without $\alpha\mathcal{W}$, $\alpha$ is proportional to $\delta S$ up to linear order.
-A good example is Rashba Hamiltonian in the main text, where $\delta S=4\pi m\alpha\sqrt{2m\epsilon}+\text{O}(\alpha^2).$  Thus
-\begin{equation}
-\mathcal{H}=
-\mathcal{H}_0+\delta S \mathcal{W}'+\text{O}(\delta S^2),
-\end{equation}
-where $\delta S \mathcal{W}'=\alpha \mathcal{W}$.
-We seek a generalized quantization condition of the form 
-\begin{equation}
-l^{2}S+\lambda_{a}+\gamma=2\pi n.
-\end{equation}
-In previously-studied quantization rules for non-degenerate and degenerate band subspaces, $\lambda$ is field-independent and of order one.
-The additional small parameter in quasi-degenerate magnetotransport allows to formulate a dimensionless quantity that is of order one: $l^2\delta S$.
-We therefore posit a field-dependent $\lambda$ that is  of order $\text{O}(1,l^2\delta S)$.
-
-To obtain a quantization rule up to order $\text{O}(1,l^2\delta S)$, we need to formulate an effective Hamiltonian that is accurate to $\text{O}(l^{-2},\delta S)$.  Following the
-idea of [Roth], it is not difficult to verify this effective Hamiltonian for a specific band is 
-\begin{align}
-H &= H_{0,0}+H_{1,0}+H_{0,1}+\text{o}(l^{-2}, \delta S),\\
-H_{0, 0}&=\epsilon_0(\boldsymbol{K}),\\
-[H_{0, 1}]_{nm}&=\delta S [\mathcal{W}'(\boldsymbol{K})]_{nm} = \alpha [\mathcal{W}(\boldsymbol{K})]_{nm},
-\end{align}
-where $\epsilon_0$ is band dispersion of $\mathcal{H}$ and $H_{1,0}(\boldsymbol{k})$ is still Eq. (\ref{eq:H1}) evaluated in the absence of $\alpha\mathcal{W}$. $\text{o}$ here is small-o notation
-
-We now group the  terms in effective Hamiltonian as $\tilde{H_0}=H_{0,0}$ and $\tilde{H}_{1}:=H_{1,0}+H_{0,1}$. The Schr\"odinger equation is now
-\begin{equation}
-(\tilde{H}_{0}(\boldsymbol{K})+\tilde{H}_{1}(\boldsymbol{K})-E)f=\text{o}(l^{-2}, \delta S).
-\end{equation}
+\mathfrak{H}_{1}(\boldsymbol{k})=BM_{z}-g_s\mu_{B}Bs_z/\hbar+eB\epsilon_{\alpha\beta}\mathfrak{X}_{\beta}v_{\alpha}.
+\end{equation}
+$\mathfrak{H}_0(\bK)$ and $\mathfrak{H}_1(\bK)$ defined above are applicable to $D$-fold exactly degenerate bands.
+
+Eq. (\ref{eq:schrodinger}) can be solved by WKB approximation. To the leading order (i.e., with $\mathfrak{H}_0(\bK)$ only), solutions of Eq. (\ref{eq:schrodinger}) are Zil'berman functions
+\begin{equation}
+g_{\bk}=\frac{1}{\sqrt{|v_x|}}e^{il^2k_x^0k_y}e^{-il^{2}\int k_x^\nu dk_y}\delta_{k_x^0 k_x},
+\end{equation}
+$k_x^\nu$ is a function of $k_y$ satisfying $\epsilon(k_x^\nu,k_y)=0$.
+Generally, $\epsilon(k_x^\nu,k_y)=0$ may have several solutions of $k_x$ for given $k_y$ and these solutions are indexed by $\nu$.
+$g_\bk$ above is expressed in Landau gauge, where $k_x=k_x^0$ is a constant of motion.
+
+\section{Proof of quasidegenerate quantization rule\label{app:quantizationruleproof}}
+
+In this appendix, we prove the quantization rule introduced in the main text in the framework of effective Hamiltonian (cf.
+App.
+\ref{app:revieweffham}).
+This proof is applicable to $D$-fold quasidegenerate bands, with $D>1$.
+Although less common than $D=2$, $D>2$ is relevant in some materials.
+For example, bands at $k_z=\pi$ plane of $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$-symmetric material with negligible SOC are four fold (quasi)degenerate.
+
+As stated in the main text, our start point is a decomposition of the Hamiltonian $\hat{H}$ into $\hat{H_0}$ and a perturbation $\zeta \hat{H}_1$, with $\zeta$ a dimensionless small parameter.
+The quasidegeneracy originates from $
+\zeta\hat{H}$ breaking the exactly $D$-fold degenerate bands of $\hat{H_0}$. For 2-fold quasidegeneracy, $\zeta$ can be chosen as $\delta S/S$ in the main text.
+
+The effective Hamiltonian $\effH$ is now governed by two small parameters: one is $1/l^2S$ due to the smallness of the field; one is $\zeta$ due to the assumption of quasidegeneracy.
+The zeroth order Hamiltonian is now $\effH_0=\epsilon_0(\bK)$, with $\epsilon_0(\bK)$ band structure of $\hat{H}_0$.
+The first order term of $\effH$ in $1/l^2S$ and $s$ is
+\begin{equation}
+\effH_1(\bk) = \zeta\epsilon_1(\bk)+B(M_{z}-g_s\mu_{B}s_{z}/\hbar+e\epsilon_{\alpha\beta}\mathfrak{X}_{\beta}v_{\alpha}). \label{effham1}
+\end{equation}
+$M_z$, $s_z$, $\mathfrak{X}$ and $v$ in Eq.(\ref{effham1}) should be evaluated in the band structure of $\hat{H_0}$.
+$\epsilon_1(\bk)$ is the projection of $\hat{H}_1$ to the D-fold degenerate bands of $\hat{H}_0$.
+
 Similar to what is done in [100page], we seek the solution to the Schr\"odinger equation using superposition\textbf{[strange way to put it]} of Zilberman-Fischbeck functions
@@
 \section{Codimension of Landau level quasidegeneracy}\la{app:codimension}
-
-In this appendix, we expose mathematical details of symmetry analysis of the quasidegenerate propagator $\A$ and derive symmetry constrained codimension of degeneracy manifold.
-We restrict our analysis to two-by-two $\A$.
 
@@
 
-Since direction of external magnetic field is fixed (pointing to $-z$ direction in our convention), only symmetry operators mapping $z$ to $\pm z$ are relevant for cyclotron orbits.
+In this appendix, we expose mathematical details of symmetry analysis of the quasidegenerate propagator $\A$ and derive symmetry constrained codimension of degeneracy manifold.
+We restrict our analysis to two-by-two $\A$.
+
+%Since direction of external magnetic field is fixed (pointing to $-z$ direction in our convention), only symmetry operators mapping $z$ to $\pm z$ are relevant for cyclotron orbits.
 These symmetry operators can be classified into ten and only ten classes [100p].
@@
 This reduction of relevant symmetry classes is due to components of $\calh$ transforming differently under symmetry operations.
-$\delta\epsilon$ transforms as a scalar but orbital moment and spin transforms as a pseudovector.
+$\delta\epsilon$ transforms as a scalar but $B\mathcal{M}$ as a pseudovector.
 The five symmetry classes are tabulated in Table \ref{table:codimension} in the main text.
-Here we calculate codimension of degeneracy manifold for all the ten classes since the other five classes are relevant for quantization rule of degenerate bands.
+Here we calculate codimension of degeneracy manifold for all the ten classes since the other five classes are relevant to exactly-degenerate bands.
 
 Sewing matrix is necessary to express the constraints on the propagator $\A$.
-\red{For a symmetry operator $\hat{g}$ acting on wave functions as $\hat{g}|\psi(\br)\rangle=|\psi(g^{-1}\br)\rangle$ [Really need to introduce $\check{g}$?]}, the sewing matrix $\breve{g}$ is defined as
+For a symmetry operator $\hat{g}$ acting on wave functions as $\hat{g}|\psi(\br)\rangle=|\psi(\check{g}^{-1}\br)\rangle$, the sewing matrix $\breve{g}$ is defined as
 \e{
@@
 }
-Here, $K$ is complex conjugation; $\hat{g}(\bk)=e^{-i\bk\cdot\hat{\br}}\hat{g}e^{i\bk\cdot\hat{\br}}$; $g\circ\bk$ is the image of $\bk$ under the action of $g$; $n$ and $m$ \textbf{[m=1,2,n=1,2]} runs over the degenerate subspace.
-Diagonalized representation matrix of unitary $\hat{g}$ introduced in the main text is sewing matrix in a special gauge, so we use the same symbol $\breve{g}$.
-\textbf{[introduce what this gauge freedom is, and what are gauge-invariant quantities]}
-
-Sewing matrix is needed to express symmetry constraints since there is an ambiguity in choosing the basis of degenerate subspace.
-Therefore, it can be drastically simplified if a good basis is chosen.
-\textbf{[give equation for how breveg is transformed with a different gauge choice]} Generally, we have the following rules for two-by-two sewing matrix:
+Here, $\hat{g}(\bk)=e^{-i\bk\cdot\hat{\br}}\hat{g}e^{i\bk\cdot\hat{\br}}$; $n=1,2$ and $m=1,2$ runs over the degenerate subspace of $\hat{H}_0$.
+By a basis transformation in the degenerate subspace as
+\e{
+|u_{n\bk}\rangle \to \sum_{m=1}^2|u_{m\bk}\rangle V_{mn}(\bk),
+}
+$\breve{g}$ transforms as
+\e{
+\breve{g}(\bk) \to V^\dagger(g\circ \bk)\breve{g}(\bk)K^{s(g)}V(\bk)K^{s(g)}.
+}
+Diagonalized representation matrix of unitary $\hat{g}$ introduced in the main text is sewing matrix in a special gauge, where $\hat{g}(\bk)$ maps $|u_n\rangle$ to itself up to a phase.
+This phase is called eigenvalue of the symmetry.
+We define order $N$ of $g$ as the smallest positive integer fulfilling $g^N$ is identity, $2\pi$ rotation, lattice translation or combination of them.
+
+The codimension calculation can be drastically simplified if a good gauge is chosen. Generally, we have the following rules for two-by-two sewing matrix:
 \begin{itemize}
@@
 For the special case of $\hat{g}$ that is order-2, $\breve{g}$ can be transformed into either $\sigma_z$  or $i\sigma_y$.
-We define order $N$ of $g$ as the smallest positive integer fulfilling $g^N$ is identity, $2\pi$ rotation, lattice translation or products of them.
-\textbf{[this definition of order should be moved up to above paragraphs where you introduce basic manipulations of sewing matrix]}
 \end{itemize}
-The first two claims are obvious \textbf{[it's only obvious once you give the equation for gauge-transform of breveg]} and the last claim can be verified by a direction calculation showing diagonal terms can be eliminated by a gauge transformation no matter what $\breve{g}$ is at the beginning.
-\textbf{[add this last proof in separate appendix]}
+The first two claims are obvious and the last claim can be verified by a direction calculation showing diagonal terms can be eliminated by a gauge transformation no matter what $\breve{g}$ is at the beginning (cf.
+App.
+\ref{app:makinggoffdiagonal}).
 
@@
 }
-\textbf{[define K to the power]} where $\A[\bk_f\leftarrow \bk_i]$ is a segment of the propagator from $\bk_i$ to $\bk_f$ along the cyclotron orbit.
+where $\A[\bk_f\leftarrow \bk_i]$ is a segment of the propagator from $\bk_i$ to $\bk_f$ along the cyclotron orbit.
 $e^{i\phi}$ is a phase factor that appears for $g$ that is a nonsymmorphic element; however this phase always drops out[100page] for closed orbits and will be neglected in the subsequent analysis.
@@
 }
-with $\cos(\varphi)=\text{Re}(\alpha)$.
+with $e^{i\varphi}=\text{Re}(\alpha)+i\sqrt{\text{Im}(\alpha)^2+|\beta|^2}$.
 The sufficient and necessary condition for $A_{1/N}^N \propto I$ is $\text{Re}(\alpha)=\cos(n\pi/N)$, with $n\in\mathbb{Z}$.
@@
 }
-\section{Two-by-two sewing matrix of antiunitary symmetry operator can be made off-diagonal}
+\section{Two-by-two sewing matrix of antiunitary symmetry operator can be made off-diagonal\label{app:makinggoffdiagonal}}
 
@@
 
-\section{Dimension of degeneracy manifolds}\la{app:nullity}
+\section{Dimension of degeneracy manifolds \textbf{[remove before post]}}\la{app:nullity}
 
@@
 In particular, $D^{\pm}_{ij}(\bze)$ is the identity matrix, which is consistent with $n=0$ manifold being a point; $D^{\pm}_{ij}(\pi,0,0)$ is a diagonal matrix with only a single nonzero entry ($-1$), which is consistent with the $n=1$ manifold being a two-sphere.
-\section{Reducing nonlocal magnetic breakdown to local magnetic breakdown}
+\section{Reducing nonlocal magnetic breakdown to local magnetic breakdown \textbf{[remove before post]}}
 We take Rashba-Zeeman model as an example, revealing that quantization rule for nonlocal magnetic breakdown, in the limit of $\Delta\gg\epsilon_c$, becomes quantization rule for local magnetic breakdown.
@@
 
-\section{Fixing discontinuity in magnetic breakdown with Zeeman coupling}
+\section{Fixing discontinuity in magnetic breakdown with Zeeman coupling \textbf{[remove before post]}}
 

### 2018-09-29 paper.tex
Updates from ShareLaTeX

@@
 \ref{fig:orbits}(a)] is much smaller than their average area:\footnote{The expressions for $\delta S$ and $S$ in \q{deltaSvsS} are asymptotically valid for $E{\gg}m\alpha^2$.}
-\e{\delta S = 2\pi k_E \f{2\alpha m}{\hbar^2} \ll S =\pi k_E^2; \;\; k_{E}:=\f{\sqrt{2m E}}{\hbar} .\la{deltaSvsS}}
+\e{\delta S = 2\pi k_E \f{2\alpha m}{\hbar^2} \ll S =\pi k_E^2; \;\; k_{E}:=\f{\sqrt{2m E}}{\hbar} .\label{deltaSvsS}}
 $S$ is equivalently the area of the circular, constant-energy contour in the absence of spin-orbit coupling ($\alpha{=}0$).
@@
 In the zeroth-order  solution, all Landau levels are spin-degenerate with a level spacing
-\e{ \var_c:=\f{2\pi}{l^2|\partial S/\partial E|}:=\f{\hbar^2}{ml^2}:=\f{h}{T_c}. \la{def:cyclotron}} 
+\e{ \var_c:=\f{2\pi}{l^2|\partial S/\partial E|}:=\f{\hbar^2}{ml^2}:=\f{h}{T_c}. \label{def:cyclotron}} 
 Here, $\var_c$ and $T_c$ are respectively the cyclotron energy and period of the zeroth-order orbit, and $m$ is the effective mass.
@@
 For example in the Rashba model, $\delta v_{\pm}/v=m\alpha/\hbar k_E{\sim}\delta S/S{\ll}1$.}
-\e{-\int_0^{T_c} (\delta \var_+{-}\delta \var_-) \frac{dt}{\hbar} \approx l^2\delta S. \la{spinsplitwkb}}
+\e{-\int_0^{T_c} (\delta \var_+{-}\delta \var_-) \frac{dt}{\hbar} \approx l^2\delta S. \label{spinsplitwkb}}
 %In the  Rashba model,   $\delta \var_{\pm}(E){=}{\pm} (\alpha/\hbar)\sqrt{2mE}$ is independent of $\bk$ due to a continuous rotational symmetry of $H_R$. \\
@@
 \e{
-M_z=\f{ie\hbar}{2}\sum_l'\f{\Pi_{x,ml}\Pi_{y,ln}-\Pi_{y,ml}\Pi_{x,ln}}{\epsilon_m-\epsilon_l}. \la{eq:orbitalmoment}
+M_z=\f{ie\hbar}{2}\sum_l'\f{\Pi_{x,ml}\Pi_{y,ln}-\Pi_{y,ml}\Pi_{x,ln}}{\epsilon_m-\epsilon_l}. \label{eq:orbitalmoment}
 }
@@
 There is finally a geometric contribution to the Zeeman interaction, which involves the two-by-two non-Abelian Berry connection  as well as the  zeroth-order band velocity:
-\e{\mathfrak{X}_{\beta,mn}{=}i\braket{u_m}{\partial u_n/\partial k_{\beta}},  \;\;v_{\alpha}:= \f{1}{\hbar}\p{\var}{k_{\alpha}},\la{berryconn}}
+\e{\mathfrak{X}_{\beta,mn}{=}i\braket{u_m}{\partial u_n/\partial k_{\beta}},  \;\;v_{\alpha}:= \f{1}{\hbar}\p{\var}{k_{\alpha}},\label{berryconn}}
 with $\{u_n\}_{n=1}^2$ the periodic component of Bloch functions in the quasidegenerate band. 
@@
 
-\subsection{Recovering the Onsager-Lifshitz-Roth quantization rules in two limits}\la{sec:recoveronsager}
+\subsection{Recovering the Onsager-Lifshitz-Roth quantization rules in two limits}\label{sec:recoveronsager}
 
@@
 By  neglecting  $B\calm_{+-}$ in favor of intraband elements,  $\cala$ reduces to a diagonal matrix with  diagonal entries ($e^{i\lambda_{\pm}}$) given by:
-\e{\lambda_{\sma{\pm}} = -\int_0^{T_c}\calh_{\sma{\pm\pm}}\f{dt}{\hbar}=\pm \f{1}{2}l^2\delta S - B\int_0^{T_c}\calm_{\sma{\pm\pm}}\f{dt}{\hbar}.  \la{phaseindependentorbit}} 
+\e{\lambda_{\sma{\pm}} = -\int_0^{T_c}\calh_{\sma{\pm\pm}}\f{dt}{\hbar}=\pm \f{1}{2}l^2\delta S - B\int_0^{T_c}\calm_{\sma{\pm\pm}}\f{dt}{\hbar}.  \label{phaseindependentorbit}} 
 In the second equality, we have applied \q{spinsplitwkb} and assumed that 
@@
 In the  energy basis of the Rashba Hamiltonian $H_R$ [cf.\ \q{eq:Rashba-Hamiltonian}],
-\e{\calh(\bk)=-\alpha k\tau_z{+}\f{g_s}{2}\mu_{\sma{B}}B\tau_x {-} \f{eB\hbar}{2m} (\tau_x-I) \epsilon_{\alpha\beta} k_{\alpha}\nabla_{\beta}\theta,\la{rashbaeffham}}
+\e{\calh(\bk)=-\alpha k\tau_z{+}\f{g_s}{2}\mu_{\sma{B}}B\tau_x {-} \f{eB\hbar}{2m} (\tau_x-I) \epsilon_{\alpha\beta} k_{\alpha}\nabla_{\beta}\theta,\label{rashbaeffham}}
 where $\tau_i$ are a new set of Pauli matrices with $\tau_z{=}{+} 1$ and ${-}1$ corresponding to the outer and inner orbits, respectively.
@@
 In the weak-hybridization regime: $l^2\delta S  \gg \pi|g_{\text{eff}}{-}2|$, we may expand \q{eq:Rashba-lambda} as a Laurent series in $B$:
-\e{\lambda_{\pm}= \pm \f{l^2\delta S}{2} +\pi \pm \f{\pi^2}{4}\f{(g_{\text{eff}}-2)^2}{l^2\delta S} + O(B^2). \la{lambdasmallB}}
+\e{\lambda_{\pm}= \pm \f{l^2\delta S}{2} +\pi \pm \f{\pi^2}{4}\f{(g_{\text{eff}}-2)^2}{l^2\delta S} + O(B^2). \label{lambdasmallB}}
 \q{eq:rule}, combined with the first two terms on the right-hand-side of \q{lambdasmallB}, may alternatively be derived from 
@@
 \begin{equation}
- H_{RD}(\bk)=\frac{{\hbar^2}k^2}{2m}+\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+\beta(k_{x}\sigma_{x}-k_{y}\sigma_{y}).\la{hamRD}
+ H_{RD}(\bk)=\frac{{\hbar^2}k^2}{2m}+\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+\beta(k_{x}\sigma_{x}-k_{y}\sigma_{y}).\label{hamRD}
 \end{equation}
@@
 (\ref{eq:rule}) (black lines) and numerical diagonalization of the Peierls-Onsager Hamiltonian  $H_{RD}(\bK)$ (red dots).
-Parameters for (b): $\alpha=7.5$($10^{5}$cm/s$\cdot\hbar$), $m=0.076m_e$, $\beta=3~(6)$($10^{5}$cm/s$\cdot\hbar$) for left (right) panels.
+Parameters for (b): $\alpha=7.5$($10^{5}$cm/s$\cdot\hbar$), $m=0.076m_0$, $\beta=3~(6)$($10^{5}$cm/s$\cdot\hbar$) for left (right) panels.
 (c) For various spin-orbit parameters $(\alpha,\beta)$ of the Rashba-Dresselhaus model and various field strength (satisfying $l^2S(E)\gg 1$), we plot  $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that lies closest to energy $E=0.4eV$, where $\epsilon_\text{rule}$ is determined by Eq.
@@
 We also plot in (d) $l^2\delta S^2/S$, which has a strong positive relation with error in (c).
-Parameters for (c-d): $m=0.076m_e$.
+Parameters for (c-d): $m=0.076m_0$.
 Units: $\alpha$($1.5\times 10^{5}$cm/s$\cdot\hbar$), $\beta$($1.5\times 10^{5}$cm/s$\cdot\hbar$), $l^2 S$($10^2$).\label{fig:RD}}
@@
 
-\subsection{Rashba 2DEG with in-plane Zeeman field}\la{sec:inplanezeeman}
+\subsection{Rashba 2DEG with in-plane Zeeman field}\label{sec:inplanezeeman}
 
@@
 \e{ 
-H_{RZ}=\f{{\hbar^2}k^{2}}{2m}+\delta \var; \;\;\;\delta \var=\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+\zpar\sigma_{y}, \la{eq:RZ-Hamiltonian}}
+H_{RZ}=\f{{\hbar^2}k^{2}}{2m}+\delta \var; \;\;\;\delta \var=\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+\zpar\sigma_{y}, \label{eq:RZ-Hamiltonian}}
 with $\zpar{:}{=}{g_s}\mu_B B_{\parallel}/2$.
@@
 $\delta E$ is extracted at 0.45eV and the II-Dirac point is located at 0.5eV.
-Parameters for lower panel of (b): $m$: 0.076$m_e$, $\alpha$: 1.5($10^{5}$cm/s$\cdot\hbar$), $Z_\parallel$: 1meV.
+Parameters for lower panel of (b): $m$: 0.076$m_0$, $\alpha$: 1.5($10^{5}$cm/s$\cdot\hbar$), $Z_\parallel$: 1meV.
 Out of plane Zeeman coupling is ignored here.
@@
 We only plotted in region where $0.4<\epsilon_0<1.0$(eV).\cite{RZfignote}, Units: $\alpha$($1.5\times 10^{5}$cm/s$\cdot\hbar$).
-Parameters for (d): $m=0.076m_e$, $l=100$\AA.
+Parameters for (d): $m=0.076m_0$, $l=100$\AA.
 \label{fig:RZ}}.
@@
 \e{
-\calh = -\alpha k_{E}\omega^{\sma{\perp}}_c t\,\sigma_x+(Z_\parallel-\alpha k_{E})\sigma_y-Z_\perp\sigma_z,\la{effhamIIDirac}
+\calh = -\alpha k_{E}\omega^{\sma{\perp}}_c t\,\sigma_x+(Z_\parallel-\alpha k_{E})\sigma_y-Z_\perp\sigma_z,\label{effhamIIDirac}
 }
@@
 Generally, the probability of tunneling across the hybridization-induced barrier is  $\rho^2{=}\exp(-2\pi\barmu)$, with $\barmu{=}{E_g}^2/{2v_d \hbar}$ and $E_g$ the energy gap at the center of the anticrossing;[Landau and lifshitz, Wittig] in this context,
-\e{\barmu=\frac{Z_\perp^2+(Z_\parallel-\alpha k_{E})^2}{2\alpha k_{E}\var^{\sma{\perp}}_c}, \la{mu1}}
+\e{\barmu=\frac{Z_\perp^2+(Z_\parallel-\alpha k_{E})^2}{2\alpha k_{E}\var^{\sma{\perp}}_c}, \label{mu1}}
 with $2\alpha k_E$ the spin-orbit splitting at energy $E$ [cf.\ \fig{fig:orbits}(a)].
@@
 To determine the Landau levels, one needs not just the probability for tunneling but also the phase of the probability amplitude. The full information is encoded in a scattering matrix [AALG]
-\e{\mathbb{S}=\matrixtwo{\tau e^{i\barphi}}{-\rho}{\rho}{\tau e^{-i\barphi}},\;\rho=e^{-\pi\barmu},\;\tau=\sqrt{1-\rho^{2}}\la{scattmat}}
+\e{\mathbb{S}=\matrixtwo{\tau e^{i\barphi}}{-\rho}{\rho}{\tau e^{-i\barphi}},\;\rho=e^{-\pi\barmu},\;\tau=\sqrt{1-\rho^{2}}\label{scattmat}}
 which is a connection formula that matches the two-component semiclassical (WKB) wavefunction across the Dirac point.
@@
 The time-ordered, coherent process of Landau-Zener tunneling/transmission and adiabatic dynamics is described by the propagator:
-\e{{\A}= \matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}} \diagmatrix{e^{i\tilde{\lambda}_+}}{e^{i\tilde{\lambda}_-}}. \la{propinplanezeeman}}
+\e{{\A}= \matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}} \diagmatrix{e^{i\tilde{\lambda}_+}}{e^{i\tilde{\lambda}_-}}. \label{propinplanezeeman}}
 The adiabatic phase $\tilde{\lambda}_{\pm}$ is the sum of a dynamical phase ${\pm} l^2 \delta S/2$ and  the single-band Berry phase $\phi^B_\pm$, for the outer ($+$) and inner ($-$) orbit respectively.
@@
 \text{cos}\left[\frac{\Omega_{-}+\Omega_{+}}{2}\right]=\tau\,\text{cos}\left[\frac{\Omega_{-}-\Omega_{+}}{2}+\bar{\varphi}\right], \lin
-\ins{with}\;\Omega_{\pm}=l^2 (S\pm \delta S/2)+\phi_{\pm}^B +\gamma_{\pm}, \la{coscos}
+\ins{with}\;\Omega_{\pm}=l^2 (S\pm \delta S/2)+\phi_{\pm}^B +\gamma_{\pm}, \label{coscos}
 }
@@
 
-\subsection{Relating the eigenvalue-degeneracy of $\A$ to the quasidegeneracy of Landau levels}\la{sec:relatedegeneracies}
+\subsection{Relating the eigenvalue-degeneracy of $\A$ to the quasidegeneracy of Landau levels}\label{sec:relatedegeneracies}
 
@@
 For fixed $\bar{B}$, we are therefore guaranteed to find a number (of order one) of paired Landau levels  in close proximity to $\bar{E}$, with each pair having an energetic splitting of order:
-\e{\bigg|\f{E_{1}-E_2}{\var_c}\bigg|_{B=\bar{B}} = \order\left( \f{\partial \lambda_a/\partial E}{\bar{l}^2\partial  S/\partial E}  \right)\ll 1,\la{llquasideg}}
+\e{\bigg|\f{E_{1}-E_2}{\var_c}\bigg|_{B=\bar{B}} = \order\left( \f{\partial \lambda_a/\partial E}{\bar{l}^2\partial  S/\partial E}  \right)\ll 1,\label{llquasideg}}
 with $\bar{l}$ magnetic length of $\bar{B}$.
 Alternatively, we may fix $\bar{E}$ and investigate how Landau levels disperse as a function of $B$; the analog of \q{llquasideg}  is the existence of paired Landau levels in close proximity to $\bar{l}^2$, with a splitting of order:
-\e{\bigg|\f{l^2_{+}-l^2_-}{T_{{l^2}}}\bigg|_{E=\bar{E}} = O\left( \f{1}{S}\p{\lambda_a}{l^2} \right)\ll 1,\;\; T_{{l^2}}:=\f{2\pi}{S(\bar{E})}.\la{llquasidegB} }
+\e{\bigg|\f{l^2_{+}-l^2_-}{T_{{l^2}}}\bigg|_{E=\bar{E}} = O\left( \f{1}{S}\p{\lambda_a}{l^2} \right)\ll 1,\;\; T_{{l^2}}:=\f{2\pi}{S(\bar{E})}.\label{llquasidegB} }
 $\partial \lambda_a/\partial l^2$ is estimated in \app{sec:slowvariation}, and
@@
 
-\subsection{Codimension analysis without symmetry, and with band-conservation symmetry}\la{sec:introducecodimension}
+\subsection{Codimension analysis without symmetry, and with band-conservation symmetry}\label{sec:introducecodimension}
 
@@
 In the canonical parametrization of $\text{SU}(2)$ over the three-sphere $S^3$:
-\e{{\cal \bar{A}}{=}\matrixtwo{r_1{+}ir_2}{r_3{+}ir_4}{{-}r_3{+}ir_4}{r_1{-}ir_2},\;\; \sum_{j=1}^4r_j^2{=}1,\;\; r_j\in \mathbb{R},  \la{s3}}
+\e{{\cal \bar{A}}{=}\matrixtwo{r_1{+}ir_2}{r_3{+}ir_4}{{-}r_3{+}ir_4}{r_1{-}ir_2},\;\; \sum_{j=1}^4r_j^2{=}1,\;\; r_j\in \mathbb{R},  \label{s3}}
 ${\cal \bar{A}}{=}{\pm}I$ lie on distinct points of $S^3$, and are attainable by tuning three real parameters: $r_2{=}r_3{=}r_4{=}0$.
@@
 
-\subsection{Codimension reduction for the Rashba 2DEG}\la{sec:singleparameterrashba}
+\subsection{Codimension reduction for the Rashba 2DEG}\label{sec:singleparameterrashba}
 
@@
 
-\subsubsection{With continuous rotational symmetry}\la{sec:ctsrot}
+\subsubsection{With continuous rotational symmetry}\label{sec:ctsrot}
 
@@
 Consequently, the propagator [cf.\ \q{eq:prop}] simplifies to the exponential form:
-\e{\A{=}\exp(-2\pi i\sum_{j}r_j\tau_j),\la{expform}}
+\e{\A{=}\exp(-2\pi i\sum_{j}r_j\tau_j),\label{expform}}
 where
@@
 
-\subsubsection{With discrete rotational symmetry}\la{sec:disrot}
+\subsubsection{With discrete rotational symmetry}\label{sec:disrot}
 
@@
 implies that the propagator over the time interval $[T_c/2,0]$ is symmetry-related to that over $[T_c,T_c/2]$:
-\e{\A=\A_{T_c\leftarrow T_c/2}\A_{T_c/2\leftarrow 0}=\sigma_z{\A}_{T_c/2\leftarrow 0}\sigma_z {\A}_{T_c/2\leftarrow 0}.\la{eq:sigmazconstraint}}
+\e{\A=\A_{T_c\leftarrow T_c/2}\A_{T_c/2\leftarrow 0}=\sigma_z{\A}_{T_c/2\leftarrow 0}\sigma_z {\A}_{T_c/2\leftarrow 0}.\label{eq:sigmazconstraint}}
 The tracelessness of $\calh$ (at each $\bk$) implies that  ${\A}_{\sma{T_c/2\leftarrow 0}}$  has unit determinant. 
@@
 
-\subsection{Codimension reduction for 2DEG with distinct, symmetry-related II-Dirac points}\la{sec:rotsymmbreakdown}
+\subsection{Codimension reduction for 2DEG with distinct, symmetry-related II-Dirac points}\label{sec:rotsymmbreakdown}
 
@@
 We begin with a minimal, $\mathfrak{c}_2$-symmetric model:
-\e{H=\f{{\hbar^2}k^2}{2m_1}+ \bigg(\f{{\hbar^2}k^2}{2m_2}-\mu\bigg)\sigma_z +wk_y\sigma_x,\la{modelC2breakdown}}
+\e{H=\f{{\hbar^2}k^2}{2m_1}+ \bigg(\f{{\hbar^2}k^2}{2m_2}-\mu\bigg)\sigma_z +wk_y\sigma_x,\label{modelC2breakdown}}
 with $0{<}m_1{\ll}m_2$ and positive $\mu$.  The $\mathfrak{c}_2$ symmetry manifests as $\sigma_z H(\bk)\sigma_z{=}H({-}\bk)$, and relates 
@@
 In the vicinity of either point, the  Hamiltonian has the linearized form 
-\e{H_{\pm} =\pm {\hbar}\sqrt{\f{2\mu}{m_2}}\bigg(\frac{m_2}{m_1}+\sz\bigg)\delta k_x+w\delta k_{y}\sx+\epsilon_0, \la{linearHam2}}
+\e{H_{\pm} =\pm {\hbar}\sqrt{\f{2\mu}{m_2}}\bigg(\frac{m_2}{m_1}+\sz\bigg)\delta k_x+w\delta k_{y}\sx+\epsilon_0, \label{linearHam2}}
 from which we deduce that both Dirac points are  type-II if $m_1{<}m_2$; we further assume $m_1{\ll}m_2$ so that the quasidegeneracy condition ($\delta S/S$) is satisfied.
@@
 For sufficiently weak field, interband tunneling is localized near either II-Dirac point, and occurs with the Landau-Zener probability:
-\e{\rho^2=e^{-2\pi\bar{\mu}}, \; \bar{\mu}=\f{\big(Z_{\perp}^2+(m_1/m_2)^2(E-\epsilon_0)^2\big)l^2}{2w\sqrt{2E/m_1}}. \la{landauzenerc2} }
+\e{\rho^2=e^{-2\pi\bar{\mu}}, \; \bar{\mu}=\f{\big(Z_{\perp}^2+(m_1/m_2)^2(E-\epsilon_0)^2\big)l^2}{2w\sqrt{2E/m_1}}. \label{landauzenerc2} }
 Elsewhere, an electron undergoes adiabatic (band-conserving) dynamics.
@@
 \e{\A={e^{i(\tilde{\lambda}_++\tilde{\lambda}_-)}}\left(\matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}}{\diagmatrix{e^{i\f{\tilde{\lambda}_+-\tilde{\lambda}_-}{2}}}{e^{i\f{\tilde{\lambda}_--\tilde{\lambda}_+}{2}}}} \right)^2.
-\la{propC2breakdown}}
+\label{propC2breakdown}}
 The half-period propagator may be taken from \qq{scattmat}{propinplanezeeman}, with  $\bar{\mu}$ here given by \q{landauzenerc2}, and  $\tilde{\lambda}_{\pm}{=}{\pm}l^2\delta S/4$ plus a field-independent geometric phase.
@@
 \tau\cos\f{\Delta}{2}= \begin{cases} 0, & {\A}=+I \\
-                 \pm 1, & \A =-I\end{cases}.\la{c2breakdowndgncondition}
+                 \pm 1, & \A =-I\end{cases}.\label{c2breakdowndgncondition}
 \end{align}
@@
 
-\subsection{The ten-fold table for symmetry constrained codimensions}\la{sec:tenfold}
+\subsection{The ten-fold table for symmetry constrained codimensions}\label{sec:tenfold}
 
@@
 
-\subsubsection{Ten-fold classification of orbits}\la{sec:reviewtenfold}
+\subsubsection{Ten-fold classification of orbits}\label{sec:reviewtenfold}
 
@@
 \begin{align}
-&g: \vectwo{\br}{t} \rightarrow \matrixtwo{\check{g}}{0}{0}{ (-1)^{s(g)}}\vectwo{\br}{t}+\vectwo{\bdelta}{0}, \la{definesg}
+&g: \vectwo{\br}{t} \rightarrow \matrixtwo{\check{g}}{0}{0}{ (-1)^{s(g)}}\vectwo{\br}{t}+\vectwo{\bdelta}{0}, \label{definesg}
 \end{align}
@@
 $\check{g}$ is the matrix representation of $g$ in real space, and the corresponding action of  $g$ on the crystal wavevector is
-\e{\bk \rightarrow g\circ\bk := (-1)^{s(g)}\check{g}\bk. \la{gmapk}}
+\e{\bk \rightarrow g\circ\bk := (-1)^{s(g)}\check{g}\bk. \label{gmapk}}
 Given $\hat{H}$ and the orientation of the magnetic field, electrons follow orbits (denoted $\frako$) that are confined to field-orthogonal $\bk$-planes.
@@
 
-\subsection{Single-parameter tunability for the destructive interference of the fundamental harmonic}\la{sec:quantosc_equidis}
+\subsection{Single-parameter tunability for the destructive interference of the fundamental harmonic}\label{sec:quantosc_equidis}
 
@@
 Horizontal grey lines are $\delta\lambda=\pi$.
-Upper panel of (b): Landau levels near fields indicated by vertical grey lines in right panel of (a) at $\beta=3(10^{5}$cm/s$\cdot\hbar$), corresponding to $\delta\lambda=0$, $\delta\lambda=\pi/2$ and $\delta\lambda=\pi$ respectively.
-The line of $\beta=3(10^{5}$cm/s$\cdot\hbar$) is indicated by a black arrow in (a).
-Lower panel (b): Oscillations of chemical potentials corresponding to upper panel.
+Upper panel of (b): Landau levels near fields indicated by vertical grey lines in (a) at $\beta=3.0(10^{5}$cm/s$\cdot\hbar$), corresponding to $\delta\lambda=0$, $\delta\lambda=\pi/2$ and $\delta\lambda=\pi$ respectively.
+The line of $\beta=3.0(10^{5}$cm/s$\cdot\hbar$) is indicated by a black arrow in (a).
+Lower panel (b): Oscillations of chemical potentials corresponding to the upper panel.
 Fixed partical number density is assumed.
-In this figure, other parameters are $m=0.076m_e$, $\alpha=7.5(10^{5}$cm/s$\cdot\hbar$) and $E=0.4$eV.
+In this figure, other parameters are $m=0.076m_0$, $\alpha=7.5(10^{5}$cm/s$\cdot\hbar$) and $E=0.4$eV.
 \label{fig:qo}}
@@
 
-\subsection{Schubnikov-de Haas effect for quasidegenerate orbits in symmetry class 1-4}\la{sec:quantosc_quasideg}
+\subsection{Schubnikov-de Haas effect for quasidegenerate orbits in symmetry class 1-4}\label{sec:quantosc_quasideg}
 
@@
 
-\section{Discussion and outlook}\la{sec:discussion}
+\section{Discussion and outlook}\label{sec:discussion}
 
@@
 Components of $\boldsymbol{K}$ do not commute with each other, thus substituting $\boldsymbol{k}$ to $\boldsymbol{K}$ is performed in a Weyl-symmetric manner that can be formally done using Fourier transformation.
-Wave functions in momentum representation are represented as $\phi=\sum_{\boldsymbol{k}}f_{\boldsymbol{k}}\psi_{\boldsymbol{k}}$, where $\psi_{\boldsymbol{k}}$ is modified Bloch wave function whose specific form is presented in Ref.
+For a single band, the wave function in reciprocal space are expanded as $\phi=\sum_{\boldsymbol{k}}f_{\boldsymbol{k}}\psi_{\boldsymbol{k}}$, where $\psi_{\boldsymbol{k}}$ is modified Bloch wave function whose specific form is presented in Ref.
 [Roth].
@@
 \end{equation}
-Subleading order term of effective Hamiltonian $\mathfrak{H}_{1}(\boldsymbol{K})$ is also obtained by substituting $\boldsymbol{k}$ to $\boldsymbol{K}$ in $\mathfrak{H}_{1}(\boldsymbol{k})$, where $\mathfrak{H}_{1}(\boldsymbol{k})$ encodes information of non-Abelian Berry connection, orbital moment and Zeeman energy.
+Subleading order term of effective Hamiltonian $\mathfrak{H}_{1}(\boldsymbol{K})$ is also obtained by substituting $\boldsymbol{k}$ to $\boldsymbol{K}$ in $\mathfrak{H}_{1}(\boldsymbol{k})$, where $\mathfrak{H}_{1}(\boldsymbol{k})$ encodes information of Berry connection, orbital moment and Zeeman energy.
 Assuming a magnetic field $B$ in $-z$ direction,
@@
 \end{equation}
-$\mathfrak{H}_0(\bK)$ and $\mathfrak{H}_1(\bK)$ defined above are applicable to $D$-fold exactly degenerate bands.
 
@@
 \begin{equation}
-g_{\bk}=\frac{1}{\sqrt{|v_x|}}e^{il^2k_x^0k_y}e^{-il^{2}\int k_x^\nu dk_y}\delta_{k_x^0 k_x},
-\end{equation}
-$k_x^\nu$ is a function of $k_y$ satisfying $\epsilon(k_x^\nu,k_y)=0$.
-Generally, $\epsilon(k_x^\nu,k_y)=0$ may have several solutions of $k_x$ for given $k_y$ and these solutions are indexed by $\nu$.
+g_{\bk}^\nu=\frac{1}{\sqrt{|v_x^\nu|}}e^{il^2k_x^0k_y}e^{-il^{2}\int k_x^\nu dk_y}\delta_{k_x^0 k_x},
+\end{equation}
+$k_x^\nu$ is a function of $k_y$ satisfying $\epsilon(k_x^\nu,k_y)=0$ and quantities with a superscript $\nu$ should be evaluated at $\bk = (k_x^\nu, k_y)$.
+Generally, $\epsilon(k_x^\nu,k_y)=0$ have several solutions of $k_x$ for a given $k_y$ and these solutions are indexed by $\nu$.
 $g_\bk$ above is expressed in Landau gauge, where $k_x=k_x^0$ is a constant of motion.
+Quantization rule for cyclotron motion may be obtained by solving boundary condition equations of $f_{\bk} = \sum_\nu g_{\bk}^\nu$ at turning points.
 
@@
 
-As stated in the main text, our start point is a decomposition of the Hamiltonian $\hat{H}$ into $\hat{H_0}$ and a perturbation $\zeta \hat{H}_1$, with $\zeta$ a dimensionless small parameter.
-The quasidegeneracy originates from $
-\zeta\hat{H}$ breaking the exactly $D$-fold degenerate bands of $\hat{H_0}$. For 2-fold quasidegeneracy, $\zeta$ can be chosen as $\delta S/S$ in the main text.
-
-The effective Hamiltonian $\effH$ is now governed by two small parameters: one is $1/l^2S$ due to the smallness of the field; one is $\zeta$ due to the assumption of quasidegeneracy.
-The zeroth order Hamiltonian is now $\effH_0=\epsilon_0(\bK)$, with $\epsilon_0(\bK)$ band structure of $\hat{H}_0$.
-The first order term of $\effH$ in $1/l^2S$ and $s$ is
-\begin{equation}
-\effH_1(\bk) = \zeta\epsilon_1(\bk)+B(M_{z}-g_s\mu_{B}s_{z}/\hbar+e\epsilon_{\alpha\beta}\mathfrak{X}_{\beta}v_{\alpha}). \label{effham1}
-\end{equation}
-$M_z$, $s_z$, $\mathfrak{X}$ and $v$ in Eq.(\ref{effham1}) should be evaluated in the band structure of $\hat{H_0}$.
+As stated in the main text, our start point is a decomposition of the Hamiltonian $\hat{H}$ into $\hat{H_0}$ and a perturbation $\delta\hat{H}=\eta\hat{H}_1$, with $\eta$ a dimensionless small parameter.
+The quasidegeneracy originates from $\zeta\hat{H}$ breaking the exactly $D$-fold degenerate bands of $\hat{H_0}$.
+For 2-fold quasidegeneracy, $\eta$ can be chosen as $\delta S/S$ in the main text.
+
+The effective Hamiltonian $\effH$ is now governed by two small parameters: one is $1/l^2S$ due to the smallness of the field; one is $\eta$ due to the assumption of quasidegeneracy.
+The zeroth order (in the sense of both small parameters) Hamiltonian is now $\effH_0=\epsilon_0(\bK)$, with $\epsilon_0(\bK)$ band structure of $\hat{H}_0$.
+The first order term of $\effH$ in $1/l^2S$ and $\eta$ is
+\begin{equation}
+\effH_1(\bk) = \eta\epsilon_1(\bk)+B(M_{z}-g_s\mu_{B}s_{z}/\hbar+e\epsilon_{\alpha\beta}\mathfrak{X}_{\beta}v_{\alpha}). \label{effham1}
+\end{equation}
+$M_z$, $s_z$, $\mathfrak{X}$ and $v$ in Eq.
+(\ref{effham1}) should be evaluated in the band structure of $\hat{H_0}$.
 $\epsilon_1(\bk)$ is the projection of $\hat{H}_1$ to the D-fold degenerate bands of $\hat{H}_0$.
-
-Similar to what is done in [100page], we seek the solution to the Schr\"odinger equation using superposition\textbf{[strange way to put it]} of Zilberman-Fischbeck functions
-\begin{equation}
-\boldsymbol{f}=A\boldsymbol{f}^{0},
+In the main text, $\effH_1(\bk)$ is written as $\H(\bk)$.
+
+Similar to what is done in Ref. [100page], we seek the solution to the Schr\"odinger equation using the following multicomponent wave function ansatz
+\begin{equation}
+\boldsymbol{f}^\nu=\A^\nu\boldsymbol{g}^\nu,
 \end{equation}
@@
 \begin{equation}
-f_{a}^{0}=c_{a}\frac{1}{\sqrt{|v_0^{x}|}}e^{ik_{0}^{x}k^{y}l^{2}}e^{-il^{2}\int k^{x}dk^{y}}\delta_{k_{0}^{x}k^{x}}.
-\end{equation}
-$A$ is a square matrix with the assumption $A_{ab}$ is of order $O(1,l^2\delta S)$. Following section V of [100page], we have:
-\begin{widetext}
-\begin{equation}
-[H_{0}(\boldsymbol{K})]_{ab}A_{bc}f_{c}^{0}=A_{ac}\epsilon_0(\boldsymbol{K})f_{c}^{0}+il^{-2}\partial_{y}A_{ac}\hbar v_0^{x}f_{c}^{0}+\text{o}(l^{-2}, \delta S),
-\end{equation}
+g_a^\nu=c_{a}^\nu\frac{1}{\sqrt{|v_x^\nu|}}e^{ik^{0}_{x}k_{y}l^{2}}e^{-il^{2}\int k_{x}^\nu dk_{y}}\delta_{k^{0}_{x}k_{x}},~a\in{1..D}
+\end{equation}
+and $c_a^\nu$ is $\bk$ independent.
+$\A^\nu$ is a $k_y$ dependent square matrix with the assumption $\A_{ab}^\nu$ is of order $\order(1, \eta l^2)$, with $\order(a, b)$ big-O notation indicating order of magnitude of either $a$ or $b$ (whichever is larger).
+Following section V A 2 of Ref.
+[100page],:
+\e{
+[\effH_{0}(\boldsymbol{K})]_{ab}\A_{bc}^\nu g_{c}^\nu=&\A_{ac}^\nu\epsilon_0(\bK)g_{c}^\nu+i\hbar l^{-2} v_{x}^\nu(\partial_{y}\A_{ac}^\nu)g_{c}^\nu\nonumber\\
+&+\text{o}(l^{-2}, \eta),
+}
 and
 \begin{equation}
-[\tilde{H}_{1}(\boldsymbol{K})]_{ab}A_{bc}f_{c}^{0}=[\tilde{H}_{1}]_{ab}A_{bc}f_{c}^{0}+\text{o}(l^{-2}, \delta S).
-\end{equation}
-\textbf{[Let's clarify at what wavevector tildeH1 is supposed to be evaluated.
-Let's also write out explicitly the next order term in B10, which is proportional to the spin-orbit-induced change in the band velocity.
-At two points in the paper, I said that the relative change in velocity must be small, so here it will be justified.
-]}
-\end{widetext}
-
-Sch\"rodinger equation then becomes 
-\begin{equation}
-il^{-2}\partial_{y}A_{ac}\hbar v^{x}f_{c}^{0}+[\tilde{H}_{1}]_{ab}A_{bc}f_{c}^{0}=\text{o}(l^{-2}, \delta S).
-\end{equation}
-We want the above equation to hold for any $\mathbf{c}$, so 
-\begin{equation}
-\hbar\partial_{y}A_{ac}=il^{2}[v^{x\nu}]^{-1}[\tilde{H}_{1}]_{ab}A{}_{bc},
-\end{equation}
-thus
-\begin{equation}
-A=\overline{\text{exp}}[il^{2}\int\frac{\tilde{H}_{1}}{\hbar v_0^{x}}dk^{y}].
-\end{equation}
-$\lambda_{a}$ are again given by eigenphases of propagator $A$ along a complete orbit
-\begin{equation}
-\mathcal{A}[\mathfrak{o}]=\overline{\exp}[il^{2}\oint_{\mathfrak{o}}\frac{\tilde{H}_{1}}{\hbar v_0^{x}}dk^{y}].
-\end{equation}
-
-\section{Consistency conditions for our quantization rule}\la{sec:slowvariation}
-
-The following are consistency conditions for our quantization rule:
+[\effH_{1}(\bK)]_{ab}\A_{bc}^\nu g_{c}^\nu=[\effH_{1}]_{ab}\A_{bc}^\nu g_{c}^\nu+\text{o}(l^{-2}, \eta),\label{effH1onA}
+\end{equation}
+where $\text{o}$ is small-o notation.
+One term omitted in Eq.
+(\ref{effH1onA}) in $\text{o}(l^{-2},\eta)$ is $i l^{-2}(\partial_{y}A_{ac}^\nu)g_{c}^\nu d\effH_1/dk_x$.
+This omission can be justified if terms in Eq.
+({\ref{effham1}}), including the change of velocity due to $\delta\hat{H}$, are not anomalously large.
+
+Sch\"rodinger equation then reads 
+\begin{equation}
+i\hbar l^{-2} v_{x}^\nu (\partial_{y}\A_{ac}^\nu)  g_{c}^\nu+[\effH_{1}]_{ab}\A_{bc}^\nu g_{c}^\nu=\text{o}(l^{-2}, \eta).
+\end{equation}
+For the above equation to hold for any $\mathbf{c}$,
+\begin{equation}
+\hbar\partial_{y}\A_{ac}^\nu=il^{2}[v_{x}^\nu]^{-1}[\effH_{1}]_{ab}\A_{bc}^\nu.
+\end{equation}
+Therefore,
+\begin{equation}
+\A^\nu=\overline{\exp}[il^{2}\int\frac{\effH_{1}}{\hbar v_{x}^\nu}dk_{y}],
+\end{equation}
+Eq. ({\ref{eq:prop}}) can be obtained by solving boundary conditions at turning points.
+
+\section{Consistency conditions for the quasidegenerate quantization rule}\label{sec:slowvariation}
+
+The following are consistency conditions for the quasidegenerate quantization rule:
 \e{ |l^2S| \gg |\lambda_a|,\, \left|l^2\p{S}{E}\right| \gg \left|\p{\lambda_a}{E}\right|,\, \left|S\right| \gg \left|\p{\lambda_a}{l^2}\right|.} 
@@
 Analogously, for $\lambda_a$ to vary by $2\pi$ due to a variation of $E$ (at fixed field) by $\delta E$, we estimate [from \q{phaseindependentorbit}] that $\delta E {\sim} 2\pi/l^2 (\partial \delta S/\partial E)$, which is generically much larger than the cyclotron energy $\epsilon_c{=}2\pi/l^2 (\partial  S/\partial E)$.
-In the strong-field regime (where $\delta \var$ may be neglected from \q{eq:H1}), $\lambda_a$ is independent of $B$ (to the accuracy of our semiclassical theory\textbf{[add footnote to describe higher order corrections]}), and depends on $E$ solely through the slow variation of $\calm$.
+In the strong-field regime (where $\delta \var$ may be neglected from \q{eq:H1}), $\lambda_a$ is independent of $B$ (to the accuracy of semiclassical theory), and depends on $E$ solely through the slow variation of $\calm$.
 In the absence of symmetry, we estimate
 \e{\p{\lambda_{a}}{E}=\order\left(\f{g_s}{m_0}\p{m}{E},\f{\partial^2S/\partial E^2}{\partial S/\partial E} \right)\ll \f{2\pi}{\var_c},} 
-where $\order(a,b)$ is defined as the order of magnitude of either $a$ or $b$ (whichever is larger), $m_0$ is the free-electron mass, and $m{=}\hbar^2(\partial S/\partial E)/2\pi$ the effective mass.
-The first argument of $\order$ originates from the energy dependence of the effective g-factor (with $g_s$ the free-electron g-factor, and $m/m_0$ the dimensionless effective mass); the second argument accounts for possible non-analyticities in the area of $\frako_0$, which may originate from saddle- or II-Dirac points in the zeroth-order band Hamiltonian.
-
-\section{Existence of Landau-level quasidegeneracy}\la{sec:proofLLquasideg}
+where $m_0$ is the free-electron mass, and $m{=}\hbar^2(\partial S/\partial E)/2\pi$ the effective mass.
+The first argument of $\order$ originates from the energy dependence of the effective $g$-factor; the second argument accounts for possible non-analyticities in the area of $\frako_0$, which may originate from saddle- or II-Dirac points in the zeroth-order band Hamiltonian.
+
+\section{Existence of Landau-level quasidegeneracy}\label{sec:proofLLquasideg}
 
@@
 Generically, either of $m_{\pm}:=\calq_{\pm}(\bar{E},\bar{B})\in \R$ is not integer-valued, but 
-\e{\big(\calq_{+}-\calq_{-}\big)\bigg|_{\bar{E},\bar{B}}=\f{\lambda_+-\lambda_-}{2\pi}\bigg|_{\bar{E},\bar{B}} \in \Z. \la{diffinteger}} 
+\e{\big(\calq_{+}-\calq_{-}\big)\bigg|_{\bar{E},\bar{B}}=\f{\lambda_+-\lambda_-}{2\pi}\bigg|_{\bar{E},\bar{B}} \in \Z. \label{diffinteger}} 
 Let $n_{\pm}$ be the closest integer to $m_{\pm}$ (this implies $|n_{\pm}-m_{\pm}|<1$).
@@
 We estimate
-\e{\f{E_+-E_-}{\var_c} \approx &\; \f{r}{\var_c}\left(\f1{\calq'_+}-\f1{\calq'_-}\right)\approx  \f{r}{2\pi}\var_c \left( \lambda'_- -\lambda'_+\right). \la{estimate}}
+\e{\f{E_+-E_-}{\var_c} \approx &\; \f{r}{\var_c}\left(\f1{\calq'_+}-\f1{\calq'_-}\right)\approx  \f{r}{2\pi}\var_c \left( \lambda'_- -\lambda'_+\right). \label{estimate}}
 What is left is to estimate $\lambda_{\pm}'$, which we have accomplished in \s{sec:qtznrules} in both weak- and strong-field regimes.
@@
 We denote  $\dot{O}:=\partial O/\partial(l^2)$ evaluated at $(\bar{E},\bar{B})$, and estimate
-\e{\f{l^2_+-l^2_-}{T_{\sma{1/B}}} \approx  \f{r }{2\pi}T_{\sma{1/B}} \left( \dot{\lambda}_- -\dot{\lambda}_+\right)=O\left(\f{\delta S}{S}\bigg|_{\bar{E}}\right). \la{estimateB}}
-The order-of-magnitude estimate is obtained in the limit $\var_c\ll \Delta$, where $\lambda_{\pm}\approx \pm l^2\delta S/2$ [cf.\ \q{phaseindependentorbit}].
-In the opposite limit $\Delta\gg \var_c$, $\lambda_{\pm}$ is independent of $B$ within the accuracy of our semiclassical theory.
-
-\section{Codimension of Landau level quasidegeneracy}\la{app:codimension}
+\e{\f{l^2_+-l^2_-}{T_{l^2}} \approx  \f{r }{2\pi}T_{l^2} \left( \dot{\lambda}_- -\dot{\lambda}_+\right)=\order\left(\f{\delta S}{S}\bigg|_{\bar{E}}\right). \label{estimateB}}
+The order-of-magnitude estimate is obtained in the limit $l^2\delta S \gg 1$, where $\lambda_{\pm}\approx \pm l^2\delta S/2$ [cf.\ \q{phaseindependentorbit}].
+In the opposite limit $l^2\delta S \ll 1$, $\lambda_{\pm}$ is independent of $B$ within the accuracy of our semiclassical theory.
+
+\section{Codimension of Landau level quasidegeneracy}\label{app:codimension}
 
 \begin{table*}[t]
-\begin{tabular*}{2\columnwidth}{l@{\extracolsep{\fill}}ccccccc}
+\begin{tabular*}{2\columnwidth}{c@{\extracolsep{\fill}}ccccccc}
 \hlineB{2}
-             & $u$ & $s$ & symmetry constraint & $\det{\A}$ & $\breve{g}$ & codimension \\
+             class number & $u$ & $s$ & symmetry constraint & $\det{\A}$ & $\breve{g}$ & codimension \\
 \hline
-(I) $\forall \bk \in \frako$, $g\circ \bk=\bk$ & 0 & 0 & $\A=\breve{g}\A\breve{g}^{-1}$ & - & $\breve{g}\propto I$ & 3  \\
+1 & 0 & 0 & $\A=\breve{g}\A\breve{g}^{-1}$ & - & $\breve{g}\propto I$ & 3  \\
 &  &  &  & - & $\breve{g} \not\propto I$ & 1  \\
-& 0 & 1 & $\A=\breve{g}\A^*\breve{g}^{-1}$ & 1 & $(\breve{g}K)^2=I$ & 1 \\
+2& 0 & 1 & $\A=\breve{g}\A^*\breve{g}^{-1}$ & 1 & $(\breve{g}K)^2=I$ & 1 \\
 &  &  &  & 1 & $(\breve{g}K)^2=-I$ & 3 \\
@@
 &  &  &  & -1 & $(\breve{g}K)^2=-I$ & $\times$ \\
-(II-A) $|g\circ \frako| = |\frako|$ & 0 & 0 & $\A=\breve{g}(g^{L-1}\circ\bk_0)\prod_{i=0}^{L-1} \A_{1/L}$ & - & - & 1 \\
-$\exists \bk \in \frako, g\circ \bk\ne\bk$ & 0 & 1 & $\A=\breve{g}(g^{L-1}\circ\bk_0)\prod_{i=0}^{L-1} K^i\A_{1/L}K^i$ & - & $L=N$ & 1 \\
+3 & 0 & 0 & $\A=\breve{g}(g^{L-1}\circ\bk_0) \A_{1/L}^{L}$ & - & - & 1 \\
+4 & 0 & 1 & $\A=\breve{g}(g^{L-1}\circ\bk_0) (K^i\A_{1/L}K^i)^L$ & - & $L=N$ & 1 \\
 & & & & 1 & $L\ne N$ & 1 \\
@@
 & & & & -1 & $L\ne N$, $(\breve{g}K)^2=-I$ & $\times$ \\
-& 1 & 0 & $\A=\breve{g}\A^\dagger\breve{g}^{-1}$ & 1 &$\breve{g} \propto \sigma_z$& 2\\
+5 & 1 & 0 & $\A=\breve{g}\A^\dagger\breve{g}^{-1}$ & 1 &$\breve{g} \propto \sigma_z$& 2\\
 & & & & 1 &$\breve{g} \not\propto \sigma_z$ & 0\\
@@
 & & & & -1 &$\breve{g} \not\propto I$& 0\\
-& 1 & 1 & $\A=\breve{g}\A^T\breve{g}^{-1}$ & - & $(\breve{g}K)^2=I$ & 2 \\
+6 & 1 & 1 & $\A=\breve{g}\A^T\breve{g}^{-1}$ & - & $(\breve{g}K)^2=I$ & 2 \\
 & & & & - & $(\breve{g}K)^2\ne I$ & 0 \\
-(II-B) $|g\circ \frako| \ne |\frako|$ & 0 & 0 & $\A_2=\breve{g}\A_1\breve{g}^{-1}$ & - & - & 3 \\
-& 0 & 1 & $\A_2=\breve{g}\A_1^*\breve{g}^{-1}$ & - & - & 3\\
-& 1 & 0 & $\A_2=\breve{g}\A_1^\dagger\breve{g}^{-1}$ & - & - & 3\\
-& 1 & 1 & $\A_2=\breve{g}\A_1^T\breve{g}^{-1}$ & - & - & 3 & \\
+7 & 0 & 0 & $\A_2=\breve{g}\A_1\breve{g}^{-1}$ & - & - & 3 \\
+8 & 0 & 1 & $\A_2=\breve{g}\A_1^*\breve{g}^{-1}$ & - & - & 3\\
+9 & 1 & 0 & $\A_2=\breve{g}\A_1^\dagger\breve{g}^{-1}$ & - & - & 3\\
+10 & 1 & 1 & $\A_2=\breve{g}\A_1^T\breve{g}^{-1}$ & - & - & 3 & \\
 \hlineB{2}
 \end{tabular*}
-\caption{ \textbf{[for II-A-1, you might replace product with a power, and breveg by a phase factor; it looks a little disconcerting that L-1 is specially chosen in the argument.
-]} Codimensions of degeneracy manifold of $\A$ or $\A'$ under constraints of different type of symmetries.
+\caption{Codimensions of degeneracy manifold of $\A$ under constraints of different type of symmetries.
 Most of the symmetry constraints on $\A$ are reproduced from Ref.
-[100p] except for the first two classes in type II-A, where a special gauge is chosen.
+[100p] except for class 3 and 4, where a special gauge is chosen.
 $\infty$ in the codimension column denotes that eigenvalues of $\A$ cannot be degenerate; $\times$ denotes an entry where we cannot self-consistently impose the symmetry constraint and the conditions on det$\A$ and $\breve{g}$ for a two-by-two unitary $\A$.
-In the second to last column, $\breve{g}$ is either chosen to be diagonal or off-diagonal \label{table:fullcodimension}}
+In the second to last column, $\breve{g}$ is either chosen to be diagonal or off-diagonal.\label{table:fullcodimension}}
 \end{table*}
@@
 
-For four of  the ten classes (class II-B), the symmetry relates the propagators of distinct and disconnected orbits, but each propagator (corresponding to one orbit) is itself unconstrained.
-Therefore, the codimensions are still 3 \textbf{[must be careful in presentation, how do we distinguish orbit degeneracies from the spin degeneracies that is the focus of this work]}.
-For the other six classes, a case by case study is needed.
-
-The symmetry constraints in Table \ref{table:fullcodimension} can be divided into two types: (i) the first two rows of class II-A and (ii) other rows.
+For four of  the ten classes (7, 8, 9, 10), the symmetry relates the propagators of distinct and disconnected orbits, but each propagator (corresponding to one orbit) is itself unconstrained.
+Therefore, the codimensions are still 3.
+For the other six classes, self constraints of $\A$ are imposed.
+In particular, in class 2, 4, 5, $\det(\A)$ is quantized at $\pm 1$ [topofermiology, 100p].
+
+The symmetry constraints in Table \ref{table:fullcodimension} can be divided into two types: (i) class-3, 4 and (ii) other classes.
 For symmetry constraints of type (i), the full propagator is decomposed into products of $L$ (whose meaning will be explained below) segments of the propagator.
@@
 
-\paragraph*{class I-1} According to the general rules of sewing matrix, the sewing matrix $\breve{g}$ can be made diagonal by a gauge transformation
+\paragraph*{class-1} According to the general rules of sewing matrix, the sewing matrix $\breve{g}$ can be made diagonal by a gauge transformation
 \e{
@@
 
-\paragraph*{class I-2}
+\paragraph*{class-2}
 By a gauge transformation, the sewing matrix $\breve{g}$ can be made off-diagonal
@@
 }
-In this gauge, the symmetry constraints are expressed as (notice that $\det(\A)=\pm 1$ in this class \textbf{[this should not be inserted as a casual remark, please formalize]})
+In this gauge, the symmetry constraints are expressed as
 \e{
@@
 }
-This immediately gives corresponding rows in table. \ref{table:fullcodimension}.
-
-\paragraph*{class II-A-3 and class II-A-4} Calculation of codimensions for the two classes follow the same pattern as class I and is therefore omitted here.
-
-\paragraph*{class II-A-1} In this class \textbf{[not just this class, also II-A-2]}, the full propagator can be constructed from $1/L$ of it, where $L$ is the smallest positive integer fulfilling $g^L\circ \bk_0=\bk_0$.
+This immediately yeilds corresponding rows in table. \ref{table:fullcodimension}.
+
+\paragraph*{class-3} In this class (and also class-4), the full propagator can be constructed from $1/L$ of it, where $L$ is the smallest positive integer fulfilling $g^L\circ \bk_0=\bk_0$.
 Here, $\bk_0$ is the base point of $\A$.
 In this class, $L=N$.
-A good example in this class is $\mathfrak{c}_{Nz}$, $N$-fold rotation in z direction.\textbf{ [give the more general expression first before you perform your gauge transform]} Generally, by gauge transformation at $g^n\circ \bk_0$, $\breve{g}(g^n\circ \bk_0)$ can be transformed to identity for $0 \le n < N-1$ and the full propagator is
-\e{
-\A=\breve{g}(g^{N-1}\circ\bk_0)\prod_{i=0}^{N-1} \A_{1/N}
+A good example in this class is $\mathfrak{c}_{Nz}$, $N$-fold rotation in $z$ direction.
+Generally, by gauge transformation at $g^n\circ \bk_0$, $\breve{g}(g^n\circ \bk_0)$ can be transformed to identity for $0 \le n < N-1$ and the full propagator is
+\e{
+\A=\breve{g}(g^{N-1}\circ\bk_0)\A_{1/N}^N
 }
@@
 For the purpose of determining degeneracies, we may focus on
-$\prod_{i=0}^{N-1} \A_{1/N}$. Using the parametrization in Eq. (\ref{eq:paramA1/N}), we diagonalize $A_{1/N}$ as 
+$\A_{1/N}^N$. Using the parametrization in Eq. (\ref{eq:paramA1/N}), we diagonalize $A_{1/N}$ as 
 \e{
@@
 Tuning $\text{Re}(\alpha)=\cos(n\pi/N)$ requires only one parameter, except for $n=0$ and $n=N$, where three parameters are required.
-\textbf{A few more details in above proof would be helpful}
 
@@
 $\varphi$ sweeps through $n\pi/N$ where degeneracies of $\A$ are expected.
-$e^{i\varphi}$ hits $\pm 1$ once in every $N$ degeneracies and therefore the other $n-1$ degenerates are stable, i.e., have codimension 1.
-
-\paragraph*{class II-A-2} In class II-A-1, $L=N$ is guaranteed.
-However, in class II-A-2, this is generally not true.
-For symmetry operations still respecting $L=N$, the codimension calculation is similar to what is done in class II-A-1.
+$e^{i\varphi}$ hits $\pm 1$ once in every $N$ degeneracies and therefore the other $N-1$ degenerates are stable, i.e., have codimension 1.
+
+\paragraph*{class-5} In class-4, $L=N$ is guaranteed.
+However, in class-5, this is generally not true.
+For symmetry operations still respecting $L=N$, the codimension calculation is similar to what is done in class-4.
 The only example of $L\ne N$ is $T\mathfrak{c}_{6z,n\boldsymbol{c}/6}$ ($n\in\{0,1,2,3,4,5\}$), where $L=3$ and $N=6$.
@@
 and the codimension is 1.
-If $h=i\sigma_y$, from the fourth entry of class I-2, we deduce $\det \A_{1/L}=1$.
+If $h=i\sigma_y$, from the fourth entry of class 2, we deduce $\det \A_{1/L}=1$.
 Choosing the parametrization in Eq.
@@
 
-In the main text, we focus on degenerate bands whose degeneracy is protected by continuous spin rotational symmetry (i.e., no SOC) or antiunitary symmetry $g$ with $g\circ \bk=\bk$ and $g^2=-1$.
-For the former case, we have argued in the main text that $\det{\A}=1$ if $\det{\A}$ is quantized; for the latter case, we have presented in table \ref{table:fullcodimension} $\det{\A}=1$ (Notice $g$ belongs to class I-2).
-Therefore, we safely ignore $\det{\A}=-1$ entries in table \ref{table:fullcodimension} and obtain table \ref{table:codimension} in the main text.
-\textbf{[more general argument?:  if we’re concerned with spinful orbits, and in symmetry classes where u+s=1, delta var is traceless, hence det A=+1.]
-}
+\paragraph*{class-5 and 6} Calculation of codimensions for the two classes follow the same pattern as class-1 and 2 and is therefore omitted here.
+
+In the main text, we assume the SOC can be turned off continuously without increasing or decreasing degree of degeneracy.
+With this assumption, $\det(A)=1$ for class-2, 4, 5, reducing Tab.
+\ref{table:fullcodimension} to Tab.
+\ref{table:codimension}.
+
 \section{Two-by-two sewing matrix of antiunitary symmetry operator can be made off-diagonal\label{app:makinggoffdiagonal}}
@@
 \end{widetext}
-Parametrizing $a=a_{1}+ia_{2}$, $b=b_{1}+ib_{2}$, $\alpha=\alpha_{1}+i\alpha_{2}$
-and $\beta=\beta_{1}+i\beta_{2}$, we first remove the imaginary part
-of $a^{*}b^{*}\alpha+bb^{*}\beta^{*}+aa^{*}\beta-ab\alpha^{*}$. If
-we take both $a$ and $b$ to be real, we want
-\begin{align*}
-0 & =2ab\alpha_{2}-b^{2}\beta_{2}+a^{2}\beta_{2}\\
-2ab\alpha_{2} & =(b^{2}-a^{2})\beta_{2}\\
-2b\sqrt{1-b^{2}}\alpha_{2} & =(2b^{2}-1)\beta_{2}.
-\end{align*}
+Decomposing real and imaginary parts of the parameters: $a=a_{1}+ia_{2}$, $b=b_{1}+ib_{2}$, $\alpha=\alpha_{1}+i\alpha_{2}$
+and $\beta=\beta_{1}+i\beta_{2}$, the imaginary part
+of $a^{*}b^{*}\alpha+bb^{*}\beta^{*}+aa^{*}\beta-ab\alpha^{*}$ can be removed by $a_2=b_2=0$ and 
+\begin{equation}
+2b_1\sqrt{1-b_1^{2}}\alpha_{2} & =(2b_1^{2}-1)\beta_{2}.
+\end{equation}
 This is always possible since $2b\sqrt{1-b^{2}}/(2b^{2}-1)$ can take
@@
 $\beta$ is real since a preliminary transformation can remove its
-imaginary part. Then we want
-\begin{align*}
-0 & =a^{*2}\alpha+a^{*}b\beta^{*}-a^{*}b\beta+b^{2}\alpha^{*}\\
-(a_{1}-ia_{2})^{2}(\alpha_{1}+i\alpha_{2}) & =-(b_{1}+ib_{2})^{2}(\alpha_{1}-i\alpha_{2})\\
-(a_{1}^{2}-a_{2}^{2}-2ia_{1}a_{2})(\alpha_{1}+i\alpha_{2}) & =-(b_{1}^{2}-b_{2}^{2}+2ib_{1}b_{2})(\alpha_{1}-i\alpha_{2}).
-\end{align*}
-Real and imaginary part of the above equation are
-\[
+imaginary part.
+
+The equation of $a^{*2}\alpha+a^{*}b\beta^{*}-a^{*}b\beta+b^{2}\alpha^{*}=0$ then becomes
+\begin{equation}
 (a_{1}^{2}-a_{2}^{2})\alpha_{1}+2a_{1}a_{2}\alpha_{2}=-(b_{1}^{2}-b_{2}^{2})\alpha_{1}-2b_{1}b_{2}\alpha_{2}
-\]
+\end{equation}
 and 
-\[
-(a_{1}^{2}-a_{2}^{2})\alpha_{2}-2a_{1}a_{2}\alpha_{1}=(b_{1}^{2}-b_{2}^{2})\alpha_{2}-2b_{1}b_{2}\alpha_{1}.
-\]
-Therefore
-\[
-\frac{\alpha_{2}}{\alpha_{1}}=-\frac{(a_{1}^{2}-a_{2}^{2})+(b_{1}^{2}-b_{2}^{2})}{2a_{1}a_{2}+2b_{1}b_{2}}=\frac{2a_{1}a_{2}-2b_{1}b_{2}}{(a_{1}^{2}-a_{2}^{2})-(b_{1}^{2}-b_{2}^{2})},
-\]
-equivalent to
-\[
+\begin{equation}
+    (a_{1}^{2}-a_{2}^{2})\alpha_{2}-2a_{1}a_{2}\alpha_{1}=(b_{1}^{2}-b_{2}^{2})\alpha_{2}-2b_{1}b_{2}\alpha_{1},
+\end{equation}
+which is equivalent to
+
+\e{
 |a|=|b|=\frac{\sqrt{2}}{2}
-\]
+}
 and 
-\[
+\e{
 \frac{\alpha_{2}}{\alpha_{1}}=-\frac{(a_{1}^{2}-a_{2}^{2})+(b_{1}^{2}-b_{2}^{2})}{2a_{1}a_{2}+2b_{1}b_{2}}.
-\]
+}
 This can always be satisfied. For example, we can always take $b=1/2+i/2$
 and the above equation becomes
-\[
+\e{
 \frac{\alpha_{2}}{\alpha_{1}}=\frac{(2a_{2}^{2}-1/2)}{2a_{2}\sqrt{1/2-a_{2}^{2}}+1/2},
-\]
-which is always possible since $\frac{(2a_{2}^{2}-1/2)}{2a_{2}\sqrt{1/2-a_{2}^{2}}+1/2}$
-can take any value.
-
-\section{Method of numerical diagonalization}\la{sec:numerical}
-
-The techniques for solving $\mathcal{H}_R(\bK)$ in \textbf{[eq]} is standard, but we describe it here since it is also used in numerical diagonalization of other Hamiltonians below with no closed analytic solutions.
-This technique relies on the fact that the commutation relation $[K_x,K_y]=il^{-2}$ bears similarity to that of position operator and momentum operator of simple harmonic oscillators.
+}
+which is always possible since the right hand side  can take any value.
+
+\section{Method of numerical diagonalization}\label{sec:numerical}
+
+Numerical diagonalization relies on the fact that the commutation relation $[K_x,K_y]=il^{-2}$ bears similarity to that of position operator and momentum operator of simple harmonic oscillators.
 Therefore, $K_x$ and $K_y$ can be organized into creation and annihilation operators
@@
 \end{align}
-Under this transformation, $\mathcal{H}_R(\bK)$ is transformed to
+Under this transformation, $H_R(\bK)$ is transformed to
 \begin{align}
 \begin{split}
-\mathcal{H}_{R}(\boldsymbol{K})=&\frac{1}{ml^2}(a^{\dagger}a+\frac{1}{2})
+H_{R}(\boldsymbol{K})=&\frac{\hbar^2}{ml^2}(a^{\dagger}a+\frac{1}{2})
 \\&+\sqrt{2}\alpha l^{-1}\left(\begin{array}{cc}
@@
 \end{array}\right)
--\frac{g_s'\sigma^z}{4ml^2},
+-\frac{g_\text{eff}\hbar^2\sigma^z}{4ml^2},
 \end{split}\label{eq:Rashba-ho}
@@
 (\ref{eq:Rashba-ho}) have solutions in the form of $(c_1|n+1\rangle,c_2|n\rangle)$ where $c_1$ and $c_2$ are some constants and $|n\rangle$ labels the eigenstate of $a^\dagger a$.
-
-\textbf{[combine this with above]
-}Electron spectrum of this Hamiltonian in magnetic field is not exactly solvable to our knowledge.
-Yet multiband Peierls substitution is still applicable and the system can still be mapped into two coupled harmonic oscillators similar to Eq.
-(\ref{eq:Rashba-ho}).
-This Hamiltonian is infinite dimensional and can be diagonalized by cutting off at a high occupation number.
-
-\section{Dimension of degeneracy manifolds \textbf{[remove before post]}}\la{app:nullity}
-
-Any $SU(2)$ matrix can be expressed as ${\cal \bar{A}}= e^{i\br\cdot \bsigma}$ with $\br=(x,y,z)$ a real three vector and $\bsigma=(\sigma_x,\sigma_y,\sigma_z)$ the vector of Pauli matrices.
-The condition for degeneracy can be expressed as
-\e{ 0=D^{\pm}=\det[{\cal \bar{A}}\pm I] = 2(1\pm \cos r)\in \R, \as r:=|\br|. \la{semipos}}
-Parametrizing  ${\cal \bar{A}}(\bR)$ with $\bR$ a real $d$-vector, we define the partial derivatives
-\e{  D^{\pm}_j:= \p{D^{\pm}}{ R_j}\in \R, \as D^{\pm}_{ij}:= \p{^2D^{\pm}}{ R_i\partial R_j} \in \R.  }
-$D^{\pm}_{ij}$, also known as the Hessian matrix, is real and symmetric.
-
-Let us prove that $D^{\pm}_j$ vanishes (for all $j$) when evaluated on the degeneracy manifold.
-We express $D^{\pm}$ as the characteristic polynomial det$[{\cal \bar{A}}-\zeta I]$ evaluated at $\zeta=\mp 1$:
-\e{ D^{\pm}(\bR)=c_0(\bR)(\mp 1-\zeta_1(\bR))(\mp 1-\zeta_2(\bR)) }
-where $\zeta_j$ are the unimodular eigenvalues of ${\cal \bar{A}}$. In this form it is clear that
-the first derivatives of $D^{\pm}$ vanish when $\zeta_1=\zeta_2=\pm 1$.
-
-To alternatively derive the vanishing of $D^{\pm}_j$ where $D^{\pm}{=}0$, we may apply that  $D^{\pm}\in [0,4]$ [derived from \q{semipos}].
-As an implication, consider a small displacement $\delta \bR$ away from  a point $\bR_0$  on the degeneracy manifold $D^{+}=0$:
-\e{ D^+(\bR_0+\delta \bR)\eq  \f1{2} \sum_{i,j=1}^d\delta R_i D^{+}_{ij}(\bR_0) \delta R_j + O(\delta R_i^3) \lin 
-\eq \f1{2}\sum_{j=1}^d c^2_j h_j + O(\delta R_i^3).\la{taylor}} 
-Since $D^{\pm}$ is a semipositive definite function, it must be that $\sum_{ij}\delta R_i D^{+}_{ij}(\bR_0) \delta R_j\geq 0$ for any $\delta \bR$, i.e., the Hessian must be semipositive definite on the degeneracy manifold.
-In the last equality of \q{taylor}, we decomposed $\delta \bR=\sum_jc_j\bv_j$ into the real, orthonormal eigenvectors $\bv_j$ of $D^{+}_{ij}(\bR_0)$ with corresponding real eigenvalues $h_j$; note $h_j\geq 0$.
-We see that if $\bR_0+\delta \bR$ lies on the degeneracy manifold (i.e., $D^+(\bR_0+\delta \bR)=0$),  $\delta \bR$ must lie in the null space of $D^{+}_{ij}(\bR_0)$.
-This implies that the dimension of the degeneracy manifold is bounded by the dimension of this null space (i.e., the nullity).
-
-To illustrate these degeneracy manifolds for $\bR=\br=(r_1,r_2,r_3)$ a real three-vector, and $\hat{r}_i:=r_i/r$ 
-\e{ D^{\pm}_j = \mp 2\sin (r) \hat{r}_i, \as D^{\pm}_{ij}= \f{\sin r}{r}\big(\delta_{ij}-\hat{r}_i\hat{r}_j\big)+\hat{r}_i\hat{r}_j\cos r.}
-The degeneracy manifolds are given by $r=n\pi$ with $n\in \Z$.
-In particular, $D^{\pm}_{ij}(\bze)$ is the identity matrix, which is consistent with $n=0$ manifold being a point; $D^{\pm}_{ij}(\pi,0,0)$ is a diagonal matrix with only a single nonzero entry ($-1$), which is consistent with the $n=1$ manifold being a two-sphere.
-\section{Reducing nonlocal magnetic breakdown to local magnetic breakdown \textbf{[remove before post]}}
-We take Rashba-Zeeman model as an example, revealing that quantization rule for nonlocal magnetic breakdown, in the limit of $\Delta\gg\epsilon_c$, becomes quantization rule for local magnetic breakdown.
-
-In the limit of $\Delta\gg\epsilon_c$, the two orbits become nondegenerate everywhere except for the type II Dirac point. It is natural to decompose the propagator into two parts
-\begin{equation}
-\A = \A_2\A_1,
-\end{equation}
-where $\A_1:=\A[t_-\leftarrow t_+]$ encodes information of cyclotron motion from leaving the vicinity of the Dirac point (denoted as $t_+$) to entering the vicinity of the Dirac point again (denoted as $t_-$) and $\A_2:=\A[t_+\leftarrow t_-]$ encodes information of cyclotron passing the vicinity of the Dirac point.
-Notice that we have written down $\A$ (and $\A_1$, $\A_2$) in constant basis since $\calh$ diverges near the Dirac point if expressed in the energy band basis.
-$t_+-t_-\ll T_c$ due to the smallness of the Dirac point.
-A gauge transformation expresses $\A_1$ in the energy basis
-\begin{equation}
-V_+^\dagger\A V_+ = V_+^\dagger\A_2V_-V_-^\dagger\A_1V_+,
-\end{equation}
-where $V_\pm=V(\bk(t_\pm))$.
-We emphasize that while $V_-^\dagger\A_1V_+$ can be understand as $\A_1$ in energy basis, $V_+^\dagger\A_2V_-$ cannot due to the divergence of single band Berry connection at Dirac point.
-Since $\Delta\gg\epsilon_c$, diagonal terms of $\A_1$ is much larger than off-diagonal terms such that to the lowest order off diagonal terms can be neglected.
-Therefore,
-\begin{equation}
-\A_1\approx\matrixtwo{\delta \Omega_1}{0}{0}{\delta \Omega_2},
-\end{equation}
-where $\delta\Omega_{1(2)}$ is the semiclassical phase accumulated from $t_+$ to $t_-$ besides $l^2 S$ by the two bands.
-
-The other part $\mathcal{S}:=V_+^\dagger\A_2V_-$ is a standard Landau-Zener problem, as will be shown below. In the constant basis, 
-\begin{equation}
-\calh(t)=\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+Z_\parallel\sigma_{y}-Z_\perp\sigma_{z},
-\end{equation}
-where $k_x=-k_F \cos(\omega_c t)$ and $k_y=k_F \sin(\omega_c t)$. Since $t_+-t_-\ll T_c$, we can keep only the linear terms in $t$,
-\begin{equation}
-\calh(t)\approx-\alpha k_F \omega_c t\sigma_x+(Z_\parallel-\alpha k_F)\sigma_y-Z_\perp\sigma_z.
-\end{equation}
-It is now obvious that $\mathcal{S}$ is a Landau-Zener problem: $\alpha k_F \omega_c t\sigma_x$ is linear in time; $(Z_\parallel-\alpha k_F)\sigma_y-Z_\perp\sigma_z$ is time independent; columns of $V_-$ and $V_+$ are approximately eigenvectors of $\sigma_x$.
-Therefore, $\mathcal{S}$ takes the form of a magnetic junction scattering matrix with
-\e{\mu=\frac{ml^2(Z_\perp^2+(Z_\parallel-\alpha k_F)^2)}{2\alpha k_F}.}
-
-Generally, $\mu$ should diverge at type I-type II Dirac point transition point, which is not the case in the above equation. Therefore, $\mu$ in the above equation is only an approximate result.
-
-The quantization rule is now
-\e{
-\det\left[e^{il^2S}\mathcal{S}\matrixtwo{\delta \Omega_1}{0}{0}{\delta \Omega_2}-I\right]=0,
-}
-giving rise to cos-cos quantization condition.
-
-We now compare $\mu$ derived here and $\mu$ defined in [AALG]. In [AALG], $Z_\perp$ was ignored and
-\e{
-\mu = \f{(k_F^2/2m-Z_\parallel^2/2m\alpha^2)^2l^2}{2\alpha^2[\,(Z_\parallel/m\alpha^2)^2-1\,]^{3/2}}.
-}
-If $Z/m\alpha^2$ is large, i.e., deep in type II Dirac point regime, we can ignore the 1 in the denominator,
-\e{
-\mu &\approx \f{ml^2(\alpha^2 k_F^2-Z_\parallel^2)^2}{8Z_\parallel^3}\\
- &= \f{ml^2(\alpha k_F-Z_\parallel)^2(\alpha k_F+Z_\parallel)^2}{8Z_\parallel^3}.
-}
-For tunneling effect to be significant, $Z\approx \alpha k_F$, therefore,
-\e{
-\mu \approx \f{ml^2(\alpha k_F-Z_\parallel)^2}{2\alpha k_F},
-}
-consistent with $\mu$ derived with $\A$.
-
-\section{Fixing discontinuity in magnetic breakdown with Zeeman coupling \textbf{[remove before post]}}
-
-For the II-Dirac point in the main text, if Zeeman coupling is taken into account, the Dirac point is gapped:
-\e{
-H &= (\sigma_y-a)k_x-k_y\sigma_x-\lambda\sigma_z\\
- &:= H_0+H_Z.
-}
-where $\lambda$ is considered as a small parameter and $a>1$. Eigenvalue of $H$ is 
-\e{
-\epsilon_\pm&=-a k_x \pm\sqrt{k_x^2+k_y^2+\lambda^2}\\
-&:=-a k_x \pm\Delta
-} and eigenvectors are
-\begin{equation}
-\psi_\pm=\f{1}{\sqrt{2\Delta(\Delta\pm\lambda)}}\left(
-\begin{array}{c}
--\lambda\mp\Delta\\
--k_y+ik_x
-\end{array}
-\right).
-\end{equation}
-
-The Berry connection for lower band is 
-\e{
-A_x&=\f{k_y}{2\Delta(\Delta+\lambda)},\\
-A_y&=-\f{k_x}{2\Delta(\Delta+\lambda)}.
-}
-
-Constant energy contours are now described by a hyperbola
-
-\e{
-(k_x+\f{a\epsilon}{a^2-1})^2-\f{k_y^2}{a^2-1}=\f{1}{a^2-1}[\lambda^2+(\frac{a^2}{(a^2-1)^2}-1)\epsilon]
-}
-
-For a general hyperbola
-\e{
-\f{(kx+b)^2}{c^2}-\f{k_y^2}{d^2}=1,
-}
-the lower branch is 
-\e{
-k_x = -a\sqrt{1+\frac{k_y^2}{b^2}}-c
-}
-and Berry phase is
-\e{
-\phi&=\int A_xdk_x+A_ydk_y\\
-&=\int dk_y (\f{k_y}{2\Delta(\Delta+\lambda)}\f{-ak_y}{b\sqrt{b^2+k_y^2}}-\f{k_x}{2\Delta(\Delta+\lambda)}).
-}
-
+For Hamiltonian $H(\bK)$ that is not exactly solvable, it can be diagonalized by cutting off at a high occupation number of the coupled harmonic oscillators.
 \end{document}

### 2018-10-01 paper.tex
Updates from ShareLaTeX

@@
 The quantization rule for Landau levels reflects the single-valuedness of the semiclassical (WKB) wavefunction over $\frako_0$,[Berry, Mount] i.e.,  the phase accumulated by an electron (over one cyclotron period $T_c$) is an integer multiple of $2\pi$: $(l^2S(E){+}\gamma)/2\pi{\in}\Z$.
-The leading-order phase   involves the classical action $S{:}{=}-\int_{0}^{T_c} k_x \dot{k}_y dt$  corresponding to $(K_x,K_y)$;[mount] $S$ has a dual interpretation as the signed area (in $\bk$-space) enclosed by $\frako_0$, as illustrated in Fig.
+The leading-order phase   is the classical action $l^2S{:}{=}{-}l^2\int_{0}^{T_c} k_x \dot{k}_y dt$  corresponding to $(K_x,K_y)$;[mount] $S$ has a dual interpretation as the signed area (in $\bk$-space) enclosed by $\frako_0$, as illustrated in Fig.
 \ref{fig:orbits}(b).
@@
 $\delta \var$ is the projection of $\delta \hat{H}$ to the degenerate band subspace of $\hat{H}_0$.
-In the basis of energy-split bands (which we label by ${+}$ and $-$ for bands corresponding to the outer and inner orbit respectively), $\delta \var$ is a diagonal matrix whose diagonal entries ($\delta \var_+,\delta \var_-$, corresponding to outer and inner orbit respectively; $\delta \var_+<\delta \var_-$) are related to the hybridization parameter:\footnote{The neglected term on the right-hand side of  \q{spinsplitwkb} is smaller (than the kept term) by a factor $\delta v_{\pm}/v$, which is the relative change in band speed $v=|\boldsymbol{v}|=\hbar^{-1}|\partial \var/\partial \bk|$ induced by the spin-orbit coupling.
+$\delta \var$ is assumed to be traceless; this property is guaranteed for $\delta \hat{H}$ a spin-orbit coupling that breaks the spin SU(2) symmetry of $\hat{H}_0$;\footnote{The Pauli spin-orbit coupling term ${\propto} \bs{\cdot} (\bE {\times} \bp)$ is traceless in any spin-symmetric (pseudo-)spinor basis.
+Viewing the spin-orbit coupling as a small parameter in degenerate perturbation theory, the lowest-order splitting of any spin-degenerate energy level is always symmetric about the zeroth-order energy.
+This follows because the zeroth-order, spin-symmetric wavefunctions (associated to a spin-degenerate level) are tensor products of spin and spatial wavefunctions: $\ket{\Psi_{\pm}}{:}{=}\ket{{\pm}\hat{n}}{\otimes} \ket{\psi}$ with $\hat{n}$ a unit vector and  $\bs{\cdot} \hat{n} \ket{{\pm}\hat{n}}{=}{\pm}\ket{\pm \hat{n}}$.
+Hence, $\braopket{\Psi_{\pm}}{\bs{\cdot} (\bE {\times} \bp)}{\Psi_{\pm}}{=}{\pm}\hat{n}\cdot\braopket{\psi}{\bE {\times} \bp}{\psi}$.} more generally, one may always absorb the traceful part (of  the projection of $\delta \hat{H}$) into the definition of $\var(\bk)$.
+In the basis of energy-split bands (which we label by ${+}$ and $-$ for bands corresponding to the outer and inner orbit respectively), $\delta \var$ is a diagonal matrix whose diagonal entries ($\delta \var_+,~\delta \var_-{=}{-}\delta \var_+$)  are related to the hybridization parameter:\footnote{The neglected term on the right-hand side of \q{spinsplitwkb} is smaller (than the kept term) by a factor $\delta v_{\pm}/v$, which is the relative change in band speed $v=|\boldsymbol{v}|=\hbar^{-1}|\partial \var/\partial \bk|$ induced by the spin-orbit coupling.
 This factor is assumed to be small.
@@
 \e{-\int_0^{T_c} (\delta \var_+{-}\delta \var_-) \frac{dt}{\hbar} \approx l^2\delta S. \label{spinsplitwkb}}
+
+%is not traceless, the traceful part can always be absorbed into the redefinition of $S$ within the accuracy of first order perturbation theory.
+
 %In the  Rashba model,   $\delta \var_{\pm}(E){=}{\pm} (\alpha/\hbar)\sqrt{2mE}$ is independent of $\bk$ due to a continuous rotational symmetry of $H_R$. \\
@@
 \e{\lambda_{\sma{\pm}} = -\int_0^{T_c}\calh_{\sma{\pm\pm}}\f{dt}{\hbar}=\pm \f{1}{2}l^2\delta S - B\int_0^{T_c}\calm_{\sma{\pm\pm}}\f{dt}{\hbar}.  \label{phaseindependentorbit}} 
-In the second equality, we have applied \q{spinsplitwkb} and assumed that 
- $\delta \var$ is traceless (this assumption is  valid for splittings of a spin degeneracy\footnote{The Pauli spin-orbit coupling term ${\propto} \bs{\cdot} (\bE {\times} \bp)$ (that is derived from the non-relativistic limit of the Dirac equation) is traceless in any spin-symmetric (pseudo-)spinor basis.
-Viewing the spin-orbit coupling as a small parameter in degenerate perturbation theory, the lowest-order splitting of any spin-degenerate energy level is always symmetric about the zeroth-order energy.
-This follows because the zeroth-order, spin-symmetric wavefunctions (associated to a spin-degenerate level) are tensor products of spin and spatial wavefunctions: $\ket{\Psi_{\pm}}{:}{=}\ket{{\pm}\hat{n}}{\otimes} \ket{\psi}$ with $\hat{n}$ a unit vector and  $\bs{\cdot} \hat{n} \ket{{\pm}\hat{n}}{=}{\pm}\ket{\pm \hat{n}}$.
-Hence, $\braopket{\Psi_{\pm}}{\bs{\cdot} (\bE {\times} \bp)}{\Psi_{\pm}}{=}{\pm}\hat{n}\cdot\braopket{\psi}{\bE {\times} \bp}{\psi}$.
-\textbf{Please generalize above proof to the case where H0 already includes centrosymmetric SOC.
-}}).
 \q{eq:rule}, combined with \q{phaseindependentorbit}, may be identified as the Onsager-Lifshitz rule[onsager,lifshitz] for  two independent, nondegenerate orbits of areas $S{\pm}\delta S$, and with subleading phase corrections that were first identified by Roth[rothII].\footnote{We remark that \q{phaseindependentorbit} neglects the contribution by band $-$ to the orbital moment of band $+$: $\delta M_z=il^{-2}\epsilon_{\ab}(\delta \var_+-\delta \var_-)\mathfrak{X}^{\alpha}_{+-}\mathfrak{X}^{\beta}_{-+}$.
@@
 \begin{equation}
-\lambda_{\pm}=\pm\f1{2}\sqrt{({l^2\delta S})^2+\pi^2(g_{\sma{\text{eff}}}-2)^2}+\pi. \label{eq:Rashba-lambda}
-\end{equation}
-This is a function of the differential action $\delta S$ [cf.\ \q{deltaSvsS}] and  the effective  $g$-factor ($g_{\sma{\text{eff}}}{:}{=}g_sm/m_0$), which is the free-electron $g$-factor multiplied with the ratio of  effective ($m$) and free-electron ($m_0$) masses.
+\lambda_{\pm}=\pm\f1{2}\sqrt{({l^2\delta S})^2+\pi^2(g_sm/m_0-2)^2}+\pi. \label{eq:Rashba-lambda}
+\end{equation}
+This is a function of the differential area $\delta S$ [cf.\ \q{deltaSvsS}] and the effective mass $m$.
 The standalone $\pi$ term is the single-band Berry phase associated to the winding of $\theta_{\bk}$ by ${\pm}2\pi$.
@@
 
-In the weak-hybridization regime: $l^2\delta S  \gg \pi|g_{\text{eff}}{-}2|$, we may expand \q{eq:Rashba-lambda} as a Laurent series in $B$:
-\e{\lambda_{\pm}= \pm \f{l^2\delta S}{2} +\pi \pm \f{\pi^2}{4}\f{(g_{\text{eff}}-2)^2}{l^2\delta S} + O(B^2). \label{lambdasmallB}}
+In the weak-hybridization regime: $l^2\delta S  \gg \pi|g_s m/m_0{-}2|$, we may expand \q{eq:Rashba-lambda} as a Laurent series in $B$:
+\e{\lambda_{\pm}= \pm \f{l^2\delta S}{2} +\pi \pm \f{\pi^2}{4}\f{(g_sm/m_0-2)^2}{l^2\delta S} + O(B^2). \label{lambdasmallB}}
 \q{eq:rule}, combined with the first two terms on the right-hand-side of \q{lambdasmallB}, may alternatively be derived from 
@@
 
-In the strong-hybridization regime: $l^2\delta S {\ll}\pi(g_{\text{eff}}{-}2)$, $\lambda_{\pm}{\approx}{\pm}\pi g_{\text{eff}} /2$ mod $2\pi$, which corresponds to the Zeeman splitting of Landau levels by $g_{s}\mu_BB$, in the \textit{absence} of the spin-orbit interaction.
+In the strong hybridization regime: $l^2\delta S {\ll}\pi(g_sm/m_0{-}2)$, $\lambda_{\pm}{\approx}{\pm}\pi g_sm/2m_0$ mod $2\pi$, which corresponds to the Zeeman splitting of Landau levels by $g_{s}\mu_BB$, in the \textit{absence} of the spin-orbit interaction.
 
@@
 &n_{\pm}=\frac{l^2S}{2\pi}+\frac{l^2\delta S}{16\pi}\f{\delta S}{S}\lin 
-&\pm\f1{2}\sqrt{\bigg(\frac{l^2\delta S}{8\pi}\f{\delta S}{S}\bigg)^2+(l^2\delta S)^2+\pi^2(g_{\sma{\text{eff}}}-2)^2},\label{eq:Rashba-exact}}
+&\pm\f1{2}\sqrt{\bigg(\frac{l^2\delta S}{8\pi}\f{\delta S}{S}\bigg)^2+(l^2\delta S)^2+\pi^2(\f{g_sm}{m_0}-2)^2},\label{eq:Rashba-exact}}
 with the functional forms of $\delta S(E)$ and $S(E)$ provided in \q{deltaSvsS};  $n_{+}{\ge} 1$ and $n_-{\ge} 0$ here are integer-valued labels for two distinct sets of levels.
@@
 
-We begin again with the Rashba model of a rotationally-symmetric Dirac cone. To convert this Dirac point to its asymmetric variant, 
+%\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+\zpar\sigma_{y},
+
+We begin again with the Rashba model [cf.\ \q{eq:Rashba-Hamiltonian}] of a rotationally-symmetric Dirac cone. To convert this Dirac point to its asymmetric variant, 
 let us introduce a Zeeman coupling to an in-plane magnetic field $B_\parallel$ (parallel to the $+y$ direction):
 \e{ 
-H_{RZ}=\f{{\hbar^2}k^{2}}{2m}+\delta \var; \;\;\;\delta \var=\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+\zpar\sigma_{y}, \label{eq:RZ-Hamiltonian}}
-with $\zpar{:}{=}{g_s}\mu_B B_{\parallel}/2$.
+H_{RZ}=\f{{\hbar^2}k^{2}}{2m}+\delta \var; \;\;\;\delta \var=d_x\sigma_x+d_y\sigma_y,\lin
+(d_x,d_y):=(-\alpha k_y,\alpha k_x+\zpar),\;\;\;\zpar:= g_s \mu_B B_{\parallel}/2.
+\label{eq:RZ-Hamiltonian}}
 While this field breaks both time-reversal ($T$) and two-fold rotational ($C_2$) symmetries, the composition $C_2T$ is preserved as $\sigma_x H^*_{RZ}(\bk)\sigma_x{=}H_{RZ}(\bk),$ which constrains spin to lie in-plane at each $\bk$.
@@
 \caption{(a) Trefoille-shaped cyclotron orbit for the Rashba-Zeeman model at the energy of the Dirac point.
-The orbit is drawn over the  spin-splitting field ($d_x,d_y$) of the Hamiltonian $H_{RZ}{=}d_0(\bk)I{+}d_x(\bk)\sigma_x{+}d_y(\bk)\sigma_y$, with $d_j$ obtainable from \q{eq:RZ-Hamiltonian}.
-The wavefunction along the inner (resp.\ outer) component of the trefoille orbit has its pseudospin aligned parallel (resp.\ anti-parallel) to the spin-orbit field.
-(b) Upper panel: a sketch of Landau level dispersion near II-Dirac point of Rashba model with in plane Zeeman field in the weak hybridization limit.
-The dashed line representing first order solution [cf.
-Eq.
-(\ref{RZfirstorderE})] oscillates around the solid line [zeroth order solution, cf.
-Eq.
-({trefoillerule})].
-Due to the smallness of $\delta S$, the oscillation should not be observable in the scale of several Landau levels.
-Therefore, We exaggerate the oscillation frequency in the sketch.
+The orbit is drawn over the  spin-splitting field ($d_x,d_y$) of the degeneracy-lifting Hamiltonian $\delta\var$ [cf.\ \q{eq:RZ-Hamiltonian}].
+The wavefunction along the inner (resp.\ outer) component of the trefoille orbit has its pseudospin aligned parallel (resp.\ anti-parallel) to the spin-splitting field.
+(b) Upper panel: a schematic illustration of Landau levels near the II-Dirac point of the Rashba model (with in-plane Zeeman field, and in the weak- hybridization limit).
+The solid line represents the Onsager-Lifshitz quantization of the trefoille orbit [cf.\ Eq.\ ({trefoillerule})], and the dashed line incorporates the first-order correction [cf.\ Eq.\ (\ref{RZfirstorderE})] due to tunneling.
 Lower panel: oscillation of $\delta E_n$ [cf.
@@
 (\ref{RZfirstorderE}) (black dashed line) and numerical diagonalization (red solid line).
-$\delta E$ is extracted at 0.45eV and the II-Dirac point is located at 0.5eV.
-Parameters for lower panel of (b): $m$: 0.076$m_0$, $\alpha$: 1.5($10^{5}$cm/s$\cdot\hbar$), $Z_\parallel$: 1meV.
-Out of plane Zeeman coupling is ignored here.
+$\delta E$ is extracted at the Landau level closest to 0.45eV and the II-Dirac point is located at 0.5eV.
+Parameters for lower panel of (b): $m{=}0.076m_0$, $\alpha{=} 1.5(10^{5}$cm/s$\cdot\hbar$), $Z_\parallel {=}$1meV.
+Out-of-plane Zeeman coupling is negligibly weak for the choice of $m$.
 (c) A sketch of cyclotron orbits of Rashba Hamiltonian with in-plane magnetic field.
-Inset: illustration of $S_{\sma{\square}}$ by the purple rectangle.
+Inset: an enlarged view of near II-Dirac point.
 (d) For various configurations ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in left panel $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that is closest to $\epsilon_0$ in Eq.
@@
 Corresponding $l^2 \delta S^2/S$ are plotted in right panel.
-We only plotted in region where $0.4<\epsilon_0<1.0$(eV).\cite{RZfignote}, Units: $\alpha$($1.5\times 10^{5}$cm/s$\cdot\hbar$).
+We only plotted in region where $0.4{<}\epsilon_0{<}1.0$(eV).\cite{RZfignote}, Units: $\alpha$($1.5\times 10^{5}$cm/s$\cdot\hbar$).
 Parameters for (d): $m=0.076m_0$, $l=100$\AA.
@@
 with $2\alpha k_E$ the spin-orbit splitting at energy $E$ [cf.\ \fig{fig:orbits}(a)].
-$\bar{\mu}$ has an alternative interpretation as the area of rectangle inscribed between the two hyperbolic arms $S_{\sma{\square}}$, as illustrated in the inset of Fig.
-\ref{fig:RZ}(c).
 In the absence of the out-of-plane Zeeman coupling ($Z_\perp{=}0$), $\bar{\mu}$ would vanish at the energy of the II-Dirac point -- leading to unit-probability Klein tunneling, as was first proposed by [Obrien] in a different model of the II-Dirac point.
@@
 The time-ordered, coherent process of Landau-Zener tunneling/transmission and adiabatic dynamics is described by the propagator:
-\e{{\A}= \matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}} \diagmatrix{e^{i\tilde{\lambda}_+}}{e^{i\tilde{\lambda}_-}}. \label{propinplanezeeman}}
+\e{{\A}= \matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}} \diagmatrix{e^{i\tilde{\lambda}_-}}{e^{i\tilde{\lambda}_+}}. \label{propinplanezeeman}}
 The adiabatic phase $\tilde{\lambda}_{\pm}$ is the sum of a dynamical phase ${\pm} l^2 \delta S/2$ and  the single-band Berry phase $\phi^B_\pm$, for the outer ($+$) and inner ($-$) orbit respectively.
@@
 The decomposition of the effective Hamiltonian [cf.\ Eq.
-(\ref{calHRZ})] into sums of Pauli matrices ($\calh{=}\sum_jd_j\sigma_j$) defines a three-vector $\bd{=}({-}\alpha k_y$,$Z_\parallel{+}\alpha k_x,{-}Z_\perp$).
- $\phi_{\pm}^B$  equals half the solid angle subtended by   ${\mp} \bd(\bk)$ as $\bk$ is varied along the outer/inner orbit.[Berry]   These angles are indicated in the figure by blue outlines.\label{fig:blochsphere}}
+(\ref{calHRZ})] into  Pauli matrices ($\calh{=}\sum_j\calh_j\sigma_j$) defines a three-vector $\boldsymbol{\calh}{=}({-}\alpha k_y$,$Z_\parallel{+}\alpha k_x,{-}Z_\perp$).
+$\phi_{\pm}^B$ equals half the solid angle subtended by   ${\mp} \boldsymbol{\calh}(\bk)$ [solid blue line] as $\bk$ is varied along the outer/inner orbit;[Berry] the orientation of the solid angle is indicated by blue dotted lines.
+The out-of-plane Zeeman interaction lifts $\boldsymbol{\calh}$ out of the x-y plane, but this occurs at most over a fraction ${\sim}(\bar{\mu}_{\sma{\text{min}}}m_0/m{\ll}1)$ of the cyclotron period.
+\label{fig:blochsphere}}
 \end{figure}
@@
 }
-$\Omega_{\pm}$ is the phase acquired by an electron in adiabatically traversing orbit $\pm$; the quantum Maslov correction $\gamma_{\pm}{=}\pi$ for circular orbits.
+$\Omega_{\pm}$ are phases acquired by an electron in adiabatically traversing the orbits labelled $\pm$, respectively; the quantum Maslov correction $\gamma_{\pm}{=}\pi$ for circular orbits.
 A quantization rule analogous to \q{coscos} was previously derived by us for a II-Dirac point that intermediates an electron- and hole-like orbit [AALG].
@@
 
-In the limit $B{\rightarrow}0$ (equivalently, $\bar{\mu}{\rightarrow} \infty$), Landau-Zener tunneling is negligible ($\tau{\rightarrow}1,\bar{\varphi}{\rightarrow}0$), and \q{coscos} simplifies to the Onsager-Lifshitz-Roth rules ($\Omega_{\pm}/2\pi{\in}\Z$) for  two independent orbits.
+In the limit $\bar{\mu}{\rightarrow} \infty$, Landau-Zener tunneling is negligible ($\tau{\rightarrow}1,\bar{\varphi}{\rightarrow}0$), and \q{coscos} simplifies to the Onsager-Lifshitz-Roth rules ($\Omega_{\pm}/2\pi{\in}\Z$) for  two independent orbits.
 
@@
 To recapitulate, $E_n^0(B)$ [cf.\ \q{trefoillerule}] exhibits a periodicity on short scales associated to the large area of the trefoille orbit.
-This short-scale periodicity is lost due to  finite-$\tau$ corrections, yet a longer-range correlation (associated to the smaller differential action $\delta S$ between spin-split orbits) persists, as shown by the first-order-in-$\tau$ correction:\footnote{The general form of this perturbative calculation can be found in Sec.
+This short-scale periodicity is lost due to  finite-$\tau$ corrections, yet a longer-range correlation (associated to the smaller differential area $\delta S$ between spin-split orbits) persists, as shown by the first-order-in-$\tau$ correction:\footnote{The general form of this perturbative calculation can be found in Sec.
 IX-E of [100page].}
@@
 
-We have argued in \s{sec:qtznrules} that the subleading corrections ($\lambda_{1,2}$) to the quantization rule [cf.\ \q{eq:rule}] generically lift the spin-degeneracy of Landau levels -- the level splitting is approximately $\var_c\delta_\lambda/2\pi$ with $\delta \lambda=|\lambda_1-\lambda_2|$.
+We have argued in \s{sec:qtznrules} that the subleading corrections ($\lambda_{1,2}$) to the quantization rule [cf.\ \q{eq:rule}] generically lift the spin-degeneracy of Landau levels -- the level splitting is approximately $\var_c\delta \lambda/2\pi$ with $\delta \lambda=|\lambda_1-\lambda_2|$.
 Conversely, Landau levels are approximately spin-degenerate if $\lambda_1{=}\lambda_2$ (mod $2\pi$) -- this degeneracy condition for the eigenvalues of $\A$ may require fine-tuning of the Peierls-Onsager Hamiltonian.
@@
 Before this general symmetry classification,  we will first develop physical intuition by studying two rotationally-symmetric models [cf.\ \s{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}] where only one tunable parameter is needed -- this can be the $B$ field itself.
-Finally, the experimental implications of single- and double-parameter tuning of Landau-level degeneracies are discussed in \s{sec:qo}.
+
+%Finally, the experimental implications of single- and double-parameter tuning of Landau-level degeneracies are discussed in \s{sec:qo}.
 
@@
 \e{\bigg|\f{E_{1}-E_2}{\var_c}\bigg|_{B=\bar{B}} = \order\left( \f{\partial \lambda_a/\partial E}{\bar{l}^2\partial  S/\partial E}  \right)\ll 1,\label{llquasideg}}
-with $\bar{l}$ magnetic length of $\bar{B}$.
+with $\bar{l}$ the magnetic length associated to $\bar{B}$.
 Alternatively, we may fix $\bar{E}$ and investigate how Landau levels disperse as a function of $B$; the analog of \q{llquasideg}  is the existence of paired Landau levels in close proximity to $\bar{l}^2$, with a splitting of order:
@@
 
-%To exemplify the role of rotational symmetry in reducing codimension, we return to the Rashba model [cf.\ \q{eq:Rashba-Hamiltonian}] absent Dresselhaus spin-orbit coupling and in-plane Zeeman field.
-Owing to a continuous rotational symmetry (denoted $\mathfrak{c}_{\infty}$), $\calh(\bk)$ is a constant along the circular zeroth-order orbit [cf.\ \q{rashbaeffham}], and therefore the propagator simplifies to $\A{=}$exp$[{-}i\calh T_c/\hbar]$.
-The latter is expressible in the exponential form:
-%\e{\A =e^{-i2\pi(r_1\tau_1{+}r_3\tau_3)}, \;\;(r_1,r_3){=}\bigg(\f{g_{\sma{\text{eff}}}}{4}-\f1{2},\f1{2}-\f{\alpha k_{{E}}}{\var_c}\bigg).\notag} 
-%All degeneracies occur along circles of radius $\sqrt{r_1^2+r_3^2}{=}{j}/2$, with ${j}$ a nonnegative, even (resp.\ positive, odd) integer for  $\A{=}I$ (resp.\ $\A{=}{-}I$).
-In this exactly-soluble model [cf.\ \q{eq:Rashba-exact}], all  degeneracies (${j} {\ge} 0$) of $\A$ correspond to exact Landau-level degeneracies, rather than the near degeneracies described by \qq{llquasideg}{llquasidegB}.
-
-%That the ${j}{=}0$ manifold has codimension two can be understood from an elementary result in quantum mechanics: taking $\alpha{=}0$ \textit{and} $m{=}m_0$, we recover the Zeeman-split Landau levels of a free electron gas without spin-orbit coupling; all levels (except the lowest) are spin-degenerate owing to the equality of the Zeeman and cyclotron energies.[LandauLifshitzstatphysI]   All other manifolds ($j{>}0$) have unit codimension, and can be reached by varying $B$ alone (with fixed $g_{\sma{\text{eff}}}$).
-
 To understand why rotational symmetry reduces codimension in the Landau-level problem, we return to the Rashba model [cf.
@@
 Consequently, the propagator [cf.\ \q{eq:prop}] simplifies to the exponential form:
-\e{\A{=}\exp(-2\pi i\sum_{j}r_j\tau_j),\label{expform}}
+\e{\A{=}-\exp(-2\pi i\sum_{j}r_j\tau_j),\label{expform}}
 where
-\e{\br=\f{\br_0(|\br_0|+\pi)}{|\br_0|},\br_0{=}\bigg(\f{g_{\sma{\text{eff}}}}{4}{-}\f1{2},0,-\f{\alpha k_{\sma{E}}}{\var_c}\bigg).}
+\e{\br{=}\bigg(\f{g_sm}{4m_0}{-}\f1{2},0,-\f{\alpha k_{\sma{E}}}{\var_c}\bigg).}
 Any $\text{SU}(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}] for some (possibly non-unique) $\br$, with $r_2$ not necessarily zero.
@@
 
-All eigenvalue degeneracies of $\A$ occur on spheres in $\br$-space with radii $|\br|{=}\sqrt{r_1^2{+}r_2^2{+}r_3^2}$ equal to an integer ($j$)  multiple of $1/2$;  ${j}$ is even (resp.
-odd) for  $\A{=}I$ (resp.\ $\A{=}{-}I$).
+All eigenvalue degeneracies of $\A$ occur on spheres in $\br$-space with radii $|\br|{=}\sqrt{r_1^2{+}r_2^2{+}r_3^2}$ equal to an integer ($j$)  multiple of $1/2$;  ${j}$ is odd (resp.
+even) for  $\A{=}I$ (resp.\ $\A{=}{-}I$).
 This condition $|\br|{=}j/2$ (for any nonzero $j$) may be attained by tuning a single parameter.
@@
 (a) The degeneracy manifold of $\A{=}I$ is a path-connected hypersurface.
-(b) illustrates the degeneracy manifold of $\A=-I$, which lie confined to  the $\alpha{=}0$ and $\beta{=}0$ planes.
+Points in $\alpha=0$ or $\beta=0$ planes are colored in red.
+(b) illustrates the degeneracy manifold of $\A=-I$, which lie confined to  the $\alpha{=}0$ and $\beta{=}0$ planes (blue translucent planes).
 Each $\mathfrak{c}_{\infty}$-symmetric plane contains an infinite set of concentric, circular line degeneracies.
@@
 
-Since $\A$ depends on $\alpha,~\beta,~l,~E,~m$ only through $\alpha k_E /\var_c$, $\beta k_E /\var_c$ and $g_\text{eff}$, let us consider the three-dimensional parameter space $(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_{\sma{\text{eff}}}){\in} \mathbb{R}^3$.
-$\A(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_{\sma{\text{eff}}}){=}{\pm} I$ determines a set of concentric circles in the $\beta{=}0$ plane, as per the $\mathfrak{c}_{\infty}$-symmetric case study in \s{sec:ctsrot}.
+Since $\A$ depends on $\alpha,~\beta,~l,~E,~m$ only through $\alpha k_E /\var_c$, $\beta k_E /\var_c$ and $g_sm/m_0$, let us consider the three-dimensional parameter space $(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_sm/m_0){\in} \mathbb{R}^3$.
+$\A(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_sm/m_0){=}{\pm} I$ determines a set of concentric circles in the $\beta{=}0$ plane, as per the $\mathfrak{c}_{\infty}$-symmetric case study in \s{sec:ctsrot}.
 Moving off this plane, we find that $\A{=}I$ is satisfied in a  neighborhood of $\beta{=}0$, i.e., $\A{=}I$ defines a hypersurface in $\mathbb{R}^3$ that is illustrated in \fig{fig:dgn}(a).
@@
 To recapitulate, we have found that one of every two Landau-level crossings (those labelled by odd $j$) destabilize due to the symmetry reduction.
-\textbf{[Bonus content:consider the Berry phase of the eigenstate of A.
-Is it quantized for a symmetrically chosen loop in r space?]}
+
+\textbf{[Bonus content:consider the Berry phase of the eigenstate of A. Is it quantized for a symmetrically chosen loop in r space?]}
 %If a line node (in the $\beta{=}0$ plane) were perturbatively stable to finite $\beta$, then it would be embedded in a two-dimensional degeneracy hypersurface of $\mathbb{R}^3$; if the planar line node were unstable, this embedding does not happen, i.e., the planar line node is simply a line node in $\mathbb{R}^3$.
@@
 with $\sum_{j=1}^4r_j^2{=}1$.
-It follows that $r_2{=}0$ is a necessary and sufficient condition for ${\cal \bar{A}}{=}I$.
+It follows that $r_2{=}0$ is a necessary and sufficient condition for $\bar{\A}{=}I$.
 The corresponding degeneracy manifold is a path-connected hypersurface, which separates $\br=(r_1,r_2,r_3,r_4)$-space into two distinct connected components.
-\textbf{[does this conclusion generalize to any N]} \fig{fig:dgn}(a) illustrates the same hypersurface in distinct coordinates: $(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_{\sma{\text{eff}}})$.
+Generally, degenerate manifold of $\A$ of $\mathfrak{c}_N$ symmetric Hamiltonian separates $\br$-space (parametrizing $1/N$ of $\A$) into $N$ distinct connected components.
+\fig{fig:dgn}(a) illustrates the $\A=-I$ degenerate manifold in distinct coordinates: $(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_sm/m_0)$.
 On the other hand, ${\cal \bar{A}}{=}{-}I$ occurs if and only if $\br{=}(0,\pm 1,0,0)$.
@@
 \caption{Cyclotron orbits for $\mathfrak{c}_2$-symmetric [(a)] and $\mathfrak{c}_3$-symmetric [(b)] breakdown.
-Bottom right inset of (a) presents an enlarged view of the breakdown junction, where the purple rectangle has area $S_{\sma{\square}}$.\label{fig:Cn-breakdown}}
+Top right inset of (a) presents an enlarged view of the breakdown junction, where the purple rectangle has area $S_{\sma{\square}}$.
+(c) Klein tunneling limit of $\mathfrak{c}_2$-symmetric (upper) and $\mathfrak{c}_3$-symmetric (lower) breakdown cyclotron orbits.
+(d) Two Feynman paths that switch to the other band by one tunneling event.
+(e) Two Feynman paths that returns to the same band by zero or two tunneling events.
+\label{fig:Cn-breakdown}}
 \end{figure}
@@
 \e{H_{\pm} =\pm {\hbar}\sqrt{\f{2\mu}{m_2}}\bigg(\frac{m_2}{m_1}+\sz\bigg)\delta k_x+w\delta k_{y}\sx+\epsilon_0, \label{linearHam2}}
-from which we deduce that both Dirac points are  type-II if $m_1{<}m_2$; we further assume $m_1{\ll}m_2$ so that the quasidegeneracy condition ($\delta S/S$) is satisfied.
+from which we deduce that both Dirac points are  type-II if $m_1{<}m_2$; we further assume $m_1{\ll}m_2$ so that the quasidegeneracy condition ($\delta S/S{\ll}1$) is satisfied.
 
@@
 For sufficiently weak field, interband tunneling is localized near either II-Dirac point, and occurs with the Landau-Zener probability:
-\e{\rho^2=e^{-2\pi\bar{\mu}}, \; \bar{\mu}=\f{\big(Z_{\perp}^2+(m_1/m_2)^2(E-\epsilon_0)^2\big)l^2}{2w\sqrt{2E/m_1}}. \label{landauzenerc2} }
+\e{\rho^2=e^{-2\pi\bar{\mu}}, \; \bar{\mu}=\f{\big(Z_{\perp}^2+(m_1/m_2)^2(E-\epsilon_0)^2\big)l^2}{2w\sqrt{2E/m_1}}. \label{landauzenerc2}}
+Equivalently, $\bar{\mu}{=}S_{\sma{\square}}l^2/8$, with $S_{\sma{\square}}$ the area of rectangle inscribed between the two hyperbolic arms [cf.\  Fig\ref{fig:Cn-breakdown}(a)].
 Elsewhere, an electron undergoes adiabatic (band-conserving) dynamics.
 Due to $\mathfrak{c}_2$ symmetry, the time-evolution propagator over the full cyclotron period is simply the square of the propagator for half the period:
-\e{\A={e^{i(\tilde{\lambda}_++\tilde{\lambda}_-)}}\left(\matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}}{\diagmatrix{e^{i\f{\tilde{\lambda}_+-\tilde{\lambda}_-}{2}}}{e^{i\f{\tilde{\lambda}_--\tilde{\lambda}_+}{2}}}} \right)^2.
-\label{propC2breakdown}}
+\e{\A=\left(\matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}}{\diagmatrix{e^{i\tilde{\lambda}_-}}{e^{i\tilde{\lambda}_+}}} \right)^2. \label{propC2breakdown}}
 The half-period propagator may be taken from \qq{scattmat}{propinplanezeeman}, with  $\bar{\mu}$ here given by \q{landauzenerc2}, and  $\tilde{\lambda}_{\pm}{=}{\pm}l^2\delta S/4$ plus a field-independent geometric phase.
@@
 \begin{align}
-\Delta:= \tilde{\lambda}_+{-}\tilde{\lambda}_{-}{+}2\bar{\varphi},\;\;
+\Delta:= \tilde{\lambda}_-{-}\tilde{\lambda}_{+}{+}2\bar{\varphi},\;\;
 \tau\cos\f{\Delta}{2}= \begin{cases} 0, & {\A}=+I \\
@@
 \end{align}
-$\Delta$ is the differential phase between two Feynman loops  that involve a single tunneling event  over one cyclotron period, as illustrated in Fig.\ \ref{fig:Cn-breakdown}(a) \textbf{[might be good to draw loops in figure using (translucent?) colors other than black]}.
-The adiabatic limit is given by $\tau{=}1$ and $\bar{\varphi}{=}0$, which leads to the satisfaction of \q{c2breakdowndgncondition} for $l^2$ equal to an integer multiple of $2\pi/\delta S$.
+$\Delta$ is the differential phase between two Feynman paths  that involve a single tunneling event  over one cyclotron period, as illustrated in Fig. \ref{fig:Cn-breakdown}(d).
+The adiabatic limit is given by $\tau{=}1$ and $\bar{\varphi}{=}0$, which leads to the satisfaction of \q{c2breakdowndgncondition} for $l^2$ equal to an integer multiple of $2\pi/\delta S$ up to a field indepedent offset.
 As noted in \s{sec:introducecodimension}, such a periodicity corresponds to a differential increment of a single, magnetic flux quantum.
@@
 Deviating from the adiabatic limit, we deduce from \q{c2breakdowndgncondition} that  $\A{=}I$ remains attainable by varying $B$, but $\A{=}{-}I$ is unattainable because $\tau{<}1$; this is consistent with the codimension analysis of \q{proprashba}.
-The conditions $\A{=}I$ and $\rho{>}0$ are interpreted as the destructive interference of  two, single-tunneling Feynman loops, i.e., $\Delta{=}\pi$.
-Concurrently, there is constructive interference of the Feynman loops involving zero and two tunneling events.
-The differential phase between outer and inner zero-tunneling (band-conserving) loops is simply $2\Delta{=}2\pi$ (by $\mathfrak{c}_2$ symmetry), hence Landau levels are quasidegenerate.
+The conditions $\A{=}I$ and $\rho{>}0$ are interpreted as the destructive interference of  two, single-tunneling Feynman path (cf.
+Fig.
+\ref{fig:Cn-breakdown}(d)).
+Concurrently, there is constructive interference of the Feynman loops involving zero and two tunneling events (cf.
+Fig.
+\ref{fig:Cn-breakdown}(e)).
+The differential phase between outer and inner zero-tunneling (band-conserving) loops is simply 0 (mod $2\pi$), hence Landau levels are quasidegenerate.
 Such quasidegeneracies recur as $\Delta$ advances by $2\pi$, corresponding to a periodicity in $l^2$ of $4\pi/\delta S$ (or two flux quanta).
-This periodicity is not affected by the additional phase $2\bar{\phi}$ in $\Delta$, because $\bar{\phi}$  varies on the scale  $2\pi/S_{\sma{\square}}$ \textbf{[we can't use symbols we don't define; footnotes don't count]},\footnote{For $\bar{\varphi}(\bar{\mu})$ to vary  $\sim 1$, the Landau-Zener parameter $\bar{\mu}$ must vary by $\sim 1$ [cf.\  Fig.\ 10 in 100page].
-Moreover, $2\pi\barmu{:}{=} (2\pi/8) l^2S_{\sma{\square}}$.[AALG]} which is much larger than
- $4\pi/\delta S$. To recapitulate, half the Landau-level quasi-crossings (over the $B$ axis) are destabilized by tunneling; the robustness of the other half relies on $\mathfrak{c}_2$ symmetry.
+This periodicity is not affected by the additional phase $2\bar{\phi}$ in $\Delta$, because $\bar{\phi}$ varies on the scale  $2\pi/S_{\sma{\square}}$,\footnote{For $\bar{\varphi}(\bar{\mu})$ to vary  $\sim 1$, the Landau-Zener parameter $\bar{\mu}$ must vary by $\sim 1$ [cf.\  Fig.\ 10 in 100page].
+Moreover, $2\pi\barmu{:}{=} (2\pi/8) l^2S_{\sma{\square}}$.[AALG]} which is much larger than $4\pi/\delta S$.
+To recapitulate, half the Landau-level quasi-crossings (over the $B$ axis) are destabilized  by tunneling; the robustness of the other half relies on $\mathfrak{c}_2$ symmetry.
+There exists a complementary argument for the existence of Landau-level quasi-crossings in the Klein-tunneling limit $(\tau{=}0)$: the two independent orbits are related by $\mathfrak{c}_2$ symmetry, leading to exactly-degenerate Landau levels.
 
@@
 \ref{fig:Cn-breakdown}(b).
-The corresponding propagator $\A$ has a form analogous to \q{propC2breakdown} -- but with $(\cdot)^2$ replaced by $(\cdot)^3$, and with $\tilde{\lambda}_\pm{=}{\pm} l^2\delta S/4$ replaced by $\pm l^2\delta S/6$ (plus a field-independent geometric correction).
-The degeneracy condition is modified to $\tau\cos[(\tilde{\lambda}_+-\tilde{\lambda}_-)/2{+}\bar{\varphi}]{=}{\pm} 1,{\pm} 1/2$.
+In the adiabatic regime ($\tau{\approx}1$), Landau-level quasidegeneracies occur with a periodicity of one flux quantum; however, in the Klein-tunneling regime ($\tau{\approx}0$), there exists only one dominant orbit shaped like a three-fold-symmetric trefoil knot --  all Landau levels are nondegenerate with spacing determined by the effective mass of the trefoil; this property generalizes to $\mathfrak{c}_N$-symmetric II-Dirac models with odd $N$.
+
+To resolve this tension (for $N{=}3$), consider that the propagator $\A$ has a form analogous to \q{propC2breakdown} -- but with $(\cdot)^2$ replaced by $(\cdot)^3$, and with $\tilde{\lambda}_\pm{=}{\pm} l^2\delta S/4$ replaced by $\pm l^2\delta S/6$ (plus a field-independent geometric correction).
+The degeneracy condition is modified to $\tau\cos[(\tilde{\lambda}_+{-}\tilde{\lambda}_-)/2{+}\bar{\varphi}]{=}{\pm} 1,{\pm} 1/2$.
 With nonzero tunneling ($1/2{<}\tau {<}1$), only $\pm 1/2$ is attainable -- this implies that of every three degeneracies that exist in the adiabatic limit, only two are perturbatively stable.
@@
 \ref{app:codimension}.
-%$\cala{=}{\pm} I$ is attained if and only if  $\tau \cos(\delta \lambda_+{+}\bar{\varphi}){=}{\mp}1/2$.
-
-%There then are no more $B$-tunable degeneracies beyond a critical field where  $\tau{<}1/2$.
-
-%In the zero-tunneling limit ($\rho{=}0$), the condition for degeneracy (of $\cala$) is that $\exp[i(\phi_+{+}\bar{\varphi})]$ is a sixth root of unity -- the periodicity in $l^2$ corresponds to a single quantum of differential magnetic flux.
-
-\textbf{Bonus: A different realization of two-fold symmetric breakdown: angular magnetoresistance oscillations.}
-%\red{[I begin to question this again.
-In my previous understanding, the in-plane magnetic field changes the band structure while the out-of-plane magnetic field produces LLs.
-Now I believe the in-plane magnetic field cannot be simply understood simply as a change in band structures.
-Therefore, I am not quite sure whether it is related to magnetic breakdown.]}
+
+\textbf{[Bonus: A different realization of two-fold symmetric breakdown: angular magnetoresistance oscillations.]}
 
@@
 \end{tabular*}
-\caption{Codimensions of degeneracy manifold of two-by-two propagator $\A$ under constraints of different type of symmetries.
-The first column is class number.
+\caption{Symmetry-constrained codimensions for the two-by-two propagator $\A$.
+The first column numbers the symmetry class of $\A$.
 The second and third column defines how the symmetry acts on the cyclotron orbit.
-The next two columns are intrinsic properties of $g$ (cf.
-Sec.
-\ref{sec:reviewtenfold}).
-The sixth column indicates whether this symmetry class applies to quasidegenerate propagator $\A$.
+The next two columns  inform us if the mapping $\bk{\rightarrow}g{\circ}\bk$ [cf.\ \q{gmapk}]  preserves ($u{=}0$) or inverts ($u{=}0$) the orientation of the orbit, and if $g$ preserves ($s{=}0$) or inverts ($s{=}1$) the arrow of time.
+The sixth column indicates whether this  class is potentially a symmetry of quasidegenerate orbits.
 The seventh column specifies additional conditions (on the representation of $g$) which must be imposed to uniquely determine the codimension.
-$\breve{g}$ is the diagonalized, unitary matrix representation of $g$ in the degenerate subspace of $\hat{H}_0$.
-In class 5, $\breve g$ is evaluated at $\bk$ where $g\circ\bk=\bk$.
-Symmetry operations whose sewing matrices are needed are mostly reflections and glide planes.
-For convenience, we presented in table \ref{table:sewing-matrix} sewing matrix for common reflections and glide planes.
+$\breve{g}$ is defined as the diagonalized, unitary matrix representation of $g$ in the degenerate subspace of $\hat{H}_0$.
+In class 5, $\breve g$ is evaluated at $g$-invariant $\bk$ ($g\circ\bk=\bk$).
+For the reader's convenience, we present some commonly-used matrix representations for exactly degenerate bands in Tab.\ \ref{table:sewing-matrix}.
 The last column presents codimensions of the degeneracy manifold.
-In class 2, 4 and 5, $\A$ is subject to another requirement: $\text{det}(\A)=\pm 1$ [topofermi].
-For spin degeneracy studied in current work, we assume SOC can be turned off continuously without lifting the degeneracies or increasing the degree of degenearcies.
-With this assumption, $\text{det}(\A)=1$, which is utilized to obtain the current table.
+For exactly-degenerate orbits in class 2, 4 and 5, $\A$ satisfies $\text{det}(\A){=}1$,[topofermi] with the assumption that spin-orbit coupling can be turned off continuously without changing the degeneracy of the orbit.
  \label{table:codimension}}
@@
 To clarify, we define the $g$-constrained codimension as the minimal codimension -- among all degeneracy manifolds -- as enforced by $g$ symmetry.
-For example, we have found that two-fold rotational symmetry reduces the codimension of the $\A{=}{+}I$ manifold (to unity), but not the codimension of the $\A{=}{-}I$ manifold [cf.\ \q{proprashba}]; the rotation-constrained codimension is then unity.
-Each entry in the right-most column of Tab.\ \ref{table:codimension} equals the $g$-constrained codimension for any $g$ in that class.\textbf{[chong, please add footnote describing how the notion of symmetry-constrained codimension is useful for class 3 and 4.
-We don't need to give details, just some easy-to-read facts.]}
+To motivate `minimal' in this definition, we have found that two-fold rotational symmetry reduces the codimension of the $\A{=}{+}I$ manifold (to unity), but not the codimension of the $\A{=}{-}I$ manifold [cf.\ \q{proprashba}]; the rotation-constrained codimension is then unity.
+Generally, it is only in class 3 and 4 that different  degeneracy manifolds may have different codimensions.
+Each entry in the right-most column of Tab.\ \ref{table:codimension} equals the $g$-constrained codimension for any $g$ in that class (and possibly satisfying an additional constraint on the representation of $g$, as specified by the second-to-last column).
 
@@
 The former is exemplified by $T\inv$ symmetry, and the latter by $T\rot_{2z}$ (the composition of time reversal with a two-fold rotation about the field direction).
-For an exactly-degenerate orbit $\frako$ confined to a $\rot_{2z}$-invariant plane, the wavefunction can be made real at each $\bk$ in $\frako$, and hence the associated propagator $\A$ is unitarily equivalent to a special orthogonal matrix[AA] with a single, tunable angle of rotation -- this provides an intuitive explanation for the unit codimension.
+For an exactly-degenerate orbit $\frako$ confined to a $\rot_{2z}$-invariant plane, the associated propagator $\A$ is unitarily equivalent to a special orthogonal matrix [AA,100page] with a single, tunable angle of rotation -- this provides an intuitive explanation for the unit codimension.
 
@@
 \begin{table}
-\begin{tabular*}{\columnwidth}{l@{\extracolsep{\fill}}ccc}
+\begin{tabular*}{\columnwidth}{c@{\extracolsep{\fill}}ccc}
 \hlineB{2.0}
- symmetry  & origin of degeneracy & $\breve{g}\propto$ \\
+class No. & symmetry  & origin of degeneracy & $\breve{g}\propto$ \\
 \hline 
- $\mathfrak{t} \mathfrak{r}_x^n \mathfrak{r}_z^m$ & $T\mathfrak{i}$ & $\sigma_z$ \\
-  $\mathfrak{t} \mathfrak{r}_x^n \mathfrak{r}_z^m$ & continuous spin rotation & $\sigma_z$ \\
- $\mathfrak{r}_z$, $\mathfrak{r}_x$, $\mathfrak{r}_{x,\boldsymbol{c}/2}\mathfrak{r}_z$ & $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$ & $I$ \\
-$\mathfrak{r}_{x,\boldsymbol{c}/2}$, $\mathfrak{r}_x \mathfrak{r}_z$  & $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$ & $\sigma_z$ \\
+\multirow{2}{*}{1} & \multirow{2}{*}{$\mathfrak{r}_z$, $\mathfrak{r}_{z,\boldsymbol{a(b)}/2}$} & $T\mathfrak{i}$, spin SU(2) & $\sigma_z$ \\
+\cline{3-4}
+ & & $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$ & $I$ \\
+\hline
+\multirow{3}{*}{5} & $\mathfrak{r}_{x(y),\boldsymbol{c}/2}$ & $T\mathfrak{i}$, spin SU(2), $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$ & $\sigma_z$ \\
+\cline{2-4}
+& $\mathfrak{r}_{x(y)}$,$\mathfrak{r}_{x(y),\boldsymbol{b(a)}/2}$, & $T\mathfrak{i}$, spin SU(2) & $\sigma_z$ \\
+\cline{3-4}
+& $\mathfrak{c}_{2x(y)}$, $\mathfrak{c}_{2x(y),\boldsymbol{b(a)}/2}$ & $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$ & $I$\\
 \hlineB{2.0}
 \end{tabular*}
-\caption{Two by two sewing matrices for reflections (e.g., $\mathfrak{r}_x$) and glide planes (e.g., $\mathfrak{r}_{x,\boldsymbol{c}/2}$).
-The two-fold degeneracy are assumed to be protected by either spatial-time inversion symmetry ($T\mathfrak{i}$), composition of time reversal and two fold rotation symmetry ($T\mathfrak{c}_{2z,\boldsymbol{c}/2}$) at $k_z=\pi$ and continous spin rotation symmetry (i.e., negligible SOC).
-Glide operation in $x$ or $y$ direction is irrelevant; for example, $\mathfrak{r}_x$ and $\mathfrak{r}_{x,\boldsymbol{b/2}}$ share the same entry.
-$x$ and $y$ are equivalent; for example, $\mathfrak{r}_x$ and $\mathfrak{r}_y$ share the same entry.
-$\mathfrak{t}$ is (arbitrary) translation.
+\caption{Matrix representations of reflections (e.g., $\mathfrak{r}_x$) and rotations (e.g.
+$\mathfrak{c}_{2y}$) followed by possible half a lattice translations in $x,~y,~z$ directions (labeled by $\boldsymbol{a,~b,~c}$ respectively).
+This table is relevant for magnetic field in $\pm z$ direction.
+The two-fold exact degeneracy are assumed to be protected by either spatial-time inversion symmetry ($T\mathfrak{i}$), composition of time reversal and nonsymmorphic two fold rotation symmetry ($T\mathfrak{c}_{2z,\boldsymbol{c}/2}$) at $k_z=\pi$ or spin SU(2) (i.e., negligible SOC).
 \label{table:sewing-matrix}}
@@
 In the weak-field, adiabatic regime, the antinodes of this pattern occur with period $2\pi/\delta S$ in $l^2$ [cf.\ \s{sec:introducecodimension}]; in the non-adiabatic regime, the antinodes are generically aperiodic [cf.\ \q{lambdasmallB}].
-Such beatings have been observed for semiconductor heterostructures[das,several more]; our contribution is the first quantitative theory  [summarized by the quantization rule of \qq{eq:rule}{berryconn} and the Lifshitz-Kosevich formula of \q{eq:LK}] from which one can calculate the beating pattern.
+Such beatings have been observed for semiconductor heterostructures[das,several more].
+Our contribution is the first semiclassical theory  [summarized by the quantization rule of \qq{eq:rule}{berryconn} and the Lifshitz-Kosevich formula of \q{eq:LK}] from which one can calculate the beating pattern; in particular, one may extract the intervals (in $1/B$) between antinodes  for the Rashba 2DEG [by imposing $\delta \lambda{\equiv}\pi$ in \q{eq:Rashba-lambda}] and for the Rashba-Dresselhaus 2DEG [see the next \s{sec:quantosc_quasideg}].
 
@@
 \includegraphics[width=1.0\columnwidth]{qo.png}
-\caption{Quantum oscillation of the Rashba-Dresselhaus 2DEG.
+\caption{Quantum oscillations in the Rashba-Dresselhaus 2DEG.
 (a) Evolution of $\delta\lambda$ with respect to the inverse field for different values of $\beta$.
-Horizontal grey lines are $\delta\lambda=\pi$.
-Upper panel of (b): Landau levels near fields indicated by vertical grey lines in (a) at $\beta=3.0(10^{5}$cm/s$\cdot\hbar$), corresponding to $\delta\lambda=0$, $\delta\lambda=\pi/2$ and $\delta\lambda=\pi$ respectively.
-The line of $\beta=3.0(10^{5}$cm/s$\cdot\hbar$) is indicated by a black arrow in (a).
-Lower panel (b): Oscillations of chemical potentials corresponding to the upper panel.
-Fixed partical number density is assumed.
-In this figure, other parameters are $m=0.076m_0$, $\alpha=7.5(10^{5}$cm/s$\cdot\hbar$) and $E=0.4$eV.
+The horizontal dashed line indicates $\delta\lambda=\pi$.
+For $\beta=3.0(10^{5}$cm/s$\cdot\hbar$), we have plotted -- in the upper panel of (b) -- the Landau levels at three $B$ values, as indicated by the vertical dashed lines in (a).
+The evolution of $\delta \lambda$ for  $\beta=3.0(10^{5}$cm/s$\cdot\hbar$) is given by a cyan-colored line indicated by a black arrow in (a); the three chosen $B$ values correspond approximately to  $\delta\lambda{=}0$, $\delta\lambda{=}\pi/2$ and $\delta\lambda{=}\pi$ respectively.
+Lower panel of (b) illustrates the saw-tooth oscillation of the chemical potential (at fixed electron density) corresponding to the upper panel.
+Other parameters chosen in (b): $m{=}0.076m_0$, $\alpha{=}7.5(10^{5}$cm/s$\cdot\hbar$) and $E=0.4$eV.
 \label{fig:qo}}
@@
 Where $\delta\lambda{\equiv}\pi$, Landau levels are  quasi-equidistant, hence adjacent minima (of conductivity) should be identically low.
-Where $\delta\lambda{\equiv}0$, every consecutive gap is small compared to $k_BT$ and $h/\tau_{\sma{D}}$, hence every other  minimum (of conductivity) is smeared out.[rashba] $0{\leq}\delta\lambda{\leq}{\pi}$ thus characterizes a smooth crossover between period-doubled and -undoubled oscillations, as representatively illustrated in \fig{fig:qo}(b).
+Where $\delta\lambda{\equiv}0$, every consecutive gap is small compared to $k_BT$ and $h/\tau_{\sma{D}}$, hence every other  minimum (of conductivity) vanishes.[rashba] $0{\leq}\delta\lambda{\leq}{\pi}$ thus characterizes a smooth crossover between period-doubled and -undoubled oscillations, as representatively illustrated in \fig{fig:qo}(b).
 
@@
 \textbf{[work in progress]}
-Tunable parameters: B, orientation of B, bias voltage. The first is not applicable to exactly-degenerate orbits.
+Summary: We have extended the semiclassical theory to describe  quasidegenerate orbits.
+A nontrivial implication of our theory is the determination of symmetry constrained codimension, summarized in tab I.
+The codimension is the number of tunable real parameters needed to attain a Landau-level quasidegeneracy.
+Tunable parameters: B, orientation of B, bias voltage.
+The first is not applicable to exactly-degenerate orbits.
 For spin-split bands, $\lambda$ depends strongly on the $B$ field for quasidegenerate orbits; for degenerate orbits, the $B$-dependence of $\lambda$ is relatively weaker, i.e., of higher power in the small parameter $B$ [Roth, Niu, Fuchs].
@@
 
-Application to $D>4$. Not uncommon to find spin-degenerate bands (in centrosymmetric solids) which are quasi-four-fold degenerate.
-
-Phase offset of quantum oscillations. Is it quantized for quasidegenerate orbits?
+Application to $D>4$.
+Not uncommon to find spin-degenerate bands (in centrosymmetric solids) which are quasi-four-fold degenerate.
+\red{[I introduced in the first paragraph of App.
+B how D=4 is useful]}
+
+\red{[Maybe talk about codimension for $D>2$. However, I have no idea what that may be. I don't even find a good parametrization of SU(3).]}
+
+Phase offset of quantum oscillations. Is it quantized for quasidegenerate orbits? \red{[$\det \A$=1 means two opposite offsets, not quantized offset.]}
+
+Wilson loop.
 
@@
 In the absence of symmetry, we estimate
-\e{\p{\lambda_{a}}{E}=\order\left(\f{g_s}{m_0}\p{m}{E},\f{\partial^2S/\partial E^2}{\partial S/\partial E} \right)\ll \f{2\pi}{\var_c},} 
+\e{\p{\lambda_{a}}{E}=\order\left(\f{g_s}{m_0}\p{m}{E},\f{\partial^2S/\partial E^2}{\partial S/\partial E} \right)\ll \f{2\pi}{\var_c}, \la{dlambdadE}} 
 where $m_0$ is the free-electron mass, and $m{=}\hbar^2(\partial S/\partial E)/2\pi$ the effective mass.
@@
 We estimate
-\e{\f{E_+-E_-}{\var_c} \approx &\; \f{r}{\var_c}\left(\f1{\calq'_+}-\f1{\calq'_-}\right)\approx  \f{r}{2\pi}\var_c \left( \lambda'_- -\lambda'_+\right). \label{estimate}}
-What is left is to estimate $\lambda_{\pm}'$, which we have accomplished in \s{sec:qtznrules} in both weak- and strong-field regimes.
-Combining our estimates for $\lambda'$ with \q{estimate}, we  arrive at \q{llquasideg}.
-
+\e{\f{E_+-E_-}{\var_c} \approx &\; \f{r}{\var_c}\left(\f1{\calq'_+}-\f1{\calq'_-}\right)\approx  \f{r}{2\pi}\var_c \left( \lambda'_- -\lambda'_+\right), \label{estimate}}
+which is a justification for the order-of-magnitude estimate in \q{llquasideg}.
+What is left is to estimate $\lambda_{\pm}'$, which we have accomplished in \app{sec:slowvariation} in both weak- and strong-field regimes.
+Combining  \q{dlambdadE} with \q{estimate}, we deduce the inequality in \q{llquasideg}.
 %From \s{sec:qtznrules}, we know that for sufficiently weak field ($\var_c\ll \Delta$), $\lambda_{\pm}'\approx \pm l^2\delta S'/2$.
@@
 \item If $g\circ\bk=\bk$ and $\hat{g}$ is antiunitary, $\breve{g}(\bk)$ can be transformed into an off-diagonal matrix (diagonal terms are 0) by a gauge transformation.
-For the special case of $\hat{g}$ that is order-2, $\breve{g}$ can be transformed into either $\sigma_z$  or $i\sigma_y$.
+For the special case of $\hat{g}$ that is order-2, $\breve{g}$ can be transformed into either $\sigma_x$  or $i\sigma_y$.
 \end{itemize}
@@
 \end{array}\right)
--\frac{g_\text{eff}\hbar^2\sigma^z}{4ml^2},
+-\frac{g_s\hbar^2\sigma^z}{4m_0l^2},
 \end{split}\label{eq:Rashba-ho}

### 2018-10-01 paper.tex
Updates from ShareLaTeX

@@
 To recapitulate, half the Landau-level quasi-crossings (over the $B$ axis) are destabilized  by tunneling; the robustness of the other half relies on $\mathfrak{c}_2$ symmetry.
-There exists a complementary argument for the existence of Landau-level quasi-crossings in the Klein-tunneling limit $(\tau{=}0)$: the two independent orbits are related by $\mathfrak{c}_2$ symmetry, leading to exactly-degenerate Landau levels.
+There exists a complementary argument for the existence of Landau-level quasi-crossings in the Klein-tunneling limit $(\tau{=}0)$ (cf.
+Fig.
+\ref{fig:Cn-breakdown}(c) upper panel): the two independent orbits are related by $\mathfrak{c}_2$ symmetry, leading to exactly-degenerate Landau levels.
 
@@
 \ref{fig:Cn-breakdown}(b).
-In the adiabatic regime ($\tau{\approx}1$), Landau-level quasidegeneracies occur with a periodicity of one flux quantum; however, in the Klein-tunneling regime ($\tau{\approx}0$), there exists only one dominant orbit shaped like a three-fold-symmetric trefoil knot --  all Landau levels are nondegenerate with spacing determined by the effective mass of the trefoil; this property generalizes to $\mathfrak{c}_N$-symmetric II-Dirac models with odd $N$.
+In the adiabatic regime ($\tau{\approx}1$), Landau-level quasidegeneracies occur with a periodicity of one flux quantum; however, in the Klein-tunneling regime ($\tau{\approx}0$), there exists only one dominant orbit shaped like a three-fold-symmetric trefoil knot (cf.
+Fig.\ref{fig:Cn-breakdown}(c) lower panel) --  all Landau levels are nondegenerate with spacing determined by the effective mass of the trefoil; this property generalizes to $\mathfrak{c}_N$-symmetric II-Dirac models with odd $N$.
 

### 2018-10-02 paper.tex
Updates from ShareLaTeX

@@
-\documentclass[aps, prb, showpacs, twocolumn, notitlepage, superscriptaddress]{revtex4-1}
+\documentclass[aps, prb, showpacs, twocolumn, notitlepage, superscriptaddress, floatfix]{revtex4-1}
 \usepackage{amsmath}
@@
 \usepackage{boldline}
+\usepackage{microtype}
 \usepackage[normalem]{ulem}
@@
 In the opposing regimes $l^2\delta S {{\ll}} 1$  and $l^2\delta S{\gg}1$, we recover the known Onsager-Lifshitz-Roth rules for nondegenerate and degenerate orbits, respectively.
-In the absence of crystallographic symmetry, three real parameters are needed to tune a degeneracy between two Landau levels which have been split by the spin-orbit and Zeeman interactions.
+In the absence of crystallographic symmetry, three real parameters are needed to tune a spin-degeneracy between two Landau levels.
 Here, we identify symmetry classes for which such degeneracies can be tuned by varying a single parameter, which might be the magnitude or orientation of the field, or a bias voltage in tunneling spectroscopy.
-We demonstrate the utility of our rule for the Rashba 2DEG (for which an in-plane Zeeman field can induce a type-II Dirac point), Dresselhaus spin-orbit-coupled systems, and the angular magnetoresistance oscillations of semiconductor bilayer heterostructures.
+We demonstrate the utility of our rule for the Rashba 2DEG -- with an arbitrarily oriented magnetic field, and with the possible addition of the Dresselhaus spin-orbit interaction.
 \end{abstract}
 \date{\today}
+
+%, and the angular magnetoresistance oscillations of semiconductor bilayer heterostructures.
 
@@
 \includegraphics[width=1.0\columnwidth]{RZ.png}
-\caption{(a) Trefoille-shaped cyclotron orbit for the Rashba-Zeeman model at the energy of the Dirac point.
+\caption{ Characterization of the Rashba 2DEG with an in-plane Zeeman field.
+(a) illustrates the trefoille-shaped cyclotron orbit at the energy of the II-Dirac point.
 The orbit is drawn over the  spin-splitting field ($d_x,d_y$) of the degeneracy-lifting Hamiltonian $\delta\var$ [cf.\ \q{eq:RZ-Hamiltonian}].
 The wavefunction along the inner (resp.\ outer) component of the trefoille orbit has its pseudospin aligned parallel (resp.\ anti-parallel) to the spin-splitting field.
-(b) Upper panel: a schematic illustration of Landau levels near the II-Dirac point of the Rashba model (with in-plane Zeeman field, and in the weak- hybridization limit).
-The solid line represents the Onsager-Lifshitz quantization of the trefoille orbit [cf.\ Eq.\ ({trefoillerule})], and the dashed line incorporates the first-order correction [cf.\ Eq.\ (\ref{RZfirstorderE})] due to tunneling.
-Lower panel: oscillation of $\delta E_n$ [cf.
+The upper panel of (b) schematically illustrates  Landau levels near the II-Dirac point (in the weak-hybridization regime).
+The solid line represents the Onsager-Lifshitz quantization of the trefoille \textbf{[please change trefoille everywhere to trefoil]} orbit [cf.\ Eq.\ ({trefoillerule})], and the dashed line incorporates the first-order correction [cf.\ Eq.\ (\ref{RZfirstorderE})] due to tunneling.
+Lower panel of (b): red solid line shows the energetic difference between Landau levels determined by numerical diagonalization and Landau levels obtained by the trefoil quantization rule  [cf.\ Eq.\ ({trefoillerule})]; this solid line may be compared to the perturbative formula $\delta E_n$ [cf.
 Eq.
-(\ref{RZfirstorderE})] for even integer $n$ with respect to magnetic field calculated by Eq.
-(\ref{RZfirstorderE}) (black dashed line) and numerical diagonalization (red solid line).
-$\delta E$ is extracted at the Landau level closest to 0.45eV and the II-Dirac point is located at 0.5eV.
+(\ref{RZfirstorderE})], which is plotted as a black dashed line.
+This comparison is made (at each $1/B$) for the Landau level closest to 0.45eV and with even Landau-level index $n$; the II-Dirac point is located at 0.5eV.
 Parameters for lower panel of (b): $m{=}0.076m_0$, $\alpha{=} 1.5(10^{5}$cm/s$\cdot\hbar$), $Z_\parallel {=}$1meV.
@@
 The decomposition of the effective Hamiltonian [cf.\ Eq.
-(\ref{calHRZ})] into  Pauli matrices ($\calh{=}\sum_j\calh_j\sigma_j$) defines a three-vector $\boldsymbol{\calh}{=}({-}\alpha k_y$,$Z_\parallel{+}\alpha k_x,{-}Z_\perp$).
+(\ref{calHRZ})] into  Pauli matrices ($\calh{=}\sum_j\calh_j\sigma_j$) defines a three-vector $\boldsymbol{\calh}{=}({-}\alpha k_y$,$\alpha k_x{+}Z_\parallel,{-}Z_\perp$).
 $\phi_{\pm}^B$ equals half the solid angle subtended by   ${\mp} \boldsymbol{\calh}(\bk)$ [solid blue line] as $\bk$ is varied along the outer/inner orbit;[Berry] the orientation of the solid angle is indicated by blue dotted lines.
@@
 
- To generalize the above discussion, let us parametrize ${\cal \bar{A}}$ by $d$ independent real numbers  $\{r_1,\ldots,r_{d}\}{:}{=}\br $;  ${\cal \bar{A}}(\br){=}{\pm}I$ defines a set of submanifolds in $\br$-space which we refer to as degeneracy manifolds; in the above example, these manifolds comprise two points on $S^3$.
-The codimension of the degeneracy manifold  is defined as $d$ minus the dimension of said manifold; alternatively stated, the codimension is the number of linearly-independent parameters needed to fine-tune a degeneracy.
+ To generalize the above discussion, let us parametrize ${\cal \bar{A}}$ by $d$ real coordinates  $\{r_1,\ldots,r_{d}\}{:}{=}\br $;  ${\cal \bar{A}}(\br){=}{\pm}I$ defines a set of submanifolds in $\br$-space which we refer to as degeneracy manifolds; in the above example, these manifolds comprise two points on $S^3$.
+The codimension of the degeneracy manifold  is defined as $d$ minus the dimension of said manifold; \textbf{[there are inconsistencies in these definitions, if we impose $d$ to be number of parameters (without imposing linear independence), then $d=4$ for canonical parametrization, and our definition of codimension as d minus dimension of degeneracy manifold gives 4.
+however, if we impose linearly-independent parameters, then we also run into trouble if we allow for symmetric coordinates that are not well-defined at points.]}\red{[First of all, I am not quite sure why the word linear independence is used in the current context.
+I would have used `independent', which means the parameters can be tuned simultaneously.
+One thing that you would probably dislike is that codimension defined by me would be dependent on the parameters $\br$, so it's OK that codimension in canonical parametrizaiton is three while codimension in exponential parametrization is one.
+The precise codimension would be the number of independent parameters needed to find a degeneracy.
+Although codimension depends on the parameters, the codimension found by us is generally universal.
+For example, for rotation symmetry in class 3, we parametrize $\A_{1/2}$ by canonical parametrization $\br_c$.
+There exists a mapping from physical parameters $\br$ to $\br_c$.
+Notice this mapping is not possible for exponential parametrization $\br_e$ since the exponential parametrization of identity is not unique.
+For a nonpathological parameter choice $\br$, the map is well behaved.
+The definition of `well-behaved': any $n\le 3$ dimensional manifold in $\br$ is mapped to $n$ dimensional manifold in $\br_c$.
+With this assumption, codimension of $\A$ in $\br_c$ and $\br$ are actually the same.
+Exponential parametrization is one example of pathological mapping, which maps to sphere to a point (identity).
+However, pathological parameter choice usually does not increase codimension.
+This can be argued in the following way: If the map from $\br$ to $\br_c$ maps a $n\le 3$ dimensional manifold in $\br$ to a $m<n$ dimensional manifold, we remove the corresponding manifold in $\br$.
+After all such manifolds removed, the map become what I defined as `well-behaved' and the codimension should be the same.
+If the manifold removed in $\br$ were mapped to $\A\propto I$, then the codimension decreases, which is the case in exponential parametrization.
+In the presentation, let's be vague and just say codimension is number of independent parameters needed to find a degeneracy.]} alternatively stated, the codimension is the number of linearly-independent parameters needed to fine-tune a degeneracy.
 Here and henceforth, we adopt the shorthand that  \textit{parameters} will always refer to real parameters, and \textit{codimension} always refers to a codimension of a degeneracy manifold.
@@
 
-At energies close to the Dirac point ($E{-}\epsilon_0 {\ll} wm_2(2\epsilon_0/m_1)^{\sma{1/2}}$), there are two concentric orbits which (nearly) touch at both Dirac points, as illustrated in Fig.
-\ref{fig:Cn-breakdown} (a).
+At energies close to the Dirac point ($E{-}\epsilon_0 {\ll} wm_2(2\epsilon_0/m_1)^{\sma{1/2}}$), there are two concentric orbits which (nearly) touch at both Dirac points, as illustrated in Fig.\ \ref{fig:Cn-breakdown}(a).
 For sufficiently weak field, interband tunneling is localized near either II-Dirac point, and occurs with the Landau-Zener probability:
@@
 \multirow{2}{*}{1} & \multirow{10}{*}{$|g\circ \frako_0| = |\frako_0|$} & \multirow{4}{*}{$\forall \bk \in \frako_0$, $g\circ \bk=\bk$} & \multirow{2}{*}{0} & \multirow{2}{*}{0} & \multirow{2}{*}{$\surd$} & $\breve{g}\propto I$ & 3  \\
+\cline{7-8}
  & & & & & & $\breve{g}\not\propto I$ & 1 \\
@@
 \multirow{2}{*}{2} & & & \multirow{2}{*}{0} & \multirow{2}{*}{1} & & $g^2=1$ & 1  \\
+\cline{7-8}
  & & &  &  & & $g^2=-1$ & 3  \\
@@
 \multirow{2}{*}{5} & & & \multirow{2}{*}{1} & \multirow{2}{*}{0} & & $\breve{g} \propto \sigma_z$ & 2  \\
+\cline{7-8}
  & & & &  & & $\breve{g} \not\propto \sigma_z$ & 0  \\
@@
 \multirow{2}{*}{6} & & & \multirow{2}{*}{1} & \multirow{2}{*}{1} & \multirow{2}{*}{$\surd$} & $g^2=1$ & 2  \\
+\cline{7-8}
 & & & & & & $g^2=-1$ & 0  \\
@@
 The second and third column defines how the symmetry acts on the cyclotron orbit.
-The next two columns  inform us if the mapping $\bk{\rightarrow}g{\circ}\bk$ [cf.\ \q{gmapk}]  preserves ($u{=}0$) or inverts ($u{=}0$) the orientation of the orbit, and if $g$ preserves ($s{=}0$) or inverts ($s{=}1$) the arrow of time.
+The next two columns  inform us if the mapping $\bk{\rightarrow}g{\circ}\bk$ [cf.\ \q{gmapk}]  preserves ($u{=}0$) or inverts ($u{=}1$) the orientation of the orbit, and if $g$ preserves ($s{=}0$) or inverts ($s{=}1$) the arrow of time.
 The sixth column indicates whether this  class is potentially a symmetry of quasidegenerate orbits.
@@
 In class 5, $\breve g$ is evaluated at $g$-invariant $\bk$ ($g\circ\bk=\bk$).
-For the reader's convenience, we present some commonly-used matrix representations for exactly degenerate bands in Tab.\ \ref{table:sewing-matrix}.
-The last column presents codimensions of the degeneracy manifold.
+For the reader's convenience, we present some commonly-encountered matrix representations for exactly-degenerate orbits in Tab.\ \ref{table:sewing-matrix}.
+The last column presents codimensions of the degeneracy manifold \textbf{[remind reader what is degeneracy manifold]}.
 For exactly-degenerate orbits in class 2, 4 and 5, $\A$ satisfies $\text{det}(\A){=}1$,[topofermi] with the assumption that spin-orbit coupling can be turned off continuously without changing the degeneracy of the orbit.
@@
 Generalizing our rotational-symmetric case studies in
-Sec.\ \ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown}, we now present the symmetry-constrained codimensions for all ten[topoferm] symmetry classes of orbits.
+Sec.
+\ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown}, we now present the symmetry-constrained codimensions for all ten[topoferm] symmetry classes of orbits.
 Depending on the class, the codimension is either $0,1,2$ or $3$.
@@
 For these five classes (labelled 1, 3, 6, 7 and 10 according to the first column of Tab.\ \ref{table:codimension}), we list their corresponding \textit{symmetry-constrained codimensions} in the right-most column of Tab.\ \ref{table:codimension}; these numbers are derived in  App.\ \ref{app:codimension}.
-To clarify, we define the $g$-constrained codimension as the minimal codimension -- among all degeneracy manifolds -- as enforced by $g$ symmetry.
-To motivate `minimal' in this definition, we have found that two-fold rotational symmetry reduces the codimension of the $\A{=}{+}I$ manifold (to unity), but not the codimension of the $\A{=}{-}I$ manifold [cf.\ \q{proprashba}]; the rotation-constrained codimension is then unity.
-Generally, it is only in class 3 and 4 that different  degeneracy manifolds may have different codimensions.
-Each entry in the right-most column of Tab.\ \ref{table:codimension} equals the $g$-constrained codimension for any $g$ in that class (and possibly satisfying an additional constraint on the representation of $g$, as specified by the second-to-last column).
-
-Of the five classes only three (1, 3 and 6) potentially have symmetry-constrained codimensions that are reduced from three: these three have in common that  $|g\circ\frako_0|{=}|\frako_0|$, and therefore the propagator $\A$ [cf.\ \q{eq:prop}] is self-constrained.
+To clarify, we define the $g$-constrained codimension as a number which is robust to any perturbation of the Hamiltonian that preserves $g$ symmetry and the homotopy class of $\frako_0$.
+Each entry in the right-most column of Tab.\ \ref{table:codimension} equals the $g$-constrained codimension for any $g$ specified by the corresponding row.
+
+%in that class (and possibly satisfying an additional constraint on the representation of $g$, as specified by the second-to-last column).
+
+Of the five classes only classes 1, 3 and 6 potentially have symmetry-constrained codimensions that are reduced from three: classes 1, 3 and 6 have in common that  $|g\circ\frako_0|{=}|\frako_0|$, and therefore the propagator $\A$ [cf.\ \q{eq:prop}] is self-constrained.
 To clarify, a self-constraint relates  the propagator $\A$ [cf.\ \q{eq:prop}] to itself or to its inverse $\A^{-1}$, depending respectively on whether $u{=}0$ or $1$.
@@
 The symmetry-constrained codimension here is unity, as has been modelled in Sec.\ \ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown}.
+Only in class 3 (among 1,3,6) do there exist different  degeneracy manifolds with different codimensions; in such case we define the symmetry-constrained codimension to be the minimal codimension among all manifolds.
+For example, we have found that two-fold rotational symmetry reduces the codimension of the $\A{=}{+}I$ manifold (to unity), but not the codimension of the $\A{=}{-}I$ manifold [cf.\ \q{proprashba}].
+The rotation-constrained codimension is then unity, and hence the entry $1$ in the right-most column for class 3.
 
@@
 \end{tabular*}
-\caption{Matrix representations of reflections (e.g., $\mathfrak{r}_x$) and rotations (e.g.
-$\mathfrak{c}_{2y}$) followed by possible half a lattice translations in $x,~y,~z$ directions (labeled by $\boldsymbol{a,~b,~c}$ respectively).
-This table is relevant for magnetic field in $\pm z$ direction.
-The two-fold exact degeneracy are assumed to be protected by either spatial-time inversion symmetry ($T\mathfrak{i}$), composition of time reversal and nonsymmorphic two fold rotation symmetry ($T\mathfrak{c}_{2z,\boldsymbol{c}/2}$) at $k_z=\pi$ or spin SU(2) (i.e., negligible SOC).
+\caption{Matrix representations of reflections (e.g., $\mathfrak{r}_x$), rotations (e.g.
+$\mathfrak{c}_{2y}$), glide reflections (e.g., $\mathfrak{r}_{x,\ba/2}$) and screw rotations (e.g., $\mathfrak{c}_{2y,\ba/2}$).
+The latter two nonsymmorphic elements involve  half a lattice translation in the $x,~y,$ or $z$ direction (labeled by $\boldsymbol{a,~b,~c}$ respectively).
+The $z$ axis of our Cartesian coordinate system is aligned parallel to the  magnetic field.
+This table is applicable to exactly-degenerate orbits whose degeneracy is protected by either spacetime inversion symmetry ($T\mathfrak{i}$), the composition of time reversal and nonsymmorphic two fold rotation symmetry ($T\mathfrak{c}_{2z,\boldsymbol{c}/2}$) [for orbits confined to the $k_z=\pi$ plane] or spin SU(2) symmetry (i.e., negligible spin-orbit coupling).
 \label{table:sewing-matrix}}
@@
 In the weak-field, adiabatic regime, the antinodes of this pattern occur with period $2\pi/\delta S$ in $l^2$ [cf.\ \s{sec:introducecodimension}]; in the non-adiabatic regime, the antinodes are generically aperiodic [cf.\ \q{lambdasmallB}].
-Such beatings have been observed for semiconductor heterostructures[das,several more].
-Our contribution is the first semiclassical theory  [summarized by the quantization rule of \qq{eq:rule}{berryconn} and the Lifshitz-Kosevich formula of \q{eq:LK}] from which one can calculate the beating pattern; in particular, one may extract the intervals (in $1/B$) between antinodes  for the Rashba 2DEG [by imposing $\delta \lambda{\equiv}\pi$ in \q{eq:Rashba-lambda}] and for the Rashba-Dresselhaus 2DEG [see the next \s{sec:quantosc_quasideg}].
+
+Such beatings have been observed for semiconductor heterostructures[das,several more]; in some experiments,[das] the phase offset $\lambda_a$ [cf.\ \q{eq:LK}] has been measured and fitted phenomenologically to a Laurent series in $B$.[das] It has been appreciated that the leading-order term (${\sim}1/B$) originates from the zero-field splitting of orbits (due to spin-orbit coupling);[das] our contribution is a quantitative theory of the expansion coefficients of this Laurent series -- we have related the subleading term   $({\sim}B^0)$ to  a generalized Zeeman interaction, and higher-order terms to a competition between spin-orbit coupling and the Zeeman interaction [cf.\ \q{eq:Rashba-lambda}].
+As one application, one may extract the intervals (in $1/B$) between antinodes  for the Rashba 2DEG [by imposing $\delta \lambda{\equiv}\pi$ in \q{eq:Rashba-lambda}] and for the Rashba-Dresselhaus 2DEG [see the next \s{sec:quantosc_quasideg}].
+
+%Our contribution is the first semiclassical theory  [summarized by the quantization rule of \qq{eq:rule}{berryconn} and the Lifshitz-Kosevich formula of \q{eq:LK}] from which one can calculate the beating pattern;
 
@@
 \includegraphics[width=1.0\columnwidth]{qo.png}
-\caption{Quantum oscillations in the Rashba-Dresselhaus 2DEG.
+\caption{\textbf{[please redefine alpha and beta such that it has units of cm per s, in whole paper]} Quantum oscillations in the Rashba-Dresselhaus 2DEG.
 (a) Evolution of $\delta\lambda$ with respect to the inverse field for different values of $\beta$.
@@
 For $\beta=3.0(10^{5}$cm/s$\cdot\hbar$), we have plotted -- in the upper panel of (b) -- the Landau levels at three $B$ values, as indicated by the vertical dashed lines in (a).
-The evolution of $\delta \lambda$ for  $\beta=3.0(10^{5}$cm/s$\cdot\hbar$) is given by a cyan-colored line indicated by a black arrow in (a); the three chosen $B$ values correspond approximately to  $\delta\lambda{=}0$, $\delta\lambda{=}\pi/2$ and $\delta\lambda{=}\pi$ respectively.
+The evolution of $\delta \lambda$ for  $\beta=3.0(10^{5}$cm/s$\cdot\hbar$ ) \textbf{[bracket is unconventional notation; try $3.0\times 10^5$ or $3.0\cdot 10^5$]} is given by a cyan-colored line indicated by a black arrow in (a); the three chosen $B$ values correspond approximately to  $\delta\lambda{=}0$, $\delta\lambda{=}\pi/2$ and $\delta\lambda{=}\pi$ respectively.
 Lower panel of (b) illustrates the saw-tooth oscillation of the chemical potential (at fixed electron density) corresponding to the upper panel.
@@
 
-\section{Discussion and outlook}\label{sec:discussion}
-
-\textbf{[work in progress]}
-Summary: We have extended the semiclassical theory to describe  quasidegenerate orbits.
+\section{Summary, discussion and outlook}\label{sec:discussion}
+
+We have extended the semiclassical theory of Landau quantization to describe  quasidegenerate cyclotron orbits, i.e., orbits which are split in $\bk$-space with a differential area ($\delta S$) that is much less than their average area.
+The quantization rule for two quasidegenerate orbits is summarized in \qq{eq:rule}{berryconn}, and may be applied to spin-degenerate orbits which are split by spin-orbit coupling or by breaking of a crystalline point-group symmetry.
+The former type of splitting is exemplified by  our case study of the Rashba 2DEG (with arbitrarily-oriented field and addition of Dresselhaus spin-orbit coupling).
+
+The subleading phase corrections ($\lambda_1,\lambda_2$) in our quantization rule  [\q{eq:rule}] encode the dynamical correction due to the splitting of  orbits, as well as a generalized two-band Zeeman interaction.
+Where $\lambda_1{=}\lambda_2$ mod $2\pi$, there exist a number (of order one) paired Landau levels which are either exactly spin-degenerate, or nearly spin-degenerate in the sense of \qq{llquasideg}{llquasidegB}.
+\textbf{[bonus:schematic picture to illustrate of order one paired LLs near degeneracy of lambda (might introduce picture earlier, in section where we introduce quasidegeneracy)]} Such paired Landau levels have been referred to as \textit{quasidegenerate}.
+
+For each of the five symmetry classes of near-degenerate orbits \textbf{[please replace quasidegenerate orbit with near-degenerate orbit, however keep quasidegenerate LL.
+One reason: quasidegenerate LL includes exactly degenerate; near-degenerate orbit has nonzero splitting]},  we have determined the number of tunable real parameters needed to attain a Landau-level quasidegeneracy;  these numbers may be viewed as symmetry-dependent  measures of Landau-level repulsion.
+We have referred to these numbers as \textit{symmetry-constrained codimensions}.
+Depending on the symmetry class and representation, the codimension ranges from $0,1,2$ to $3$, as summarized in the right-most column of Tab.\ \ref{table:codimension}.
+
+If the codimension is unity, it is possible to tune the magnitude of the field to attain Landau-level quasidegeneracies; the implications for this tunability -- in the Schubnikov-de Haas effect -- are discussed in \s{sec:quantosc_quasideg}.
+If the codimension is two, an additional experimentally tunable parameter is needed: e.g., the orientation of the field[magic angle], or the bias voltage in tunneling spectroscopy[cite stm papers].
+
+With the inclusion of nonsymmorphic space-group symmetries, it is not uncommon to find energy bands which are (nearly) four-fold degenerate.[michel and zak,hourglass,Barry] This motivates a  generalization of our rule -- for any number of near-degenerate orbits -- that is presented in  \app{app:quantizationruleproof}.
+The symmetry-constrained codimensions in the more general case is left to future investigations.
+
+Our quantization rule [\qq{eq:rule}{berryconn}] may be applied, as a special case, to \textit{exactly-degenerate orbits} -- spin-differentiated orbits which overlap exactly in $\bk$-space.
+There are ten possible symmetry classes for exactly-degenerate orbits -- five more than for near-degenerate orbits.
+For each of this ten, we have also determined their symmetry-constrained codimensions in Tab.\ \ref{table:codimension}.
+We remark on one further distinction from near-degenerate orbits --  the magnitude of the field becomes less useful as a tuning parameter, however the field orientation and bias voltage remain feasible options.
+
+\textbf{[confusing issue to settle: five vs ten becomes confusing if we now say that our topofermiology table applies to all ten classes of quasidegenerate orbits.
+We may have to modify.][generalization to wilson loop; explains movable crossings in recent works]}
+\red{[
+Let's say only five rows of both tables are useful for quasidegenerate orbits.
+This is more accurate since you wrote explicitly the symmetry constraints in terms of sewing matrix in topofermi.
+These symmetry constraints for the five unticked classes in the topofermi table are not applicable to quasidegenerate orbits.
+We should just say $\det \A=1$ for the three unticked self-constrained classes for quasidegenerate orbits.
+This conclusion comes from the fact that we defined $\delta \epsilon$ to be traceless, rather than symmetry constraints expressed with sewing matrix in the topofermi table.
+]}
+
+%.
 A nontrivial implication of our theory is the determination of symmetry constrained codimension, summarized in tab I.
@@
 The first is not applicable to exactly-degenerate orbits.
-For spin-split bands, $\lambda$ depends strongly on the $B$ field for quasidegenerate orbits; for degenerate orbits, the $B$-dependence of $\lambda$ is relatively weaker, i.e., of higher power in the small parameter $B$ [Roth, Niu, Fuchs].
+%For spin-split bands, $\lambda$ depends strongly on the $B$ field for quasidegenerate orbits; for degenerate orbits, the $B$-dependence of $\lambda$ is relatively weaker, i.e., of higher power in the small parameter $B$ [Roth, Niu, Fuchs].
 A more useful tuning parameter in the latter case would be the bias voltage in tunneling spectroscopy experiments.
 
-Application to $D>4$.
+%Application to $D>4$.
 Not uncommon to find spin-degenerate bands (in centrosymmetric solids) which are quasi-four-fold degenerate.
@@
 
-\red{[Maybe talk about codimension for $D>2$. However, I have no idea what that may be. I don't even find a good parametrization of SU(3).]}
-
-Phase offset of quantum oscillations. Is it quantized for quasidegenerate orbits? \red{[$\det \A$=1 means two opposite offsets, not quantized offset.]}
-
-Wilson loop.
+%\red{[Maybe talk about codimension for $D>2$. However, I have no idea what that may be. I don't even find a good parametrization of SU(3).]}
 
@@
 \end{equation}
-$k_x^\nu$ is a function of $k_y$ satisfying $\epsilon(k_x^\nu,k_y)=0$ and quantities with a superscript $\nu$ should be evaluated at $\bk = (k_x^\nu, k_y)$.
+where $k_x^\nu$ is a function of $k_y$ satisfying $\epsilon(k_x^\nu,k_y)=0$ and quantities with a superscript $\nu$ should be evaluated at $\bk = (k_x^\nu, k_y)$.
 Generally, $\epsilon(k_x^\nu,k_y)=0$ have several solutions of $k_x$ for a given $k_y$ and these solutions are indexed by $\nu$.
-$g_\bk$ above is expressed in Landau gauge, where $k_x=k_x^0$ is a constant of motion.
+$g_{\bk}$ above is expressed in Landau gauge, where $k_x=k_x^0$ is a constant of motion.
 Quantization rule for cyclotron motion may be obtained by solving boundary condition equations of $f_{\bk} = \sum_\nu g_{\bk}^\nu$ at turning points.
@@
 Eq. ({\ref{eq:prop}}) can be obtained by solving boundary conditions at turning points.
+
+Besides the effective Hamiltonian approach described above, semiclassical wave packet theory has been developed in coupled bands[Niucoupled].
+It is possible that quantization rule expressed in \qq{eq:rule}{berryconn} can be derived by a `requantization' [NiuRMP] of the wave packet theory.
 
@@
 \begin{equation}
-2b_1\sqrt{1-b_1^{2}}\alpha_{2} & =(2b_1^{2}-1)\beta_{2}.
+2b_1\sqrt{1-b_1^{2}}\alpha_{2} =(2b_1^{2}-1)\beta_{2}.
 \end{equation}

### 2018-10-02 paper.tex
Updates from ShareLaTeX

@@
-\documentclass[aps, prb, showpacs, twocolumn, notitlepage, superscriptaddress, floatfix]{revtex4-1}
+\documentclass[aps, prb, showpacs, twocolumn, notitlepage, superscriptaddress]{revtex4-1}
 \usepackage{amsmath}
@@
 \usepackage{boldline}
-\usepackage{microtype}
 \usepackage[normalem]{ulem}
@@
 
+\renewcommand{\topfraction}{.85}
+\renewcommand{\bottomfraction}{.7}
+\renewcommand{\textfraction}{.15}
+\renewcommand{\floatpagefraction}{.66}
+\renewcommand{\dbltopfraction}{.66}
+\renewcommand{\dblfloatpagefraction}{.66}
+\setcounter{topnumber}{9}
+\setcounter{bottomnumber}{9}
+\setcounter{totalnumber}{20}
+\setcounter{dbltopnumber}{9}
+
 \begin{document}
 
-\title{Landau quantization of nearly degenerate bands}
+\title{Landau quantization of nearly-degenerate bands}
 
@@
 \begin{abstract}
-\textbf{[abstract needs revamp]}
- In the semiclassical theory of Landau levels, a Bloch electron is driven by a magnetic field  along constant-energy band contours (in quasimomentum space) known as orbits.
-We introduce a quantization rule for Landau levels of nearly degenerate orbits which are split by spin-orbit coupling.
-The average area $S$ of two spin-orbit-split orbits is assumed much larger than the difference in areas ($\delta S$), and also much larger than the inverse square of the magnetic length ($\lmt$).
-By treating both $\delta S/S$ and $1/l^2S$ as small parameters with finite ratio $l^2\delta S$, our perspective diverges from and generalizes previous semiclassical theories.
-$l^2\delta S$ is the dimensionless measure of the field-induced hybridization between spin-orbit-split orbits; we allow for $l^2\delta S$ to be comparable with the Zeeman coupling.
-In the opposing regimes $l^2\delta S {{\ll}} 1$  and $l^2\delta S{\gg}1$, we recover the known Onsager-Lifshitz-Roth rules for nondegenerate and degenerate orbits, respectively.
-In the absence of crystallographic symmetry, three real parameters are needed to tune a spin-degeneracy between two Landau levels.
-Here, we identify symmetry classes for which such degeneracies can be tuned by varying a single parameter, which might be the magnitude or orientation of the field, or a bias voltage in tunneling spectroscopy.
-We demonstrate the utility of our rule for the Rashba 2DEG -- with an arbitrarily oriented magnetic field, and with the possible addition of the Dresselhaus spin-orbit interaction.
+In the semiclassical theory of Landau levels, a Bloch electron is driven by a magnetic field  along constant-energy band contours  known as cyclotron orbits.
+We introduce a quantization rule for Landau levels of nearly-degenerate orbits whose differential area ($\delta S$) in $\bk$-space is much smaller than their average area $S$.
+The splitting of two nearly-degenerate orbits commonly originate from spin-orbit coupling, or by the breaking of a crystalline point-group symmetry.
+By treating both $\delta S/S$ and $1/l^2S$ ($l$ being the magnetic length) as small parameters with finite ratio $l^2\delta S$, our perspective diverges from and generalizes previous semiclassical theories.
+$1/l^2\delta S$ measures the hybridization of split orbits due to the Zeeman interaction; in the opposing regimes $l^2\delta S {{\ll}} 1$  and $l^2\delta S{\gg}1$, we recover the known Onsager-Lifshitz-Roth rules for nondegenerate and exactly-degenerate orbits, respectively.
+In the absence of crystalline point-group symmetries, three tunable real parameters are needed to attain a spin-degeneracy between two Landau levels; we have exhaustively identified all symmetry classes of orbits for which this number is reduced from three.
+In particular, only one parameter is needed for rotational-symmetric orbits; this parameter may be the magnitude \textit{or} orientation of the field, or the bias voltage in tunneling spectroscopy.
+An implication of single-parameter tunability is a smooth crossover between period-doubled and -undoubled quantum oscillations in the Schubnikov-de Haas effect.
+We demonstrate the utility of our quantization rule, as well as the tunability of Landau-level degeneracies, for the Rashba two-dimensional electron gas -- subject to an arbitrarily oriented magnetic field, and possibly augmented by the Dresselhaus spin-orbit interaction.
 \end{abstract}
@@
 In the absence of magnetic breakdown, semiclassical quantization rules are well-known for Landau levels of  both nondegenerate [Onsager, Lifshitz] and degenerate [Roth, Mikitik, Topoferm, 100page] energy bands.
-Our work generalizes these rules to nearly-degenerate bands, whose orbits are split in $\bk$-space with a differential area  $\delta S$ that is much less than the average area $S$ of the orbits; we shall refer to $\delta S/S{\ll}1$ as the \textit{quasidegeneracy} condition.
-Quasidegenerate orbits commonly originate from spin-orbit-splitting of energy bands in noncentrosymmetric solids.
-We provide an illustrative model of a two dimensional electron gas (2DEG) with Rashba spin-orbit coupling:
-\begin{equation}
-H_R=\frac{{\hbar^2} k^2}{2m}+\alpha  (k_{x}\sigma_{y}-k_{y}\sigma_{x}).\label{eq:Rashba-Hamiltonian}
+Our work generalizes these rules to nearly-degenerate bands, whose orbits are split in $\bk$-space with a differential area  $\delta S$ that is much less than the average area $S$ of the orbits; we shall refer to $\delta S/S{\ll}1$ as the \textit{near-degeneracy} condition.
+Nearly-degenerate orbits commonly originate from the spin-orbit-splitting of energy bands, as exemplified by a two dimensional electron gas (2DEG) with Rashba spin-orbit coupling:
+\begin{equation}
+H_R=\frac{{\hbar^2} k^2}{2m}+\hbar\alpha  (k_{x}\sigma_{y}-k_{y}\sigma_{x}).\label{eq:Rashba-Hamiltonian}
 \end{equation}
@@
 \ref{fig:orbits}(a)] is much smaller than their average area:\footnote{The expressions for $\delta S$ and $S$ in \q{deltaSvsS} are asymptotically valid for $E{\gg}m\alpha^2$.}
-\e{\delta S = 2\pi k_E \f{2\alpha m}{\hbar^2} \ll S =\pi k_E^2; \;\; k_{E}:=\f{\sqrt{2m E}}{\hbar} .\label{deltaSvsS}}
+\e{\delta S = 4\pi m \alpha k_E/\hbar\ll S =\pi k_E^2; \;\; k_{E}:=\f{\sqrt{2m E}}{\hbar} .\label{deltaSvsS}}
 $S$ is equivalently the area of the circular, constant-energy contour in the absence of spin-orbit coupling ($\alpha{=}0$).
@@
 This condition is assumed by previous semiclassical theories.
-[Kohn, Blount, Roth, Wannier, Fredkin, Niu, Mikitik, topoferm, 100page] As a generalization, we will treat $\delta S/S$ as an extra small parameters throughout this work with finite ratio $l^2\delta S$.
-
-$(l^2\delta S)^{-1}$ is a measure of the field-induced hybridization of the quasidegenerate orbits, and shall be called the hybridization parameter. 
+[Kohn, Blount, Roth, Wannier, Fredkin, Niu, Mikitik, topoferm, 100page] As a generalization, we will treat $\delta S/S$ as an additional small parameter, while keeping the ratio $l^2\delta S$ finite.
+
+$(l^2\delta S)^{-1}$ is a measure of the field-induced hybridization of the nearly-degenerate orbits, and shall be called the hybridization parameter. 
 In the regime that $l^2\delta S$ is much greater than the Zeeman interaction, we expect that the Onsager-Lifshitz quantization rules apply independently to the two concentric (but decoupled) orbits.
@@
 In the  semiclassical description,  we are interested in  field-induced dynamics within a low-energy degenerate band of $\hat{H}_0$ with  dispersion $\var(\bk)$, e.g., $\var(\bk){=}\hbar^2 k^2/2m{+}\order(k^4)$ in the Rashba model.
-Landau quantization is well-known to derive from the Peierls substitution $\var(\bk){\rightarrow}\var(\bK)$, [Peierls] with the kinematic quasimomentum operator   $\boldsymbol{K}{:}{=}\boldsymbol{k}{+}(e/\hbar) \boldsymbol{A}(i\nabla_{\boldsymbol{k}})$ and $\boldsymbol{A}(\br)$ being the electromagnetic vector potential.
+Landau quantization is well-known to derive from the Peierls substitution $\var(\bk){\rightarrow}\var(\bK)$\cite{peierls_substitution}, with the kinematic quasimomentum operator   $\boldsymbol{K}{:}{=}\boldsymbol{k}{+}(e/\hbar) \boldsymbol{A}(i\nabla_{\boldsymbol{k}})$ and $\boldsymbol{A}(\br)$ being the electromagnetic vector potential.
 Assuming that the field is aligned in the ${-}z$ direction, $[K_x,K_y]{=}i\lmt$.
 The semiclassical solution corresponds to  cyclotron revolutions of an electron around a constant-energy contour of $\var(\bk)$ [see Fig.
-\ref{fig:orbits}(b)]]; this contour, equipped with an orientation given by the equation of motion ($ \hbar dk_{\alpha}/dt {=} \lmt \epsilon_{\ab}\partial \var/\partial k_{\beta} $, with $\epsilon_{xy}{=}{-}\epsilon_{yx}{=}1$), shall be referred as the zeroth-order orbit $\frako_0$.
+\ref{fig:orbits}(b)]; this contour, equipped with an orientation given by the equation of motion ($ \hbar dk_{\alpha}/dt {=} \lmt \epsilon_{\ab}\partial \var/\partial k_{\beta} $, with $\epsilon_{xy}{=}{-}\epsilon_{yx}{=}1$), shall be referred as the zeroth-order orbit $\frako_0$.
 In this work, we focus only on closed orbits which do not wrap
@@
 
-The quantization rule for Landau levels reflects the single-valuedness of the semiclassical (WKB) wavefunction over $\frako_0$,[Berry, Mount] i.e.,  the phase accumulated by an electron (over one cyclotron period $T_c$) is an integer multiple of $2\pi$: $(l^2S(E){+}\gamma)/2\pi{\in}\Z$.
-The leading-order phase   is the classical action $l^2S{:}{=}{-}l^2\int_{0}^{T_c} k_x \dot{k}_y dt$  corresponding to $(K_x,K_y)$;[mount] $S$ has a dual interpretation as the signed area (in $\bk$-space) enclosed by $\frako_0$, as illustrated in Fig.
+The quantization rule for Landau levels reflects the single-valuedness of the semiclassical (WKB) wavefunction over $\frako_0$,\textbf{[Berry, Mount]} i.e.,  the phase accumulated by an electron (over one cyclotron period $T_c$) is an integer multiple of $2\pi$: $(l^2S(E){+}\gamma)/2\pi{\in}\Z$.
+The leading-order phase   is the classical action $l^2S{:}{=}{-}l^2\int_{0}^{T_c} k_x \dot{k}_y dt$  corresponding to $(K_x,K_y)$;\textbf{[Mount]} $S$ has a dual interpretation as the signed area (in $\bk$-space) enclosed by $\frako_0$, as illustrated in Fig.
 \ref{fig:orbits}(b).
-$\gamma$ is a subleading Maslov correction [caustic] that generally equals $\pi$ times the rotation number $r$ of $\frako_0$ (i.e., the number of rotations made by the tangent vector over one cycle);[100page] for orbits that are deformable to a circle,  $r{=}{\pm} 1$.
+$\gamma$ is a subleading Maslov correction \textbf{[caustic]} that generally equals $\pi$ times the rotation number $r$ of $\frako_0$ (i.e., the number of rotations made by the tangent vector over one cycle)\cite{100p}; for orbits that are deformable to a circle,  $r{=}{\pm} 1$.
 In the zeroth-order  solution, all Landau levels are spin-degenerate with a level spacing
@@
 This implies that the spin-degeneracy of Landau levels is split by approximately  $\var_c|\lambda_1{-}\lambda_2|/2\pi$.
-The phase offsets $\lambda_a$ can be viewed as Floquet quasienergies of a time-periodic, perturbative Hamiltonian ($\calh$) that governs the dynamics of the spinor wavefunction.
+The phase offsets $\lambda_a$ can be viewed as Floquet quasienergies\cite{shirley_solution_1965} of a time-periodic, perturbative Hamiltonian ($\calh$) that governs the dynamics of the spinor wavefunction.
 $\lambda_a$ is obtained  from  eigenvalues $\{e^{i\lambda_a}\}_{a=1}^2$ of a time-evolution propagator -- the time-ordered exponential
@@
 
-The remaining terms in \q{eq:H1} describe a generalized Zeeman interaction $B\calm$ which is the first-order-in-$B$ correction to the Peierls-Onsager Hamiltonian $\var(\bK)$.[kohn,blount,roth] Included in this interaction is the Zeeman coupling to the spin ($g_s\mu_Bs_z/\hbar$) and orbital ($M_z$) magnetic moment of the quasidegenerate band; the latter is expressible in terms of matrix elements of the velocity operator $\boldsymbol{\Pi}_{mn}=i\langle\psi_m|[\hat{H}, \hat{\boldsymbol{r}}]|\psi_n\rangle/\hbar$ between Bloch wave functions $\psi_{n\bk}$:
+The remaining terms in \q{eq:H1} describe a generalized Zeeman interaction $B\calm$ which is the first-order-in-$B$ correction to the Peierls-Onsager Hamiltonian $\var(\bK)$\cite{rotheffham}.\textbf{[kohn,blount]} Included in this interaction is the Zeeman coupling to the spin ($g_s\mu_Bs_z/\hbar$) and orbital ($M_z$) magnetic moment\cite{thonhauser_orbital_2005} of the nearly-degenerate band; the latter is expressible in terms of matrix elements of the velocity operator $\boldsymbol{\Pi}_{mn}=i\langle\psi_m|[\hat{H}, \hat{\boldsymbol{r}}]|\psi_n\rangle/\hbar$ between Bloch wave functions $\psi_{n\bk}$:
 \e{
@@
 Here, the summation in $l$ does not include the two quasidegenerate bands.
-There is finally a geometric contribution to the Zeeman interaction, which involves the two-by-two non-Abelian Berry connection  as well as the  zeroth-order band velocity:
+There is finally a geometric contribution to the Zeeman interaction, which involves the two-by-two non-Abelian Berry connection\cite{berry_quantal_1984} as well as the  zeroth-order band velocity:
 \e{\mathfrak{X}_{\beta,mn}{=}i\braket{u_m}{\partial u_n/\partial k_{\beta}},  \;\;v_{\alpha}:= \f{1}{\hbar}\p{\var}{k_{\alpha}},\label{berryconn}}
-with $\{u_n\}_{n=1}^2$ the periodic component of Bloch functions in the quasidegenerate band. 
+with $\{u_n\}_{n=1}^2$ the periodic component of Bloch functions. 
 %which provides a geometric characterization of band wavefunctions along $\frako_0$.\\
@@
 
-\noi{i} If $|\var_+{-}\var_-|$ is everywhere (along $\frako_0$) much greater than $B|\calm_{+-}|$, then an electron would undergo adiabatic (band-conserving) dynamics[nenciu] along two independent, nondegenerate orbits.
-Such an adiabatic regime always exists as $B{\rightarrow} 0$ for quasidegenerate orbits that do not intersect, e.g, at a type-II Dirac point, which is the subject of the case studies in \s{sec:inplanezeeman} and \s{sec:rotsymmbreakdown}.
+\noi{i} If $|\var_+{-}\var_-|$ is everywhere (along $\frako_0$) much greater than $B|\calm_{+-}|$, then an electron would undergo adiabatic (band-conserving) dynamics \textbf{[Nenciu]} along two independent, nondegenerate orbits.
+Such an adiabatic regime always exists as $B{\rightarrow} 0$ for nearly-degenerate orbits that do not intersect, e.g, at a type-II Dirac point, which is the subject of the case studies in \s{sec:inplanezeeman} and \s{sec:rotsymmbreakdown}.
 By  neglecting  $B\calm_{+-}$ in favor of intraband elements,  $\cala$ reduces to a diagonal matrix with  diagonal entries ($e^{i\lambda_{\pm}}$) given by:
 \e{\lambda_{\sma{\pm}} = -\int_0^{T_c}\calh_{\sma{\pm\pm}}\f{dt}{\hbar}=\pm \f{1}{2}l^2\delta S - B\int_0^{T_c}\calm_{\sma{\pm\pm}}\f{dt}{\hbar}.  \label{phaseindependentorbit}} 
-\q{eq:rule}, combined with \q{phaseindependentorbit}, may be identified as the Onsager-Lifshitz rule[onsager,lifshitz] for  two independent, nondegenerate orbits of areas $S{\pm}\delta S$, and with subleading phase corrections that were first identified by Roth[rothII].\footnote{We remark that \q{phaseindependentorbit} neglects the contribution by band $-$ to the orbital moment of band $+$: $\delta M_z=il^{-2}\epsilon_{\ab}(\delta \var_+-\delta \var_-)\mathfrak{X}^{\alpha}_{+-}\mathfrak{X}^{\beta}_{-+}$.
+\q{eq:rule}, combined with \q{phaseindependentorbit}, may be identified as the Onsager-Lifshitz rule \textbf{[Onsager,Lifshitz]} for two independent, nondegenerate orbits of areas $S{\pm}\delta S$, and with subleading phase corrections that were first identified by Roth\cite{rothmag}.\footnote{We remark that \q{phaseindependentorbit} neglects the contribution by band $-$ to the orbital moment of band $+$: $\delta M_z=il^{-2}\epsilon_{\ab}(\delta \var_+-\delta \var_-)\mathfrak{X}^{\alpha}_{+-}\mathfrak{X}^{\beta}_{-+}$.
 $\mathfrak{X}^{\alpha}_{+-}$, being an off-diagonal matrix element of the position operator, is generically of order a lattice constant $a$.
-We then estimate $\int_0^{T_c} B\delta M_z dt/\hbar=O(a^2 \delta S )$, which is negligible compared to $l^2\delta S/2$.
-Note also that the single-band orbital moment simply vanishes in some symmetry classes of orbits.[100page] } The perturbative inclusion of $B\calm_{\sma{+-}}$ results in  a correction to $\lambda_{\pm}$ [cf.\ \q{phaseindependentorbit}] that is expressible as a power series in $B$, with a leading term proportional to $B$; this will be confirmed in a subsequent case study [cf.\ \q{lambdasmallB}] and applied to understand beatings in quantum-oscillatory phenomena in  \s{sec:qo}.
-\\
+We then estimate $\int_0^{T_c} B\delta M_z dt/\hbar=O(a^2 \delta S)$, which is negligible compared to $l^2\delta S/2$.
+Note also that the single-band orbital moment simply vanishes in some symmetry classes of orbits\cite{100p}.} The perturbative inclusion of $B\calm_{\sma{+-}}$ results in a correction to $\lambda_{\pm}$ [cf.\ \q{phaseindependentorbit}] that is expressible as a power series in $B$, with a leading term proportional to $1/B$; this will be confirmed in a subsequent case study [cf.\ \q{lambdasmallB}] and applied to understand beatings in quantum-oscillatory phenomena in \s{sec:qo}.
 
@@
 \noi{ii} Let us consider the opposite regime where the Zeeman splitting due to $B\calm$ is much greater than $(\delta \var_+{-}\delta\var_-)$.
-\qq{eq:rule}{berryconn}, with $\calh{\approx}B\calm$, may then be identified with the quantization rule (formulated previously by us [topoferm,100page]) for degenerate orbits of any symmetry.\footnote{An equivalent but less general formulation was proposed earlier in [RothII] and [Mikitik,Sharlai] for centrosymmetric solids with time-reversal symmetry (at zero field).
+\qq{eq:rule}{berryconn}, with $\calh{\approx}B\calm$, may then be identified with the quantization rule (formulated previously by us\cite{topoferm,100p}) for degenerate orbits of any symmetry.\footnote{An equivalent but less general formulation was proposed earlier in Ref.
+\onlinecite{rothmag} and \textbf{[Mikitik,Sharlai]} for centrosymmetric solids with time-reversal symmetry (at zero field).
 For comparison, it should be emphasized that \qq{eq:rule}{berryconn} applies to solids of any symmetry, including magnetically-ordered solids.}
@@
 
-We will first apply our rule to the Landau levels of the Rashba model [cf.\ \q{eq:Rashba-Hamiltonian}], for which analytic expressions exist for verification; shortly after we will demonstrate the utility of our quantization rule for the 2DEG with both Rashba and Dresselhaus spin-orbit interactions, for which there exists no known analytic closed-form solution.
+We will first apply our rule to the Landau levels of the Rashba model [cf.\ \q{eq:Rashba-Hamiltonian}], for which analytic expressions exist for verification\cite{bychkov_oscillatory_1984}; shortly after we will demonstrate the utility of our quantization rule for the 2DEG with both Rashba and Dresselhaus spin-orbit interactions, for which there exists no known analytic closed-form solution.
 
@@
 In the energy basis of the Rashba Hamiltonian $H_R$ [cf.\ \q{eq:Rashba-Hamiltonian}],
-\e{\calh(\bk)=-\alpha k\tau_z{+}\f{g_s}{2}\mu_{\sma{B}}B\tau_x {-} \f{eB\hbar}{2m} (\tau_x-I) \epsilon_{\alpha\beta} k_{\alpha}\nabla_{\beta}\theta,\label{rashbaeffham}}
+\e{\calh(\bk)=-\hbar\alpha k\tau_z{+}\f{g_s}{2}\mu_{\sma{B}}B\tau_x {-} \f{eB\hbar}{2m} (\tau_x-I) \epsilon_{\alpha\beta} k_{\alpha}\nabla_{\beta}\theta,\label{rashbaeffham}}
 where $\tau_i$ are a new set of Pauli matrices with $\tau_z{=}{+} 1$ and ${-}1$ corresponding to the outer and inner orbits, respectively.
-$e^{i\theta_{\bk}}{=}(ik_x{-}k_y)/k$ is the angle of the in-plane spin-splitting field $({-}\alpha k_y,\alpha k_x,0)$ of $H_R$, which winds once over $\frako_0$; the spin of our basis vectors likewise winds, in parallel (or anti-parallel) alignment with this field (see Fig.
+$e^{i\theta_{\bk}}{=}(ik_x{-}k_y)/k$ is the angle of the in-plane spin-splitting field $(-\hbar\alpha k_y,\hbar\alpha k_x,0)$ of $H_R$, which winds once over $\frako_0$; the spin of our basis vectors likewise winds, in parallel (or anti-parallel) alignment with this field (see Fig.
 (\ref{fig:orbits})(b)).
@@
 the remaining terms may be interpreted as B-induced deformations of the bands.
-It is well-known that the Zeeman term tends to polarize spin in the direction ($\vec{z}$) of $\bB$; remarkably, the non-abelian Berry term   also has a polarizing effect, but with opposite sign.
+It is well-known that the Zeeman term tends to polarize spin in the direction of $\bB$; remarkably, the non-abelian Berry term  also has a polarizing effect, but with opposite sign.
 These two effects completely cancel for free electrons ($m{=}m_0$, with $m_0$ being free electron mass.), but not generically in band systems.
@@
 \e{\lambda_{\pm}= \pm \f{l^2\delta S}{2} +\pi \pm \f{\pi^2}{4}\f{(g_sm/m_0-2)^2}{l^2\delta S} + O(B^2). \label{lambdasmallB}}
-\q{eq:rule}, combined with the first two terms on the right-hand-side of \q{lambdasmallB}, may alternatively be derived from 
-the standard Onsager-Lifshitz rules for two independent orbits, with a common $\pi$ Berry-phase correction for each orbit:\footnote{The intra-band Zeeman and orbital-moment couplings vanish due spacetime-inversion symmetry.[topoferm]} $l^2(S{\pm}\delta S)/2\pi {\in}\Z$.
+\q{eq:rule}, combined with the first two terms on the right-hand-side of \q{lambdasmallB}, may alternatively be derived from  the standard Onsager-Lifshitz rules for two independent orbits, with a common $\pi$ Berry-phase correction for each orbit:\footnote{The intra-band Zeeman and orbital-moment couplings vanish due spacetime-inversion symmetry\cite{topoferm}.} $l^2(S{\pm}\delta S)/2\pi {\in}\Z$.
 Higher-order terms in \q{lambdasmallB} reflect the field-induced hybridization of the spin-orbit-split orbits.
 
-In the strong hybridization regime: $l^2\delta S {\ll}\pi(g_sm/m_0{-}2)$, $\lambda_{\pm}{\approx}{\pm}\pi g_sm/2m_0$ mod $2\pi$, which corresponds to the Zeeman splitting of Landau levels by $g_{s}\mu_BB$, in the \textit{absence} of the spin-orbit interaction.
+In the strong hybridization regime where $l^2\delta S {\ll}\pi(g_sm/m_0{-}2)$, $\lambda_{\pm}{\approx}{\pm}\pi g_sm/2m_0$ mod $2\pi$, which corresponds to the Zeeman splitting of Landau levels by $g_{s}\mu_BB$, in the \textit{absence} of the spin-orbit interaction.
 
@@
 Our quantization rule [\q{eq:rule} with \q{eq:Rashba-lambda}] may be compared with the  exact Landau-level spectrum of the Peierls-substituted Hamiltonian $H_R(\bK)$.
-The exact levels are given implicitly by
+The exact levels are given implicitly by\cite{bychkov_oscillatory_1984}
 \e{
@@
 with the functional forms of $\delta S(E)$ and $S(E)$ provided in \q{deltaSvsS};  $n_{+}{\ge} 1$ and $n_-{\ge} 0$ here are integer-valued labels for two distinct sets of levels.
-In the quasidegenerate regime ($E{\gg}m\alpha^2$), terms involving $\delta S/S$ may be neglected and \q{eq:Rashba-exact} reduces to our quantization rule with $\lambda_{\pm}$ given by \q{eq:Rashba-lambda}.
+In the nearly-degenerate regime ($E{\gg}m\alpha^2$), terms involving $\delta S/S$ may be neglected and \q{eq:Rashba-exact} reduces to our quantization rule with $\lambda_{\pm}$ given by \q{eq:Rashba-lambda}.
 
@@
 \begin{equation}
- H_{RD}(\bk)=\frac{{\hbar^2}k^2}{2m}+\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+\beta(k_{x}\sigma_{x}-k_{y}\sigma_{y}).\label{hamRD}
+ H_{RD}(\bk)=\frac{{\hbar^2}k^2}{2m}+\hbar\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+\hbar\beta(k_{x}\sigma_{x}-k_{y}\sigma_{y}).\label{hamRD}
 \end{equation}
@@
 (\ref{eq:rule}) (black lines) and numerical diagonalization of the Peierls-Onsager Hamiltonian  $H_{RD}(\bK)$ (red dots).
-Parameters for (b): $\alpha=7.5$($10^{5}$cm/s$\cdot\hbar$), $m=0.076m_0$, $\beta=3~(6)$($10^{5}$cm/s$\cdot\hbar$) for left (right) panels.
+Parameters for (b): $\alpha=7.5\times10^{5}$cm/s, $m=0.076m_0$, $\beta=3.0(6.0)\times 10^{5}$cm/s for left (right) panels.
 (c) For various spin-orbit parameters $(\alpha,\beta)$ of the Rashba-Dresselhaus model and various field strength (satisfying $l^2S(E)\gg 1$), we plot  $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that lies closest to energy $E=0.4eV$, where $\epsilon_\text{rule}$ is determined by Eq.
@@
 Parameters for (c-d): $m=0.076m_0$.
-Units: $\alpha$($1.5\times 10^{5}$cm/s$\cdot\hbar$), $\beta$($1.5\times 10^{5}$cm/s$\cdot\hbar$), $l^2 S$($10^2$).\label{fig:RD}}
+Units: $\alpha$($10^{5}$cm/s), $\beta$($10^{5}$cm/s), $l^2 S$($10^2$).\label{fig:RD}}
 \end{figure}
@@
 
-Our next case study involves orbits that (nearly) touch at a type-II Dirac point -- an asymmetric variant of the conventional Dirac point (as will be introduced below).
-Quantum tunneling localized to a type-II Dirac point  (in short, a II-Dirac point) is known to be mathematically equivalent to  Landau-Zener breakdown, with the electric force replaced by the Lorentz force.[Blount, Obrien, AALG] Here, we will demonstrate how  Landau-Zener dynamics emerge from our quantization rule [\qq{eq:rule}{eq:H1}], and explore (for the first time) how these dynamics are modified by the Zeeman effect.
-In particular, we will show that the perfect Klein tunneling predicted by O'Brien et al [OBrien] is never perfect with a proper account of the Zeeman effect.
+Our next case study involves orbits that (nearly) touch at a type-II Dirac point\cite{soluyanov_type-ii_2015,muechler_tilted_2016} -- an asymmetric variant of the conventional Dirac point (as will be introduced below).
+Quantum tunneling localized to a type-II Dirac point  (in short, a II-Dirac point) is known to be mathematically equivalent to  Landau-Zener breakdown, with the electric force replaced by the Lorentz force\cite{AALG,obrien_magnetic_2016}.\textbf{[Blount]} Here, we will demonstrate how Landau-Zener dynamics emerge from our quantization rule [\qq{eq:rule}{eq:H1}], and explore (for the first time) how these dynamics are modified by the Zeeman effect.
+In particular, we will show that the perfect Klein tunneling predicted by O'Brien \textit{et al}\cite{obrien_magnetic_2016} is never perfect with a proper account of the Zeeman effect.
 
@@
 H_{RZ}=\f{{\hbar^2}k^{2}}{2m}+\delta \var; \;\;\;\delta \var=d_x\sigma_x+d_y\sigma_y,\lin
-(d_x,d_y):=(-\alpha k_y,\alpha k_x+\zpar),\;\;\;\zpar:= g_s \mu_B B_{\parallel}/2.
+(d_x,d_y):=(-\hbar\alpha k_y,\hbar\alpha k_x+\zpar),\;\;\;\zpar:= g_s \mu_B B_{\parallel}/2.
 \label{eq:RZ-Hamiltonian}}
@@
 \begin{eqnarray}
-\bar{k}_x & = & -\frac{\zpar}{\alpha},\;\bar{k}_y=0,\;\epsilon_{0}=\frac{{\hbar^2}\zpar^{2}}{2m\alpha^2},\label{whereisdiracpoint}
+\bar{k}_x & = & -\frac{\zpar}{\hbar\alpha},\;\bar{k}_y=0,\;\epsilon_{0}=\frac{\zpar^{2}}{2m\alpha^2},\label{whereisdiracpoint}
 \end{eqnarray}
@@
 \e{
-H & =\alpha\left[\left(\sigma_y-\frac{{\hbar^2}\zpar}{m\alpha^2}\right)\delta k_{x}-\delta k_{y}\sigma_{x}\right]+\epsilon_{0}.}
-When $|\hbar^2\zpar|>|m\alpha^2|$, the Dirac cone tilts over in the $x$ direction, leading to a Lifshitz transition  of the constant-energy band contours -- from circular to hyperbolic (in the linearized approximation), as illustrated in Fig.
+H & =\hbar\alpha\left[\left(\sigma_y-\frac{\zpar}{m\alpha^2}\right)\delta k_{x}-\delta k_{y}\sigma_{x}\right]+\epsilon_{0}.}
+When $|\zpar|>|m\alpha^2|$, the Dirac cone tilts over in the $x$ direction, leading to a Lifshitz transition  of the constant-energy band contours -- from circular to hyperbolic (in the linearized approximation), as illustrated in Fig.
 \ref{fig:RZ}(c).
 An over-tilted Dirac cone shall be referred to as type-II.
-Our case study of a II-Dirac point  connects  two electron-like  pockets [cf.\ \fig{fig:RZ}(a,c)], and  differs from previous case studies [OBrien, AALG] that connect an electron- and hole-like pocket.
+Our case study of a II-Dirac point  connects  two electron-like  pockets [cf.\ \fig{fig:RZ}(a,c)], and  differs from previous case studies\cite{obrien_magnetic_2016,AALG} that connect an electron- and hole-like pocket.
 
@@
 \includegraphics[width=1.0\columnwidth]{RZ.png}
-\caption{ Characterization of the Rashba 2DEG with an in-plane Zeeman field.
-(a) illustrates the trefoille-shaped cyclotron orbit at the energy of the II-Dirac point.
+\caption{Characterization of the Rashba 2DEG with an in-plane Zeeman field.
+(a) illustrates the trefoil-shaped cyclotron orbit at the energy of the II-Dirac point.
 The orbit is drawn over the  spin-splitting field ($d_x,d_y$) of the degeneracy-lifting Hamiltonian $\delta\var$ [cf.\ \q{eq:RZ-Hamiltonian}].
-The wavefunction along the inner (resp.\ outer) component of the trefoille orbit has its pseudospin aligned parallel (resp.\ anti-parallel) to the spin-splitting field.
+The wavefunction along the inner (resp.\ outer) component of the trefoil orbit has its pseudospin aligned parallel (resp.\ anti-parallel) to the spin-splitting field.
 The upper panel of (b) schematically illustrates  Landau levels near the II-Dirac point (in the weak-hybridization regime).
-The solid line represents the Onsager-Lifshitz quantization of the trefoille \textbf{[please change trefoille everywhere to trefoil]} orbit [cf.\ Eq.\ ({trefoillerule})], and the dashed line incorporates the first-order correction [cf.\ Eq.\ (\ref{RZfirstorderE})] due to tunneling.
-Lower panel of (b): red solid line shows the energetic difference between Landau levels determined by numerical diagonalization and Landau levels obtained by the trefoil quantization rule  [cf.\ Eq.\ ({trefoillerule})]; this solid line may be compared to the perturbative formula $\delta E_n$ [cf.
+The dashed line represents the Onsager-Lifshitz quantization of the trefoil orbit [cf.\ Eq.\ (\ref{trefoilrule})], and the solid line incorporates the first-order correction [cf.\ Eq.\ (\ref{RZfirstorderE})] due to tunneling.
+Lower panel of (b): red dashed line shows the energetic difference between Landau levels determined by numerical diagonalization and Landau levels obtained by the trefoil quantization rule  [cf.\ Eq.\ (\ref{trefoilrule})]; this red dashed line may be compared to the perturbative formula $\delta E_n$ [cf.
 Eq.
-(\ref{RZfirstorderE})], which is plotted as a black dashed line.
+(\ref{RZfirstorderE})], which is plotted as a black solid line.
 This comparison is made (at each $1/B$) for the Landau level closest to 0.45eV and with even Landau-level index $n$; the II-Dirac point is located at 0.5eV.
-Parameters for lower panel of (b): $m{=}0.076m_0$, $\alpha{=} 1.5(10^{5}$cm/s$\cdot\hbar$), $Z_\parallel {=}$1meV.
+Parameters for lower panel of (b): $m{=}0.076m_0$, $\alpha{=} 1.5\times10^{5}$cm/s, $Z_\parallel {=}$1meV.
 Out-of-plane Zeeman coupling is negligibly weak for the choice of $m$.
@@
 Corresponding $l^2 \delta S^2/S$ are plotted in right panel.
-We only plotted in region where $0.4{<}\epsilon_0{<}1.0$(eV).\cite{RZfignote}, Units: $\alpha$($1.5\times 10^{5}$cm/s$\cdot\hbar$).
+We only plotted in region where $0.4{<}\epsilon_0{<}1.0$(eV)\cite{RZfignote}.
 Parameters for (d): $m=0.076m_0$, $l=100$\AA.
@@
 \begin{equation}
-\calh(t)=\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+Z_\parallel\sigma_{y}-Z_\perp\sigma_{z}.\label{calHRZ}
+\calh(t)=\hbar\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+Z_\parallel\sigma_{y}-Z_\perp\sigma_{z}.\label{calHRZ}
 \end{equation}
@@
 We focus first on the regime where, on average (over $\frako_0$), the energy splitting $|\delta \var_+{-}\delta \var_-|$ [cf.\ \q{eq:RZ-Hamiltonian}] is much greater than $B_\perp|\calm_{\sma{+-}}|$.
-Equivalently, we are in the regime where $\alpha k_{\sma{E}}{\gg}\var_c^\perp$.\footnote{The orbit-averaged energy splitting is of order $\alpha k_{\sma{E}}$ for energies near the Dirac point.
+Equivalently, we are in the regime where $\hbar\alpha k_{\sma{E}}{\gg}\var_c^\perp$.\footnote{The orbit-averaged energy splitting is of order $\alpha k_{\sma{E}}$ for energies near the Dirac point.
 $B_\perp|\calm_{\sma{+-}}|$ is simply the Berry contribution to the Zeeman interaction, and has the form of the right-most term in \q{rashbaeffham}; this term is of order $\var_c$.} This implies that the split orbits do not appreciably hybridize -- except in the vicinity of the II-Dirac point where orbits (nearly) touch.
@@
 \e{
-\calh = -\alpha k_{E}\omega^{\sma{\perp}}_c t\,\sigma_x+(Z_\parallel-\alpha k_{E})\sigma_y-Z_\perp\sigma_z,\label{effhamIIDirac}
-}
-The eigenbasis of $\sigma_x$ corresponds to two diabatic levels with characteristic slope $v_d{:}{=}\alpha k_E\omega^{\sma{\perp}}_c$; near $t{=}0$, the diabatic levels anticross  due to the hybridization terms proportional to $\sigma_{y,z}$.
-Generally, the probability of tunneling across the hybridization-induced barrier is  $\rho^2{=}\exp(-2\pi\barmu)$, with $\barmu{=}{E_g}^2/{2v_d \hbar}$ and $E_g$ the energy gap at the center of the anticrossing;[Landau and lifshitz, Wittig] in this context,
-\e{\barmu=\frac{Z_\perp^2+(Z_\parallel-\alpha k_{E})^2}{2\alpha k_{E}\var^{\sma{\perp}}_c}, \label{mu1}}
-with $2\alpha k_E$ the spin-orbit splitting at energy $E$ [cf.\ \fig{fig:orbits}(a)].
-In the absence of the out-of-plane Zeeman coupling ($Z_\perp{=}0$), $\bar{\mu}$ would vanish at the energy of the II-Dirac point -- leading to unit-probability Klein tunneling, as was first proposed by [Obrien] in a different model of the II-Dirac point.
-However, with a proper account of $Z_\perp$, we find instead that $\bar{\mu}$ has a nonvanishing minimum: $\bar{\mu}_{\sma{\text{min}}}{:}{=} ( m/m_0)(Z_\perp/4\alpha k_{E})$, which is a product of the dimensionless effective mass and the ratio of the out-of-plane Zeeman splitting over the spin-orbit splitting.
+\calh = -\hbar\alpha k_{E}\omega^{\sma{\perp}}_c t\,\sigma_x+(Z_\parallel-\alpha k_{E})\sigma_y-Z_\perp\sigma_z,\label{effhamIIDirac}
+}
+The eigenbasis of $\sigma_x$ corresponds to two diabatic levels with characteristic slope $v_d{:}{=}\hbar\alpha k_E\omega^{\sma{\perp}}_c$; near $t{=}0$, the diabatic levels anticross  due to the hybridization terms proportional to $\sigma_{y,z}$.
+Generally, the probability of tunneling across the hybridization-induced barrier is  $\rho^2{=}\exp(-2\pi\barmu)$, with $\barmu{=}{E_g}^2/{2v_d \hbar}$ and $E_g$ the energy gap at the center of the anticrossing\cite{wittig_landauzener_2005};\textbf{[Landau and lifshitz]} in this context,
+\e{\barmu=\frac{Z_\perp^2+(Z_\parallel-\alpha k_{E})^2}{2\hbar\alpha k_{E}\var^{\sma{\perp}}_c}, \label{mu1}}
+with $2\hbar\alpha k_E$ the spin-orbit splitting at energy $E$ [cf.\ \fig{fig:orbits}(a)].
+In the absence of the out-of-plane Zeeman coupling ($Z_\perp{=}0$), $\bar{\mu}$ would vanish at the energy of the II-Dirac point -- leading to unit-probability Klein tunneling, as was first proposed by Ref.
+\onlinecite{obrien_magnetic_2016} in a different model of the II-Dirac point.
+However, with a proper account of $Z_\perp$, we find instead that $\bar{\mu}$ has a nonvanishing minimum: $\bar{\mu}_{\sma{\text{min}}}{:}{=} ( m/m_0)(Z_\perp/4\hbar\alpha k_{E})$, which is a product of the dimensionless effective mass and the ratio of the out-of-plane Zeeman splitting over the spin-orbit splitting.
 This minimum is practically negligible for  semiconductor heterostructures with $m{\ll}m_0$, but may be relevant in heavy-fermion systems.
 
-To determine the Landau levels, one needs not just the probability for tunneling but also the phase of the probability amplitude. The full information is encoded in a scattering matrix [AALG]
+To determine the Landau levels, one needs not just the probability for tunneling but also the phase of the probability amplitude.
+The full information is encoded in a scattering matrix\cite{AALG,kaganov_coherent_1983}
 \e{\mathbb{S}=\matrixtwo{\tau e^{i\barphi}}{-\rho}{\rho}{\tau e^{-i\barphi}},\;\rho=e^{-\pi\barmu},\;\tau=\sqrt{1-\rho^{2}}\label{scattmat}}
@@
 $\phi_{\pm}^B$ equals half the solid angle subtended by   ${\mp} \boldsymbol{\calh}(\bk)$ [solid blue line] as $\bk$ is varied along the outer/inner orbit;[Berry] the orientation of the solid angle is indicated by blue dotted lines.
-The out-of-plane Zeeman interaction lifts $\boldsymbol{\calh}$ out of the x-y plane, but this occurs at most over a fraction ${\sim}(\bar{\mu}_{\sma{\text{min}}}m_0/m{\ll}1)$ of the cyclotron period.
+The out-of-plane Zeeman interaction lifts $\boldsymbol{\calh}$ out of the $x-y$ plane, but this occurs at most over a fraction ${\sim}(\bar{\mu}_{\sma{\text{min}}}m_0/m{\ll}1)$ of the cyclotron period.
 \label{fig:blochsphere}}
@@
 $\Omega_{\pm}$ are phases acquired by an electron in adiabatically traversing the orbits labelled $\pm$, respectively; the quantum Maslov correction $\gamma_{\pm}{=}\pi$ for circular orbits.
-A quantization rule analogous to \q{coscos} was previously derived by us for a II-Dirac point that intermediates an electron- and hole-like orbit [AALG].
+A quantization rule analogous to \q{coscos} was previously derived by us for a II-Dirac point that intermediates an electron- and hole-like orbit\cite{AALG}.
 
@@
 
-For any nonzero field, $0{<}\tau{<}1$ implies that the two incommensurate harmonics $(\Omega_+{\pm}\Omega_-)$ in \q{coscos} compete to produce a quasirandom Landau-level spectrum [kaganovslutskin].
+For any nonzero field, $0{<}\tau{<}1$ implies that the two incommensurate harmonics $(\Omega_+{\pm}\Omega_-)$ in \q{coscos} compete to produce a quasirandom Landau-level spectrum\cite{kaganov_coherent_1983}.
 That is to say, the spectrum is disordered on the scale of nearest-neighbor level spacings but has longer-ranged correlations.
@@
 To zeroth order, \q{coscos} reduces to
-\e{2l^2S(E_n^0)+\pi = 2\pi n \rightarrow \{E_n^0(B)\}_{n\in\Z}.\label{trefoillerule}}
-To derive the above equation, we have utilized $\phi^B_-{+}\phi^B_+{=}0$, which is valid for any two-band model in the quasidegenerate regime\footnote{For two band models, Berry phases of the two bands sum up to 0 on arbitrary path}; in \fig{fig:blochsphere} this is reflected in the sum of solid angles (at fixed energy) equalling $4\pi$.
-\q{trefoillerule} may be interpreted as a quantization rule for a trefoille-shaped orbit with net area $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels (sketched by solid lines in the upper panel of Fig.
+\e{2l^2S(E_n^0)+\pi = 2\pi n \rightarrow \{E_n^0(B)\}_{n\in\Z}.\label{trefoilrule}}
+To derive the above equation, we have utilized $\phi^B_-{+}\phi^B_+{=}0$, which is valid for any two-band model in the nearly-degenerate regime\footnote{For two band models, Berry phases of the two bands sum up to 0 on arbitrary path}; in \fig{fig:blochsphere} this is reflected in the sum of solid angles (at fixed energy) equalling $4\pi$.
+\q{trefoilrule} may be interpreted as a quantization rule for a trefoil-shaped orbit with net area $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels (sketched by solid lines in the upper panel of Fig.
 \ref{fig:RZ}(b)) are periodic in $E{\rightarrow}E{+}\pi/l^2(\partial S/\partial E)$ and in $l^2{\rightarrow}l^2{+}\pi/S$.
 Both periods are approximately half that of either disconnected  orbit, in the assumed quasidegenerate regime $\delta S{\ll}S$.
-The $\pi$ correction in \q{trefoillerule} is the Berry phase associated to a $2\pi$ rotation of the wavefunction spin over a single trefoille orbit, as illustrated in Fig.
+The $\pi$ correction in \q{trefoilrule} is the Berry phase associated to a $2\pi$ rotation of the wavefunction spin over a single trefoil orbit, as illustrated in Fig.
 \ref{fig:RZ}(a).
-The Maslov phase, which is generally equal to $\pi$ times the rotation number of an orbit, is trivially $2\pi$ for the trefoille orbit.
-
-To recapitulate, $E_n^0(B)$ [cf.\ \q{trefoillerule}] exhibits a periodicity on short scales associated to the large area of the trefoille orbit.
+The Maslov phase, which is generally equal to $\pi$ times the rotation number of an orbit, is trivially $2\pi$ for the trefoil orbit.
+
+To recapitulate, $E_n^0(B)$ [cf.\ \q{trefoilrule}] exhibits a periodicity on short scales associated to the large area of the trefoil orbit.
 This short-scale periodicity is lost due to  finite-$\tau$ corrections, yet a longer-range correlation (associated to the smaller differential area $\delta S$ between spin-split orbits) persists, as shown by the first-order-in-$\tau$ correction:\footnote{The general form of this perturbative calculation can be found in Sec.
-IX-E of [100page].}
+IX-E of Ref.
+\onlinecite{100p}.}
 \e{&\delta E_n(B) = \f{(-1)^n}{2\pi} \tau \var_c^\perp \cos\bigg(\f{l^2\delta S}{{2}}+\f{\phi_+^B-\phi_-^B}{2}-\bar{\varphi}\bigg) \lin
@@
 
-If the quasidegenerate orbits are appreciably hybridized ($\alpha k_{\sma{E}}{\lesssim}\var_c$), our quantization rule \qq{eq:rule}{eq:H1} remains valid but the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}.
+If the quasidegenerate orbits are appreciably hybridized ($\hbar\alpha k_{\sma{E}}{\lesssim}\var_c$), our quantization rule \qq{eq:rule}{eq:H1} remains valid but the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}.
 We may anyway diagonalize $\cala$ numerically, and compare the resultant semiclassical Landau levels with the exact diagonalization of $H_{RZ}(\boldsymbol{K})$; to our knowledge, there exists no analytic solution of $H_{RZ}(\boldsymbol{K})$ for generic values of $\alpha,\zpar$ and $B_{\perp}$.
@@
 \section{Tuning the spin-degeneracy of Landau Levels}\label{sec:llquasideg}
+
+\begin{figure}
+\includegraphics[width=1.0\columnwidth]{LL.png}
+\caption{\red{A schematic diagram of Landau level dispersion with respect to $B$ for nearly degenerate orbits.
+One region of Landau level quasidegeneracies (corresponding to $\delta\lambda\equiv 0$) is indicated by a red rectangle.}\label{fig:LL}}
+\end{figure}
 
@@
 \e{l^2\left|\p{S}{E}\right| \gg \left|\p{\lambda_a}{E}\right|,\, \left|S\right| \gg \left|\p{\lambda_a}{l^2}\right|;} 
-these inequalities are guaranteed by the quasidegeneracy condition ($\delta S{\ll}S$) and the smoothness of $S(E)$, as shown in \app{sec:slowvariation}.
+these inequalities are guaranteed by the nearly-degeneracy condition ($\delta S{\ll}S$) and the smoothness of $S(E)$, as shown in \app{sec:slowvariation}.
 For fixed $\bar{B}$, we are therefore guaranteed to find a number (of order one) of paired Landau levels  in close proximity to $\bar{E}$, with each pair having an energetic splitting of order:
-\e{\bigg|\f{E_{1}-E_2}{\var_c}\bigg|_{B=\bar{B}} = \order\left( \f{\partial \lambda_a/\partial E}{\bar{l}^2\partial  S/\partial E}  \right)\ll 1,\label{llquasideg}}
+\e{\bigg|\f{E_{1}-E_2}{\var_c}\bigg|_{B=\bar{B}} \sim \order\left( \f{\partial \lambda_a/\partial E}{\bar{l}^2\partial  S/\partial E}  \right)\ll 1,\label{llquasideg}}
 with $\bar{l}$ the magnetic length associated to $\bar{B}$.
 Alternatively, we may fix $\bar{E}$ and investigate how Landau levels disperse as a function of $B$; the analog of \q{llquasideg}  is the existence of paired Landau levels in close proximity to $\bar{l}^2$, with a splitting of order:
-\e{\bigg|\f{l^2_{+}-l^2_-}{T_{{l^2}}}\bigg|_{E=\bar{E}} = O\left( \f{1}{S}\p{\lambda_a}{l^2} \right)\ll 1,\;\; T_{{l^2}}:=\f{2\pi}{S(\bar{E})}.\label{llquasidegB} }
+\e{\bigg|\f{l^2_{+}-l^2_-}{T_{{l^2}}}\bigg|_{E=\bar{E}} \sim O\left( \f{1}{S}\p{\lambda_a}{l^2} \right)\ll 1,\;\; T_{{l^2}}:=\f{2\pi}{S(\bar{E})}.\label{llquasidegB} }
 $\partial \lambda_a/\partial l^2$ is estimated in \app{sec:slowvariation}, and
@@
 Each such pair of Landau levels will be called \textit{quasidegenerate}.
+Landau level quasidegeneracy is sketched in Fig.
+\ref{fig:LL}.
 
@@
 \q{eq:prop}] are attainable by tuning three real parameters.
-Analogously, it is well known (as the non-crossing rule in quantum theory[von Neumann,wigner]) that eigenvalue-degeneracies of complex, finite-dimensional matrix Hamiltonians are also attainable by tuning three real parameters.
+Analogously, it is well known (as the non-crossing rule in quantum theory\cite{neumann2000behaviour}) that eigenvalue-degeneracies of complex, finite-dimensional matrix Hamiltonians are also attainable by tuning three real parameters.
  To prove the non-crossing rule for two-by-two unitaries, we begin by decomposing any such matrix as $\A{=}e^{i\phi}{\cal \bar{A}}$, with  ${\cal \bar{A}}{\in}\text{SU}(2)$.
@@
 
- To generalize the above discussion, let us parametrize ${\cal \bar{A}}$ by $d$ real coordinates  $\{r_1,\ldots,r_{d}\}{:}{=}\br $;  ${\cal \bar{A}}(\br){=}{\pm}I$ defines a set of submanifolds in $\br$-space which we refer to as degeneracy manifolds; in the above example, these manifolds comprise two points on $S^3$.
-The codimension of the degeneracy manifold  is defined as $d$ minus the dimension of said manifold; \textbf{[there are inconsistencies in these definitions, if we impose $d$ to be number of parameters (without imposing linear independence), then $d=4$ for canonical parametrization, and our definition of codimension as d minus dimension of degeneracy manifold gives 4.
+Symmetry may reduce the number of tunable parameters needed to attain an eigenvalue degeneracy for $\A$.
+A case in point is band-conservation symmetry in the adiabatic regime (cf.\ \s{sec:qtznrules}), which restricts $\cala$ to have diagonal form  ($r_3{=}r_4{=}0$) in the basis of energy bands [cf.\ \q{phaseindependentorbit}].
+The phase of $r_1{\pm}ir_2$ equals ${\pm} l^2\delta S/2$ plus field-independent corrections.
+This  phase -- a single parameter --  can be  tuned to attain $\cala{=}{\pm}I$.
+As a function of $l^2$, we deduce that Landau-level quasidegeneracies occur  with a periodicity of $2\pi/\delta S$.
+This periodicity  has a dual interpretation  in real space -- as a periodic increment of a single flux quantum for  the differential magnetic flux (between the two split orbits).
+
+To generalize the discussion beyond band-conservation symmetry, it is instructive to adopt a geometric perspective on degeneracies.
+A generic SU(2) matrix that is constrained by symmetry may no longer be uniformly distributed over $S^3$ [cf.\ \q{s3}], e.g., ${\cal \bar{A}}$ with band-conservation symmetry is uniformly distributed over a phase in $S^1$.
+In such cases, we are  motivated to adopt \textit{symmetric coordinates} [$\{r_1,\ldots,r_{d}\}{:}{=}\br$] that independently parametrize the symmetry-constrained SU(2) matrix; the precise nature of these constraints will be developed in subsequent subsections.
+In our example, we may choose the symmetric coordinate as the phase of the diagonal element of ${\cal \bar{A}}$.
+Such coordinates are generally not relatable -- by a non-singular coordinate transformation -- to the canonical coordinates [\q{s3}] of asymmetric special unitaries.
+${\cal \bar{A}}(\br){=}{\pm}I$ then defines a set of submanifolds in $\br$-space which we refer to as \textit{degeneracy manifolds}.
+The \textit{codimension} of the degeneracy manifold  is defined as $d$ minus the dimension of said manifold; alternatively stated, the codimension is the number of independently-tunable parameters (in $\br$) needed to attain a degeneracy.
+Here and henceforth, we adopt the shorthand that  \textit{parameters} (or coordinates) will always refer to real parameters (coordinates), and \textit{codimension} always refers to a codimension of a degeneracy manifold.
+In our example, the degeneracy manifolds  are two points on $S^1$, and each has unit codimension.
+
+One of our main results is that rotational symmetry (with rotational axis parallel to the field) also results in degeneracy manifolds with unit codimension.
+This will be demonstrated by two  case studies: the Rashba 2DEG in \s{sec:singleparameterrashba}, and a model with II-Dirac points in \ref{sec:rotsymmbreakdown}.
+
+%Generally, such \textit{symmetry-constrained coordinates} are not necessarily related to the canonical coordinates of \q{s3} by a non-singular
+
+%${\cal \bar{A}}(\br){=}{\pm}I$ defines a set of submanifolds in $\br$-space which we refer to as degeneracy manifolds; in the above example, these manifolds comprise two points on $S^3$.
+
+ %\textbf{[there are inconsistencies in these definitions, if we impose $d$ to be number of parameters (without imposing linear independence), then $d=4$ for canonical parametrization, and our definition of codimension as d minus dimension of degeneracy manifold gives 4.
 however, if we impose linearly-independent parameters, then we also run into trouble if we allow for symmetric coordinates that are not well-defined at points.]}\red{[First of all, I am not quite sure why the word linear independence is used in the current context.
 I would have used `independent', which means the parameters can be tuned simultaneously.
-One thing that you would probably dislike is that codimension defined by me would be dependent on the parameters $\br$, so it's OK that codimension in canonical parametrizaiton is three while codimension in exponential parametrization is one.
-The precise codimension would be the number of independent parameters needed to find a degeneracy.
+One thing that you would probably dislike is that codimension defined by me would be dependent on the parameters $\br$, so it's OK that codimension in canonical parametrization is three while codimension in exponential parametrization is one.
+The precise definition of codimension would be the number of independent parameters needed to find a degeneracy.
 Although codimension depends on the parameters, the codimension found by us is generally universal.
@@
 
-It is well-known that symmetry may reduce the codimension of Hamiltonians, e.g., an antiunitary symmetry may restrict complex Hamiltonians to real Hamiltonians, thus reducing codimension from three to two.[wigner,von neumann] In our context, an analog would be the symmetry of band conservation in the adiabatic regime (cf.\ \s{sec:qtznrules}), which restricts $\cala$ to have diagonal form  ($r_3{=}r_4{=}0$) in the basis of energy bands [cf.\ \q{phaseindependentorbit}].
-The phase of $r_1{\pm}ir_2$ equals ${\pm} l^2\delta S/2$ plus field-independent corrections.
-Since this  phase alone  can be  tuned to attain $\cala{=}{\pm}I$, the codimension is unity.
-As a function of $l^2$, we deduce that Landau-level quasi-crossings occur  with a periodicity of $2\pi/\delta S$.
-This periodicity  has a dual interpretation  in real space -- as a periodic increment of a single flux quantum for  the differential magnetic flux (between the two split orbits).
-
-We may ask if these quasi-crossings (based on band-conservation symmetry) persist at stronger fields where adiabaticity breaks down.
-If no symmetry remains, then the codimension is three [cf.\ \q{s3}], hence Landau-level quasi-crossings should not generically be found by varying $B$ alone.
-One of our main results is that  rotational symmetry (with rotational axis parallel to the field) results in degeneracy manifolds with unit codimension.
-This will be demonstrated by two  case studies: the Rashba 2DEG in \s{sec:singleparameterrashba}, and a model with II-Dirac points in \ref{sec:rotsymmbreakdown}.
+%It is well-known that symmetry may reduce the codimension of Hamiltonians, e.g., an antiunitary symmetry may restrict complex Hamiltonians to real Hamiltonians, thus reducing codimension from three to two.[wigner,von neumann] In our context, an analog would be
+
+%We may ask if these quasidegeneracies (based on band-conservation symmetry) persist at stronger fields where adiabaticity breaks down.
+If no symmetry remains, then the codimension is three [cf.\ \q{s3}], hence Landau-level quasidegeneracies should not generically be found by varying $B$ alone.
 
@@
 
-In this and the subsequent section (\s{sec:rotsymmbreakdown}), we will demonstrate how rotational symmetry reduces codimension in the Landau-level problem.
+%In this and the subsequent section (\s{sec:rotsymmbreakdown}), we will demonstrate how rotational symmetry reduces codimension in the Landau-level problem.
 Before delving into this, it is instructive to consider the conceptually-simplest analog in differential geometry: if we parametrize the 2D plane by Cartesian coordinates $(x,y){\in}\R^2$, it is apparent that two parameters must be tuned to arrive at the origin.
@@
 To understand why rotational symmetry reduces codimension in the Landau-level problem, we return to the Rashba model [cf.
-\ \q{eq:Rashba-Hamiltonian}] without in-plane Zeeman field.
+\q{eq:Rashba-Hamiltonian}].
 This model has a continuous rotational symmetry (denoted $\mathfrak{c}_{\infty}$), which manifests as the constancy of $\calh(\bk){:}{=}\sum_{j=1}^3r_j\tau_j$ over the circular zeroth-order orbit [cf.\ \q{rashbaeffham}]; here, $\br{=}(r_1,r_2,r_3)$ is a real three-vector and $\{\tau_j\}$ a set of Pauli matrices.
@@
 where
-\e{\br{=}\bigg(\f{g_sm}{4m_0}{-}\f1{2},0,-\f{\alpha k_{\sma{E}}}{\var_c}\bigg).}
+\e{\br{=}\bigg(\f{g_sm}{4m_0}{-}\f1{2},0,-\f{\hbar\alpha k_{\sma{E}}}{\var_c}\bigg).}
 Any $\text{SU}(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}] for some (possibly non-unique) $\br$, with $r_2$ not necessarily zero.
@@
 This condition $|\br|{=}j/2$ (for any nonzero $j$) may be attained by tuning a single parameter.
-In other words,
-all nonzero-radius spheres are unit-codimensional surfaces (known as hypersurfaces), whose stability rely on $\mathfrak{c}_{\infty}$ symmetry.
+In other words, all nonzero-radius spheres are unit-codimensional surfaces (known as hypersurfaces), whose stability rely on $\mathfrak{c}_{\infty}$ symmetry.
 These hypersurfaces separate $\br$-space into infinitely-many, distinct connected components, i.e., the zeroth homotopy group $\pi_0$ comprises an infinite set.
 Each hypersurface may thus be viewed as a symmetry-protected, topological defect, which separates domains (in $\br$-space) where Landau levels are non-quasidegenerate.
-By varying $B$ alone (at fixed energy), one then transits between different domains; each penetration of a hypersurface is accompanied by a Landau-level quasi-crossing.
-For the exactly-soluble Rashba model ($r_2{=}0$), these $\mathfrak{c}_{\infty}$-protected quasi-crossings  are consistent with (and partially explain)  the abundance of \textit{exact} level crossings in the spectrum of $H_R(\bK)$ [cf.\ \q{eq:Rashba-exact}], which would otherwise seem mysterious in face of  the Wigner-von Neuman non-crossing rule[wigner neumann].
-
-The zero-radius sphere (i.e., a point) has codimension three, as would be expected if symmetry were absent [cf.\ \s{sec:introducecodimension}].
-This point degeneracy can be understood from an elementary result in quantum mechanics: taking $\alpha{=}r_2{=}0$ \textit{and} $m{=}m_0$, we recover the Zeeman-split Landau levels of a free electron gas without spin-orbit coupling; all levels (except the lowest) are spin-degenerate owing to the equality of the Zeeman and cyclotron energies.[LandauLifshitzstatphysI]
-
-The above discussion is reminiscent of topological (semi)metals which host Dirac-Weyl points and/or line nodes (of Bloch-Hamiltonian degeneracies).
-Both Dirac points (in 2D $\bk$-space, e.g., graphene) and  line nodes (in 3D $\bk$-space) are attainable by tuning two wavenumbers; the stability of such codimension-two manifolds
- relies on crystallographic point-group symmetries.
+By varying $B$ alone (at fixed energy), one then transits between different domains; each penetration of a hypersurface is accompanied by a Landau-level quasidegeneracy.
+For the exactly-soluble Rashba model ($r_2{=}0$), these $\mathfrak{c}_{\infty}$-protected quasidegeneracies  are consistent with (and partially demystify)  the abundance of \textit{exact} level crossings in the spectrum of $H_R(\bK)$ [cf.\ \q{eq:Rashba-exact}]; such crossings are not expected from the Wigner-von Neuman non-crossing rule\cite{neumann2000behaviour}.
+The zero-radius sphere (i.e., a point) has codimension three, as would be expected if symmetry were absent [cf.
+\s{sec:introducecodimension}].
+This point degeneracy can be understood from an elementary result in quantum mechanics: taking $\alpha{=}r_2{=}0$ \textit{and} $m{=}m_0$, we recover the Zeeman-split Landau levels of a free electron gas without spin-orbit coupling; all levels (except the lowest) are spin-degenerate owing to the equality of the Zeeman and cyclotron energies\cite{landau2013course}.
+
+The above discussion is reminiscent of topological (semi)metals which host Dirac-Weyl points\cite{wang2012dirac,wan2011topological} and/or line nodes\cite{burkov2011topological} (of Bloch-Hamiltonian degeneracies).
+Both Dirac points (in 2D $\bk$-space, e.g., graphene\cite{neto2009electronic}) and line nodes (in 3D $\bk$-space) are attainable by tuning two wavenumbers; the stability of such codimension-two manifolds relies on crystallographic point-group symmetries.
 On the other hand, Weyl points in 3D $\bk$-space have codimension three and do not require any point-group symmetry for their stability.
-Just like Weyl points, the point degeneracy of $\A$ is associated with a nontrivial Chern number (defined as an integral of the Berry curvature\footnote{The curvature is defined with respect to a line bundle formed from the nondegenerate eigenvector of $\cala$.} over a Gaussian surface surrounding the point).
+Just like Weyl points, the point degeneracy of $\A$ is associated with a nontrivial Chern number\cite{TKNN} (defined as an integral of the Berry curvature\cite{berry_quantal_1984} over a Gaussian surface surrounding the point).\footnote{The curvature is defined with respect to a line bundle formed from the nondegenerate eigenvector of $\cala$.}
 
@@
 It is possible for $\mathfrak{c}_{\infty}$-symmetric $\bk{\cdot}\bp$ models to approximate Bloch Hamiltonians (defined over the Brillouin torus) with a discrete, order-$N$ rotational symmetry (denoted $\mathfrak{c}_N$).
-How robust are the above-mentioned Landau-level quasi-crossings  (over the $B$ axis) when $\mathfrak{c}_{\infty}$ symmetry is perturbatively reduced to $\mathfrak{c}_N$?
-For any  integer $N{\geq}2$, we find that $N{-}1$ of every $N$ quasi-crossings  are perturbatively stable.
+How robust are the above-mentioned Landau-level quasidegeneracies  (over the $B$ axis) when $\mathfrak{c}_{\infty}$ symmetry is perturbatively reduced to $\mathfrak{c}_N$?
+For any  integer $N{\geq}2$, we find that $N{-}1$ of every $N$ quasidegeneracies  are perturbatively stable.
 This general statement is proven in App.
@@
 
-Since $\A$ depends on $\alpha,~\beta,~l,~E,~m$ only through $\alpha k_E /\var_c$, $\beta k_E /\var_c$ and $g_sm/m_0$, let us consider the three-dimensional parameter space $(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_sm/m_0){\in} \mathbb{R}^3$.
-$\A(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_sm/m_0){=}{\pm} I$ determines a set of concentric circles in the $\beta{=}0$ plane, as per the $\mathfrak{c}_{\infty}$-symmetric case study in \s{sec:ctsrot}.
+Since $\A$ depends on $\alpha,~\beta,~l,~E,~m$ only through $\hbar\alpha k_E /\var_c$, $\hbar\beta k_E /\var_c$ and $g_sm/m_0$, let us consider the three-dimensional parameter space $(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0){\in} \mathbb{R}^3$.
+$\A(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0){=}{\pm} I$ determines a set of concentric circles in the $\beta{=}0$ plane, as per the $\mathfrak{c}_{\infty}$-symmetric case study in \s{sec:ctsrot}.
 Moving off this plane, we find that $\A{=}I$ is satisfied in a  neighborhood of $\beta{=}0$, i.e., $\A{=}I$ defines a hypersurface in $\mathbb{R}^3$ that is illustrated in \fig{fig:dgn}(a).
@@
 To demonstrate how the $\A{=}I$ hypersurface derives from $\mathfrak{c}_2$ symmetry, consider  the effective Hamiltonian $\calh$ 
-\e{\calh=\alpha (k_{x}\sigma_{y}{-}k_{y}\sigma_{x})+\beta (k_{x}\sigma_{x}{-}k_{y}\sigma_{y})-\f{g_s}{2}\mu_{B}B\sigma_z,}
+\e{\calh=\hbar\alpha (k_{x}\sigma_{y}{-}k_{y}\sigma_{x})+\hbar\beta (k_{x}\sigma_{x}{-}k_{y}\sigma_{y})-\f{g_s}{2}\mu_{B}B\sigma_z,}
 in a momentum-independent basis where the Pauli matrices correspond to spin operators. The two-fold rotational symmetry 
@@
 The tracelessness of $\calh$ (at each $\bk$) implies that  ${\A}_{\sma{T_c/2\leftarrow 0}}$  has unit determinant.
-Utilizing the canonical parametrization for this $\text{SU}(2)$ matrix [Eq. (\ref{s3}) with ${\cal \bar{A}}$ replaced by ${\A}_{\sma{T_c/2\leftarrow 0}}$], we derive 
-\e{
-{\A}={\cal \bar{A}}=\matrixtwo{1{-}2r_2(r_2{-}ir_1)}{2ir_2(r_3{+}ir_4)}{{-}2ir_2(r_3{-}ir_4)}{1{-}2r_2(r_2{+}ir_1)} \label{proprashba}
+\red{Since the full propagator $\A$ can be obtained with the knowledge of half of it $\A_{\sma{T_c/2\leftarrow 0}}$, the symmetric coordinates are naturally chosen as the canonical parametrization for this $\text{SU}(2)$ matrix [Eq.
+(\ref{s3}) with ${\cal \bar{A}}$ replaced by ${\A}_{\sma{T_c/2\leftarrow 0}}$].} In this symmetric coordinates, we derive
+\e{
+{\A}={\cal \bar{A}}(r_1,r_2,r_3)=\matrixtwo{1{-}2r_2(r_2{-}ir_1)}{2ir_2(r_3{+}ir_4)}{{-}2ir_2(r_3{-}ir_4)}{1{-}2r_2(r_2{+}ir_1)} \label{proprashba}
 }
@@
 It follows that $r_2{=}0$ is a necessary and sufficient condition for $\bar{\A}{=}I$.
-The corresponding degeneracy manifold is a path-connected hypersurface, which separates $\br=(r_1,r_2,r_3,r_4)$-space into two distinct connected components.
-Generally, degenerate manifold of $\A$ of $\mathfrak{c}_N$ symmetric Hamiltonian separates $\br$-space (parametrizing $1/N$ of $\A$) into $N$ distinct connected components.
-\fig{fig:dgn}(a) illustrates the $\A=-I$ degenerate manifold in distinct coordinates: $(\alpha k_{\sma{E}}/\var_c,\beta k_{\sma{E}}/\var_c,g_sm/m_0)$.
-On the other hand, ${\cal \bar{A}}{=}{-}I$ occurs if and only if $\br{=}(0,\pm 1,0,0)$.
-These two points are mapped to a path-connected line node confined to the $\alpha{=}0$ and $\beta{=}0$ planes [cf.\ \fig{fig:dgn}(b)]; the difference in codimension originates from the  $\mathfrak{c}_{\infty}$ symmetry within these two planes [cf.\ \s{sec:ctsrot}], which was not accounted for in the $\mathfrak{c}_2$-symmetric analysis of \q{proprashba}.
+The corresponding degeneracy manifold is a path-connected hypersurface, which separates $\br{=}(r_1,r_2,r_3)$-space into two distinct connected components.
+As proven in App.
+\ref{app:codimension}, this conclusion generalizes for any $N{\geq}2$: the degenerate manifolds of $\mathfrak{c}_N$-symmetric $\A$ separate the space of symmetric coordinates into $N$ distinct connected components.
+
+\red{Returning to the Rashba-Dresselhaus model, if the map $f$ from physical variables $(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0)$ to the symmetric coordinates is well-behaved, the inverse image of $r_2=0$ in $(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0)$ would be a two dimensional manifold, as illustrated in \fig{fig:dgn}(a).
+On the other hand, ${\cal \bar{A}}{=}{-}I$ occurs if and only if $\br{=}(0,\pm 1,0)$.
+The inverse image of $f$ of the two points is a path-connected line node confined to the $\alpha{=}0$ and $\beta{=}0$ planes [cf.\ \fig{fig:dgn}(b)];} the difference in codimension originates from the $\mathfrak{c}_{\infty}$ symmetry within these two planes [cf.\ \s{sec:ctsrot}], which was not accounted for in the $\mathfrak{c}_2$-symmetric analysis of \q{proprashba}.
 
@@
 For $N{=}2$, we will demonstrate that the codimension for $\cala{=}I$ (but not for $\cala{=}{-}I$) remains unity, in accordance with the symmetric-coordinate analysis of \q{proprashba}; the persistence of  Landau-level quasidegeneracies  (at finite tunneling probability) will be demystified in terms of the destructive interference of tunneling Feynman paths.
-For $N{=}3$, we will find that two of three Landau-level quasi-crossings are perturbatively stable against tunneling, but even these will destabilize beyond a critical tunneling strength.
+For $N{=}3$, we will find that two of three Landau-level quasidegeneracies are perturbatively stable against tunneling, but even these will destabilize beyond a critical tunneling strength.
 
@@
 Such quasidegeneracies recur as $\Delta$ advances by $2\pi$, corresponding to a periodicity in $l^2$ of $4\pi/\delta S$ (or two flux quanta).
-This periodicity is not affected by the additional phase $2\bar{\phi}$ in $\Delta$, because $\bar{\phi}$ varies on the scale  $2\pi/S_{\sma{\square}}$,\footnote{For $\bar{\varphi}(\bar{\mu})$ to vary  $\sim 1$, the Landau-Zener parameter $\bar{\mu}$ must vary by $\sim 1$ [cf.\  Fig.\ 10 in 100page].
-Moreover, $2\pi\barmu{:}{=} (2\pi/8) l^2S_{\sma{\square}}$.[AALG]} which is much larger than $4\pi/\delta S$.
-To recapitulate, half the Landau-level quasi-crossings (over the $B$ axis) are destabilized  by tunneling; the robustness of the other half relies on $\mathfrak{c}_2$ symmetry.
-There exists a complementary argument for the existence of Landau-level quasi-crossings in the Klein-tunneling limit $(\tau{=}0)$ (cf.
+This periodicity is not affected by the additional phase $2\bar{\phi}$ in $\Delta$, because $\bar{\phi}$ varies on the scale  $2\pi/S_{\sma{\square}}$,\footnote{For $\bar{\varphi}(\bar{\mu})$ to vary  $\sim 1$, the Landau-Zener parameter $\bar{\mu}$ must vary by $\sim 1$ [cf.\  Fig.\ 10 in Ref.
+\onlinecite{100p}].
+Moreover, $2\pi\barmu{:}{=} (2\pi/8) l^2S_{\sma{\square}}$.\cite{AALG}} which is much larger than $4\pi/\delta S$.
+To recapitulate, half the Landau-level quasidegeneracies (over the $B$ axis) are destabilized  by tunneling; the robustness of the other half relies on $\mathfrak{c}_2$ symmetry.
+There exists a complementary argument for the existence of Landau-level quasidegeneracies in the Klein-tunneling limit $(\tau{=}0)$ (cf.
 Fig.
@@
 In the adiabatic regime ($\tau{\approx}1$), Landau-level quasidegeneracies occur with a periodicity of one flux quantum; however, in the Klein-tunneling regime ($\tau{\approx}0$), there exists only one dominant orbit shaped like a three-fold-symmetric trefoil knot (cf.
-Fig.\ref{fig:Cn-breakdown}(c) lower panel) --  all Landau levels are nondegenerate with spacing determined by the effective mass of the trefoil; this property generalizes to $\mathfrak{c}_N$-symmetric II-Dirac models with odd $N$.
+Fig.
+\ref{fig:Cn-breakdown}(c) lower panel) --  all Landau levels are nondegenerate with spacing determined by the effective mass of the trefoil; this property generalizes to $\mathfrak{c}_N$-symmetric II-Dirac models with odd $N$.
 
@@
 
-We conclude this section with a general result that is valid for any integer $N{\geq}2$: of every $N$ quasi-crossings that exist in the adiabatic limit, $N{-}1$ of them are perturbatively stable against tunneling that respects  $\mathfrak{c}_N$ symmetry.
+We conclude this section with a general result that is valid for any integer $N{\geq}2$: of every $N$ quasidegeneracies that exist in the adiabatic limit, $N{-}1$ of them are perturbatively stable against tunneling that respects  $\mathfrak{c}_N$ symmetry.
 We prove this in App.
@@
 \hlineB{2.0}
-             class number & action on orbit & action on $\bk$ & $u$ & $s$ & quasidegenerate & $g$ & codimension\\
+             class number & action on orbit & action on $\bk$ & $u$ & $s$ & nearly-degenerate & $g$ & codimension\\
 \hline
@@
 The next two columns  inform us if the mapping $\bk{\rightarrow}g{\circ}\bk$ [cf.\ \q{gmapk}]  preserves ($u{=}0$) or inverts ($u{=}1$) the orientation of the orbit, and if $g$ preserves ($s{=}0$) or inverts ($s{=}1$) the arrow of time.
-The sixth column indicates whether this  class is potentially a symmetry of quasidegenerate orbits.
+The sixth column indicates whether this  class is potentially a symmetry of nearly-degenerate orbits.
 The seventh column specifies additional conditions (on the representation of $g$) which must be imposed to uniquely determine the codimension.
@@
 For the reader's convenience, we present some commonly-encountered matrix representations for exactly-degenerate orbits in Tab.\ \ref{table:sewing-matrix}.
-The last column presents codimensions of the degeneracy manifold \textbf{[remind reader what is degeneracy manifold]}.
+The last column presents codimensions of the degeneracy manifold defined in symmetric coordinates [cf.
+Sec.
+\ref{sec:introducecodimension}].
 For exactly-degenerate orbits in class 2, 4 and 5, $\A$ satisfies $\text{det}(\A){=}1$,[topofermi] with the assumption that spin-orbit coupling can be turned off continuously without changing the degeneracy of the orbit.
@@
 Sec.
-\ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown}, we now present the symmetry-constrained codimensions for all ten[topoferm] symmetry classes of orbits.
+\ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown}, we now present the symmetry-constrained codimensions for all ten symmetry classes of orbits\cite{topoferm}.
 Depending on the class, the codimension is either $0,1,2$ or $3$.
@@
 
-\subsubsection{Ten-fold classification of orbits}\label{sec:reviewtenfold}
+\subsubsection{\red{Ten-fold classification of orbits and symmetric coordinates}}\label{sec:reviewtenfold}
 
@@
 For example, a rotation with axis parallel to the field is orientation-preserving, while a reflection with axis orthogonal to the field is orientation-inverting.
-The combination of all distinguishing criteria leads to   a ten-fold classification of orbits $\frako_0$ with $g$ symmetry, as was first presented in [topoferm] and is summarized by the ten numbered rows in \tab{table:codimension}.
+The combination of all distinguishing criteria leads to   a ten-fold classification of orbits $\frako_0$ with $g$ symmetry, as was first presented in Ref.
+\onlinecite{topoferm} and is summarized by the ten numbered rows in \tab{table:codimension}.
+
+\red{Among the ten symmetry classes, only six of them (class 1-6) impose self constraints on $\A$.
+These self constraints can be divided into two types: (i) restricting $\A$ to only a submanifold of SU(2) (class 1, 2, 5, 6); (ii) expressing the propagator $\A$ with only a fraction of it [e.g., Eq.
+(\ref{eq:sigmazconstraint})] (class 3, 4).
+For the former case, we define symmetric coordinates by restricting canonical parametrization of $\A$ to that submanifold; for the latter case, we define symmetric coordinates as canonical parametrization of the said fraction of $\A$.}
 
@@
 
-\subsubsection{Symmetry-constrained codimension for quasidegenerate orbits}\label{sec:codimquasideg}
-
-In the particular context of quasidegenerate bands, $\hat{H}{=}\hat{H}_0{+}\delta \hat{H}$ is the sum of a zeroth-order Hamiltonian (with spin-degenerate bands) and a symmetry-lowering perturbation.
+\subsubsection{Symmetry-constrained codimension for nearly-degenerate orbits}\label{sec:codimquasideg}
+
+In the particular context of nearly-degenerate bands, $\hat{H}{=}\hat{H}_0{+}\delta \hat{H}$ is the sum of a zeroth-order Hamiltonian (with spin-degenerate bands) and a symmetry-lowering perturbation.
 Given a zeroth-order orbit $\frako_0$ of $\hat{H}_0$, we  are interested in the subgroup of $\hat{H}$ that  maps $\frako_0$ to itself or to a distinct zeroth-order orbit.
@@
 Since $g$ is  a symmetry of  $\delta \hat{H}$, $\delta\epsilon$ is invariant under action of $g$.
-On the other hand, $\mathcal{M}$ is the field-parallel component of a pseudovector that is odd under time reversal,[sakurai] hence changes under $g$ to  $(-1)^{u+s}\mathcal{M}$  (plus a gauge-dependent term[100page] which is not essential to the present argument).
+On the other hand, $\mathcal{M}$ is the field-parallel component of a pseudovector that is odd under time reversal\cite{sakurai1995modern}, hence changes under $g$ to  $(-1)^{u+s}\mathcal{M}$ (plus a gauge-dependent term\cite{100p} which is not essential to the present argument).
 Only with $u{+}s{=}0$ or $2$ would both terms in $\H$ transform consistently (invariantly) under $g$ -- this identifies the five ticked classes in Tab.\ \ref{table:codimension}.
@@
 For these five classes (labelled 1, 3, 6, 7 and 10 according to the first column of Tab.\ \ref{table:codimension}), we list their corresponding \textit{symmetry-constrained codimensions} in the right-most column of Tab.\ \ref{table:codimension}; these numbers are derived in  App.\ \ref{app:codimension}.
-To clarify, we define the $g$-constrained codimension as a number which is robust to any perturbation of the Hamiltonian that preserves $g$ symmetry and the homotopy class of $\frako_0$.
+Recall that the codimension is the number of independently-tunable parameters needed to attain a degeneracy for $\A$.
+We define the $g$-constrained codimension as a codimension which is robust to any perturbation of the Hamiltonian that preserves $g$ symmetry and the homotopy class\cite{100p} of the zeroth-order orbit (e.g., a circular orbit cannot be deformed into a figure of eight).
 Each entry in the right-most column of Tab.\ \ref{table:codimension} equals the $g$-constrained codimension for any $g$ specified by the corresponding row.
@@
 The symmetry-constrained codimension here is unity, as has been modelled in Sec.\ \ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown}.
-Only in class 3 (among 1,3,6) do there exist different  degeneracy manifolds with different codimensions; in such case we define the symmetry-constrained codimension to be the minimal codimension among all manifolds.
+Only in class 3 (among 1, 3, 6) do there exist different  degeneracy manifolds with different codimensions; in such case we define the symmetry-constrained codimension to be the minimal codimension among all manifolds.
 For example, we have found that two-fold rotational symmetry reduces the codimension of the $\A{=}{+}I$ manifold (to unity), but not the codimension of the $\A{=}{-}I$ manifold [cf.\ \q{proprashba}].
@@
 
-This work has mainly focused on the Landau quantization of quasidegenerate bands, which are eigenstates of the field-independent Hamiltonian $\hat{H}_0{+}\delta \hat{H}$.
+This work has mainly focused on the Landau quantization of nearly-degenerate bands, which are eigenstates of the field-independent Hamiltonian $\hat{H}_0{+}\delta \hat{H}$.
 In this section we focus on higher-symmetry solids where the degeneracy-lifting perturbation $\delta \hat{H}$ is disallowed.
@@
 
-We answer this question in nearly the same vein as for quasidegenerate orbits: the quantization rule for exactly-degenerate orbits[topoferm] has the same form as \qq{eq:rule}{berryconn} with $\delta \var{=}\delta S{=}0.$ An eigenvalue-degeneracy of $\A$ would also imply a Landau-level quasidegeneracy, since the analysis of \s{sec:relatedegeneracies} applies to the special case $\delta S{=}0$.
+We answer this question in nearly the same vein as for nearly-degenerate orbits: the quantization rule for exactly-degenerate orbits\cite{topoferm} has the same form as \qq{eq:rule}{berryconn} with $\delta \var{=}\delta S{=}0.$ An eigenvalue-degeneracy of $\A$ would also imply a Landau-level quasidegeneracy, since the analysis of \s{sec:relatedegeneracies} applies to the special case $\delta S{=}0$.
 
 There is, however, a difference in the possible symmetry classes that apply to exactly-degenerate vs quasidegenerate orbits.
-In \s{sec:codimquasideg}, we restricted ourselves to symmetries  that map the magnetic moment  $\calm$ to itself (plus a gauge-dependent term[100page]), so that both terms in $\calh{=}\delta \var{+}B\calm$ transform consistently as scalars.
+In \s{sec:codimquasideg}, we restricted ourselves to symmetries  that map the magnetic moment  $\calm$ to itself (plus a gauge-dependent term\cite{100p}), so that both terms in $\calh{=}\delta \var{+}B\calm$ transform consistently as scalars.
 In the present context, this restriction is void because $\delta\var{=}0$, hence we \textit{also} allow for symmetries that invert the sign of $\calm$.
@@
 The former is exemplified by $T\inv$ symmetry, and the latter by $T\rot_{2z}$ (the composition of time reversal with a two-fold rotation about the field direction).
-For an exactly-degenerate orbit $\frako$ confined to a $\rot_{2z}$-invariant plane, the associated propagator $\A$ is unitarily equivalent to a special orthogonal matrix [AA,100page] with a single, tunable angle of rotation -- this provides an intuitive explanation for the unit codimension.
+For an exactly-degenerate orbit $\frako$ confined to a $\rot_{2z}$-invariant plane, the associated propagator $\A$ is unitarily equivalent to a special orthogonal matrix\cite{100p}\textbf{[AA]} with a single, tunable angle of rotation -- this provides an intuitive explanation for the unit codimension.
 
@@
 
-In \s{sec:qtznrules} we have presented a quantization rule [\qq{eq:rule}{berryconn}] that is applicable to both quasidegenerate ($0{<}\delta S{<}S$) orbits and exactly-degenerate ($\delta S{=}0$) orbits.
-This section explores the implication of this rule for quantum-oscillatory phenomena of the Schubnikov-de Haas (SdH) [SdH] and de Haas-van Alphen (dHvA) [dhva] types.
-In \s{sec:quantosc_equidis}, we present a generalized Lifshitz-Kosevich formula that inputs our rule and outputs quantum oscillations.
+In \s{sec:qtznrules} we have presented a quantization rule [\qq{eq:rule}{berryconn}] that is applicable to both nearly-degenerate ($0{<}\delta S{\ll}S$) orbits and exactly-degenerate ($\delta S{=}0$) orbits.
+This section explores the implication of this rule for quantum-oscillatory phenomena of the Schubnikov-de Haas (SdH)\cite{SdH} and de Haas-van Alphen (dHvA)\cite{dHvA} types.
+In \s{sec:quantosc_equidis}, we present a generalized Lifshitz-Kosevich formula\cite{lifshitz_kosevich,lifshitz_kosevich_jetp} that inputs our rule and outputs quantum oscillations.
 Applying this formula in the high-temperature regime, we will prove that  destructive interference of the fundamental quantum-oscillatory harmonic may  be tuned by at most one parameter in any symmetry class; this parameter may be the magnitude ($B$) of the magnetic field for quasidegenerate orbits, but not for exactly-degenerate orbits.
@@
 
-Lifshitz-Kosevich formulae[lifshitzkosevich] allow for a harmonic analysis of quantum oscillations, and have previously been derived for  exactly-degenerate orbits in symmetry class 1[rothII], with the generalization to all ten symmetry classes in Ref.
-[topoferm].
-A simple generalization of the derivation in [topoferm] extend the utility of these existing formulae to quasi-degenerate orbits of any symmetry.
+Lifshitz-Kosevich formula\cite{lifshitz_kosevich,lifshitz_kosevich_jetp} allow for a harmonic analysis of quantum oscillations, and have previously been derived for  exactly-degenerate orbits in symmetry class 1\cite{rothmag}, with the generalization to all ten symmetry classes in Ref.
+\onlinecite{topoferm}.
+A simple generalization of the derivation in \onlinecite{topoferm} extend the utility of these existing formulae to nearly-degenerate orbits.
 For example, the oscillatory component of the magnetization of 2D metals has the form
@@
 \end{equation}
-where the argument of the sine function involve quantities from our  quantization rule [\qq{eq:rule}{berryconn}]; $T$ is temperature and $\tau_{\sma{D}}$  the Dingle scattering lifetime.
+where the argument of the sine function involve quantities from our quantization rule [\qq{eq:rule}{berryconn}]; $T$ is temperature and $\tau_{\sma{D}}$  the Dingle scattering lifetime\cite{Dingle_collisions}.
 All the quantities on the right handside of Eq.\ (\ref{eq:LK}) are evaluated at the chemical potential.
 \q{eq:LK} corrects the analogous formula in Ref.
-[topoferm] by a factor of half.
+\onlinecite{topoferm} by a factor of half.
 
@@
 To prove this, we return to the canonical parametrization of the SU(2) component (${\cal \bar{A}}$) of $\A$ [cf.\ \q{s3}].
-The necessary and sufficient condition for $\delta \lambda{\equiv}\pi$ is that ${\cal \bar{A}}(r_1,r_2,r_3,r_4)$ has eigenvalues $+i$ and $-i$; the latter condition is equivalent to setting $r_1{=}0$ in \q{s3} -- a condition on a single parameter.\footnote{For an alternative proof,   $\delta \lambda{\equiv}\pi$ is equivalent to ${ \bar{\cal A}}{=}Ve^{i\sigma_z\pi/2}V^{-1}$ for some unitary $V\in U(2)$.
+The necessary and sufficient condition for $\delta \lambda{\equiv}\pi$ is that ${\cal \bar{A}}(r_1,r_2,r_3)$ has eigenvalues $+i$ and $-i$; the latter condition is equivalent to setting $r_1{=}0$ in \q{s3} -- a condition on a single parameter.\footnote{For an alternative proof,  $\delta \lambda{\equiv}\pi$ is equivalent to ${ \bar{\cal A}}{=}Ve^{i\sigma_z\pi/2}V^{-1}$ for some unitary $V\in U(2)$.
 The manifold associated to $\delta \lambda{\equiv}\pi$ is then the space of unitary matrices  that do not commute with $e^{i\sigma_z\pi/2}$.
@@
 The codimension is then obtained from deducting two from the total number (three)  of linearly-independent Hermitian generators  for U(2).
-This approach of determining codimension is similar to that in [JHNR].}
-
-For exactly-degenerate orbits, the single parameter to attain destructive interference might be the chemical potential (as illustrated for the quantum oscillations of Na$_3$Bi in [topoferm]) or the orientation of the magnetic field; however $\lambda_a$ is independent of the field magnitude ($B$), as explained in \s{sec:codimexactdeg}.
-In principle, one may account for linear-in-$B$ corrections to $\lambda_a$ at stronger fields, however a quantitative theory for such corrections only exists (thus far) for non-degenerate orbits.[rothII,fischbeck,niu,fuchs]
-
-For quasidegenerate orbits,  $\lambda_a$ is expandable as a Laurent series in $B$ with leading term $1/B$ [cf.\ \q{lambdasmallB}], hence $B$ can be tuned to attain destructive interference.
+This approach of determining codimension is similar to that in Ref.
+\textbf{[JHNR]}.}
+
+For exactly-degenerate orbits, the single parameter to attain destructive interference might be the chemical potential (as illustrated for the quantum oscillations of Na$_3$Bi in Ref.
+\onlinecite{topoferm}) or the orientation of the magnetic field; however $\lambda_a$ is independent of the field magnitude ($B$), as explained in \s{sec:codimexactdeg}.
+In principle, one may account for linear-in-$B$ corrections to $\lambda_a$ at stronger fields, however a quantitative theory for such corrections only exists (thus far) for non-degenerate orbits\cite{rothmag,fuchs_landau_2017,gao_zero-field_2017}.\textbf{[fischbeck]}
+
+For nearly-degenerate orbits, $\lambda_a$ is expandable as a Laurent series in $B$ with leading term $1/B$ [cf.\ \q{lambdasmallB}], hence $B$ can be tuned to attain destructive interference.
 The slow variation of $\lambda_a$ compared to the action $l^2S$ [cf.\ \app{sec:slowvariation}] implies a beating pattern for the fundamental harmonic.
@@
 
-Such beatings have been observed for semiconductor heterostructures[das,several more]; in some experiments,[das] the phase offset $\lambda_a$ [cf.\ \q{eq:LK}] has been measured and fitted phenomenologically to a Laurent series in $B$.[das] It has been appreciated that the leading-order term (${\sim}1/B$) originates from the zero-field splitting of orbits (due to spin-orbit coupling);[das] our contribution is a quantitative theory of the expansion coefficients of this Laurent series -- we have related the subleading term   $({\sim}B^0)$ to  a generalized Zeeman interaction, and higher-order terms to a competition between spin-orbit coupling and the Zeeman interaction [cf.\ \q{eq:Rashba-lambda}].
-As one application, one may extract the intervals (in $1/B$) between antinodes  for the Rashba 2DEG [by imposing $\delta \lambda{\equiv}\pi$ in \q{eq:Rashba-lambda}] and for the Rashba-Dresselhaus 2DEG [see the next \s{sec:quantosc_quasideg}].
+Such beatings have been observed for semiconductor heterostructures \textbf{[das,several more]}; in some experiments, \textbf{[das]} the phase offset $\lambda_a$ [cf.\ \q{eq:LK}] has been measured and fitted phenomenologically to a Laurent series in $B$.
+\textbf{[das]} It has been appreciated that the leading-order term (${\sim}1/B$) originates from the zero-field splitting of orbits (due to spin-orbit coupling);\textbf{[das]} our contribution is a quantitative theory of the expansion coefficients of this Laurent series -- we have related the subleading term  $({\sim}B^0)$ to a generalized Zeeman interaction, and higher-order terms to a competition between spin-orbit coupling and the Zeeman interaction [cf.\ \q{eq:Rashba-lambda}].
+As one application, one may extract the intervals (in $1/B$) between antinodes  for the Rashba 2DEG [by imposing $\delta \lambda{\equiv}\pi$ in \q{eq:Rashba-lambda}] and for the Rashba-Dresselhaus 2DEG (see \s{sec:quantosc_quasideg}).
 
@@
 \includegraphics[width=1.0\columnwidth]{qo.png}
-\caption{\textbf{[please redefine alpha and beta such that it has units of cm per s, in whole paper]} Quantum oscillations in the Rashba-Dresselhaus 2DEG.
+\caption{Quantum oscillations in the Rashba-Dresselhaus 2DEG.
 (a) Evolution of $\delta\lambda$ with respect to the inverse field for different values of $\beta$.
 The horizontal dashed line indicates $\delta\lambda=\pi$.
-For $\beta=3.0(10^{5}$cm/s$\cdot\hbar$), we have plotted -- in the upper panel of (b) -- the Landau levels at three $B$ values, as indicated by the vertical dashed lines in (a).
-The evolution of $\delta \lambda$ for  $\beta=3.0(10^{5}$cm/s$\cdot\hbar$ ) \textbf{[bracket is unconventional notation; try $3.0\times 10^5$ or $3.0\cdot 10^5$]} is given by a cyan-colored line indicated by a black arrow in (a); the three chosen $B$ values correspond approximately to  $\delta\lambda{=}0$, $\delta\lambda{=}\pi/2$ and $\delta\lambda{=}\pi$ respectively.
+For $\beta=3.0\times 10^{5}$cm/s, we have plotted -- in the upper panel of (b) -- the Landau levels at three $B$ values, as indicated by the vertical dashed lines in (a).
+The evolution of $\delta \lambda$ for $\beta=3.0\times 10^{5}$cm/s is given by a cyan-colored line indicated by a black arrow in (a); the three chosen $B$ values correspond approximately to  $\delta\lambda{=}0$, $\delta\lambda{=}\pi/2$ and $\delta\lambda{=}\pi$ respectively.
 Lower panel of (b) illustrates the saw-tooth oscillation of the chemical potential (at fixed electron density) corresponding to the upper panel.
-Other parameters chosen in (b): $m{=}0.076m_0$, $\alpha{=}7.5(10^{5}$cm/s$\cdot\hbar$) and $E=0.4$eV.
+Other parameters chosen in (b): $m{=}0.076m_0$, $\alpha{=}7.5\times10^{5}$cm/s and $E=0.4$eV.
 \label{fig:qo}}
@@
 
-\subsection{Schubnikov-de Haas effect for quasidegenerate orbits in symmetry class 1-4}\label{sec:quantosc_quasideg}
-
-Let us focus on quasidegenerate orbits for which a single parameter ($B$) can be tuned to attain $\delta \lambda{\equiv}0$ (equivalently, to attain a Landau-level quasidegeneracy).
+\subsection{Schubnikov-de Haas effect for nearly-degenerate orbits in symmetry class 1-4}\label{sec:quantosc_quasideg}
+
+Let us focus on nearly-degenerate orbits for which a single parameter ($B$) can be tuned to attain $\delta \lambda{\equiv}0$ (equivalently, to attain a Landau-level quasidegeneracy).
 These orbits lie in symmetry classes 1 to 4; in classes 1 and 2 further assumptions must be made about the symmetry representation, as explained in \s{sec:codimquasideg} and summarized in \tab{table:codimension}.
@@
 We propose a signature for tunable quasidegeneracies in the  Schubnikov-de Haas effect at fixed particle density $n_e$, low temperature ($k_BT{\ll}\var_c$) and weak disorder ($\omega_c\tau_{\sma{D}}{\gg}1$).
-In this regime, it is known that minima of the longitudinal conductivity occur at discrete fields (denoted $B_{\nu}$)  where the filling is integer-valued;[vinter] the period of quantum oscillations is determined by the total density $n_e$ through $1/B_j{-}1/B_{j+1}{=}e/n_eh$.
+In this regime, it is known that minima of the longitudinal conductivity occur at discrete fields (denoted $B_{\nu}$)  where the filling is integer-valued\cite{vinter_resolution_1980}; the period of quantum oscillations is determined by the total density $n_e$ through $1/B_j{-}1/B_{j+1}{=}e/n_eh$.
 As $B$ increases through $B_j$, a Landau level is completely depopulated, leading to a periodic drop in the chemical potential ($\mu$) by the energy gap  between Landau levels, as illustrated in \fig{fig:qo}(b).
@@
 Our contribution is the exhaustive  identification of symmetry classes (1 to 4) for which such a crossover will occur.
-In particular, we are proposing that the crossover occurs for the Rashba-Dresselhaus 2DEG [cf.\ \q{hamRD}], whose quasidegenerate orbits fall into class 3.
+In particular, we are proposing that the crossover occurs for the Rashba-Dresselhaus 2DEG [cf.\ \q{hamRD}], whose nearly-degenerate orbits fall into class 3.
 For this model,  Fig.\ \ref{fig:qo}(a) plots $\delta \lambda$ vs $1/B$ for various choices of the Dresselhaus coupling $\beta$.
@@
 
-We have extended the semiclassical theory of Landau quantization to describe  quasidegenerate cyclotron orbits, i.e., orbits which are split in $\bk$-space with a differential area ($\delta S$) that is much less than their average area.
-The quantization rule for two quasidegenerate orbits is summarized in \qq{eq:rule}{berryconn}, and may be applied to spin-degenerate orbits which are split by spin-orbit coupling or by breaking of a crystalline point-group symmetry.
+We have extended the semiclassical theory of Landau quantization to describe nearly-degenerate cyclotron orbits, i.e., orbits which are split in $\bk$-space with a differential area ($\delta S$) that is much less than their average area.
+The quantization rule for two nearly-degenerate orbits is summarized in \qq{eq:rule}{berryconn}, and may be applied to spin-degenerate orbits which are split by spin-orbit coupling or by breaking of a crystalline point-group symmetry.
 The former type of splitting is exemplified by  our case study of the Rashba 2DEG (with arbitrarily-oriented field and addition of Dresselhaus spin-orbit coupling).
@@
 The subleading phase corrections ($\lambda_1,\lambda_2$) in our quantization rule  [\q{eq:rule}] encode the dynamical correction due to the splitting of  orbits, as well as a generalized two-band Zeeman interaction.
-Where $\lambda_1{=}\lambda_2$ mod $2\pi$, there exist a number (of order one) paired Landau levels which are either exactly spin-degenerate, or nearly spin-degenerate in the sense of \qq{llquasideg}{llquasidegB}.
-\textbf{[bonus:schematic picture to illustrate of order one paired LLs near degeneracy of lambda (might introduce picture earlier, in section where we introduce quasidegeneracy)]} Such paired Landau levels have been referred to as \textit{quasidegenerate}.
-
-For each of the five symmetry classes of near-degenerate orbits \textbf{[please replace quasidegenerate orbit with near-degenerate orbit, however keep quasidegenerate LL.
-One reason: quasidegenerate LL includes exactly degenerate; near-degenerate orbit has nonzero splitting]},  we have determined the number of tunable real parameters needed to attain a Landau-level quasidegeneracy;  these numbers may be viewed as symmetry-dependent  measures of Landau-level repulsion.
+$\lambda_1{=}\lambda_2$ mod $2\pi$, there exist a number (of order one) paired Landau levels which are either exactly spin-degenerate, or nearly spin-degenerate in the sense of \qq{llquasideg}{llquasidegB}, as illustrated in Fig.
+\ref{fig:LL}.
+Such paired Landau levels have been referred to as \textit{quasidegenerate}.
+
+For each of the five symmetry classes of nearly-degenerate orbits, we have determined the number of tunable real parameters needed to attain a Landau-level quasidegeneracy; these numbers may be viewed as symmetry-dependent measures of Landau-level repulsion.
 We have referred to these numbers as \textit{symmetry-constrained codimensions}.
-Depending on the symmetry class and representation, the codimension ranges from $0,1,2$ to $3$, as summarized in the right-most column of Tab.\ \ref{table:codimension}.
+Depending on the symmetry class and representation, the codimension ranges from 0, 1, 2 to 3, as summarized in the right-most column of Tab.\ \ref{table:codimension}.
 
 If the codimension is unity, it is possible to tune the magnitude of the field to attain Landau-level quasidegeneracies; the implications for this tunability -- in the Schubnikov-de Haas effect -- are discussed in \s{sec:quantosc_quasideg}.
-If the codimension is two, an additional experimentally tunable parameter is needed: e.g., the orientation of the field[magic angle], or the bias voltage in tunneling spectroscopy[cite stm papers].
-
-With the inclusion of nonsymmorphic space-group symmetries, it is not uncommon to find energy bands which are (nearly) four-fold degenerate.[michel and zak,hourglass,Barry] This motivates a  generalization of our rule -- for any number of near-degenerate orbits -- that is presented in  \app{app:quantizationruleproof}.
+If the codimension is two, an additional experimentally tunable parameter is needed: e.g., the orientation of the field\cite{yakovenko_angular_2006}, or the bias voltage in tunneling spectroscopy\textbf{[cite stm papers]}.
+
+With the inclusion of nonsymmorphic space-group symmetries, it is not uncommon to find energy bands which are (nearly) four-fold degenerate\cite{michel_elementary_2001,wang_hourglass_2016,bradlyn_topological_2017}.
+This motivates a generalization of our rule -- for any number of nearly-degenerate orbits -- that is presented in \app{app:quantizationruleproof}.
 The symmetry-constrained codimensions in the more general case is left to future investigations.
@@
 
-\textbf{[confusing issue to settle: five vs ten becomes confusing if we now say that our topofermiology table applies to all ten classes of quasidegenerate orbits.
-We may have to modify.][generalization to wilson loop; explains movable crossings in recent works]}
-\red{[
-Let's say only five rows of both tables are useful for quasidegenerate orbits.
-This is more accurate since you wrote explicitly the symmetry constraints in terms of sewing matrix in topofermi.
-These symmetry constraints for the five unticked classes in the topofermi table are not applicable to quasidegenerate orbits.
-We should just say $\det \A=1$ for the three unticked self-constrained classes for quasidegenerate orbits.
-This conclusion comes from the fact that we defined $\delta \epsilon$ to be traceless, rather than symmetry constraints expressed with sewing matrix in the topofermi table.
-]}
-
-%.
-A nontrivial implication of our theory is the determination of symmetry constrained codimension, summarized in tab I.
-The codimension is the number of tunable real parameters needed to attain a Landau-level quasidegeneracy.
-Tunable parameters: B, orientation of B, bias voltage.
-The first is not applicable to exactly-degenerate orbits.
-%For spin-split bands, $\lambda$ depends strongly on the $B$ field for quasidegenerate orbits; for degenerate orbits, the $B$-dependence of $\lambda$ is relatively weaker, i.e., of higher power in the small parameter $B$ [Roth, Niu, Fuchs].
-A more useful tuning parameter in the latter case would be the bias voltage in tunneling spectroscopy experiments.
-
-%Application to $D>4$.
-Not uncommon to find spin-degenerate bands (in centrosymmetric solids) which are quasi-four-fold degenerate.
-\red{[I introduced in the first paragraph of App.
-B how D=4 is useful]}
-
-%\red{[Maybe talk about codimension for $D>2$. However, I have no idea what that may be. I don't even find a good parametrization of SU(3).]}
-
-% Our conclusion that spin-degenerate Landau levels may be obtained by tuning a single parameter  may seem to contradict a theorem by Wigner and von Neumann that states the codimension of degeneracies of a complex Hermitian matrix is three; in our context this matrix is the Peierls-Onsager Hamiltonian whose spectrum corresponds to Landau levels.
-This theorem leads to the famous ``no-crossing rule" in physics, which states that generically there are no crossings of energy levels of Hamiltonians defined over  one- or two-dimensional parameter spaces.
-To reconcile our findings with this theorem, one should recognize that any energy level obtained from a semiclassical quantization rule is only asymptotically accurate (in powers of $B$, and the spin-orbit coupling).
-A degeneracy obtained from this approximation scheme may in principle be split on a scale of order $\var_c^2/E$ or $\var_c\var_s/E$; in principle, the approximation can be improved order by order.
-This distinction between asymptotically-accurate and exact degeneracies  affords a reconciliation with the Wigner-von Neumann theorem, but should  not typically be resolvable in experiments  due to the broadening effects of  temperature and disorder-induced scattering.
-
-%In summary, we have developed a theory to calculate landau levels in the case of quasidegenerate orbits.
-This theory is asymtotically correct with small $k$ space splitting and works equally well if there are band touchings between the two quasidegenerate orbits.
-Aperiodic beating pattern in quantum oscillation is predicted to be observed in such systems.
+\red{For two fold exactly-degenerate orbits, three out of five symmetry classes feature $\lambda_1+\lambda_2=0$ with the assumption of SOC can be continuously tuned to zero without changing the degree of degeneracy.
+Although these three symmetry classes do not impose constraints on nearly-degenerate orbit, due to the traceless spin splitting Hamiltonian matrix, $\lambda_1+\lambda_2=0$ remains true for nearly-degenerate orbits.}
+
+\red{Symmetry constrained codimension discussed in the current work is useful even beyond magnetotransport.
+Specifically, as a special case of Eq.
+({\ref{eq:prop}}) by ignoring Zeeman interaction, Wilson loop share the same symmetry constrained codimension presented in Tab.
+\ref{table:codimension}.
+This observation may be helpful in explaining movable crossings in some Wilson loop spectra \textbf{[cite something]}.}
+
+\red{Nontrivial nature of Landau quantization for nearly-degenerate orbits originates from the field induced hybridization of nearly degenerate bands.
+With the recent development of high magnetic field instrument, we envision quantization rule presented in the current work would be more and more relevant to magnetotransport in future experiments.}
 
@@
 
-\section{Proof of quasidegenerate quantization rule\label{app:quantizationruleproof}}
+\section{Proof of nearly-degenerate quantization rule\label{app:quantizationruleproof}}
 
@@
 \ref{app:revieweffham}).
-This proof is applicable to $D$-fold quasidegenerate bands, with $D>1$.
+This proof is applicable to $D$-fold nearly-degenerate bands, with $D>1$.
 Although less common than $D=2$, $D>2$ is relevant in some materials.
-For example, bands at $k_z=\pi$ plane of $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$-symmetric material with negligible SOC are four fold (quasi)degenerate.
+For example, bands at $k_z=\pi$ plane of $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$-symmetric material with negligible SOC are four fold (nearly-)degenerate.
 
 As stated in the main text, our start point is a decomposition of the Hamiltonian $\hat{H}$ into $\hat{H_0}$ and a perturbation $\delta\hat{H}=\eta\hat{H}_1$, with $\eta$ a dimensionless small parameter.
-The quasidegeneracy originates from $\zeta\hat{H}$ breaking the exactly $D$-fold degenerate bands of $\hat{H_0}$.
-For 2-fold quasidegeneracy, $\eta$ can be chosen as $\delta S/S$ in the main text.
-
-The effective Hamiltonian $\effH$ is now governed by two small parameters: one is $1/l^2S$ due to the smallness of the field; one is $\eta$ due to the assumption of quasidegeneracy.
+The nearly-degeneracy originates from $\eta\hat{H}$ breaking the exactly $D$-fold degenerate bands of $\hat{H_0}$.
+For 2-fold nearly-degeneracy, $\eta$ can be chosen as $\delta S/S$ in the main text.
+
+The effective Hamiltonian $\effH$ is now governed by two small parameters: one is $1/l^2S$ due to the smallness of the field; one is $\eta$ due to the assumption of nearly-degeneracy.
 The zeroth order (in the sense of both small parameters) Hamiltonian is now $\effH_0=\epsilon_0(\bK)$, with $\epsilon_0(\bK)$ band structure of $\hat{H}_0$.
@@
 
-Similar to what is done in Ref. [100page], we seek the solution to the Schr\"odinger equation using the following multicomponent wave function ansatz
+Similar to what is done in Ref. \onlinecite{100p}, we seek the solution to the Schr\"odinger equation using the following multicomponent wave function ansatz
 \begin{equation}
@@
 Following section V A 2 of Ref.
-[100page],:
+\onlinecite{100p},:
 \e{
@@
 \end{equation}
-Eq. ({\ref{eq:prop}}) can be obtained by solving boundary conditions at turning points.
-
-Besides the effective Hamiltonian approach described above, semiclassical wave packet theory has been developed in coupled bands[Niucoupled].
-It is possible that quantization rule expressed in \qq{eq:rule}{berryconn} can be derived by a `requantization' [NiuRMP] of the wave packet theory.
-
-\section{Consistency conditions for the quasidegenerate quantization rule}\label{sec:slowvariation}
-
-The following are consistency conditions for the quasidegenerate quantization rule:
+Eq.
+({\ref{eq:prop}}) can be obtained by solving boundary conditions at turning points.
+Eq.
+({\ref{eq:prop}}) is gauge invariant under a gauge transformation since the cyclotron orbit is closed [See Eq.
+(133) of Ref.
+\onlinecite{100p}].
+
+Besides the effective Hamiltonian approach described above, semiclassical wave packet theory has been developed in coupled bands\cite{culcer_coherent_2005}.
+It is possible that quantization rule expressed in \qq{eq:rule}{berryconn} can be derived by a `requantization' of the wave packet theory\cite{xiao_berry_2010}.
+
+\section{Consistency conditions for the nearly-degenerate quantization rule}\label{sec:slowvariation}
+
+The following are consistency conditions for the nearly-degenerate quantization rule:
 \e{ |l^2S| \gg |\lambda_a|,\, \left|l^2\p{S}{E}\right| \gg \left|\p{\lambda_a}{E}\right|,\, \left|S\right| \gg \left|\p{\lambda_a}{l^2}\right|.} 
 Due to the latter two inequalities, we shall refer to $\lambda_{a}$ as \textit{slowly-varying} (with respect to $E$ and $B$), in comparison with the rapidly-varying $l^2S$.
-To appreciate the difference in scales, consider that for $\lambda_a$ to change by $2\pi$ due to a variation $l^2$ (at fixed energy), we estimate [in the weak-field regime; cf.\ \q{phaseindependentorbit}] that $l^2$ must change on the scale of $2\pi/\delta S$; this scale is much greater than the period of quantum oscillations ($T_{1/B}{:}{=}2\pi/ S$), by our assumption of quasidegeneracy.
+To appreciate the difference in scales, consider that for $\lambda_a$ to change by $2\pi$ due to a variation $l^2$ (at fixed energy), we estimate [in the weak-field regime; cf.\ \q{phaseindependentorbit}] that $l^2$ must change on the scale of $2\pi/\delta S$; this scale is much greater than the period of quantum oscillations ($T_{1/B}{:}{=}2\pi/ S$), by our assumption of nearly-degeneracy.
 Analogously, for $\lambda_a$ to vary by $2\pi$ due to a variation of $E$ (at fixed field) by $\delta E$, we estimate [from \q{phaseindependentorbit}] that $\delta E {\sim} 2\pi/l^2 (\partial \delta S/\partial E)$, which is generically much larger than the cyclotron energy $\epsilon_c{=}2\pi/l^2 (\partial  S/\partial E)$.
@@
 
-This appendix demonstrates that, if a degeneracy of $\cala$ [$e^{i\lambda_+}{=}e^{i\lambda_-}$] occurs at $(\bar{E},\bar{B})$, there exists two Landau levels in close proximity to $(\bar{E},\bar{B})$ which satisfy the quasidegeneracy conditions defined in \qq{llquasideg}{llquasidegB}.
+This appendix demonstrates that, if a degeneracy of $\cala$ [$e^{i\lambda_+}{=}e^{i\lambda_-}$] occurs at $(\bar{E},\bar{B})$, there exists two Landau levels in close proximity to $(\bar{E},\bar{B})$ which satisfy the nearly-degeneracy conditions defined in \qq{llquasideg}{llquasidegB}.
 
@@
 
-In this appendix, we expose mathematical details of symmetry analysis of the quasidegenerate propagator $\A$ and derive symmetry constrained codimension of degeneracy manifold.
+In this appendix, we expose mathematical details of symmetry analysis of the nearly-degenerate propagator $\A$ and derive symmetry constrained codimension of degeneracy manifold.
 We restrict our analysis to two-by-two $\A$.
@@
 where $\A[\bk_f\leftarrow \bk_i]$ is a segment of the propagator from $\bk_i$ to $\bk_f$ along the cyclotron orbit.
-$e^{i\phi}$ is a phase factor that appears for $g$ that is a nonsymmorphic element; however this phase always drops out[100page] for closed orbits and will be neglected in the subsequent analysis.
+$e^{i\phi}$ is a phase factor that appears for $g$ that is a nonsymmorphic element; however this phase always drops out\cite{100p} for closed orbits and will be neglected in the subsequent analysis.
 
@@
 H_{R}(\boldsymbol{K})=&\frac{\hbar^2}{ml^2}(a^{\dagger}a+\frac{1}{2})
-\\&+\sqrt{2}\alpha l^{-1}\left(\begin{array}{cc}
+\\&+\sqrt{2}\hbar\alpha l^{-1}\left(\begin{array}{cc}
 0 & -ia^{\dagger}\\

### 2018-10-03 paper.tex
Updates from ShareLaTeX

@@
 
-\renewcommand{\topfraction}{.85}
-\renewcommand{\bottomfraction}{.7}
-\renewcommand{\textfraction}{.15}
-\renewcommand{\floatpagefraction}{.66}
-\renewcommand{\dbltopfraction}{.66}
-\renewcommand{\dblfloatpagefraction}{.66}
-\setcounter{topnumber}{9}
-\setcounter{bottomnumber}{9}
-\setcounter{totalnumber}{20}
-\setcounter{dbltopnumber}{9}
+\renewcommand{\topfraction}{1}
+\renewcommand{\bottomfraction}{1}
+\renewcommand{\textfraction}{0.1}
+\renewcommand{\floatpagefraction}{1}
+\setcounter{topnumber}{3}
+\setcounter{bottomnumber}{3}
 
@@
 
-\title{Landau quantization of nearly-degenerate bands}
+\title{Landau quantization of nearly degenerate bands}
 
@@
 We introduce a quantization rule for Landau levels of nearly-degenerate orbits whose differential area ($\delta S$) in $\bk$-space is much smaller than their average area $S$.
-The splitting of two nearly-degenerate orbits commonly originate from spin-orbit coupling, or by the breaking of a crystalline point-group symmetry.
+The splitting of two nearly-degenerate orbits commonly originates from spin-orbit coupling, or from the breaking of a crystalline point-group symmetry.
 By treating both $\delta S/S$ and $1/l^2S$ ($l$ being the magnetic length) as small parameters with finite ratio $l^2\delta S$, our perspective diverges from and generalizes previous semiclassical theories.
@@
 In the absence of crystalline point-group symmetries, three tunable real parameters are needed to attain a spin-degeneracy between two Landau levels; we have exhaustively identified all symmetry classes of orbits for which this number is reduced from three.
-In particular, only one parameter is needed for rotational-symmetric orbits; this parameter may be the magnitude \textit{or} orientation of the field, or the bias voltage in tunneling spectroscopy.
-An implication of single-parameter tunability is a smooth crossover between period-doubled and -undoubled quantum oscillations in the Schubnikov-de Haas effect.
+In particular, only one parameter is needed for rotational-symmetric orbits; this parameter may be the magnitude or orientation of the field, or the bias voltage in tunneling spectroscopy.
+A signature of single-parameter tunability is a smooth crossover between period-doubled and -undoubled quantum oscillations in the low-temperature, Schubnikov-de Haas effect.
 We demonstrate the utility of our quantization rule, as well as the tunability of Landau-level degeneracies, for the Rashba two-dimensional electron gas -- subject to an arbitrarily oriented magnetic field, and possibly augmented by the Dresselhaus spin-orbit interaction.
@@
 
-%, and the angular magnetoresistance oscillations of semiconductor bilayer heterostructures.
-
-% We demonstrate the utility of our rule for quasidegenerate orbits which  touch at isolated (type-II Dirac) points, as well as for orbits which (nearly) touch at \emph{all points} along their trajectory.
-In the former case, a wavepacket follows each spin-orbit-split orbit adiabatically, except at localized regions where quantum  tunneling (known as magnetic breakdown) is appreciable; in the latter case, adiabaticity is irrelevant and the orbits are completely reconstructed by the field.
-
-%Magnetic breakdown is the phenomenon of quantum tunneling between semiclassical orbits; conventionally, the tunneling region is localized to \emph{isolated}  points   in momentum space, as exemplified by saddle- or Dirac points.
-Here, we introduce a qualitatively distinct form of tunneling that is delocalized over the entire orbit.
-Such nonlocal breakdown occurs wherever two orbits nearly touch at \emph{all points} along their trajectory, as exemplified in solids by the spin-orbit splitting of spin-degenerate energy bands.
-We formulate the Bohr-Sommerfeld quantization rules that are predictive of Landau levels in the presence of nonlocal breakdown.
-We propose the experimental signature to be an aperiodic beating in quantum oscillations of the magnetization or resistivity, which contrasts with the periodic beating that is well-known for two decoupled orbits.
-
-%By accounting for all dynamical and geometric phases induced by this spin-splitting, our work extends the known Onsager-Lifshitz-Roth rules for nondegenerate and degenerate orbits.
-
 \maketitle
@@
 
-%Semiclassical theory is predictive of Landau levels for solids in a weak magnetic field $B$.
-This theory has been extended to describe quantum tunneling between two orbits which intersect at \emph{isolated} points.
-Examples of such isolated points include saddle and type-II Dirac points, where tunneling respectively occurs between orbits of the same band (known as intraband magnetic breakdown) and between orbits of distinct bands (interband breakdown).
-As $B {\rightarrow} 0$, tunneling is localized to an arbitrarily small neighborhood of such isolated points, and occurs with half probability for the saddlepoint, and with unit probability for the  Dirac point.\footnote{If orbits nearly intersect, tunneling occurs with a probability that asymptotically $\sim e^{-c/B}$, where $c$ is field-independent;[Blount] as a  rule of thumb, this probability ${\sim} 1$ if the \emph{minimal} separation of the two orbits in $\bk$-space is of order of the inverse magnetic length.}
-
-%This work introduces a qualitatively distinct form of tunneling that occurs between two orbits which nearly touch at \emph{all} points along their trajectory.
-This is exemplified in solids by energy bands that are split on a scale $\Delta$ due to spin-orbit coupling, as illustrated in Fig.
-\ref{fig:orbits} for the Rashba model of a two dimensional (2D) electron gas.
-Generally, the probability of tunneling on any interval of the orbit in reciprocal space \emph{vanishes} in proportion with the length of the interval.
-Yet the net probability of tunneling over the entire orbit is generically ${\sim} 1$, if $\Delta$ is of order the cyclotron energy.
-Such tunneling that is delocalized over the entire orbit may be referred to as nonlocal breakdown, in contrast with the localized breakdown that occurs at saddle and Dirac points.
-
-%In this work, we study quasidegenerate orbits and formulate Bohr-Sommerfield quantization rule for them.
-We find the tunneling between the orbits can be described by a propagator and compare the quantization rule to Landau levels from exact diagonalization.
-Finally, we discuss experimental signatures of such tunneling.
-
-In the absence of magnetic breakdown, semiclassical quantization rules are well-known for Landau levels of  both nondegenerate [Onsager, Lifshitz] and degenerate [Roth, Mikitik, Topoferm, 100page] energy bands.
-Our work generalizes these rules to nearly-degenerate bands, whose orbits are split in $\bk$-space with a differential area  $\delta S$ that is much less than the average area $S$ of the orbits; we shall refer to $\delta S/S{\ll}1$ as the \textit{near-degeneracy} condition.
+Semiclassical quantization rules are well-known for the Landau levels of  both nondegenerate\cite{Onsager,lifshitz_kosevich,lifshitz_kosevich_jetp} and exactly-degenerate\cite{rotheffham,rothmag,topoferm,100p,Mikitik_quantizationrule} energy bands; the latter is exemplified by the spin-degenerate bands of centrosymmetric solids.
+These rules become increasingly accurate as the area of the cyclotron orbit becomes much larger than the inverse square of the magnetic length $l{=}\sqrt{\hbar/eB}$.
+
+Our work generalizes these rules to the Landau quantization of nearly-degenerate bands, whose cyclotron orbits are split in $\bk$-space with a differential area  $\delta S$ that is much less than their average area $S$; $\delta S/S{\ll}1$ shall be referred to as the \textit{near-degeneracy} condition.
 Nearly-degenerate orbits commonly originate from the spin-orbit-splitting of energy bands, as exemplified by a two dimensional electron gas (2DEG) with Rashba spin-orbit coupling:
@@
 \end{equation}
-At energies much greater than $m\alpha^2$, the differential area of the two spin-orbit-split orbits [see Fig.
-\ref{fig:orbits}(a)] is much smaller than their average area:\footnote{The expressions for $\delta S$ and $S$ in \q{deltaSvsS} are asymptotically valid for $E{\gg}m\alpha^2$.}
-\e{\delta S = 4\pi m \alpha k_E/\hbar\ll S =\pi k_E^2; \;\; k_{E}:=\f{\sqrt{2m E}}{\hbar} .\label{deltaSvsS}}
-$S$ is equivalently the area of the circular, constant-energy contour in the absence of spin-orbit coupling ($\alpha{=}0$).
-
-Semiclassical quantization rules work in semiclassical regime where magnetic length $l=\sqrt{\hbar/eB}$ is much larger than characteristic length of cyclotron motion in $\bk$-space, i.e., $1/l^2 S\ll 1$.
-This condition is assumed by previous semiclassical theories.
-[Kohn, Blount, Roth, Wannier, Fredkin, Niu, Mikitik, topoferm, 100page] As a generalization, we will treat $\delta S/S$ as an additional small parameter, while keeping the ratio $l^2\delta S$ finite.
-
-$(l^2\delta S)^{-1}$ is a measure of the field-induced hybridization of the nearly-degenerate orbits, and shall be called the hybridization parameter. 
-In the regime that $l^2\delta S$ is much greater than the Zeeman interaction, we expect that the Onsager-Lifshitz quantization rules apply independently to the two concentric (but decoupled) orbits.
-In the opposite regime, we should recover the known quantization rule for degenerate orbits.
-[topoferm, 100p, roth, mikitik] Our goal is to present a unifying rule that interpolates smoothly between the two known regimes.
+As illustrated in Fig.\ \ref{fig:orbits}(a), the near-degeneracy condition is satisfied at energies much greater than $m\alpha^2$:\footnote{The expressions for $\delta S$ and $S$ in \q{deltaSvsS} are asymptotically valid for $E{\gg}m\alpha^2$.}
+\e{\delta S = 4\pi m \alpha k_E/\hbar\ll S =\pi k_E^2; \;\; k_{E}:=\f{\sqrt{2m E}}{\hbar}.\label{deltaSvsS}}
+$S$ is equivalently the area of the  constant-energy contour in the absence of spin-orbit coupling ($\alpha{=}0$).
+
+\begin{figure}
+\includegraphics[width=0.9\columnwidth]{orbits.png}
+\caption{(a) Solid (resp.\ dashed) lines illustrate the band dispersion of an electron gas with (resp.\ without) Rashba spin-orbit coupling.
+The oriented circles illustrate the spin-orbit-split orbits for a magnetic field pointing to $-z$ direction.
+(b) The zeroth-order orbit $\frako_0$ is indicated by a dashed circle with area $S$; $\delta S$ is the differential area  between two spin-orbit-split orbits.
+The spin texture is indicated by purple arrows.\label{fig:orbits}}
+\end{figure}
+
+By treating both $\delta S/S$ and $1/l^2S$  as small parameters with finite ratio $l^2\delta S$, our perspective diverges from and generalizes previous semiclassical theories\cite{kohn_effham,blount_effham,rotheffham,wannier_fredkin,gao_zero-field_2017,topoferm,100p,Mikitik_quantizationrule} which have only a single, small parameter ($1/l^2S$).
+$1/l^2\delta S$ measures the hybridization of nearly-degenerate orbits by the Zeeman interaction.
+In the regime $l^2\delta S{\gg}1$, the Onsager-Lifshitz quantization rules apply independently to  two concentric (but decoupled) orbits.
+In the opposite regime $l^2\delta S{\ll}1$, the spin-orbit splitting of energies is negligible, and we may then apply the known quantization rule for exactly-degenerate bands\cite{rotheffham,rothmag,topoferm,100p,Mikitik_quantizationrule}.
+The goal of this work is to formulate a unifying rule that interpolates smoothly between these two known regimes; such a rule is presented in \s{sec:qtznrules}.
+
+In \s{sec:Rashba}, we demonstrate the utility of this rule for the Rashba 2DEG with an arbitrarily-oriented magnetic field, and possibly augmented by the Dresselhaus spin-orbit coupling.
+A sufficiently strong in-plane field not only moves the Dirac point but tilts the Dirac cone over -- into a type-II Dirac point\cite{soluyanov_type-ii_2015}.
+In \s{sec:inplanezeeman}, we investigate the Landau-Zener tunneling dynamics that occur in the vicinity of a II-Dirac point; in particular, we will critically evaluate a recent claim\cite{obrien_magnetic_2016} of perfect Klein tunneling at the energy of the Dirac point.
+
+A symmetry analysis (cf.\ \s{sec:llquasideg}) of our quantization rule allows us to determine how many tunable parameters are needed to attain a (pseudo-)spin degeneracy between two Landau levels.
+This degeneracy is exact in symmetry classes where Landau levels are distinguishable by different quantum numbers; absent such quantum numbers, it is still possible for the repulsion between two Landau levels to be anomalously small -- this notion of a Landau-level quasidegeneracy is formulated in \s{sec:relatedegeneracies}.
+Due to a rotational symmetry of the Rashba-Dresselhaus 2DEG, we find that only a single tunable parameter is needed to attain a Landau-level quasidegeneracy (cf.\ \s{sec:ctsrot}); this parameter can be the magnitude or orientation of the field, or the bias voltage in tunneling spectroscopy.
+
+In \s{sec:quantosc_quasideg}, we propose  the signature of single-parameter tunability in the low-temperature Schubnikov-de Haas effect\cite{SdH}: a smooth crossover between period-doubled and -undoubled quantum oscillations.
+For a harmonic analysis of  quantum oscillations, we present in \s{sec:quantosc_equidis} a generalized Lifshitz-Kosevich formula that inputs our quantization rule and outputs harmonics.
+In particular, we show that destructive interference of the fundamental harmonic is always tunable by a single parameter, leading to a beating pattern in the high-temperature quantum oscillations; the beating nodes recur \textit{aperiodically} in $1/B$, due to a competition between spin-orbit splitting and the Zeeman interaction.
+
+We conclude in \s{sec:discussion} by summarizing  the technical results of this work, highlighting certain key equations, and presenting an outlook for future investigations.
 
@@
 
-Let us apply a magnetic field, and first consider the spin-degenerate Landau levels obtained by neglecting both $\delta H$ and the Zeeman splitting.
+Let us apply a magnetic field, and first consider the spin-degenerate Landau levels obtained by neglecting both $\delta \hat{H}$ and the Zeeman splitting.
 In the  semiclassical description,  we are interested in  field-induced dynamics within a low-energy degenerate band of $\hat{H}_0$ with  dispersion $\var(\bk)$, e.g., $\var(\bk){=}\hbar^2 k^2/2m{+}\order(k^4)$ in the Rashba model.
@@
 \ref{fig:orbits}(b)]; this contour, equipped with an orientation given by the equation of motion ($ \hbar dk_{\alpha}/dt {=} \lmt \epsilon_{\ab}\partial \var/\partial k_{\beta} $, with $\epsilon_{xy}{=}{-}\epsilon_{yx}{=}1$), shall be referred as the zeroth-order orbit $\frako_0$.
-In this work, we focus only on closed orbits which do not wrap
-non-contractibly around the Brillouin torus.
-
-%(in $\bk$ space)  defined at zero spin-orbit coupling [$\alpha{=}0$; see Fig.
-\ref{fig:orbits}(b)].
-This cyclotron motion obeys the equation of motion:  $ \hbar dk_{\alpha}/dt = \lmt \epsilon_{\ab}\partial \var/\partial k_{\beta} $, with $\epsilon_{xy}{=}{-}\epsilon_{yx}{=}1$.
-The spin-orbit-free band contour, equipped with an orientation given by the equation of motion, shall be referred as the zeroth-order orbit $\frako_0$.
-In this work, we focus only on orbits which are closed, i.e., orbits that do not cross the Brillouin-zone edge.
-
-%$T_c:=2\pi\hbar/\var_c$
-
-The quantization rule for Landau levels reflects the single-valuedness of the semiclassical (WKB) wavefunction over $\frako_0$,\textbf{[Berry, Mount]} i.e.,  the phase accumulated by an electron (over one cyclotron period $T_c$) is an integer multiple of $2\pi$: $(l^2S(E){+}\gamma)/2\pi{\in}\Z$.
-The leading-order phase   is the classical action $l^2S{:}{=}{-}l^2\int_{0}^{T_c} k_x \dot{k}_y dt$  corresponding to $(K_x,K_y)$;\textbf{[Mount]} $S$ has a dual interpretation as the signed area (in $\bk$-space) enclosed by $\frako_0$, as illustrated in Fig.
+In this work, we focus only on closed orbits which do not wrap non-contractibly around the Brillouin torus.
+
+The quantization rule for Landau levels reflects the single-valuedness of the semiclassical (WKB) wavefunction\cite{berry_mount_review} over $\frako_0$, i.e.,  the phase accumulated by an electron (over one cyclotron period $T_c$) is an integer multiple of $2\pi$: $(l^2S(E){+}\gamma)/2\pi{\in}\Z$.
+The leading-order phase   is the classical action $l^2S{:}{=}{-}l^2\int_{0}^{T_c} k_x \dot{k}_y dt$; $S$ has a dual interpretation as the signed area (in $\bk$-space) enclosed by $\frako_0$, as illustrated in Fig.
 \ref{fig:orbits}(b).
-$\gamma$ is a subleading Maslov correction \textbf{[caustic]} that generally equals $\pi$ times the rotation number $r$ of $\frako_0$ (i.e., the number of rotations made by the tangent vector over one cycle)\cite{100p}; for orbits that are deformable to a circle,  $r{=}{\pm} 1$.
+$\gamma$ is a subleading Maslov correction\cite{keller1958} that generally equals $\pi$ times the rotation number $r$ of $\frako_0$ (i.e., the number of rotations made by the tangent vector over one cycle)\cite{100p}; for orbits that are deformable to a circle,  $r{=}{\pm} 1$.
 In the zeroth-order  solution, all Landau levels are spin-degenerate with a level spacing
@@
 
-%rather than the ever-present macroscopic degeneracy associated to the cyclotron motion of a single species of fermions.
-
 To the first order, $\delta \hat{H}$ and the Zeeman interaction induce a subleading phase offset ($\lambda_a$) which generically differs for the two orthogonal spinor states (labelled $a{=}1,2$):
@@
 $\delta \var$ is the projection of $\delta \hat{H}$ to the degenerate band subspace of $\hat{H}_0$.
-$\delta \var$ is assumed to be traceless; this property is guaranteed for $\delta \hat{H}$ a spin-orbit coupling that breaks the spin SU(2) symmetry of $\hat{H}_0$;\footnote{The Pauli spin-orbit coupling term ${\propto} \bs{\cdot} (\bE {\times} \bp)$ is traceless in any spin-symmetric (pseudo-)spinor basis.
+$\delta \var$ is assumed to be traceless; this property is guaranteed if $\delta \hat{H}$ represents a spin-orbit coupling term that breaks the spin SU(2) symmetry of $\hat{H}_0$;\footnote{The Pauli spin-orbit coupling term ${\propto} \bs{\cdot} (\bE {\times} \bp)$ is traceless in any spin-symmetric (pseudo-)spinor basis.
 Viewing the spin-orbit coupling as a small parameter in degenerate perturbation theory, the lowest-order splitting of any spin-degenerate energy level is always symmetric about the zeroth-order energy.
@@
 
-The remaining terms in \q{eq:H1} describe a generalized Zeeman interaction $B\calm$ which is the first-order-in-$B$ correction to the Peierls-Onsager Hamiltonian $\var(\bK)$\cite{rotheffham}.\textbf{[kohn,blount]} Included in this interaction is the Zeeman coupling to the spin ($g_s\mu_Bs_z/\hbar$) and orbital ($M_z$) magnetic moment\cite{thonhauser_orbital_2005} of the nearly-degenerate band; the latter is expressible in terms of matrix elements of the velocity operator $\boldsymbol{\Pi}_{mn}=i\langle\psi_m|[\hat{H}, \hat{\boldsymbol{r}}]|\psi_n\rangle/\hbar$ between Bloch wave functions $\psi_{n\bk}$:
+The remaining terms in \q{eq:H1} describe a generalized Zeeman interaction $B\calm$ which is the first-order-in-$B$ correction to the Peierls-Onsager Hamiltonian $\var(\bK)$\cite{rotheffham,blount_effham,kohn_effham}.
+Included in this interaction is the Zeeman coupling to the spin ($g_s\mu_Bs_z/\hbar$) and orbital ($M_z$) magnetic moment\cite{thonhauser_orbital_2005} of the nearly-degenerate band; the latter is expressible in terms of matrix elements of the velocity operator $\boldsymbol{\Pi}_{mn}=i\langle\psi_m|[\hat{H}, \hat{\boldsymbol{r}}]|\psi_n\rangle/\hbar$ between Bloch wave functions $\psi_{n\bk}$:
 \e{
@@
 }
-Here, the summation in $l$ does not include the two quasidegenerate bands.
+Here, the summation in $l$ does not include the two nearly-degenerate bands.
 There is finally a geometric contribution to the Zeeman interaction, which involves the two-by-two non-Abelian Berry connection\cite{berry_quantal_1984} as well as the  zeroth-order band velocity:
@@
 \qq{eq:rule}{berryconn} allow us to determine $\lambda_{1,2}$ to the lowest order  in $1/l^2S$ and $\delta S/S$, and for arbitrary values of $l^2\delta S$ and $|B\calm|/\delta \var_{\pm}$.
-We remark that the quantization rule is invariant under basis transformations within the degenerate band subspace (See App.
-\ref{app:quantizationruleproof}); other basis, such as $\bk$-independent basis where Berry connections are trivial, may be more convenient in many discussions.
+We remark that the quantization rule is invariant under basis transformations within the nearly-degenerate band subspace (see App.
+\ref{app:quantizationruleproof}); in subsequent discussions, it may be more convenient to adopt a $\bk$-independent basis where the non-abelian Berry connection vanishes.
 
@@
 
-\begin{figure}
-\includegraphics[width=0.9\columnwidth]{orbits.png}
-\caption{(a) Solid (resp.\ dashed) lines respectively illustrate the band dispersion of an electron gas with (resp.\ without) Rashba spin-orbit coupling.
-The oriented circles illustrate the spin-orit-split orbits for a magnetic field pointing to $-z$ direction.
-(b) The zeroth-order orbit $\frako_0$ is indicated by a dashed circle with area $S$; $\delta S$ is the differential area  between two spin-orbit-split orbits.
-The spin texture is indicated by purple arrows.\label{fig:orbits}}
-\end{figure}
-
 \subsection{Recovering the Onsager-Lifshitz-Roth quantization rules in two limits}\label{sec:recoveronsager}
@@
 
-\noi{i} If $|\var_+{-}\var_-|$ is everywhere (along $\frako_0$) much greater than $B|\calm_{+-}|$, then an electron would undergo adiabatic (band-conserving) dynamics \textbf{[Nenciu]} along two independent, nondegenerate orbits.
+\noi{i} If $|\var_+{-}\var_-|$ is everywhere (along $\frako_0$) much greater than $B|\calm_{+-}|$, then an electron would undergo adiabatic (band-conserving) dynamics\cite{nenciu_review} along two independent, nondegenerate orbits.
 Such an adiabatic regime always exists as $B{\rightarrow} 0$ for nearly-degenerate orbits that do not intersect, e.g, at a type-II Dirac point, which is the subject of the case studies in \s{sec:inplanezeeman} and \s{sec:rotsymmbreakdown}.
@@
 \e{\lambda_{\sma{\pm}} = -\int_0^{T_c}\calh_{\sma{\pm\pm}}\f{dt}{\hbar}=\pm \f{1}{2}l^2\delta S - B\int_0^{T_c}\calm_{\sma{\pm\pm}}\f{dt}{\hbar}.  \label{phaseindependentorbit}} 
-\q{eq:rule}, combined with \q{phaseindependentorbit}, may be identified as the Onsager-Lifshitz rule \textbf{[Onsager,Lifshitz]} for two independent, nondegenerate orbits of areas $S{\pm}\delta S$, and with subleading phase corrections that were first identified by Roth\cite{rothmag}.\footnote{We remark that \q{phaseindependentorbit} neglects the contribution by band $-$ to the orbital moment of band $+$: $\delta M_z=il^{-2}\epsilon_{\ab}(\delta \var_+-\delta \var_-)\mathfrak{X}^{\alpha}_{+-}\mathfrak{X}^{\beta}_{-+}$.
+\q{eq:rule}, combined with \q{phaseindependentorbit}, may be identified as the Onsager-Lifshitz rule\cite{Onsager,lifshitz_kosevich,lifshitz_kosevich_jetp} for two independent, nondegenerate orbits of areas $S{\pm}\delta S$, and with subleading phase corrections that were first identified by Roth\cite{rothmag}.\footnote{We remark that \q{phaseindependentorbit} neglects the contribution by band $-$ to the orbital moment of band $+$: $\delta M_z=il^{-2}\epsilon_{\ab}(\delta \var_+-\delta \var_-)\mathfrak{X}^{\alpha}_{+-}\mathfrak{X}^{\beta}_{-+}$.
 $\mathfrak{X}^{\alpha}_{+-}$, being an off-diagonal matrix element of the position operator, is generically of order a lattice constant $a$.
@@
 
-%the hybridization parameter  $(l^2\delta S)^{-1}$ with the interband matrix elements of the generalized Zeeman interaction $\mathbb{Z}_{+-}{:}{=}B\int_0^{T_c}|\calm_{+-}|dt/\hbar$,  where \qq{eq:rule}{eq:H1} reduce to the known Onsager-Lifshitz-Roth rules for (i) two independent, nondegenerate orbits, and for (ii) degenerate orbits.
-\\
-
-%\noi{i} Let us consider the zero-hybridization limit ($l^2\delta S{\gg}1$) for two spin-orbit-split orbits that do not exactly intersect (e.g., at a type-II Dirac point\footnote{Though the adiabatic limit does not exist for orbits that exactly intersect at type-II Dirac points, these orbits are nevertheless describable by our quantization rule, as exemplified in the case studies of \s{sec:inplanezeeman} and \s{sec:rotsymmbreakdown}.}).
-
 \noi{ii} Let us consider the opposite regime where the Zeeman splitting due to $B\calm$ is much greater than $(\delta \var_+{-}\delta\var_-)$.
 \qq{eq:rule}{berryconn}, with $\calh{\approx}B\calm$, may then be identified with the quantization rule (formulated previously by us\cite{topoferm,100p}) for degenerate orbits of any symmetry.\footnote{An equivalent but less general formulation was proposed earlier in Ref.
-\onlinecite{rothmag} and \textbf{[Mikitik,Sharlai]} for centrosymmetric solids with time-reversal symmetry (at zero field).
+\onlinecite{rothmag} and Ref.
+\onlinecite{Mikitik_quantizationrule} for centrosymmetric solids with time-reversal symmetry (at zero field).
 For comparison, it should be emphasized that \qq{eq:rule}{berryconn} applies to solids of any symmetry, including magnetically-ordered solids.}
-
-%The competition between $B\calm$ and $\delta \epsilon$ decides 
-%whether the spin-orbit-split energy bands are nontrivially hybridized by the magnetic field.
-More precisely, the competition is between $\delta \epsilon$ and the inter-band matrix elements of $B\calm$; the former (resp.\ latter) is always dominant for sufficiently weak (resp.\ large) field, as  we will illustrate in the case study of \s{sec:Rashba}.
-
-%This leading dependence originates from $\A$ being generated by $\delta \var T_c {\propto}1/B$ [cf.\ \qq{eq:prop}{eq:H1}].
-
-%One motivation for the form of \q{eq:rule} is a separation of scales for different components of
-
-%Separating the semiclassical phase (acquired by a spinor wavepacket over one cyclotron period) into multiple components [as in \q{eq:rule}] may be motivated as a separation of scales. 
-% in absolute magnitude, the rate of variation of $\partial l^2S$ (with respect to $E$ and $B$) is also much greater.
-
-%Such non-analyticities might originate from saddle- or II-Dirac points of the zero-field Hamiltonian \textit{without} spin-orbit coupling.
-
-%is estimated to be $\sim\epsilon_c E/\Delta$, much larger than cyclotron energy $\epsilon_c$ due to $\Delta\ll E$. Therefore, the dependence of $\lambda_a$ on $E$ is also weak.
 
@@
 
-%In the absence of symmetry, three real parameters 
-%certain symmetries  reduce the number of tuning parameters to one, as  will be investigated in \s{sec:llquasideg}.
-
 \section{Case study: Rashba 2DEG with arbitrarily-oriented fields}
 
-%We begin with some preliminary remarks that apply to all case studies in this work.
-Our chosen studies are modeled (in zero field) by $\bk{\cdot}\bp$ Hamiltonians which are expanded (to quadratic order) about a high-symmetry wavevector ($\bk$).
-Our model Hamiltonians are written in a (pseudo-)spinor basis, i.e., they are two-dimensional at each $\bk$ [as exemplified by \q{eq:Rashba-Hamiltonian}]; this is the minimal dimension needed to model quasidegenerate orbits.
-
-%Any (pseudo-)spinor Hamiltonian can be  decomposed, at each $\bk$, into traceful ($\var(\bk)$) and traceless ($\delta \var$) components.
-We operationally identify the traceful component as the zeroth-order band Hamiltonian (with spin $\text{SU}(2)$ symmetry), and the traceless component as the spin-orbit term; the former produces spin-degenerate energy bands, and the latter splits the degeneracy.
-This identification has a microscopic justification: the Pauli spin-orbit coupling term  (that is derived from the non-relativistic limit of the Dirac equation) is  traceless in any spin-symmetric  (pseudo-)spinor basis.\footnote{The Pauli spin-orbit term is proportional to  $ \bs{\cdot} (\bE {\times} \bp)$.
-Viewing the spin-orbit coupling as a small parameter in degenerate perturbation theory, the lowest-order splitting of any spin-degenerate energy level is always symmetric about the zeroth-order energy.
-This follows because the zeroth-order, spin-symmetric wavefunctions (associated to a spin-degenerate level) are tensor products of spin and spatial wavefunctions: $\ket{\Psi_{\pm}}{:}{=}\ket{{\pm}\hat{n}}{\otimes} \ket{\psi}$ with $\hat{n}$ a unit vector and  $\bs{\cdot} \hat{n} \ket{{\pm}\hat{n}}{=}{\pm}\ket{\pm \hat{n}}$.
-Hence, $\braopket{\Psi_{\pm}}{\bs{\cdot} (\bE {\times} \bp)}{\Psi_{\pm}}{=}{\pm}\hat{n}\cdot\braopket{\psi}{\bE {\times} \bp}{\psi}$.
-} $H_0$ determines the zeroth-order orbit $\frako_0$ (and associated action $S$ and cyclotron energy $\var_c$).
-$H_{so}$ is simply identified with $\delta \var$, the spin-orbit term in the effective Hamiltonian $\calh$.
-One useful implication of this discussion is that $\delta \var$ is traceless.
-
 \subsection{2DEG with Rashba and Dresselhaus spin-orbit interactions}\label{sec:Rashba}
-
-%[ denoted by $\ket{u_{\pm,\bk}}=(1,\pm e^{i\theta_{\bk}})^t$ with $k e^{i\theta_{\bk}}=k_y+ik_x$ ]
-
-%basis of spin-orbit-split energy  bands (defined at zero field),
 
@@
 The first term of  $\calh$ corresponds to the spin-orbit-induced splitting of the energy-degenerate bands;
-the remaining terms may be interpreted as B-induced deformations of the bands.
+the remaining terms may be interpreted as $B$-induced deformations of the bands.
 It is well-known that the Zeeman term tends to polarize spin in the direction of $\bB$; remarkably, the non-abelian Berry term  also has a polarizing effect, but with opposite sign.
@@
 The orbital moment term $B M_z$, which generally couples the two-band subspace (of interest) to all other bands, is absent in any simplified two-band model.
-%Observe that  that $\calh$ is actually time-independent, which originates from a  that is unbroken by the field (aligned with the rotational axis). Consequently,
 
@@
 In the strong hybridization regime where $l^2\delta S {\ll}\pi(g_sm/m_0{-}2)$, $\lambda_{\pm}{\approx}{\pm}\pi g_sm/2m_0$ mod $2\pi$, which corresponds to the Zeeman splitting of Landau levels by $g_{s}\mu_BB$, in the \textit{absence} of the spin-orbit interaction.
-
-%In the case of free electrons ($m{=}m_0$), we recover  an elementary result in quantum mechanics -- that all levels (except the lowest) are spin-degenerate due to the equality of cyclotron and Zeeman energies.
-
-%Eq. (\ref{eq:prop}) interpolates smoothly between the quantization rules for degenerate and independent orbits.
-
-%For $\delta\epsilon=0$, Eq. (\ref{eq:prop}) is exactly the propagator for degenerate bands in Ref. [100p].
-
-%If $\delta\epsilon$ dominates over all other terms in \q{eq:H1}, tunneling matrix elements between energy bands may be neglected.
-That is to say, the propagator is well-approximated by a diagonal matrix in the basis of energy bands; each diagonal element corresponds to the phase offset for an independent orbit.
-
-%To better appreciate this, 
-%$\A$ has the form:
-%\begin{equation}
-%\A=\overline{\exp}[i\oint_\frako_0\left(\begin{array}{cc}
-%-\alpha l^{2}mk_F+\frac{1}{2} & -\frac{1}{2}+\frac{g'_s}{4}\\
-%-\frac{1}{2}+\frac{g'_s}{4}& \alpha l^{2}mk_F+\frac{1}{2}
-%\end{array}\right)d\theta],\label{eq:Rashba-prop}
-%\end{equation}
-%where $\theta$ is a polar angle parametrizing the cyclotron orbit, and $g_s'{:}{=}g_{s} m/m_0$ is an effective $g$ factor weighted by the ratio of the effective mass $m$ over the free-electron mass $m_0$.
-Off-diagonal elements of $\A$ induce inter-band tunneling, and are contributed by the Berry connection (the term $-1/2$) and the Zeeman coupling  ($g_s'/4$).
-That both terms are $k$-independent originate from the continuous rotational symmetry (in $z$ direction) of the Rashba Hamiltonian.
-%Diagonalizing Eq. (\ref{eq:Rashba-prop}), we obtain subleading order correction to quantization rule as
-
-%The two quantities under the square root reflect a competition between intra- and inter-band matrix elements.
-The latter reflects a quantum interference between the Zeeman coupling and the non-abelian Berry connection, which is captured by our quasidegenerate quantization rule but absent in the standard Onsager-Lifshitz rules for independent orbits.
-To appreciate this, suppose we employ the standard rules[roth,100page] and properly account for the Zeeman coupling, the orbital moment, and the single-band Berry phase.
-The  Zeeman coupling  modifies the zero-field energy bands in two ways: it enlarges the spin-orbit-induced energy gap as $\Delta {\rightarrow} \Delta'{:}{=} \sqrt{(\Delta)^2{+}(g_s\mu_BB)^2}$, and it tilts the spin (along either orbit) out of the xy-plane.
-For $\Delta'{\gg}\var_c$, we may treat each Zeeman-deformed orbit as independent, and the corresponding Onsager-Lifshitz quantization rules are
-%\e{ l^2S\pm \lambda'_{\pm} = 2n(\pi+1/2), \;\text{with}\;   \lambda'_{\pm}:=\pm 2\pi \Delta'/\var_c{+}\pi.}
-%The first component of $\lambda'$ is simply the modification of the WKB phase $l^2\delta S'$ due to both spin-orbit and Zeeman couplings; the second component is  the sum (${=}\pi$)[Fuchs,topoferm] encodes the single-band Berry phase and the orbital moment.
-A comparison of $\lambda_{\pm}$ with $\lambda'_{\pm}$ shows that the former has an extra $1/2$ under the square root [cf.\ \q{eq:Rashba-lambda}], which originates from the off-diagonal element of the non-abelian Berry connection.
-In other words, the standard Onsager-Lifshitz rules neglects the aforementioned quantum interference.
-This interference is completely destructive for free electrons ($m{=}m_0$), but not generically in band systems.
-
-%\footnote{We have further assumed here that basis functions of $\mathcal{H}_R$ are eigenstates of spin operator $s_z$, which also need not be true in band systems. }
 
@@
 
-%Perfect match between quantization rule and exact diagonalization can be observed in the left panel of \fig{fig:RD}(b) while slight deviations are seen for smaller magnetic field.
-In \fig{fig:RD}(c) we plot the errors in energies for various choices of the spin-orbit parameters $(\alpha,\beta)$, which does not exceed $2\%$ of $\var_c$ in the plot range.
-Larger errors are positively correlated with
-%$l^2\delta S^2/S$ (with $\delta S$ depending on both $\alpha$ and $\beta$), as shown in Fig.
-\ref{fig:RD}(d); see also \q{eq:Rashba-exact}, which analytically demonstrates how terms involving $l^2\delta S^2/S$ modifies the quantization rule in the case of $\beta=0$.
-
 In \s{sec:llquasideg} we will further motivate the study of $H_{RD}$ by investigating the prevalence of Landau-level degeneracies.
-
-%\red{Equation \ref{eq:Rashba-exact} indicates the error of quantization rule is mainly contributed by high order terms, such as terms proportional to $l^2 \delta S^2/S$.
-We plot in Fig.
-\ref{fig:RD}(c) $l^2 \delta S^2/S$, showing a strong positive correlation between $l^2 \delta S^2/S$ and error of quantization rules.
-
-%For a last numerical comparison, we plotted in Fig. \ref{fig:RD} (b) the Landau-level spectrum at fixed $\alpha$ and $\beta$
-
-%For fixed $\alpha$ and $\beta$, Landau fan diagrams are presented in Fig.
-\ref{fig:RD} (b), showing perfect match at relatively large magnetic field and slight deviation in smaller magnetic field between quantization rule and exact Landau levels.
-
-%A typical constant energy contour of the band structure is shown in Fig.
-\ref{fig:errors} (a), where Dresselhaus SOC breaks continous rotational symmetry to two fold rotational symmetry.
-There are no known analytic closed-form solutions to the magnetic Hamiltonian $H_{RD}(\bK)$ obtained by Peierls subtitution of $H_{RD}(\bk)$; however $H_{RD}(\bK)$ can be numerically diagonalized by standard techniques that are reviewed in App.
-\ref{sec:numerical}.
-The difference between $\lambda$ calculated by numerical diagonalization and by Eq.
-\ref{eq:prop} are shown in Fig.
-\ref{fig:errors} (c), where good agreement can be observed.
-$\Delta/\epsilon_c$ of corresponding parameter range is presented in Fig.
-\ref{fig:errors}(b).
-
-%$\lambda$ extracted from from Eq. (\ref{eq:Rashba-exact}) is consistent with what we have obtained in Eq. (\ref{eq:Rashba-lambda}).
-
-%It is instructive to consider what we would have obtained if we ignore the tunneling between the quasidegenerate orbits.
-Without tunneling, the quantization rule gives Eq.
-(\ref{eq:Rashba-exact}) with $(1/2-g_s'/4)^2$ missing under the square root.
-This difference is only relevant when $\epsilon_s$ is small enough such that this term dominates the square root, i.e., in the quasidegenerate range.
 
@@
 \includegraphics[width=1.0\columnwidth]{RD.png}
-% alpha=0.05
-% beta=0.02
-% m=0.01
 \caption{Rashba-Dresselhaus model.
@@
 Our next case study involves orbits that (nearly) touch at a type-II Dirac point\cite{soluyanov_type-ii_2015,muechler_tilted_2016} -- an asymmetric variant of the conventional Dirac point (as will be introduced below).
-Quantum tunneling localized to a type-II Dirac point  (in short, a II-Dirac point) is known to be mathematically equivalent to  Landau-Zener breakdown, with the electric force replaced by the Lorentz force\cite{AALG,obrien_magnetic_2016}.\textbf{[Blount]} Here, we will demonstrate how Landau-Zener dynamics emerge from our quantization rule [\qq{eq:rule}{eq:H1}], and explore (for the first time) how these dynamics are modified by the Zeeman effect.
+Quantum tunneling localized to a type-II Dirac point  (in short, a II-Dirac point) is known to be mathematically equivalent to  Landau-Zener breakdown, with the electric force replaced by the Lorentz force\cite{AALG,obrien_magnetic_2016,kane_blount}.
+Here, we will demonstrate how Landau-Zener dynamics emerge from our quantization rule [\qq{eq:rule}{eq:H1}], and explore (for the first time) how these dynamics are modified by the Zeeman effect.
 In particular, we will show that the perfect Klein tunneling predicted by O'Brien \textit{et al}\cite{obrien_magnetic_2016} is never perfect with a proper account of the Zeeman effect.
-
-%\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+\zpar\sigma_{y},
 
@@
 We only plotted in region where $0.4{<}\epsilon_0{<}1.0$(eV)\cite{RZfignote}.
-Parameters for (d): $m=0.076m_0$, $l=100$\AA.
-\label{fig:RZ}}.
+Parameters for (d): $m=0.076m_0$, $l=100$\AA.\label{fig:RZ}}
 \end{figure}
@@
 We shall assume  $1/\lper^2S{\ll}1$, where $S$ is the area of the zeroth-order orbit (with effective mass $m$ and radius $k_E{=}\sqrt{2mE}/\hbar$).
-For energies much greater than $m\alpha^2$ and $\zpar$, the quasidegeneracy condition ($\delta S/S{\ll}1$) is met, where $\delta S$ is the differential area induced by both spin-orbit and in-plane Zeeman couplings [see \fig{fig:RZ}(a)].
+For energies much greater than $m\alpha^2$ and $\zpar$, the nearly-degeneracy condition ($\delta S/S{\ll}1$) is met, where $\delta S$ is the differential area induced by both spin-orbit and in-plane Zeeman couplings [see \fig{fig:RZ}(a)].
 The smallness of $1/\lper^2S$ and $\delta S/S$ (with finite ratio $\lper^2\delta S$) justifies our application of the quantization rule [\qq{eq:rule}{eq:H1}],  with the effective Hamiltonian:
@@
 The eigenbasis of $\sigma_x$ corresponds to two diabatic levels with characteristic slope $v_d{:}{=}\hbar\alpha k_E\omega^{\sma{\perp}}_c$; near $t{=}0$, the diabatic levels anticross  due to the hybridization terms proportional to $\sigma_{y,z}$.
-Generally, the probability of tunneling across the hybridization-induced barrier is  $\rho^2{=}\exp(-2\pi\barmu)$, with $\barmu{=}{E_g}^2/{2v_d \hbar}$ and $E_g$ the energy gap at the center of the anticrossing\cite{wittig_landauzener_2005};\textbf{[Landau and lifshitz]} in this context,
+Generally, the probability of tunneling across the hybridization-induced barrier is  $\rho^2{=}\exp(-2\pi\barmu)$, with $\barmu{=}{E_g}^2/{2v_d \hbar}$ and $E_g$ the energy gap at the center of the anticrossing\cite{wittig_landauzener_2005,lifshitz_e.m._quantum_1991}; in this context,
 \e{\barmu=\frac{Z_\perp^2+(Z_\parallel-\alpha k_{E})^2}{2\hbar\alpha k_{E}\var^{\sma{\perp}}_c}, \label{mu1}}
@@
 
-%consist of two parts: dynamical phase $\lper^2 \delta S$ with $\delta S'$ now accounting for both spin-split and Zeeman-split area corrections,
-
-%{=}\int_{\sma{0}}^{\sma{T_c}}\calh_{jj}dt/\hbar$ is the cyclotron integral of the corresponding diagonal element of the effective Hamiltonian (in the energy-band basis).
-$\delta \Omega_{\pm}{=}{\pm}l^2\delta S/2$ plus a field-independent geometric phase (equal to the angle swept by the in-plane spin-orbit field $(\bk^2/2m_2{-}\mu,wk_x,0)$ along the spin-split trajectory; cf.\ discussion in \s{sec:Rashba}).
-
 \begin{figure}
@@
 (\ref{calHRZ})] into  Pauli matrices ($\calh{=}\sum_j\calh_j\sigma_j$) defines a three-vector $\boldsymbol{\calh}{=}({-}\alpha k_y$,$\alpha k_x{+}Z_\parallel,{-}Z_\perp$).
-$\phi_{\pm}^B$ equals half the solid angle subtended by   ${\mp} \boldsymbol{\calh}(\bk)$ [solid blue line] as $\bk$ is varied along the outer/inner orbit;[Berry] the orientation of the solid angle is indicated by blue dotted lines.
+$\phi_{\pm}^B$ equals half the solid angle subtended by   ${\mp} \boldsymbol{\calh}(\bk)$ [solid blue line] as $\bk$ is varied along the outer/inner orbit\cite{berry_quantal_1984}; the orientation of the solid angle is indicated by blue dotted lines.
 The out-of-plane Zeeman interaction lifts $\boldsymbol{\calh}$ out of the $x-y$ plane, but this occurs at most over a fraction ${\sim}(\bar{\mu}_{\sma{\text{min}}}m_0/m{\ll}1)$ of the cyclotron period.
@@
 A quantization rule analogous to \q{coscos} was previously derived by us for a II-Dirac point that intermediates an electron- and hole-like orbit\cite{AALG}.
-
-%Let us first investigate the minimal- and maximal-tunneling limits for \q{coscos}.
-At energies away from the Dirac point ($E{\neq}\epsilon_0$) and in the limit $B{\rightarrow}0$, Landau-Zener tunneling is negligible ($\tau{\rightarrow}1,\bar{\varphi}{\rightarrow}0$), and \q{coscos} simplifies to the Onsager-Lifshitz-Roth rules ($\Omega_{\pm}/2\pi{\in}\Z$) for  two independent orbits.
 
@@
 \ref{fig:RZ}(b)) are periodic in $E{\rightarrow}E{+}\pi/l^2(\partial S/\partial E)$ and in $l^2{\rightarrow}l^2{+}\pi/S$.
-Both periods are approximately half that of either disconnected  orbit, in the assumed quasidegenerate regime $\delta S{\ll}S$.
+Both periods are approximately half that of either disconnected  orbit, in the assumed nearly-degenerate regime $\delta S{\ll}S$.
 The $\pi$ correction in \q{trefoilrule} is the Berry phase associated to a $2\pi$ rotation of the wavefunction spin over a single trefoil orbit, as illustrated in Fig.
@@
 
-If the quasidegenerate orbits are appreciably hybridized ($\hbar\alpha k_{\sma{E}}{\lesssim}\var_c$), our quantization rule \qq{eq:rule}{eq:H1} remains valid but the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}.
+If the nearly-degenerate orbits are appreciably hybridized ($\hbar\alpha k_{\sma{E}}{\lesssim}\var_c$), our quantization rule \qq{eq:rule}{eq:H1} remains valid but the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}.
 We may anyway diagonalize $\cala$ numerically, and compare the resultant semiclassical Landau levels with the exact diagonalization of $H_{RZ}(\boldsymbol{K})$; to our knowledge, there exists no analytic solution of $H_{RZ}(\boldsymbol{K})$ for generic values of $\alpha,\zpar$ and $B_{\perp}$.
@@
 \includegraphics[width=1.0\columnwidth]{LL.png}
-\caption{\red{A schematic diagram of Landau level dispersion with respect to $B$ for nearly degenerate orbits.
-One region of Landau level quasidegeneracies (corresponding to $\delta\lambda\equiv 0$) is indicated by a red rectangle.}\label{fig:LL}}
+\caption{A schematic diagram of Landau level dispersion (solid lines) with respect to $B$ for nearly-degenerate orbits.
+$\delta\lambda$ is plotted in the colored background.
+Landau level quasidegeneracies occur at $\delta\lambda\equiv 0\equiv 2\pi$.\label{fig:LL}}
 \end{figure}
@@
 Before this general symmetry classification,  we will first develop physical intuition by studying two rotationally-symmetric models [cf.\ \s{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}] where only one tunable parameter is needed -- this can be the $B$ field itself.
-
-%Finally, the experimental implications of single- and double-parameter tuning of Landau-level degeneracies are discussed in \s{sec:qo}.
 
@@
 \e{\bigg|\f{E_{1}-E_2}{\var_c}\bigg|_{B=\bar{B}} \sim \order\left( \f{\partial \lambda_a/\partial E}{\bar{l}^2\partial  S/\partial E}  \right)\ll 1,\label{llquasideg}}
-with $\bar{l}$ the magnetic length associated to $\bar{B}$.
+with $\bar{l}$ the magnetic length associated to $\bar{B}$; this is illustrates schematically in Fig.\ \ref{fig:LL}.
 Alternatively, we may fix $\bar{E}$ and investigate how Landau levels disperse as a function of $B$; the analog of \q{llquasideg}  is the existence of paired Landau levels in close proximity to $\bar{l}^2$, with a splitting of order:
@@
 Each such pair of Landau levels will be called \textit{quasidegenerate}.
-Landau level quasidegeneracy is sketched in Fig.
-\ref{fig:LL}.
 
@@
 
-%If special unitaries were uniformly distributed over $S^3$, then encountering a spectral degeneracy for a randomly-selected special unitary would be an exceedingly rare event -- three parameters need be tuned to find either pole on $S^3$,  i.e., the codimension of degeneracy manifold is three.
-If only one  or two  parameters (in $\{r_1,\ldots,r_4\}$)  can be tuned, then in general we should not expect a degeneracy.
-
 Symmetry may reduce the number of tunable parameters needed to attain an eigenvalue degeneracy for $\A$.
@@
 As a function of $l^2$, we deduce that Landau-level quasidegeneracies occur with a periodicity of $2\pi/\delta S$.
-This periodicity  has a dual interpretation  in real space -- as a periodic increment of a single flux quantum for  the differential magnetic flux (between the two split orbits).
+This periodicity  has a dual interpretation -- as a periodic increment of a single flux quantum for the differential magnetic flux (between the two split orbits).
 
@@
 
-%Generally, such \textit{symmetry-constrained coordinates} are not necessarily related to the canonical coordinates of \q{s3} by a non-singular
-
-%${\cal \bar{A}}(\br){=}{\pm}I$ defines a set of submanifolds in $\br$-space which we refer to as degeneracy manifolds; in the above example, these manifolds comprise two points on $S^3$.
-
- %\textbf{[there are inconsistencies in these definitions, if we impose $d$ to be number of parameters (without imposing linear independence), then $d=4$ for canonical parametrization, and our definition of codimension as d minus dimension of degeneracy manifold gives 4.
-however, if we impose linearly-independent parameters, then we also run into trouble if we allow for symmetric coordinates that are not well-defined at points.]}\red{[First of all, I am not quite sure why the word linear independence is used in the current context.
-I would have used `independent', which means the parameters can be tuned simultaneously.
-One thing that you would probably dislike is that codimension defined by me would be dependent on the parameters $\br$, so it's OK that codimension in canonical parametrization is three while codimension in exponential parametrization is one.
-The precise definition of codimension would be the number of independent parameters needed to find a degeneracy.
-Although codimension depends on the parameters, the codimension found by us is generally universal.
-For example, for rotation symmetry in class 3, we parametrize $\A_{1/2}$ by canonical parametrization $\br_c$.
-There exists a mapping from physical parameters $\br$ to $\br_c$.
-Notice this mapping is not possible for exponential parametrization $\br_e$ since the exponential parametrization of identity is not unique.
-For a nonpathological parameter choice $\br$, the map is well behaved.
-The definition of `well-behaved': any $n\le 3$ dimensional manifold in $\br$ is mapped to $n$ dimensional manifold in $\br_c$.
-With this assumption, codimension of $\A$ in $\br_c$ and $\br$ are actually the same.
-Exponential parametrization is one example of pathological mapping, which maps to sphere to a point (identity).
-However, pathological parameter choice usually does not increase codimension.
-This can be argued in the following way: If the map from $\br$ to $\br_c$ maps a $n\le 3$ dimensional manifold in $\br$ to a $m<n$ dimensional manifold, we remove the corresponding manifold in $\br$.
-After all such manifolds removed, the map become what I defined as `well-behaved' and the codimension should be the same.
-If the manifold removed in $\br$ were mapped to $\A\propto I$, then the codimension decreases, which is the case in exponential parametrization.
-In the presentation, let's be vague and just say codimension is number of independent parameters needed to find a degeneracy.]} alternatively stated, the codimension is the number of linearly-independent parameters needed to fine-tune a degeneracy.
-Here and henceforth, we adopt the shorthand that  \textit{parameters} will always refer to real parameters, and \textit{codimension} always refers to a codimension of a degeneracy manifold.
-
-%, which may be viewed as imposing a $U(1){\times}U(1)$ symmetry.\footnote{$\cala$ commutes with any diagonal unitary matrix, with diagonal entries equal to two arbitrary $U(1)$ phase factors.} T
-
-%It is well-known that symmetry may reduce the codimension of Hamiltonians, e.g., an antiunitary symmetry may restrict complex Hamiltonians to real Hamiltonians, thus reducing codimension from three to two.[wigner,von neumann] In our context, an analog would be
-
-%We may ask if these quasidegeneracies (based on band-conservation symmetry) persist at stronger fields where adiabaticity breaks down.
-If no symmetry remains, then the codimension is three [cf.\ \q{s3}], hence Landau-level quasidegeneracies should not generically be found by varying $B$ alone.
-
-%The indicators defined above classifies symmetry operations into ten and only ten classes, presented in Tab.\ \ref{table:codimension}.
-
-%In contrast,  $T\mathfrak{r}_x$ results in manifolds with codimension two.
-The latter result, in addition to a comprehensive codimension analysis for all symmetry classes, is presented in \s{sec:tenfold}.
-
-%The first study describes a Rashba-Dresselhaus 2DEG where the adiabatic approximation breaks down at all points along the semiclassical orbit; in the second study, the adiabatic approximation breaks down only in the vicinity of type-II Dirac points.
-
-%owing to a spacetime-inversion symmetry that simultaneous inverts space and time: $(\br,t){\rightarrow}({-}\br,{-}t)$, the zero-field Bloch Hamiltonian is Kramers-degenerate at each wavevector.
-However, this same symmetry is broken in the presence of a magnetic field, and therefore does \textit{not} reduce codimension in the Landau-level problem.
-
 \subsection{Codimension reduction for the Rashba 2DEG}\label{sec:singleparameterrashba}
-
-%In this and the subsequent section (\s{sec:rotsymmbreakdown}), we will demonstrate how rotational symmetry reduces codimension in the Landau-level problem.
-Before delving into this, it is instructive to consider the conceptually-simplest analog in differential geometry: if we parametrize the 2D plane by Cartesian coordinates $(x,y){\in}\R^2$, it is apparent that two parameters must be tuned to arrive at the origin.
-If however the origin is the center of a rotation symmetry, we may instead utilize polar coordinates and tune a single parameter (the radial coordinate) to arrive at $x{=}y{=}0$.
-We see that rotational symmetry reduces the codimension of the origin from two to one.
-Here, and in the  Landau-level problem, we define codimension with respect to a \textit{symmetrically-chosen coordinates} (if symmetry exists); such symmetric coordinates need not be well-defined at isolated high-symmetry points, just as the polar coordinates are not well-defined at the rotational center.
 
@@
 \q{eq:Rashba-Hamiltonian}].
-This model has a continuous rotational symmetry (denoted $\mathfrak{c}_{\infty}$), which manifests as the constancy of $\calh(\bk){:}{=}\sum_{j=1}^3r_j\tau_j$ over the circular zeroth-order orbit [cf.\ \q{rashbaeffham}]; here, $\br{=}(r_1,r_2,r_3)$ is a real three-vector and $\{\tau_j\}$ a set of Pauli matrices.
+This model has a continuous rotational symmetry (denoted $\mathfrak{c}_{\infty}$), which manifests as the constancy of $\calh(\bk)$ over the circular zeroth-order orbit [cf.\ \q{rashbaeffham}].
 Consequently, the propagator [cf.\ \q{eq:prop}] simplifies to the exponential form:
@@
 where
-\e{\br{=}\bigg(\f{g_sm}{4m_0}{-}\f1{2},0,-\f{\hbar\alpha k_{\sma{E}}}{\var_c}\bigg).}
+\e{\br{=}\bigg(\f{g_sm}{4m_0}{-}\f1{2},0,-\f{\hbar\alpha k_{\sma{E}}}{\var_c}\bigg)} and $\{\tau_j\}$ are a set of Pauli matrices.
 Any $\text{SU}(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}] for some (possibly non-unique) $\br$, with $r_2$ not necessarily zero.
@@
 For the exactly-soluble Rashba model ($r_2{=}0$), these $\mathfrak{c}_{\infty}$-protected quasidegeneracies  are consistent with (and partially demystify)  the abundance of \textit{exact} level crossings in the spectrum of $H_R(\bK)$ [cf.\ \q{eq:Rashba-exact}]; such crossings are not expected from the Wigner-von Neuman non-crossing rule\cite{neumann2000behaviour}.
-The zero-radius sphere (i.e., a point) has codimension three, as would be expected if symmetry were absent [cf.
-\s{sec:introducecodimension}].
+The zero-radius sphere (i.e., a point) has codimension three, as would be expected if symmetry were absent (cf.
+\s{sec:introducecodimension}).
 This point degeneracy can be understood from an elementary result in quantum mechanics: taking $\alpha{=}r_2{=}0$ \textit{and} $m{=}m_0$, we recover the Zeeman-split Landau levels of a free electron gas without spin-orbit coupling; all levels (except the lowest) are spin-degenerate owing to the equality of the Zeeman and cyclotron energies\cite{landau2013course}.
@@
 
-\textbf{[Bonus content:consider the Berry phase of the eigenstate of A. Is it quantized for a symmetrically chosen loop in r space?]}
-%If a line node (in the $\beta{=}0$ plane) were perturbatively stable to finite $\beta$, then it would be embedded in a two-dimensional degeneracy hypersurface of $\mathbb{R}^3$; if the planar line node were unstable, this embedding does not happen, i.e., the planar line node is simply a line node in $\mathbb{R}^3$.
-Our numerical study shows that half the planar line nodes (corresponding to $\A{=}I$) are stable, while the other half ($\A{=}{-}I$) destabilizes.
-In $\mathbb{R}^3$, we then have pairs of line nodes and hypersurfaces enclosed by increasingly larger pairs of line nodes and hypersurfaces, as illustrated in Fig.
-\ref{fig:dgn}.
-
 To demonstrate how the $\A{=}I$ hypersurface derives from $\mathfrak{c}_2$ symmetry, consider  the effective Hamiltonian $\calh$ 
@@
 The tracelessness of $\calh$ (at each $\bk$) implies that  ${\A}_{\sma{T_c/2\leftarrow 0}}$  has unit determinant.
-\red{Since the full propagator $\A$ can be obtained with the knowledge of half of it $\A_{\sma{T_c/2\leftarrow 0}}$, the symmetric coordinates are naturally chosen as the canonical parametrization for this $\text{SU}(2)$ matrix [Eq.
-(\ref{s3}) with ${\cal \bar{A}}$ replaced by ${\A}_{\sma{T_c/2\leftarrow 0}}$].} In this symmetric coordinates, we derive
+Employing the canonical SU(2) parametrization for the half-loop propagator [Eq.
+(\ref{s3}) with ${\cal \bar{A}}$ replaced by ${\A}_{\sma{T_c/2\leftarrow 0}}$], we derive
 \e{
@@
 with $\sum_{j=1}^4r_j^2{=}1$.
-It follows that $r_2{=}0$ is a necessary and sufficient condition for $\bar{\A}{=}I$.
+\q{proprashba} is a parametrization of the two-fold-symmetric propagator by the symmetric coordinates $\br{=}(r_1,r_2,r_3)$.
+It follows that $r_2{=}0$ is a necessary and sufficient condition for $\A{=}I$.
 The corresponding degeneracy manifold is a path-connected hypersurface, which separates $\br{=}(r_1,r_2,r_3)$-space into two distinct connected components.
@@
 \ref{app:codimension}, this conclusion generalizes for any $N{\geq}2$: the degenerate manifolds of $\mathfrak{c}_N$-symmetric $\A$ separate the space of symmetric coordinates into $N$ distinct connected components.
-
-\red{Returning to the Rashba-Dresselhaus model, if the map $f$ from physical variables $(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0)$ to the symmetric coordinates is well-behaved, the inverse image of $r_2=0$ in $(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0)$ would be a two dimensional manifold, as illustrated in \fig{fig:dgn}(a).
-On the other hand, ${\cal \bar{A}}{=}{-}I$ occurs if and only if $\br{=}(0,\pm 1,0)$.
-The inverse image of $f$ of the two points is a path-connected line node confined to the $\alpha{=}0$ and $\beta{=}0$ planes [cf.\ \fig{fig:dgn}(b)];} the difference in codimension originates from the $\mathfrak{c}_{\infty}$ symmetry within these two planes [cf.\ \s{sec:ctsrot}], which was not accounted for in the $\mathfrak{c}_2$-symmetric analysis of \q{proprashba}.
-
-%If $C_2$ were the only symmetry, then three parameters would be needed to tune ${\cal \bar{A}}{=}{-}I$.
-Generally, additional symmetry further constrains $\bR$, which may effectively reduce the number of tuning parameters.
-This explains why the ${\cal \bar{A}}{=}{-}I$ manifolds, as plotted in \fig{fig:dgn}(a)], are line nodes instead of point nodes: these line nodes lie in either the $\alpha{=}0$ or the $\beta{=}0$ plane, both of which are $\mathfrak{c}_{\infty}$-symmetric.\footnote{To complete the explanation, \textbf{speculative:} the space of $C_{\infty}$-symmetric unitaries lie on lines in $\bR$-space that intersect $\bR{=}(0,1,0,0)$ [the point node].
-A singular coordinate transformation to $\br$-space maps these $C_{inf}$-symmetric lines to $\mathfrak{c}_{inf}$-symmetric planes, and the point node to a line node.}
+\fig{fig:dgn}(a) illustrates the $\A=I$ degenerate manifold in distinct parameters: $(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0)$.
+On the other hand, $\A{=}{-}I$ occurs if and only if $\br{=}(0,{\pm} 1,0)$; the inverse image of $\br{=}(0,{\pm} 1,0)$ (under $f$) is a path-connected line node confined to the $\alpha{=}0$ and $\beta{=}0$ planes [cf.\ \fig{fig:dgn}(b)]; the difference in codimension originates from the $\mathfrak{c}_{\infty}$ symmetry within these two planes [cf.\ \s{sec:ctsrot}], which was not accounted for in the $\mathfrak{c}_2$-symmetric analysis of \q{proprashba}.
+
+%Let us relate \q{proprashba} to the Rashba-Dresselhaus model.
+For any choice of parameters for $\calh$, the time-ordered exponential of $\calh$ (over half a period) is uniquely defined.
+This defines the map $f:(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0){\rightarrow}\br$.
+For a sufficiently regular $f$, the inverse image -- of a $d_s$-dimensional submanifold in $\br$-space -- must have  dimension that is greater or equal to $d_s$.
+In particular, the inverse image of the path-connected hypersurface ($r_2{=}0$) is a path-connected hypersurface in the space of $(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0)$, as illustrated in \fig{fig:dgn}(a).
 
@@
 \includegraphics[width=1.0\columnwidth]{Cn-breakdown.png}
-\caption{Cyclotron orbits for $\mathfrak{c}_2$-symmetric [(a)] and $\mathfrak{c}_3$-symmetric [(b)] breakdown.
+\caption{(a-b) Cyclotron orbits for $\mathfrak{c}_2$-symmetric [(a)] and $\mathfrak{c}_3$-symmetric [(b)] breakdown.
 Top right inset of (a) presents an enlarged view of the breakdown junction, where the purple rectangle has area $S_{\sma{\square}}$.
@@
 (e) Two Feynman paths that returns to the same band by zero or two tunneling events.
-\label{fig:Cn-breakdown}}
+(f) Schematic Landau level dispersion for $\mathfrak{c}_3$ symmetric breakdown with respect to $\tau$ at a fixed energy.
+Out of the three degeneracies in the independent limit ($\tau=1$), one of them is destabilized by infinitesimal hybridization ($\tau<1$, indicated by green dashed lines) and two of them remains stable until they annihilate at $\tau=0.5$ (indicated by red dashed line).\label{fig:Cn-breakdown}}
 \end{figure}
 
-In the adiabatic limit of two quasidegenerate orbits, we have found [in \s{sec:introducecodimension}] that the codimension for $\cala{=}{\pm} I$ is unity.
+In the adiabatic limit of two nearly-degenerate orbits, we have found [in \s{sec:introducecodimension}] that the codimension for $\cala{=}{\pm} I$ is unity.
 Here we investigate how this result changes as adiabaticity is relaxed by Landau-Zener tunneling -- that respects a discrete $N$-fold rotational symmetry ($\mathfrak{c}_N$).
@@
 For $N{=}3$, we will find that two of three Landau-level quasidegeneracies are perturbatively stable against tunneling, but even these will destabilize beyond a critical tunneling strength.
-
-%Quasidegenerate orbits feature tunneling everywhere along the cyclotron orbit and therefore demand a quantization rule that incorporates both tunneling and single band evolution of wave packets.
-Sometimes, the coherent evolution of wave packets and tunneling can be decoupled in the quantization rule in weak field limit, as exemplified by magnetic breakdown in Rashba-Zeeman model in Sec.
-\ref{sec:inplanezeeman}.
-Let us further explore single-parameter tunability of Landau-level quasidegeneracies in this limit by introducing a rotational symmetric Hamiltonian with isolated breakdown junctions at several isolated $\bk$ points.
-Besides being an interesting toy model, this Hamiltonian provides some insights of stability of Landau-level quasidegeneracies by perturbing from two otherwise independent orbits.
-
-%For simplicity, we interpret the Pauli matrices as  spin operators, and the two right-most terms of  \q{modelC2breakdown} as a spin-orbit coupling.
 
@@
 \e{H_{\pm} =\pm {\hbar}\sqrt{\f{2\mu}{m_2}}\bigg(\frac{m_2}{m_1}+\sz\bigg)\delta k_x+w\delta k_{y}\sx+\epsilon_0, \label{linearHam2}}
-from which we deduce that both Dirac points are  type-II if $m_1{<}m_2$; we further assume $m_1{\ll}m_2$ so that the quasidegeneracy condition ($\delta S/S{\ll}1$) is satisfied.
-
-%this condition is henceforth assumed.\footnote{Actually we will impose the stronger condition $m_1{\ll}m_2$, to ensure that the relative change in band velocity (due to the spin-orbit coupling) is small.
-This is a consistency requirement of our WKB theory, as explained in \app{app:quantizationruleproof}.}
-
-%; near each point the orbits are well approximated by two hyperbolic arms
-%$\phi_j{=}\int_{\sma{0}}^{\sma{T_c}}\calh_{jj}dt/\hbar$ is simply the cyclotron integral of the corresponding diagonal element of the effective Hamiltonian.
-
-% In the weak-field regime where $\var_c{=}{\hbar^2}/m_1l^2{\ll}\Delta$,
+from which we deduce that both Dirac points are  type-II if $m_1{<}m_2$; we further assume $m_1{\ll}m_2$ so that the nearly-degeneracy condition ($\delta S/S{\ll}1$) is satisfied.
 
@@
 \e{\rho^2=e^{-2\pi\bar{\mu}}, \; \bar{\mu}=\f{\big(Z_{\perp}^2+(m_1/m_2)^2(E-\epsilon_0)^2\big)l^2}{2w\sqrt{2E/m_1}}. \label{landauzenerc2}}
-Equivalently, $\bar{\mu}{=}S_{\sma{\square}}l^2/8$, with $S_{\sma{\square}}$ the area of rectangle inscribed between the two hyperbolic arms [cf.\  Fig\ref{fig:Cn-breakdown}(a)].
+Equivalently, $\bar{\mu}{=}S_{\sma{\square}}l^2/8$, with $S_{\sma{\square}}$ the area of rectangle inscribed between the two hyperbolic arms [cf.\  Fig.
+\ref{fig:Cn-breakdown}(a)].
 Elsewhere, an electron undergoes adiabatic (band-conserving) dynamics.
@@
 The half-period propagator may be taken from \qq{scattmat}{propinplanezeeman}, with  $\bar{\mu}$ here given by \q{landauzenerc2}, and  $\tilde{\lambda}_{\pm}{=}{\pm}l^2\delta S/4$ plus a field-independent geometric phase.
-
-%For the upper half ($k_y{>}0$) of Fig.
-\ref{fig:Cn-breakdown}(a), this adiabatic evolution is described by a diagonal unitary matrix in the basis of energy bands; the phase of the diagonal entry $\tilde{\lambda}_{\pm}{=}{\pm}l^2\delta S/4$ plus a field-independent geometric phase.
-The time-evolution propagator  describes the time-ordered, coherent process of Landau-Zener tunneling/transmission (as described by the scattering matrix of \q{scattmat}) and adiabatic dynamics:
-
-%The two scattering matrices for both Dirac points are identical by $\mathfrak{c}_2$ symmetry; so are the two diagonal propagators corresponding to the left and right halves of the adiabatic dynamics.
-
-% \footnote{due to this field-independent phase, it is not necessary that $\delta\lambda_+=-\delta\lambda_-$}
 
@@
 Such quasidegeneracies recur as $\Delta$ advances by $2\pi$, corresponding to a periodicity in $l^2$ of $4\pi/\delta S$ (or two flux quanta).
-This periodicity is not affected by the additional phase $2\bar{\phi}$ in $\Delta$, because $\bar{\phi}$ varies on the scale  $2\pi/S_{\sma{\square}}$,\footnote{For $\bar{\varphi}(\bar{\mu})$ to vary  $\sim 1$, the Landau-Zener parameter $\bar{\mu}$ must vary by $\sim 1$ [cf.\  Fig.\ 10 in Ref.
-\onlinecite{100p}].
-Moreover, $2\pi\barmu{:}{=} (2\pi/8) l^2S_{\sma{\square}}$.\cite{AALG}} which is much larger than $4\pi/\delta S$.
+This periodicity is not affected by the additional phase $2\bar{\phi}$ in $\Delta$, because $\bar{\phi}$ varies on the scale  $2\pi/S_{\sma{\square}}$,\footnote{For $\bar{\varphi}(\bar{\mu})$ to vary $\sim 1$, the Landau-Zener parameter $\bar{\mu}$ must vary by $\sim 1$ (cf.\  Fig.\ 10 in Ref.
+\onlinecite{100p}).
+Moreover, $2\pi\barmu{:}{=} (2\pi/8) l^2S_{\sma{\square}}$\cite{AALG}} which is much larger than $4\pi/\delta S$.
 To recapitulate, half the Landau-level quasidegeneracies (over the $B$ axis) are destabilized  by tunneling; the robustness of the other half relies on $\mathfrak{c}_2$ symmetry.
@@
 
-%The degeneracies alternate between $\cala{=}I$ and ${-}I$ on the B axis, hence the subset of degeneracies corresponding to $\cala{=}I$ (or ${-}I$) occur with a period of  $4\pi/\delta S$ (or two flux quanta).
-
-%occurs if and only if $\rho{=}0$ and  $\exp[i(\delta \lambda_+{+}\bar{\varphi})]$ is real, while
-
-%Let us investigate the fate of these degeneracies as $\rho$ increases.
-While asymmetric interband tunneling generically destabilizes all degeneracies, we will demonstrate that two-fold-symmetric interband tunneling destabilizes only half of them.
-Indeed,
-
-%for $\rho{>}0$, only 0 in Eq. (\ref{c2breakdowndgncondition}) is possible, destabilizing half of the degeneracies. \footnote{Notice cosine function reaches 0 twice in a period}
-
-%Eq.
-(\ref{c2breakdowndgncondition}) with $0$ on the right hand side is the condition for destructive interference of the two Feynman paths that contribute to interband tunneling (as illustrated in \red{[Fig]}); this occurs with a period  of   $4\pi /\delta S$ (or two flux quanta).
-
-%$2\pi\bar{\mu}{\sim}l^2 S_{\sma{\square}}/8$ where $S_{\sma{\square}}$ is much smaller than $\delta S$ [see inset of Fig. \ref{fig:Cn-breakdown}(a)].
-
-%The periodicity (in $l^2$) of the destructive interference has a dual interpretation  in real space -- as a periodic increment of \textit{two} flux quanta for  the differential magnetic flux (between the two spin-split orbits).\footnote{To clarify, band-conserving orbits do not generically describe the dynamics -- except at fine-tuned fields associated to destructive interference of interband tunneling.}
-
-%This  provides yet another  illustration of the general statement proposed in \s{sec:singleparameterrashba}: due to two-fold rotational symmetry, half the degeneracies have unit codimension, and the other half has codimension two.
+A completely different physical realization of two orbits linked by Landau-Zener tunneling was proposed in Ref.
+\onlinecite{yakovenko_angular_2006} -- for a bilayer semiconductor heterostructure subject to an obliquely-oriented field.
+The Landau-level quasidegeneracies attained at certain `magic angles' of the field orientation (a single parameter) was theoretically proposed by Yamaji\cite{yamaji_angle_1989}, and experimentally confirmed in Ref.
+\onlinecite{gusev_interlayer_2008}; however, the role of $\mathfrak{c}_2$ symmetry was not recognized in these works.
 
@@
 Beyond a critical field  (defined by $\tau{=}1/2$), all degeneracies coalesce pairwise (on the $B$ axis) and annihilate.
+This behaviour is illustrated in Fig.
+\ref{fig:Cn-breakdown}(f).
 
@@
 \ref{app:codimension}.
-
-\textbf{[Bonus: A different realization of two-fold symmetric breakdown: angular magnetoresistance oscillations.]}
 
@@
 For the reader's convenience, we present some commonly-encountered matrix representations for exactly-degenerate orbits in Tab.\ \ref{table:sewing-matrix}.
-The last column presents codimensions of the degeneracy manifold defined in symmetric coordinates [cf.
+The last column lists the symmetry-constrained codimensions [cf.
 Sec.
@@
 We then study in Sec.
-\ref{sec:codimquasideg} five of the classes which is relevant to quasidegenerate orbits.
+\ref{sec:codimquasideg} five of the classes which is relevant to nearly-degenerate orbits.
 The remaining five classes are relevant to exactly degenerate orbits, which we study in Sec.
@@
 
-\subsubsection{\red{Ten-fold classification of orbits and symmetric coordinates}}\label{sec:reviewtenfold}
-
-%%We restrict our attention to the subset of $g$ (in the space group) that preserves all field-orthogonal $\bk$-planes, where  orbits  are confined.\textbf{[might say something different about 2DEG]}
+\subsubsection{Ten-fold classification of orbits}\label{sec:reviewtenfold}
 
@@
 
-\red{Among the ten symmetry classes, only six of them (class 1-6) impose self constraints on $\A$.
-These self constraints can be divided into two types: (i) restricting $\A$ to only a submanifold of SU(2) (class 1, 2, 5, 6); (ii) expressing the propagator $\A$ with only a fraction of it [e.g., Eq.
-(\ref{eq:sigmazconstraint})] (class 3, 4).
-For the former case, we define symmetric coordinates by restricting canonical parametrization of $\A$ to that submanifold; for the latter case, we define symmetric coordinates as canonical parametrization of the said fraction of $\A$.}
-
-%In the latter case there exists no self-constraint on the propagator $\A$ [cf.\ \q{eq:prop}] due to $g$ alone, hence the codimension
-
-% preserves  ($u(g)=0$) or inverts ($u(g)=1$) the orientation of the orbit. In the latter case ($|g\circ\frako_0|\ne|\frako_0|$), no constraint exists between $\A$ and itself
-
 \subsubsection{Symmetry-constrained codimension for nearly-degenerate orbits}\label{sec:codimquasideg}
@@
 
-%\textit{quasidegenerate} orbits; such orbits are split with differential area  $\delta S$ that is much less than the area of the zeroth-order orbit $\frako_0$.
-We remind the reader that $\frako_0$ is determined from the field orientation and the spin-degenerate bands of $\hat{H}_0$, while $\delta S$ is further determined by a symmetry-lowering perturbation: $\hat{H}{=}\hat{H}_0{+}\delta \hat{H}$.
-
-%To recapitulate the discussion in \s{sec:reviewtenfold}, we are interested in $g$ belonging to the subgroup of $\hat{H}$ that 
-% maps $\frako_0$ to itself or to a distinct zeroth-order orbit.
-In the less-general context of quasidegenerate orbits, we shall impose additional restrictions that restrict $g$ to five of ten classes.
-
 For these five classes (labelled 1, 3, 6, 7 and 10 according to the first column of Tab.\ \ref{table:codimension}), we list their corresponding \textit{symmetry-constrained codimensions} in the right-most column of Tab.\ \ref{table:codimension}; these numbers are derived in  App.\ \ref{app:codimension}.
 Recall that the codimension is the number of independently-tunable parameters needed to attain a degeneracy for $\A$.
-We define the $g$-constrained codimension as a codimension which is robust to any perturbation of the Hamiltonian that preserves $g$ symmetry and the homotopy class\cite{100p} of the zeroth-order orbit (e.g., a circular orbit cannot be deformed into a figure of eight).
-Each entry in the right-most column of Tab.\ \ref{table:codimension} equals the $g$-constrained codimension for any $g$ specified by the corresponding row.
-
-%in that class (and possibly satisfying an additional constraint on the representation of $g$, as specified by the second-to-last column).
+Each listed codimension is robust to any perturbation of the Hamiltonian that preserves the corresponding symmetry (specified by the row) and the homotopy class\cite{100p} of the zeroth-order orbit (e.g., a circular orbit cannot be deformed into a figure of eight).
 
@@
 To clarify, a self-constraint relates  the propagator $\A$ [cf.\ \q{eq:prop}] to itself or to its inverse $\A^{-1}$, depending respectively on whether $u{=}0$ or $1$.
-
-%To uniquely determine the codimension in some classes,  conditions for the symmetry representation of $g$ must be specified: in class 1 for unitary $g$ that preserves the arrow of time ($s{=}0$),
 
@@
 The symmetry-constrained codimension is reduced to unity in the latter (and only the latter) case, due to the absence of level repulsion between distinct representations of $g$ -- the corresponding quasidegeneracies of Landau levels would then be exact degeneracies, rather than the near degeneracies described by \qq{llquasideg}{llquasidegB}.
-
-%we specify certain conditions on  $\breve{g}$, the \emph{diagonalized}, two-by-two matrix representation  of $g$;
 
@@
 
-%In the latter case, the codimension vanishes due to Kramers degeneracy.
-In the former case, the codimension is calculated to be 2, which is exemplified by $H_{RD}$ respecting $T\mathfrak{r}_{y=-x}$, with $\mathfrak{r}_{y=-x}$ being reflection transforming $x$ to $y$ and $z$ to $z$.
-
-%Therefore, codimension 2 in table \ref{table:codimension} instructs the degeneracy manifold in Fig.
-\ref{fig:dgn}(b) should be one dimensional, providing an alternative explanation of the line node in Fig.
-\ref{fig:dgn}(b).
-
-%Extensively studied in Sec.
-\ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown} is class-3 (3rd row in the table), where rotational symmetry guarantees Landau level quasidegeneracy can be expected by tuning $B$ alone.
-Class-1 presents another example of codimension 1.
-Unitary symmetry in class-1 with $\breve{g}\not\propto I$ assigns different symmetry eigenvalues to the two degenerate bands (of $\hat{H}_0$) on $\frako_0$ and forbids hybridization between them.
-Therefore, $\A$ assumes a diagonal form and admits only one free variable.
-Class-1 symmetries with $\breve{g}\propto I$, acting effectively as identity operator, impose no constraints on $\A$ and thus no reduction in codimension.
-
-%Codimension 0 is exemplified by class-6 with $g^2=-1$, where any eigenvector of $\A$ here is paired with another one due to Kramer's degeneracy.
-
-%\red{In our definition, $g$ is called a symmetry if $\hat{g}$ commutes with both $\hat{H}_0$ and $\delta \hat{H}$.
-Therefore, $\delta \epsilon$ is invariant under the action of $g$.
-For $\cal H$ to transform consistently under $g$, $g$ must preserve the magnetic moment $\mathcal{M}$.
-The magnetic moment is odd under time reversal, and behaves as a pseudovector under spatial transformations.[sakurai] Therefore, either (i) $g$ preserves the direction of time and is a proper transformation of space, or (ii) $g$ inverts the direction of time and is an improper transformation of space.} (i) is exemplified by a rotational symmetry with the rotational axis aligned parallel to the field, and (ii) by the composition  of time reversal $T$ and a spatial reflection $\mathfrak{r}_x$ (with reflection axis perpendicular to $\vec{B}$).
-%As discussed at the end of \s{sec:introducecodimension}, these classes either respect $u+s=0$ or $u+s=2$. \red{[These discussions moved to Sec. IV B]}
-
-%$T\mathfrak{r}_{x,\boldsymbol{c}/2}$ ($\mathfrak{r}_{x,\boldsymbol{c}/2}$ is glide plane translating in $z$ direction for half a lattice vector after flipping $x$ direction) at $k_z=\pi$ is an example of codimension 0, corresponding to class-6 (the 6th class in the table)  with condition $g^2=-1$.
-Due to similar reasons as Kramer's degeneracy, Landau-level quasidegeneracy are guaranteed for arbitrary parameter choice.
-Rotational symmetry belonging to class-3 has codimension 1, as confirmed by numerical study and arguments in Sec.
-\ref{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}.
-Codimension 2 is exemplified by $T\mathfrak{r}_x$ ($\mathfrak{r}_x$ is reflection in $x$ direction) belong to class-6 with $g^2=1$.
-Class-1 symmetries with $\breve{g}\propto I$, acting effectively as identity operator, imposes no constraints on $\A$ and thus no reduction in codimension.
-
-%\red{[need to define stable or robust]} Codimension 1 does not imply every degeneracy is robust, which is a stronger statement than degeneracy manifold can be found by tuning a parameter.
-If degeneracy manifold contains distinct components of different codimension, every degeneracy being robust implies all these components having codimension 1, which is generally not the case, as exemplified by rotational symmetry discussed in Sec.
-\ref{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}.
-Table \ref{table:codimension} only lists the smallest codimension, which is the number of parameters needed to find a degeneracy.
-
-%We end this section by a general discussion of free parameters that is most tunable in experiments.
-In transport experiments, magnetic field $B$ is generally tunable; in tunneling spectroscopy experiments, both $B$ and bias voltage $E$ is tunable.
-If codimension of degeneracy is 1, as constrained by two types of symmetries in Table \ref{table:codimension}, Landau level degeneracies can be found by tuning either $B$ or $E$.
-We have argued in Sec.
-\ref{sec:qtznrules} that $\lambda_a$ varies slowly with respect to $B$ and $E$.
-Hence an \textit{aperiodic} beating pattern is expected by tuning either $B$ or $E$.
-
 \subsubsection{Symmetry-constrained codimension for exactly-degenerate orbits}\label{sec:codimexactdeg}
@@
 
-%The preceding codimension analysis may be straighforwardly extended to  energy bands that are exactly $D$-fold degenerate (at every wavevector) in the absence of the field.
-For simplicity we focus on $D{=}2$ spin degeneracy, which may arise in solids with negligibl\e spin-orbit coupling, and also in spin-orbit-coupled solids with certain crystallographic point-group symmetries (e.g., $T\inv$ symmetry).
-
 We answer this question in nearly the same vein as for nearly-degenerate orbits: the quantization rule for exactly-degenerate orbits\cite{topoferm} has the same form as \qq{eq:rule}{berryconn} with $\delta \var{=}\delta S{=}0.$ An eigenvalue-degeneracy of $\A$ would also imply a Landau-level quasidegeneracy, since the analysis of \s{sec:relatedegeneracies} applies to the special case $\delta S{=}0$.
@@
 Some $\calm$-inverting symmetries also exhibit reduced symmetry-constrained codimensions, as listed in the five \textit{unticked} classes of \tab{table:codimension}.
-As a case in point, class-2 symmetries invert time and $\calm$, and map  every wavevector (in $\frako_0$) to itself.
+As a case in point, class 2 symmetries invert time and $\calm$, and map  every wavevector (in $\frako_0$) to itself.
 The corresponding codimension is three (resp.\ one) if $g$ squares to $-1$ (resp.\ $+1$).
 The former is exemplified by $T\inv$ symmetry, and the latter by $T\rot_{2z}$ (the composition of time reversal with a two-fold rotation about the field direction).
-For an exactly-degenerate orbit $\frako$ confined to a $\rot_{2z}$-invariant plane, the associated propagator $\A$ is unitarily equivalent to a special orthogonal matrix\cite{100p}\textbf{[AA]} with a single, tunable angle of rotation -- this provides an intuitive explanation for the unit codimension.
-
-%the angle of rotation associated to any SO(2) matrix then provides the single tuning parameter.
+For an exactly-degenerate orbit $\frako$ confined to a $\rot_{2z}$-invariant plane, the associated propagator $\A$ is unitarily equivalent to a special orthogonal matrix\cite{100p,alexandradinata_berry-phase_2016} with a single, tunable angle of rotation -- this provides an intuitive explanation for the unit codimension.
 
 The simplest example of codimension reduction by a $\calm$-preserving symmetry is that of continuous spin-rotation.
-This is a symmetry of any solid with negligible spin-orbit coupling, and results in the absence of Landau-level repulsion between different spin species [cf.\ unit symmetry-constrained codimension in class I, with non-identical symmetry eigenvalues].
+This is a symmetry of any solid with negligible spin-orbit coupling, and results in the absence of Landau-level repulsion between different spin species (cf.\ unit symmetry-constrained codimension in class 1, with non-identical symmetry eigenvalues).
 In this case the Landau-level degeneracy is exact.
@@
 However, the generic anisotropy of $\calm$ (viewed as a pseudovector) suggests that we may sweep the orientation of $B$; the generic energy-dependence of $\calm$ suggests that we may tune the bias voltage in tunneling spectroscopy.
-
-%As derived in App.\ \ref{app:codimension},
-
-%Absent this restriction, all ten symmetry classes may potentially apply to exactly-degenerate orbits, but only six of ten (with $|g\circ\frako_0|{=}|\frako_0|$) may have a symmetry-reduced codimension.
-The codimensions for three of these six classes have been explained in \s{sec:codimquasideg}, so here we focus on the other three.
-
-%Landau level quasidegeneracy is not limited to quasidegenerate bands. For degenerate bands, a similar definition is applicable: \red{[need to check]}
-%\e{ \f{E_{1}-E_2}{\var_c}\bigg|_{\bar{B}} = O\left(\f{\var_c}{E} \right). }
-
-%Landau levels of degenerate bands are characterized by a propagator $\A'$ similar to Eq.
-(\ref{eq:prop}) [100p].
-Codimension analysis can be carried out similarly and the results are presented in table \ref{table:codimension}.
-
-%Unlike $\A$, all ten classes of symmetries impose constraints on $\A'$ and thus entries not applicable to $\A$ are useful for $\A'$.
-
-%We have assumed in the above sections that the two-fold quasidegeneracy is due to small SOC.
-More generally, two-fold degenerate bands can be perturbed into quasidegenerate bands by symmetry breaking.
-From this viewpoint, our previous assumption of small SOC breaks continuous spin rotational symmetry which protects the degeneracy of spin up and spin down states.
-Other common symmetry operations capable of protecting two fold degeneracy are $T\mathfrak{i}$ and $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$ at $k_z=\pi$, where $T$ is time reversal symmetry; $\mathfrak{i}$ is inversion symmetry and $\mathfrak{c}_{2z,\boldsymbol{c}/2}$ is two-fold screw rotation in $z$ direction.
-Table \ref{table:codimension} is applicable to quasidegenerate bands ($\A$) perturbed from degenerate bands protected by all the three symmetries and degenerate bands ($\A'$) due to $T\mathfrak{i}$ or $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$.
-For degenerate bands protected by continuous spin rotation, codimension is at most 1 since $\A'$ is diagonal in spin basis.
-Codimension analysis without assumption of degenerate bands being protected by the three symmetries are presented in App.
-\ref{app:codimension}, where codimensions of Landau level quasidegeneracy for possibly fine tuned degenerate/quasidegenerate bands can be found.
 
@@
 Applying this formula in the high-temperature regime, we will prove that  destructive interference of the fundamental quantum-oscillatory harmonic may  be tuned by at most one parameter in any symmetry class; this parameter may be the magnitude ($B$) of the magnetic field for quasidegenerate orbits, but not for exactly-degenerate orbits.
-\s{sec:quantosc_quasideg} focuses on the low-temperature SdH effect for quasidegenerate orbits in symmetry classes 1 to 4 [cf.\ \tab{table:codimension}], wherein we predict a smooth crossover from period-doubled to -undoubled oscillations upon variation of $B$ (at fixed particle density).
-
-%In We have demonstrated for certain symmetry classes that Landau-level quasidegeneracies can be attained by tuning only the magnitude ($B$) of the magnetic field.
-This manifests in the Schubnikov-de Haas effect  as an aperiodic beating of the minima of conductivity (at fixed particle density), as described in \s{sec:quantosc_quasideg}.
-Analogously, it is also possible to attain quasi-equidistant Landau levels by tuning $B$; this manifests as an aperiodic, destructive interference of the fundamental quantum-oscillatory harmonic (at fixed chemical potential).
+\s{sec:quantosc_quasideg} focuses on the low-temperature SdH effect for nearly-degenerate orbits in symmetry classes 1 and 3 [cf.\ \tab{table:codimension}], wherein we predict a smooth crossover from period-doubled to -undoubled oscillations upon variation of $B$ (at fixed particle density).
 
 \subsection{Single-parameter tunability for the destructive interference of the fundamental harmonic}\label{sec:quantosc_equidis}
-
-%and in the presence of magnetic breakdown [Kaganov, lifshitz];
 
@@
 \onlinecite{topoferm}.
-A simple generalization of the derivation in \onlinecite{topoferm} extend the utility of these existing formulae to nearly-degenerate orbits.
+A simple generalization of the derivation in Ref.
+\onlinecite{topoferm} extend the utility of these existing formulae to nearly-degenerate orbits.
 For example, the oscillatory component of the magnetization of 2D metals has the form
@@
 
-%For 3D metals, the oscillLifshitz-Kosevich formula is in a similar form, presented in Ref. [topoferm].
-
 At high temperature ($kT{\gg}\var_c$) and/or with strong disorder ($\omega_c\tau_{\sma{D}}{\ll}1$), the dominant contribution to $\delta M$ is from the fundamental harmonic ($r{=}1$), which sums two sine functions with generically distinct phase offsets $\lambda_{1,2}$.
@@
 In the latter case, only even-$r$ harmonics remain.
-
-%The former is associated to Landau-level quasidegeneracies, and the latter to quasi-equidistant Landau levels with spacing ${\approx}\var_c/2$.
 
@@
 This approach of determining codimension is similar to that in Ref.
-\textbf{[JHNR]}.}
+\onlinecite{holler_non-hermitian_2018}.}
 
@@
 \onlinecite{topoferm}) or the orientation of the magnetic field; however $\lambda_a$ is independent of the field magnitude ($B$), as explained in \s{sec:codimexactdeg}.
-In principle, one may account for linear-in-$B$ corrections to $\lambda_a$ at stronger fields, however a quantitative theory for such corrections only exists (thus far) for non-degenerate orbits\cite{rothmag,fuchs_landau_2017,gao_zero-field_2017}.\textbf{[fischbeck]}
+In principle, one may account for linear-in-$B$ corrections to $\lambda_a$ at stronger fields, however a quantitative theory for such corrections only exists (thus far) for non-degenerate orbits\cite{rothmag,fuchs_landau_2018,gao_zero-field_2017,fischbeck_review}.
 
@@
 The slow variation of $\lambda_a$ compared to the action $l^2S$ [cf.\ \app{sec:slowvariation}] implies a beating pattern for the fundamental harmonic.
-In the weak-field, adiabatic regime, the antinodes of this pattern occur with period $2\pi/\delta S$ in $l^2$ [cf.\ \s{sec:introducecodimension}]; in the non-adiabatic regime, the antinodes are generically aperiodic [cf.\ \q{lambdasmallB}].
-
-Such beatings have been observed for semiconductor heterostructures \textbf{[das,several more]}; in some experiments, \textbf{[das]} the phase offset $\lambda_a$ [cf.\ \q{eq:LK}] has been measured and fitted phenomenologically to a Laurent series in $B$.
-\textbf{[das]} It has been appreciated that the leading-order term (${\sim}1/B$) originates from the zero-field splitting of orbits (due to spin-orbit coupling);\textbf{[das]} our contribution is a quantitative theory of the expansion coefficients of this Laurent series -- we have related the subleading term  $({\sim}B^0)$ to a generalized Zeeman interaction, and higher-order terms to a competition between spin-orbit coupling and the Zeeman interaction [cf.\ \q{eq:Rashba-lambda}].
-As one application, one may extract the intervals (in $1/B$) between antinodes  for the Rashba 2DEG [by imposing $\delta \lambda{\equiv}\pi$ in \q{eq:Rashba-lambda}] and for the Rashba-Dresselhaus 2DEG (see \s{sec:quantosc_quasideg}).
-
-%Our contribution is the first semiclassical theory  [summarized by the quantization rule of \qq{eq:rule}{berryconn} and the Lifshitz-Kosevich formula of \q{eq:LK}] from which one can calculate the beating pattern;
+In the weak-field, adiabatic regime, the nodes of this pattern occur with period $2\pi/\delta S$ in $l^2$ [cf.\ \s{sec:introducecodimension}]; in the non-adiabatic regime, the nodes are generically aperiodic [cf.\ \q{lambdasmallB}].
+
+Such beatings have been observed for semiconductor heterostructures\cite{das_evidence_1989,hu_zero-field_1999,wilde_inversion-asymmetry-induced_2009}; in some experiments\cite{das_evidence_1989}, the phase offset $\lambda_a$ [cf.\ \q{eq:LK}] has been measured and fitted phenomenologically to a Laurent series in $B$.
+It has been appreciated that the leading-order term (${\sim}1/B$) originates from the zero-field splitting of orbits (due to spin-orbit coupling)\cite{das_evidence_1989}; our contribution is a quantitative theory of the expansion coefficients of this Laurent series -- we have related the subleading term  $({\sim}B^0)$ to a generalized Zeeman interaction, and higher-order terms to a competition between spin-orbit coupling and the Zeeman interaction [cf.\ \q{eq:Rashba-lambda}].
+As one application, one may extract the intervals (in $1/B$) between nodes  for the Rashba 2DEG [by imposing $\delta \lambda{\equiv}\pi$ in \q{eq:Rashba-lambda}] and for the Rashba-Dresselhaus 2DEG (see \s{sec:quantosc_quasideg}).
 
@@
 
-%For quasidegenerate orbits, the single parameter might be the magnitude ($B$) of the field.
-%Generically, $\delta \lambda$ nonlinearly depends on $l^2$, leading to an \textit{aperiodic} beating in the dHvA oscillation; in figure \ref{fig:qo} (a), Whenever $\delta\lambda$ reaches $\pi$ (resp.
-$0$), a beating node (resp.
-antinode) is expected.
-
-\subsection{Schubnikov-de Haas effect for nearly-degenerate orbits in symmetry class 1-4}\label{sec:quantosc_quasideg}
+\subsection{Schubnikov-de Haas effect for nearly-degenerate orbits in symmetry class 1 and 3}\label{sec:quantosc_quasideg}
 
 Let us focus on nearly-degenerate orbits for which a single parameter ($B$) can be tuned to attain $\delta \lambda{\equiv}0$ (equivalently, to attain a Landau-level quasidegeneracy).
-These orbits lie in symmetry classes 1 to 4; in classes 1 and 2 further assumptions must be made about the symmetry representation, as explained in \s{sec:codimquasideg} and summarized in \tab{table:codimension}.
+These orbits lie in symmetry classes 1 and 3; in classes 1 further assumptions must be made about the symmetry representation, as explained in \s{sec:codimquasideg} and summarized in \tab{table:codimension}.
 
@@
 Where $\delta\lambda{\equiv}\pi$, Landau levels are  quasi-equidistant, hence adjacent minima (of conductivity) should be identically low.
-Where $\delta\lambda{\equiv}0$, every consecutive gap is small compared to $k_BT$ and $h/\tau_{\sma{D}}$, hence every other  minimum (of conductivity) vanishes.[rashba] $0{\leq}\delta\lambda{\leq}{\pi}$ thus characterizes a smooth crossover between period-doubled and -undoubled oscillations, as representatively illustrated in \fig{fig:qo}(b).
-
-%This contrasts with the high-temperature, low-disorder beating discussed in  \s{sec:quantosc_equidis}, where the antinodes occur as $\delta \lambda{\equiv}\pi$.
-
-Our contribution is the exhaustive  identification of symmetry classes (1 to 4) for which such a crossover will occur.
+Where $\delta\lambda{\equiv}0$, every consecutive gap is small compared to $k_BT$ and $h/\tau_{\sma{D}}$, hence every other  minimum (of conductivity) vanishes\cite{bychkov_oscillatory_1984}.
+$0{\leq}\delta\lambda{\leq}{\pi}$ thus characterizes a smooth crossover between period-doubled and -undoubled oscillations, as representatively illustrated in \fig{fig:qo}(b).
+
+Our contribution is the exhaustive  identification of symmetry classes (1 and 3) for which such a crossover will occur.
 In particular, we are proposing that the crossover occurs for the Rashba-Dresselhaus 2DEG [cf.\ \q{hamRD}], whose nearly-degenerate orbits fall into class 3.
@@
 As expected from the codimension analysis of \s{sec:disrot}, half of the degeneracies ($\delta\lambda {\equiv}0{\equiv}2\pi$) are lifted by introducing nonzero $\beta$.
-
-%\textbf{please see if any information in paragraph below is worth merging into text above}
-%Fig.
-\ref{fig:qo}(b) lower panel presents chemical potential oscillation with respect to $1/B$ under the assumption of zero energy and zero Landau level broadening where $\delta\lambda{\approx}2\pi$, $\delta\lambda{\approx}3\pi/2$, $\delta\lambda{\approx}\pi$ respectively; the corresponding Landau-level dispersions are obtained from exact diagonalization and plotted in upper panel of Fig.
-\ref{fig:qo}(b).
-As expected, close to Landau level quasidegeneracy ($\delta\lambda\approx 0$), half of the oscillations are smeared out and the oscillation period has effectively doubled.
-This behavior is further confirmed by the oscillation of chemical potential plotted in lower left plot of Fig.
-\ref{fig:qo}(b).
-As a contrast, middle column of Fig \ref{fig:qo}(b) shows Landau levels and chemical potential oscillation for $\delta\lambda\approx 3\pi/2$, when quantum oscillation are expected to exhibit large and small oscillations.
-For $\delta\lambda\approx\pi$, the two sets of Landau levels are equally spaced and quantum oscillation are expected to reveal the particle density of the system.
-Generally, with hybridization between cyclotron orbits, we cannot expect the beating to be periodic.
-Therefore, for 2D fixed particle density systems, both oscillation period and oscillation magnitude are beating \textit{aperiodically} with respect to magnetic field.\textbf{[to say that a period is beating aperiodically is perhaps like referring to a snake as a lion, then complaining that the lion isn't snakelike]}
-
-%While the previous subsection has made no assumptions about the 
-%For spin-degenerate Landau levels, the period of quantum oscillation is solely determined by the (assumed constant) particle number density $n_e$ as $e/n_eh$ [Vinter].
-Minima of longitudinal conductivity occur at discrete fields (denoted $B_{\nu}$)  where the filling is even-integer-valued; as $B$ increases beyond $B_{\nu}$, the complete depopulation of spin-degenerate Landau levels is accompanied by a sudden drop in the chemical potential at zero temperature.
-
-%However, these minima may be smeared out by temperature or disorder.
-Whether the minimums are vulnerable to smearing depends on the Landau level gap, i.e., the magnitude of the jump of chemical potential.
-Larger Landau level gap prevents the conduction minimum from being smeared out and thus corresponds to oscillation of larger magnitude.
-This Landau level gap is governed by $\delta\lambda$.
-
-%surface states of 3D solids (insulators and metals, of both trivial and topological categories), as well as (ii) 2DEG in semiconductor heterostructures or 2D materials on substrates.
-Quantum oscillations of the chemical potential are generically negligible in case (i),
-
-% \footnote{Suppose $\mu$ is the field-dependent chemical potential of a 3D solid with surface states.
-Since $\mu$ is an intensive quantity, it may be approximated by the chemical potential $\mu'$ corresponding to the same 3D solid but with periodic boundary conditions in three independent directions.
-If said solid is an insulator, $\mu'$ would depend smoothly on $B$; if said solid is a metal, the quantum oscillations of $\mu'$ have negligible amplitude so long as the Fermi surface is not highly anisotropic.[lifshitz,kosevich] } and non-negligible in case (ii).
-
-%Traditionally, quantum oscillations of thermodynamic and transport quantities are best understood for nondegenerate orbits in the absence of breakdown; they originate from the periodic (in $1/B$) depopulation of discrete Landau levels as $B$ is ramped up.
-For spin-degenerate orbits in the absence of breakdown, it is the depopulation of every second Landau level that is periodic.
-With magnetic breakdown at isolated points, the harmonic content of quantum oscillations generically includes multiple periods corresponding to distinct orbits.
-A distinctive feature of spin-split bands is that quantum oscillations are generically aperiodic.
-
-%It is well known that quantum oscillations from two independent cyclotron orbits (but with similar area in reciprocal space) may also exhibit periodic beatings.
-This is due to Landau levels corresponding to the two orbits may also cross approximately (with a splitting $\sim e^{-c/B}$).
-Such crossings are not so surprising, and should be attributed to band conserving symmetry introduced in Sec.
-\ref{sec:introducecodimension}.
-In contrast, for weakly spin-split bands, the two orbits are strongly hybridized; nevertheless crossings exist and are tunable by $B$.
-The hybridization of the two sets of Landau levels destroy the periodic nature of approximate crossings and is reflected in an \emph{aperiodic} beating pattern.
-%merely reflect that distinct orbits are essentially uncoupled; this is very much analogous to the crossing of levels having different symmetry eigenvalues.
-In contrast, for weakly spin-split bands, the two orbits are strongly coupled by tunneling, hence there are no obvious `symmetry eigenvalues'; nevertheless crossings exist and are tunable by $B$.
-The hybridization of the two sets of Landau levels destroy the periodic nature of approximate crossings and is reflected in an \emph{aperiodic} beating pattern.
-
-% Another distinction: for localized breakdown, crossings occur only at $B\approx 0$, while for nonlocal breakdown they recur aperiodically  at fields denoted $B_n$.
-The recurrence interval for $1/B_n$ is much larger than the period of quantum oscillations, leading to an aperiodic beating effect in the quantum oscillations.
 
@@
 If the codimension is unity, it is possible to tune the magnitude of the field to attain Landau-level quasidegeneracies; the implications for this tunability -- in the Schubnikov-de Haas effect -- are discussed in \s{sec:quantosc_quasideg}.
-If the codimension is two, an additional experimentally tunable parameter is needed: e.g., the orientation of the field\cite{yakovenko_angular_2006}, or the bias voltage in tunneling spectroscopy\textbf{[cite stm papers]}.
-
-With the inclusion of nonsymmorphic space-group symmetries, it is not uncommon to find energy bands which are (nearly) four-fold degenerate\cite{michel_elementary_2001,wang_hourglass_2016,bradlyn_topological_2017}.
-This motivates a generalization of our rule -- for any number of nearly-degenerate orbits -- that is presented in \app{app:quantizationruleproof}.
-The symmetry-constrained codimensions in the more general case is left to future investigations.
+If the codimension is two, an additional experimentally tunable parameter is needed: e.g., the orientation of the field\cite{yakovenko_angular_2006}, or the bias voltage in tunneling spectroscopy\cite{Sangjun_Cd3As2,Ilija_SnTe,kushwaha_Dirac}.
 
@@
 
-\red{For two fold exactly-degenerate orbits, three out of five symmetry classes feature $\lambda_1+\lambda_2=0$ with the assumption of SOC can be continuously tuned to zero without changing the degree of degeneracy.
-Although these three symmetry classes do not impose constraints on nearly-degenerate orbit, due to the traceless spin splitting Hamiltonian matrix, $\lambda_1+\lambda_2=0$ remains true for nearly-degenerate orbits.}
-
-\red{Symmetry constrained codimension discussed in the current work is useful even beyond magnetotransport.
-Specifically, as a special case of Eq.
-({\ref{eq:prop}}) by ignoring Zeeman interaction, Wilson loop share the same symmetry constrained codimension presented in Tab.
-\ref{table:codimension}.
-This observation may be helpful in explaining movable crossings in some Wilson loop spectra \textbf{[cite something]}.}
-
-\red{Nontrivial nature of Landau quantization for nearly-degenerate orbits originates from the field induced hybridization of nearly degenerate bands.
-With the recent development of high magnetic field instrument, we envision quantization rule presented in the current work would be more and more relevant to magnetotransport in future experiments.}
+Our codimension analysis is applicable to contexts beyond that of Landau-level repulsion.
+By keeping only the Berry term in \q{eq:H1}, Eq.\ ({\ref{eq:prop}}) reduces to the Wilson loop of the non-abelian Berry gauge field, i.e., the matrix representation of holonomy.
+Wilson loops can only be classified by symmmetry according to Tab.
+\ref{table:codimension}; the codimensions for an eigenvalue-degeneracy of the Wilson loop are also identical to those listed in   Tab.\ \ref{table:codimension}.
+This observation may be helpful in explaining some movable (but irremovable) crossings in the Wilson-loop spectra of topological crystalline insulators\cite{bouhon_wilson_2018}.
+
+Symmetry does not only constrain the level repulsion between  $\lambda_1$ and $\lambda_2$ -- in certain classes, it constrains their sum.
+In our previous work on exactly-degenerate, spin-differentiated orbits,\cite{100p,topoferm} we have derived a zero-sum rule $\lambda_1{+}\lambda_2{\equiv}0$) in classes  2,4 and 5, with the assumption that spin-orbit coupling can be continuously tuned to zero without changing the degree of degeneracy; this zero-sum rule implies a quantized phase offset for the fundamental harmonic of quantum oscillations.\cite{topoferm} Here, we report that the zero-sum rule applies \textit{also} to nearly-degenerate orbits in classes 2, 4 and 5; this may be derived by combining the symmetry analysis of Ref.\ \onlinecite{topoferm} with the tracelessness of $\delta\var$ [cf.\ \q{eq:H1}].
+
+%Although these three symmetry classes do not impose constraints on nearly-degenerate orbit, due to the traceless spin splitting Hamiltonian matrix, $\lambda_1+\lambda_2=0$ remains true for nearly-degenerate orbits.
+
+With the inclusion of nonsymmorphic space-group symmetries, it is not uncommon to find energy bands which are (nearly) four-fold degenerate\cite{michel_elementary_2001,wang_hourglass_2016,bradlyn_topological_2017}.
+This motivates a generalization of our rule -- for any number of nearly-degenerate orbits -- that is presented in \app{app:quantizationruleproof}.
+The symmetry-constrained codimensions in the more general case is left to future investigations.
 
@@
 
-We are grateful to Nicholas Read and Judith H\"oller for clarifying notions related to codimensions of matrix degeneracies. 
+We are grateful to Nicholas Read and Judith H\"oller for clarifying notions related to codimensions of eigenvalue-degeneracies.
+An instructive discussion with Victor Yakovenko helped us relate this work  to his `magic angles'.
 We acknowledge support by  the Yale Postdoctoral Prize Fellowship (AA), NSF DMR Grant No.\ 1603243 (LG),  the Ministry of Science and Technology of China, Grant No.\ 2016YFA0301001 (CW and WD), the National Natural Science Foundation of China, Grants No.\ 11674188 and 11334006 (CW and WD) and the Beijing Advanced Innovation Center for Future Chip (ICFC, CW and WD).
@@
 
-%\part{Supplementary Material}
-
 \appendix
@@
 For a single band, the wave function in reciprocal space are expanded as $\phi=\sum_{\boldsymbol{k}}f_{\boldsymbol{k}}\psi_{\boldsymbol{k}}$, where $\psi_{\boldsymbol{k}}$ is modified Bloch wave function whose specific form is presented in Ref.
-[Roth].
+\onlinecite{rotheffham}.
 The effective Hamiltonian then acts on $f_{\boldsymbol{k}}$, changing Shr\"odinger equation to:
@@
 
-%Since direction of external magnetic field is fixed (pointing to $-z$ direction in our convention), only symmetry operators mapping $z$ to $\pm z$ are relevant for cyclotron orbits.
-These symmetry operators can be classified into ten and only ten classes [100p].
-The classification is based several indicators of symmetry operator $g$, namely $u(g)=0~(1)$ representing $g$ is a proper (improper) rotation of the cyclotron orbit and $s(g)=0~(1)$ representing $g$ is unitary (antiunitary).
-However, unlike Ref.
-[100p], only five out of ten symmetry classes impose constraints on $\A$.
-This reduction of relevant symmetry classes is due to components of $\calh$ transforming differently under symmetry operations.
-$\delta\epsilon$ transforms as a scalar but $B\mathcal{M}$ as a pseudovector.
-The five symmetry classes are tabulated in Table \ref{table:codimension} in the main text.
-Here we calculate codimension of degeneracy manifold for all the ten classes since the other five classes are relevant to exactly-degenerate bands.
-
 Sewing matrix is necessary to express the constraints on the propagator $\A$.
@@
 The symmetry constraints on $\A$ expressed using sewing matrix is presented in Ref.
-[100p] and reproduced in Table \ref{table:fullcodimension} for convenience.
+\onlinecite{100p} and reproduced in Table \ref{table:fullcodimension} for convenience.
 Generally, these constraints are derived using the following relation
@@
 For the other six classes, self constraints of $\A$ are imposed.
-In particular, in class 2, 4, 5, $\det(\A)$ is quantized at $\pm 1$ [topofermiology, 100p].
-
-The symmetry constraints in Table \ref{table:fullcodimension} can be divided into two types: (i) class-3, 4 and (ii) other classes.
-For symmetry constraints of type (i), the full propagator is decomposed into products of $L$ (whose meaning will be explained below) segments of the propagator.
-These segments are related to one another by sewing matrix.
-Therefore, we parametrize the first segment of the propagator $\A_{1/L}$ as
+In particular, in class 2, 4, 5, $\det(\A)$ is quantized at $\pm 1$\cite{topoferm,100p}.
+
+The self constraints of the six classes can be divided into two types: (i) restricting $\A$ to only a submanifold of SU(2) (class 1, 2, 5, 6); (ii) expressing the propagator $\A$ as a product of propagators over a fraction of the period [e.g., Eq.
+(\ref{eq:sigmazconstraint})] (class 3, 4).
+For the former case, we define symmetric coordinates by restricting canonical parametrization of $\A$ to that submanifold; in the latter case, we employ the canonical parametrization of the fractional propagators to define symmetric coordinates for the full propagator $\A$.
+For symmetry constraints of type (i), $\A$ fulfills an equation expressed with sewing matrix at the base point of $\A$ (denoted as $\bk_0$).
+Therefore, we parametrize the propagator as
+\e{
+\A = e^{i\theta}\matrixtwo{\alpha}{\beta}{-\beta^*}{\alpha^*}, |\alpha|^2+|\beta|^2=1.
+}
+and look for how many free parameters are left after the symmetry constraint is imposed, which is codimension of degeneracy manifold.
+For symmetry constraints of type (ii) we parametrize the first fractional of the propagator $\A_{1/L}$ as
 \e{
@@
 Then we calculate the full propagator $\A$ and figure out how many parameters is needed to tune $\A$ such that $\A$ is proportional to identity, which is codimension of degeneracy manifold.
-For symmetry constraints of type (ii), $\A$ fulfills an equation expressed with sewing matrix at the base point of $\A$ (denoted as $\bk_0$).
-Therefore, we parametrize the propagator as
-\e{
-\A = e^{i\theta}\matrixtwo{\alpha}{\beta}{-\beta^*}{\alpha^*}, |\alpha|^2+|\beta|^2=1.
-}
-and look for how many free parameters are left after the symmetry constraint is imposed, which is codimension of degeneracy manifold.
-
-\paragraph*{class-1} According to the general rules of sewing matrix, the sewing matrix $\breve{g}$ can be made diagonal by a gauge transformation
+
+\paragraph*{class 1} According to the general rules of sewing matrix, the sewing matrix $\breve{g}$ can be made diagonal by a gauge transformation
 \e{
@@
 
-\paragraph*{class-2}
+\paragraph*{class 2}
 By a gauge transformation, the sewing matrix $\breve{g}$ can be made off-diagonal
@@
 
-\paragraph*{class-3} In this class (and also class-4), the full propagator can be constructed from $1/L$ of it, where $L$ is the smallest positive integer fulfilling $g^L\circ \bk_0=\bk_0$.
+\paragraph*{class 3} In this class (and also class 4), the full propagator can be constructed from $1/L$ of it, where $L$ is the smallest positive integer fulfilling $g^L\circ \bk_0=\bk_0$.
 Here, $\bk_0$ is the base point of $\A$.
@@
 
-\paragraph*{class-5} In class-4, $L=N$ is guaranteed.
-However, in class-5, this is generally not true.
-For symmetry operations still respecting $L=N$, the codimension calculation is similar to what is done in class-4.
+\paragraph*{class 5} In class 4, $L=N$ is guaranteed.
+However, in class 5, this is generally not true.
+For symmetry operations still respecting $L=N$, the codimension calculation is similar to what is done in class 4.
 The only example of $L\ne N$ is $T\mathfrak{c}_{6z,n\boldsymbol{c}/6}$ ($n\in\{0,1,2,3,4,5\}$), where $L=3$ and $N=6$.
@@
 
-\paragraph*{class-5 and 6} Calculation of codimensions for the two classes follow the same pattern as class-1 and 2 and is therefore omitted here.
+\paragraph*{class 5 and 6} Calculation of codimensions for the two classes follow the same pattern as class 1 and 2 and is therefore omitted here.
 
 In the main text, we assume the SOC can be turned off continuously without increasing or decreasing degree of degeneracy.
-With this assumption, $\det(A)=1$ for class-2, 4, 5, reducing Tab.
+With this assumption, $\det(A)=1$ for class 2, 4, 5, reducing Tab.
 \ref{table:fullcodimension} to Tab.

### 2018-12-23 paper.tex
Updates from ShareLaTeX

@@
-\documentclass[aps, prb, showpacs, twocolumn, notitlepage, superscriptaddress]{revtex4-1}
+\documentclass[aps, showpacs, twocolumn, notitlepage, superscriptaddress]{revtex4-1}
 \usepackage{amsmath}
@@
 
-\renewcommand{\topfraction}{1}
-\renewcommand{\bottomfraction}{1}
-\renewcommand{\textfraction}{0.1}
-\renewcommand{\floatpagefraction}{1}
+\renewcommand{\topfraction}{.85}
+\renewcommand{\bottomfraction}{.7}
+\renewcommand{\textfraction}{.15}
+\renewcommand{\floatpagefraction}{.66}
+\renewcommand{\dbltopfraction}{.66}
+\renewcommand{\dblfloatpagefraction}{.66}
 \setcounter{topnumber}{3}
@@
 
-\title{Landau quantization of nearly degenerate bands}
+\title{Landau quantization of nearly degenerate bands, \\
+\red{and non-crossing rules for Landau levels}}
 
@@
 \author{A. Alexandradinata}\affiliation{
-Department of Physics, Yale University, New Haven, Connecticut 06520, USA}
+Department of Physics, Yale University, New Haven, Connecticut 06520, USA}\affiliation{Department of Physics and Institute for Condensed Matter Theory, University of Illinois at Urbana-Champaign, Urbana, Illinois 61801, USA}
 
@@
 The splitting of two nearly-degenerate orbits commonly originates from spin-orbit coupling, or from the breaking of a crystalline point-group symmetry.
-By treating both $\delta S/S$ and $1/l^2S$ ($l$ being the magnetic length) as small parameters with finite ratio $l^2\delta S$, our perspective diverges from and generalizes previous semiclassical theories.
-$1/l^2\delta S$ measures the hybridization of split orbits due to the Zeeman interaction; in the opposing regimes $l^2\delta S {{\ll}} 1$  and $l^2\delta S{\gg}1$, we recover the known Onsager-Lifshitz-Roth rules for nondegenerate and exactly-degenerate orbits, respectively.
-In the absence of crystalline point-group symmetries, three tunable real parameters are needed to attain a spin-degeneracy between two Landau levels; we have exhaustively identified all symmetry classes of orbits for which this number is reduced from three.
-In particular, only one parameter is needed for rotational-symmetric orbits; this parameter may be the magnitude or orientation of the field, or the bias voltage in tunneling spectroscopy.
-A signature of single-parameter tunability is a smooth crossover between period-doubled and -undoubled quantum oscillations in the low-temperature, Schubnikov-de Haas effect.
-We demonstrate the utility of our quantization rule, as well as the tunability of Landau-level degeneracies, for the Rashba two-dimensional electron gas -- subject to an arbitrarily oriented magnetic field, and possibly augmented by the Dresselhaus spin-orbit interaction.
+By treating both $|\delta S/S|$ and $1/l^2|S|$ ($l$ being the magnetic length) as small parameters with finite ratio $l^2|\delta S|$, our perspective diverges from and generalizes previous semiclassical theories.
+$1/l^2|\delta S|$ measures the hybridization of split orbits due to the Zeeman interaction; in the opposing regimes $l^2|\delta S| {\ll} 1$  and $l^2|\delta S|{\gg}1$, we recover the known Onsager-Lifshitz-Roth rules for nondegenerate and exactly-degenerate orbits, respectively.
+We apply our quantization rule to determine the number of tunable, real parameters needed to attain a \red{(pseudo)}spin degeneracy between two Landau levels, \red{i.e., a `non-crossing rule' for Landau levels.
+Three parameters are needed}  in the absence of crystalline point-group symmetries; we have exhaustively identified all symmetry classes of orbits for which this number is reduced from three.
+In particular, only one parameter is needed for orbits which are invariant under spatial rotation \red{or inversion}; this single parameter may be the magnitude or orientation of the field, or the bias voltage in tunneling spectroscopy.
+Signatures of single-parameter tunability include (i) a smooth crossover between period-doubled and -undoubled quantum oscillations in the low-temperature Schubnikov-de Haas effect, as well as (ii) `magic angle' magnetoresistance oscillations.
+We demonstrate the utility of our quantization rule, as well as the tunability of Landau-level degeneracies, for the Rashba-Dresselhaus two-dimensional electron gas -- subject to an arbitrarily oriented magnetic field.
 \end{abstract}
@@
 
+%n close analogy with the Wigner-von Neumann `non-crossing rule' in quantum mechanics, we find that three tunable parameters are needed to attain a Landau-level quasidegeneracy -- in the absence of crystalline point-group symmetries [cf.\ \s{sec:introducecodimension}].
+%We have further determined symmetric variants of the ‘non-crossing rule’ for Landau levels, for any spacetime symmetry that occurs in crystalline solids
+
 \section{Introduction}
 
-Semiclassical quantization rules are well-known for the Landau levels of  both nondegenerate\cite{Onsager,lifshitz_kosevich,lifshitz_kosevich_jetp} and exactly-degenerate\cite{rotheffham,rothmag,topoferm,100p,Mikitik_quantizationrule} energy bands; the latter is exemplified by the spin-degenerate bands of centrosymmetric solids.
-These rules become increasingly accurate as the area of the cyclotron orbit becomes much larger than the inverse square of the magnetic length $l{=}\sqrt{\hbar/eB}$.
-
-Our work generalizes these rules to the Landau quantization of nearly-degenerate bands, whose cyclotron orbits are split in $\bk$-space with a differential area  $\delta S$ that is much less than their average area $S$; $\delta S/S{\ll}1$ shall be referred to as the \textit{near-degeneracy} condition.
-Nearly-degenerate orbits commonly originate from the spin-orbit-splitting of energy bands, as exemplified by a two dimensional electron gas (2DEG) with Rashba spin-orbit coupling:
+\begin{itemize}
+    \item \red{fix all $|S|$ and $\delta S$}
+\end{itemize}
+
+\red{Semiclassical quantization rules compactly describe the energy dispersion of Landau levels, and are predictive of quantum oscillations in transport\cite{SdH} and thermodynamic\cite{dHvA} phenomena.
+The original formulation of the rule  -- by Onsager\cite{Onsager} and Lifshitz\cite{lifshitz_kosevich,lifshitz_kosevich_jetp} -- neglects the effect of spin-orbit coupling.
+While subsequent generalizations by Roth
+\cite{rotheffham,rothmag}
+and the present authors\cite{topoferm,100p} account for the spin-orbit effect, such quantization rules are limited in application to either a single nondegenerate energy band, or to energy-degenerate bands (as exemplified by spin-degenerate bands in centrosymmetric solids).
+It is now recognized that the spin-orbit effect is encoded in subleading corrections to the quantization rule –-- which are associated to the Berry phase and the orbital magnetic moment.}
+
+\red{The Onsager-Lifshitz-Roth rule remains  unapplicable to a wide variety of spin-orbit-coupled metals lacking a spatial inversion center, or having magnetic order.
+The energy bands of such metals carry a spin degree of freedom, and the spin degeneracy of energy bands is weakly lifted by spin-orbit coupling.
+A prototypical example is given by  a two dimensional electron gas (2DEG) with Rashba spin-orbit coupling:}
 \begin{equation}
@@
 \end{equation}
-As illustrated in Fig.\ \ref{fig:orbits}(a), the near-degeneracy condition is satisfied at energies much greater than $m\alpha^2$:\footnote{The expressions for $\delta S$ and $S$ in \q{deltaSvsS} are asymptotically valid for $E{\gg}m\alpha^2$.}
+\red{Given a magnetic field in the $-z$ direction, and focusing on energies much greater than $m\alpha^2$, the cyclotron orbits [illustrated in \fig{fig:orbits}(a)]   are split in $\bk$-space with a differential area  $\delta S$ that is much less than their average area $S$:}\footnote{The expressions for $\delta S$ and $S$ in \q{deltaSvsS} are asymptotically valid for $E{\gg}m\alpha^2$.}
 \e{\delta S = 4\pi m \alpha k_E/\hbar\ll S =\pi k_E^2; \;\; k_{E}:=\f{\sqrt{2m E}}{\hbar}.\label{deltaSvsS}}
-$S$ is equivalently the area of the  constant-energy contour in the absence of spin-orbit coupling ($\alpha{=}0$).
+\red{$S$ is equivalently the area of the  constant-energy contour in the absence of spin-orbit coupling ($\alpha{=}0$).}
 
@@
 
-By treating both $\delta S/S$ and $1/l^2S$  as small parameters with finite ratio $l^2\delta S$, our perspective diverges from and generalizes previous semiclassical theories\cite{kohn_effham,blount_effham,rotheffham,wannier_fredkin,gao_zero-field_2017,topoferm,100p,Mikitik_quantizationrule} which have only a single, small parameter ($1/l^2S$).
+\red{More generally, we refer to 
+$\delta S/S{\ll}1$ (defined geometrically as the ratio of differential to average area) as the \textit{near-degeneracy} condition for energy bands.
+Our work presents a generalized rule to describe the Landau quantization of nearly-degenerate bands, for which  spin-orbit-split bands is but one example.
+This rule becomes increasingly accurate as the average area $S$ becomes much larger than the inverse square of the magnetic length $l{=}\sqrt{\hbar/eB}$.} By treating both $\delta S/S$ and $1/l^2S$  as small parameters with finite ratio $l^2\delta S$, our perspective diverges from and generalizes previous semiclassical theories\cite{kohn_effham,blount_effham,rotheffham,wannier_fredkin,gao_zero-field_2017,topoferm,100p,Mikitik_quantizationrule} which have only a single, small parameter ($1/l^2S$).
 $1/l^2\delta S$ measures the hybridization of nearly-degenerate orbits by the Zeeman interaction.
-In the regime $l^2\delta S{\gg}1$, the Onsager-Lifshitz quantization rules apply independently to  two concentric (but decoupled) orbits.
+In the regime $l^2\delta S{\gg}1$, the Onsager-Lifshitz\red{-Roth} quantization rules apply independently to  two concentric (but decoupled) orbits.
 In the opposite regime $l^2\delta S{\ll}1$, the spin-orbit splitting of energies is negligible, and we may then apply the known quantization rule for exactly-degenerate bands\cite{rotheffham,rothmag,topoferm,100p,Mikitik_quantizationrule}.
-The goal of this work is to formulate a unifying rule that interpolates smoothly between these two known regimes; such a rule is presented in \s{sec:qtznrules}.
-
-In \s{sec:Rashba}, we demonstrate the utility of this rule for the Rashba 2DEG with an arbitrarily-oriented magnetic field, and possibly augmented by the Dresselhaus spin-orbit coupling.
-A sufficiently strong in-plane field not only moves the Dirac point but tilts the Dirac cone over -- into a type-II Dirac point\cite{soluyanov_type-ii_2015}.
+Our unifying rule provides the smooth interpolation between these two known regimes.
+\red{Alternatively stated, we have extended the applicability of quantization rules to the regime where the Zeeman interaction competes with the spin-orbit interaction, where previously such rules were known only when one interaction dominates over the other.
+Indeed, in the absence of magnetic breakdown[references],
+
+This unifying rule is presented in \s{sec:qtznrules} for nearly-degenerate bands with a (pseudo)spin degree of freedom.
+As elaborated in \s{sec:discussion}, the most general formulation of our rule is applicable  to any number of nearly-degenerate bands of any symmetry.}
+
+In \s{sec:Rashba}, we demonstrate the utility of this rule for the Rashba\red{-Dresselhaus} 2DEG with an arbitrarily-oriented magnetic field.
+A sufficiently strong in-plane field not only moves the Dirac point but tilts the Dirac cone over -- into a type-II\cite{soluyanov_type-ii_2015, muechler_tilted_2016, bergholtz_topology_2015} Dirac point.
 In \s{sec:inplanezeeman}, we investigate the Landau-Zener tunneling dynamics that occur in the vicinity of a II-Dirac point; in particular, we will critically evaluate a recent claim\cite{obrien_magnetic_2016} of perfect Klein tunneling at the energy of the Dirac point.
 
-A symmetry analysis (cf.\ \s{sec:llquasideg}) of our quantization rule allows us to determine how many tunable parameters are needed to attain a (pseudo-)spin degeneracy between two Landau levels.
-This degeneracy is exact in symmetry classes where Landau levels are distinguishable by different quantum numbers; absent such quantum numbers, it is still possible for the repulsion between two Landau levels to be anomalously small -- this notion of a Landau-level quasidegeneracy is formulated in \s{sec:relatedegeneracies}.
-Due to a rotational symmetry of the Rashba-Dresselhaus 2DEG, we find that only a single tunable parameter is needed to attain a Landau-level quasidegeneracy (cf.\ \s{sec:ctsrot}); this parameter can be the magnitude or orientation of the field, or the bias voltage in tunneling spectroscopy.
+\red{\s{sec:llquasideg} applies} our quantization rule to determine how many real, tunable parameters are needed to attain a \red{(pseudo)}spin degeneracy between Landau levels.
+\red{This degeneracy may be exact if Landau-quantized wave functions transform in different unitary representations of a spatial symmetry; absent such a symmetry,} it is still possible for the repulsion between two Landau levels to be anomalously weak -- this notion of a Landau-level quasidegeneracy is formulated in \s{sec:relatedegeneracies}.
+\red{In close analogy with the Wigner-von Neumann `non-crossing rule' in quantum mechanics\cite{neumann2000behaviour}, we find that three tunable parameters are needed to attain a Landau-level quasidegeneracy -- in the absence of crystalline point-group symmetries [cf.\ \s{sec:introducecodimension}].
+We have further determined symmetric variants of the Landau-level ‘non-crossing rule’, for any spacetime symmetry that occurs in crystalline solids; our results are summarized in \tab{table:codimension}.
+In particular, we highlight that in the presence of a spatial rotation or inversion symmetry,}  only a single tunable parameter is needed to attain a Landau-level quasidegeneracy (cf.\ \s{sec:ctsrot}); this single parameter may be the magnitude or orientation of the field, or the bias voltage in tunneling spectroscopy.
 
@@
 
-%is not traceless, the traceful part can always be absorbed into the redefinition of $S$ within the accuracy of first order perturbation theory.
-
-%In the  Rashba model,   $\delta \var_{\pm}(E){=}{\pm} (\alpha/\hbar)\sqrt{2mE}$ is independent of $\bk$ due to a continuous rotational symmetry of $H_R$. \\
-
-%the wavepacket;  $g_s{\approx}2$ is the free-electron $g$-factor and $\mu_B$ the Bohr magneton.[100page] 
-%Spin in $z$ direction is represented by $s_z=\hbar\sigma_z/2$ \textbf{[detail]}.
-
 The remaining terms in \q{eq:H1} describe a generalized Zeeman interaction $B\calm$ which is the first-order-in-$B$ correction to the Peierls-Onsager Hamiltonian $\var(\bK)$\cite{rotheffham,blount_effham,kohn_effham}.
@@
 We remark that the quantization rule is invariant under basis transformations within the nearly-degenerate band subspace (see App.
-\ref{app:quantizationruleproof}); in subsequent discussions, it may be more convenient to adopt a $\bk$-independent basis where the non-abelian Berry connection vanishes.
+\ref{app:quantizationruleproof}); in subsequent case studies, it may be more convenient to adopt a $\bk$-independent basis (if such a basis exists) where the non-abelian Berry connection vanishes.
 
@@
 \e{\lambda_{\sma{\pm}} = -\int_0^{T_c}\calh_{\sma{\pm\pm}}\f{dt}{\hbar}=\pm \f{1}{2}l^2\delta S - B\int_0^{T_c}\calm_{\sma{\pm\pm}}\f{dt}{\hbar}.  \label{phaseindependentorbit}} 
-\q{eq:rule}, combined with \q{phaseindependentorbit}, may be identified as the Onsager-Lifshitz rule\cite{Onsager,lifshitz_kosevich,lifshitz_kosevich_jetp} for two independent, nondegenerate orbits of areas $S{\pm}\delta S$, and with subleading phase corrections that were first identified by Roth\cite{rothmag}.\footnote{We remark that \q{phaseindependentorbit} neglects the contribution by band $-$ to the orbital moment of band $+$: $\delta M_z=il^{-2}\epsilon_{\ab}(\delta \var_+-\delta \var_-)\mathfrak{X}^{\alpha}_{+-}\mathfrak{X}^{\beta}_{-+}$.
+\q{eq:rule}, combined with \q{phaseindependentorbit}, may be identified as the Onsager-Lifshitz rule\cite{Onsager,lifshitz_kosevich,lifshitz_kosevich_jetp} for two independent, nondegenerate orbits of areas $S{\pm}\delta S$, and with subleading phase corrections that were first identified by Roth\cite{rothmag}\footnote{We remark that \q{phaseindependentorbit} neglects the contribution by band $-$ to the orbital moment of band $+$: $\delta M_z=il^{-2}\epsilon_{\ab}(\delta \var_+-\delta \var_-)\mathfrak{X}^{\alpha}_{+-}\mathfrak{X}^{\beta}_{-+}$.
 $\mathfrak{X}^{\alpha}_{+-}$, being an off-diagonal matrix element of the position operator, is generically of order a lattice constant $a$.
 We then estimate $\int_0^{T_c} B\delta M_z dt/\hbar=O(a^2 \delta S)$, which is negligible compared to $l^2\delta S/2$.
-Note also that the single-band orbital moment simply vanishes in some symmetry classes of orbits\cite{100p}.} The perturbative inclusion of $B\calm_{\sma{+-}}$ results in a correction to $\lambda_{\pm}$ [cf.\ \q{phaseindependentorbit}] that is expressible as a power series in $B$, with a leading term proportional to $1/B$; this will be confirmed in a subsequent case study [cf.\ \q{lambdasmallB}] and applied to understand beatings in quantum-oscillatory phenomena in \s{sec:qo}.
+Note also that the single-band orbital moment simply vanishes in some symmetry classes of orbits\cite{100p}.}.
+The perturbative inclusion of $B\calm_{\sma{+-}}$ results in a correction to $\lambda_{\pm}$ [cf.\ \q{phaseindependentorbit}] that is expressible as a power series in $B$, with a leading term proportional to $1/B$; this will be confirmed in a subsequent case study [cf.\ \q{lambdasmallB}] and applied to understand beatings in quantum-oscillatory phenomena in \s{sec:qo}.
 
@@
 The upper panel of (b) schematically illustrates  Landau levels near the II-Dirac point (in the weak-hybridization regime).
-The dashed line represents the Onsager-Lifshitz quantization of the trefoil orbit [cf.\ Eq.\ (\ref{trefoilrule})], and the solid line incorporates the first-order correction [cf.\ Eq.\ (\ref{RZfirstorderE})] due to tunneling.
+The dashed line represents the Onsager-Lifshitz-Roth quantization of the trefoil orbit [cf.\ Eq.\ (\ref{trefoilrule})], and the solid line incorporates the first-order correction [cf.\ Eq.\ (\ref{RZfirstorderE})] due to tunneling.
 Lower panel of (b): red dashed line shows the energetic difference between Landau levels determined by numerical diagonalization and Landau levels obtained by the trefoil quantization rule  [cf.\ Eq.\ (\ref{trefoilrule})]; this red dashed line may be compared to the perturbative formula $\delta E_n$ [cf.
@@
 Inset: an enlarged view of near II-Dirac point.
-(d) For various configurations ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in left panel $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that is closest to $\epsilon_0$ in Eq.
-(\ref{whereisdiracpoint}), where $\epsilon_\text{rule}$ is determined by Eq.
+(d) For various parametrizations ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in the left panel the quantity $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that is closest to $\epsilon_0$ [as defined in Eq.
+(\ref{whereisdiracpoint})] $\epsilon_\text{rule}$ is determined by Eq.
 (\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RZ}(\bK)$.
-Corresponding $l^2 \delta S^2/S$ are plotted in right panel.
-We only plotted in region where $0.4{<}\epsilon_0{<}1.0$(eV)\cite{RZfignote}.
+The corresponding $l^2 \delta S^2/S$ is plotted in the right panel.
+For numerical convergence,\cite{RZfignote} we have presented data only in a strip [within ($\alpha$, $Z_\parallel$)-space] where $0.4{<}\epsilon_0{<}1.0$(eV).
 Parameters for (d): $m=0.076m_0$, $l=100$\AA.\label{fig:RZ}}
@@
 $\delta\lambda$ is plotted in the colored background.
-Landau level quasidegeneracies occur at $\delta\lambda\equiv 0\equiv 2\pi$.\label{fig:LL}}
+Landau level quasidegeneracies occur at $\delta\lambda\equiv 0\equiv 2\pi$ (\red{indicated by red dashed lines}).\label{fig:LL}}
 \end{figure}
@@
 Our answer is  $3$ in the absence of symmetry, as discussed in \s{sec:introducecodimension}; the answer may reduce to $0,1$ or $2$ depending on the symmetry class of the orbit, as will be explained in \s{sec:tenfold}.
-Before this general symmetry classification,  we will first develop physical intuition by studying two rotationally-symmetric models [cf.\ \s{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}] where only one tunable parameter is needed -- this can be the $B$ field itself.
+Before this general symmetry classification,  we will first develop physical intuition by studying two rotationally-symmetric models [cf.\ \s{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}] where only one tunable parameter is needed -- this can be \red{the magnitude of} the $B$ field itself.
 
 \subsection{Relating the eigenvalue-degeneracy of $\A$ to the quasidegeneracy of Landau levels}\label{sec:relatedegeneracies}
+
+\red{\fig{fig:LL} illustrates a typical Landau-level dispersion in the near-degeneracy regime ($\delta S{\ll} S)$ of the Rashba 2DEG.
+Each solution of the quantization rule [cf.\ \q{eq:rule}], with fixed $a\in \{1,2\}$ and $n \in \Z$, defines a curve in $(E,B)$-space that we indicate by  a solid black line.
+The condition of eigenvalue-degeneracy for $\A$: \e{\lambda_1(\bar{E},\bar{B})=\lambda_2(\bar{E},\bar{B})+2m\pi, \as m\in \Z \la{eigenvaluedegeneracyA}}
+defines a distinct set of curves [red dashed lines in \fig{fig:LL}] in the symmetry class of the Rashba 2DEG.
+(In other symmetry classes, the eigenvalue-degeneracy for $\A$ may instead define a set of points, or may generically have no solution in $(E,B)$ space.)   The two sets of curves intersect at isolated points where Landau levels are spin degenerate -- to the accuracy of our quantization rule.
+In principle, each intersection may correspond to an exact  degeneracy, if the associated Landau levels belong to different unitary representations of a spatial symmetry -- this subject will be partially addressed in subsequent subsections, but a systematic group-theoretic analysis is involved and will be left to future investigations.}
+
+\red{  Moving away from these intersection points, the repulsion between paired Landau levels  remains anomalously weak (in a manner that will be quantified in \qq{llquasideg}{llquasidegB} below) in the immediate vicinity of the red dashed lines, as illustrated by the purple-shaded regions in \fig{fig:LL}.
+From a pragmatic standpoint, a typical experiment may not be able to distinguish an exact degeneracy from an anomalously weak degeneracy (in short, a \textit{quasidegeneracy}), due to the smearing effects of temperature and/or disorder\cite{shoenberg_magnetic_2009}.
+The existence of  quasidegeneracy lines (i.e., lines of solutions to \q{eigenvaluedegeneracyA}) imposes a distinct signature on the low-temperature Schubnikov-de Haas effect, as will be elaborated in \s{sec:quantosc_quasideg}.
+We are thus motivated to (i) precisely quantify a quasidegeneracy, and (ii) identify the symmetry classes for which quasidegeneracies occur along lines rather than points (or rather than being generically nonexistent).
+The first task is carried out in the rest of this subsection, and the second will be the subject of subsequent subsections in \s{sec:llquasideg}.
+}
 
@@
 $T_{l^2}$ above is the period (in $l^2$) of quantum oscillations -- in the absence of spin-orbit coupling.
-To recapitulate, for every exact degeneracy of $\cala$, there must exist, in close proximity, a number of paired Landau levels which are exactly degenerate, or nearly degenerate in the sense of \qq{llquasideg}{llquasidegB}.
-Each such pair of Landau levels will be called \textit{quasidegenerate}.
+
+To recapitulate, for every exact degeneracy of $\cala$, there exists, in close proximity, an \red{order-one} number of paired Landau levels which are  nearly degenerate in the sense of \qq{llquasideg}{llquasidegB}.
+Each such pair of Landau levels will be described as \textit{quasidegenerate}.
+
+%\red{It is possible that a subset of these quasidegeneracies are in fact exact degeneracies, owing to Landau levels carrying different quantum numbers -- a subject we elaborate in \s{sec:discussion}.}
 
@@
 
-Since $\A$ depends on $\alpha,~\beta,~l,~E,~m$ only through $\hbar\alpha k_E /\var_c$, $\hbar\beta k_E /\var_c$ and $g_sm/m_0$, let us consider the three-dimensional parameter space $(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0){\in} \mathbb{R}^3$.
-$\A(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0){=}{\pm} I$ determines a set of concentric circles in the $\beta{=}0$ plane, as per the $\mathfrak{c}_{\infty}$-symmetric case study in \s{sec:ctsrot}.
+\red{For the Rashba-Dresselhaus 2DEG, $\A$ depends on $\alpha,~\beta,~l,~E,~m$ only through three independent parameters:}%$\hbar\alpha k_E /\var_c$, $\hbar\beta k_E /\var_c$ and $g_sm/m_0$, let us consider the three-dimensional parameter space:
+\e{\left( \f{\hbar\alpha k_{\sma{E}}}{\var_c},\f{\hbar\beta k_{\sma{E}}}{\var_c},g_s\f{m}{m_0} \right){\in} \mathbb{R}^3. \la{parameter2}}  
+$\A(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0){=}{\pm} I$ then determines a set of concentric circles in the $\beta{=}0$ plane, as per the $\mathfrak{c}_{\infty}$-symmetric case study in \s{sec:ctsrot}.
 Moving off this plane, we find that $\A{=}I$ is satisfied in a  neighborhood of $\beta{=}0$, i.e., $\A{=}I$ defines a hypersurface in $\mathbb{R}^3$ that is illustrated in \fig{fig:dgn}(a).
@@
 \ref{app:codimension}, this conclusion generalizes for any $N{\geq}2$: the degenerate manifolds of $\mathfrak{c}_N$-symmetric $\A$ separate the space of symmetric coordinates into $N$ distinct connected components.
-\fig{fig:dgn}(a) illustrates the $\A=I$ degenerate manifold in distinct parameters: $(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0)$.
-On the other hand, $\A{=}{-}I$ occurs if and only if $\br{=}(0,{\pm} 1,0)$; the inverse image of $\br{=}(0,{\pm} 1,0)$ (under $f$) is a path-connected line node confined to the $\alpha{=}0$ and $\beta{=}0$ planes [cf.\ \fig{fig:dgn}(b)]; the difference in codimension originates from the $\mathfrak{c}_{\infty}$ symmetry within these two planes [cf.\ \s{sec:ctsrot}], which was not accounted for in the $\mathfrak{c}_2$-symmetric analysis of \q{proprashba}.
+\fig{fig:dgn}(a) illustrates the $\A=I$ degenerate manifold \red{with  parameters [cf.\ \q{parameter2}] that are distinct from $\br$.}
+
+On the other hand, $\A{=}{-}I$ occurs if and only if $\br{=}(0,{\pm} 1,0)$.
+These two points are mapped to a path-connected line node confined to the $\alpha{=}0$ and $\beta{=}0$ planes [cf.\ \fig{fig:dgn}(b)]; the difference in codimension originates from the $\mathfrak{c}_{\infty}$ symmetry within these two planes [cf.\ \s{sec:ctsrot}], which was not accounted for in the $\mathfrak{c}_2$-symmetric analysis of \q{proprashba}.
 
@@
 $\Delta$ is the differential phase between two Feynman paths  that involve a single tunneling event  over one cyclotron period, as illustrated in Fig. \ref{fig:Cn-breakdown}(d).
-The adiabatic limit is given by $\tau{=}1$ and $\bar{\varphi}{=}0$, which leads to the satisfaction of \q{c2breakdowndgncondition} for $l^2$ equal to an integer multiple of $2\pi/\delta S$ up to a field indepedent offset.
+The adiabatic limit is given by $\tau{=}1$ and $\bar{\varphi}{=}0$, which leads to the satisfaction of \q{c2breakdowndgncondition} for $l^2$ equal to an integer multiple of $2\pi/\delta S$ (up to a field-independent offset).
 As noted in \s{sec:introducecodimension}, such a periodicity corresponds to a differential increment of a single, magnetic flux quantum.
@@
 A completely different physical realization of two orbits linked by Landau-Zener tunneling was proposed in Ref.
-\onlinecite{yakovenko_angular_2006} -- for a bilayer semiconductor heterostructure subject to an obliquely-oriented field.
-The Landau-level quasidegeneracies attained at certain `magic angles' of the field orientation (a single parameter) was theoretically proposed by Yamaji\cite{yamaji_angle_1989}, and experimentally confirmed in Ref.
-\onlinecite{gusev_interlayer_2008}; however, the role of $\mathfrak{c}_2$ symmetry was not recognized in these works.
+\onlinecite{yakovenko_angular_2006} and \textbf{[cite pershoguba and yakovenko]} -- for a bilayer \red{metal} subject to a tilted magnetic field.
+\red{In the absence of hybridization between the top and bottom layers, there are two decoupled orbits in each layer; in this example, the layers replace spin as a two-component degree of freedom.
+In the presence of hybridization,   Landau levels become layer-degenerate} only  at certain `magic angles'\footnote{These magic angles correspond to zeros of a Bessel function, as was first proposed by Yamaji.\cite{yamaji_angle_1989}} of the field orientation (a single parameter); this was experimentally confirmed in Ref.\ \onlinecite{gusev_interlayer_2008}.
+However, the role of $\mathfrak{c}_2$\red{/spatial inversion} symmetry was not recognized in these works.
 
@@
 \ref{sec:introducecodimension}].
-For exactly-degenerate orbits in class 2, 4 and 5, $\A$ satisfies $\text{det}(\A){=}1$,[topofermi] with the assumption that spin-orbit coupling can be turned off continuously without changing the degeneracy of the orbit.
+For exactly-degenerate orbits in class 2, 4 and 5, $\A$ satisfies $\text{det}(\A){=}1$, with the assumption that spin-orbit coupling can be turned off continuously without changing the degeneracy of the orbit\cite{topoferm}.
  \label{table:codimension}}
@@
 The simplest example is of $g$  a reflection symmetry with axis parallel to the field, and of  $\frako_0$ that is confined to a $g$-invariant $\bk$-plane.
-To uniquely determine the symmetry-constrained codimension in class 1, one must specify if the quasi-degenerate bands belong to identical or distinct representations of $g$.
-The symmetry-constrained codimension is reduced to unity in the latter (and only the latter) case, due to the absence of level repulsion between distinct representations of $g$ -- the corresponding quasidegeneracies of Landau levels would then be exact degeneracies, rather than the near degeneracies described by \qq{llquasideg}{llquasidegB}.
-
-Class 3 corresponds to spatial symmetries that preserve the arrow of time and the orientation of $\frako_0$, as exemplified by rotational symmetry with rotational axis parallel to the field.
+To uniquely determine the symmetry-constrained codimension in class 1, one must specify if the nearly degenerate bands belong to identical or distinct representations of $g$.
+The symmetry-constrained codimension is reduced to unity in the latter (and only the latter) case, due to the absence of level repulsion between distinct representations of $g$ \red{\sout{-- the corresponding quasidegeneracies of Landau levels would then be exact degeneracies, rather than the near degeneracies described by \qq{llquasideg}{llquasidegB}}}.
+
+Class 3 corresponds to spatial symmetries that preserve the arrow of time and the orientation of $\frako_0$, as exemplified by spatial rotational symmetry with rotational axis parallel to the field.
+\red{Another example is given  spatial  inversion symmetry, for $\frako_0$ that is confined to an inversion-invariant plane: $k_z=0$ or $\pi$}.
 The symmetry-constrained codimension here is unity, as has been modelled in Sec.\ \ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown}.
@@
 The symmetry-constrained codimension is $2$ or $0$, depending respectively on whether the antiunitary representation of $g$ squares to $+1$ or $-1$.
-The former is exemplified by the composition $T\mathfrak{r}_{y=-x}$ of time reversal with a reflection symmetry (with reflection axis orthogonal to the field); this is a symmetry of the Rashba-Dresselhaus Hamiltonian [cf.\ \q{hamRD}]:
+The former is exemplified by the composition of time reversal with a reflection symmetry (with reflection axis orthogonal to the field); this is a symmetry of the Rashba-Dresselhaus Hamiltonian [cf.\ \q{hamRD}]:
 \e{ g H_{RD}(k_x,k_y)g^{-1} = H(k_y,k_x),\;\; g = e^{i\sigma_z\pi/4}K,}
@@
 The propagator for an orbit in the Brillouin-zone boundary ($k_z{=}\pi$ plane) would then be Kramers-degenerate -- the symmetry-constrained codimension vanishes.
+
+\red{Finally, we point out  that the Rashba 2DEG in a tilted magnetic field, as studied in \ref{sec:inplanezeeman}, also falls into class 6  owing to the symmetry:
+\begin{equation}
+\sigma_z K H_{RZ}(k_x, k_y) K \sigma_z=H_{RZ}(k_x, -k_y).
+\end{equation}
+Consequently, the degeneracy manifolds are lines in the parameter space $(\alpha, B_\parallel, g_s)$.
+Numerically, we have determined that these lines  lie solely within the $B_\parallel=0$ and $\alpha=0$ planes.
+At any point within either  plane,  the Landau levels are exactly solvable.
+For $B_\parallel=0$, $H_{RZ}$ reduces to the Rashba Hamiltonian and the degeneracy manifolds form a series of concentric circles [illustrated in Fig.
+\ref{fig:dgn}(b) with $\beta=0$].
+For $\alpha=0$, the degeneracy manifolds occur at
+\begin{equation}
+    \f{g_s}{4} \frac{ m}{ m_0}\text{sec}(\theta)=n,\;\;(n\in\mathbb{Z}),
+\end{equation}
+with $\theta$ the tilt angle: $\cos(\theta)=B_\perp/\sqrt{B_\perp^2+B_\parallel^2}$. For common semiconductors with $m\ll m_0$, $n=\pm 1$ is attained only for $B_\parallel\gg B_\perp$.
+}
 
@@
 The subleading phase corrections ($\lambda_1,\lambda_2$) in our quantization rule  [\q{eq:rule}] encode the dynamical correction due to the splitting of  orbits, as well as a generalized two-band Zeeman interaction.
-$\lambda_1{=}\lambda_2$ mod $2\pi$, there exist a number (of order one) paired Landau levels which are either exactly spin-degenerate, or nearly spin-degenerate in the sense of \qq{llquasideg}{llquasidegB}, as illustrated in Fig.
+If $\lambda_1{=}\lambda_2$ mod $2\pi$, there exists an order-one number of paired Landau levels which are either exactly spin-degenerate, or nearly spin-degenerate in the sense of \qq{llquasideg}{llquasidegB}.
+Such paired Landau levels have been referred to as \textit{quasidegenerate}, and are illustrated in Fig.
 \ref{fig:LL}.
-Such paired Landau levels have been referred to as \textit{quasidegenerate}.
 
@@
 If the codimension is two, an additional experimentally tunable parameter is needed: e.g., the orientation of the field\cite{yakovenko_angular_2006}, or the bias voltage in tunneling spectroscopy\cite{Sangjun_Cd3As2,Ilija_SnTe,kushwaha_Dirac}.
+
+\red{We highlight a result from  Tab.\ \ref{table:codimension} that is widely applicable: the codimension is unity for orbits having either a spatial inversion or rotation symmetry (class 3).
+Both symmetries are commonly found in solids.
+From a geometric perspective, the quasidegeneracies (in this symmetry class) lie on hypersurfaces in the space of tunable parameters.
+From a topological perspective, each hypersurface is a domain wall that separates distinct connected components, and there are $N$ connected components for orbits with an order-$N$ rotational symmetry; $N=2$ in the case of inversion symmetry.
+This topological distinction between rotational symmetries of different orders has the following implication: if the rotational symmetry is reduced in order, a specific subset of the quasidegeneracies remain stable, as explained in \s{sec:singleparameterrashba} and exemplified for the Rashba-Dresselhaus 2DEG.
+For further motivation in an entirely different context, a reduction in rotational symmetry   occurs also in a phase transition to a nematic Fermi fluid\cite{fradkin_nematic_2010}; it may be possible to utilize  the selective stability of Landau-level quasidegeneracies as an experimental indicator for nematic phase transitions.
+}
 
@@
 
+%\red{Symmetry constrained codimension is the number of parameters needed to find $\lambda_1=\lambda_2 \mod 2\pi$, which is generally not a solution of our quantization rule.
+If one more parameter is available, the simultaneous solution of quantization rule and $\lambda_1=\lambda_2 \mod 2\pi$ can generally found, as illustrated in Fig.
+\ref{fig:LL}.
+These solutions are exact degeneracies in the sense of first order semiclassical approximation.
+It is possible that these solutions are exact even beyond semiclassical approximation, for example when the two crossing Landau levels belongs to the different representation of a symmetry operation.
+A general answer to whether these solutions are always exact degeneracies beyond semiclassical approximation is left for further investigation.}
+
 Our codimension analysis is applicable to contexts beyond that of Landau-level repulsion.
 By keeping only the Berry term in \q{eq:H1}, Eq.\ ({\ref{eq:prop}}) reduces to the Wilson loop of the non-abelian Berry gauge field, i.e., the matrix representation of holonomy.
-Wilson loops can only be classified by symmmetry according to Tab.
-\ref{table:codimension}; the codimensions for an eigenvalue-degeneracy of the Wilson loop are also identical to those listed in   Tab.\ \ref{table:codimension}.
-This observation may be helpful in explaining some movable (but irremovable) crossings in the Wilson-loop spectra of topological crystalline insulators\cite{bouhon_wilson_2018}.
+Any symmetric Wilson loop can be classified according to Tab.\ \ref{table:codimension}; the codimensions for an eigenvalue-degeneracy of the Wilson loop are also identical to those listed in   Tab.\ \ref{table:codimension}.
+Our work thus also explains the existence of robust crossings in the Wilson-loop spectra, which have been widely applied in topological band theory.
+For example, the existence of such crossings have been used to diagnose the presence of a 3D Dirac point protected by rotational symmetry\footnote{This has been observed numerically in \onlinecite{gresch_z2pack:_2017}, and the group-theoretic explanation may be found in Sec.
+VI-D-7 of \onlinecite{100p} or \onlinecite{li_topological_2017}}, as well as to diagnose fragile topological phases with rotational symmetry\cite{bouhon_wilson_2018,bradlyn_disconnected_2018}.
 
 Symmetry does not only constrain the level repulsion between  $\lambda_1$ and $\lambda_2$ -- in certain classes, it constrains their sum.
-In our previous work on exactly-degenerate, spin-differentiated orbits,\cite{100p,topoferm} we have derived a zero-sum rule $\lambda_1{+}\lambda_2{\equiv}0$) in classes  2,4 and 5, with the assumption that spin-orbit coupling can be continuously tuned to zero without changing the degree of degeneracy; this zero-sum rule implies a quantized phase offset for the fundamental harmonic of quantum oscillations.\cite{topoferm} Here, we report that the zero-sum rule applies \textit{also} to nearly-degenerate orbits in classes 2, 4 and 5; this may be derived by combining the symmetry analysis of Ref.\ \onlinecite{topoferm} with the tracelessness of $\delta\var$ [cf.\ \q{eq:H1}].
+In our previous work on exactly-degenerate, spin-differentiated orbits,\cite{100p,topoferm} we have derived a zero-sum rule ($\lambda_1{+}\lambda_2{\equiv}0$) in classes  2,4 and 5, with the assumption that spin-orbit coupling can be continuously tuned to zero without changing the degree of degeneracy; this zero-sum rule implies a quantized phase offset for the fundamental harmonic of quantum oscillations.\cite{topoferm} Here, we report that the zero-sum rule applies \textit{also} to nearly-degenerate orbits in classes 2, 4 and 5; this may be derived by combining the symmetry analysis of Ref.\ \onlinecite{topoferm} with the tracelessness of $\delta\var$ [cf.\ \q{eq:H1}].
 
@@
 An instructive discussion with Victor Yakovenko helped us relate this work  to his `magic angles'.
+We also thank Eduardo Fradkin for educating us on the subject of nematic Fermi fluids.
 We acknowledge support by  the Yale Postdoctoral Prize Fellowship (AA), NSF DMR Grant No.\ 1603243 (LG),  the Ministry of Science and Technology of China, Grant No.\ 2016YFA0301001 (CW and WD), the National Natural Science Foundation of China, Grants No.\ 11674188 and 11334006 (CW and WD) and the Beijing Advanced Innovation Center for Future Chip (ICFC, CW and WD).
@@
 
-\section{Review of effective Hamiltonian}\label{app:revieweffham}
-
-Effective Hamiltonian lies in the heart of semiclassical theory.
+\section{Review of the effective Hamiltonian theory}\label{app:revieweffham}
+
+The effective Hamiltonian lies at the heart of semiclassical theory.
 The leading order term (with respect to $B$) of effective Hamiltonian in momentum representation can be obtained by Peierls substitution of crystal momentum $\boldsymbol{k}$: $\boldsymbol{k}\to\boldsymbol{K}=\boldsymbol{k}+(e/\hbar)\boldsymbol{A}(i\nabla_{\boldsymbol{k}})$ in zero field band structure $\mathfrak{H}_{0}(\boldsymbol{K}):=\epsilon(\boldsymbol{k})$, where $\boldsymbol{A}$ is vector potential.

### 2019-01-29 paper.tex
Updates from ShareLaTeX

@@
 
-\renewcommand{\topfraction}{.85}
-\renewcommand{\bottomfraction}{.7}
-\renewcommand{\textfraction}{.15}
-\renewcommand{\floatpagefraction}{.66}
-\renewcommand{\dbltopfraction}{.66}
-\renewcommand{\dblfloatpagefraction}{.66}
-\setcounter{topnumber}{3}
-\setcounter{bottomnumber}{3}
+%\renewcommand{\topfraction}{.85}
+%\renewcommand{\bottomfraction}{.7}
+%\renewcommand{\textfraction}{.15}
+%\renewcommand{\floatpagefraction}{.66}
+%\renewcommand{\dbltopfraction}{.66}
+%\renewcommand{\dblfloatpagefraction}{.66}
+%\setcounter{topnumber}{3}
+%\setcounter{bottomnumber}{3}
 
@@
 \title{Landau quantization of nearly degenerate bands, \\
-\red{and non-crossing rules for Landau levels}}
+and full symmetry classification of avoided Landau-level crossings}
 
@@
 \begin{abstract}
-In the semiclassical theory of Landau levels, a Bloch electron is driven by a magnetic field  along constant-energy band contours  known as cyclotron orbits.
-We introduce a quantization rule for Landau levels of nearly-degenerate orbits whose differential area ($\delta S$) in $\bk$-space is much smaller than their average area $S$.
-The splitting of two nearly-degenerate orbits commonly originates from spin-orbit coupling, or from the breaking of a crystalline point-group symmetry.
-By treating both $|\delta S/S|$ and $1/l^2|S|$ ($l$ being the magnetic length) as small parameters with finite ratio $l^2|\delta S|$, our perspective diverges from and generalizes previous semiclassical theories.
-$1/l^2|\delta S|$ measures the hybridization of split orbits due to the Zeeman interaction; in the opposing regimes $l^2|\delta S| {\ll} 1$  and $l^2|\delta S|{\gg}1$, we recover the known Onsager-Lifshitz-Roth rules for nondegenerate and exactly-degenerate orbits, respectively.
-We apply our quantization rule to determine the number of tunable, real parameters needed to attain a \red{(pseudo)}spin degeneracy between two Landau levels, \red{i.e., a `non-crossing rule' for Landau levels.
-Three parameters are needed}  in the absence of crystalline point-group symmetries; we have exhaustively identified all symmetry classes of orbits for which this number is reduced from three.
-In particular, only one parameter is needed for orbits which are invariant under spatial rotation \red{or inversion}; this single parameter may be the magnitude or orientation of the field, or the bias voltage in tunneling spectroscopy.
-Signatures of single-parameter tunability include (i) a smooth crossover between period-doubled and -undoubled quantum oscillations in the low-temperature Schubnikov-de Haas effect, as well as (ii) `magic angle' magnetoresistance oscillations.
+Semiclassical quantization rules compactly describe the energy dispersion of Landau levels, and are predictive of quantum oscillations in transport and thermodynamic quantities.
+Such rules –- as formulated by Onsager, Lifshitz and Roth –-
+apply when the spin-orbit interaction dominates over the Zeeman interaction (or vice versa), but does not generally apply  when the two interactions are comparable in strength.
+In this work, we present a generalized quantization rule which treats the spin-orbit and Zeeman interactions on equal footing, and therefore has wider applicability to spin-orbit-coupled materials lacking a spatial inversion center, or having magnetic order.
+More generally, our rule describes the Landau quantization of any number of nearly degenerate energy bands -- in any symmetry class.
+The resultant Landau-level spectrum is generically non-equidistant but may contain \blue{spin (or pseudospin)} degeneracies.
+To tune to such degeneracies in the absence of crystalline point-group symmetries, three real parameters are needed.
+We have exhaustively identified all symmetry classes of cyclotron orbits for which this number is reduced from three, thus establishing symmetry-enforced`non-crossing rules' for Landau levels.
+In particular, only one parameter is needed {in the presence of} spatial rotation {or inversion}; this single parameter may be the magnitude or orientation of the field.
+Signatures of single-parameter tunability include (i) a smooth crossover between period-doubled and -undoubled quantum oscillations in the low-temperature Shubnikov-de Haas effect, as well as (ii) `magic-angle' magnetoresistance oscillations.
 We demonstrate the utility of our quantization rule, as well as the tunability of Landau-level degeneracies, for the Rashba-Dresselhaus two-dimensional electron gas -- subject to an arbitrarily oriented magnetic field.
@@
 \section{Introduction}
-
-\begin{itemize}
-    \item \red{fix all $|S|$ and $\delta S$}
-\end{itemize}
-
-\red{Semiclassical quantization rules compactly describe the energy dispersion of Landau levels, and are predictive of quantum oscillations in transport\cite{SdH} and thermodynamic\cite{dHvA} phenomena.
+In the semiclassical theory of a Bloch electron in a magnetic field,  quantization rules not  only serve as a compact description of the  energy dispersion of Landau levels, they also form the basis for a quantitative theory of quantum oscillations in transport\cite{SdH} and thermodynamic\cite{dHvA} quantities.
 The original formulation of the rule  -- by Onsager\cite{Onsager} and Lifshitz\cite{lifshitz_kosevich,lifshitz_kosevich_jetp} -- neglects the effect of spin-orbit coupling.
-While subsequent generalizations by Roth
-\cite{rotheffham,rothmag}
-and the present authors\cite{topoferm,100p} account for the spin-orbit effect, such quantization rules are limited in application to either a single nondegenerate energy band, or to energy-degenerate bands (as exemplified by spin-degenerate bands in centrosymmetric solids).
-It is now recognized that the spin-orbit effect is encoded in subleading corrections to the quantization rule –-- which are associated to the Berry phase and the orbital magnetic moment.}
-
-\red{The Onsager-Lifshitz-Roth rule remains  unapplicable to a wide variety of spin-orbit-coupled metals lacking a spatial inversion center, or having magnetic order.
-The energy bands of such metals carry a spin degree of freedom, and the spin degeneracy of energy bands is weakly lifted by spin-orbit coupling.
-A prototypical example is given by  a two dimensional electron gas (2DEG) with Rashba spin-orbit coupling:}
+While subsequent generalizations by Roth,
+\cite{rotheffham,rothmag} Mikitik\cite{Mikitik_quantizationrule},
+and the present authors\cite{topoferm,100p} account for the spin-orbit effect, such quantization rules apply only when the spin-orbit splitting of energy bands is much stronger (or much weaker) than the Zeeman interaction.
+
+A quantization rule that treats the spin-orbit and Zeeman interactions on equal footing has yet to be formulated.
+Such a rule would be especially relevant to spin-orbit-coupled materials lacking a spatial inversion center, or having magnetic order.
+The energy bands of these materials carry a spin-half degree of freedom, and the spin degeneracy of energy bands is weakly lifted by spin-orbit coupling or magnetic ordering.
+A prototypical example is given by  a two-dimensional electron gas (2DEG) with Rashba spin-orbit coupling:
 \begin{equation}
@@
 \end{equation}
-\red{Given a magnetic field in the $-z$ direction, and focusing on energies much greater than $m\alpha^2$, the cyclotron orbits [illustrated in \fig{fig:orbits}(a)]   are split in $\bk$-space with a differential area  $\delta S$ that is much less than their average area $S$:}\footnote{The expressions for $\delta S$ and $S$ in \q{deltaSvsS} are asymptotically valid for $E{\gg}m\alpha^2$.}
+Given a magnetic field in the $-z$ direction, and focusing on energies much greater than $m\alpha^2$, the cyclotron orbits [illustrated in \fig{fig:orbits}(a)]   are split in $\bk$-space with a differential area  $\delta S$ that is much less than their average area $S$:\footnote{The expressions for $\delta S$ and $S$ in \q{deltaSvsS} are asymptotically valid for $E{\gg}m\alpha^2$.}
 \e{\delta S = 4\pi m \alpha k_E/\hbar\ll S =\pi k_E^2; \;\; k_{E}:=\f{\sqrt{2m E}}{\hbar}.\label{deltaSvsS}}
-\red{$S$ is equivalently the area of the  constant-energy contour in the absence of spin-orbit coupling ($\alpha{=}0$).}
+$S$ is equivalently the area of the constant-energy contour in the absence of spin-orbit coupling ($\alpha{=}0$).
 
@@
 
-\red{More generally, we refer to 
-$\delta S/S{\ll}1$ (defined geometrically as the ratio of differential to average area) as the \textit{near-degeneracy} condition for energy bands.
-Our work presents a generalized rule to describe the Landau quantization of nearly-degenerate bands, for which  spin-orbit-split bands is but one example.
-This rule becomes increasingly accurate as the average area $S$ becomes much larger than the inverse square of the magnetic length $l{=}\sqrt{\hbar/eB}$.} By treating both $\delta S/S$ and $1/l^2S$  as small parameters with finite ratio $l^2\delta S$, our perspective diverges from and generalizes previous semiclassical theories\cite{kohn_effham,blount_effham,rotheffham,wannier_fredkin,gao_zero-field_2017,topoferm,100p,Mikitik_quantizationrule} which have only a single, small parameter ($1/l^2S$).
-$1/l^2\delta S$ measures the hybridization of nearly-degenerate orbits by the Zeeman interaction.
-In the regime $l^2\delta S{\gg}1$, the Onsager-Lifshitz\red{-Roth} quantization rules apply independently to  two concentric (but decoupled) orbits.
-In the opposite regime $l^2\delta S{\ll}1$, the spin-orbit splitting of energies is negligible, and we may then apply the known quantization rule for exactly-degenerate bands\cite{rotheffham,rothmag,topoferm,100p,Mikitik_quantizationrule}.
+Our work presents a generalized rule to describe the Landau quantization of nearly-degenerate energy bands, for which  spin-orbit-split bands is but one example.
+\blue{By the \textit{near-degeneracy} condition, we generally mean that
+the ratio of differential to average area is small: $|\delta S/S|{\ll}1$.
+Our proposed rule relies also on a second condition -- that $S$ is much larger than the inverse square of the magnetic length $l{=}\sqrt{\hbar/eB}$; this is the standard semiclassical condition in the Onsager-Lifshitz-Roth theory.} By treating \textit{both} $|\delta S/S|$ and $1/l^2|S|$   as small parameters with finite ratio $l^2|\delta S|$, our perspective diverges from and generalizes \textit{single-parameter} semiclassical theories.\cite{kohn_effham,blount_effham,rotheffham,wannier_fredkin,fischbeck_review,Mikitik_quantizationrule,topoferm,100p,gao_zero-field_2017}
+
+The inverse ratio $1/l^2|\delta S|$ measures the hybridization of nearly-degenerate orbits by the Zeeman interaction.
+In the regime $l^2|\delta S|{\gg}1$, the Onsager-Lifshitz{-Roth} quantization rules apply independently to  two concentric (but decoupled) orbits.
+In the opposite regime $l^2|\delta S|{\ll}1$, the spin-orbit splitting of energies is negligible, and we may then apply the known quantization rule for exactly-degenerate bands\cite{rotheffham,rothmag,topoferm,100p,Mikitik_quantizationrule}.
 Our unifying rule provides the smooth interpolation between these two known regimes.
-\red{Alternatively stated, we have extended the applicability of quantization rules to the regime where the Zeeman interaction competes with the spin-orbit interaction, where previously such rules were known only when one interaction dominates over the other.
-Indeed, in the absence of magnetic breakdown[references],
-
-This unifying rule is presented in \s{sec:qtznrules} for nearly-degenerate bands with a (pseudo)spin degree of freedom.
+{Equivalently stated, we have extended the applicability of quantization rules to the intermediate regime ($l^2|\delta S|{\sim}1$) where the Zeeman interaction is comparable with the spin-orbit interaction; previously, such rules were known only when one interaction dominates over the other.
+This extension allows  to formulate semiclassical quantization rules for spin-orbit coupled materials in \textit{any} symmetry class -- with or without spatial inversion symmetry, with or without time-reversal symmetry.
+The unifying rule is presented in \s{sec:qtznrules} for nearly-degenerate bands with a spin\blue{-half (or pseudospin-half)} degree of freedom.
 As elaborated in \s{sec:discussion}, the most general formulation of our rule is applicable  to any number of nearly-degenerate bands of any symmetry.}
 
-In \s{sec:Rashba}, we demonstrate the utility of this rule for the Rashba\red{-Dresselhaus} 2DEG with an arbitrarily-oriented magnetic field.
+In \s{sec:Rashba}, we demonstrate the utility of this rule for the Rashba{-Dresselhaus} 2DEG with an arbitrarily-oriented magnetic field.
 A sufficiently strong in-plane field not only moves the Dirac point but tilts the Dirac cone over -- into a type-II\cite{soluyanov_type-ii_2015, muechler_tilted_2016, bergholtz_topology_2015} Dirac point.
-In \s{sec:inplanezeeman}, we investigate the Landau-Zener tunneling dynamics that occur in the vicinity of a II-Dirac point; in particular, we will critically evaluate a recent claim\cite{obrien_magnetic_2016} of perfect Klein tunneling at the energy of the Dirac point.
-
-\red{\s{sec:llquasideg} applies} our quantization rule to determine how many real, tunable parameters are needed to attain a \red{(pseudo)}spin degeneracy between Landau levels.
-\red{This degeneracy may be exact if Landau-quantized wave functions transform in different unitary representations of a spatial symmetry; absent such a symmetry,} it is still possible for the repulsion between two Landau levels to be anomalously weak -- this notion of a Landau-level quasidegeneracy is formulated in \s{sec:relatedegeneracies}.
-\red{In close analogy with the Wigner-von Neumann `non-crossing rule' in quantum mechanics\cite{neumann2000behaviour}, we find that three tunable parameters are needed to attain a Landau-level quasidegeneracy -- in the absence of crystalline point-group symmetries [cf.\ \s{sec:introducecodimension}].
-We have further determined symmetric variants of the Landau-level ‘non-crossing rule’, for any spacetime symmetry that occurs in crystalline solids; our results are summarized in \tab{table:codimension}.
-In particular, we highlight that in the presence of a spatial rotation or inversion symmetry,}  only a single tunable parameter is needed to attain a Landau-level quasidegeneracy (cf.\ \s{sec:ctsrot}); this single parameter may be the magnitude or orientation of the field, or the bias voltage in tunneling spectroscopy.
-
-In \s{sec:quantosc_quasideg}, we propose  the signature of single-parameter tunability in the low-temperature Schubnikov-de Haas effect\cite{SdH}: a smooth crossover between period-doubled and -undoubled quantum oscillations.
+In \s{sec:inplanezeeman}, we investigate the Landau-Zener tunneling dynamics that occur in the vicinity of a II-Dirac point; in particular, we will {demonstrate that our quantization rule can account for quantum tunneling between nearly-degenerate bands -- a phenomenon known as interband breakdown\cite{kaganov_coherent_1983,slutskin_dynamics_1968,AALG,100p}.
+We will also} critically evaluate a recent claim\cite{obrien_magnetic_2016} of perfect Klein tunneling at the energy of the Dirac point -- \blue{we find that such tunneling is never perfect with a proper account of the Zeeman interaction.}
+
+{\s{sec:llquasideg} applies} our quantization rule to determine how many real parameters are needed to tune to a {pseudo}spin-half degeneracy in the Landau-level spectrum.
+{This degeneracy may be exact if Landau-quantized wave functions transform in different unitary representations of a spatial symmetry; absent such a symmetry,} it is still possible for the repulsion between two Landau levels to be anomalously weak -- this notion of a Landau-level quasidegeneracy is formulated in \s{sec:relatedegeneracies}.
+In close analogy with the Wigner-von Neumann `non-crossing rule' in quantum mechanics\cite{neumann2000behaviour}, we find that three tunable parameters are needed to attain a Landau-level quasidegeneracy -- in the absence of crystalline point-group symmetries (cf.\ \s{sec:introducecodimension}).
+We have further determined symmetric variants of the Landau-level ‘non-crossing rule’, for any spacetime symmetry that occurs in crystalline solids; our results are summarized in Tab.
+\ref{table:codimension-nearlydegen}-\ref{table:codimension-exactlydegen}.
+In particular, we highlight that in the presence of a spatial rotation or inversion symmetry,  only a single tunable parameter is needed to attain a Landau-level quasidegeneracy (cf.\ \s{sec:ctsrot}); this single parameter may be the magnitude or orientation of the field, or the Landau-level index itself.
+
+In \s{sec:quantosc_quasideg}, we propose a signature of single-parameter tunability in the low-temperature Shubnikov-de Haas effect\cite{SdH}: a smooth crossover between period-doubled and -undoubled quantum oscillations.
 For a harmonic analysis of  quantum oscillations, we present in \s{sec:quantosc_equidis} a generalized Lifshitz-Kosevich formula that inputs our quantization rule and outputs harmonics.
@@
 The quantization rule for Landau levels reflects the single-valuedness of the semiclassical (WKB) wavefunction\cite{berry_mount_review} over $\frako_0$, i.e.,  the phase accumulated by an electron (over one cyclotron period $T_c$) is an integer multiple of $2\pi$: $(l^2S(E){+}\gamma)/2\pi{\in}\Z$.
-The leading-order phase   is the classical action $l^2S{:}{=}{-}l^2\int_{0}^{T_c} k_x \dot{k}_y dt$; $S$ has a dual interpretation as the signed area (in $\bk$-space) enclosed by $\frako_0$, as illustrated in Fig.
+The leading-order phase   is the classical action $l^2S{:}{=}{-}l^2\int_{0}^{T_c} k_x \dot{k}_y dt$; $S$ has a dual interpretation as the signed area (positive for electron like orbits) in $\bk$-space enclosed by $\frako_0$, as illustrated in Fig.
 \ref{fig:orbits}(b).
@@
 The remaining terms in \q{eq:H1} describe a generalized Zeeman interaction $B\calm$ which is the first-order-in-$B$ correction to the Peierls-Onsager Hamiltonian $\var(\bK)$\cite{rotheffham,blount_effham,kohn_effham}.
-Included in this interaction is the Zeeman coupling to the spin ($g_s\mu_Bs_z/\hbar$) and orbital ($M_z$) magnetic moment\cite{thonhauser_orbital_2005} of the nearly-degenerate band; the latter is expressible in terms of matrix elements of the velocity operator $\boldsymbol{\Pi}_{mn}=i\langle\psi_m|[\hat{H}, \hat{\boldsymbol{r}}]|\psi_n\rangle/\hbar$ between Bloch wave functions $\psi_{n\bk}$:
-\e{
-M_z=\f{ie\hbar}{2}\sum_l'\f{\Pi_{x,ml}\Pi_{y,ln}-\Pi_{y,ml}\Pi_{x,ln}}{\epsilon_m-\epsilon_l}. \label{eq:orbitalmoment}
+Included in this interaction is the Zeeman coupling to the spin ($g_s\mu_Bs_z/\hbar$) and orbital ($M_z$) magnetic moment\cite{thonhauser_orbital_2005} of the nearly-degenerate band; the latter is expressible in terms of matrix elements of the velocity operator $\boldsymbol{\Pi}_{mn}=i\langle\psi_m|[\hat{H}_0, \hat{\boldsymbol{r}}]|\psi_n\rangle/\hbar$ between Bloch wave functions $\psi_{n\bk}$:
+\e{
+[M_z]_{mn}=\f{ie\hbar}{2}\sum_l'\f{\Pi_{x,ml}\Pi_{y,ln}-\Pi_{y,ml}\Pi_{x,ln}}{\epsilon_m-\epsilon_l}. \label{eq:orbitalmoment}
 }
 Here, the summation in $l$ does not include the two nearly-degenerate bands.
-There is finally a geometric contribution to the Zeeman interaction, which involves the two-by-two non-Abelian Berry connection\cite{berry_quantal_1984} as well as the  zeroth-order band velocity:
-\e{\mathfrak{X}_{\beta,mn}{=}i\braket{u_m}{\partial u_n/\partial k_{\beta}},  \;\;v_{\alpha}:= \f{1}{\hbar}\p{\var}{k_{\alpha}},\label{berryconn}}
+There is finally a geometric contribution to the Zeeman interaction, which involves the two-by-two non-Abelian Berry connection\cite{berry_quantal_1984,wilczek_appearance_1984} as well as the  zeroth-order band velocity:
+\e{\mathfrak{X}_{\beta,mn}{=}i\braket{u_m}{\partial u_n/\partial k_{\beta}},  \;\;\;v_{\alpha}:= \f{1}{\hbar}\p{\var}{k_{\alpha}},\label{berryconn}}
 with $\{u_n\}_{n=1}^2$ the periodic component of Bloch functions. 
@@
 
-\qq{eq:rule}{berryconn} allow us to determine $\lambda_{1,2}$ to the lowest order  in $1/l^2S$ and $\delta S/S$, and for arbitrary values of $l^2\delta S$ and $|B\calm|/\delta \var_{\pm}$.
+\qq{eq:rule}{berryconn} allow us to determine $\lambda_{1,2}$ to the lowest order  in $1/l^2|S|$ and $|\delta S/S|$, and for arbitrary finite values of $l^2|\delta S|$ and $|B\calm|/\delta \var_{\pm}$.
 We remark that the quantization rule is invariant under basis transformations within the nearly-degenerate band subspace (see App.
-\ref{app:quantizationruleproof}); in subsequent case studies, it may be more convenient to adopt a $\bk$-independent basis (if such a basis exists) where the non-abelian Berry connection vanishes.
+\ref{app:quantizationruleproof}).
+In subsequent case studies, it may be analytically convenient to adopt a $\bk$-independent basis for $\calh$, if such a basis exists; the non-abelian Berry connection -- defined with respect to this basis -- vanishes.
+
+%In other words,  \qq{eq:rule}{berryconn} is equally valid with $\{u_n\}_{n=1}^2$ replaced by energy eigenfunctions of $\hat{H}_0$ which are not simultaneously eigenfunctions of $\delta \hat{H}$.
+
+%In subsequent case studies, it may be analytically convenient to adopt a $\bk$-independent basis, if such a basis exists; the non-abelian Berry connection defined with respect to this basis would vanish.
 
@@
 \noi{i} If $|\var_+{-}\var_-|$ is everywhere (along $\frako_0$) much greater than $B|\calm_{+-}|$, then an electron would undergo adiabatic (band-conserving) dynamics\cite{nenciu_review} along two independent, nondegenerate orbits.
-Such an adiabatic regime always exists as $B{\rightarrow} 0$ for nearly-degenerate orbits that do not intersect, e.g, at a type-II Dirac point, which is the subject of the case studies in \s{sec:inplanezeeman} and \s{sec:rotsymmbreakdown}.
+Such an adiabatic regime always exists as $B{\rightarrow} 0$ for nearly-degenerate orbits that do not intersect.
+(Such intersection occurs, e.g., at a type-II Dirac point, which is the subject of the case studies in \s{sec:inplanezeeman} and \s{sec:rotsymmbreakdown}.)
 By  neglecting  $B\calm_{+-}$ in favor of intraband elements,  $\cala$ reduces to a diagonal matrix with  diagonal entries ($e^{i\lambda_{\pm}}$) given by:
 \e{\lambda_{\sma{\pm}} = -\int_0^{T_c}\calh_{\sma{\pm\pm}}\f{dt}{\hbar}=\pm \f{1}{2}l^2\delta S - B\int_0^{T_c}\calm_{\sma{\pm\pm}}\f{dt}{\hbar}.  \label{phaseindependentorbit}} 
-\q{eq:rule}, combined with \q{phaseindependentorbit}, may be identified as the Onsager-Lifshitz rule\cite{Onsager,lifshitz_kosevich,lifshitz_kosevich_jetp} for two independent, nondegenerate orbits of areas $S{\pm}\delta S$, and with subleading phase corrections that were first identified by Roth\cite{rothmag}\footnote{We remark that \q{phaseindependentorbit} neglects the contribution by band $-$ to the orbital moment of band $+$: $\delta M_z=il^{-2}\epsilon_{\ab}(\delta \var_+-\delta \var_-)\mathfrak{X}^{\alpha}_{+-}\mathfrak{X}^{\beta}_{-+}$.
-$\mathfrak{X}^{\alpha}_{+-}$, being an off-diagonal matrix element of the position operator, is generically of order a lattice constant $a$.
+\q{eq:rule}, combined with \q{phaseindependentorbit}, may be identified as the Onsager-Lifshitz rule\cite{Onsager,lifshitz_kosevich,lifshitz_kosevich_jetp} for two independent, nondegenerate orbits of areas $S{\pm}\delta S$, and with subleading phase corrections that were first identified by Roth\cite{rothmag}\footnote{\q{phaseindependentorbit} neglects the contribution by band $-$ to the single-band orbital moment\cite{chang_berry_1996} of band $+$.
+This contribution is equal to $B\delta M_z=il^{-2}\epsilon_{\ab}(\delta \var_+-\delta \var_-)\mathfrak{X}^{\alpha}_{+-}\mathfrak{X}^{\beta}_{-+}$.
+$\mathfrak{X}^{\alpha}_{+-}$, being an off-diagonal matrix element of the position operator, is generically of order the lattice constant $a$.
 We then estimate $\int_0^{T_c} B\delta M_z dt/\hbar=O(a^2 \delta S)$, which is negligible compared to $l^2\delta S/2$.
 Note also that the single-band orbital moment simply vanishes in some symmetry classes of orbits\cite{100p}.}.
-The perturbative inclusion of $B\calm_{\sma{+-}}$ results in a correction to $\lambda_{\pm}$ [cf.\ \q{phaseindependentorbit}] that is expressible as a power series in $B$, with a leading term proportional to $1/B$; this will be confirmed in a subsequent case study [cf.\ \q{lambdasmallB}] and applied to understand beatings in quantum-oscillatory phenomena in \s{sec:qo}.
+With the perturbative inclusion of $B\calm_{\sma{+-}}$, $\lambda_{\pm}$ [cf.\ \q{phaseindependentorbit}] would then be expressible as a Laurent series in $B$, with a leading term proportional to $1/B$; this will be confirmed in a subsequent case study [cf.\ \q{lambdasmallB}] and applied to understand beatings in quantum-oscillatory phenomena [cf.\ \s{sec:qo}].
 
@@
 
-The quantization rule, summarized by \qq{eq:rule}{berryconn}, is the technical accomplishment of this work; the remainder of this work is focused on unpacking its physical implications.
+The quantization rule, as summarized by \qq{eq:rule}{berryconn}, is the technical accomplishment of this work; the remainder of this work is focused on unpacking its physical implications.
 We will first demonstrate the utility of our rule in case studies where the adiabatic approximation is invalid, and $\delta \epsilon$ competes with $B\calm$.
@@
 
-\subsection{2DEG with Rashba and Dresselhaus spin-orbit interactions}\label{sec:Rashba}
-
-We will first apply our rule to the Landau levels of the Rashba model [cf.\ \q{eq:Rashba-Hamiltonian}], for which analytic expressions exist for verification\cite{bychkov_oscillatory_1984}; shortly after we will demonstrate the utility of our quantization rule for the 2DEG with both Rashba and Dresselhaus spin-orbit interactions, for which there exists no known analytic closed-form solution.
+\subsection{Rashba 2DEG with an out-of-plane field}\label{sec:Rashba}
+
+In this section, we apply our rule to the Landau levels of the Rashba model [cf.\ \q{eq:Rashba-Hamiltonian}], for which analytic, closed-form solutions exist for verification.\cite{bychkov_oscillatory_1984}
 
@@
 In the energy basis of the Rashba Hamiltonian $H_R$ [cf.\ \q{eq:Rashba-Hamiltonian}],
-\e{\calh(\bk)=-\hbar\alpha k\tau_z{+}\f{g_s}{2}\mu_{\sma{B}}B\tau_x {-} \f{eB\hbar}{2m} (\tau_x-I) \epsilon_{\alpha\beta} k_{\alpha}\nabla_{\beta}\theta,\label{rashbaeffham}}
+\e{\calh(\bk)=-\hbar\alpha k\tau_z{+}\f{g_{s\perp}}{2}\mu_{\sma{B}}B\tau_x {-} \f{eB\hbar}{2m} (\tau_x-I) \epsilon_{\alpha\beta} k_{\alpha}\nabla_{\beta}\theta,\label{rashbaeffham}}
 where $\tau_i$ are a new set of Pauli matrices with $\tau_z{=}{+} 1$ and ${-}1$ corresponding to the outer and inner orbits, respectively.
-$e^{i\theta_{\bk}}{=}(ik_x{-}k_y)/k$ is the angle of the in-plane spin-splitting field $(-\hbar\alpha k_y,\hbar\alpha k_x,0)$ of $H_R$, which winds once over $\frako_0$; the spin of our basis vectors likewise winds, in parallel (or anti-parallel) alignment with this field (see Fig.
+$e^{i\theta_{\bk}}{=}(ik_x{-}k_y)/k$ is the angle of the in-plane spin-splitting field $(-\hbar\alpha k_y,\hbar\alpha k_x,0)$ of $H_R$ [cf.\ \q{eq:Rashba-Hamiltonian}], which winds once over $\frako_0$; the spin of our basis vectors likewise winds, in parallel (or anti-parallel) alignment with this field (see Fig.
 (\ref{fig:orbits})(b)).
-Terms proportional to the rate of spin rotation ($\nabk \theta$) originate from the non-abelian Berry connection.
+Terms proportional to the rate of spin rotation ($\nabk \theta$) originate from the non-Abelian Berry connection.
 The first term of  $\calh$ corresponds to the spin-orbit-induced splitting of the energy-degenerate bands;
 the remaining terms may be interpreted as $B$-induced deformations of the bands.
-It is well-known that the Zeeman term tends to polarize spin in the direction of $\bB$; remarkably, the non-abelian Berry term  also has a polarizing effect, but with opposite sign.
-These two effects completely cancel for free electrons ($m{=}m_0$, with $m_0$ being free electron mass.), but not generically in band systems.
-The orbital moment term $B M_z$, which generally couples the two-band subspace (of interest) to all other bands, is absent in any simplified two-band model.
+The orbital moment term $B M_z$, which generally couples the two-band subspace (of interest) to all other bands, is absorbed into the Zeeman spin interaction with a phenomenological g-factor $g_{s\perp}$.\footnote{For simplicity, we neglect here off-diagonal elements of $M_z$ in the basis of $S_z=\pm 1/2$, with $\vec{z}$ the direction of the field.} It is well-known that the Zeeman term tends to polarize spin in the direction of $\bB$; remarkably, the non-Abelian Berry term  also has a polarizing effect, but with opposite sign.
+These two effects completely cancel for free electrons (with $g_{s\perp}=2$ and $m$ equal to the free-electron mass $m_0$), but not generically in band systems.
+%is absent in any simplified two-band model.
 
@@
 \begin{equation}
-\lambda_{\pm}=\pm\f1{2}\sqrt{({l^2\delta S})^2+\pi^2(g_sm/m_0-2)^2}+\pi. \label{eq:Rashba-lambda}
+\lambda_{\pm}=\pm\f1{2}\sqrt{({l^2\delta S})^2+\pi^2(g_{s\perp}m/m_0-2)^2}+\pi. \label{eq:Rashba-lambda}
 \end{equation}
@@
 
-In the weak-hybridization regime: $l^2\delta S \gg \pi|g_s m/m_0{-}2|$, we may expand \q{eq:Rashba-lambda} as a Laurent series in $B$:
-\e{\lambda_{\pm}= \pm \f{l^2\delta S}{2} +\pi \pm \f{\pi^2}{4}\f{(g_sm/m_0-2)^2}{l^2\delta S} + O(B^2). \label{lambdasmallB}}
+In the weak-hybridization regime: $l^2\delta S \gg \pi|g_{s\perp} m/m_0{-}2|$, we may expand \q{eq:Rashba-lambda} as a Laurent series in $B$:
+\e{\lambda_{\pm}= \pm \f{l^2\delta S}{2} +\pi \pm \f{\pi^2}{4}\f{(g_{s\perp}m/m_0-2)^2}{l^2\delta S} + O(B^2). \label{lambdasmallB}}
 \q{eq:rule}, combined with the first two terms on the right-hand-side of \q{lambdasmallB}, may alternatively be derived from  the standard Onsager-Lifshitz rules for two independent orbits, with a common $\pi$ Berry-phase correction for each orbit:\footnote{The intra-band Zeeman and orbital-moment couplings vanish due spacetime-inversion symmetry\cite{topoferm}.} $l^2(S{\pm}\delta S)/2\pi {\in}\Z$.
 Higher-order terms in \q{lambdasmallB} reflect the field-induced hybridization of the spin-orbit-split orbits.
-
-In the strong hybridization regime where $l^2\delta S {\ll}\pi(g_sm/m_0{-}2)$, $\lambda_{\pm}{\approx}{\pm}\pi g_sm/2m_0$ mod $2\pi$, which corresponds to the Zeeman splitting of Landau levels by $g_{s}\mu_BB$, in the \textit{absence} of the spin-orbit interaction.
-
-Our quantization rule [\q{eq:rule} with \q{eq:Rashba-lambda}] may be compared with the  exact Landau-level spectrum of the Peierls-substituted Hamiltonian $H_R(\bK)$.
-The exact levels are given implicitly by\cite{bychkov_oscillatory_1984}
+Eq.\ (\ref{lambdasmallB}) has been partially obtained by Mineev for the Rashba model;\cite{mineev_haas--van_2005} he missed the second term in $(g_{s\perp}m/m_0-2)$ [cf.\ \q{lambdasmallB}], due to his neglect of the interband Berry connection.
+
+In the strong-hybridization regime where $l^2\delta S {\ll}\pi(g_{s\perp}m/m_0{-}2)$, $\lambda_{\pm}{\approx}{\pm}\pi g_{s\perp}m/2m_0$ mod $2\pi$, which corresponds to the Zeeman splitting of Landau levels by $g_{s}\mu_BB$, in the \textit{absence} of the spin-orbit interaction.
+
+Our quantization rule [\q{eq:rule} with \q{eq:Rashba-lambda}] may be compared with the  exact Landau-level spectrum of the Peierls-substituted Hamiltonian $H_R(\bK)$ (plus the Zeeman coupling to spin).
+The exact levels\cite{bychkov_oscillatory_1984} are given implicitly by
 \e{
 &n_{\pm}=\frac{l^2S}{2\pi}+\frac{l^2\delta S}{16\pi}\f{\delta S}{S}\lin 
-&\pm\f1{2}\sqrt{\bigg(\frac{l^2\delta S}{8\pi}\f{\delta S}{S}\bigg)^2+(l^2\delta S)^2+\pi^2(\f{g_sm}{m_0}-2)^2},\label{eq:Rashba-exact}}
+&\pm\f1{2}\sqrt{\bigg(\frac{l^2\delta S}{8\pi}\f{\delta S}{S}\bigg)^2+(l^2\delta S)^2+\pi^2\bigg(\f{g_{s\perp}m}{m_0}-2\bigg)^2},\label{eq:Rashba-exact}}
 with the functional forms of $\delta S(E)$ and $S(E)$ provided in \q{deltaSvsS};  $n_{+}{\ge} 1$ and $n_-{\ge} 0$ here are integer-valued labels for two distinct sets of levels.
-In the nearly-degenerate regime ($E{\gg}m\alpha^2$), terms involving $\delta S/S$ may be neglected and \q{eq:Rashba-exact} reduces to our quantization rule with $\lambda_{\pm}$ given by \q{eq:Rashba-lambda}.
-
-Our quantization rule equally has utility where no closed-form analytic expression exists for the spectrum. Such is the case when we introduce a Dresselhaus spin-orbit coupling:
-\begin{equation}
- H_{RD}(\bk)=\frac{{\hbar^2}k^2}{2m}+\hbar\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+\hbar\beta(k_{x}\sigma_{x}-k_{y}\sigma_{y}).\label{hamRD}
-\end{equation}
-In Fig.\ \ref{fig:RD}(b-d), a comparison is made between the Landau levels obtained from exact numerical diagonalization of $H_{RD}(\bK)$ (by standard techniques reviewed in App.
-\ref{sec:numerical}) and those obtained from the quantization rule.
-The difference in energies tends to increase with smaller field [compare the left and right panels of   \fig{fig:RD}(b)] and shows a strong positive correlation with $l^2\delta S(\alpha,\beta)^2/S$ [compare \fig{fig:RD}(c) with \fig{fig:RD}(d)] for various choices of the spin-orbit parameters $(\alpha,\beta)$.
-This correlation may be anticipated from \q{eq:Rashba-exact}, which analytically demonstrates how terms involving $l^2\delta S^2/S$ modifies the quantization rule in the case where $\beta{=}0$.
-For our chosen parameters,  the difference in energies does not exceed $2\%$ of $\var_c$ as $l^2\delta S^2/S$ varies over $[0,0.75]$.
-
-In \s{sec:llquasideg} we will further motivate the study of $H_{RD}$ by investigating the prevalence of Landau-level degeneracies.
-
-\begin{figure}
-\includegraphics[width=1.0\columnwidth]{RD.png}
-\caption{Rashba-Dresselhaus model.
-(a) Typical cyclotron orbits.
-(b) Comparison of Landau levels calculated by Eq.
-(\ref{eq:rule}) (black lines) and numerical diagonalization of the Peierls-Onsager Hamiltonian  $H_{RD}(\bK)$ (red dots).
-Parameters for (b): $\alpha=7.5\times10^{5}$cm/s, $m=0.076m_0$, $\beta=3.0(6.0)\times 10^{5}$cm/s for left (right) panels.
-(c) For various spin-orbit parameters $(\alpha,\beta)$ of the Rashba-Dresselhaus model and various field strength (satisfying $l^2S(E)\gg 1$), we plot  $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that lies closest to energy $E=0.4eV$, where $\epsilon_\text{rule}$ is determined by Eq.
-(\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian  $H_{RD}(\bK)$.
-We also plot in (d) $l^2\delta S^2/S$, which has a strong positive relation with error in (c).
-Parameters for (c-d): $m=0.076m_0$.
-Units: $\alpha$($10^{5}$cm/s), $\beta$($10^{5}$cm/s), $l^2 S$($10^2$).\label{fig:RD}}
-\end{figure}
-
-\subsection{Rashba 2DEG with in-plane Zeeman field}\label{sec:inplanezeeman}
+\blue{In the near-degenerate ($\delta S/S\ll 1$) and semiclassical ($1/l^2S \ll 1$) regime, with finite $l^2\delta S$,}  the two terms in \q{eq:Rashba-exact} involving $\delta S/S$  may be neglected, and \q{eq:Rashba-exact} reduces to our quantization rule with $\lambda_{\pm}$ given by \q{eq:Rashba-lambda}.
+
+\blue{With the further inclusion of the Dresselhaus spin-orbit interaction in \q{eq:Rashba-Hamiltonian}, no closed-form analytic solution (of the Landau levels) is known.
+We may anyway verify the validity of our approximation scheme  -- by comparison with the Landau levels obtained from numerical exact diagonalization; this  is carried out in  \app{app:approximatevsexact}.}
+
+%The just-stated inequality is equivalent to an upper bound on the Landau-level index: $n_{\pm}{\ll} (S/\delta S)^2$, which is distinct from the lower bound $n_{\pm}{\gg} 1$ dictated by the usual semiclassical condition.
+
+%In the near-degenerate regime ($E{\gg}m\alpha^2$),
+
+\subsection{Case study of breakdown: Rashba 2DEG with tilted field}\label{sec:inplanezeeman}
 
@@
 H_{RZ}=\f{{\hbar^2}k^{2}}{2m}+\delta \var; \;\;\;\delta \var=d_x\sigma_x+d_y\sigma_y,\lin
-(d_x,d_y):=(-\hbar\alpha k_y,\hbar\alpha k_x+\zpar),\;\;\;\zpar:= g_s \mu_B B_{\parallel}/2.
+(d_x,d_y):=(-\hbar\alpha k_y,\hbar\alpha k_x+\zpar),\;\;\;\zpar:= g_{s\parallel} \mu_B B_{\parallel}/2.
 \label{eq:RZ-Hamiltonian}}
@@
 \e{
-H & =\hbar\alpha\left[\left(\sigma_y-\frac{\zpar}{m\alpha^2}\right)\delta k_{x}-\delta k_{y}\sigma_{x}\right]+\epsilon_{0}.}
+H & =\hbar\alpha\left[\left(\sigma_y-\frac{\zpar}{m\alpha^2}\right)\delta k_{x}-\sigma_{x}\delta k_{y}\right]+\epsilon_{0}.}
 When $|\zpar|>|m\alpha^2|$, the Dirac cone tilts over in the $x$ direction, leading to a Lifshitz transition  of the constant-energy band contours -- from circular to hyperbolic (in the linearized approximation), as illustrated in Fig.
-\ref{fig:RZ}(c).
+\ref{fig:RZ}(a).
 An over-tilted Dirac cone shall be referred to as type-II.
-Our case study of a II-Dirac point  connects  two electron-like  pockets [cf.\ \fig{fig:RZ}(a,c)], and  differs from previous case studies\cite{obrien_magnetic_2016,AALG} that connect an electron- and hole-like pocket.
+Our case study of a II-Dirac point  connects  two electron-like  pockets [cf.\ \fig{fig:RZ}(a,b)], and  differs from previous case studies\cite{obrien_magnetic_2016,AALG} that connect an electron- and hole-like pocket.
 
@@
 \includegraphics[width=1.0\columnwidth]{RZ.png}
-\caption{Characterization of the Rashba 2DEG with an in-plane Zeeman field.
-(a) illustrates the trefoil-shaped cyclotron orbit at the energy of the II-Dirac point.
-The orbit is drawn over the  spin-splitting field ($d_x,d_y$) of the degeneracy-lifting Hamiltonian $\delta\var$ [cf.\ \q{eq:RZ-Hamiltonian}].
-The wavefunction along the inner (resp.\ outer) component of the trefoil orbit has its pseudospin aligned parallel (resp.\ anti-parallel) to the spin-splitting field.
-The upper panel of (b) schematically illustrates  Landau levels near the II-Dirac point (in the weak-hybridization regime).
-The dashed line represents the Onsager-Lifshitz-Roth quantization of the trefoil orbit [cf.\ Eq.\ (\ref{trefoilrule})], and the solid line incorporates the first-order correction [cf.\ Eq.\ (\ref{RZfirstorderE})] due to tunneling.
-Lower panel of (b): red dashed line shows the energetic difference between Landau levels determined by numerical diagonalization and Landau levels obtained by the trefoil quantization rule  [cf.\ Eq.\ (\ref{trefoilrule})]; this red dashed line may be compared to the perturbative formula $\delta E_n$ [cf.
+\caption{(a) illustrates the cyclotron orbits of the Rashba 2DEG in a \blue{tilted} magnetic field.
+The inset illustrates an enlarged view of near II-Dirac point.
+(b) illustrates the cyclotron orbit at the energy of the II-Dirac point; \blue{a Klein-tunneling electron will follow a trajectory that resembles the edge of a M\"obius strip.} The orbit is drawn over the  spin-splitting field ($d_x,d_y$) of the degeneracy-lifting Hamiltonian $\delta\var$ [cf.\ \q{eq:RZ-Hamiltonian}].
+The wavefunction along the inner (resp.\ outer) component of the \blue{M\"obius-strip} orbit has its pseudospin aligned parallel (resp.\ anti-parallel) to the spin-splitting field.
+(c) schematically illustrates  Landau levels near the II-Dirac point (in the weak-hybridization regime).
+The dashed line represents the Onsager-Lifshitz-Roth quantization of the \blue{M\"obius-strip} orbit [cf.\ Eq.\ (\ref{trefoilrule})], and the solid line incorporates the first-order correction [cf.\ Eq.\ (\ref{RZfirstorderE})] due to tunneling.
+(d) \blue{The black solid line is the plot of $\delta E_n$ [cf.
+Eq.
+(\ref{RZfirstorderE})], which is the energetic correction due to deviations from perfect Klein tunneling; for comparison, the red dashed line shows the numerically-exact deviations obtained from exact diagonalization.} This comparison is made for the Landau levels closest to 0.45eV and with even Landau-level index $n$; for the parameters we have chosen ($m{=}0.076m_0$, $\alpha{=} 1.5\times10^{5}$cm/s, $Z_\parallel {=}$1meV and $g_{s\perp}=2$),  the II-Dirac point lies at 0.5eV.
+%Out-of-plane Zeeman coupling is negligibly weak.
+\label{fig:RZ}}
+\end{figure}
+
+%red dashed line shows the energetic difference between Landau levels determined by numerical diagonalization and Landau levels obtained by the M\"obius quantization rule  [cf.\ Eq.\ (\ref{trefoilrule})]; this red dashed line may be compared to the perturbative formula $\delta E_n$ [cf.
 Eq.
 (\ref{RZfirstorderE})], which is plotted as a black solid line.
-This comparison is made (at each $1/B$) for the Landau level closest to 0.45eV and with even Landau-level index $n$; the II-Dirac point is located at 0.5eV.
-Parameters for lower panel of (b): $m{=}0.076m_0$, $\alpha{=} 1.5\times10^{5}$cm/s, $Z_\parallel {=}$1meV.
-Out-of-plane Zeeman coupling is negligibly weak for the choice of $m$.
-(c) A sketch of cyclotron orbits of Rashba Hamiltonian with in-plane magnetic field.
-Inset: an enlarged view of near II-Dirac point.
-(d) For various parametrizations ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in the left panel the quantity $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that is closest to $\epsilon_0$ [as defined in Eq.
-(\ref{whereisdiracpoint})] $\epsilon_\text{rule}$ is determined by Eq.
-(\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RZ}(\bK)$.
-The corresponding $l^2 \delta S^2/S$ is plotted in the right panel.
-For numerical convergence,\cite{RZfignote} we have presented data only in a strip [within ($\alpha$, $Z_\parallel$)-space] where $0.4{<}\epsilon_0{<}1.0$(eV).
-Parameters for (d): $m=0.076m_0$, $l=100$\AA.\label{fig:RZ}}
-\end{figure}
-
-In addition to the in-plane field, let us also apply an out-of-plane field $B_{\perp}$, with associated magnetic length $\lper{=}\sqrt{\hbar/eB_{\perp}}$, cyclotron energy $\var^{\sma{\perp}}_c{:}{=}\hbar^2/m\lper^2{:}{=}\hbar \omega_c^{\sma{\perp}}{:}{=}h/T_c^{\sma{\perp}}$ and Zeeman coupling to the spin magnetic moment:  $\zper{:}{=}{g_s}\mu_B B_{\perp}/2$.
+
+In addition to the in-plane field, let us also apply an out-of-plane field $B_{\perp}$, with associated magnetic length $\lper{=}\sqrt{\hbar/eB_{\perp}}$, cyclotron energy $\var^{\sma{\perp}}_c{:}{=}\hbar^2/m\lper^2{:}{=}\hbar \omega_c^{\sma{\perp}}{:}{=}h/T_c^{\sma{\perp}}$ and Zeeman coupling to the spin magnetic moment:  $\zper{:}{=}{g_{s\perp}}\mu_B B_{\perp}/2$.
 We shall assume  $1/\lper^2S{\ll}1$, where $S$ is the area of the zeroth-order orbit (with effective mass $m$ and radius $k_E{=}\sqrt{2mE}/\hbar$).
-For energies much greater than $m\alpha^2$ and $\zpar$, the nearly-degeneracy condition ($\delta S/S{\ll}1$) is met, where $\delta S$ is the differential area induced by both spin-orbit and in-plane Zeeman couplings [see \fig{fig:RZ}(a)].
+For energies much greater than $m\alpha^2$ and $\zpar$, the nearly-degeneracy condition ($\delta S/S{\ll}1$) is met, where $\delta S$ is the differential area induced by both spin-orbit and in-plane Zeeman couplings [see \fig{fig:RZ}(b)].
 The smallness of $1/\lper^2S$ and $\delta S/S$ (with finite ratio $\lper^2\delta S$) justifies our application of the quantization rule [\qq{eq:rule}{eq:H1}],  with the effective Hamiltonian:
@@
 \end{equation}
-$t$ here is a time variable which parametrizes the zeroth-order orbit:
+Here, $t$ is a time variable which parametrizes the zeroth-order orbit:
 $\bk(t){=}({-}k_E \cos \omega_c^{\sma{\perp}} t, k_E \sin \omega_c^{\sma{\perp}} t )$.
-In the momentum-independent spin basis of \q{calHRZ}, the non-Abelian Berry connection vanishes, hence the generalized Zeeman interaction $B_{\sma{\perp}}\calm$ simply reduces to the Zeeman interaction with the spin  moment: $Z_\perp\sigma_{z}$.
+In the momentum-independent spin basis of \q{calHRZ}, the non-Abelian Berry connection $\mathfrak{X}$ [in \q{eq:H1}]  vanishes, hence the generalized Zeeman interaction $B_{\sma{\perp}}\calm$ simply reduces to the Zeeman coupling to the spin  moment: $Z_\perp\sigma_{z}$.
 
@@
 \onlinecite{obrien_magnetic_2016} in a different model of the II-Dirac point.
-However, with a proper account of $Z_\perp$, we find instead that $\bar{\mu}$ has a nonvanishing minimum: $\bar{\mu}_{\sma{\text{min}}}{:}{=} ( m/m_0)(Z_\perp/4\hbar\alpha k_{E})$, which is a product of the dimensionless effective mass and the ratio of the out-of-plane Zeeman splitting over the spin-orbit splitting.
-This minimum is practically negligible for  semiconductor heterostructures with $m{\ll}m_0$, but may be relevant in heavy-fermion systems.
+However, with a proper account of $Z_\perp$, we find instead that $\bar{\mu}$ has a nonvanishing minimum: $\bar{\mu}_{\sma{\text{min}}}{:}{=} (g_{s\perp} m/m_0)(Z_\perp/4\hbar\alpha k_{E})$, which is a product of the dimensionless effective mass and the ratio of the out-of-plane Zeeman splitting over the spin-orbit splitting.
+\blue{This minimum may be significant for semiconductor heterostructures (e.g.,  $g_{s\perp}m/m_0{\sim} 1$ in InAs heterostructures\cite{pakmehr_g-factor_2015}) and  for heavy-fermion systems.}
 
@@
 \includegraphics[width=1.0\columnwidth]{blochsphere.png}
-\caption{Solid-angle representation of  the single-band Berry phase $\phi_{\pm}^B$ for inner (subscript $-$, upper panel) and outer ($+$, lower panel) orbit, at various energies close to the Dirac point $\epsilon_0$ [cf.\ Eq.
+\caption{Solid-angle representation of  the single-band Berry phase $\phi_{\pm}^B$ for inner (subscript $-$, upper panel) and outer ($+$, lower panel) orbit, at various energies close to the Dirac-point energy $\epsilon_0$ [cf.\ Eq.
 (\ref{whereisdiracpoint})].
@@
 $\phi_{\pm}^B$ equals half the solid angle subtended by   ${\mp} \boldsymbol{\calh}(\bk)$ [solid blue line] as $\bk$ is varied along the outer/inner orbit\cite{berry_quantal_1984}; the orientation of the solid angle is indicated by blue dotted lines.
-The out-of-plane Zeeman interaction lifts $\boldsymbol{\calh}$ out of the $x-y$ plane, but this occurs at most over a fraction ${\sim}(\bar{\mu}_{\sma{\text{min}}}m_0/m{\ll}1)$ of the cyclotron period.
+The out-of-plane Zeeman interaction lifts $\boldsymbol{\calh}$ out of the $x-y$ plane, but this effect is significant only over a fraction $(\sim Z_{\perp}/\hbar \alpha k_E)$  of the cyclotron period.
+% ${\sim}[(\bar{\mu}_{\sma{\text{min}}}/g_{s\perp})(m_0/m){\ll}1]$
 \label{fig:blochsphere}}
@@
 To derive the above equation, we have utilized $\phi^B_-{+}\phi^B_+{=}0$, which is valid for any two-band model in the nearly-degenerate regime\footnote{For two band models, Berry phases of the two bands sum up to 0 on arbitrary path}; in \fig{fig:blochsphere} this is reflected in the sum of solid angles (at fixed energy) equalling $4\pi$.
-\q{trefoilrule} may be interpreted as a quantization rule for a trefoil-shaped orbit with net area $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels (sketched by solid lines in the upper panel of Fig.
-\ref{fig:RZ}(b)) are periodic in $E{\rightarrow}E{+}\pi/l^2(\partial S/\partial E)$ and in $l^2{\rightarrow}l^2{+}\pi/S$.
+\q{trefoilrule} may be interpreted as a quantization rule for a trajectory on a M\"obius strip  with net area $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels (sketched by solid lines in the upper panel of Fig.
+\ref{fig:RZ}(c)) are periodic in $E{\rightarrow}E{+}\pi/l^2(\partial S/\partial E)$ and in $l^2{\rightarrow}l^2{+}\pi/S$.
 Both periods are approximately half that of either disconnected  orbit, in the assumed nearly-degenerate regime $\delta S{\ll}S$.
-The $\pi$ correction in \q{trefoilrule} is the Berry phase associated to a $2\pi$ rotation of the wavefunction spin over a single trefoil orbit, as illustrated in Fig.
-\ref{fig:RZ}(a).
-The Maslov phase, which is generally equal to $\pi$ times the rotation number of an orbit, is trivially $2\pi$ for the trefoil orbit.
-
-To recapitulate, $E_n^0(B)$ [cf.\ \q{trefoilrule}] exhibits a periodicity on short scales associated to the large area of the trefoil orbit.
-This short-scale periodicity is lost due to  finite-$\tau$ corrections, yet a longer-range correlation (associated to the smaller differential area $\delta S$ between spin-split orbits) persists, as shown by the first-order-in-$\tau$ correction:\footnote{The general form of this perturbative calculation can be found in Sec.
+The $\pi$ correction in \q{trefoilrule} is the Berry phase associated to a $2\pi$ rotation of the wavefunction spin over a single M\"obius orbit, as illustrated in Fig.
+\ref{fig:RZ}(b).
+The Maslov phase, which is generally equal to $\pi$ times the rotation number of an orbit, is trivially $2\pi$ for the M\"obius orbit.
+
+To recapitulate, $E_n^0(B)$ [cf.\ \q{trefoilrule}] exhibits a periodicity on short scales associated to the large area of the M\"obius orbit.
+This short-scale periodicity is lost due to  imperfect Klein tunneling, yet a longer-range correlation (associated to the smaller differential area $\delta S$ between spin-split orbits) persists, as shown by the first-order-in-$\tau$ correction:\footnote{The general form of this perturbative calculation can be found in Sec.
 IX-E of Ref.
@@
 with the right-hand side (of each line) evaluated at $E{=}E_n^0(B)$.
-The second line is an approximation for $Z_{\perp}{\rightarrow}0$, and has greater utility where $m{\ll}m_0$.
-$E_n^{(0)}+\delta E_n$ are sketched in the upper panel of Fig.
-\ref{fig:RZ}(b) as dashed lines.
-The validity of Eq.
-(\ref{RZfirstorderE}) is confirmed by a comparison between $\delta E_n$ in Eq.
-(\ref{RZfirstorderE}) and $\delta E_n$ extracted from numerical diagonalization in the lower panel of Fig.
-\ref{fig:RZ}(b).
-
-If the nearly-degenerate orbits are appreciably hybridized ($\hbar\alpha k_{\sma{E}}{\lesssim}\var_c$), our quantization rule \qq{eq:rule}{eq:H1} remains valid but the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}.
-We may anyway diagonalize $\cala$ numerically, and compare the resultant semiclassical Landau levels with the exact diagonalization of $H_{RZ}(\boldsymbol{K})$; to our knowledge, there exists no analytic solution of $H_{RZ}(\boldsymbol{K})$ for generic values of $\alpha,\zpar$ and $B_{\perp}$.
-For fixed  $B_{\perp}$ and a range of $(\alpha,\zpar)$ wherein  $l^2\delta S^2/S$ varies over $[0,0.2]$, the difference between semiclassical and exact Landau levels never exceeds  0.3\% of the cyclotron energy $\var_c$; this difference shows a strong positive correlation with $l^2\delta S^2/S$ [compare the left and right panels of Fig.\ \ref{fig:RZ} (d)], just like in the Rashba-Dresselhaus model.
-
-\section{Tuning the spin-degeneracy of Landau Levels}\label{sec:llquasideg}
+The second line is an approximation for $Z_{\perp}{\rightarrow}0$, and has greater utility where $g_{s\perp}m{\ll}m_0$.
+\blue{For two adjacent Landau levels, we have plotted $E_n^{(0)}+\delta E_n$ as dashed lines in Fig.
+\ref{fig:RZ}(c).
+The validity of Eq.\ (\ref{RZfirstorderE}) is  further supported by a comparison with numerically-exact Landau levels, as illustrated in Fig.\ \ref{fig:RZ}(d).}
+
+\section{Tuning the (pseudo)spin-half degeneracy of Landau Levels}\label{sec:llquasideg}
 
@@
 $\delta\lambda$ is plotted in the colored background.
-Landau level quasidegeneracies occur at $\delta\lambda\equiv 0\equiv 2\pi$ (\red{indicated by red dashed lines}).\label{fig:LL}}
+Landau level quasidegeneracies occur at $\delta\lambda\equiv 0\equiv 2\pi$ ({indicated by red dashed lines}).\label{fig:LL}}
 \end{figure}
 
-We have argued in \s{sec:qtznrules} that the subleading corrections ($\lambda_{1,2}$) to the quantization rule [cf.\ \q{eq:rule}] generically lift the spin-degeneracy of Landau levels -- the level splitting is approximately $\var_c\delta \lambda/2\pi$ with $\delta \lambda=|\lambda_1-\lambda_2|$.
+{The Landau levels derived from \q{eq:rule} are generically non-equidistant, and the spin\blue{-half (or pseudospin-half)} degeneracy between Landau levels is generically lifted due to the subleading corrections ($\lambda_{1,2}$).
+As argued in \s{sec:qtznrules},} the level splitting is approximately $\var_c\delta \lambda/2\pi$ with $\delta \lambda=|\lambda_1-\lambda_2|$.
 Conversely, Landau levels are approximately spin-degenerate if $\lambda_1{=}\lambda_2$ (mod $2\pi$) -- this degeneracy condition for the eigenvalues of $\A$ may require fine-tuning of the Peierls-Onsager Hamiltonian.
 
-In \s{sec:relatedegeneracies}, we will describe the precise relation between eigenvalue-degeneracies of  $\A$ and (near) degeneracies of Landau levels.
+In \s{sec:relatedegeneracies}, we will relate the eigenvalue-degeneracies of  $\A$ to the (near) degeneracies of Landau levels.
 We then ask how many tunable real parameters are needed to attain an eigenvalue-degeneracy of $\A$.
-Our answer is  $3$ in the absence of symmetry, as discussed in \s{sec:introducecodimension}; the answer may reduce to $0,1$ or $2$ depending on the symmetry class of the orbit, as will be explained in \s{sec:tenfold}.
-Before this general symmetry classification,  we will first develop physical intuition by studying two rotationally-symmetric models [cf.\ \s{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}] where only one tunable parameter is needed -- this can be \red{the magnitude of} the $B$ field itself.
+Our answer is  $3$ in the absence of crystallographic point-group symmetry, as discussed in \s{sec:introducecodimension}; the answer may reduce to $0,1$ or $2$ depending on the symmetry class of the orbit, as will be explained in \s{sec:tenfold}.
+Before this general symmetry classification,  we will first develop physical intuition by studying two rotationally-symmetric models [cf.\ \s{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}] where only one tunable parameter is needed -- this can be the magnitude of the $B$ field itself.
 
@@
 
-\red{\fig{fig:LL} illustrates a typical Landau-level dispersion in the near-degeneracy regime ($\delta S{\ll} S)$ of the Rashba 2DEG.
+\fig{fig:LL} illustrates a typical Landau-level dispersion in the near-degeneracy regime ($\delta S{\ll} S)$ of the Rashba 2DEG (in an out-of-plane field).
 Each solution of the quantization rule [cf.\ \q{eq:rule}], with fixed $a\in \{1,2\}$ and $n \in \Z$, defines a curve in $(E,B)$-space that we indicate by  a solid black line.
 The condition of eigenvalue-degeneracy for $\A$: \e{\lambda_1(\bar{E},\bar{B})=\lambda_2(\bar{E},\bar{B})+2m\pi, \as m\in \Z \la{eigenvaluedegeneracyA}}
-defines a distinct set of curves [red dashed lines in \fig{fig:LL}] in the symmetry class of the Rashba 2DEG.
-(In other symmetry classes, the eigenvalue-degeneracy for $\A$ may instead define a set of points, or may generically have no solution in $(E,B)$ space.)   The two sets of curves intersect at isolated points where Landau levels are spin degenerate -- to the accuracy of our quantization rule.
-In principle, each intersection may correspond to an exact  degeneracy, if the associated Landau levels belong to different unitary representations of a spatial symmetry -- this subject will be partially addressed in subsequent subsections, but a systematic group-theoretic analysis is involved and will be left to future investigations.}
-
-\red{  Moving away from these intersection points, the repulsion between paired Landau levels  remains anomalously weak (in a manner that will be quantified in \qq{llquasideg}{llquasidegB} below) in the immediate vicinity of the red dashed lines, as illustrated by the purple-shaded regions in \fig{fig:LL}.
+defines a distinct set of curves [red dashed lines in \fig{fig:LL}] -- for the symmetry class of the Rashba 2DEG.
+(For other symmetry classes, the eigenvalue-degeneracy for $\A$ may instead define a set of points, or may generically have no solution in $(E,B)$ space.)   The two sets of curves (solid and dashed) intersect at isolated points where Landau levels are spin degenerate -- to the accuracy of our quantization rule.
+In principle, such an intersection may correspond to an exact  degeneracy, if the associated Landau levels belong to different unitary representations of a spatial symmetry -- this subject will be partially addressed in subsequent subsections, but a systematic group-theoretic analysis is involved and will be left to future investigations.
+
+Moving away from these intersection points, the repulsion between paired Landau levels  remains anomalously weak (in a manner that will be quantified in \qq{llquasideg}{llquasidegB} below) in the immediate vicinity of the red dashed lines, as illustrated by the purple-shaded regions in \fig{fig:LL}.
 From a pragmatic standpoint, a typical experiment may not be able to distinguish an exact degeneracy from an anomalously weak degeneracy (in short, a \textit{quasidegeneracy}), due to the smearing effects of temperature and/or disorder\cite{shoenberg_magnetic_2009}.
-The existence of  quasidegeneracy lines (i.e., lines of solutions to \q{eigenvaluedegeneracyA}) imposes a distinct signature on the low-temperature Schubnikov-de Haas effect, as will be elaborated in \s{sec:quantosc_quasideg}.
-We are thus motivated to (i) precisely quantify a quasidegeneracy, and (ii) identify the symmetry classes for which quasidegeneracies occur along lines rather than points (or rather than being generically nonexistent).
+The existence of  quasidegeneracy lines (i.e., lines of solutions to \q{eigenvaluedegeneracyA}) imposes a distinct signature on the low-temperature Shubnikov-de Haas effect, as will be elaborated in \s{sec:quantosc_quasideg}.
+We are thus motivated to (i) precisely quantify a quasidegeneracy, and (ii) identify the symmetry classes for which quasidegeneracies occur along lines rather than points, or rather than being generically nonexistent.
 The first task is carried out in the rest of this subsection, and the second will be the subject of subsequent subsections in \s{sec:llquasideg}.
-}
-
-Suppose the propagator $\A$ were degenerate at $(\bar{E},\bar{B})$, i.e., $\lambda_1(\bar{E},\bar{B})=\lambda_2(\bar{E},\bar{B})$ mod $2\pi$.
+
+Suppose the propagator $\A$ were degenerate at $(\bar{E},\bar{B})$ [cf.\ \q{eigenvaluedegeneracyA}].
 Generically, $(\bar{E},\bar{B})$ is not \emph{simultaneously} a solution of the quantization rule in \q{eq:rule}.
@@
 \e{l^2\left|\p{S}{E}\right| \gg \left|\p{\lambda_a}{E}\right|,\, \left|S\right| \gg \left|\p{\lambda_a}{l^2}\right|;} 
-these inequalities are guaranteed by the nearly-degeneracy condition ($\delta S{\ll}S$) and the smoothness of $S(E)$, as shown in \app{sec:slowvariation}.
-For fixed $\bar{B}$, we are therefore guaranteed to find a number (of order one) of paired Landau levels  in close proximity to $\bar{E}$, with each pair having an energetic splitting of order:
+these inequalities are guaranteed by the nearly-degeneracy condition ($\delta S{\ll}S$) and the smoothness of $S(E)$, as shown in \app{sec:proofLLquasideg}.
+For fixed $\bar{B}$, we are therefore guaranteed to find paired Landau levels  in close proximity to $\bar{E}$, with each pair having an energetic splitting of order:
 \e{\bigg|\f{E_{1}-E_2}{\var_c}\bigg|_{B=\bar{B}} \sim \order\left( \f{\partial \lambda_a/\partial E}{\bar{l}^2\partial  S/\partial E}  \right)\ll 1,\label{llquasideg}}
-with $\bar{l}$ the magnetic length associated to $\bar{B}$; this is illustrates schematically in Fig.\ \ref{fig:LL}.
+with $\bar{l}$ the magnetic length associated to $\bar{B}$; this is illustrated schematically in Fig.\ \ref{fig:LL}.
+At fixed $B$, the number of Landau levels sandwiched between two adjacent curves of \q{eigenvaluedegeneracyA} is of order $\bar{l}^2(\partial S/\partial E)/(\partial \lambda_a/\partial E).$
+
 Alternatively, we may fix $\bar{E}$ and investigate how Landau levels disperse as a function of $B$; the analog of \q{llquasideg}  is the existence of paired Landau levels in close proximity to $\bar{l}^2$, with a splitting of order:
 \e{\bigg|\f{l^2_{+}-l^2_-}{T_{{l^2}}}\bigg|_{E=\bar{E}} \sim O\left( \f{1}{S}\p{\lambda_a}{l^2} \right)\ll 1,\;\; T_{{l^2}}:=\f{2\pi}{S(\bar{E})}.\label{llquasidegB} }
-$\partial \lambda_a/\partial l^2$ is estimated in \app{sec:slowvariation}, and
+$\partial \lambda_a/\partial l^2$ is estimated in \app{sec:proofLLquasideg}, and
 $T_{l^2}$ above is the period (in $l^2$) of quantum oscillations -- in the absence of spin-orbit coupling.
-
-To recapitulate, for every exact degeneracy of $\cala$, there exists, in close proximity, an \red{order-one} number of paired Landau levels which are  nearly degenerate in the sense of \qq{llquasideg}{llquasidegB}.
+At fixed $E$, the number of Landau levels sandwiched between two adjacent curves of \q{eigenvaluedegeneracyA} is of order $S/(\partial \lambda_a/\partial l^2).$
+
+To recapitulate, for every exact degeneracy of $\cala$, there exist, in close proximity, paired Landau levels which are  nearly degenerate in the sense of \qq{llquasideg}{llquasidegB}.
 Each such pair of Landau levels will be described as \textit{quasidegenerate}.
@@
 
-One of our main results is that  rotational symmetry (with rotational axis parallel to the field) also results in degeneracy manifolds with unit codimension.
+One of our main results is that  rotational symmetry (with rotational axis parallel to the field) results in degeneracy manifolds with unit codimension.
 This will be demonstrated by two  case studies: the Rashba 2DEG in \s{sec:singleparameterrashba}, and a model with II-Dirac points in \ref{sec:rotsymmbreakdown}.
 
-\subsection{Codimension reduction for the Rashba 2DEG}\label{sec:singleparameterrashba}
-
-\subsubsection{With continuous rotational symmetry}\label{sec:ctsrot}
+\subsection{Codimension reduction for the Rashba-Dresselhaus 2DEG}\label{sec:singleparameterrashba}
+
+\subsubsection{Rashba 2DEG with continuous rotational symmetry}\label{sec:ctsrot}
 
@@
 where
-\e{\br{=}\bigg(\f{g_sm}{4m_0}{-}\f1{2},0,-\f{\hbar\alpha k_{\sma{E}}}{\var_c}\bigg)} and $\{\tau_j\}$ are a set of Pauli matrices.
+\e{\br{=}\bigg(\f{g_{s\perp}m}{4m_0}{-}\f1{2},0,-\f{\hbar\alpha k_{\sma{E}}}{\var_c}\bigg) \la{rvectorrashba}} 
+and $\{\tau_j\}$ are a set of Pauli matrices.
 Any $\text{SU}(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}] for some (possibly non-unique) $\br$, with $r_2$ not necessarily zero.
@@
 \s{sec:introducecodimension}).
-This point degeneracy can be understood from an elementary result in quantum mechanics: taking $\alpha{=}r_2{=}0$ \textit{and} $m{=}m_0$, we recover the Zeeman-split Landau levels of a free electron gas without spin-orbit coupling; all levels (except the lowest) are spin-degenerate owing to the equality of the Zeeman and cyclotron energies\cite{landau2013course}.
-
-The above discussion is reminiscent of topological (semi)metals which host Dirac-Weyl points\cite{wang2012dirac,wan2011topological} and/or line nodes\cite{burkov2011topological} (of Bloch-Hamiltonian degeneracies).
-Both Dirac points (in 2D $\bk$-space, e.g., graphene\cite{neto2009electronic}) and line nodes (in 3D $\bk$-space) are attainable by tuning two wavenumbers; the stability of such codimension-two manifolds relies on crystallographic point-group symmetries.
+This point degeneracy can be understood from an elementary result in quantum mechanics: taking $\alpha{=}0$, $g_{s\perp}{=}2$ {and} $m{=}m_0$ in \q{rvectorrashba}, we recover the Zeeman-split Landau levels of a free electron gas without spin-orbit coupling; all levels (except the lowest) are spin-degenerate owing to the equality of the Zeeman and cyclotron energies\cite{landau2013course}.
+
+The above discussion is reminiscent of topological semimetals whose corresponding Bloch Hamiltonians are energy-degenerate at Dirac-Weyl points\cite{wang2012dirac,wan2011topological} and/or line nodes.\cite{burkov2011topological} Both Dirac points (in 2D $\bk$-space, e.g., graphene\cite{neto2009electronic}) and line nodes (in 3D $\bk$-space) are attainable by tuning two wavenumbers; the stability of such codimension-two manifolds relies on crystallographic point-group symmetries.
 On the other hand, Weyl points in 3D $\bk$-space have codimension three and do not require any point-group symmetry for their stability.
@@
 
-\subsubsection{With discrete rotational symmetry}\label{sec:disrot}
+\subsubsection{Rashba-Dresselhaus 2DEG with discrete rotational symmetry}\label{sec:disrot}
 
@@
 This general statement is proven in App.
-\ref{app:codimension}, and here we illustrate it for a specific model of $N{=}2$ -- we will reduce the $\mathfrak{c}_{\infty}$ symmetry of the Rashba model [cf.\ \q{hamRD}] to  $\mathfrak{c}_2$  by adding the Dresselhaus spin-orbit term (${\propto} \beta$).
-
-\red{For the Rashba-Dresselhaus 2DEG, $\A$ depends on $\alpha,~\beta,~l,~E,~m$ only through three independent parameters:}%$\hbar\alpha k_E /\var_c$, $\hbar\beta k_E /\var_c$ and $g_sm/m_0$, let us consider the three-dimensional parameter space:
-\e{\left( \f{\hbar\alpha k_{\sma{E}}}{\var_c},\f{\hbar\beta k_{\sma{E}}}{\var_c},g_s\f{m}{m_0} \right){\in} \mathbb{R}^3. \la{parameter2}}  
-$\A(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0){=}{\pm} I$ then determines a set of concentric circles in the $\beta{=}0$ plane, as per the $\mathfrak{c}_{\infty}$-symmetric case study in \s{sec:ctsrot}.
+\ref{app:codimension}, and here we illustrate it for a specific model of $N{=}2$ -- we will reduce the $\mathfrak{c}_{\infty}$ symmetry of the Rashba model [cf.\ \q{eq:Rashba-Hamiltonian}] to  $\mathfrak{c}_2$  by adding the Dresselhaus spin-orbit interaction (with coupling parameter $\beta$):
+\begin{equation}
+ H_{RD}(\bk)=\frac{{\hbar^2}k^2}{2m}+\hbar\alpha(k_{x}\sigma_{y}-k_{y}\sigma_{x})+\hbar\beta(k_{x}\sigma_{x}-k_{y}\sigma_{y}).\label{hamRD}
+\end{equation}
+{For the Rashba-Dresselhaus 2DEG, $\A$ depends on $\alpha,~\beta,~l,~E,~m$ only through three independent parameters:}%$\hbar\alpha k_E /\var_c$, $\hbar\beta k_E /\var_c$ and $g_sm/m_0$, let us consider the three-dimensional parameter space:
+\e{\left( \f{\hbar\alpha k_{\sma{E}}}{\var_c},\f{\hbar\beta k_{\sma{E}}}{\var_c},g_{s\perp}\f{m}{m_0} \right){\in} \mathbb{R}^3. \la{parameter2}}  
+$\A(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_{s\perp}m/m_0){=}{\pm} I$ then determines a set of concentric circles in the $\beta{=}0$ plane, as per the $\mathfrak{c}_{\infty}$-symmetric case study in \s{sec:ctsrot}.
 Moving off this plane, we find that $\A{=}I$ is satisfied in a  neighborhood of $\beta{=}0$, i.e., $\A{=}I$ defines a hypersurface in $\mathbb{R}^3$ that is illustrated in \fig{fig:dgn}(a).
@@
 To demonstrate how the $\A{=}I$ hypersurface derives from $\mathfrak{c}_2$ symmetry, consider  the effective Hamiltonian $\calh$ 
-\e{\calh=\hbar\alpha (k_{x}\sigma_{y}{-}k_{y}\sigma_{x})+\hbar\beta (k_{x}\sigma_{x}{-}k_{y}\sigma_{y})-\f{g_s}{2}\mu_{B}B\sigma_z,}
+\e{\calh=\hbar\alpha (k_{x}\sigma_{y}{-}k_{y}\sigma_{x})+\hbar\beta (k_{x}\sigma_{x}{-}k_{y}\sigma_{y})-\f{g_{s\perp}}{2}\mu_{B}B\sigma_z,}
 in a momentum-independent basis where the Pauli matrices correspond to spin operators. The two-fold rotational symmetry 
@@
 Employing the canonical SU(2) parametrization for the half-loop propagator [Eq.
-(\ref{s3}) with ${\cal \bar{A}}$ replaced by ${\A}_{\sma{T_c/2\leftarrow 0}}$], we derive
+(\ref{s3}) with ${\cal \bar{A}}$ replaced by ${\A}_{\sma{T_c/2\leftarrow 0}}$], we derive from \q{eq:sigmazconstraint} that
 \e{
@@
 \ref{app:codimension}, this conclusion generalizes for any $N{\geq}2$: the degenerate manifolds of $\mathfrak{c}_N$-symmetric $\A$ separate the space of symmetric coordinates into $N$ distinct connected components.
-\fig{fig:dgn}(a) illustrates the $\A=I$ degenerate manifold \red{with  parameters [cf.\ \q{parameter2}] that are distinct from $\br$.}
+\fig{fig:dgn}(a) illustrates the $\A=I$ degenerate manifold {in the coordinates of  \q{parameter2} (which are distinct from the $\br$-coordinates in \q{proprashba}).}
 
@@
 (c) Klein tunneling limit of $\mathfrak{c}_2$-symmetric (upper) and $\mathfrak{c}_3$-symmetric (lower) breakdown cyclotron orbits.
-(d) Two Feynman paths that switch to the other band by one tunneling event.
-(e) Two Feynman paths that returns to the same band by zero or two tunneling events.
-(f) Schematic Landau level dispersion for $\mathfrak{c}_3$ symmetric breakdown with respect to $\tau$ at a fixed energy.
-Out of the three degeneracies in the independent limit ($\tau=1$), one of them is destabilized by infinitesimal hybridization ($\tau<1$, indicated by green dashed lines) and two of them remains stable until they annihilate at $\tau=0.5$ (indicated by red dashed line).\label{fig:Cn-breakdown}}
+(d) Feynman paths that switch between bands through  one tunneling event.
+(e) Feynman paths that preserve the band index through either zero or two tunneling events.
+(f) Schematic Landau-level dispersion for $\mathfrak{c}_3$ symmetric breakdown with respect to $\tau$ at a fixed energy.
+For the plotted interval of $1/B$, there are three quasidegenerate points (indicated by solid dots) in the  limit of zero Landau-Zener tunneling ($\tau=1$).
+Only two of three quasidegeneracies are stable upon inclusion of tunneling.
+That is to say, two of three  two points extend into quasidegenerate lines (indicated by red dashed lines) as $\tau$ is decreased from unity, while the third point is isolated, i.e., the quasidegeneracy is immediately lost as $\tau$ is decreased.
+At $\tau=0.5$, the two quasidegenerate lines eventually merge and annihilate.\label{fig:Cn-breakdown}}
 \end{figure}
+
+%one of them is destabilized by infinitesimal hybridization ($\tau<1$, indicated by green dashed lines) and two of them remains stable until they annihilate at $\tau=0.5$ (indicated by red dashed line)
 
@@
 A completely different physical realization of two orbits linked by Landau-Zener tunneling was proposed in Ref.
-\onlinecite{yakovenko_angular_2006} and \textbf{[cite pershoguba and yakovenko]} -- for a bilayer \red{metal} subject to a tilted magnetic field.
-\red{In the absence of hybridization between the top and bottom layers, there are two decoupled orbits in each layer; in this example, the layers replace spin as a two-component degree of freedom.
+\onlinecite{yakovenko_angular_2006} and Ref.
+\onlinecite{pershoguba_effects_2015} -- for a bilayer {metal} subject to a tilted magnetic field.
+{In the absence of hybridization between the top and bottom layers, there are two decoupled orbits in each layer; in this example, the layers replace spin as a two-component degree of freedom.
 In the presence of hybridization,   Landau levels become layer-degenerate} only  at certain `magic angles'\footnote{These magic angles correspond to zeros of a Bessel function, as was first proposed by Yamaji.\cite{yamaji_angle_1989}} of the field orientation (a single parameter); this was experimentally confirmed in Ref.\ \onlinecite{gusev_interlayer_2008}.
-However, the role of $\mathfrak{c}_2$\red{/spatial inversion} symmetry was not recognized in these works.
+However, the role of $\mathfrak{c}_2${/spatial inversion} symmetry was not recognized in these works.
 
@@
 \ref{fig:Cn-breakdown}(b).
-In the adiabatic regime ($\tau{\approx}1$), Landau-level quasidegeneracies occur with a periodicity of one flux quantum; however, in the Klein-tunneling regime ($\tau{\approx}0$), there exists only one dominant orbit shaped like a three-fold-symmetric trefoil knot (cf.
+In the adiabatic regime ($\tau{\approx}1$), Landau-level quasidegeneracies are periodic in correspondence with a differential increment of one flux quantum; however, in the Klein-tunneling regime ($\tau{\approx}0$), there exists only one dominant orbit shaped like a three-fold-symmetric trefoil knot (cf.
 Fig.
@@
 \begin{table*}
-\begin{tabular*}{\textwidth}{c@{\extracolsep{\fill}}ccccccc}
-\hlineB{2.0}
-             class number & action on orbit & action on $\bk$ & $u$ & $s$ & nearly-degenerate & $g$ & codimension\\
+\begin{tabular}{|c|c|c|c|c|c|c|}
 \hline 
-\multirow{2}{*}{1} & \multirow{10}{*}{$|g\circ \frako_0| = |\frako_0|$} & \multirow{4}{*}{$\forall \bk \in \frako_0$, $g\circ \bk=\bk$} & \multirow{2}{*}{0} & \multirow{2}{*}{0} & \multirow{2}{*}{$\surd$} & $\breve{g}\propto I$ & 3  \\
-\cline{7-8}
- & & & & & & $\breve{g}\not\propto I$ & 1 \\
- \cline{4-8}
-\multirow{2}{*}{2} & & & \multirow{2}{*}{0} & \multirow{2}{*}{1} & & $g^2=1$ & 1  \\
-\cline{7-8}
- & & &  &  & & $g^2=-1$ & 3  \\
-\cline{3-8}
-3 & & \multirow{6}{*}{$\exists \bk \in \frako_0, g\circ \bk\ne\bk$} & 0 & 0 & $\surd$ & - & 1   \\
-\cline{4-8}
-4 & & & 0 & 1 & & - & 1   \\
-\cline{4-8}
-\multirow{2}{*}{5} & & & \multirow{2}{*}{1} & \multirow{2}{*}{0} & & $\breve{g} \propto \sigma_z$ & 2  \\
-\cline{7-8}
- & & & &  & & $\breve{g} \not\propto \sigma_z$ & 0  \\
-\cline{4-8}
-\multirow{2}{*}{6} & & & \multirow{2}{*}{1} & \multirow{2}{*}{1} & \multirow{2}{*}{$\surd$} & $g^2=1$ & 2  \\
-\cline{7-8}
-& & & & & & $g^2=-1$ & 0  \\
+action on orbit  & action on $\boldsymbol{k}$  & $u$ & $s$  & class \blue{label} & $g$  & codimension\tabularnewline
 \hline 
-7 & \multirow{4}{*}{$|g\circ \frako_0| \ne |\frako_0|$} & \multirow{4}{*}{-} & 0 & 0 & $\surd$ & - & 3 \\
-\cline{4-8}
-8 &  &  & 0 & 1 & & - & 3 \\
-\cline{4-8}
-9 &  &  & 1 & 0 & & - & 3 \\
-\cline{4-8}
-10 &  &  & 1 & 1 & $\surd$ & - & 3 \\
-\hlineB{2.0}
-\end{tabular*}
-\caption{Symmetry-constrained codimensions for the two-by-two propagator $\A$.
-The first column numbers the symmetry class of $\A$.
-The second and third column defines how the symmetry acts on the cyclotron orbit.
+\multirow{5}{*}{$|g\circ\mathfrak{o}_{0}|=|\mathfrak{o}_{0}|$} & \multirow{2}{*}{$\forall\boldsymbol{k}\in\mathfrak{o}_{0},g\circ\boldsymbol{k}=\boldsymbol{k}$} & \multirow{2}{*}{0} & \multirow{2}{*}{0} & \multirow{2}{*}{\blue{I-1}} & $\breve{g}\propto I$  & 3\tabularnewline
+\cline{6-7} 
+ &  &  &  &  & $\breve{g}\not\propto I$  & 1\tabularnewline
+\cline{2-7} 
+ & \multirow{3}{*}{$\exists\boldsymbol{k}\in\mathfrak{o}_{0},g\circ\boldsymbol{k}\neq\boldsymbol{k}$} & 0 & 0 & II-1 & - & 1\tabularnewline
+\cline{3-7} 
+ &  & \multirow{2}{*}{1} & \multirow{2}{*}{1} & \multirow{2}{*}{II-2} & $g^{2}=1$  & 2\tabularnewline
+\cline{6-7} 
+ &  &  &  &  & $g^{2}=-1$  & 0\tabularnewline
+\hline 
+\multirow{2}{*}{$|g\circ\mathfrak{o}_{0}|\neq|\mathfrak{o}_{0}|$ } & \multirow{2}{*}{-} & 0 & 0 & III-1 & - & 3\tabularnewline
+\cline{3-7} 
+ &  & 1 & 1 & III-2 & - & 3\tabularnewline
+\hline 
+\end{tabular}
+\caption{\blue{Symmetry-constrained codimensions for nearly-degenerate orbits, which fall into five symmetry classes (as numbered in the first column).
+This table is also applicable to exactly-degenerate orbits, which fall into ten symmetry classes -- five here, and five in  \tab{table:codimension-exactlydegen}.} The second and third columns define how the symmetry acts on the cyclotron orbit.
 The next two columns  inform us if the mapping $\bk{\rightarrow}g{\circ}\bk$ [cf.\ \q{gmapk}]  preserves ($u{=}0$) or inverts ($u{=}1$) the orientation of the orbit, and if $g$ preserves ($s{=}0$) or inverts ($s{=}1$) the arrow of time.
-The sixth column indicates whether this  class is potentially a symmetry of nearly-degenerate orbits.
-The seventh column specifies additional conditions (on the representation of $g$) which must be imposed to uniquely determine the codimension.
+The sixth column specifies additional conditions -- on the representation of $g$ -- which must be imposed to uniquely determine the codimension.
 $\breve{g}$ is defined as the diagonalized, unitary matrix representation of $g$ in the degenerate subspace of $\hat{H}_0$.
-In class 5, $\breve g$ is evaluated at $g$-invariant $\bk$ ($g\circ\bk=\bk$).
 For the reader's convenience, we present some commonly-encountered matrix representations for exactly-degenerate orbits in Tab.\ \ref{table:sewing-matrix}.
@@
 \ref{sec:introducecodimension}].
-For exactly-degenerate orbits in class 2, 4 and 5, $\A$ satisfies $\text{det}(\A){=}1$, with the assumption that spin-orbit coupling can be turned off continuously without changing the degeneracy of the orbit\cite{topoferm}.
- \label{table:codimension}}
+\label{table:codimension-nearlydegen}}
+\end{table*}
+%the two-by-two propagator $\A$ -- for the five symmetry classes which apply to both nearly- and exactly-degenerate orbits. .
+
+\begin{table*}
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+action on orbit  & action on $\boldsymbol{k}$  & $u$ & $s$  & class \blue{label} & $g$  & codimension\tabularnewline
+\hline 
+\multirow{5}{*}{$|g\circ\mathfrak{o}_{0}|=|\mathfrak{o}_{0}|$} & \multirow{2}{*}{$\forall\boldsymbol{k}\in\mathfrak{o}_{0},g\circ\boldsymbol{k}=\boldsymbol{k}$} & \multirow{2}{*}{0} & \multirow{2}{*}{1} & \multirow{2}{*}{I-2} & $g^{2}=1$  & 1\tabularnewline
+\cline{6-7} 
+ &  &  &  &  & $g^{2}=-1$  & 3\tabularnewline
+\cline{2-7} 
+ & \multirow{3}{*}{$\exists\boldsymbol{k}\in\mathfrak{o}_{0},g\circ\boldsymbol{k}\neq\boldsymbol{k}$} & 0 & 1 & II-3 & - & 1\tabularnewline
+\cline{3-7} 
+ &  & \multirow{2}{*}{1} & \multirow{2}{*}{0} & \multirow{2}{*}{II-4} & $\breve{g}\propto\sigma_{z}$  & 2\tabularnewline
+\cline{6-7} 
+ &  &  &  &  & $\breve{g}\propto\sigma_{z}$  & 0\tabularnewline
+\hline 
+\multirow{2}{*}{$|g\circ\mathfrak{o}_{0}|\neq|\mathfrak{o}_{0}|$ } & \multirow{2}{*}{-} & 0 & 1 & III-3 & - & 3\tabularnewline
+\cline{3-7} 
+ &  & 1 & 0 & III-4 & - & 3\tabularnewline
+\hline 
+\end{tabular}
+\caption{\blue{Symmetry-constrained codimensions for five of ten symmetry classes of exactly-degenerate orbits; the other five are described in \tab{table:codimension-nearlydegen}.
+We employ the same notations as in the caption of Tab.
+\ref{table:codimension-nearlydegen}.} In class II-4, $\breve g$ is evaluated at $g$-invariant $\bk$ ($g\circ\bk=\bk$).
+For exactly-degenerate orbits in class I-2, II-3 and II-4, the two-by-two matrix propagator $\A$ has unit determinant, assuming that spin-orbit coupling can be turned off continuously without changing the degeneracy of the orbit.\cite{topoferm}\label{table:codimension-exactlydegen}}
 \end{table*}
@@
 Given $\hat{H}$ and the orientation of the magnetic field, electrons follow orbits (denoted $\frako$) that are confined to field-orthogonal $\bk$-planes.
-Given an orbit $\frako$, we restrict our attention to the subgroup of $\hat{H}$ that maps the orbit to itself (denoted as $|g\circ\frako|{=}|\frako|$) or to a distinct orbit ($|g\circ\frako|{\ne}|\frako|$).
+Given an orbit $\frako$ in a $\bk$-plane, we restrict our attention to the subgroup of $\hat{H}$ that preserves the plane.
+Any element of this subgroup maps the orbit to itself (denoted as $|g\circ\frako|{=}|\frako|$) or to a distinct orbit ($|g\circ\frako|{\ne}|\frako|$).
 In the former mapping, we may further distinguish two cases: (a)  $g$ maps every $\bk$ on the orbit to itself, as exemplified by the composition $T\inv$ of time reversal ($T$) and spatial inversion ($\inv$)  symmetries.
@@
 The combination of all distinguishing criteria leads to   a ten-fold classification of orbits $\frako_0$ with $g$ symmetry, as was first presented in Ref.
-\onlinecite{topoferm} and is summarized by the ten numbered rows in \tab{table:codimension}.
+\onlinecite{topoferm} and is summarized by the ten numbered rows in Tab.
+\ref{table:codimension-nearlydegen}-\ref{table:codimension-exactlydegen}.
 
@@
 Of the ten classes described in \s{sec:reviewtenfold}, only five   are relevant to quasidegenerate orbits (which are split with differential area  $\delta S$ that is much less than the area of $\frako_0$).
-To identify this five, recall that the subleading corrections to our quantization rule are determined by the propagator $\A$ [cf.\ \q{eq:prop}], which is a time-ordered exponential of an effective Hamiltonian $\H{=}\delta\epsilon{+}B \mathcal{M}$ [cf.\ \q{eq:H1}]; $\H$ perturbatively encodes $\delta H$ and the Zeeman interaction, for an electron travelling over  $\frako_0$.
+To identify these five, recall that $\lambda_a$ in our quantization rule is determined by the propagator $\A$ [cf.\ \q{eq:prop}], which is a time-ordered exponential of an effective Hamiltonian $\H{=}\delta\epsilon{+}B \mathcal{M}$ [cf.\ \q{eq:H1}]; $\H$ perturbatively encodes $\delta H$ and the Zeeman interaction, for an electron travelling over  $\frako_0$.
 Since $g$ is  a symmetry of  $\delta \hat{H}$, $\delta\epsilon$ is invariant under action of $g$.
 On the other hand, $\mathcal{M}$ is the field-parallel component of a pseudovector that is odd under time reversal\cite{sakurai1995modern}, hence changes under $g$ to  $(-1)^{u+s}\mathcal{M}$ (plus a gauge-dependent term\cite{100p} which is not essential to the present argument).
-Only with $u{+}s{=}0$ or $2$ would both terms in $\H$ transform consistently (invariantly) under $g$ -- this identifies the five ticked classes in Tab.\ \ref{table:codimension}.
-
-For these five classes (labelled 1, 3, 6, 7 and 10 according to the first column of Tab.\ \ref{table:codimension}), we list their corresponding \textit{symmetry-constrained codimensions} in the right-most column of Tab.\ \ref{table:codimension}; these numbers are derived in  App.\ \ref{app:codimension}.
+Only with $u{+}s{=}0$ or $2$ would both terms in $\H$ transform consistently (invariantly) under $g$ -- this identifies the five classes in Tab.\ \ref{table:codimension-nearlydegen}.
+
+For these five classes, we list their corresponding \textit{symmetry-constrained codimensions} in the right-most column of Tab.\ \ref{table:codimension-nearlydegen}; these numbers are derived in  App.\ \ref{app:codimension}.
 Recall that the codimension is the number of independently-tunable parameters needed to attain a degeneracy for $\A$.
-Each listed codimension is robust to any perturbation of the Hamiltonian that preserves the corresponding symmetry (specified by the row) and the homotopy class\cite{100p} of the zeroth-order orbit (e.g., a circular orbit cannot be deformed into a figure of eight).
-
-Of the five classes only classes 1, 3 and 6 potentially have symmetry-constrained codimensions that are reduced from three: classes 1, 3 and 6 have in common that  $|g\circ\frako_0|{=}|\frako_0|$, and therefore the propagator $\A$ [cf.\ \q{eq:prop}] is self-constrained.
-To clarify, a self-constraint relates  the propagator $\A$ [cf.\ \q{eq:prop}] to itself or to its inverse $\A^{-1}$, depending respectively on whether $u{=}0$ or $1$.
-
-Class 1 groups together  spatial symmetries that preserve the arrow of time and map every $\bk$ on $\frako_0$ to itself.
-The simplest example is of $g$  a reflection symmetry with axis parallel to the field, and of  $\frako_0$ that is confined to a $g$-invariant $\bk$-plane.
-To uniquely determine the symmetry-constrained codimension in class 1, one must specify if the nearly degenerate bands belong to identical or distinct representations of $g$.
-The symmetry-constrained codimension is reduced to unity in the latter (and only the latter) case, due to the absence of level repulsion between distinct representations of $g$ \red{\sout{-- the corresponding quasidegeneracies of Landau levels would then be exact degeneracies, rather than the near degeneracies described by \qq{llquasideg}{llquasidegB}}}.
-
-Class 3 corresponds to spatial symmetries that preserve the arrow of time and the orientation of $\frako_0$, as exemplified by spatial rotational symmetry with rotational axis parallel to the field.
-\red{Another example is given  spatial  inversion symmetry, for $\frako_0$ that is confined to an inversion-invariant plane: $k_z=0$ or $\pi$}.
+Each listed codimension is robust to any perturbation of the Hamiltonian that preserves the corresponding symmetry (specified by the row) and the homotopy class\cite{100p} of the zeroth-order orbit.
+(An example of a change in homotopy class is given by a deformation of a circular orbit into a figure of eight.)
+
+Of the five classes only classes I-1, II-1 and II-2 potentially have symmetry-constrained codimensions that are reduced from three: classes I-1, II-1 and II-2 have in common that  $|g\circ\frako_0|{=}|\frako_0|$, and therefore the propagator $\A$ [cf.\ \q{eq:prop}] is self-constrained.
+To clarify, a self-constraining symmetry relates the propagator $\A$ [cf.\ \q{eq:prop}] to itself or to its inverse $\A^{-1}$, depending respectively on whether $u{=}0$ or $1$.
+
+Class I-1 groups together spatial symmetries that preserve the arrow of time and map every $\bk$ on $\frako_0$ to itself.
+The simplest example of such a symmetry ($g$) is a reflection symmetry with axis parallel to the field, and of  $\frako_0$ that is confined to a $g$-invariant $\bk$-plane.
+To uniquely determine the symmetry-constrained codimension in class I-1, one must specify if the nearly degenerate bands belong to identical or distinct representations of $g$.
+The symmetry-constrained codimension is reduced to unity in the latter (and only the latter) case, due to the absence of level repulsion between distinct representations of $g$.
+
+Class II-1 corresponds to spatial symmetries that preserve the arrow of time and the orientation of $\frako_0$, as exemplified by spatial rotational symmetry with rotational axis parallel to the field.
+Another example is given spatial inversion symmetry, for $\frako_0$ that is confined to an inversion-invariant plane: $k_z=0$ or $\pi$.
 The symmetry-constrained codimension here is unity, as has been modelled in Sec.\ \ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown}.
-Only in class 3 (among 1, 3, 6) do there exist different  degeneracy manifolds with different codimensions; in such case we define the symmetry-constrained codimension to be the minimal codimension among all manifolds.
-For example, we have found that two-fold rotational symmetry reduces the codimension of the $\A{=}{+}I$ manifold (to unity), but not the codimension of the $\A{=}{-}I$ manifold [cf.\ \q{proprashba}].
-The rotation-constrained codimension is then unity, and hence the entry $1$ in the right-most column for class 3.
-
-Symmetries in class 6 reverse both the arrow of time and the orientation of the orbit.
+For a fixed orbit $\frako_0$ in class II-1, there may exist different degeneracy manifolds with different codimensions; in such case we define the symmetry-constrained codimension to be the minimal codimension among all manifolds.\footnote{For a fixed orbit in class I-1 or II-2, all degeneracy manifolds have the same codimension.} For example, we have found that two-fold rotational symmetry reduces the codimension of the $\A{=}{+}I$ manifold (to unity), but not the codimension of the $\A{=}{-}I$ manifold [cf.\ \fig{fig:dgn} and \q{proprashba}].
+The rotation-constrained codimension is then unity, and hence the entry $1$ in the right-most column for class II-1.
+
+Symmetries in class II-2 reverse both the arrow of time and the orientation of the orbit.
 The symmetry-constrained codimension is $2$ or $0$, depending respectively on whether the antiunitary representation of $g$ squares to $+1$ or $-1$.
@@
 with $K$ implementing complex conjugation.
-A consequence of this symmetry is that the degeneracy line node in Fig.
+A consequence of this symmetry is that any of the quasidegeneracy lines in Fig.
 \ref{fig:dgn}(b) is robust -- a property we had previously (and consistently) deduced from continuous rotational symmetry.
+
 An example of $g^2{=}-1$ is given by
@@
 
-\red{Finally, we point out  that the Rashba 2DEG in a tilted magnetic field, as studied in \ref{sec:inplanezeeman}, also falls into class 6  owing to the symmetry:
+Finally, we point out that the Rashba 2DEG in a tilted magnetic field, as studied in \ref{sec:inplanezeeman}, also falls into class II-2  owing to the symmetry:
 \begin{equation}
@@
 \end{equation}
-Consequently, the degeneracy manifolds are lines in the parameter space $(\alpha, B_\parallel, g_s)$.
+Consequently, the degeneracy manifolds are lines in the parameter space $(\alpha, B_\parallel, g_{s\perp})$.
 Numerically, we have determined that these lines lie solely within the $B_\parallel=0$ and $\alpha=0$ planes.
@@
 \end{equation}
-with $\theta$ the tilt angle: $\cos(\theta)=B_\perp/\sqrt{B_\perp^2+B_\parallel^2}$. For common semiconductors with $m\ll m_0$, $n=\pm 1$ is attained only for $B_\parallel\gg B_\perp$.
-}
+with $\theta$ the tilt angle: $\cos(\theta)=B_\perp/\sqrt{B_\perp^2+B_\parallel^2}$.
 
@@
 In this section we focus on higher-symmetry solids where the degeneracy-lifting perturbation $\delta \hat{H}$ is disallowed.
-$\hat{H}_0$ may or may not include spin-orbit coupling; in the former case, a crystalline point-group symmetry (e.g., $T\inv$ symmetry) is required for energy bands to be two-fold degenerate at zero field.
+$\hat{H}_0$ may or may not include spin-orbit coupling; in the former case, a crystalline point-group symmetry (e.g., $T\inv$ symmetry) is required for energy bands of $\hat{H}_0$ to be two-fold degenerate at each $\bk$.
 
@@
 Despite the exact degeneracy of orbits, the corresponding Landau levels are generically split by the Zeeman interaction $B\calm$.
-We may therefore ask, in complete analogy: how many tunable parameters are required to attain a Landau-level (quasi)degeneracy for exactly-degenerate orbits?
+We may therefore ask, in complete analogy: how many tunable parameters are required to attain a Landau-level quasidegeneracy for exactly-degenerate orbits?
 
@@
 
-Some $\calm$-inverting symmetries also exhibit reduced symmetry-constrained codimensions, as listed in the five \textit{unticked} classes of \tab{table:codimension}.
-As a case in point, class 2 symmetries invert time and $\calm$, and map  every wavevector (in $\frako_0$) to itself.
+Some $\calm$-inverting symmetries also exhibit reduced symmetry-constrained codimensions, as listed in the five classes of \tab{table:codimension-exactlydegen}.
+As a case in point, class II-2 symmetries invert time and $\calm$, and map every wavevector (in $\frako_0$) to itself.
 The corresponding codimension is three (resp.\ one) if $g$ squares to $-1$ (resp.\ $+1$).
@@
 
-The simplest example of codimension reduction by a $\calm$-preserving symmetry is that of continuous spin-rotation.
-This is a symmetry of any solid with negligible spin-orbit coupling, and results in the absence of Landau-level repulsion between different spin species (cf.\ unit symmetry-constrained codimension in class 1, with non-identical symmetry eigenvalues).
-In this case the Landau-level degeneracy is exact.
+The simplest example of codimension reduction by a $\calm$-preserving symmetry is that of continuous spin rotation in class I-1.
+This is a symmetry of any solid with negligible spin-orbit coupling, and results in the absence of Landau-level repulsion between different spin species -- this implies codimension is 1 [cf.\ class I-1 in \tab{table:codimension-nearlydegen}, with non-identical symmetry eigenvalues].
 
@@
 We conclude this section by commenting on the tunable experimental parameters that are relevant to exactly-degenerate orbits.
-The absence of $\delta\var$  implies that the eigenvalues of $\cala$ are independent of the magnitude of $B$ [cf.\ \q{lambdasmallB} with $\delta S{=}0$].
-However, the generic anisotropy of $\calm$ (viewed as a pseudovector) suggests that we may sweep the orientation of $B$; the generic energy-dependence of $\calm$ suggests that we may tune the bias voltage in tunneling spectroscopy.
+The absence of $\delta\var$  implies that the eigenvalues of $\cala$ are independent of the magnitude of $B$ [cf.\ \q{eq:Rashba-lambda} with $\delta S{=}0$].
+However, the generic anisotropy of the Zeeman interaction suggests that we may sweep the orientation of $B$; the generic energy-dependence of $\calm$ suggests that we may tune the Landau-level index, e.g., by varying a bias voltage in tunneling spectroscopy.
 
@@
 
-\section{Quantum-oscillatory phenomena for exactly- and quasi-degenerate orbits}\label{sec:qo}
+\section{Quantum-oscillatory phenomena for exactly- and nearly-degenerate orbits}\label{sec:qo}
 
 In \s{sec:qtznrules} we have presented a quantization rule [\qq{eq:rule}{berryconn}] that is applicable to both nearly-degenerate ($0{<}\delta S{\ll}S$) orbits and exactly-degenerate ($\delta S{=}0$) orbits.
-This section explores the implication of this rule for quantum-oscillatory phenomena of the Schubnikov-de Haas (SdH)\cite{SdH} and de Haas-van Alphen (dHvA)\cite{dHvA} types.
+This section explores the implication of this rule for quantum-oscillatory phenomena of the Shubnikov-de Haas (SdH)\cite{SdH} and de Haas-van Alphen (dHvA)\cite{dHvA} types.
 In \s{sec:quantosc_equidis}, we present a generalized Lifshitz-Kosevich formula\cite{lifshitz_kosevich,lifshitz_kosevich_jetp} that inputs our rule and outputs quantum oscillations.
-Applying this formula in the high-temperature regime, we will prove that  destructive interference of the fundamental quantum-oscillatory harmonic may  be tuned by at most one parameter in any symmetry class; this parameter may be the magnitude ($B$) of the magnetic field for quasidegenerate orbits, but not for exactly-degenerate orbits.
-\s{sec:quantosc_quasideg} focuses on the low-temperature SdH effect for nearly-degenerate orbits in symmetry classes 1 and 3 [cf.\ \tab{table:codimension}], wherein we predict a smooth crossover from period-doubled to -undoubled oscillations upon variation of $B$ (at fixed particle density).
+Applying this formula in the high-temperature regime, we will prove that  destructive interference of the fundamental quantum-oscillatory harmonic may  be tuned by a single parameter in any symmetry class; this parameter may be the magnitude ($B$) of the magnetic field for quasidegenerate orbits, but not for exactly-degenerate orbits.
+\s{sec:quantosc_quasideg} focuses on the low-temperature SdH effect for nearly-degenerate orbits in symmetry classes I-1 and II-1 [cf.\ \tab{table:codimension-nearlydegen}], wherein we predict a smooth crossover from period-doubled to -undoubled oscillations upon variation of $B$ (at fixed particle density).
 
@@
 
-Lifshitz-Kosevich formula\cite{lifshitz_kosevich,lifshitz_kosevich_jetp} allow for a harmonic analysis of quantum oscillations, and have previously been derived for  exactly-degenerate orbits in symmetry class 1\cite{rothmag}, with the generalization to all ten symmetry classes in Ref.
+Lifshitz-Kosevich formulae\cite{lifshitz_kosevich,lifshitz_kosevich_jetp} allow for a harmonic analysis of quantum oscillations, and have previously been derived for  exactly-degenerate orbits in symmetry class I-1\cite{rothmag}, with the generalization to all ten symmetry classes in Ref.
 \onlinecite{topoferm}.
@@
 where the argument of the sine function involve quantities from our quantization rule [\qq{eq:rule}{berryconn}]; $T$ is temperature and $\tau_{\sma{D}}$  the Dingle scattering lifetime\cite{Dingle_collisions}.
-All the quantities on the right handside of Eq.\ (\ref{eq:LK}) are evaluated at the chemical potential.
-\q{eq:LK} corrects the analogous formula in Ref.
-\onlinecite{topoferm} by a factor of half.
+All the quantities on the right-hand side of Eq.\ (\ref{eq:LK}) are evaluated at the chemical potential.
+(\q{eq:LK} corrects the analogous formula in Ref.\ \onlinecite{topoferm} by a factor of half.)
 
@@
 
-We have shown in \s{sec:llquasideg} that  the number of tunable parameters required to attain  $\delta \lambda{\equiv}0$ ranges from $0$ to $3$; this number is a symmetry-dependent measure of Landau-level repulsion [cf.\ \tab{table:codimension}].
+We have shown in \s{sec:llquasideg} that  the number of tunable parameters required to attain  $\delta \lambda{\equiv}0$ ranges from $0$ to $3$; this number is a symmetry-dependent measure of Landau-level repulsion [cf.\ \tab{table:codimension-nearlydegen} and \tab{table:codimension-exactlydegen}].
 As illustrated in the right-most panel of Fig 7(b), $\delta \lambda{\equiv}\pi$ is the condition  for Landau levels to be quasi-equidistant  with spacing ${\approx}\var_c/2$; since no level repulsion need be overcome,
@@
 To prove this, we return to the canonical parametrization of the SU(2) component (${\cal \bar{A}}$) of $\A$ [cf.\ \q{s3}].
-The necessary and sufficient condition for $\delta \lambda{\equiv}\pi$ is that ${\cal \bar{A}}(r_1,r_2,r_3)$ has eigenvalues $+i$ and $-i$; the latter condition is equivalent to setting $r_1{=}0$ in \q{s3} -- a condition on a single parameter.\footnote{For an alternative proof,  $\delta \lambda{\equiv}\pi$ is equivalent to ${ \bar{\cal A}}{=}Ve^{i\sigma_z\pi/2}V^{-1}$ for some unitary $V\in U(2)$.
+The necessary and sufficient condition for $\delta \lambda{\equiv}\pi$ is that ${\cal \bar{A}}(r_1,r_2,r_3)$ has eigenvalues $+i$ and $-i$; this is equivalent to setting $r_1{=}0$ in \q{s3} -- a condition on a single parameter.\footnote{For an alternative proof,  $\delta \lambda{\equiv}\pi$ is equivalent to ${ \bar{\cal A}}{=}Ve^{i\sigma_z\pi/2}V^{-1}$ for some unitary $V\in U(2)$.
 The manifold associated to $\delta \lambda{\equiv}\pi$ is then the space of unitary matrices  that do not commute with $e^{i\sigma_z\pi/2}$.
@@
 For exactly-degenerate orbits, the single parameter to attain destructive interference might be the chemical potential (as illustrated for the quantum oscillations of Na$_3$Bi in Ref.
-\onlinecite{topoferm}) or the orientation of the magnetic field; however $\lambda_a$ is independent of the field magnitude ($B$), as explained in \s{sec:codimexactdeg}.
-In principle, one may account for linear-in-$B$ corrections to $\lambda_a$ at stronger fields, however a quantitative theory for such corrections only exists (thus far) for non-degenerate orbits\cite{rothmag,fuchs_landau_2018,gao_zero-field_2017,fischbeck_review}.
+\onlinecite{topoferm}) or the orientation of the magnetic field; however $\lambda_a$ is independent of the field magnitude ($B$) to the accuracy\cite{rothmag,fuchs_landau_2018,gao_zero-field_2017,fischbeck_review} of our theory, as explained in \s{sec:codimexactdeg}.
+
+%Going beyond the accuracy of our theory, one may account for linear-in-$B$ corrections to $\lambda_a$ at stronger fields, however a quantitative theory for such corrections only exists (thus far) for non-degenerate orbits\cite{rothmag,fuchs_landau_2018,gao_zero-field_2017,fischbeck_review}.
 
 For nearly-degenerate orbits, $\lambda_a$ is expandable as a Laurent series in $B$ with leading term $1/B$ [cf.\ \q{lambdasmallB}], hence $B$ can be tuned to attain destructive interference.
-The slow variation of $\lambda_a$ compared to the action $l^2S$ [cf.\ \app{sec:slowvariation}] implies a beating pattern for the fundamental harmonic.
-In the weak-field, adiabatic regime, the nodes of this pattern occur with period $2\pi/\delta S$ in $l^2$ [cf.\ \s{sec:introducecodimension}]; in the non-adiabatic regime, the nodes are generically aperiodic [cf.\ \q{lambdasmallB}].
-
-Such beatings have been observed for semiconductor heterostructures\cite{das_evidence_1989,hu_zero-field_1999,wilde_inversion-asymmetry-induced_2009}; in some experiments\cite{das_evidence_1989}, the phase offset $\lambda_a$ [cf.\ \q{eq:LK}] has been measured and fitted phenomenologically to a Laurent series in $B$.
-It has been appreciated that the leading-order term (${\sim}1/B$) originates from the zero-field splitting of orbits (due to spin-orbit coupling)\cite{das_evidence_1989}; our contribution is a quantitative theory of the expansion coefficients of this Laurent series -- we have related the subleading term  $({\sim}B^0)$ to a generalized Zeeman interaction, and higher-order terms to a competition between spin-orbit coupling and the Zeeman interaction [cf.\ \q{eq:Rashba-lambda}].
-As one application, one may extract the intervals (in $1/B$) between nodes  for the Rashba 2DEG [by imposing $\delta \lambda{\equiv}\pi$ in \q{eq:Rashba-lambda}] and for the Rashba-Dresselhaus 2DEG (see \s{sec:quantosc_quasideg}).
+The slow variation of $\lambda_a$ compared to the action $l^2S$ [cf.\ \app{sec:proofLLquasideg}] implies a beating pattern for the fundamental harmonic.
+In the weak-field, adiabatic regime, the nodes of this pattern occur with period $2\pi/\delta S$ in $l^2$ [cf.\ \s{sec:introducecodimension}]; in the non-adiabatic regime, this periodicity is lost due to field-induced hybridization of orbits [cf.\ \q{lambdasmallB}].
+
+Such beatings have been observed for semiconductor heterostructures\cite{das_evidence_1989,hu_zero-field_1999,wilde_inversion-asymmetry-induced_2009} and inversion-asymmetric metals\cite{terashima_fermi_2008,onuki_chiral-structure-driven_2014,maurya_splitting_2018}.
+In most experiments, the beating has been used to infer the magnitude of the spin-orbit coupling\cite{das_evidence_1989,onuki_chiral-structure-driven_2014,maurya_splitting_2018}; some of these experiments\cite{das_evidence_1989} paid attention to  the aperiodicity of the beating, and attributed it phenomenologically to a $B$-dependent splitting of the two orbits, which have distinct frequencies $f_1$ and $f_2$ in $1/B$.
+In our language, $|f_1-f_2|=B\delta\lambda/2\pi$, with the leading term of $\delta \lambda(E,B)$ proportional to $1/B$.
+
+Our contribution is a quantitative theory of the $B$ dependence of $\delta\lambda$ -- we have related the subleading term  $({\sim}B^0)$ to a generalized Zeeman interaction, and higher-order terms to a competition between spin-orbit coupling and the Zeeman interaction [cf.\ \q{eq:Rashba-lambda}].
+As one application, one may extract the intervals (in $1/B$) between nodes for the Rashba 2DEG [by imposing $\delta \lambda{\equiv}\pi$ in \q{eq:Rashba-lambda}] and for the Rashba-Dresselhaus 2DEG (see the subsequent \s{sec:quantosc_quasideg}).
+
+%In some experiments\cite{das_evidence_1989}, it has been recognized that the oscillation frequency in $1/B$, denoted as $f$, is weakly dependent on $B$ itself; 
+%the possibly aperiodic beatings has been interpreted as a $B$ dependent oscillation frequency difference $\delta f$ between the two splitted orbits.
+In our language, the frequency difference is related to $\delta\lambda$ as $\delta f=B\delta\lambda/2\pi$.
+It has been appreciated that the leading-order term of $\lambda$ (${\sim}1/B$) originates from the zero-field splitting of orbits; this has been applied to estimate the strength of the spin-orbit coupling\cite{das_evidence_1989,onuki_chiral-structure-driven_2014,maurya_splitting_2018}.
 
@@
 
-\subsection{Schubnikov-de Haas effect for nearly-degenerate orbits in symmetry class 1 and 3}\label{sec:quantosc_quasideg}
+\subsection{Shubnikov-de Haas effect for nearly-degenerate orbits in symmetry class I-1 and II-1}\label{sec:quantosc_quasideg}
 
 Let us focus on nearly-degenerate orbits for which a single parameter ($B$) can be tuned to attain $\delta \lambda{\equiv}0$ (equivalently, to attain a Landau-level quasidegeneracy).
-These orbits lie in symmetry classes 1 and 3; in classes 1 further assumptions must be made about the symmetry representation, as explained in \s{sec:codimquasideg} and summarized in \tab{table:codimension}.
-
-We propose a signature for tunable quasidegeneracies in the  Schubnikov-de Haas effect at fixed particle density $n_e$, low temperature ($k_BT{\ll}\var_c$) and weak disorder ($\omega_c\tau_{\sma{D}}{\gg}1$).
+Such orbits with unit codimension lie in symmetry classes I-1 and II-1; in class I-1 further assumptions must be made about the symmetry representation, as explained in \s{sec:codimquasideg} and summarized in \tab{table:codimension-nearlydegen}.
+
+We propose a signature for tunable quasidegeneracies in the  Shubnikov-de Haas effect at fixed particle density $n_e$, low temperature ($k_BT{\ll}\var_c$) and weak disorder ($\omega_c\tau_{\sma{D}}{\gg}1$).
 In this regime, it is known that minima of the longitudinal conductivity occur at discrete fields (denoted $B_{\nu}$)  where the filling is integer-valued\cite{vinter_resolution_1980}; the period of quantum oscillations is determined by the total density $n_e$ through $1/B_j{-}1/B_{j+1}{=}e/n_eh$.
-As $B$ increases through $B_j$, a Landau level is completely depopulated, leading to a periodic drop in the chemical potential ($\mu$) by the energy gap  between Landau levels, as illustrated in \fig{fig:qo}(b).
+As $B$ increases through $B_j$, a Landau level is completely depopulated, leading to a periodic drop in the chemical potential ($\mu$) by the energy gap  between adjacent Landau levels, as illustrated in \fig{fig:qo}(b).
 Where $\delta\lambda{\equiv}\pi$, Landau levels are  quasi-equidistant, hence adjacent minima (of conductivity) should be identically low.
 Where $\delta\lambda{\equiv}0$, every consecutive gap is small compared to $k_BT$ and $h/\tau_{\sma{D}}$, hence every other  minimum (of conductivity) vanishes\cite{bychkov_oscillatory_1984}.
-$0{\leq}\delta\lambda{\leq}{\pi}$ thus characterizes a smooth crossover between period-doubled and -undoubled oscillations, as representatively illustrated in \fig{fig:qo}(b).
-
-Our contribution is the exhaustive  identification of symmetry classes (1 and 3) for which such a crossover will occur.
-In particular, we are proposing that the crossover occurs for the Rashba-Dresselhaus 2DEG [cf.\ \q{hamRD}], whose nearly-degenerate orbits fall into class 3.
+$0{\leq}\delta\lambda{\leq}{\pi}$ thus characterizes a smooth crossover between period-doubled and -undoubled oscillations, as representatively illustrated in \fig{fig:qo}(b); the amplitude of oscillations in the undoubled regime is roughly half the amplitude in the doubled regime.
+
+Our contribution is the exhaustive  identification of symmetry classes (I-1 and II-1) for which such a crossover will occur.
+In particular, we are proposing that the crossover occurs for the Rashba-Dresselhaus 2DEG [cf.\ \q{hamRD}], whose nearly-degenerate orbits fall into class II-1.
 For this model,  Fig.\ \ref{fig:qo}(a) plots $\delta \lambda$ vs $1/B$ for various choices of the Dresselhaus coupling $\beta$.
@@
 The quantization rule for two nearly-degenerate orbits is summarized in \qq{eq:rule}{berryconn}, and may be applied to spin-degenerate orbits which are split by spin-orbit coupling or by breaking of a crystalline point-group symmetry.
-The former type of splitting is exemplified by  our case study of the Rashba 2DEG (with arbitrarily-oriented field and addition of Dresselhaus spin-orbit coupling).
+The former type of splitting is exemplified by  our case study of the Rashba-Dresselhaus 2DEG with an arbitrarily-oriented field.
 
 The subleading phase corrections ($\lambda_1,\lambda_2$) in our quantization rule  [\q{eq:rule}] encode the dynamical correction due to the splitting of  orbits, as well as a generalized two-band Zeeman interaction.
-If $\lambda_1{=}\lambda_2$ mod $2\pi$, there exists an order-one number of paired Landau levels which are either exactly spin-degenerate, or nearly spin-degenerate in the sense of \qq{llquasideg}{llquasidegB}.
+If $\lambda_1{=}\lambda_2$ mod $2\pi$ for specific values of energy $E$ and magnetic field $B$, there exist -- in close proximity to $E$ and $B$ --    paired Landau levels which are either exactly pseudospin-degenerate, or nearly pseudospin-degenerate in the sense of \qq{llquasideg}{llquasidegB}.
 Such paired Landau levels have been referred to as \textit{quasidegenerate}, and are illustrated in Fig.
@@
 We have referred to these numbers as \textit{symmetry-constrained codimensions}.
-Depending on the symmetry class and representation, the codimension ranges from 0, 1, 2 to 3, as summarized in the right-most column of Tab.\ \ref{table:codimension}.
-
-If the codimension is unity, it is possible to tune the magnitude of the field to attain Landau-level quasidegeneracies; the implications for this tunability -- in the Schubnikov-de Haas effect -- are discussed in \s{sec:quantosc_quasideg}.
-If the codimension is two, an additional experimentally tunable parameter is needed: e.g., the orientation of the field\cite{yakovenko_angular_2006}, or the bias voltage in tunneling spectroscopy\cite{Sangjun_Cd3As2,Ilija_SnTe,kushwaha_Dirac}.
-
-\red{We highlight a result from  Tab.\ \ref{table:codimension} that is widely applicable: the codimension is unity for orbits having either a spatial inversion or rotation symmetry (class 3).
+Depending on the symmetry class and representation, the codimension ranges from 0, 1, 2 to 3, as summarized in the right-most column of Tab.\ \ref{table:codimension-nearlydegen}- \ref{table:codimension-exactlydegen}.
+
+If the codimension is unity, it is possible (for nearly-degenerate orbits) to tune the magnitude of the field to attain Landau-level quasidegeneracies; the implications for this tunability -- in the Shubnikov-de Haas effect of two-dimensional metals -- are discussed in \s{sec:quantosc_quasideg}.
+If the codimension is two, an additional parameter is needed: e.g., the orientation of the field\cite{yakovenko_angular_2006}, or the Landau-level index (tuned through the bias voltage in tunneling spectroscopy\cite{Sangjun_Cd3As2,Ilija_SnTe,kushwaha_Dirac}).
+While we have mainly exemplified our theory for 2DEGs or two-dimensional metals, we remark that for the Landau levels of three-dimensional solids, the crystal wavevector parallel to the field provides yet another tunable parameter.
+
+We highlight a result from  Tab.\ \ref{table:codimension-nearlydegen} that is widely applicable: the codimension is unity for orbits having either a spatial inversion or rotation symmetry (class II-1).
 Both symmetries are commonly found in solids.
@@
 For further motivation in an entirely different context, a reduction in rotational symmetry   occurs also in a phase transition to a nematic Fermi fluid\cite{fradkin_nematic_2010}; it may be possible to utilize  the selective stability of Landau-level quasidegeneracies as an experimental indicator for nematic phase transitions.
-}
 
@@
 There are ten possible symmetry classes for exactly-degenerate orbits -- five more than for near-degenerate orbits.
-For each of this ten, we have also determined their symmetry-constrained codimensions in Tab.\ \ref{table:codimension}.
-We remark on one further distinction from near-degenerate orbits --  the magnitude of the field becomes less useful as a tuning parameter, however the field orientation and bias voltage remain feasible options.
+For each of this ten, we have also determined their symmetry-constrained codimensions in Tab.\ \ref{table:codimension-nearlydegen}- \ref{table:codimension-exactlydegen}.
+We remark on one further distinction from nearly-degenerate orbits --  the magnitude of the field becomes less useful as a tuning parameter, however the field orientation and Landau-level index remain feasible options.
 
@@
 Our codimension analysis is applicable to contexts beyond that of Landau-level repulsion.
-By keeping only the Berry term in \q{eq:H1}, Eq.\ ({\ref{eq:prop}}) reduces to the Wilson loop of the non-abelian Berry gauge field, i.e., the matrix representation of holonomy.
-Any symmetric Wilson loop can be classified according to Tab.\ \ref{table:codimension}; the codimensions for an eigenvalue-degeneracy of the Wilson loop are also identical to those listed in   Tab.\ \ref{table:codimension}.
+By keeping only the Berry term in \q{eq:H1}, Eq.\ ({\ref{eq:prop}}) reduces to the Wilson loop of the non-abelian Berry gauge field\cite{wilczek_appearance_1984}, i.e., the matrix representation of holonomy.
+Any symmetric Wilson loop can be classified according to Tab.\ \ref{table:codimension-nearlydegen}-\ref{table:codimension-exactlydegen}; the codimensions for an eigenvalue-degeneracy of the Wilson loop are also identical to those listed in Tab.\ \ref{table:codimension-nearlydegen}-\ref{table:codimension-exactlydegen}.
 Our work thus also explains the existence of robust crossings in the Wilson-loop spectra, which have been widely applied in topological band theory.
@@
 Symmetry does not only constrain the level repulsion between $\lambda_1$ and $\lambda_2$ -- in certain classes, it constrains their sum.
-In our previous work on exactly-degenerate, spin-differentiated orbits,\cite{100p,topoferm} we have derived a zero-sum rule ($\lambda_1{+}\lambda_2{\equiv}0$) in classes  2,4 and 5, with the assumption that spin-orbit coupling can be continuously tuned to zero without changing the degree of degeneracy; this zero-sum rule implies a quantized phase offset for the fundamental harmonic of quantum oscillations.\cite{topoferm} Here, we report that the zero-sum rule applies \textit{also} to nearly-degenerate orbits in classes 2, 4 and 5; this may be derived by combining the symmetry analysis of Ref.\ \onlinecite{topoferm} with the tracelessness of $\delta\var$ [cf.\ \q{eq:H1}].
+In our previous work on exactly-degenerate, spin-differentiated orbits\cite{100p,topoferm}, we have derived a zero-sum rule ($\lambda_1{+}\lambda_2{\equiv}0$) in classes  I-1, II-3 and II-4, with the assumption that spin-orbit coupling can be continuously tuned to zero without changing the degree of degeneracy; this zero-sum rule implies a quantized phase offset for the fundamental harmonic of quantum oscillations\cite{topoferm}.
+Here, we report that the zero-sum rule applies \textit{also} to nearly-degenerate orbits in classes I-1, II-3 and II-4; this may be derived by combining the symmetry analysis of Ref.\ \onlinecite{topoferm} with the tracelessness of $\delta\var$ [cf.\ \q{eq:H1}].
 
@@
 An instructive discussion with Victor Yakovenko helped us relate this work  to his `magic angles'.
+We acknowledge Xi Dai for a useful discussion of the Zeeman interaction in the context of breakdown.
 We also thank Eduardo Fradkin for educating us on the subject of nematic Fermi fluids.
-We acknowledge support by  the Yale Postdoctoral Prize Fellowship (AA), NSF DMR Grant No.\ 1603243 (LG),  the Ministry of Science and Technology of China, Grant No.\ 2016YFA0301001 (CW and WD), the National Natural Science Foundation of China, Grants No.\ 11674188 and 11334006 (CW and WD) and the Beijing Advanced Innovation Center for Future Chip (ICFC, CW and WD).
+We acknowledge support from the Ministry of Science and Technology of China, Grant No.\ 2016YFA0301001 (CW and WD), the National Natural Science Foundation of China, Grants No.\ 11674188 and 11334006 (CW and WD), the Beijing Advanced Innovation Center for Future Chip (CW and WD), the Yale Postdoctoral Prize Fellowship (AA) and NSF DMR Grant No.\ 1603243 (LG).
 This work was performed in part at Aspen Center for Physics, which is supported by National Science Foundation grant PHY-1607611.
@@
 
-\section{Review of the effective Hamiltonian theory}\label{app:revieweffham}
-
-The effective Hamiltonian lies at the heart of semiclassical theory.
-The leading order term (with respect to $B$) of effective Hamiltonian in momentum representation can be obtained by Peierls substitution of crystal momentum $\boldsymbol{k}$: $\boldsymbol{k}\to\boldsymbol{K}=\boldsymbol{k}+(e/\hbar)\boldsymbol{A}(i\nabla_{\boldsymbol{k}})$ in zero field band structure $\mathfrak{H}_{0}(\boldsymbol{K}):=\epsilon(\boldsymbol{k})$, where $\boldsymbol{A}$ is vector potential.
-Components of $\boldsymbol{K}$ do not commute with each other, thus substituting $\boldsymbol{k}$ to $\boldsymbol{K}$ is performed in a Weyl-symmetric manner that can be formally done using Fourier transformation.
-For a single band, the wave function in reciprocal space are expanded as $\phi=\sum_{\boldsymbol{k}}f_{\boldsymbol{k}}\psi_{\boldsymbol{k}}$, where $\psi_{\boldsymbol{k}}$ is modified Bloch wave function whose specific form is presented in Ref.
-\onlinecite{rotheffham}.
-The effective Hamiltonian then acts on $f_{\boldsymbol{k}}$, changing Shr\"odinger equation to:
-\begin{equation}
-(\mathfrak{H}(\boldsymbol{K})-E)f_{\boldsymbol{k}}=0.\label{eq:schrodinger}
-\end{equation}
-Subleading order term of effective Hamiltonian $\mathfrak{H}_{1}(\boldsymbol{K})$ is also obtained by substituting $\boldsymbol{k}$ to $\boldsymbol{K}$ in $\mathfrak{H}_{1}(\boldsymbol{k})$, where $\mathfrak{H}_{1}(\boldsymbol{k})$ encodes information of Berry connection, orbital moment and Zeeman energy.
-Assuming a magnetic field $B$ in $-z$ direction,
-\begin{equation}
-\mathfrak{H}_{1}(\boldsymbol{k})=BM_{z}-g_s\mu_{B}Bs_z/\hbar+eB\epsilon_{\alpha\beta}\mathfrak{X}_{\beta}v_{\alpha}.
-\end{equation}
-
-Eq. (\ref{eq:schrodinger}) can be solved by WKB approximation. To the leading order (i.e., with $\mathfrak{H}_0(\bK)$ only), solutions of Eq. (\ref{eq:schrodinger}) are Zil'berman functions
-\begin{equation}
-g_{\bk}^\nu=\frac{1}{\sqrt{|v_x^\nu|}}e^{il^2k_x^0k_y}e^{-il^{2}\int k_x^\nu dk_y}\delta_{k_x^0 k_x},
-\end{equation}
-where $k_x^\nu$ is a function of $k_y$ satisfying $\epsilon(k_x^\nu,k_y)=0$ and quantities with a superscript $\nu$ should be evaluated at $\bk = (k_x^\nu, k_y)$.
-Generally, $\epsilon(k_x^\nu,k_y)=0$ have several solutions of $k_x$ for a given $k_y$ and these solutions are indexed by $\nu$.
-$g_{\bk}$ above is expressed in Landau gauge, where $k_x=k_x^0$ is a constant of motion.
-Quantization rule for cyclotron motion may be obtained by solving boundary condition equations of $f_{\bk} = \sum_\nu g_{\bk}^\nu$ at turning points.
-
 \section{Proof of nearly-degenerate quantization rule\label{app:quantizationruleproof}}
 
-In this appendix, we prove the quantization rule introduced in the main text in the framework of effective Hamiltonian (cf.
-App.
-\ref{app:revieweffham}).
+In this appendix, we prove the quantization rule introduced in the main text in the framework of effective Hamiltonian.
 This proof is applicable to $D$-fold nearly-degenerate bands, with $D>1$.
@@
 
-As stated in the main text, our start point is a decomposition of the Hamiltonian $\hat{H}$ into $\hat{H_0}$ and a perturbation $\delta\hat{H}=\eta\hat{H}_1$, with $\eta$ a dimensionless small parameter.
+The proof of the quantization rule is a direct WKB solution of the Schr\"odinger equation.
+During the derivation, it is important to keep the order of magnitude of different quantities in control, which we use big-O notation and little-o nontation to quantify.
+The definitions for big-O notation and little-o notation we adopt are: $f(\boldsymbol{x})\sim\text{O}(\{g_i(\boldsymbol{x}), i\in 1..N\})$ as $\boldsymbol{x}\to\boldsymbol{0}$ if and only if $\exists C>0~\exists \delta>0$ such that for all $\boldsymbol{x}$ with $||\boldsymbol{x}||_\infty<\delta$, $|f(\boldsymbol{x})|<C\text{max}\{|g_i(\boldsymbol{x})|, i\in 1..N\}$; $f(\boldsymbol{x})\sim\text{o}(\{g_i(\boldsymbol{x}), i\in 1..N\})$ as $\boldsymbol{x}\to\boldsymbol{0}$ if and only if $\forall \epsilon>0~\exists \delta>0$ such that for all $\boldsymbol{x}$ with $||\boldsymbol{x}||_\infty<\delta$, $|f(\boldsymbol{x})|<\epsilon\text{max}\{|g_i(\boldsymbol{x})|, i\in 1..N\}$.
+Here, $||\boldsymbol{x}||_\infty=\text{max}\{|x_i|\}$ is uniform norm of the vector $\boldsymbol{x}$.
+
+As stated in \s{sec:qtznrules}, our starting point is a decomposition of the Hamiltonian $\hat{H}$ into $\hat{H}_0$ and a perturbation $\delta\hat{H}=\eta\hat{H}_1$, with $\eta$ a dimensionless small parameter.
 The nearly-degeneracy originates from $\eta\hat{H}$ breaking the exactly $D$-fold degenerate bands of $\hat{H_0}$.
@@
 
-The effective Hamiltonian $\effH$ is now governed by two small parameters: one is $1/l^2S$ due to the smallness of the field; one is $\eta$ due to the assumption of nearly-degeneracy.
-The zeroth order (in the sense of both small parameters) Hamiltonian is now $\effH_0=\epsilon_0(\bK)$, with $\epsilon_0(\bK)$ band structure of $\hat{H}_0$.
-The first order term of $\effH$ in $1/l^2S$ and $\eta$ is
+To express the Schr\"odinger equation in a tractable form, the effective Hamiltonian formalism is needed\cite{rotheffham,100p}.
+To the leading order in $B$ and $\eta$, the effective Hamiltonian $\mathfrak{H}(\boldsymbol{K})$ is the Peierls-Onsager Hamiltonian: $\mathfrak{H}_{0}(\boldsymbol{K}):=\epsilon(\boldsymbol{K})$, with $\epsilon(\boldsymbol{k})$ zero-field energy dispersion of $\hat{H}_0(\bk)$ and $\boldsymbol{K}=\boldsymbol{k}+(e/\hbar)\boldsymbol{A}(i\nabla_{\boldsymbol{k}})$.
+The effective Hamiltonian is expressed in the basis of a set of modified Bloch functions $\psi_{\boldsymbol{k}}$ \cite{rotheffham}.
+Expanding the wave function $\phi$ in this basis ($\phi=\sum_{\boldsymbol{k}}f_{\boldsymbol{k}}\psi_{\boldsymbol{k}}$), The Schr\"odinger equation becomes
+\begin{equation}
+(\mathfrak{H}(\boldsymbol{K})-E)f_{\boldsymbol{k}}=0.\label{eq:schrodinger}
+\end{equation}
+The subleading term $\mathfrak{H}_{1}(\boldsymbol{K})$ of the effective Hamiltonian comes from two parts: the first part is obtained by Peierls substitution of the generalized Zeeman interaction in the absence of $\delta \hat{H}$, which includes the Zeeman coupling to orbital and spin moments, as well as a geometric Berry contribution.
+The other part is Peierls substited $\epsilon_1(\bK)$, with $\epsilon(\bk)$ the projection of $\hat{H}_1$ to the $D$-fold degenerate bands of $\hat{H}_0$.
+In total,
 \begin{equation}
@@
 $M_z$, $s_z$, $\mathfrak{X}$ and $v$ in Eq.
-(\ref{effham1}) should be evaluated in the band structure of $\hat{H_0}$.
-$\epsilon_1(\bk)$ is the projection of $\hat{H}_1$ to the D-fold degenerate bands of $\hat{H}_0$.
+(\ref{effham1}) should be evaluated with wavefunctions in the degenerate subspace of $\hat{H}_0$.
+.
 In the main text, $\effH_1(\bk)$ is written as $\H(\bk)$.
+The above equation presupposes that the  magnetic field $B$ lies in the $-z$ direction.
+
+Employing the Landau gauge for Eq.
+(\ref{eq:schrodinger}) with $k_x$ a good quantum number, we seek a semiclassical solution in the WKB approximation.
+To the leading order (i.e., with $\mathfrak{H}_0(\bK)$ only), solutions of Eq.
+(\ref{eq:schrodinger}) are Zil'berman functions
+\begin{equation}
+g_{\bk}^\nu=\frac{1}{\sqrt{|v_x^\nu|}}e^{il^2k_x^0k_y}e^{-il^{2}\int k_x^\nu dk_y}\delta_{k_x^0 k_x},\la{zilberman}
+\end{equation}
+where $k_x^\nu$ is a function of $k_y$ satisfying   $\epsilon(k_x^\nu,k_y)=E$.
+The multiple solutions to $\epsilon(k_x^\nu,k_y)=E$ are indexed by $\nu$.
+Quantities   with the superscript $\nu$ (e.g., $v_x^\nu(\bk)$ in \q{zilberman}) should be evaluated at  $\bk = (k_x^\nu, k_y)$.
+
+%The solution to the  effective Schr\"odinger equation is defined by imposing a hard-wall boundary condition [on $f_{\bk} = \sum_\nu g_{\bk}^\nu$] at the classical turning points.
+In this manner we obtain  the  quantization rule for cyclotron motion.
 
@@
 \begin{equation}
-\boldsymbol{f}^\nu=\A^\nu\boldsymbol{g}^\nu,
+\boldsymbol{f}^\nu=\A^\nu\boldsymbol{g}^\nu,\label{wkb-wf}
 \end{equation}
@@
 and $c_a^\nu$ is $\bk$ independent.
-$\A^\nu$ is a $k_y$ dependent square matrix with the assumption $\A_{ab}^\nu$ is of order $\order(1, \eta l^2)$, with $\order(a, b)$ big-O notation indicating order of magnitude of either $a$ or $b$ (whichever is larger).
+$\A^\nu$ is a $k_y$ dependent square matrix with the assumption $\A_{ab}^\nu$ is of order $\order(1, \eta l^2)$, \red{where $\order(a, b)$ is a shorthand for $\order(\{a, b\})$}.
 Following section V A 2 of Ref.
@@
 \end{equation}
-where $\text{o}$ is small-o notation.
+where $\text{o}$ is little-o notation.
 One term omitted in Eq.
@@
 \begin{equation}
-\hbar\partial_{y}\A_{ac}^\nu=il^{2}[v_{x}^\nu]^{-1}[\effH_{1}]_{ab}\A_{bc}^\nu.
+\hbar\partial_{y}\A_{ac}^\nu=il^{2}[v_{x}^\nu]^{-1}[\effH_{1}]_{ab}\A_{bc}^\nu+\red{\text{o}(1, \eta l^2)}.
 \end{equation}
@@
 \begin{equation}
-\A^\nu=\overline{\exp}[il^{2}\int\frac{\effH_{1}}{\hbar v_{x}^\nu}dk_{y}],
+\A^\nu=\overline{\exp}[il^{2}\int\frac{\effH_{1}}{\hbar v_{x}^\nu}dk_{y}]+\red{\text{o}(1, \eta l^2)},
 \end{equation}
@@
 
+\red{The quantization rule can be obtained by requiring the wavefunction in Eq.
+(\ref{wkb-wf}) is single valued\cite{100p}, which directly leads the the quantization rule stated in \qq{eq:rule}{berryconn}.
+Since $\lambda$ is the eigenphase of $\A$ over a full cyclotron orbit, it bears the same uncertainty $\text{o}(1, \eta l^2)$.
+For example, for the Rashba model, the quantization rule misses a term proportional to $\eta^2 l^2$ [$l^2\delta S^2/S$ in Eq.
+(\ref{eq:Rashba-exact})].
+The quantization rule thus requires an extra condition $l^2\delta S^2/S\ll 1$, which is an upper bound for Landau level index: $n\ll(\delta S/S)^2$.}
+
 Besides the effective Hamiltonian approach described above, semiclassical wave packet theory has been developed in coupled bands\cite{culcer_coherent_2005}.
@@
 
-\section{Consistency conditions for the nearly-degenerate quantization rule}\label{sec:slowvariation}
-
-The following are consistency conditions for the nearly-degenerate quantization rule:
+\section{Comparison of numerically-exact Landau levels with our approximation scheme}\la{app:approximatevsexact}
+
+\red{In this appendix, we compare the exact Landau levels obtained from numerical diagonalization (with standard techniques reviewed in App.
+\ref{sec:numerical}) to the approximate Landau levels obtained from our quantization rule, as summarized in \qq{eq:rule}{berryconn}.
+The comparison shall be made for the Rashba-Dresselhaus 2DEG in an out-of-plane field [see Fig.\ \ref{fig:error}(a)], and for the Rashba 2DEG in a tilted field [see Fig.\ \ref{fig:error}(b)].
+In both cases, a closed-form analytic expression for the Landau-level spectrum is not known.
+We quantify the error of quantization rule by calculating $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for different parameter choices in both models.
+Semiclassical condition ($l^2 S\gg 1$) and near degeneracy condition ($\delta S/S\ll 1$) are satisfied within the parameter range in Fig.
+\ref{fig:error}.
+Just as for the Rashba model [cf.
+Eq.(\ref{eq:Rashba-exact})], the accuracy of our rule improves with decreasing parameter $l^2\delta S(\alpha,\beta)^2/S$, suggesting this term being the one of the leading error terms of the quantization rule [cf.
+the discussion in App.
+\ref{app:quantizationruleproof}].}
+
+%\red{In Fig.\ \ref{fig:error}(a), a comparison is made between the Landau levels obtained from exact numerical diagonalization of $H_{RD}(\bK)$ (plus the Zeeman coupling to spin) and those obtained from the quantization rule.
+Just as for the Rashba model, the accuracy of our rule improves with decreasing parameter $l^2\delta S(\alpha,\beta)^2/S$ [cf.
+Eq.(\ref{eq:Rashba-exact}) and the discussion in App.
+\ref{app:quantizationruleproof}].
+The error has been estimated by comparing the difference in energies (rule-obtained vs exact-diagonalized) for a single Landau level.
+For our chosen spin-orbit parameters $\alpha$ and $\beta$ range, the difference in energies does not exceed $2\%$ of $\var_c$ as $l^2\delta S^2/S$ varies over $[0,0.8]$.}
+
+%In Fig.
+\ref{fig:error} (b), we focus on a regime ($\hbar\alpha k_{\sma{E}}{\lesssim}\var_c$) where the nearly-degenerate orbits are appreciably hybridized and calculate the error defined above for the Landau level closest to the Dirac point.
+For fixed  $B_{\perp}$ and a range of $(\alpha,\zpar)$ wherein  $l^2\delta S^2/S$ varies over $[0,0.2]$, the difference between semiclassical and exact Landau levels never exceeds 0.3\% of the cyclotron energy $\var_c$.
+
+%Assuming the semiclassical and near-degeneracy conditions, our quantization rule \qq{eq:rule}{eq:H1} remains valid, however the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}.
+We may anyway diagonalize $\cala$ numerically, and compare the resultant semiclassical Landau levels with the exact diagonalization of $H_{RZ}(\boldsymbol{K})$; to our knowledge, there exists no analytic solution of $H_{RZ}(\boldsymbol{K})$ for generic values of $\alpha,\zpar$ and $B_{\perp}$.
+For fixed  $B_{\perp}$ and a range of $(\alpha,\zpar)$ wherein  $l^2\delta S^2/S$ varies over $[0,0.2]$, the difference between semiclassical and exact Landau levels never exceeds  0.3\% of the cyclotron energy $\var_c$; this difference shows a strong positive correlation with $l^2\delta S^2/S$ [compare the left and right panels of Fig.\ \ref{fig:RZ} (d)], just like in the Rashba-Dresselhaus model.
+
+%as illustrated in in \fig{fig:RD}(a). Here we have shown a strong positive correlation between the error of the quantization rule and  $l^2\delta S(\alpha,\beta)^2/S$;
+
+%The difference in energies tends to increase with smaller field [compare the left and right panels of   \fig{fig:RD}(b)] and shows a strong positive correlation with $l^2\delta S(\alpha,\beta)^2/S$ [compare \fig{fig:RD}(c) with \fig{fig:RD}(d)] for various choices of the spin-orbit parameters $(\alpha,\beta)$.
+This correlation may be anticipated from \q{eq:Rashba-exact}, which analytically demonstrates how terms involving $l^2\delta S^2/S$ modifies the quantization rule in the case where $\beta{=}0$.
+
+%In \s{sec:llquasideg} we will further motivate the study of $H_{RD}$ by investigating the prevalence of Landau-level degeneracies.
+
+\begin{figure}
+\includegraphics[width=1.0\columnwidth]{error.png}
+\caption{\red{Comparison of quantization rule and exact diagonalization.
+(a) For various spin-orbit parameters $(\alpha,\beta)$ of the Rashba-Dresselhaus model, we plot in left panel $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that lies closest to energy $E=0.4eV$, where $\epsilon_\text{rule}$ is determined by Eq.
+(\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RD}(\bK)$ with Zeeman interaction for spin.
+We also plot in right panel $l^2\delta S^2/S$, which has a strong positive relation with error.
+(b) For various parametrizations ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in the left panel the error for a single Landau level that is closest to $\epsilon_0$ [as defined in Eq.
+(\ref{whereisdiracpoint})] $\epsilon_\text{rule}$ is determined by Eq.
+(\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RZ}(\bK)$ with Zeeman interaction for spin.
+The corresponding $l^2 \delta S^2/S$ is plotted in the right panel.
+For numerical convergence\cite{RZfignote}, we have presented data only in a strip [within ($\alpha$, $Z_\parallel$)-space] where $0.4{<}\epsilon_0{<}1.0$(eV).Parameters for (a): $m=0.076m_0$, $l=200$\AA~and $g_{s\perp}=2$; parameters for (d): $m=0.076m_0$, $l=100$\AA~and $g_{s\perp}=2$.}\label{fig:error}}
+\end{figure}
+
+%\subsection{Rashba 2DEG in a tilted field}\la{app:rashba2DEGtilted_comparenumerics}
+
+%In \s{sec:inplanezeeman}, we focused on a parameter regime ($\hbar\alpha k_{\sma{E}}{\gg}\var_c$) of the Rashba 2DEG (in tilted field), where the nearly-degenerate spin-split orbits are negligibly hybridized by the Zeeman interaction -- except near a type-II Dirac point.
+
+\section{Existence of Landau-level quasidegeneracy}\label{sec:proofLLquasideg}
+
+For our quantization rules to be consistent, the following inequalities are necessary:
 \e{ |l^2S| \gg |\lambda_a|,\, \left|l^2\p{S}{E}\right| \gg \left|\p{\lambda_a}{E}\right|,\, \left|S\right| \gg \left|\p{\lambda_a}{l^2}\right|.} 
 Due to the latter two inequalities, we shall refer to $\lambda_{a}$ as \textit{slowly-varying} (with respect to $E$ and $B$), in comparison with the rapidly-varying $l^2S$.
-To appreciate the difference in scales, consider that for $\lambda_a$ to change by $2\pi$ due to a variation $l^2$ (at fixed energy), we estimate [in the weak-field regime; cf.\ \q{phaseindependentorbit}] that $l^2$ must change on the scale of $2\pi/\delta S$; this scale is much greater than the period of quantum oscillations ($T_{1/B}{:}{=}2\pi/ S$), by our assumption of nearly-degeneracy.
+To appreciate the difference in scales, consider that for $\lambda_a$ to change by $2\pi$ due to a variation $l^2$ (at fixed energy), we estimate [in the weak-field regime; cf.\ \q{phaseindependentorbit}] that $l^2$ must change on the scale of $2\pi/\delta S$; this scale is much greater than the period of quantum oscillations ($T_{l^2}{:}{=}2\pi/S$), by our assumption of near degeneracy.
 Analogously, for $\lambda_a$ to vary by $2\pi$ due to a variation of $E$ (at fixed field) by $\delta E$, we estimate [from \q{phaseindependentorbit}] that $\delta E {\sim} 2\pi/l^2 (\partial \delta S/\partial E)$, which is generically much larger than the cyclotron energy $\epsilon_c{=}2\pi/l^2 (\partial  S/\partial E)$.
-In the strong-field regime (where $\delta \var$ may be neglected from \q{eq:H1}), $\lambda_a$ is independent of $B$ (to the accuracy of semiclassical theory), and depends on $E$ solely through the slow variation of $\calm$.
+In the strong-field regime (where $\delta \var$ may be neglected from \q{eq:H1}), $\lambda_a$ is independent of $B$ (to the accuracy of our theory), and depends on $E$ solely through the slow variation of $\calm$.
 In the absence of symmetry, we estimate
@@
 
-\section{Existence of Landau-level quasidegeneracy}\label{sec:proofLLquasideg}
-
-This appendix demonstrates that, if a degeneracy of $\cala$ [$e^{i\lambda_+}{=}e^{i\lambda_-}$] occurs at $(\bar{E},\bar{B})$, there exists two Landau levels in close proximity to $(\bar{E},\bar{B})$ which satisfy the nearly-degeneracy conditions defined in \qq{llquasideg}{llquasidegB}.
+Armed with the inequalities above, we now demonstrate that, if a degeneracy of $\cala$ [$e^{i\lambda_+}{=}e^{i\lambda_-}$] occurs at $(\bar{E},\bar{B})$, there exists two Landau levels in close proximity to $(\bar{E},\bar{B})$ which satisfy the nearly-degeneracy conditions defined in \qq{llquasideg}{llquasidegB}.
 
@@
 \e{\f{E_+-E_-}{\var_c} \approx &\; \f{r}{\var_c}\left(\f1{\calq'_+}-\f1{\calq'_-}\right)\approx  \f{r}{2\pi}\var_c \left( \lambda'_- -\lambda'_+\right), \label{estimate}}
-which is a justification for the order-of-magnitude estimate in \q{llquasideg}.
-What is left is to estimate $\lambda_{\pm}'$, which we have accomplished in \app{sec:slowvariation} in both weak- and strong-field regimes.
-Combining  \q{dlambdadE} with \q{estimate}, we deduce the inequality in \q{llquasideg}.
+which is a justification for the order-of-magnitude estimate in \q{llquasideg}. Combining  \q{dlambdadE} with \q{estimate}, we deduce the inequality in \q{llquasideg}.  
 %From \s{sec:qtznrules}, we know that for sufficiently weak field ($\var_c\ll \Delta$), $\lambda_{\pm}'\approx \pm l^2\delta S'/2$.
@@
 \hlineB{2}
-             class number & $u$ & $s$ & symmetry constraint & $\det{\A}$ & $\breve{g}$ & codimension \\
+class label & $u$ & $s$ & symmetry constraint & $\det{\A}$ & $\breve{g}$ & codimension \\
 \hline
-1 & 0 & 0 & $\A=\breve{g}\A\breve{g}^{-1}$ & - & $\breve{g}\propto I$ & 3  \\
+I-1 & 0 & 0 & $\A=\breve{g}\A\breve{g}^{-1}$ & - & $\breve{g}\propto I$ & 3  \\
 &  &  &  & - & $\breve{g} \not\propto I$ & 1  \\
-2& 0 & 1 & $\A=\breve{g}\A^*\breve{g}^{-1}$ & 1 & $(\breve{g}K)^2=I$ & 1 \\
+I-2 & 0 & 1 & $\A=\breve{g}\A^*\breve{g}^{-1}$ & 1 & $(\breve{g}K)^2=I$ & 1 \\
 &  &  &  & 1 & $(\breve{g}K)^2=-I$ & 3 \\
@@
 &  &  &  & -1 & $(\breve{g}K)^2=-I$ & $\times$ \\
-3 & 0 & 0 & $\A=\breve{g}(g^{L-1}\circ\bk_0) \A_{1/L}^{L}$ & - & - & 1 \\
-4 & 0 & 1 & $\A=\breve{g}(g^{L-1}\circ\bk_0) (K^i\A_{1/L}K^i)^L$ & - & $L=N$ & 1 \\
+II-1 & 0 & 0 & $\A=\breve{g}(g^{L-1}\circ\bk_0) \A_{1/L}^{L}$ & - & - & 1 \\
+II-2 & 1 & 1 & $\A=\breve{g}\A^T\breve{g}^{-1}$ & - & $(\breve{g}K)^2=I$ & 2 \\
+& & & & - & $(\breve{g}K)^2\ne I$ & 0 \\
+II-3 & 0 & 1 & $\A=\breve{g}(g^{L-1}\circ\bk_0) (K^i\A_{1/L}K^i)^L$ & - & $L=N$ & 1 \\
 & & & & 1 & $L\ne N$ & 1 \\
@@
 & & & & -1 & $L\ne N$, $(\breve{g}K)^2=-I$ & $\times$ \\
-5 & 1 & 0 & $\A=\breve{g}\A^\dagger\breve{g}^{-1}$ & 1 &$\breve{g} \propto \sigma_z$& 2\\
+II-4 & 1 & 0 & $\A=\breve{g}\A^\dagger\breve{g}^{-1}$ & 1 &$\breve{g} \propto \sigma_z$& 2\\
 & & & & 1 &$\breve{g} \not\propto \sigma_z$ & 0\\
@@
 & & & & -1 &$\breve{g} \not\propto I$& 0\\
-6 & 1 & 1 & $\A=\breve{g}\A^T\breve{g}^{-1}$ & - & $(\breve{g}K)^2=I$ & 2 \\
-& & & & - & $(\breve{g}K)^2\ne I$ & 0 \\
-7 & 0 & 0 & $\A_2=\breve{g}\A_1\breve{g}^{-1}$ & - & - & 3 \\
-8 & 0 & 1 & $\A_2=\breve{g}\A_1^*\breve{g}^{-1}$ & - & - & 3\\
-9 & 1 & 0 & $\A_2=\breve{g}\A_1^\dagger\breve{g}^{-1}$ & - & - & 3\\
-10 & 1 & 1 & $\A_2=\breve{g}\A_1^T\breve{g}^{-1}$ & - & - & 3 & \\
+III-1 & 0 & 0 & $\A_2=\breve{g}\A_1\breve{g}^{-1}$ & - & - & 3 \\
+III-2 & 1 & 1 & $\A_2=\breve{g}\A_1^T\breve{g}^{-1}$ & - & - & 3 & \\
+III-3 & 0 & 1 & $\A_2=\breve{g}\A_1^*\breve{g}^{-1}$ & - & - & 3\\
+III-4 & 1 & 0 & $\A_2=\breve{g}\A_1^\dagger\breve{g}^{-1}$ & - & - & 3\\
 \hlineB{2}
@@
 
-For four of  the ten classes (7, 8, 9, 10), the symmetry relates the propagators of distinct and disconnected orbits, but each propagator (corresponding to one orbit) is itself unconstrained.
+For four of  the ten classes (III 1-4), the symmetry relates the propagators of distinct and disconnected orbits, but each propagator (corresponding to one orbit) is itself unconstrained.
 Therefore, the codimensions are still 3.
 For the other six classes, self constraints of $\A$ are imposed.
-In particular, in class 2, 4, 5, $\det(\A)$ is quantized at $\pm 1$\cite{topoferm,100p}.
-
-The self constraints of the six classes can be divided into two types: (i) restricting $\A$ to only a submanifold of SU(2) (class 1, 2, 5, 6); (ii) expressing the propagator $\A$ as a product of propagators over a fraction of the period [e.g., Eq.
-(\ref{eq:sigmazconstraint})] (class 3, 4).
+In particular, in class I-2, II-3, II-4, $\det(\A)$ is quantized at $\pm 1$\cite{topoferm,100p}.
+
+The self constraints of the six classes can be divided into two types: (i) restricting $\A$ to only a submanifold of SU(2) (class I-1, I-2, II-2, II-4); (ii) expressing the propagator $\A$ as a product of propagators over a fraction of the period [e.g., Eq.
+(\ref{eq:sigmazconstraint})] (class II-1, II-3).
 For the former case, we define symmetric coordinates by restricting canonical parametrization of $\A$ to that submanifold; in the latter case, we employ the canonical parametrization of the fractional propagators to define symmetric coordinates for the full propagator $\A$.
@@
 
-\paragraph*{class 1} According to the general rules of sewing matrix, the sewing matrix $\breve{g}$ can be made diagonal by a gauge transformation
+\paragraph*{class I-1} According to the general rules of sewing matrix, the sewing matrix $\breve{g}$ can be made diagonal by a gauge transformation
 \e{
@@
 
-\paragraph*{class 2}
+\paragraph*{class I-2}
 By a gauge transformation, the sewing matrix $\breve{g}$ can be made off-diagonal
@@
 
-\paragraph*{class 3} In this class (and also class 4), the full propagator can be constructed from $1/L$ of it, where $L$ is the smallest positive integer fulfilling $g^L\circ \bk_0=\bk_0$.
+\paragraph*{class II-1} In this class (and also class II-3), the full propagator can be constructed from $1/L$ of it, where $L$ is the smallest positive integer fulfilling $g^L\circ \bk_0=\bk_0$.
 Here, $\bk_0$ is the base point of $\A$.
@@
 
-\paragraph*{class 5} In class 4, $L=N$ is guaranteed.
-However, in class 5, this is generally not true.
-For symmetry operations still respecting $L=N$, the codimension calculation is similar to what is done in class 4.
+\paragraph*{class II-3} In class II-1, $L=N$ is guaranteed.
+However, in class II-3, this is generally not true.
+For symmetry operations still respecting $L=N$, the codimension calculation is similar to what is done in class II-1.
 The only example of $L\ne N$ is $T\mathfrak{c}_{6z,n\boldsymbol{c}/6}$ ($n\in\{0,1,2,3,4,5\}$), where $L=3$ and $N=6$.
@@
 and the codimension is 1.
-If $h=i\sigma_y$, from the fourth entry of class 2, we deduce $\det \A_{1/L}=1$.
+If $h=i\sigma_y$, from the fourth entry of class I-2, we deduce $\det \A_{1/L}=1$.
 Choosing the parametrization in Eq.
@@
 
-\paragraph*{class 5 and 6} Calculation of codimensions for the two classes follow the same pattern as class 1 and 2 and is therefore omitted here.
+\paragraph*{class II-2 and II-4} Calculation of codimensions for the two classes follow the same pattern as class I-1 and I-2 and is therefore omitted here.
 
 In the main text, we assume the SOC can be turned off continuously without increasing or decreasing degree of degeneracy.
-With this assumption, $\det(A)=1$ for class 2, 4, 5, reducing Tab.
+With this assumption, $\det(A)=1$ for class I-2, II-3, II-4, reducing Tab.
 \ref{table:fullcodimension} to Tab.

### 2019-01-31 paper.tex
submitted to PRX

@@
 Semiclassical quantization rules compactly describe the energy dispersion of Landau levels, and are predictive of quantum oscillations in transport and thermodynamic quantities.
-Such rules –- as formulated by Onsager, Lifshitz and Roth –-
+Such rules -- as formulated by Onsager, Lifshitz and Roth --
 apply when the spin-orbit interaction dominates over the Zeeman interaction (or vice versa), but does not generally apply when the two interactions are comparable in strength.
@@
 More generally, our rule describes the Landau quantization of any number of nearly degenerate energy bands -- in any symmetry class.
-The resultant Landau-level spectrum is generically non-equidistant but may contain \blue{spin (or pseudospin)} degeneracies.
+The resultant Landau-level spectrum is generically non-equidistant but may contain spin (or pseudospin) degeneracies.
 To tune to such degeneracies in the absence of crystalline point-group symmetries, three real parameters are needed.
-We have exhaustively identified all symmetry classes of cyclotron orbits for which this number is reduced from three, thus establishing symmetry-enforced`non-crossing rules' for Landau levels.
+We have exhaustively identified all symmetry classes of cyclotron orbits for which this number is reduced from three, thus establishing symmetry-enforced `non-crossing rules' for Landau levels.
 In particular, only one parameter is needed {in the presence of} spatial rotation {or inversion}; this single parameter may be the magnitude or orientation of the field.
@@
 The original formulation of the rule -- by Onsager\cite{Onsager} and Lifshitz\cite{lifshitz_kosevich,lifshitz_kosevich_jetp} -- neglects the effect of spin-orbit coupling.
-While subsequent generalizations by Roth,
-\cite{rotheffham,rothmag} Mikitik\cite{Mikitik_quantizationrule},
-and the present authors\cite{topoferm,100p} account for the spin-orbit effect, such quantization rules apply only when the spin-orbit splitting of energy bands is much stronger (or much weaker) than the Zeeman interaction.
+While subsequent generalizations by Roth\cite{rotheffham,rothmag}, Mikitik\cite{Mikitik_quantizationrule}, and the present authors\cite{topoferm,100p} account for the spin-orbit effect, such quantization rules apply only when the spin-orbit splitting of energy bands is much stronger (or much weaker) than the Zeeman interaction.
 
@@
 \end{equation}
-Given a magnetic field in the $-z$ direction, and focusing on energies much greater than $m\alpha^2$, the cyclotron orbits [illustrated in \fig{fig:orbits}(a)]   are split in $\bk$-space with a differential area  $\delta S$ that is much less than their average area $S$:\footnote{The expressions for $\delta S$ and $S$ in \q{deltaSvsS} are asymptotically valid for $E{\gg}m\alpha^2$.}
+Given a magnetic field in the $-z$ direction, and focusing on energies much greater than $m\alpha^2$, the cyclotron orbits [illustrated in \fig{fig:orbits}(a)]   are split in $\bk$-space with a differential area  $\delta S$ that is much less than their average area $S$\footnote{The expressions for $\delta S$ and $S$ in \q{deltaSvsS} are asymptotically valid for $E{\gg}m\alpha^2$.}:
 \e{\delta S = 4\pi m \alpha k_E/\hbar\ll S =\pi k_E^2; \;\; k_{E}:=\f{\sqrt{2m E}}{\hbar}.\label{deltaSvsS}}
@@
 Our work presents a generalized rule to describe the Landau quantization of nearly-degenerate energy bands, for which  spin-orbit-split bands is but one example.
-\blue{By the \textit{near-degeneracy} condition, we generally mean that
+By the \textit{near-degeneracy} condition, we generally mean that
 the ratio of differential to average area is small: $|\delta S/S|{\ll}1$.
-Our proposed rule relies also on a second condition -- that $S$ is much larger than the inverse square of the magnetic length $l{=}\sqrt{\hbar/eB}$; this is the standard semiclassical condition in the Onsager-Lifshitz-Roth theory.} By treating \textit{both} $|\delta S/S|$ and $1/l^2|S|$   as small parameters with finite ratio $l^2|\delta S|$, our perspective diverges from and generalizes \textit{single-parameter} semiclassical theories.\cite{kohn_effham,blount_effham,rotheffham,wannier_fredkin,fischbeck_review,Mikitik_quantizationrule,topoferm,100p,gao_zero-field_2017}
+Our proposed rule relies also on a second condition -- that $S$ is much larger than the inverse square of the magnetic length $l{=}\sqrt{\hbar/eB}$; this is the standard semiclassical condition in the Onsager-Lifshitz-Roth theory.
+By treating \textit{both} $|\delta S/S|$ and $1/l^2|S|$   as small parameters with finite ratio $l^2|\delta S|$, our perspective diverges from and generalizes \textit{single-parameter} semiclassical theories\cite{kohn_effham,blount_effham,rotheffham,wannier_fredkin,fischbeck_review,Mikitik_quantizationrule,topoferm,100p,gao_zero-field_2017}.
 
@@
 This extension allows  to formulate semiclassical quantization rules for spin-orbit coupled materials in \textit{any} symmetry class -- with or without spatial inversion symmetry, with or without time-reversal symmetry.
-The unifying rule is presented in \s{sec:qtznrules} for nearly-degenerate bands with a spin\blue{-half (or pseudospin-half)} degree of freedom.
+The unifying rule is presented in \s{sec:qtznrules} for nearly-degenerate bands with a spin-half (or pseudospin-half) degree of freedom.
 As elaborated in \s{sec:discussion}, the most general formulation of our rule is applicable  to any number of nearly-degenerate bands of any symmetry.}
@@
 In \s{sec:inplanezeeman}, we investigate the Landau-Zener tunneling dynamics that occur in the vicinity of a II-Dirac point; in particular, we will {demonstrate that our quantization rule can account for quantum tunneling between nearly-degenerate bands -- a phenomenon known as interband breakdown\cite{kaganov_coherent_1983,slutskin_dynamics_1968,AALG,100p}.
-We will also} critically evaluate a recent claim\cite{obrien_magnetic_2016} of perfect Klein tunneling at the energy of the Dirac point -- \blue{we find that such tunneling is never perfect with a proper account of the Zeeman interaction.}
+We will also} critically evaluate a recent claim\cite{obrien_magnetic_2016} of perfect Klein tunneling at the energy of the Dirac point -- we find that such tunneling is never perfect with a proper account of the Zeeman interaction.
 
@@
 
-In this section, we apply our rule to the Landau levels of the Rashba model [cf.\ \q{eq:Rashba-Hamiltonian}], for which analytic, closed-form solutions exist for verification.\cite{bychkov_oscillatory_1984}
+In this section, we apply our rule to the Landau levels of the Rashba model [cf.\ \q{eq:Rashba-Hamiltonian}], for which analytic, closed-form solutions exist for verification\cite{bychkov_oscillatory_1984}.
 
@@
 the remaining terms may be interpreted as $B$-induced deformations of the bands.
-The orbital moment term $B M_z$, which generally couples the two-band subspace (of interest) to all other bands, is absorbed into the Zeeman spin interaction with a phenomenological g-factor $g_{s\perp}$.\footnote{For simplicity, we neglect here off-diagonal elements of $M_z$ in the basis of $S_z=\pm 1/2$, with $\vec{z}$ the direction of the field.} It is well-known that the Zeeman term tends to polarize spin in the direction of $\bB$; remarkably, the non-Abelian Berry term  also has a polarizing effect, but with opposite sign.
+The orbital moment term $B M_z$, which generally couples the two-band subspace (of interest) to all other bands, is absorbed into the Zeeman spin interaction with a phenomenological g-factor $g_{s\perp}$\footnote{For simplicity, we neglect here off-diagonal elements of $M_z$ in the basis of $S_z=\pm 1/2$, with $\vec{z}$ the direction of the field.}.
+It is well-known that the Zeeman term tends to polarize spin in the direction of $\bB$; remarkably, the non-Abelian Berry term  also has a polarizing effect, but with opposite sign.
 These two effects completely cancel for free electrons (with $g_{s\perp}=2$ and $m$ equal to the free-electron mass $m_0$), but not generically in band systems.
@@
 \e{\lambda_{\pm}= \pm \f{l^2\delta S}{2} +\pi \pm \f{\pi^2}{4}\f{(g_{s\perp}m/m_0-2)^2}{l^2\delta S} + O(B^2). \label{lambdasmallB}}
-\q{eq:rule}, combined with the first two terms on the right-hand-side of \q{lambdasmallB}, may alternatively be derived from  the standard Onsager-Lifshitz rules for two independent orbits, with a common $\pi$ Berry-phase correction for each orbit:\footnote{The intra-band Zeeman and orbital-moment couplings vanish due spacetime-inversion symmetry\cite{topoferm}.} $l^2(S{\pm}\delta S)/2\pi {\in}\Z$.
+\q{eq:rule}, combined with the first two terms on the right-hand-side of \q{lambdasmallB}, may alternatively be derived from  the standard Onsager-Lifshitz rules for two independent orbits, with a common $\pi$ Berry-phase correction for each orbit\footnote{The intra-band Zeeman and orbital-moment couplings vanish due spacetime-inversion symmetry\cite{topoferm}.}: $l^2(S{\pm}\delta S)/2\pi {\in}\Z$.
 Higher-order terms in \q{lambdasmallB} reflect the field-induced hybridization of the spin-orbit-split orbits.
-Eq.\ (\ref{lambdasmallB}) has been partially obtained by Mineev for the Rashba model;\cite{mineev_haas--van_2005} he missed the second term in $(g_{s\perp}m/m_0-2)$ [cf.\ \q{lambdasmallB}], due to his neglect of the interband Berry connection.
+Eq.\ (\ref{lambdasmallB}) has been partially obtained by Mineev for the Rashba model\cite{mineev_haas--van_2005}; he missed the second term in $(g_{s\perp}m/m_0-2)$ [cf.\ \q{lambdasmallB}], due to his neglect of the interband Berry connection.
 
@@
 with the functional forms of $\delta S(E)$ and $S(E)$ provided in \q{deltaSvsS};  $n_{+}{\ge} 1$ and $n_-{\ge} 0$ here are integer-valued labels for two distinct sets of levels.
-\blue{In the near-degenerate ($\delta S/S\ll 1$) and semiclassical ($1/l^2S \ll 1$) regime, with finite $l^2\delta S$,}  the two terms in \q{eq:Rashba-exact} involving $\delta S/S$  may be neglected, and \q{eq:Rashba-exact} reduces to our quantization rule with $\lambda_{\pm}$ given by \q{eq:Rashba-lambda}.
-
-\blue{With the further inclusion of the Dresselhaus spin-orbit interaction in \q{eq:Rashba-Hamiltonian}, no closed-form analytic solution (of the Landau levels) is known.
-We may anyway verify the validity of our approximation scheme  -- by comparison with the Landau levels obtained from numerical exact diagonalization; this  is carried out in  \app{app:approximatevsexact}.}
-
-%The just-stated inequality is equivalent to an upper bound on the Landau-level index: $n_{\pm}{\ll} (S/\delta S)^2$, which is distinct from the lower bound $n_{\pm}{\gg} 1$ dictated by the usual semiclassical condition.
-
-%In the near-degenerate regime ($E{\gg}m\alpha^2$),
+In the near-degenerate ($\delta S/S\ll 1$) and semiclassical ($1/l^2S \ll 1$) regime, with finite $l^2\delta S$, the two terms in \q{eq:Rashba-exact} involving $\delta S/S$  may be neglected, and \q{eq:Rashba-exact} reduces to our quantization rule with $\lambda_{\pm}$ given by \q{eq:Rashba-lambda}.
+
+With the further inclusion of the Dresselhaus spin-orbit interaction in \q{eq:Rashba-Hamiltonian}, no closed-form analytic solution (of the Landau levels) is known.
+We may anyway verify the validity of our approximation scheme  -- by comparison with the Landau levels obtained from numerical exact diagonalization; this  is carried out in  \app{app:approximatevsexact}.
 
@@
 \includegraphics[width=1.0\columnwidth]{RZ.png}
-\caption{(a) illustrates the cyclotron orbits of the Rashba 2DEG in a \blue{tilted} magnetic field.
+\caption{(a) illustrates the cyclotron orbits of the Rashba 2DEG in a tilted magnetic field.
 The inset illustrates an enlarged view of near II-Dirac point.
-(b) illustrates the cyclotron orbit at the energy of the II-Dirac point; \blue{a Klein-tunneling electron will follow a trajectory that resembles the edge of a M\"obius strip.} The orbit is drawn over the  spin-splitting field ($d_x,d_y$) of the degeneracy-lifting Hamiltonian $\delta\var$ [cf.\ \q{eq:RZ-Hamiltonian}].
-The wavefunction along the inner (resp.\ outer) component of the \blue{M\"obius-strip} orbit has its pseudospin aligned parallel (resp.\ anti-parallel) to the spin-splitting field.
+(b) illustrates the cyclotron orbit at the energy of the II-Dirac point; a Klein-tunneling electron will follow a trajectory that resembles the edge of a M\"obius strip.
+The orbit is drawn over the  spin-splitting field ($d_x,d_y$) of the degeneracy-lifting Hamiltonian $\delta\var$ [cf.\ \q{eq:RZ-Hamiltonian}].
+The wavefunction along the inner (resp.\ outer) component of the M\"obius-strip orbit has its pseudospin aligned parallel (resp.\ anti-parallel) to the spin-splitting field.
 (c) schematically illustrates  Landau levels near the II-Dirac point (in the weak-hybridization regime).
-The dashed line represents the Onsager-Lifshitz-Roth quantization of the \blue{M\"obius-strip} orbit [cf.\ Eq.\ (\ref{trefoilrule})], and the solid line incorporates the first-order correction [cf.\ Eq.\ (\ref{RZfirstorderE})] due to tunneling.
-(d) \blue{The black solid line is the plot of $\delta E_n$ [cf.
+The dashed line represents the Onsager-Lifshitz-Roth quantization of the M\"obius-strip orbit [cf.\ Eq.\ (\ref{trefoilrule})], and the solid line incorporates the first-order correction [cf.\ Eq.\ (\ref{RZfirstorderE})] due to tunneling.
+(d) The black solid line is the plot of $\delta E_n$ [cf.
 Eq.
-(\ref{RZfirstorderE})], which is the energetic correction due to deviations from perfect Klein tunneling; for comparison, the red dashed line shows the numerically-exact deviations obtained from exact diagonalization.} This comparison is made for the Landau levels closest to 0.45eV and with even Landau-level index $n$; for the parameters we have chosen ($m{=}0.076m_0$, $\alpha{=} 1.5\times10^{5}$cm/s, $Z_\parallel {=}$1meV and $g_{s\perp}=2$),  the II-Dirac point lies at 0.5eV.
+(\ref{RZfirstorderE})], which is the energetic correction due to deviations from perfect Klein tunneling; for comparison, the red dashed line shows the numerically-exact deviations obtained from exact diagonalization.
+This comparison is made for the Landau levels closest to 0.45eV and with even Landau-level index $n$; for the parameters we have chosen ($m{=}0.076m_0$, $\alpha{=} 1.5\times10^{5}$cm/s, $Z_\parallel {=}$1meV and $g_{s\perp}=2$),  the II-Dirac point lies at 0.5eV.
 %Out-of-plane Zeeman coupling is negligibly weak.
@@
 However, with a proper account of $Z_\perp$, we find instead that $\bar{\mu}$ has a nonvanishing minimum: $\bar{\mu}_{\sma{\text{min}}}{:}{=} (g_{s\perp} m/m_0)(Z_\perp/4\hbar\alpha k_{E})$, which is a product of the dimensionless effective mass and the ratio of the out-of-plane Zeeman splitting over the spin-orbit splitting.
-\blue{This minimum may be significant for semiconductor heterostructures (e.g.,  $g_{s\perp}m/m_0{\sim} 1$ in InAs heterostructures\cite{pakmehr_g-factor_2015}) and  for heavy-fermion systems.}
+This minimum may be significant for semiconductor heterostructures (e.g.,  $g_{s\perp}m/m_0{\sim} 1$ in InAs heterostructures\cite{pakmehr_g-factor_2015}) and  for heavy-fermion systems.
 
@@
 The second line is an approximation for $Z_{\perp}{\rightarrow}0$, and has greater utility where $g_{s\perp}m{\ll}m_0$.
-\blue{For two adjacent Landau levels, we have plotted $E_n^{(0)}+\delta E_n$ as dashed lines in Fig.
+For two adjacent Landau levels, we have plotted $E_n^{(0)}+\delta E_n$ as dashed lines in Fig.
 \ref{fig:RZ}(c).
-The validity of Eq.\ (\ref{RZfirstorderE}) is  further supported by a comparison with numerically-exact Landau levels, as illustrated in Fig.\ \ref{fig:RZ}(d).}
+The validity of Eq.\ (\ref{RZfirstorderE}) is  further supported by a comparison with numerically-exact Landau levels, as illustrated in Fig.\ \ref{fig:RZ}(d).
 
@@
 
-{The Landau levels derived from \q{eq:rule} are generically non-equidistant, and the spin\blue{-half (or pseudospin-half)} degeneracy between Landau levels is generically lifted due to the subleading corrections ($\lambda_{1,2}$).
+{The Landau levels derived from \q{eq:rule} are generically non-equidistant, and the spin-half (or pseudospin-half) degeneracy between Landau levels is generically lifted due to the subleading corrections ($\lambda_{1,2}$).
 As argued in \s{sec:qtznrules},} the level splitting is approximately $\var_c\delta \lambda/2\pi$ with $\delta \lambda=|\lambda_1-\lambda_2|$.
-Conversely, Landau levels are approximately spin-degenerate if $\lambda_1{=}\lambda_2$ (mod $2\pi$) -- this degeneracy condition for the eigenvalues of $\A$ may require fine-tuning of the Peierls-Onsager Hamiltonian.
+Conversely, Landau levels are approximately spin-degenerate if $\lambda_1{=}\lambda_2$ (mod $2\pi$) -- this degeneracy condition for the eigenvalues of $\A$ typically requires fine-tuning of some Hamiltonian parameters.
 
@@
 For the exactly-soluble Rashba model ($r_2{=}0$), these $\mathfrak{c}_{\infty}$-protected quasidegeneracies  are consistent with (and partially demystify)  the abundance of \textit{exact} level crossings in the spectrum of $H_R(\bK)$ [cf.\ \q{eq:Rashba-exact}]; such crossings are not expected from the Wigner-von Neuman non-crossing rule\cite{neumann2000behaviour}.
-The zero-radius sphere (i.e., a point) has codimension three, as would be expected if symmetry were absent (cf.
+The zero-radius sphere (that is, a point) has codimension three, as would be expected if symmetry were absent (cf.
 \s{sec:introducecodimension}).
@@
 
-The above discussion is reminiscent of topological semimetals whose corresponding Bloch Hamiltonians are energy-degenerate at Dirac-Weyl points\cite{wang2012dirac,wan2011topological} and/or line nodes.\cite{burkov2011topological} Both Dirac points (in 2D $\bk$-space, e.g., graphene\cite{neto2009electronic}) and line nodes (in 3D $\bk$-space) are attainable by tuning two wavenumbers; the stability of such codimension-two manifolds relies on crystallographic point-group symmetries.
+The above discussion is reminiscent of topological semimetals whose corresponding Bloch Hamiltonians are energy-degenerate at Dirac-Weyl points\cite{wang2012dirac,wan2011topological} and/or line nodes\cite{burkov2011topological}.
+Both Dirac points (in 2D $\bk$-space, e.g., graphene\cite{neto2009electronic}) and line nodes (in 3D $\bk$-space) are attainable by tuning two wavenumbers; the stability of such codimension-two manifolds relies on crystallographic point-group symmetries.
 On the other hand, Weyl points in 3D $\bk$-space have codimension three and do not require any point-group symmetry for their stability.
-Just like Weyl points, the point degeneracy of $\A$ is associated with a nontrivial Chern number\cite{TKNN} (defined as an integral of the Berry curvature\cite{berry_quantal_1984} over a Gaussian surface surrounding the point).\footnote{The curvature is defined with respect to a line bundle formed from the nondegenerate eigenvector of $\cala$.}
+Just like Weyl points, the point degeneracy of $\A$ is associated with a nontrivial Chern number\cite{TKNN} (defined as an integral of the Berry curvature\cite{berry_quantal_1984} over a Gaussian surface surrounding the point)\footnote{The curvature is defined with respect to a line bundle formed from the nondegenerate eigenvector of $\cala$.} .
 
@@
 On the other hand, $\A{=}{-}I$ occurs if and only if $\br{=}(0,{\pm} 1,0)$.
-These two points are mapped to a path-connected line node confined to the $\alpha{=}0$ and $\beta{=}0$ planes [cf.\ \fig{fig:dgn}(b)]; the difference in codimension originates from the $\mathfrak{c}_{\infty}$ symmetry within these two planes [cf.\ \s{sec:ctsrot}], which was not accounted for in the $\mathfrak{c}_2$-symmetric analysis of \q{proprashba}.
+These two points are mapped to a path-connected line node confined to the $\alpha{=}0$ and $\beta{=}0$ planes [cf.\ \fig{fig:dgn}(b)]; the difference in codimension originates from the $\mathfrak{c}_{\infty}$ symmetry within these two planes (cf.\ \s{sec:ctsrot}), which was not accounted for in the $\mathfrak{c}_2$-symmetric analysis of \q{proprashba}.
 
@@
 
-In the adiabatic limit of two nearly-degenerate orbits, we have found [in \s{sec:introducecodimension}] that the codimension for $\cala{=}{\pm} I$ is unity.
+In the adiabatic limit of two nearly-degenerate orbits, we have found (in \s{sec:introducecodimension}) that the codimension for $\cala{=}{\pm} I$ is unity.
 Here we investigate how this result changes as adiabaticity is relaxed by Landau-Zener tunneling -- that respects a discrete $N$-fold rotational symmetry ($\mathfrak{c}_N$).
@@
 Deviating from the adiabatic limit, we deduce from \q{c2breakdowndgncondition} that $\A{=}I$ remains attainable by varying $B$, but $\A{=}{-}I$ is unattainable because $\tau{<}1$; this is consistent with the codimension analysis of \q{proprashba}.
-The conditions $\A{=}I$ and $\rho{>}0$ are interpreted as the destructive interference of  two, single-tunneling Feynman path (cf.
+The conditions $\A{=}I$ and $\rho{>}0$ are interpreted as the destructive interference of  two, single-tunneling Feynman path [cf.
 Fig.
-\ref{fig:Cn-breakdown}(d)).
-Concurrently, there is constructive interference of the Feynman loops involving zero and two tunneling events (cf.
+\ref{fig:Cn-breakdown}(d)].
+Concurrently, there is constructive interference of the Feynman loops involving zero and two tunneling events [cf.
 Fig.
-\ref{fig:Cn-breakdown}(e)).
+\ref{fig:Cn-breakdown}(e)].
 The differential phase between outer and inner zero-tunneling (band-conserving) loops is simply 0 (mod $2\pi$), hence Landau levels are quasidegenerate.
 Such quasidegeneracies recur as $\Delta$ advances by $2\pi$, corresponding to a periodicity in $l^2$ of $4\pi/\delta S$ (or two flux quanta).
-This periodicity is not affected by the additional phase $2\bar{\phi}$ in $\Delta$, because $\bar{\phi}$ varies on the scale  $2\pi/S_{\sma{\square}}$,\footnote{For $\bar{\varphi}(\bar{\mu})$ to vary $\sim 1$, the Landau-Zener parameter $\bar{\mu}$ must vary by $\sim 1$ (cf.\  Fig.\ 10 in Ref.
+This periodicity is not affected by the additional phase $2\bar{\phi}$ in $\Delta$, because $\bar{\phi}$ varies on the scale  $2\pi/S_{\sma{\square}}$\footnote{For $\bar{\varphi}(\bar{\mu})$ to vary $\sim 1$, the Landau-Zener parameter $\bar{\mu}$ must vary by $\sim 1$ (cf.\  Fig.\ 10 in Ref.
 \onlinecite{100p}).
-Moreover, $2\pi\barmu{:}{=} (2\pi/8) l^2S_{\sma{\square}}$\cite{AALG}} which is much larger than $4\pi/\delta S$.
+Moreover, $2\pi\barmu{:}{=} (2\pi/8) l^2S_{\sma{\square}}$\cite{AALG}}, which is much larger than $4\pi/\delta S$.
 To recapitulate, half the Landau-level quasidegeneracies (over the $B$ axis) are destabilized  by tunneling; the robustness of the other half relies on $\mathfrak{c}_2$ symmetry.
@@
 \hline 
-action on orbit  & action on $\boldsymbol{k}$  & $u$ & $s$  & class \blue{label} & $g$  & codimension\tabularnewline
+action on orbit & action on $\boldsymbol{k}$  & $u$ & $s$  & class label & $g$  & codimension\tabularnewline
 \hline 
-\multirow{5}{*}{$|g\circ\mathfrak{o}_{0}|=|\mathfrak{o}_{0}|$} & \multirow{2}{*}{$\forall\boldsymbol{k}\in\mathfrak{o}_{0},g\circ\boldsymbol{k}=\boldsymbol{k}$} & \multirow{2}{*}{0} & \multirow{2}{*}{0} & \multirow{2}{*}{\blue{I-1}} & $\breve{g}\propto I$  & 3\tabularnewline
+\multirow{5}{*}{$|g\circ\mathfrak{o}_{0}|=|\mathfrak{o}_{0}|$} & \multirow{2}{*}{$\forall\boldsymbol{k}\in\mathfrak{o}_{0},g\circ\boldsymbol{k}=\boldsymbol{k}$} & \multirow{2}{*}{0} & \multirow{2}{*}{0} & \multirow{2}{*}{I-1} & $\breve{g}\propto I$  & 3\tabularnewline
 \cline{6-7} 
@@
 \end{tabular}
-\caption{\blue{Symmetry-constrained codimensions for nearly-degenerate orbits, which fall into five symmetry classes (as numbered in the first column).
-This table is also applicable to exactly-degenerate orbits, which fall into ten symmetry classes -- five here, and five in  \tab{table:codimension-exactlydegen}.} The second and third columns define how the symmetry acts on the cyclotron orbit.
+\caption{Symmetry-constrained codimensions for nearly-degenerate orbits, which fall into five symmetry classes (as numbered in the first column).
+This table is also applicable to exactly-degenerate orbits, which fall into ten symmetry classes -- five here, and five in  \tab{table:codimension-exactlydegen}.
+The second and third columns define how the symmetry acts on the cyclotron orbit.
 The next two columns  inform us if the mapping $\bk{\rightarrow}g{\circ}\bk$ [cf.\ \q{gmapk}]  preserves ($u{=}0$) or inverts ($u{=}1$) the orientation of the orbit, and if $g$ preserves ($s{=}0$) or inverts ($s{=}1$) the arrow of time.
@@
 \hline 
-action on orbit  & action on $\boldsymbol{k}$  & $u$ & $s$  & class \blue{label} & $g$  & codimension\tabularnewline
+action on orbit  & action on $\boldsymbol{k}$  & $u$ & $s$  & class label & $g$  & codimension\tabularnewline
 \hline 
@@
 \end{tabular}
-\caption{\blue{Symmetry-constrained codimensions for five of ten symmetry classes of exactly-degenerate orbits; the other five are described in \tab{table:codimension-nearlydegen}.
+\caption{Symmetry-constrained codimensions for five of ten symmetry classes of exactly-degenerate orbits; the other five are described in \tab{table:codimension-nearlydegen}.
 We employ the same notations as in the caption of Tab.
-\ref{table:codimension-nearlydegen}.} In class II-4, $\breve g$ is evaluated at $g$-invariant $\bk$ ($g\circ\bk=\bk$).
+\ref{table:codimension-nearlydegen}.
+In class II-4, $\breve g$ is evaluated at $g$-invariant $\bk$ ($g\circ\bk=\bk$).
 For exactly-degenerate orbits in class I-2, II-3 and II-4, the two-by-two matrix propagator $\A$ has unit determinant, assuming that spin-orbit coupling can be turned off continuously without changing the degeneracy of the orbit.\cite{topoferm}\label{table:codimension-exactlydegen}}
@@
 All the quantities on the right-hand side of Eq.\ (\ref{eq:LK}) are evaluated at the chemical potential.
-(\q{eq:LK} corrects the analogous formula in Ref.\ \onlinecite{topoferm} by a factor of half.)
+[\q{eq:LK} corrects the analogous formula in Ref.\ \onlinecite{topoferm} by a factor of half.]
 
@@
 There are ten possible symmetry classes for exactly-degenerate orbits -- five more than for near-degenerate orbits.
-For each of this ten, we have also determined their symmetry-constrained codimensions in Tab.\ \ref{table:codimension-nearlydegen}- \ref{table:codimension-exactlydegen}.
+For each of this ten, we have also determined their symmetry-constrained codimensions in Tab.\ \ref{table:codimension-nearlydegen}-\ref{table:codimension-exactlydegen}.
 We remark on one further distinction from nearly-degenerate orbits --  the magnitude of the field becomes less useful as a tuning parameter, however the field orientation and Landau-level index remain feasible options.
@@
 
-We are grateful to Nicholas Read and Judith H\"oller for clarifying notions related to codimensions of eigenvalue-degeneracies.
-An instructive discussion with Victor Yakovenko helped us relate this work  to his `magic angles'.
-We acknowledge Xi Dai for a useful discussion of the Zeeman interaction in the context of breakdown.
-We also thank Eduardo Fradkin for educating us on the subject of nematic Fermi fluids.
+We are grateful to Nicholas Read and Judith H\"oller for clarifying notions related to codimensions of eigenvalue-degeneracies, and to Xi Dai for an instructive discussion on the Zeeman interaction in the context of breakdown.
+We thank Victor Yakovenko for  educating us on `magic-angle' magnetoresistance oscillations, and  Eduardo Fradkin for his expertise on nematic Fermi fluids.
 We acknowledge support from the Ministry of Science and Technology of China, Grant No.\ 2016YFA0301001 (CW and WD), the National Natural Science Foundation of China, Grants No.\ 11674188 and 11334006 (CW and WD), the Beijing Advanced Innovation Center for Future Chip (CW and WD), the Yale Postdoctoral Prize Fellowship (AA) and NSF DMR Grant No.\ 1603243 (LG).
@@
 This work was supported in part by the Gordon and Betty Moore Foundation EPiQS Initiative through Grant No.
-GBMF4305 at the University of Illinois.
+GBMF4305 at the University of Illinois.\\
 \end{acknowledgments}
 
-\bibliography{paper}
-
 \appendix
 
-\section{Proof of nearly-degenerate quantization rule\label{app:quantizationruleproof}}
-
-In this appendix, we prove the quantization rule introduced in the main text in the framework of effective Hamiltonian.
-This proof is applicable to $D$-fold nearly-degenerate bands, with $D>1$.
-Although less common than $D=2$, $D>2$ is relevant in some materials.
-For example, bands at $k_z=\pi$ plane of $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$-symmetric material with negligible SOC are four fold (nearly-)degenerate.
-
-The proof of the quantization rule is a direct WKB solution of the Schr\"odinger equation.
-During the derivation, it is important to keep the order of magnitude of different quantities in control, which we use big-O notation and little-o nontation to quantify.
-The definitions for big-O notation and little-o notation we adopt are: $f(\boldsymbol{x})\sim\text{O}(\{g_i(\boldsymbol{x}), i\in 1..N\})$ as $\boldsymbol{x}\to\boldsymbol{0}$ if and only if $\exists C>0~\exists \delta>0$ such that for all $\boldsymbol{x}$ with $||\boldsymbol{x}||_\infty<\delta$, $|f(\boldsymbol{x})|<C\text{max}\{|g_i(\boldsymbol{x})|, i\in 1..N\}$; $f(\boldsymbol{x})\sim\text{o}(\{g_i(\boldsymbol{x}), i\in 1..N\})$ as $\boldsymbol{x}\to\boldsymbol{0}$ if and only if $\forall \epsilon>0~\exists \delta>0$ such that for all $\boldsymbol{x}$ with $||\boldsymbol{x}||_\infty<\delta$, $|f(\boldsymbol{x})|<\epsilon\text{max}\{|g_i(\boldsymbol{x})|, i\in 1..N\}$.
-Here, $||\boldsymbol{x}||_\infty=\text{max}\{|x_i|\}$ is uniform norm of the vector $\boldsymbol{x}$.
+The appendices are organized as follows: in App.
+\ref{app:quantizationruleproof}, we prove the quantization rule of \qq{eq:rule}{berryconn}.
+The Landau levels derived from this quantization rule are then compared with numerically-exact Landau levels in App.
+\ref{app:approximatevsexact}, for the Rashba-Dresselhaus 2DEG in a magnetic field.
+In App.
+\ref{sec:proofLLquasideg}, the existence of Landau-level quasidegeneracies is proven.
+In App.
+\ref{app:codimension}, we derive the symmetry-constrained codimensions of Landau-level quasidegeneracies, in all symmetry classes of cyclotron orbits.
+
+%utilizing a mathematical result proved in App. \ref{app:makinggoffdiagonal}.
+
+%The numerical diagonalization method is reviewed in App. \ref{sec:numerical}.
+
+\section{Proof of quantization rule for the Landau levels of nearly-degenerate bands \label{app:quantizationruleproof}}
+
+In this appendix, we derive the quantization rule for the Landau levels of nearly-degenerate energy bands.
+We assume the energy bands are nearly $D$-fold degenerate at generic wavevectors.
+The Landau quantization of such bands results in the quantization rule of  \qq{eq:rule}{berryconn} for $D=2$; these equations will be generalized (below) for $D>2$.
+Although less common than $D=2$, $D>2$ is relevant in  materials with nonsymmorphic symmetries.
+For example in screw- and time-reversal-invariant solids with weak spin-orbit coupling, bands in a high-symmetry plane (e.g., $k_z=\pi$ for the screw $\mathfrak{c}_{2z,\boldsymbol{c}/2}$)  are nearly four-fold degenerate.
+
+The quantization rule is derived from the WKB solution of an effective Schr\"odinger equation.
+During the derivation, it is important to control the error in our approximation scheme, which we use big-O and little-o notations to quantify.
+They are defined as:
+\begin{itemize}
+    \item 
+    \begin{equation}
+        f(\boldsymbol{x})\sim\text{O}(\{g_i(\boldsymbol{x}), i\in 1..N\})
+    \end{equation}
+    as $\boldsymbol{x}\to\boldsymbol{0}$ if and only if $\exists C>0$ and $\exists \delta>0$ such that for all $\boldsymbol{x}$ with $||\boldsymbol{x}||_\infty<\delta$,
+    \begin{equation}
+        |f(\boldsymbol{x})|<C\text{max}\{|g_i(\boldsymbol{x})|, i\in 1..N\};
+    \end{equation}
+    \item 
+    \begin{equation}
+        f(\boldsymbol{x})\sim\text{o}(\{g_i(\boldsymbol{x}), i\in 1..N\})
+    \end{equation}
+    as $\boldsymbol{x}\to\boldsymbol{0}$ if and only if $\forall \epsilon>0,~\exists \delta>0$ such that for all $\boldsymbol{x}$ with $||\boldsymbol{x}||_\infty<\delta$,
+    \begin{equation}
+        |f(\boldsymbol{x})|<\epsilon\text{max}\{|g_i(\boldsymbol{x})|, i\in 1..N\}.
+    \end{equation}
+\end{itemize}
+Here, $||\boldsymbol{x}||_\infty=\text{max}\{|x_i|\}$ is the uniform norm of the vector $\boldsymbol{x}$.
 
 As stated in \s{sec:qtznrules}, our starting point is a decomposition of the Hamiltonian $\hat{H}$ into $\hat{H}_0$ and a perturbation $\delta\hat{H}=\eta\hat{H}_1$, with $\eta$ a dimensionless small parameter.
-The nearly-degeneracy originates from $\eta\hat{H}$ breaking the exactly $D$-fold degenerate bands of $\hat{H_0}$.
+We assume that $\eta\hat{H}$ perturbatively breaks the  $D$-fold energy degeneracy (at generic wavevectors) of $\hat{H_0}$.
 For 2-fold nearly-degeneracy, $\eta$ can be chosen as $\delta S/S$ in the main text.
 
-To express the Schr\"odinger equation in a tractable form, the effective Hamiltonian formalism is needed\cite{rotheffham,100p}.
-To the leading order in $B$ and $\eta$, the effective Hamiltonian $\mathfrak{H}(\boldsymbol{K})$ is the Peierls-Onsager Hamiltonian: $\mathfrak{H}_{0}(\boldsymbol{K}):=\epsilon(\boldsymbol{K})$, with $\epsilon(\boldsymbol{k})$ zero-field energy dispersion of $\hat{H}_0(\bk)$ and $\boldsymbol{K}=\boldsymbol{k}+(e/\hbar)\boldsymbol{A}(i\nabla_{\boldsymbol{k}})$.
-The effective Hamiltonian is expressed in the basis of a set of modified Bloch functions $\psi_{\boldsymbol{k}}$ \cite{rotheffham}.
-Expanding the wave function $\phi$ in this basis ($\phi=\sum_{\boldsymbol{k}}f_{\boldsymbol{k}}\psi_{\boldsymbol{k}}$), The Schr\"odinger equation becomes
-\begin{equation}
-(\mathfrak{H}(\boldsymbol{K})-E)f_{\boldsymbol{k}}=0.\label{eq:schrodinger}
-\end{equation}
-The subleading term $\mathfrak{H}_{1}(\boldsymbol{K})$ of the effective Hamiltonian comes from two parts: the first part is obtained by Peierls substitution of the generalized Zeeman interaction in the absence of $\delta \hat{H}$, which includes the Zeeman coupling to orbital and spin moments, as well as a geometric Berry contribution.
-The other part is Peierls substited $\epsilon_1(\bK)$, with $\epsilon(\bk)$ the projection of $\hat{H}_1$ to the $D$-fold degenerate bands of $\hat{H}_0$.
-In total,
-\begin{equation}
-\effH_1(\bk) = \eta\epsilon_1(\bk)+B(M_{z}-g_s\mu_{B}s_{z}/\hbar+e\epsilon_{\alpha\beta}\mathfrak{X}_{\beta}v_{\alpha}). \label{effham1}
+For an approximate, semiclassical solution to the time-independent Schr\"odinger equation, we employ the effective Hamiltonian formalism \cite{rotheffham,100p}.
+The effective Hamiltonian is expressed in a basis of a field-augmented Bloch functions $\{\tilde{\psi}_{n\boldsymbol{k}}\}_{n=1}^D$,\cite{rotheffham} which are modifications of Bloch functions that span the  energy-degenerate subspace of $\hat{H}_0$.
+Expanding an energy eigenfunction $\phi$ in this basis ($\phi=\sum_{n=1}^D\sum_{\boldsymbol{k}}f_{n\boldsymbol{k}}\tilde{\psi}_{n\boldsymbol{k}}$), the Schr\"odinger equation effectively becomes
+\begin{equation}
+(\mathfrak{H}(\boldsymbol{K})-E)\boldsymbol{f}_{\boldsymbol{k}}=0,\label{eq:schrodinger}
+\end{equation}
+with $\mathfrak{H}(\boldsymbol{K})$ (the effective Hamiltonian) a $D$-by-$D$ matrix differential operator.
+
+In general, the effective Hamiltonian has an asymptotic expansion in powers of the  parameters $a/l^2 (\propto B)$ and $\eta$, which are both assumed small with finite ratio $l^2\eta/a^2$; $a$ here is a crystalline lattice period, which we henceforth set to one for convenience.
+To the leading order in $l^{-2}$ and $\eta$, the effective Hamiltonian  is the Peierls-Onsager Hamiltonian: $\mathfrak{H}_{0}(\boldsymbol{K}):=\epsilon(\boldsymbol{K})$.
+This is just the Weyl-symmetric Peierls substitution $\bk \rightarrow \bK$ for the dispersion ($\epsilon(\boldsymbol{k})$) of the $D$-fold degenerate band of $\hat{H}_0(\bk)$, and $\boldsymbol{K}=\boldsymbol{k}+(e/\hbar)\boldsymbol{A}(i\nabla_{\boldsymbol{k}})$ here are the kinematic quasimomentum operators.
+
+The subleading term $\mathfrak{H}_{1}(\boldsymbol{K})$ (denoted $\H$ in the main text) of the effective Hamiltonian has two additive components: the first is obtained by Peierls substitution of the generalized Zeeman interaction (in the absence of $\delta \hat{H}$), which includes the Zeeman coupling to orbital and spin moments, as well as a geometric Berry contribution.
+The second component is the Peierls-substitution of   $\delta \epsilon(\bk)$, which is the projection of $\hat{H}_1$ to the $D$-fold degenerate bands of $\hat{H}_0$.
+In combination,
+\begin{equation}
+\effH_1(\bk) = \eta\delta \epsilon(\bk)+B(M_{z}-g_s\mu_{B}s_{z}/\hbar+e\epsilon_{\alpha\beta}\mathfrak{X}_{\beta}v_{\alpha}). \label{effham1}
 \end{equation}
@@
 (\ref{effham1}) should be evaluated with wavefunctions in the degenerate subspace of $\hat{H}_0$.
-.
-In the main text, $\effH_1(\bk)$ is written as $\H(\bk)$.
 The above equation presupposes that the  magnetic field $B$ lies in the $-z$ direction.
@@
 To the leading order (i.e., with $\mathfrak{H}_0(\bK)$ only), solutions of Eq.
-(\ref{eq:schrodinger}) are Zil'berman functions
+(\ref{eq:schrodinger}) are Zil'berman functions\cite{zilberman} labelled by the wavevector $k_x^0$:
 \begin{equation}
@@
 and $c_a^\nu$ is $\bk$ independent.
-$\A^\nu$ is a $k_y$ dependent square matrix with the assumption $\A_{ab}^\nu$ is of order $\order(1, \eta l^2)$, \red{where $\order(a, b)$ is a shorthand for $\order(\{a, b\})$}.
+$\A^\nu$ is a $k_y$ dependent square matrix with the assumption $\A_{ab}^\nu$ is of order $\order(1, \eta l^2):=\order(\{1,\eta l^2\})$.
 Following section V A 2 of Ref.
@@
 \begin{equation}
-[\effH_{1}(\bK)]_{ab}\A_{bc}^\nu g_{c}^\nu=[\effH_{1}]_{ab}\A_{bc}^\nu g_{c}^\nu+\text{o}(l^{-2}, \eta),\label{effH1onA}
-\end{equation}
-where $\text{o}$ is little-o notation.
+[\effH_{1}(\bK)]_{ab}\A_{bc}^\nu g_{c}^\nu=[\effH_{1}]_{ab}\A_{bc}^\nu g_{c}^\nu+\text{o}(l^{-2}, \eta).\label{effH1onA}
+\end{equation}
 One term omitted in Eq.
@@
 \begin{equation}
-\hbar\partial_{y}\A_{ac}^\nu=il^{2}[v_{x}^\nu]^{-1}[\effH_{1}]_{ab}\A_{bc}^\nu+\red{\text{o}(1, \eta l^2)}.
-\end{equation}
-Therefore,
-\begin{equation}
-\A^\nu=\overline{\exp}[il^{2}\int\frac{\effH_{1}}{\hbar v_{x}^\nu}dk_{y}]+\red{\text{o}(1, \eta l^2)},
-\end{equation}
-Eq.
-({\ref{eq:prop}}) can be obtained by solving boundary conditions at turning points.
-Eq.
-({\ref{eq:prop}}) is gauge invariant under a gauge transformation since the cyclotron orbit is closed [See Eq.
+\hbar\partial_{y}\A_{ac}^\nu=il^{2}[v_{x}^\nu]^{-1}[\effH_{1}]_{ab}\A_{bc}^\nu+{\text{o}(1, \eta l^2)}.
+\end{equation}
+The solution to this differential equation is a path-ordered exponential:
+\begin{equation}
+\A^\nu=\overline{\exp}[il^{2}\int\frac{\effH_{1}}{\hbar v_{x}^\nu}dk_{y}]+{\text{o}(1, \eta l^2)},
+\end{equation}
+
+%Eq. ({\ref{eq:prop}}) can be obtained by solving boundary conditions at turning points.
+
+By imposing a hard-wall boundary condition at classical turning points, and requiring that the wavefunction in Eq.
+(\ref{wkb-wf}) be single-valued,\cite{100p} we obtain the quantization rule  stated in \qq{eq:rule}{berryconn}; in \q{eq:rule}, $a$ now runs from $1$ to $D$.
+Due to the geometric Berry term, Eq.
+({\ref{eq:prop}}) transforms covariantly under basis transformations within the degenerate subspace of $\hat{H}_0$ [See Eq.
 (133) of Ref.
-\onlinecite{100p}].
-
-\red{The quantization rule can be obtained by requiring the wavefunction in Eq.
-(\ref{wkb-wf}) is single valued\cite{100p}, which directly leads the the quantization rule stated in \qq{eq:rule}{berryconn}.
-Since $\lambda$ is the eigenphase of $\A$ over a full cyclotron orbit, it bears the same uncertainty $\text{o}(1, \eta l^2)$.
-For example, for the Rashba model, the quantization rule misses a term proportional to $\eta^2 l^2$ [$l^2\delta S^2/S$ in Eq.
+\onlinecite{100p}], and as a consequence $\{\lambda_a\}_{a=1}^D$ is well-defined modulo $2\pi$.
+
+Since $\lambda_a$ is the eigenphase of $\A$ over a full cyclotron orbit, it carries the same uncertainty $\text{o}(1, \eta l^2)$.
+For example, in the Rashba model with an out-of-plane field, a comparison with the exact solution shows that our quantization rule misses terms of the order $\eta^2 l^2$; precisely, the missed terms are each proportional to  $l^2\delta S^2/S$ in Eq.
 (\ref{eq:Rashba-exact})].
-The quantization rule thus requires an extra condition $l^2\delta S^2/S\ll 1$, which is an upper bound for Landau level index: $n\ll(\delta S/S)^2$.}
-
-Besides the effective Hamiltonian approach described above, semiclassical wave packet theory has been developed in coupled bands\cite{culcer_coherent_2005}.
-It is possible that quantization rule expressed in \qq{eq:rule}{berryconn} can be derived by a `requantization' of the wave packet theory\cite{xiao_berry_2010}.
-
-\section{Comparison of numerically-exact Landau levels with our approximation scheme}\la{app:approximatevsexact}
-
-\red{In this appendix, we compare the exact Landau levels obtained from numerical diagonalization (with standard techniques reviewed in App.
+These missed terms are small under our assumption of small $\eta$ and small $l^{-2}$ with finite ratio $l^2\eta$.
+We remark that $l^2\delta S^2/S\ll 1$, along with the standard semiclassical condition, sets a double-sided constraint on the magnetic field: $S^{-1} \ll l^2 \ll S/(\delta S)^2$.
+
+%The quantization rule thus requires an extra condition $l^2\delta S^2/S\ll 1$, which is an upper bound for Landau level index: $n\ll(S/\delta S)^2$.
+
+Besides the effective-Hamiltonian approach described here, semiclassical wave packet theory has been developed for multiple coupled bands\cite{culcer_coherent_2005}.
+It is possible that quantization rule [of \qq{eq:rule}{berryconn}] can be alternatively derived by a `requantization' of the wave packet theory\cite{xiao_berry_2010}; we leave this for future investigation.
+
+\section{Comparison of numerically-exact Landau levels with our approximation scheme}\label{app:approximatevsexact}
+
+In this appendix, we compare the exact Landau levels obtained from numerical diagonalization (with standard techniques reviewed in App.
 \ref{sec:numerical}) to the approximate Landau levels obtained from our quantization rule, as summarized in \qq{eq:rule}{berryconn}.
@@
 In both cases, a closed-form analytic expression for the Landau-level spectrum is not known.
-We quantify the error of quantization rule by calculating $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for different parameter choices in both models.
-Semiclassical condition ($l^2 S\gg 1$) and near degeneracy condition ($\delta S/S\ll 1$) are satisfied within the parameter range in Fig.
+We quantify the error of our quantization rule by $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for different parameter choices in both models.
+The semiclassical ($l^2 S\gg 1$) and near-degeneracy conditions ($\delta S/S\ll 1$) are satisfied within the parameter range in Fig.
 \ref{fig:error}.
-Just as for the Rashba model [cf.
-Eq.(\ref{eq:Rashba-exact})], the accuracy of our rule improves with decreasing parameter $l^2\delta S(\alpha,\beta)^2/S$, suggesting this term being the one of the leading error terms of the quantization rule [cf.
+Just as for the Rashba 2DEG in an out-of-plane field [cf.
+Eq.(\ref{eq:Rashba-exact})], the accuracy of our rule improves with decreasing parameter $l^2\delta S^2/S$,  suggesting that this parameter gives the dominant contribution to the error of the quantization rule [cf.
 the discussion in App.
-\ref{app:quantizationruleproof}].}
+\ref{app:quantizationruleproof}].
 
@@
 \includegraphics[width=1.0\columnwidth]{error.png}
-\caption{\red{Comparison of quantization rule and exact diagonalization.
+\caption{{Comparison of quantization rule and exact diagonalization.
 (a) For various spin-orbit parameters $(\alpha,\beta)$ of the Rashba-Dresselhaus model, we plot in left panel $\text{error}:=|\epsilon_\text{rule}-\epsilon_\text{exact}|/\var_c$ for a single Landau level that lies closest to energy $E=0.4eV$, where $\epsilon_\text{rule}$ is determined by Eq.
-(\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RD}(\bK)$ with Zeeman interaction for spin.
-We also plot in right panel $l^2\delta S^2/S$, which has a strong positive relation with error.
+(\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RD}(\bK)$ plus the Zeeman coupling to spin.
+We also plot in right panel $l^2\delta S^2/S$, which has a strong positive correlation with the error.
 (b) For various parametrizations ($\alpha$, $Z_\parallel$) of $H_{RZ}$, we plot in the left panel the error for a single Landau level that is closest to $\epsilon_0$ [as defined in Eq.
 (\ref{whereisdiracpoint})] $\epsilon_\text{rule}$ is determined by Eq.
-(\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RZ}(\bK)$ with Zeeman interaction for spin.
+(\ref{eq:rule}) and $\epsilon_{\text{exact}}$ is obtained by numerical diagonalization of the Peierls-Onsager Hamiltonian $H_{RZ}(\bK)$ plus the Zeeman coupling to spin.
 The corresponding $l^2 \delta S^2/S$ is plotted in the right panel.
@@
 
+\subsection{Method of numerical diagonalization}\label{sec:numerical}
+
+Numerical diagonalization relies on  $[K_x,K_y]=il^{-2}$ being algebraically similar  to the commutation relation  of position and momentum (in quantum mechanics with quantum parameter $\hbar$).
+Analogously, $K_x$ and $K_y$ can expressed with creation and annihilation operators
+\begin{align}
+\begin{split}
+K_x=&l^{-1}(a+a^\dagger)/\sqrt{2},\\
+K_y=&-il^{-1}(a-a^\dagger)/\sqrt{2}.
+\end{split}
+\end{align}
+Performing the above substitution for  $H_R(\bK)$ (with the Zeeman coupling to spin),
+\begin{align}
+\begin{split}
+H_{R}(\boldsymbol{K})=&\frac{\hbar^2}{ml^2}(a^{\dagger}a+\frac{1}{2})
+\\&+\sqrt{2}\hbar\alpha l^{-1}\left(\begin{array}{cc}
+0 & -ia^{\dagger}\\
+ia & 0
+\end{array}\right)
+-\frac{g_{s\perp}\hbar^2\sigma^z}{4m_0l^2}.
+\end{split}\label{eq:Rashba-ho}
+\end{align}
+Eq.
+(\ref{eq:Rashba-ho}) have solutions in the form of $(c_1|n+1\rangle,c_2|n\rangle)$ where $c_1$ and $c_2$ are some constants and $|n\rangle$ is an eigenstate of $a^\dagger a$ with eigenvalue $n$.
+Any Hamiltonian $H(\bK)$ can be numerically diagonalized with a  cutoff for the index $n$, which we assume to be large.
+
 %\subsection{Rashba 2DEG in a tilted field}\la{app:rashba2DEGtilted_comparenumerics}
@@
 
-\section{Existence of Landau-level quasidegeneracy}\label{sec:proofLLquasideg}
+\section{Existence of Landau-level quasidegeneracy\label{sec:proofLLquasideg}}
 
@@
 Due to the latter two inequalities, we shall refer to $\lambda_{a}$ as \textit{slowly-varying} (with respect to $E$ and $B$), in comparison with the rapidly-varying $l^2S$.
-To appreciate the difference in scales, consider that for $\lambda_a$ to change by $2\pi$ due to a variation $l^2$ (at fixed energy), we estimate [in the weak-field regime; cf.\ \q{phaseindependentorbit}] that $l^2$ must change on the scale of $2\pi/\delta S$; this scale is much greater than the period of quantum oscillations ($T_{l^2}{:}{=}2\pi/S$), by our assumption of near degeneracy.
-Analogously, for $\lambda_a$ to vary by $2\pi$ due to a variation of $E$ (at fixed field) by $\delta E$, we estimate [from \q{phaseindependentorbit}] that $\delta E {\sim} 2\pi/l^2 (\partial \delta S/\partial E)$, which is generically much larger than the cyclotron energy $\epsilon_c{=}2\pi/l^2 (\partial  S/\partial E)$.
-In the strong-field regime (where $\delta \var$ may be neglected from \q{eq:H1}), $\lambda_a$ is independent of $B$ (to the accuracy of our theory), and depends on $E$ solely through the slow variation of $\calm$.
+
+To appreciate the difference in scales, consider that for $\lambda_a$ to change by $2\pi$ due to a variation $l^2$ (at fixed energy), we estimate from \q{phaseindependentorbit} that $l^2$ must change on the scale of $2\pi/\delta S$; this scale is much greater than the period of quantum oscillations ($T_{l^2}{:}{=}2\pi/S$), by our assumption of near degeneracy.
+The above estimate was carried out in the weak-hybridization regime, where the Zeeman interaction is much weaker than the spin-orbit-splitting of energy bands.
+In the strong-hybridization regime, $\lambda$ is independent of $l^2$ to the accuracy of our theory.
+
+Analogously, for $\lambda_a$ to vary by $2\pi$ due to a variation of $E\rightarrow E+\delta E$ (at fixed field), we estimate in the weak-hybridization regime [cf.\ \q{phaseindependentorbit}] that $\delta E {\sim} 2\pi/l^2 (\partial \delta S/\partial E)$, which is generically much larger than the cyclotron energy $\epsilon_c{=}2\pi/l^2 (\partial  S/\partial E)$.
+In the strong-hybridization regime, $\lambda_a$ depends on $E$ solely through the slow variation of $\calm$.
 In the absence of symmetry, we estimate
@@
 where $m_0$ is the free-electron mass, and $m{=}\hbar^2(\partial S/\partial E)/2\pi$ the effective mass.
-The first argument of $\order$ originates from the energy dependence of the effective $g$-factor; the second argument accounts for possible non-analyticities in the area of $\frako_0$, which may originate from saddle- or II-Dirac points in the zeroth-order band Hamiltonian.
-
-Armed with the inequalities above, we now demonstrate that, if a degeneracy of $\cala$ [$e^{i\lambda_+}{=}e^{i\lambda_-}$] occurs at $(\bar{E},\bar{B})$, there exists two Landau levels in close proximity to $(\bar{E},\bar{B})$ which satisfy the nearly-degeneracy conditions defined in \qq{llquasideg}{llquasidegB}.
+The first argument of $\order$ originates from the energy dependence of the effective $g$-factor; the second argument accounts for possible non-analyticities in the area of $\frako_0$, which may originate from saddle- or II-Dirac points in the zeroth-order Hamiltonian $\hat{H}_0$.
+
+Armed with the above inequalities, we now demonstrate that, if a degeneracy of $\cala$ [$e^{i\lambda_+}{=}e^{i\lambda_-}$] occurs at $(\bar{E},\bar{B})$, there exists two Landau levels in close proximity to $(\bar{E},\bar{B})$ which satisfy the nearly-degeneracy conditions defined in \qq{llquasideg}{llquasidegB}.
 
@@
 We estimate
-\e{\f{E_+-E_-}{\var_c} \approx &\; \f{r}{\var_c}\left(\f1{\calq'_+}-\f1{\calq'_-}\right)\approx  \f{r}{2\pi}\var_c \left( \lambda'_- -\lambda'_+\right), \label{estimate}}
-which is a justification for the order-of-magnitude estimate in \q{llquasideg}. Combining  \q{dlambdadE} with \q{estimate}, we deduce the inequality in \q{llquasideg}.  
+\e{\f{E_+-E_-}{\var_c} \approx &\; \f{r}{\var_c}\left(\f1{\calq'_+}-\f1{\calq'_-}\right)\approx  \f{r}{2\pi}\var_c \left( \lambda'_- -\lambda'_+\right). \label{estimate}}
+Combining \q{estimate} with the above estimates for $\lambda'_{\pm}$, we derive \q{llquasideg}.  
 %From \s{sec:qtznrules}, we know that for sufficiently weak field ($\var_c\ll \Delta$), $\lambda_{\pm}'\approx \pm l^2\delta S'/2$.
@@
 It is most convenient at this point to change variables from $B\rightarrow l^2$ (the square of the magnetic length).
-Let us  define   $l^2_{\pm}$ such that $\calq_{\pm}(\bar{E},l^2_{\pm}){=}\calq_{\pm}(\bar{E},l^2_{\pm}){+}r{\in} \Z$.
+Let us  define   $l^2_{\pm}$ such that $\calq_{\pm}(\bar{E},l^2_{\pm}){=}\calq_{\pm}(\bar{E},\bar{l}^2){+}r{\in} \Z$.
 We denote  $\dot{O}:=\partial O/\partial(l^2)$ evaluated at $(\bar{E},\bar{B})$, and estimate
-\e{\f{l^2_+-l^2_-}{T_{l^2}} \approx  \f{r }{2\pi}T_{l^2} \left( \dot{\lambda}_- -\dot{\lambda}_+\right)=\order\left(\f{\delta S}{S}\bigg|_{\bar{E}}\right). \label{estimateB}}
-The order-of-magnitude estimate is obtained in the limit $l^2\delta S \gg 1$, where $\lambda_{\pm}\approx \pm l^2\delta S/2$ [cf.\ \q{phaseindependentorbit}].
+\e{\f{l^2_+-l^2_-}{T_{l^2}} \approx  \f{r }{2\pi}T_{l^2} \left( \dot{\lambda}_- -\dot{\lambda}_+\right). \label{estimateB}}
+Combining \q{estimateB} with the above estimates for $\dot{\lambda}_{\pm}$, we derive \q{llquasidegB}.
+
+%The order-of-magnitude estimate is obtained in the limit $l^2\delta S \gg 1$, where $\lambda_{\pm}\approx \pm l^2\delta S/2$ [cf.\ \q{phaseindependentorbit}].
 In the opposite limit $l^2\delta S \ll 1$, $\lambda_{\pm}$ is independent of $B$ within the accuracy of our semiclassical theory.
@@
 Most of the symmetry constraints on $\A$ are reproduced from Ref.
-[100p] except for class 3 and 4, where a special gauge is chosen.
+\onlinecite{100p} except for class II-1 and II-3, where a special gauge is chosen.
 $\infty$ in the codimension column denotes that eigenvalues of $\A$ cannot be degenerate; $\times$ denotes an entry where we cannot self-consistently impose the symmetry constraint and the conditions on det$\A$ and $\breve{g}$ for a two-by-two unitary $\A$.
@@
 
-In this appendix, we expose mathematical details of symmetry analysis of the nearly-degenerate propagator $\A$ and derive symmetry constrained codimension of degeneracy manifold.
-We restrict our analysis to two-by-two $\A$.
-
-Sewing matrix is necessary to express the constraints on the propagator $\A$.
-For a symmetry operator $\hat{g}$ acting on wave functions as $\hat{g}|\psi(\br)\rangle=|\psi(\check{g}^{-1}\br)\rangle$, the sewing matrix $\breve{g}$ is defined as
-\e{
-   \breve{g}_{nm} = \langle u_{n,g\circ\bk}|\hat{g}(\bk)|u_{m,\bk} \rangle K^{s(g)}.
-}
-Here, $\hat{g}(\bk)=e^{-i\bk\cdot\hat{\br}}\hat{g}e^{i\bk\cdot\hat{\br}}$; $n=1,2$ and $m=1,2$ runs over the degenerate subspace of $\hat{H}_0$.
-By a basis transformation in the degenerate subspace as
+In this appendix, we perform a symmetry analysis of the two-by-two matrix  propagator $\A$  [defined in \qq{eq:prop}{berryconn}], and derive the symmetry-constrained codimensions of the eigenvalue-degeneracies of $\A$.
+
+For a symmetry $g$ which acts on spacetime as $\br \rightarrow \check{g} \br$ and $t\rightarrow (-1)^{s(g)}t$, 
+we define $\hat{g}$ as the corresponding operator  on wave functions: $\hat{g} \psi(\br,s)=\sum_{s'}\psi(\check{g}^{-1} \br,s')[D_g]_{s's}$, with $D_g$ the spinor representation of $g$.
+The sewing matrix $\breve{g}$ is defined as
+\e{
+   \breve{g}(\bk)_{nm} :\eq \langle u_{n,g\circ\bk}|\hat{g}(\bk)|u_{m,\bk} \rangle K^{s(g)}, \lin
+   \hat{g}(\bk):\eq e^{-i\bk\cdot\hat{\br}}\hat{g}e^{i\bk\cdot\hat{\br}}.
+}
+Here, $n=1,2$ and $m=1,2$ runs over the degenerate subspace of $\hat{H}_0$; $K^1:=K$ which implements complex conjugation, while $K^0$ is the identity operation.
+By a basis transformation in the degenerate subspace:
 \e{
@@
 }
-Diagonalized representation matrix of unitary $\hat{g}$ introduced in the main text is sewing matrix in a special gauge, where $\hat{g}(\bk)$ maps $|u_n\rangle$ to itself up to a phase.
-This phase is called eigenvalue of the symmetry.
-We define order $N$ of $g$ as the smallest positive integer fulfilling $g^N$ is identity, $2\pi$ rotation, lattice translation or combination of them.
-
-The codimension calculation can be drastically simplified if a good gauge is chosen. Generally, we have the following rules for two-by-two sewing matrix:
+This shall be referred to as a gauge transformation.
+Any unitary $\hat{g}$ can be diagonalized by a gauge transformation, such that  $\hat{g}(\bk)$ maps $|u_n\rangle$ to itself, up to a phase factor which we identify as the symmetry eigenvalue.
+We define order $N$ of $g$ as the smallest positive integer such that $g^N$ is either the identity, or any multiplicative combination of  a $2\pi$ rotation (which acts nontrivially on half-integer-spin representations) and a lattice translation.
+
+The codimension calculation can be  simplified by choosing a convenient gauge; the codimension is of course gauge-invariant. Generally, we have the following rules for two-by-two sewing matrix:
 \begin{itemize}
@@
 \end{itemize}
-The first two claims are obvious and the last claim can be verified by a direction calculation showing diagonal terms can be eliminated by a gauge transformation no matter what $\breve{g}$ is at the beginning (cf.
-App.
-\ref{app:makinggoffdiagonal}).
+The first two claims are simple to show, and the last claim is verified  in App. \ref{app:makinggoffdiagonal} below.
 
@@
 
-In the main text, we assume the SOC can be turned off continuously without increasing or decreasing degree of degeneracy.
-With this assumption, $\det(A)=1$ for class I-2, II-3, II-4, reducing Tab.
-\ref{table:fullcodimension} to Tab.
-\ref{table:codimension}.
-
-\section{Two-by-two sewing matrix of antiunitary symmetry operator can be made off-diagonal\label{app:makinggoffdiagonal}}
-
-We parametrize $\breve{g}$ as
-\begin{equation}
-\breve{g}=e^{i\theta}\left(\begin{array}{cc}
-\alpha & \beta\\
--\beta^{*} & \alpha^{*}
-\end{array}\right),
-\end{equation}
-and $V$ by
-\begin{equation}
-V=e^{i\phi}\left(\begin{array}{cc}
-a & b\\
--b^{*} & a^{*}
-\end{array}\right),
-\end{equation}
-\begin{widetext}
-then 
-\begin{align}
-\breve{g} & \to V^{\dagger}\breve{g}V^{*}\\
- & =e^{i(\theta-2\phi)}\left(\begin{array}{cc}
-a^{*} & -b\\
-b^{*} & a
-\end{array}\right)\left(\begin{array}{cc}
-\alpha & \beta\\
--\beta^{*} & \alpha^{*}
-\end{array}\right)\left(\begin{array}{cc}
-a^{*} & b^{*}\\
--b & a
-\end{array}\right)\\
- & =e^{i(\theta-2\phi)}\left(\begin{array}{cc}
-a^{*2}\alpha+a^{*}b\beta^{*}-a^{*}b\beta+b^{2}\alpha^{*} & a^{*}b^{*}\alpha+bb^{*}\beta^{*}+aa^{*}\beta-ab\alpha^{*}\\
-\cdots & \cdots
-\end{array}\right).
-\end{align}
-\end{widetext}
-Decomposing real and imaginary parts of the parameters: $a=a_{1}+ia_{2}$, $b=b_{1}+ib_{2}$, $\alpha=\alpha_{1}+i\alpha_{2}$
-and $\beta=\beta_{1}+i\beta_{2}$, the imaginary part
-of $a^{*}b^{*}\alpha+bb^{*}\beta^{*}+aa^{*}\beta-ab\alpha^{*}$ can be removed by $a_2=b_2=0$ and 
-\begin{equation}
-2b_1\sqrt{1-b_1^{2}}\alpha_{2} =(2b_1^{2}-1)\beta_{2}.
-\end{equation}
-This is always possible since $2b\sqrt{1-b^{2}}/(2b^{2}-1)$ can take
-any real value for $b\in[-1,1]$. Therefore, we can safely assume
-$\beta$ is real since a preliminary transformation can remove its
-imaginary part.
-
-The equation of $a^{*2}\alpha+a^{*}b\beta^{*}-a^{*}b\beta+b^{2}\alpha^{*}=0$ then becomes
-\begin{equation}
-(a_{1}^{2}-a_{2}^{2})\alpha_{1}+2a_{1}a_{2}\alpha_{2}=-(b_{1}^{2}-b_{2}^{2})\alpha_{1}-2b_{1}b_{2}\alpha_{2}
-\end{equation}
-and 
-\begin{equation}
-    (a_{1}^{2}-a_{2}^{2})\alpha_{2}-2a_{1}a_{2}\alpha_{1}=(b_{1}^{2}-b_{2}^{2})\alpha_{2}-2b_{1}b_{2}\alpha_{1},
-\end{equation}
-which is equivalent to
-
-\e{
-|a|=|b|=\frac{\sqrt{2}}{2}
-}
-and 
-\e{
-\frac{\alpha_{2}}{\alpha_{1}}=-\frac{(a_{1}^{2}-a_{2}^{2})+(b_{1}^{2}-b_{2}^{2})}{2a_{1}a_{2}+2b_{1}b_{2}}.
-}
-This can always be satisfied. For example, we can always take $b=1/2+i/2$
-and the above equation becomes
-\e{
-\frac{\alpha_{2}}{\alpha_{1}}=\frac{(2a_{2}^{2}-1/2)}{2a_{2}\sqrt{1/2-a_{2}^{2}}+1/2},
-}
-which is always possible since the right hand side  can take any value.
-
-\section{Method of numerical diagonalization}\label{sec:numerical}
-
-Numerical diagonalization relies on the fact that the commutation relation $[K_x,K_y]=il^{-2}$ bears similarity to that of position operator and momentum operator of simple harmonic oscillators.
-Therefore, $K_x$ and $K_y$ can be organized into creation and annihilation operators
-\begin{align}
-\begin{split}
-K_x=&l^{-1}(a+a^\dagger)/\sqrt{2},\\
-K_y=&-il^{-1}(a-a^\dagger)/\sqrt{2}.
-\end{split}
-\end{align}
-Under this transformation, $H_R(\bK)$ is transformed to
-\begin{align}
-\begin{split}
-H_{R}(\boldsymbol{K})=&\frac{\hbar^2}{ml^2}(a^{\dagger}a+\frac{1}{2})
-\\&+\sqrt{2}\hbar\alpha l^{-1}\left(\begin{array}{cc}
-0 & -ia^{\dagger}\\
-ia & 0
-\end{array}\right)
--\frac{g_s\hbar^2\sigma^z}{4m_0l^2},
-\end{split}\label{eq:Rashba-ho}
-\end{align}
-where Zeeman coupling is already added.
-Eq.
-(\ref{eq:Rashba-ho}) have solutions in the form of $(c_1|n+1\rangle,c_2|n\rangle)$ where $c_1$ and $c_2$ are some constants and $|n\rangle$ labels the eigenstate of $a^\dagger a$.
-For Hamiltonian $H(\bK)$ that is not exactly solvable, it can be diagonalized by cutting off at a high occupation number of the coupled harmonic oscillators.
+Assuming that the spin-orbit coupling can be turned off continuously without changing the degree ($D=2$) of degeneracy, $\det(A)=1$ for class I-2, II-3, II-4, and thus Tab.
+\ref{table:fullcodimension} simplified to Tab.
+\ref{table:codimension-nearlydegen}-\ref{table:codimension-exactlydegen}.
+
+\subsection{Two-by-two sewing matrix of antiunitary symmetry operator can be made off-diagonal\label{app:makinggoffdiagonal}}
+
+Here we derive the third rule for gauge transformations (the third bulleted point in the previous subsection).
+We will show a gauge exists where $\breve{g}$ (the sewing matrix of an antiunitary symmetry, at a $g$-invariant wavevector) is off-diagonal.
+We will arrive at this gauge by a sequence of gauge transformations: $\breve{g}\rightarrow \dg{V}\breve{g}V^*$.
+
+\noi{i} The square of an antiunitary operator is unitary, hence $\breve{g}\breve{g}^* \rightarrow V^{-1}\breve{g}\breve{g}^*V$ can be diagonalized.
+In this diagonalized gauge, it is simple to see that either $\breve{g}$ is off-diagonal or it is a (complex) symmetric unitary matrix.
+In the former case, our job is done.
+Let us henceforth deal with the latter.
+
+\noi{ii} Any symmetric unitary matrix can be diagonalized by conjugation with a real orthogonal matrix,\footnote{To appreciate this, consider that any unitary matrix can be expressed as $e^{ih}$ with Hermitian $h$.
+If this unitary is also symmetric, $h$ must also by symmetric, hence also real.
+Thus the eigenvectors of a symmetric unitary can always be chosen to be real.} which we identify with $V$ in the next gauge transformation.
+Henceforth we assume $\breve{g}$ is diagonal.
+
+\noi{iii} By an appropriately chosen $V$ that is diagonal, we can always simplify $\breve{g}$ to the identity matrix.
+
+\noi{iv} Finally, with $V=e^{-i(\pi/4)\sigma_x}$, we obtain $\breve{g}=i\sigma_x$, with $\sigma_x$ an off-diagonal Pauli matrix. This completes the proof.\\
+
+In the special case that $g$ is order-two, then the associativity condition for $g$ imposes that $\breve{g}\breve{g}^*=\pm I$.
+In the case of $+I$, then $\breve{g}$ is symmetric, and we may apply (ii-iv) above to simplify $\breve{g}=i\sigma_x$; this can be made real by a final gauge transformation with $V=e^{i\pi/4}\sigma_x$.
+In the case where $\breve{g}\breve{g}^*=-I$, then $\breve{g}$ must be skew-symmetric (under transpose).
+Any skew-symmetric unitary matrix is proportional to $i\sigma_y$, up to a phase factor that can be gauged away.
+
+%We begin by parametrizing $\breve{g}$ as
+%\begin{equation}
+%\breve{g}=e^{i\theta}\left(\begin{array}{cc}
+%\alpha & \beta\\
+%-\beta^{*} & \alpha^{*}
+%\end{array}\right), \as |\alpha|^2+|\beta^2|=1,
+%\end{equation}
+%and $V$ as
+%\begin{equation}
+%V=e^{i\phi}\left(\begin{array}{cc}
+%a & b\\
+%-b^{*} & a^{*}
+%\end{array}\right), \as |a|^2+|b|^2=1,
+%\end{equation}
+%\begin{widetext}
+%which is possible since both two-by-two matrices are unitary. Under a gauge transformation, 
+%\begin{align}
+%\breve{g} & \to V^{\dagger}\breve{g}V^{*}\\
+% & =e^{i(\theta-2\phi)}\left(\begin{array}{cc}
+%a^{*} & -b\\
+%b^{*} & a
+%\end{array}\right)\left(\begin{array}{cc}
+%\alpha & \beta\\
+%-\beta^{*} & \alpha^{*}
+%\end{array}\right)\left(\begin{array}{cc}
+%a^{*} & b^{*}\\
+%-b & a
+%\end{array}\right)\\
+% & =e^{i(\theta-2\phi)}\left(\begin{array}{cc}
+%a^{*2}\alpha+a^{*}b\beta^{*}-a^{*}b\beta+b^{2}\alpha^{*} & a^{*}b^{*}\alpha+bb^{*}\beta^{*}+aa^{*}\beta-ab\alpha^{*}\\
+%\cdots & \cdots
+%\end{array}\right).
+%\end{align}
+%\end{widetext}
+%Decomposing real and imaginary parts of the parameters: $a=a_{1}+ia_{2}$, $b=b_{1}+ib_{2}$, $\alpha=\alpha_{1}+i\alpha_{2}$
+%and $\beta=\beta_{1}+i\beta_{2}$, the imaginary part
+%of $a^{*}b^{*}\alpha+bb^{*}\beta^{*}+aa^{*}\beta-ab\alpha^{*}$ can be removed by $a_2=b_2=0$ and 
+%\begin{equation}
+%2b_1\sqrt{1-b_1^{2}}\alpha_{2} =(2b_1^{2}-1)\beta_{2}.
+%\end{equation}
+%This is always possible since $2b\sqrt{1-b^{2}}/(2b^{2}-1)$ can take
+%any real value for $b\in[-1,1]$. Therefore, we can safely assume
+%$\beta$ is real since a preliminary transformation can remove its
+%imaginary part.
+
+%The equation of $a^{*2}\alpha+a^{*}b\beta^{*}-a^{*}b\beta+b^{2}\alpha^{*}=0$ then becomes
+%\begin{equation}
+%(a_{1}^{2}-a_{2}^{2})\alpha_{1}+2a_{1}a_{2}\alpha_{2}=-(b_{1}^{2}-b_{2}^{2})\alpha_{1}-2b_{1}b_{2}\alpha_{2}
+%\end{equation}
+%and 
+%\begin{equation}
+%    (a_{1}^{2}-a_{2}^{2})\alpha_{2}-2a_{1}a_{2}\alpha_{1}=(b_{1}^{2}-b_{2}^{2})\alpha_{2}-2b_{1}b_{2}\alpha_{1},
+%\end{equation}
+%which is equivalent to
+
+%\e{
+%|a|=|b|=\frac{\sqrt{2}}{2}
+%}
+%and 
+%\e{
+%\frac{\alpha_{2}}{\alpha_{1}}=-\frac{(a_{1}^{2}-a_{2}^{2})+(b_{1}^{2}-b_{2}^{2})}{2a_{1}a_{2}+2b_{1}b_{2}}.
+%}
+%This can always be satisfied. For example, we can always take $b=1/2+i/2$
+%and the above equation becomes
+%\e{
+%\frac{\alpha_{2}}{\alpha_{1}}=\frac{(2a_{2}^{2}-1/2)}{2a_{2}\sqrt{1/2-a_{2}^{2}}+1/2},
+%}
+%which is always possible since the right hand side  can take any value.
+
+\bibliography{paper}
+
 \end{document}

### 2019-02-01 paper.tex
fix typo

@@
 To derive the above equation, we have utilized $\phi^B_-{+}\phi^B_+{=}0$, which is valid for any two-band model in the nearly-degenerate regime\footnote{For two band models, Berry phases of the two bands sum up to 0 on arbitrary path}; in \fig{fig:blochsphere} this is reflected in the sum of solid angles (at fixed energy) equalling $4\pi$.
-\q{trefoilrule} may be interpreted as a quantization rule for a trajectory on a M\"obius strip  with net area $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels (sketched by solid lines in the upper panel of Fig.
+\q{trefoilrule} may be interpreted as a quantization rule for a trajectory on a M\"obius strip  with net area $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels (sketched by solid lines in Fig.
 \ref{fig:RZ}(c)) are periodic in $E{\rightarrow}E{+}\pi/l^2(\partial S/\partial E)$ and in $l^2{\rightarrow}l^2{+}\pi/S$.
@@
 
-{The Landau levels derived from \q{eq:rule} are generically non-equidistant, and the spin-half (or pseudospin-half) degeneracy between Landau levels is generically lifted due to the subleading corrections ($\lambda_{1,2}$).
-As argued in \s{sec:qtznrules},} the level splitting is approximately $\var_c\delta \lambda/2\pi$ with $\delta \lambda=|\lambda_1-\lambda_2|$.
+The Landau levels derived from \q{eq:rule} are generically non-equidistant, and the spin-half (or pseudospin-half) degeneracy between Landau levels is generically lifted due to the subleading corrections ($\lambda_{1,2}$).
+As argued in \s{sec:qtznrules}, the level splitting is approximately $\var_c\delta \lambda/2\pi$ with $\delta \lambda=|\lambda_1-\lambda_2|$.
 Conversely, Landau levels are approximately spin-degenerate if $\lambda_1{=}\lambda_2$ (mod $2\pi$) -- this degeneracy condition for the eigenvalues of $\A$ typically requires fine-tuning of some Hamiltonian parameters.

### 2019-03-18 paper.tex
Updates from Overleaf

@@
 Symmetry does not only constrain the level repulsion between $\lambda_1$ and $\lambda_2$ -- in certain classes, it constrains their sum.
-In our previous work on exactly-degenerate, spin-differentiated orbits\cite{100p,topoferm}, we have derived a zero-sum rule ($\lambda_1{+}\lambda_2{\equiv}0$) in classes  I-1, II-3 and II-4, with the assumption that spin-orbit coupling can be continuously tuned to zero without changing the degree of degeneracy; this zero-sum rule implies a quantized phase offset for the fundamental harmonic of quantum oscillations\cite{topoferm}.
+In our previous work on exactly-degenerate, spin-differentiated orbits\cite{100p,topoferm}, we have derived a zero-sum rule ($\lambda_1{+}\lambda_2{\equiv}0$) in classes I-2, II-3 and II-4, with the assumption that spin-orbit coupling can be continuously tuned to zero without changing the degree of degeneracy; this zero-sum rule implies a quantized phase offset for the fundamental harmonic of quantum oscillations\cite{topoferm}.
 Here, we report that the zero-sum rule applies \textit{also} to nearly-degenerate orbits in classes I-1, II-3 and II-4; this may be derived by combining the symmetry analysis of Ref.\ \onlinecite{topoferm} with the tracelessness of $\delta\var$ [cf.\ \q{eq:H1}].

### 2019-04-03 paper.tex
Updates from Overleaf

@@
 \label{eq:RZ-Hamiltonian}}
-While this field breaks both time-reversal ($T$) and two-fold rotational ($C_2$) symmetries, the composition $C_2T$ is preserved as $\sigma_x H^*_{RZ}(\bk)\sigma_x{=}H_{RZ}(\bk),$ which constrains spin to lie in-plane at each $\bk$.
+While this field breaks both time-reversal ($T$) and two-fold rotational ($\mathfrak{c}_2$) symmetries, the composition $\mathfrak{c}_2T$ is preserved as $\sigma_x H^*_{RZ}(\bk)\sigma_x{=}H_{RZ}(\bk),$ which constrains spin to lie in-plane at each $\bk$.
 In this symmetry class, Dirac nodes are irremovable but movable in two-dimensional $\bk$-space.
@@
 The decomposition of the effective Hamiltonian [cf.\ Eq.
-(\ref{calHRZ})] into  Pauli matrices ($\calh{=}\sum_j\calh_j\sigma_j$) defines a three-vector $\boldsymbol{\calh}{=}({-}\alpha k_y$,$\alpha k_x{+}Z_\parallel,{-}Z_\perp$).
+(\ref{calHRZ})] into  Pauli matrices ($\calh{=}\sum_j\calh_j\sigma_j$) defines a three-vector $\boldsymbol{\calh}{=}({-}\alpha k_y$,$\alpha k_x{+}Z_\parallel,{-}Z_\perp)$.
 $\phi_{\pm}^B$ equals half the solid angle subtended by   ${\mp} \boldsymbol{\calh}(\bk)$ [solid blue line] as $\bk$ is varied along the outer/inner orbit\cite{berry_quantal_1984}; the orientation of the solid angle is indicated by blue dotted lines.
@@
 
-\fig{fig:LL} illustrates a typical Landau-level dispersion in the near-degeneracy regime ($\delta S{\ll} S)$ of the Rashba 2DEG (in an out-of-plane field).
+\fig{fig:LL} illustrates a typical Landau-level dispersion in the near-degeneracy regime ($\delta S{\ll} S)$ of the Rashba-Dresselhaus 2DEG [cf.
+Eq.
+\ref{hamRD}] in an out-of-plane field.
 Each solution of the quantization rule [cf.\ \q{eq:rule}], with fixed $a\in \{1,2\}$ and $n \in \Z$, defines a curve in $(E,B)$-space that we indicate by  a solid black line.

### 2019-04-03 paper.tex
Updates from Overleaf

@@
 $\delta \var$ is the projection of $\delta \hat{H}$ to the degenerate band subspace of $\hat{H}_0$.
-$\delta \var$ is assumed to be traceless; this property is guaranteed if $\delta \hat{H}$ represents a spin-orbit coupling term that breaks the spin SU(2) symmetry of $\hat{H}_0$;\footnote{The Pauli spin-orbit coupling term ${\propto} \bs{\cdot} (\bE {\times} \bp)$ is traceless in any spin-symmetric (pseudo-)spinor basis.
+$\delta \var$ is assumed to be traceless; this property is guaranteed if $\delta \hat{H}$ represents a spin-orbit coupling term that breaks the spin $\text{SU}(2)$ symmetry of $\hat{H}_0$;\footnote{The Pauli spin-orbit coupling term ${\propto} \bs{\cdot} (\bE {\times} \bp)$ is traceless in any spin-symmetric (pseudo-)spinor basis.
 Viewing the spin-orbit coupling as a small parameter in degenerate perturbation theory, the lowest-order splitting of any spin-degenerate energy level is always symmetric about the zeroth-order energy.
@@
 The condition of eigenvalue-degeneracy for $\A$: \e{\lambda_1(\bar{E},\bar{B})=\lambda_2(\bar{E},\bar{B})+2m\pi, \as m\in \Z \la{eigenvaluedegeneracyA}}
-defines a distinct set of curves [red dashed lines in \fig{fig:LL}] -- for the symmetry class of the Rashba 2DEG.
+defines a distinct set of curves [red dashed lines in \fig{fig:LL}] -- for the symmetry class of the Rashba-Dresselhaus 2DEG.
 (For other symmetry classes, the eigenvalue-degeneracy for $\A$ may instead define a set of points, or may generically have no solution in $(E,B)$ space.)   The two sets of curves (solid and dashed) intersect at isolated points where Landau levels are spin degenerate -- to the accuracy of our quantization rule.
@@
 To generalize the discussion beyond band-conservation symmetry, it is instructive to adopt a geometric perspective on degeneracies.
-A generic SU(2) matrix that is constrained by symmetry may no longer be uniformly distributed over $S^3$ [cf.\ \q{s3}], e.g., ${\cal \bar{A}}$ with band-conservation symmetry is uniformly distributed over a phase in $S^1$.
-In such cases, we are  motivated to adopt \textit{symmetric coordinates} [$\{r_1,\ldots,r_{d}\}{:}{=}\br$] that independently parametrize the symmetry-constrained SU(2) matrix; the precise nature of these constraints will be developed in subsequent subsections.
+A generic $\text{SU}(2)$ matrix that is constrained by symmetry may no longer be uniformly distributed over $S^3$ [cf.\ \q{s3}], e.g., ${\cal \bar{A}}$ with band-conservation symmetry is uniformly distributed over a phase in $S^1$.
+In such cases, we are  motivated to adopt \textit{symmetric coordinates} [$\{r_1,\ldots,r_{d}\}{:}{=}\br$] that independently parametrize the symmetry-constrained $\text{SU}(2)$ matrix; the precise nature of these constraints will be developed in subsequent subsections.
 In our example, we may choose the symmetric coordinate as the phase of the diagonal element of ${\cal \bar{A}}$.
@@
 The tracelessness of $\calh$ (at each $\bk$) implies that  ${\A}_{\sma{T_c/2\leftarrow 0}}$  has unit determinant.
-Employing the canonical SU(2) parametrization for the half-loop propagator [Eq.
+Employing the canonical $\text{SU}(2)$ parametrization for the half-loop propagator [Eq.
 (\ref{s3}) with ${\cal \bar{A}}$ replaced by ${\A}_{\sma{T_c/2\leftarrow 0}}$], we derive from \q{eq:sigmazconstraint} that
@@
 \hline 
-\multirow{2}{*}{1} & \multirow{2}{*}{$\mathfrak{r}_z$, $\mathfrak{r}_{z,\boldsymbol{a(b)}/2}$} & $T\mathfrak{i}$, spin SU(2) & $\sigma_z$ \\
+\multirow{2}{*}{1} & \multirow{2}{*}{$\mathfrak{r}_z$, $\mathfrak{r}_{z,\boldsymbol{a(b)}/2}$} & $T\mathfrak{i}$, spin $\text{SU}(2)$ & $\sigma_z$ \\
 \cline{3-4}
@@
 \hline
-\multirow{3}{*}{5} & $\mathfrak{r}_{x(y),\boldsymbol{c}/2}$ & $T\mathfrak{i}$, spin SU(2), $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$ & $\sigma_z$ \\
+\multirow{3}{*}{5} & $\mathfrak{r}_{x(y),\boldsymbol{c}/2}$ & $T\mathfrak{i}$, spin $\text{SU}(2)$, $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$ & $\sigma_z$ \\
 \cline{2-4}
-& $\mathfrak{r}_{x(y)}$,$\mathfrak{r}_{x(y),\boldsymbol{b(a)}/2}$, & $T\mathfrak{i}$, spin SU(2) & $\sigma_z$ \\
+& $\mathfrak{r}_{x(y)}$,$\mathfrak{r}_{x(y),\boldsymbol{b(a)}/2}$, & $T\mathfrak{i}$, spin $\text{SU}(2)$ & $\sigma_z$ \\
 \cline{3-4}
@@
 The $z$ axis of our Cartesian coordinate system is aligned parallel to the  magnetic field.
-This table is applicable to exactly-degenerate orbits whose degeneracy is protected by either spacetime inversion symmetry ($T\mathfrak{i}$), the composition of time reversal and nonsymmorphic two fold rotation symmetry ($T\mathfrak{c}_{2z,\boldsymbol{c}/2}$) [for orbits confined to the $k_z=\pi$ plane] or spin SU(2) symmetry (i.e., negligible spin-orbit coupling).
+This table is applicable to exactly-degenerate orbits whose degeneracy is protected by either spacetime inversion symmetry ($T\mathfrak{i}$), the composition of time reversal and nonsymmorphic two fold rotation symmetry ($T\mathfrak{c}_{2z,\boldsymbol{c}/2}$) [for orbits confined to the $k_z=\pi$ plane] or spin $\text{SU}(2)$ symmetry (i.e., negligible spin-orbit coupling).
 \label{table:sewing-matrix}}
@@
 we expect $\delta \lambda{\equiv}\pi$ is attainable with at most one tunable parameter (in any symmetry class).
-To prove this, we return to the canonical parametrization of the SU(2) component (${\cal \bar{A}}$) of $\A$ [cf.\ \q{s3}].
+To prove this, we return to the canonical parametrization of the $\text{SU}(2)$ component (${\cal \bar{A}}$) of $\A$ [cf.\ \q{s3}].
 The necessary and sufficient condition for $\delta \lambda{\equiv}\pi$ is that ${\cal \bar{A}}(r_1,r_2,r_3)$ has eigenvalues $+i$ and $-i$; this is equivalent to setting $r_1{=}0$ in \q{s3} -- a condition on a single parameter.\footnote{For an alternative proof,  $\delta \lambda{\equiv}\pi$ is equivalent to ${ \bar{\cal A}}{=}Ve^{i\sigma_z\pi/2}V^{-1}$ for some unitary $V\in U(2)$.
@@
 
-The self constraints of the six classes can be divided into two types: (i) restricting $\A$ to only a submanifold of SU(2) (class I-1, I-2, II-2, II-4); (ii) expressing the propagator $\A$ as a product of propagators over a fraction of the period [e.g., Eq.
+The self constraints of the six classes can be divided into two types: (i) restricting $\A$ to only a submanifold of $\text{SU}(2)$ (class I-1, I-2, II-2, II-4); (ii) expressing the propagator $\A$ as a product of propagators over a fraction of the period [e.g., Eq.
 (\ref{eq:sigmazconstraint})] (class II-1, II-3).

### 2019-04-04 paper.tex
Updates from Overleaf

@@
 \end{tabular}
-\caption{Symmetry-constrained codimensions for nearly-degenerate orbits, which fall into five symmetry classes (as numbered in the first column).
+\caption{Symmetry-constrained codimensions for nearly-degenerate orbits, which fall into five symmetry classes (as numbered in the fifth column).
 This table is also applicable to exactly-degenerate orbits, which fall into ten symmetry classes -- five here, and five in  \tab{table:codimension-exactlydegen}.
-The second and third columns define how the symmetry acts on the cyclotron orbit.
+The first and second columns define how the symmetry acts on the cyclotron orbit.
 The next two columns inform us if the mapping $\bk{\rightarrow}g{\circ}\bk$ [cf.\ \q{gmapk}]  preserves ($u{=}0$) or inverts ($u{=}1$) the orientation of the orbit, and if $g$ preserves ($s{=}0$) or inverts ($s{=}1$) the arrow of time.
@@
 
-Of the ten classes described in \s{sec:reviewtenfold}, only five   are relevant to quasidegenerate orbits (which are split with differential area  $\delta S$ that is much less than the area of $\frako_0$).
+Of the ten classes described in \s{sec:reviewtenfold}, only five are relevant to nearly-degenerate orbits (which are split with differential area  $\delta S$ that is much less than the area of $\frako_0$).
 To identify these five, recall that $\lambda_a$ in our quantization rule is determined by the propagator $\A$ [cf.\ \q{eq:prop}], which is a time-ordered exponential of an effective Hamiltonian $\H{=}\delta\epsilon{+}B \mathcal{M}$ [cf.\ \q{eq:H1}]; $\H$ perturbatively encodes $\delta H$ and the Zeeman interaction, for an electron travelling over  $\frako_0$.

### 2019-04-05 paper.tex
Updates from Overleaf

@@
 \hlineB{2.0}
-class No. & symmetry  & origin of degeneracy & $\breve{g}\propto$ \\
+class label & symmetry  & origin of degeneracy & $\breve{g}\propto$ \\
 \hline 
-\multirow{2}{*}{1} & \multirow{2}{*}{$\mathfrak{r}_z$, $\mathfrak{r}_{z,\boldsymbol{a(b)}/2}$} & $T\mathfrak{i}$, spin $\text{SU}(2)$ & $\sigma_z$ \\
+\multirow{2}{*}{I-1} & \multirow{2}{*}{$\mathfrak{r}_z$, $\mathfrak{r}_{z,\boldsymbol{a(b)}/2}$} & $T\mathfrak{i}$, spin $\text{SU}(2)$ & $\sigma_z$ \\
 \cline{3-4}
@@
 \hline
-\multirow{3}{*}{5} & $\mathfrak{r}_{x(y),\boldsymbol{c}/2}$ & $T\mathfrak{i}$, spin $\text{SU}(2)$, $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$ & $\sigma_z$ \\
+\multirow{3}{*}{II-4} & $\mathfrak{r}_{x(y),\boldsymbol{c}/2}$ & $T\mathfrak{i}$, spin $\text{SU}(2)$, $T\mathfrak{c}_{2z,\boldsymbol{c}/2}$ & $\sigma_z$ \\
 \cline{2-4}
@@
 The latter two nonsymmorphic elements involve  half a lattice translation in the $x,~y,$ or $z$ direction (labeled by $\boldsymbol{a,~b,~c}$ respectively).
-The $z$ axis of our Cartesian coordinate system is aligned parallel to the  magnetic field.
+The $-z$ axis of our Cartesian coordinate system is aligned parallel to the  magnetic field.
 This table is applicable to exactly-degenerate orbits whose degeneracy is protected by either spacetime inversion symmetry ($T\mathfrak{i}$), the composition of time reversal and nonsymmorphic two fold rotation symmetry ($T\mathfrak{c}_{2z,\boldsymbol{c}/2}$) [for orbits confined to the $k_z=\pi$ plane] or spin $\text{SU}(2)$ symmetry (i.e., negligible spin-orbit coupling).
@@
 
-At high temperature ($kT{\gg}\var_c$) and/or with strong disorder ($\omega_c\tau_{\sma{D}}{\ll}1$), the dominant contribution to $\delta M$ is from the fundamental harmonic ($r{=}1$), which sums two sine functions with generically distinct phase offsets $\lambda_{1,2}$.
+At high temperature ($k_BT{\gg}\var_c$) and/or with strong disorder ($\omega_c\tau_{\sma{D}}{\ll}1$), the dominant contribution to $\delta M$ is from the fundamental harmonic ($r{=}1$), which sums two sine functions with generically distinct phase offsets $\lambda_{1,2}$.
 This summation (or interference) is constructive if $\delta \lambda{=}|\lambda_1{-}\lambda_2|{\equiv}0$, and destructive if $\delta \lambda{\equiv}\pi$  ($\equiv$ denotes an equivalence modulo $2\pi$).
@@
 We have shown in \s{sec:llquasideg} that  the number of tunable parameters required to attain  $\delta \lambda{\equiv}0$ ranges from $0$ to $3$; this number is a symmetry-dependent measure of Landau-level repulsion [cf.\ \tab{table:codimension-nearlydegen} and \tab{table:codimension-exactlydegen}].
-As illustrated in the right-most panel of Fig 7(b), $\delta \lambda{\equiv}\pi$ is the condition  for Landau levels to be quasi-equidistant  with spacing ${\approx}\var_c/2$; since no level repulsion need be overcome,
+As illustrated in the right-most panel of Fig.
+\fig{fig:qo}(b), $\delta \lambda{\equiv}\pi$ is the condition  for Landau levels to be quasi-equidistant  with spacing ${\approx}\var_c/2$; since no level repulsion need be overcome,
 we expect $\delta \lambda{\equiv}\pi$ is attainable with at most one tunable parameter (in any symmetry class).
@@
 
-%Going beyond the accuracy of our theory, one may account for linear-in-$B$ corrections to $\lambda_a$ at stronger fields, however a quantitative theory for such corrections only exists (thus far) for non-degenerate orbits\cite{rothmag,fuchs_landau_2018,gao_zero-field_2017,fischbeck_review}.
-
 For nearly-degenerate orbits, $\lambda_a$ is expandable as a Laurent series in $B$ with leading term $1/B$ [cf.\ \q{lambdasmallB}], hence $B$ can be tuned to attain destructive interference.
@@
 As one application, one may extract the intervals (in $1/B$) between nodes for the Rashba 2DEG [by imposing $\delta \lambda{\equiv}\pi$ in \q{eq:Rashba-lambda}] and for the Rashba-Dresselhaus 2DEG (see the subsequent \s{sec:quantosc_quasideg}).
-
-%In some experiments\cite{das_evidence_1989}, it has been recognized that the oscillation frequency in $1/B$, denoted as $f$, is weakly dependent on $B$ itself; 
-%the possibly aperiodic beatings has been interpreted as a $B$ dependent oscillation frequency difference $\delta f$ between the two splitted orbits.
-In our language, the frequency difference is related to $\delta\lambda$ as $\delta f=B\delta\lambda/2\pi$.
-It has been appreciated that the leading-order term of $\lambda$ (${\sim}1/B$) originates from the zero-field splitting of orbits; this has been applied to estimate the strength of the spin-orbit coupling\cite{das_evidence_1989,onuki_chiral-structure-driven_2014,maurya_splitting_2018}.
 
@@
 
-%\red{Symmetry constrained codimension is the number of parameters needed to find $\lambda_1=\lambda_2 \mod 2\pi$, which is generally not a solution of our quantization rule.
-If one more parameter is available, the simultaneous solution of quantization rule and $\lambda_1=\lambda_2 \mod 2\pi$ can generally found, as illustrated in Fig.
-\ref{fig:LL}.
-These solutions are exact degeneracies in the sense of first order semiclassical approximation.
-It is possible that these solutions are exact even beyond semiclassical approximation, for example when the two crossing Landau levels belongs to the different representation of a symmetry operation.
-A general answer to whether these solutions are always exact degeneracies beyond semiclassical approximation is left for further investigation.}
-
 Our codimension analysis is applicable to contexts beyond that of Landau-level repulsion.
@@
 Here, we report that the zero-sum rule applies \textit{also} to nearly-degenerate orbits in classes I-1, II-3 and II-4; this may be derived by combining the symmetry analysis of Ref.\ \onlinecite{topoferm} with the tracelessness of $\delta\var$ [cf.\ \q{eq:H1}].
-
-%Although these three symmetry classes do not impose constraints on nearly-degenerate orbit, due to the traceless spin splitting Hamiltonian matrix, $\lambda_1+\lambda_2=0$ remains true for nearly-degenerate orbits.
 
@@
 
-%utilizing a mathematical result proved in App. \ref{app:makinggoffdiagonal}.
-
-%The numerical diagonalization method is reviewed in App. \ref{sec:numerical}.
-
 \section{Proof of quantization rule for the Landau levels of nearly-degenerate bands \label{app:quantizationruleproof}}
@@
 
-%The solution to the  effective Schr\"odinger equation is defined by imposing a hard-wall boundary condition [on $f_{\bk} = \sum_\nu g_{\bk}^\nu$] at the classical turning points.
-In this manner we obtain  the  quantization rule for cyclotron motion.
-
 Similar to what is done in Ref. \onlinecite{100p}, we seek the solution to the Schr\"odinger equation using the following multicomponent wave function ansatz
@@
 \end{equation}
-
-%Eq. ({\ref{eq:prop}}) can be obtained by solving boundary conditions at turning points.
 
@@
 We remark that $l^2\delta S^2/S\ll 1$, along with the standard semiclassical condition, sets a double-sided constraint on the magnetic field: $S^{-1} \ll l^2 \ll S/(\delta S)^2$.
-
-%The quantization rule thus requires an extra condition $l^2\delta S^2/S\ll 1$, which is an upper bound for Landau level index: $n\ll(S/\delta S)^2$.
 
@@
 \ref{app:quantizationruleproof}].
-
-%\red{In Fig.\ \ref{fig:error}(a), a comparison is made between the Landau levels obtained from exact numerical diagonalization of $H_{RD}(\bK)$ (plus the Zeeman coupling to spin) and those obtained from the quantization rule.
-Just as for the Rashba model, the accuracy of our rule improves with decreasing parameter $l^2\delta S(\alpha,\beta)^2/S$ [cf.
-Eq.(\ref{eq:Rashba-exact}) and the discussion in App.
-\ref{app:quantizationruleproof}].
-The error has been estimated by comparing the difference in energies (rule-obtained vs exact-diagonalized) for a single Landau level.
-For our chosen spin-orbit parameters $\alpha$ and $\beta$ range, the difference in energies does not exceed $2\%$ of $\var_c$ as $l^2\delta S^2/S$ varies over $[0,0.8]$.}
-
-%In Fig.
-\ref{fig:error} (b), we focus on a regime ($\hbar\alpha k_{\sma{E}}{\lesssim}\var_c$) where the nearly-degenerate orbits are appreciably hybridized and calculate the error defined above for the Landau level closest to the Dirac point.
-For fixed  $B_{\perp}$ and a range of $(\alpha,\zpar)$ wherein  $l^2\delta S^2/S$ varies over $[0,0.2]$, the difference between semiclassical and exact Landau levels never exceeds 0.3\% of the cyclotron energy $\var_c$.
-
-%Assuming the semiclassical and near-degeneracy conditions, our quantization rule \qq{eq:rule}{eq:H1} remains valid, however the propagator $\cala$ no longer has the closed analytic form of \q{propinplanezeeman}.
-We may anyway diagonalize $\cala$ numerically, and compare the resultant semiclassical Landau levels with the exact diagonalization of $H_{RZ}(\boldsymbol{K})$; to our knowledge, there exists no analytic solution of $H_{RZ}(\boldsymbol{K})$ for generic values of $\alpha,\zpar$ and $B_{\perp}$.
-For fixed  $B_{\perp}$ and a range of $(\alpha,\zpar)$ wherein  $l^2\delta S^2/S$ varies over $[0,0.2]$, the difference between semiclassical and exact Landau levels never exceeds  0.3\% of the cyclotron energy $\var_c$; this difference shows a strong positive correlation with $l^2\delta S^2/S$ [compare the left and right panels of Fig.\ \ref{fig:RZ} (d)], just like in the Rashba-Dresselhaus model.
-
-%as illustrated in in \fig{fig:RD}(a). Here we have shown a strong positive correlation between the error of the quantization rule and  $l^2\delta S(\alpha,\beta)^2/S$;
-
-%The difference in energies tends to increase with smaller field [compare the left and right panels of   \fig{fig:RD}(b)] and shows a strong positive correlation with $l^2\delta S(\alpha,\beta)^2/S$ [compare \fig{fig:RD}(c) with \fig{fig:RD}(d)] for various choices of the spin-orbit parameters $(\alpha,\beta)$.
-This correlation may be anticipated from \q{eq:Rashba-exact}, which analytically demonstrates how terms involving $l^2\delta S^2/S$ modifies the quantization rule in the case where $\beta{=}0$.
-
-%In \s{sec:llquasideg} we will further motivate the study of $H_{RD}$ by investigating the prevalence of Landau-level degeneracies.
 
@@
 
-%\subsection{Rashba 2DEG in a tilted field}\la{app:rashba2DEGtilted_comparenumerics}
-
-%In \s{sec:inplanezeeman}, we focused on a parameter regime ($\hbar\alpha k_{\sma{E}}{\gg}\var_c$) of the Rashba 2DEG (in tilted field), where the nearly-degenerate spin-split orbits are negligibly hybridized by the Zeeman interaction -- except near a type-II Dirac point.
-
 \section{Existence of Landau-level quasidegeneracy\label{sec:proofLLquasideg}}
@@
 Combining \q{estimate} with the above estimates for $\lambda'_{\pm}$, we derive \q{llquasideg}.
-%From \s{sec:qtznrules}, we know that for sufficiently weak field ($\var_c\ll \Delta$), $\lambda_{\pm}'\approx \pm l^2\delta S'/2$.
-For $\var_c\gg \Delta$, $\lambda_{\pm}'$ is determined by the energy dependence of the field-dependent terms in the effective Hamiltonian $\calh$.
 
@@
 Combining \q{estimateB} with the above estimates for $\dot{\lambda}_{\pm}$, we derive \q{llquasidegB}.
-
-%The order-of-magnitude estimate is obtained in the limit $l^2\delta S \gg 1$, where $\lambda_{\pm}\approx \pm l^2\delta S/2$ [cf.\ \q{phaseindependentorbit}].
-In the opposite limit $l^2\delta S \ll 1$, $\lambda_{\pm}$ is independent of $B$ within the accuracy of our semiclassical theory.
 
@@
 
-%We begin by parametrizing $\breve{g}$ as
-%\begin{equation}
-%\breve{g}=e^{i\theta}\left(\begin{array}{cc}
-%\alpha & \beta\\
-%-\beta^{*} & \alpha^{*}
-%\end{array}\right), \as |\alpha|^2+|\beta^2|=1,
-%\end{equation}
-%and $V$ as
-%\begin{equation}
-%V=e^{i\phi}\left(\begin{array}{cc}
-%a & b\\
-%-b^{*} & a^{*}
-%\end{array}\right), \as |a|^2+|b|^2=1,
-%\end{equation}
-%\begin{widetext}
-%which is possible since both two-by-two matrices are unitary. Under a gauge transformation, 
-%\begin{align}
-%\breve{g} & \to V^{\dagger}\breve{g}V^{*}\\
-% & =e^{i(\theta-2\phi)}\left(\begin{array}{cc}
-%a^{*} & -b\\
-%b^{*} & a
-%\end{array}\right)\left(\begin{array}{cc}
-%\alpha & \beta\\
-%-\beta^{*} & \alpha^{*}
-%\end{array}\right)\left(\begin{array}{cc}
-%a^{*} & b^{*}\\
-%-b & a
-%\end{array}\right)\\
-% & =e^{i(\theta-2\phi)}\left(\begin{array}{cc}
-%a^{*2}\alpha+a^{*}b\beta^{*}-a^{*}b\beta+b^{2}\alpha^{*} & a^{*}b^{*}\alpha+bb^{*}\beta^{*}+aa^{*}\beta-ab\alpha^{*}\\
-%\cdots & \cdots
-%\end{array}\right).
-%\end{align}
-%\end{widetext}
-%Decomposing real and imaginary parts of the parameters: $a=a_{1}+ia_{2}$, $b=b_{1}+ib_{2}$, $\alpha=\alpha_{1}+i\alpha_{2}$
-%and $\beta=\beta_{1}+i\beta_{2}$, the imaginary part
-%of $a^{*}b^{*}\alpha+bb^{*}\beta^{*}+aa^{*}\beta-ab\alpha^{*}$ can be removed by $a_2=b_2=0$ and 
-%\begin{equation}
-%2b_1\sqrt{1-b_1^{2}}\alpha_{2} =(2b_1^{2}-1)\beta_{2}.
-%\end{equation}
-%This is always possible since $2b\sqrt{1-b^{2}}/(2b^{2}-1)$ can take
-%any real value for $b\in[-1,1]$. Therefore, we can safely assume
-%$\beta$ is real since a preliminary transformation can remove its
-%imaginary part.
-
-%The equation of $a^{*2}\alpha+a^{*}b\beta^{*}-a^{*}b\beta+b^{2}\alpha^{*}=0$ then becomes
-%\begin{equation}
-%(a_{1}^{2}-a_{2}^{2})\alpha_{1}+2a_{1}a_{2}\alpha_{2}=-(b_{1}^{2}-b_{2}^{2})\alpha_{1}-2b_{1}b_{2}\alpha_{2}
-%\end{equation}
-%and 
-%\begin{equation}
-%    (a_{1}^{2}-a_{2}^{2})\alpha_{2}-2a_{1}a_{2}\alpha_{1}=(b_{1}^{2}-b_{2}^{2})\alpha_{2}-2b_{1}b_{2}\alpha_{1},
-%\end{equation}
-%which is equivalent to
-
-%\e{
-%|a|=|b|=\frac{\sqrt{2}}{2}
-%}
-%and 
-%\e{
-%\frac{\alpha_{2}}{\alpha_{1}}=-\frac{(a_{1}^{2}-a_{2}^{2})+(b_{1}^{2}-b_{2}^{2})}{2a_{1}a_{2}+2b_{1}b_{2}}.
-%}
-%This can always be satisfied. For example, we can always take $b=1/2+i/2$
-%and the above equation becomes
-%\e{
-%\frac{\alpha_{2}}{\alpha_{1}}=\frac{(2a_{2}^{2}-1/2)}{2a_{2}\sqrt{1/2-a_{2}^{2}}+1/2},
-%}
-%which is always possible since the right hand side  can take any value.
-
 \bibliography{paper}

### 2019-04-05 paper.tex
Updates from Overleaf

@@
 
-%\renewcommand{\topfraction}{.85}
-%\renewcommand{\bottomfraction}{.7}
-%\renewcommand{\textfraction}{.15}
-%\renewcommand{\floatpagefraction}{.66}
-%\renewcommand{\dbltopfraction}{.66}
-%\renewcommand{\dblfloatpagefraction}{.66}
-%\setcounter{topnumber}{3}
-%\setcounter{bottomnumber}{3}
-
 \begin{document}
@@
 
-%n close analogy with the Wigner-von Neumann `non-crossing rule' in quantum mechanics, we find that three tunable parameters are needed to attain a Landau-level quasidegeneracy -- in the absence of crystalline point-group symmetries [cf.\ \s{sec:introducecodimension}].
-%We have further determined symmetric variants of the ‘non-crossing rule’ for Landau levels, for any spacetime symmetry that occurs in crystalline solids
-
 \section{Introduction}
@@
 
-%In other words,  \qq{eq:rule}{berryconn} is equally valid with $\{u_n\}_{n=1}^2$ replaced by energy eigenfunctions of $\hat{H}_0$ which are not simultaneously eigenfunctions of $\delta \hat{H}$.
-
-%In subsequent case studies, it may be analytically convenient to adopt a $\bk$-independent basis, if such a basis exists; the non-abelian Berry connection defined with respect to this basis would vanish.
-
-%It will be useful to separate $B$-independent and $B$-dependent terms in \q{eq:H1}; the latter we denote as $B\calm$, with $\calm$ having the dimension of a magnetic moment.
-Let us explain each term in the order of its appearance.\\
-
 \subsection{Recovering the Onsager-Lifshitz-Roth quantization rules in two limits}\label{sec:recoveronsager}
@@
 \\
-
-%\footnote{Though the adiabatic limit does not exist for orbits that exactly intersect at type-II Dirac points, these orbits are nevertheless describable by our quantization rule, as exemplified in the case studies of \s{sec:inplanezeeman} and \s{sec:rotsymmbreakdown}.}}
 
@@
 This comparison is made for the Landau levels closest to 0.45eV and with even Landau-level index $n$; for the parameters we have chosen ($m{=}0.076m_0$, $\alpha{=} 1.5\times10^{5}$cm/s, $Z_\parallel {=}$1meV and $g_{s\perp}=2$),  the II-Dirac point lies at 0.5eV.
-%Out-of-plane Zeeman coupling is negligibly weak.
 \label{fig:RZ}}
 \end{figure}
-
-%red dashed line shows the energetic difference between Landau levels determined by numerical diagonalization and Landau levels obtained by the M\"obius quantization rule  [cf.\ Eq.\ (\ref{trefoilrule})]; this red dashed line may be compared to the perturbative formula $\delta E_n$ [cf.
-Eq.
-(\ref{RZfirstorderE})], which is plotted as a black solid line.
 
@@
 The out-of-plane Zeeman interaction lifts $\boldsymbol{\calh}$ out of the $x-y$ plane, but this effect is significant only over a fraction $(\sim Z_{\perp}/\hbar \alpha k_E)$  of the cyclotron period.
-% ${\sim}[(\bar{\mu}_{\sma{\text{min}}}/g_{s\perp})(m_0/m){\ll}1]$
 \label{fig:blochsphere}}
@@
 
-%\red{It is possible that a subset of these quasidegeneracies are in fact exact degeneracies, owing to Landau levels carrying different quantum numbers -- a subject we elaborate in \s{sec:discussion}.}
-
 \subsection{Codimension analysis without symmetry, and with band-conservation symmetry}\label{sec:introducecodimension}
@@
 \end{equation}
-{For the Rashba-Dresselhaus 2DEG, $\A$ depends on $\alpha,~\beta,~l,~E,~m$ only through three independent parameters:}%$\hbar\alpha k_E /\var_c$, $\hbar\beta k_E /\var_c$ and $g_sm/m_0$, let us consider the three-dimensional parameter space:
+{For the Rashba-Dresselhaus 2DEG, $\A$ depends on $\alpha,~\beta,~l,~E,~m$ only through three independent parameters:}
 \e{\left( \f{\hbar\alpha k_{\sma{E}}}{\var_c},\f{\hbar\beta k_{\sma{E}}}{\var_c},g_{s\perp}\f{m}{m_0} \right){\in} \mathbb{R}^3. \la{parameter2}}  
@@
 These two points are mapped to a path-connected line node confined to the $\alpha{=}0$ and $\beta{=}0$ planes [cf.\ \fig{fig:dgn}(b)]; the difference in codimension originates from the $\mathfrak{c}_{\infty}$ symmetry within these two planes (cf.\ \s{sec:ctsrot}), which was not accounted for in the $\mathfrak{c}_2$-symmetric analysis of \q{proprashba}.
-
-%Let us relate \q{proprashba} to the Rashba-Dresselhaus model.
-For any choice of parameters for $\calh$, the time-ordered exponential of $\calh$ (over half a period) is uniquely defined.
-This defines the map $f:(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0){\rightarrow}\br$.
-For a sufficiently regular $f$, the inverse image -- of a $d_s$-dimensional submanifold in $\br$-space -- must have  dimension that is greater or equal to $d_s$.
-In particular, the inverse image of the path-connected hypersurface ($r_2{=}0$) is a path-connected hypersurface in the space of $(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_sm/m_0)$, as illustrated in \fig{fig:dgn}(a).
 
@@
 \end{figure}
-
-%one of them is destabilized by infinitesimal hybridization ($\tau<1$, indicated by green dashed lines) and two of them remains stable until they annihilate at $\tau=0.5$ (indicated by red dashed line)
 
@@
 \end{table*}
-%the two-by-two propagator $\A$ -- for the five symmetry classes which apply to both nearly- and exactly-degenerate orbits. .
 

### 2019-04-06 paper.tex
Updates from Overleaf

@@
 The corresponding $l^2 \delta S^2/S$ is plotted in the right panel.
-For numerical convergence\cite{RZfignote}, we have presented data only in a strip [within ($\alpha$, $Z_\parallel$)-space] where $0.4{<}\epsilon_0{<}1.0$(eV).Parameters for (a): $m=0.076m_0$, $l=200$\AA~and $g_{s\perp}=2$; parameters for (d): $m=0.076m_0$, $l=100$\AA~and $g_{s\perp}=2$.}\label{fig:error}}
+For numerical convergence\cite{RZfignote}, we have presented data only in a strip [within ($\alpha$, $Z_\parallel$)-space] where $0.4{<}\epsilon_0{<}1.0$(eV).Parameters for (a): $m=0.076m_0$, $l=200$\AA~and $g_{s\perp}=2$; parameters for (b): $m=0.076m_0$, $l=100$\AA~and $g_{s\perp}=2$.}\label{fig:error}}
 \end{figure}
@@
 \begin{table*}[t]
-\begin{tabular*}{2\columnwidth}{c@{\extracolsep{\fill}}ccccccc}
+\begin{tabular*}{2\columnwidth}{c@{\extracolsep{\fill}}cccccc}
 \hlineB{2}
@@
 III-1 & 0 & 0 & $\A_2=\breve{g}\A_1\breve{g}^{-1}$ & - & - & 3 \\
-III-2 & 1 & 1 & $\A_2=\breve{g}\A_1^T\breve{g}^{-1}$ & - & - & 3 & \\
+III-2 & 1 & 1 & $\A_2=\breve{g}\A_1^T\breve{g}^{-1}$ & - & - & 3 \\
 III-3 & 0 & 1 & $\A_2=\breve{g}\A_1^*\breve{g}^{-1}$ & - & - & 3\\

### 2019-05-16 paper.tex
Updates from Overleaf

@@
 \title{Landau quantization of nearly degenerate bands, \\
-and full symmetry classification of avoided Landau-level crossings}
+and full symmetry classification of Landau-level crossings}
 
@@
 The original formulation of the rule -- by Onsager\cite{Onsager} and Lifshitz\cite{lifshitz_kosevich,lifshitz_kosevich_jetp} -- neglects the effect of spin-orbit coupling.
-While subsequent generalizations by Roth\cite{rotheffham,rothmag}, Mikitik\cite{Mikitik_quantizationrule}, and the present authors\cite{topoferm,100p} account for the spin-orbit effect, such quantization rules apply only when the spin-orbit splitting of energy bands is much stronger (or much weaker) than the Zeeman interaction.
+While subsequent generalizations \cite{rotheffham, rothmag, mikitik_manifestation_1999, topoferm, 100p, gao_zero-field_2017, fuchs_landau_2018} account for the spin-orbit effect, such quantization rules apply only when the spin-orbit splitting of energy bands is much stronger (or much weaker) than the Zeeman interaction.
 
@@
 Our work presents a generalized rule to describe the Landau quantization of nearly-degenerate energy bands, for which  spin-orbit-split bands is but one example.
-By the \textit{near-degeneracy} condition, we generally mean that
+The \textit{near-degeneracy} condition means that
 the ratio of differential to average area is small: $|\delta S/S|{\ll}1$.
 Our proposed rule relies also on a second condition -- that $S$ is much larger than the inverse square of the magnetic length $l{=}\sqrt{\hbar/eB}$; this is the standard semiclassical condition in the Onsager-Lifshitz-Roth theory.
-By treating \textit{both} $|\delta S/S|$ and $1/l^2|S|$   as small parameters with finite ratio $l^2|\delta S|$, our perspective diverges from and generalizes \textit{single-parameter} semiclassical theories\cite{kohn_effham,blount_effham,rotheffham,wannier_fredkin,fischbeck_review,Mikitik_quantizationrule,topoferm,100p,gao_zero-field_2017}.
-
-The inverse ratio $1/l^2|\delta S|$ measures the hybridization of nearly-degenerate orbits by the Zeeman interaction.
-In the regime $l^2|\delta S|{\gg}1$, the Onsager-Lifshitz{-Roth} quantization rules apply independently to  two concentric (but decoupled) orbits.
-In the opposite regime $l^2|\delta S|{\ll}1$, the spin-orbit splitting of energies is negligible, and we may then apply the known quantization rule for exactly-degenerate bands\cite{rotheffham,rothmag,topoferm,100p,Mikitik_quantizationrule}.
-Our unifying rule provides the smooth interpolation between these two known regimes.
-{Equivalently stated, we have extended the applicability of quantization rules to the intermediate regime ($l^2|\delta S|{\sim}1$) where the Zeeman interaction is comparable with the spin-orbit interaction; previously, such rules were known only when one interaction dominates over the other.
-This extension allows  to formulate semiclassical quantization rules for spin-orbit coupled materials in \textit{any} symmetry class -- with or without spatial inversion symmetry, with or without time-reversal symmetry.
+By treating \textit{both} $|\delta S/S|$ and $1/l^2|S|$   as small parameters with finite ratio $l^2|\delta S|$, our perspective diverges from and generalizes \textit{single-parameter} semiclassical theories\cite{kohn_effham,blount_effham,rotheffham,wannier_fredkin,fischbeck_review,mikitik_manifestation_1999,topoferm,100p,gao_zero-field_2017}.
+
+%the hybridization of nearly-degenerate orbits by the Zeeman interaction.
+
+The parameter $l^2|\delta S|$ is a field-dependent, dimensionless measure of the spin-orbit splitting of energy bands. 
+Where $l^2|\delta S|$ is much greater than the interband magnetic moment of wavepackets\cite{rothmag} (in units of the effective Bohr magneton), the Onsager-Lifshitz{-Roth} quantization rules apply independently to  two concentric (but decoupled) orbits.
+The wavepacket's magnetic moment is the generalization of the magnetic moment of electron spin; it further accounts for the orbital moment,\cite{chang_berry_1996} as well as the effect of Berry curvature.
+Where $l^2|\delta S|$ is much less than the dimensionless magnetic moment, the spin-orbit splitting of energies is negligible, and we may then apply the known quantization rule for exactly-degenerate bands\cite{rotheffham,rothmag,topoferm,100p,mikitik_manifestation_1999}.
+Our unifying rule provides the smooth interpolation between the regimes of small and large $l^2|\delta S|$.
+Equivalently stated, we have extended the applicability of quantization rules to the intermediate regime  where the generalized Zeeman interaction (with the wavepacket's magnetic moment) is comparable with the spin-orbit interaction.
+This extension allows us  to formulate semiclassical quantization rules for spin-orbit coupled materials in \textit{any} symmetry class -- with or without spatial inversion symmetry, with or without time-reversal symmetry.
 The unifying rule is presented in \s{sec:qtznrules} for nearly-degenerate bands with a spin-half (or pseudospin-half) degree of freedom.
-As elaborated in \s{sec:discussion}, the most general formulation of our rule is applicable  to any number of nearly-degenerate bands of any symmetry.}
+As elaborated in \s{sec:discussion}, the most general formulation of our rule is applicable  to any number of nearly-degenerate bands of any symmetry.
 
@@
 The remaining terms in \q{eq:H1} describe a generalized Zeeman interaction $B\calm$ which is the first-order-in-$B$ correction to the Peierls-Onsager Hamiltonian $\var(\bK)$\cite{rotheffham,blount_effham,kohn_effham}.
-Included in this interaction is the Zeeman coupling to the spin ($g_s\mu_Bs_z/\hbar$) and orbital ($M_z$) magnetic moment\cite{thonhauser_orbital_2005} of the nearly-degenerate band; the latter is expressible in terms of matrix elements of the velocity operator $\boldsymbol{\Pi}_{mn}=i\langle\psi_m|[\hat{H}_0, \hat{\boldsymbol{r}}]|\psi_n\rangle/\hbar$ between Bloch wave functions $\psi_{n\bk}$:
+Included in this interaction is the Zeeman coupling to the spin ($g_s\mu_Bs_z/\hbar$, with $\mu_B=e\hbar/2m_0$) and orbital ($M_z$) magnetic moment\cite{thonhauser_orbital_2005} of the nearly-degenerate band; the latter is expressible in terms of matrix elements of the velocity operator $\boldsymbol{\Pi}_{mn}=i\langle\psi_m|[\hat{H}_0, \hat{\boldsymbol{r}}]|\psi_n\rangle/\hbar$ between Bloch wave functions $\psi_{n\bk}$:
 \e{
@@
 \e{\mathfrak{X}_{\beta,mn}{=}i\braket{u_m}{\partial u_n/\partial k_{\beta}},  \;\;\;v_{\alpha}:= \f{1}{\hbar}\p{\var}{k_{\alpha}},\label{berryconn}}
-with $\{u_n\}_{n=1}^2$ the periodic component of Bloch functions. 
+with $\{u_{n\bk}\}_{n=1}^2$ the cell-periodic component of Bloch functions $\{\psi_{n\bk}\}_{n=1}^2$. 
 %which provides a geometric characterization of band wavefunctions along $\frako_0$.\\
@@
 
-\noi{i} If $|\var_+{-}\var_-|$ is everywhere (along $\frako_0$) much greater than $B|\calm_{+-}|$, then an electron would undergo adiabatic (band-conserving) dynamics\cite{nenciu_review} along two independent, nondegenerate orbits.
+\noi{i} If $|\delta \var_+{-}\delta \var_-|$ is everywhere (along $\frako_0$) much greater than $B|\calm_{+-}|$, then an electron would undergo adiabatic (band-conserving) dynamics\cite{nenciu_review} along two independent, nondegenerate orbits.
 Such an adiabatic regime always exists as $B{\rightarrow} 0$ for nearly-degenerate orbits that do not intersect.
@@
 \onlinecite{rothmag} and Ref.
-\onlinecite{Mikitik_quantizationrule} for centrosymmetric solids with time-reversal symmetry (at zero field).
+\onlinecite{mikitik_manifestation_1999} for centrosymmetric solids with time-reversal symmetry (at zero field).
 For comparison, it should be emphasized that \qq{eq:rule}{berryconn} applies to solids of any symmetry, including magnetically-ordered solids.}
@@
 
-In this section, we apply our rule to the Landau levels of the Rashba model [cf.\ \q{eq:Rashba-Hamiltonian}], for which analytic, closed-form solutions exist for verification\cite{bychkov_oscillatory_1984}.
+In this section, we apply our rule to the Landau levels of the Rashba model [cf.\ \q{eq:Rashba-Hamiltonian}], for which continuous rotational symmetry exists in the presence of an out-of-plane field.
+In such case, analytic, closed-form solutions\cite{bychkov_oscillatory_1984} exist for verification of our rule.
 
@@
 In the energy basis of the Rashba Hamiltonian $H_R$ [cf.\ \q{eq:Rashba-Hamiltonian}],
-\e{\calh(\bk)=-\hbar\alpha k\tau_z{+}\f{g_{s\perp}}{2}\mu_{\sma{B}}B\tau_x {-} \f{eB\hbar}{2m} (\tau_x-I) \epsilon_{\alpha\beta} k_{\alpha}\nabla_{\beta}\theta,\label{rashbaeffham}}
+\e{\calh(\bk)=-\hbar\alpha k\tau_z{+}\f{g_{s\perp}}{2}\mu_{\sma{B}}B\tau_x {-} \mu_{\sma{B}}B (\tau_x-I) \epsilon_{\alpha\beta} k_{\alpha}\nabla_{\beta}\theta,\label{rashbaeffham}}
 where $\tau_i$ are a new set of Pauli matrices with $\tau_z{=}{+} 1$ and ${-}1$ corresponding to the outer and inner orbits, respectively.
@@
 
-In the weak-hybridization regime: $l^2\delta S \gg \pi|g_{s\perp} m/m_0{-}2|$, we may expand \q{eq:Rashba-lambda} as a Laurent series in $B$:
+Near the adiabatic regime: $l^2\delta S \gg \pi|g_{s\perp} m/m_0{-}2|$, we may expand \q{eq:Rashba-lambda} as a Laurent series in $B$:
 \e{\lambda_{\pm}= \pm \f{l^2\delta S}{2} +\pi \pm \f{\pi^2}{4}\f{(g_{s\perp}m/m_0-2)^2}{l^2\delta S} + O(B^2). \label{lambdasmallB}}
-\q{eq:rule}, combined with the first two terms on the right-hand-side of \q{lambdasmallB}, may alternatively be derived from  the standard Onsager-Lifshitz rules for two independent orbits, with a common $\pi$ Berry-phase correction for each orbit\footnote{The intra-band Zeeman and orbital-moment couplings vanish due spacetime-inversion symmetry\cite{topoferm}.}: $l^2(S{\pm}\delta S)/2\pi {\in}\Z$.
+\q{eq:rule}, combined with the first two terms on the right-hand-side of \q{lambdasmallB}, may alternatively be derived from the standard Onsager-Lifshitz rules for two independent orbits, with a common $\pi$ Berry-phase correction for each orbit\footnote{The intra-band Zeeman and orbital-moment couplings vanish due spacetime-inversion symmetry\cite{topoferm}.}.
 Higher-order terms in \q{lambdasmallB} reflect the field-induced hybridization of the spin-orbit-split orbits.
+\red{In particular, the linear-in-$B$ term   is related\cite{gao_zero-field_2017} to the  single-band magnetic susceptibility $\chi_\pm$ as $(\pi\hbar B/e)d\chi_\pm/dE$; this identification has been made by Yang \emph{et al}\cite{gao_zero-field_2017}, as well as Fuchs \emph{et al}\cite{fuchs_landau_2018}.}
 Eq.\ (\ref{lambdasmallB}) has been partially obtained by Mineev for the Rashba model\cite{mineev_haas--van_2005}; he missed the second term in $(g_{s\perp}m/m_0-2)$ [cf.\ \q{lambdasmallB}], due to his neglect of the interband Berry connection.
 
-In the strong-hybridization regime where $l^2\delta S {\ll}\pi(g_{s\perp}m/m_0{-}2)$, $\lambda_{\pm}{\approx}{\pm}\pi g_{s\perp}m/2m_0$ mod $2\pi$, which corresponds to the Zeeman splitting of Landau levels by $g_{s}\mu_BB$, in the \textit{absence} of the spin-orbit interaction.
+%\red{Eq.
+(\ref{lambdasmallB}) can also be obtained by systematically including the magnetic susceptibility\cite{gao_zero-field_2017,fuchs_landau_2018} and taking the nearly-degenerate limit $E \gg m\alpha^2$.}
+
+In the strong-hybridization regime ($l^2\delta S {\ll}\pi(g_{s\perp}m/m_0{-}2)$) where adiabaticity is lost, $\lambda_{\pm}{\approx}{\pm}\pi g_{s\perp}m/2m_0$ mod $2\pi$, which corresponds to the Zeeman splitting of Landau levels by $g_{s}\mu_BB$, in the \textit{absence} of the spin-orbit interaction.
 
@@
 &n_{\pm}=\frac{l^2S}{2\pi}+\frac{l^2\delta S}{16\pi}\f{\delta S}{S}\lin 
-&\pm\f1{2}\sqrt{\bigg(\frac{l^2\delta S}{8\pi}\f{\delta S}{S}\bigg)^2+(l^2\delta S)^2+\pi^2\bigg(\f{g_{s\perp}m}{m_0}-2\bigg)^2},\label{eq:Rashba-exact}}
+&\pm\f1{4\pi}\sqrt{\bigg(\frac{l^2\delta S}{16\pi}\f{\delta S}{S}\bigg)^2+(l^2\delta S)^2+\pi^2\bigg(\f{g_{s\perp}m}{m_0}-2\bigg)^2},\label{eq:Rashba-exact}}
 with the functional forms of $\delta S(E)$ and $S(E)$ provided in \q{deltaSvsS};  $n_{+}{\ge} 1$ and $n_-{\ge} 0$ here are integer-valued labels for two distinct sets of levels.
@@
 We shall assume  $1/\lper^2S{\ll}1$, where $S$ is the area of the zeroth-order orbit (with effective mass $m$ and radius $k_E{=}\sqrt{2mE}/\hbar$).
-For energies much greater than $m\alpha^2$ and $\zpar$, the nearly-degeneracy condition ($\delta S/S{\ll}1$) is met, where $\delta S$ is the differential area induced by both spin-orbit and in-plane Zeeman couplings [see \fig{fig:RZ}(b)].
+The nearly-degeneracy condition ($\delta S/S{\ll}1$) is met for $E\gg m\alpha^2, \zpar$;\footnote{This inequality follows from  $E\approx k^2/2m$ being much greater than the spin-orbit interaction ($\sim \alpha k$) and the $k$-independent Zeeman interaction ($\zpar$); only the latter two interactions split the spin degeneracy of energy bands.} here, $\delta S$ means the differential area induced by both spin-orbit and in-plane Zeeman couplings [see \fig{fig:RZ}(b)].
 The smallness of $1/\lper^2S$ and $\delta S/S$ (with finite ratio $\lper^2\delta S$) justifies our application of the quantization rule [\qq{eq:rule}{eq:H1}], with the effective Hamiltonian:
@@
 \e{
-\calh = -\hbar\alpha k_{E}\omega^{\sma{\perp}}_c t\,\sigma_x+(Z_\parallel-\alpha k_{E})\sigma_y-Z_\perp\sigma_z,\label{effhamIIDirac}
+\calh = -\hbar\alpha k_{E}\omega^{\sma{\perp}}_c t\,\sigma_x+(Z_\parallel-\hbar \alpha k_{E})\sigma_y-Z_\perp\sigma_z,\label{effhamIIDirac}
 }
 The eigenbasis of $\sigma_x$ corresponds to two diabatic levels with characteristic slope $v_d{:}{=}\hbar\alpha k_E\omega^{\sma{\perp}}_c$; near $t{=}0$, the diabatic levels anticross  due to the hybridization terms proportional to $\sigma_{y,z}$.
-Generally, the probability of tunneling across the hybridization-induced barrier is  $\rho^2{=}\exp(-2\pi\barmu)$, with $\barmu{=}{E_g}^2/{2v_d \hbar}$ and $E_g$ the energy gap at the center of the anticrossing\cite{wittig_landauzener_2005,lifshitz_e.m._quantum_1991}; in this context,
-\e{\barmu=\frac{Z_\perp^2+(Z_\parallel-\alpha k_{E})^2}{2\hbar\alpha k_{E}\var^{\sma{\perp}}_c}, \label{mu1}}
+Generally, the probability of tunneling between two hyperbolic arms (across the hybridization-induced barrier) is  $\rho^2{=}\exp(-2\pi\barmu)$, with $\barmu{=}{E_g}^2/{2v_d \hbar}$ and $E_g$ the energy gap at the center of the anticrossing\cite{wittig_landauzener_2005,lifshitz_e.m._quantum_1991}; in this context,
+\e{\barmu=\frac{Z_\perp^2+(Z_\parallel-\hbar \alpha k_{E})^2}{2\hbar\alpha k_{E}\var^{\sma{\perp}}_c}, \label{mu1}}
 with $2\hbar\alpha k_E$ the spin-orbit splitting at energy $E$ [cf.\ \fig{fig:orbits}(a)].
-In the absence of the out-of-plane Zeeman coupling ($Z_\perp{=}0$), $\bar{\mu}$ would vanish at the energy of the II-Dirac point -- leading to unit-probability Klein tunneling, as was first proposed by Ref.
+In the absence of the out-of-plane Zeeman coupling ($Z_\perp{=}0$), $\bar{\mu}$ would vanish at the energy of the II-Dirac point (where $Z_{\parallel}=\hbar\alpha k_E$).
+This leads to unit-probability Klein tunneling, as was first proposed by Ref.
 \onlinecite{obrien_magnetic_2016} in a different model of the II-Dirac point.
-However, with a proper account of $Z_\perp$, we find instead that $\bar{\mu}$ has a nonvanishing minimum: $\bar{\mu}_{\sma{\text{min}}}{:}{=} (g_{s\perp} m/m_0)(Z_\perp/4\hbar\alpha k_{E})$, which is a product of the dimensionless effective mass and the ratio of the out-of-plane Zeeman splitting over the spin-orbit splitting.
+However, with a proper account of $Z_\perp$, we find instead that $\bar{\mu}$ has a nonvanishing minimum: $\bar{\mu}_{\sma{\text{min}}}{:}{=} (g_{s\perp} m/m_0)(Z_\perp/8\hbar\alpha k_{E})$, which is a product of the dimensionless effective mass and the ratio of the out-of-plane Zeeman splitting over the spin-orbit splitting.
 This minimum may be significant for semiconductor heterostructures (e.g.,  $g_{s\perp}m/m_0{\sim} 1$ in InAs heterostructures\cite{pakmehr_g-factor_2015}) and  for heavy-fermion systems.
@@
 
-Away from the II-Dirac point, an electron undergoes adiabatic (band-conserving) dynamics.
+At parts of the semiclassical trajectory away from the II-Dirac point, an electron undergoes adiabatic (band-conserving) dynamics.
 The time-ordered, coherent process of Landau-Zener tunneling/transmission and adiabatic dynamics is described by the propagator:
@@
 The adiabatic phase $\tilde{\lambda}_{\pm}$ is the sum of a dynamical phase ${\pm} l^2 \delta S/2$ and  the single-band Berry phase $\phi^B_\pm$, for the outer ($+$) and inner ($-$) orbit respectively.
-At energies far above the Dirac point ($|E{-}\epsilon_0|{\gg}|Z_{\perp}|$) where the Zeeman interaction is negligible, both orbits encircle the Dirac point and hence $\phi_{\pm}^B{\approx}{\pm}\pi$; far below the Dirac point, neither orbit encircles the Dirac point, leading to $\phi_{\pm}^B{\approx}0$.
+The out-of-plane Zeeman interaction breaks the $C_2T$ symmetry that quantizes $\phi^B_\pm$ to integer multiples of $\pi$.
+At energies far above the Dirac point ($|E{-}\epsilon_0|{\gg}|Z_{\perp}|$) where the out-of-plane Zeeman interaction is negligible, both orbits encircle the Dirac point and hence $\phi_{\pm}^B{\approx}{\pm}\pi$; far below the Dirac point, neither orbit encircles the Dirac point, leading to $\phi_{\pm}^B{\approx}0$.
 At intermediate energies, $\phi_{+}^B$ (resp.\ $\phi_{-}^B$) is a continuous and decreasing (resp.\ increasing) function of energy, as supported by the Bloch-sphere argument in Fig.
@@
 For any nonzero field, $0{<}\tau{<}1$ implies that the two incommensurate harmonics $(\Omega_+{\pm}\Omega_-)$ in \q{coscos} compete to produce a quasirandom Landau-level spectrum\cite{kaganov_coherent_1983}.
-That is to say, the spectrum is disordered on the scale of nearest-neighbor level spacings but has longer-ranged correlations.
-To appreciate this, let us analyze the Landau levels (near the Dirac point) perturbatively in the small parameter $\tau$.
-To zeroth order, \q{coscos} reduces to
+That is to say, the spectrum is no longer quasiperiodic in $l^2$ with a single period (as characteristic of Landau levels in the semiclassical regime without breakdown\cite{Onsager,lifshitz_kosevich,lifshitz_kosevich_jetp}); instead, the spectrum becomes correlated at multiple scales (in $l^2)$,\cite{kaganov_coherent_1983,slutskin_dynamics_1968,AALG,100p} corresponding to the multiple Feynman trajectories that are enabled by tunneling.
+
+To appreciate this, let us analyze the Landau levels (near the Dirac point) perturbatively in the small parameter $\tau$. To zeroth order, \q{coscos} reduces to
 \e{2l^2S(E_n^0)+\pi = 2\pi n \rightarrow \{E_n^0(B)\}_{n\in\Z}.\label{trefoilrule}}
 To derive the above equation, we have utilized $\phi^B_-{+}\phi^B_+{=}0$, which is valid for any two-band model in the nearly-degenerate regime\footnote{For two band models, Berry phases of the two bands sum up to 0 on arbitrary path}; in \fig{fig:blochsphere} this is reflected in the sum of solid angles (at fixed energy) equalling $4\pi$.
-\q{trefoilrule} may be interpreted as a quantization rule for a trajectory on a M\"obius strip  with net area $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels (sketched by solid lines in Fig.
+\q{trefoilrule} may be interpreted as a quantization rule for a trajectory on a M\"obius strip [cf.
+\fig{fig:RZ}(b)] with net area $2S{=}4\pi m E{/\hbar^2}$; the corresponding Landau levels (sketched by dashed lines in Fig.
 \ref{fig:RZ}(c)) are periodic in $E{\rightarrow}E{+}\pi/l^2(\partial S/\partial E)$ and in $l^2{\rightarrow}l^2{+}\pi/S$.
@@
 To recapitulate, $E_n^0(B)$ [cf.\ \q{trefoilrule}] exhibits a periodicity on short scales associated to the large area of the M\"obius orbit.
-This short-scale periodicity is lost due to  imperfect Klein tunneling, yet a longer-range correlation (associated to the smaller differential area $\delta S$ between spin-split orbits) persists, as shown by the first-order-in-$\tau$ correction:\footnote{The general form of this perturbative calculation can be found in Sec.
+This short-scale periodicity is lost due to  imperfect Klein tunneling, yet a longer-range correlation (associated to the smaller differential area $\delta S$ between spin-split orbits) persists, as the solution $(E_n^0+\delta E_n)$ of \q{coscos} to the first order in $\tau$ shows:\footnote{The general form of this perturbative calculation can be found in Sec.
 IX-E of Ref.
@@
 
-\section{Tuning the (pseudo)spin-half degeneracy of Landau Levels}\label{sec:llquasideg}
+\section{Symmetry classification of Landau-Level crossings}\label{sec:llquasideg}
 
@@
 \includegraphics[width=1.0\columnwidth]{LL.png}
-\caption{A schematic diagram of Landau level dispersion (solid lines) with respect to $B$ for nearly-degenerate orbits.
+\caption{A schematic illustration of Landau level dispersion (solid lines) with respect to $B$ for nearly-degenerate orbits.
+For better illustration, we have exaggerated the change of $\delta\lambda$ with respect to $B$ and $E$.
 $\delta\lambda$ is plotted in the colored background.
-Landau level quasidegeneracies occur at $\delta\lambda\equiv 0\equiv 2\pi$ ({indicated by red dashed lines}).\label{fig:LL}}
+Landau level quasidegeneracies occur at $\delta\lambda\equiv 0$ ({indicated by red dashed lines}).\label{fig:LL}}
 \end{figure}
@@
 In \s{sec:relatedegeneracies}, we will relate the eigenvalue-degeneracies of  $\A$ to the (near) degeneracies of Landau levels.
-We then ask how many tunable real parameters are needed to attain an eigenvalue-degeneracy of $\A$.
-Our answer is  $3$ in the absence of crystallographic point-group symmetry, as discussed in \s{sec:introducecodimension}; the answer may reduce to $0,1$ or $2$ depending on the symmetry class of the orbit, as will be explained in \s{sec:tenfold}.
-Before this general symmetry classification,  we will first develop physical intuition by studying two rotationally-symmetric models [cf.\ \s{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown}] where only one tunable parameter is needed -- this can be the magnitude of the $B$ field itself.
+We then ask how many tunable real parameters are needed to attain an eigenvalue-degeneracy of $\A$; \red{this number provides a classification of Landau-level crossings.} Our answer is  $3$ in the absence of crystallographic point-group symmetry, as discussed in \s{sec:introducecodimension}; the answer may reduce to $0,1$ or $2$ depending on the symmetry class of the orbit, as  summarized in \tab{table:codimension-nearlydegen} and \ref{table:codimension-exactlydegen} of \s{sec:tenfold}.
+
+\red{Depending on preference, a reader may directly read \s{sec:relatedegeneracies},\ref{sec:introducecodimension} and \ref{sec:tenfold}, which have been written in self-contained fashion.
+A physical-motivated reader may prefer to go through all subsections in order: \s{sec:singleparameterrashba} and \ref{sec:rotsymmbreakdown} further describe two rotationally-symmetric models that are motivated by the Rashba-Dresselhaus 2DEG.
+In these models, only one tunable parameter is needed -- this can be the magnitude of the $B$ field itself.}
 
@@
 $T_{l^2}$ above is the period (in $l^2$) of quantum oscillations -- in the absence of spin-orbit coupling.
-At fixed $E$, the number of Landau levels sandwiched between two adjacent curves of \q{eigenvaluedegeneracyA} is of order $S/(\partial \lambda_a/\partial l^2).$
+At fixed $E$, the number of Landau levels sandwiched between two adjacent curves of \q{eigenvaluedegeneracyA} is of order $S/(\partial \lambda_a/\partial l^2).$ The derivation of Eq.
+(\ref{llquasideg}) and Eq.
+(\ref{llquasidegB}) is presented in App.
+\ref{sec:proofLLquasideg}.
 
@@
 
-\subsection{Codimension analysis without symmetry, and with band-conservation symmetry}\label{sec:introducecodimension}
-
-In the absence of symmetry, eigenvalue-degeneracies of the unitary propagator $\A$ [cf.
-\q{eq:prop}] are attainable by tuning three real parameters.
-Analogously, it is well known (as the non-crossing rule in quantum theory\cite{neumann2000behaviour}) that eigenvalue-degeneracies of complex, finite-dimensional matrix Hamiltonians are also attainable by tuning three real parameters.
-To prove the non-crossing rule for two-by-two unitaries, we begin by decomposing any such matrix as $\A{=}e^{i\phi}{\cal \bar{A}}$, with  ${\cal \bar{A}}{\in}\text{SU}(2)$.
-Then the necessary and sufficient condition for an eigenvalue-degeneracy of $\A$ is that ${\cal \bar{A}}{=}{\pm}I$.
+\subsection{Landau-level crossings in the absence of symmetry, and with band-conservation symmetry}\label{sec:introducecodimension}
+
+In the absence of symmetry,  it is well known (as the non-crossing rule in quantum theory\cite{neumann2000behaviour}) that eigenvalue-degeneracies of complex, finite-dimensional matrix Hamiltonians are attainable by tuning three parameters.
+Here and henceforth,   \textit{parameters}  will always refer to real parameters.
+Since unitary matrices are exponentiated Hamiltonians (multiplied by $i$), the eigenvalue-degeneracies of the two-by-two unitary propagator $\A$ [cf.
+\q{eq:prop}] are also attainable by tuning three parameters (in the absence of symmetry).\textbf{[Fritz Haake, chaos]} We briefly review how this  result is attained; the elementary argument that will be presented here will be nontrivially generalized to other symmetry classes of orbits in the subsequent sections.
+
+We begin by decomposing a two-by-two unitary  matrix as \red{$\A{=}e^{i\phi}{\cal \bar{A}}\in \text{U}(2)$, with  ${\cal \bar{A}}{\in}\text{SU}(2)$; it is possible in some case studies that $\A={\cal \bar{A}}$.} The necessary and sufficient condition for an eigenvalue-degeneracy of $\A$ is that ${\cal \bar{A}}{=}{\pm}I$.
 In the canonical parametrization of $\text{SU}(2)$ over the three-sphere $S^3$:
-\e{{\cal \bar{A}}{=}\matrixtwo{r_1{+}ir_2}{r_3{+}ir_4}{{-}r_3{+}ir_4}{r_1{-}ir_2},\;\; \sum_{j=1}^4r_j^2{=}1,\;\; r_j\in \mathbb{R},  \label{s3}}
+\e{{\cal \bar{A}}{=}\matrixtwo{r_1{+}ir_2}{r_3{+}ir_4}{{-}r_3{+}ir_4}{r_1{-}ir_2},\;\; \sum_{j=1}^4r_j^2{=}1,\;\; r_j\in \mathbb{R}.  \label{s3}}
 ${\cal \bar{A}}{=}{\pm}I$ lie on distinct points of $S^3$, and are attainable by tuning three real parameters: $r_2{=}r_3{=}r_4{=}0$.
@@
 
-Symmetry may reduce the number of tunable parameters needed to attain an eigenvalue degeneracy for $\A$.
+As a shorthand, we will refer to the number of parameters (needed to tune to an eigenvalue-degeneracy of $\cala$) as the \textit{codimension}; the geometric interpretation of codimension is elaborated in \app{app:codimension}.
+
+Symmetry reduces codimension.
 A case in point is band-conservation symmetry in the adiabatic regime (cf.\ \s{sec:qtznrules}), which restricts $\cala$ to have diagonal form  ($r_3{=}r_4{=}0$) in the basis of energy bands [cf.\ \q{phaseindependentorbit}].
-The phase of $r_1{\pm}ir_2$ equals ${\pm} l^2\delta S/2$ plus field-independent corrections.
+The phase of $r_1{\pm}ir_2$ equals ${\pm} l^2\delta S/2$ plus subleading corrections.
 This  phase -- a single parameter --  can be  tuned to attain $\cala{=}{\pm}I$.
@@
 
-To generalize the discussion beyond band-conservation symmetry, it is instructive to adopt a geometric perspective on degeneracies.
+%To generalize the discussion beyond band-conservation symmetry, it is instructive to adopt a geometric perspective on degeneracies.
 A generic $\text{SU}(2)$ matrix that is constrained by symmetry may no longer be uniformly distributed over $S^3$ [cf.\ \q{s3}], e.g., ${\cal \bar{A}}$ with band-conservation symmetry is uniformly distributed over a phase in $S^1$.
@@
 
-One of our main results is that  rotational symmetry (with rotational axis parallel to the field) results in degeneracy manifolds with unit codimension.
-This will be demonstrated by two  case studies: the Rashba 2DEG in \s{sec:singleparameterrashba}, and a model with II-Dirac points in \ref{sec:rotsymmbreakdown}.
+One of our main results is that   rotational symmetry (with rotational axis parallel to the field) reduces  codimension to one.
+This will be demonstrated by two  case studies: the Rashba 2DEG in \s{sec:singleparameterrashba}, and a model with II-Dirac points in \s{sec:rotsymmbreakdown}.
 
@@
 \q{eq:Rashba-Hamiltonian}].
-This model has a continuous rotational symmetry (denoted $\mathfrak{c}_{\infty}$), which manifests as the constancy of $\calh(\bk)$ over the circular zeroth-order orbit [cf.\ \q{rashbaeffham}].
+This model has a continuous rotational symmetry (denoted $\mathfrak{c}_{\infty}$), which manifests as the constancy of $\calh(\bk)$ over the circular zeroth-order orbit [cf.\ \q{rashbaeffham} with the simplification $\epsilon_{\alpha\beta} k_{\alpha}\nabla_{\beta}\theta=1$].
 Consequently, the propagator [cf.\ \q{eq:prop}] simplifies to the exponential form:
-\e{\A{=}-\exp(-2\pi i\sum_{j}r_j\tau_j),\label{expform}}
+\e{\A{=}-\exp(-2\pi i\sum_{j}\xi_j\tau_j),\label{expform}}
 where
-\e{\br{=}\bigg(\f{g_{s\perp}m}{4m_0}{-}\f1{2},0,-\f{\hbar\alpha k_{\sma{E}}}{\var_c}\bigg) \la{rvectorrashba}} 
+\e{\boldsymbol{\xi}{=}\bigg(\f{g_{s\perp}m}{4m_0}{-}\f1{2},0,-\f{\hbar\alpha k_{\sma{E}}}{\var_c}\bigg) \label{rvectorrashba}} 
 and $\{\tau_j\}$ are a set of Pauli matrices.
-Any $\text{SU}(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}] for some (possibly non-unique) $\br$, with $r_2$ not necessarily zero.
-We will demonstrate codimension reduction for the general form of $\A$ (having any $\br$), with the Rashba model as a particular realization.
-
-All eigenvalue degeneracies of $\A$ occur on spheres in $\br$-space with radii $|\br|{=}\sqrt{r_1^2{+}r_2^2{+}r_3^2}$ equal to an integer ($j$)  multiple of $1/2$;  ${j}$ is odd (resp.
+Any $\text{SU}(2)$ matrix can be expressed in the exponential form [cf.\ \q{expform}] for some (possibly non-unique) $\boldsymbol{\xi}$, with $\xi_2$ not necessarily zero.
+We will demonstrate codimension reduction for the general form of $\A$ (having any $\boldsymbol{\xi}$), with the Rashba model as a particular realization.
+
+All eigenvalue degeneracies of $\A$ occur on two-spheres in $\boldsymbol{\xi}$-space with radii $|\boldsymbol{\xi}|{=}\sqrt{\xi_1^2{+}\xi_2^2{+}\xi_3^2}$ equal to an integer ($j$)  multiple of $1/2$;  ${j}$ is odd (resp.
 even) for  $\A{=}I$ (resp.\ $\A{=}{-}I$).
-This condition $|\br|{=}j/2$ (for any nonzero $j$) may be attained by tuning a single parameter.
+The condition $|\boldsymbol{\xi}|{=}j/2$ (for any nonzero, integer-valued $j$) may be attained by tuning a single parameter.
 In other words, all nonzero-radius spheres are unit-codimensional surfaces (known as hypersurfaces), whose stability rely on $\mathfrak{c}_{\infty}$ symmetry.
-These hypersurfaces separate $\br$-space into infinitely-many, distinct connected components, i.e., the zeroth homotopy group $\pi_0$ comprises an infinite set.
-Each hypersurface may thus be viewed as a symmetry-protected, topological defect, which separates domains (in $\br$-space) where Landau levels are non-quasidegenerate.
+
+These hypersurfaces separate $\boldsymbol{\xi}$-space into infinitely-many, distinct connected components, i.e., the zeroth homotopy group $\pi_0$ comprises an infinite set.
+Each hypersurface may thus be viewed as a symmetry-protected, topological defect, which separates domains (in $\boldsymbol{\xi}$-space) where Landau levels are non-quasidegenerate.
 By varying $B$ alone (at fixed energy), one then transits between different domains; each penetration of a hypersurface is accompanied by a Landau-level quasidegeneracy.
-For the exactly-soluble Rashba model ($r_2{=}0$), these $\mathfrak{c}_{\infty}$-protected quasidegeneracies  are consistent with (and partially demystify)  the abundance of \textit{exact} level crossings in the spectrum of $H_R(\bK)$ [cf.\ \q{eq:Rashba-exact}]; such crossings are not expected from the Wigner-von Neuman non-crossing rule\cite{neumann2000behaviour}.
+For the exactly-soluble Rashba model ($\xi_2{=}0$), these $\mathfrak{c}_{\infty}$-protected quasidegeneracies  are consistent with (and partially demystify)  the abundance of \textit{exact} level crossings in the spectrum of $H_R(\bK)$ [cf.\ \q{eq:Rashba-exact}]; such crossings are not expected from the Wigner-von Neuman non-crossing rule\cite{neumann2000behaviour}.
 The zero-radius sphere (that is, a point) has codimension three, as would be expected if symmetry were absent (cf.
@@
 
-The above discussion is reminiscent of topological semimetals whose corresponding Bloch Hamiltonians are energy-degenerate at Dirac-Weyl points\cite{wang2012dirac,wan2011topological} and/or line nodes\cite{burkov2011topological}.
-Both Dirac points (in 2D $\bk$-space, e.g., graphene\cite{neto2009electronic}) and line nodes (in 3D $\bk$-space) are attainable by tuning two wavenumbers; the stability of such codimension-two manifolds relies on crystallographic point-group symmetries.
+\red{The above discussion is reminiscent of nodal  (Dirac-Weyl) points, lines and hypersurfaces in the quasiparticle spectra of topological semimetals\cite{wang2012dirac,wan2011topological,burkov2011topological} and superconductors\cite{agterberg_bogoliubov_2017,bzdusek_robust_2017}.} Both Dirac points (in 2D $\bk$-space, e.g., graphene\cite{neto2009electronic}) and line nodes (in 3D $\bk$-space) are attainable by tuning two wavenumbers; the stability of such codimension-two manifolds is due to the protection of symmetries.
 On the other hand, Weyl points in 3D $\bk$-space have codimension three and do not require any point-group symmetry for their stability.
@@
 \includegraphics[width=1.0\columnwidth]{dgn.png}
-\caption{Degeneracy manifolds of the Rashba-Dresselhaus model.
-(a) The degeneracy manifold of $\A{=}I$ is a path-connected hypersurface.
+\caption{Landau-level quasidegeneracy in the Rashba-Dresselhaus model.
+(a)  $\A{=}I$ defines a path-connected hypersurface.
 Points in $\alpha=0$ or $\beta=0$ planes are colored in red.
-(b) illustrates the degeneracy manifold of $\A=-I$, which lie confined to  the $\alpha{=}0$ and $\beta{=}0$ planes (blue translucent planes).
+(b)  $\A=-I$ defines a manifold which lie confined to  the $\alpha{=}0$ and $\beta{=}0$ planes (blue translucent planes).
 Each $\mathfrak{c}_{\infty}$-symmetric plane contains an infinite set of concentric, circular line degeneracies.
@@
 {For the Rashba-Dresselhaus 2DEG, $\A$ depends on $\alpha,~\beta,~l,~E,~m$ only through three independent parameters:}
-\e{\left( \f{\hbar\alpha k_{\sma{E}}}{\var_c},\f{\hbar\beta k_{\sma{E}}}{\var_c},g_{s\perp}\f{m}{m_0} \right){\in} \mathbb{R}^3. \la{parameter2}}  
-$\A(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_{s\perp}m/m_0){=}{\pm} I$ then determines a set of concentric circles in the $\beta{=}0$ plane, as per the $\mathfrak{c}_{\infty}$-symmetric case study in \s{sec:ctsrot}.
+\e{\left( \f{\hbar\alpha k_{\sma{E}}}{\var_c},\f{\hbar\beta k_{\sma{E}}}{\var_c},g_{s\perp}\f{m}{m_0} \right){\in} \mathbb{R}^3, \label{parameter2}}
+\red{which is not the exponential parametrization of Eq.\ (\ref{expform}-\ref{rvectorrashba}).} $\A(\hbar\alpha k_{\sma{E}}/\var_c,\hbar\beta k_{\sma{E}}/\var_c,g_{s\perp}m/m_0){=}{\pm} I$ then determines a set of concentric circles in the $\beta{=}0$ plane, as per the $\mathfrak{c}_{\infty}$-symmetric case study in \s{sec:ctsrot}.
 Moving off this plane, we find that $\A{=}I$ is satisfied in a  neighborhood of $\beta{=}0$, i.e., $\A{=}I$ defines a hypersurface in $\mathbb{R}^3$ that is illustrated in \fig{fig:dgn}(a).
@@
 It follows that $r_2{=}0$ is a necessary and sufficient condition for $\A{=}I$.
-The corresponding degeneracy manifold is a path-connected hypersurface, which separates $\br{=}(r_1,r_2,r_3)$-space into two distinct connected components.
+$\A{=}I$ thus defines a path-connected hypersurface, which separates $\br{=}(r_1,r_2,r_3)$-space into two distinct connected components.
 As proven in App.
 \ref{app:codimension}, this conclusion generalizes for any $N{\geq}2$: the degenerate manifolds of $\mathfrak{c}_N$-symmetric $\A$ separate the space of symmetric coordinates into $N$ distinct connected components.
-\fig{fig:dgn}(a) illustrates the $\A=I$ degenerate manifold {in the coordinates of  \q{parameter2} (which are distinct from the $\br$-coordinates in \q{proprashba}).}
+\fig{fig:dgn}(a) illustrates the $\A=I$ manifold {in the coordinates of  \q{parameter2} (which are distinct from the $\br$-coordinates in \q{proprashba}).}
 
@@
 Due to $\mathfrak{c}_2$ symmetry, the time-evolution propagator over the full cyclotron period is simply the square of the propagator for half the period:
-\e{\A=\left(\matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}}{\diagmatrix{e^{i\tilde{\lambda}_-}}{e^{i\tilde{\lambda}_+}}} \right)^2. \label{propC2breakdown}}
-The half-period propagator may be taken from \qq{scattmat}{propinplanezeeman}, with  $\bar{\mu}$ here given by \q{landauzenerc2}, and  $\tilde{\lambda}_{\pm}{=}{\pm}l^2\delta S/4$ plus a field-independent geometric phase.
+\e{\A=\left(\matrixtwo{\tau e^{i\bar{\varphi}}}{-\rho}{\rho}{\tau e^{-i\bar{\varphi}}}{\diagmatrix{e^{i\tilde{\lambda}_-}}{e^{i\tilde{\lambda}_+}}} \right)^2, \label{propC2breakdown}}
+\red{with $\rho=e^{-\pi\barmu}$,  $\tau=\sqrt{1-\rho^{2}}$ [cf.\ \qq{scattmat}{propinplanezeeman}], and  $\tilde{\lambda}_{\pm}{=}{\pm}l^2\delta S/4$ plus a field-independent geometric phase.}
 
@@
 
-\subsection{The ten-fold table for symmetry constrained codimensions}\label{sec:tenfold}
+\subsection{The ten-fold table for symmetry-constrained codimensions}\label{sec:tenfold}
 
@@
 
-Generalizing our rotational-symmetric case studies in
-Sec.
-\ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown}, we now present the symmetry-constrained codimensions for all ten symmetry classes of orbits\cite{topoferm}.
+Going beyond band-conservation and rotational symmetry, we present the symmetry-constrained codimensions for all ten symmetry classes of orbits\cite{topoferm}.
 Depending on the class, the codimension is either $0,1,2$ or $3$.
@@
 \ref{sec:codimquasideg} five of the classes which is relevant to nearly-degenerate orbits.
-The remaining five classes are relevant to exactly degenerate orbits, which we study in Sec.
+All ten classes are relevant to exactly degenerate orbits, which we study in Sec.
 \ref{sec:codimexactdeg}.
@@
 Class II-1 corresponds to spatial symmetries that preserve the arrow of time and the orientation of $\frako_0$, as exemplified by spatial rotational symmetry with rotational axis parallel to the field.
-Another example is given spatial inversion symmetry, for $\frako_0$ that is confined to an inversion-invariant plane: $k_z=0$ or $\pi$.
-The symmetry-constrained codimension here is unity, as has been modelled in Sec.\ \ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown}.
-For a fixed orbit $\frako_0$ in class II-1, there may exist different degeneracy manifolds with different codimensions; in such case we define the symmetry-constrained codimension to be the minimal codimension among all manifolds.\footnote{For a fixed orbit in class I-1 or II-2, all degeneracy manifolds have the same codimension.} For example, we have found that two-fold rotational symmetry reduces the codimension of the $\A{=}{+}I$ manifold (to unity), but not the codimension of the $\A{=}{-}I$ manifold [cf.\ \fig{fig:dgn} and \q{proprashba}].
-The rotation-constrained codimension is then unity, and hence the entry $1$ in the right-most column for class II-1.
+Another example is given by spatial inversion symmetry, for $\frako_0$ that is confined to an inversion-invariant plane: $k_z=0$ or $\pi$.
+The symmetry-constrained codimension here is unity,\footnote{For a fixed orbit $\frako_0$ in class II-1, the manifolds defined by $\A=+I$ may have different codimensions with that of $\A=-I$; in such case we define the symmetry-constrained codimension to be the minimal codimension among all manifolds.
+For example, we have found that two-fold rotational symmetry reduces the codimension of the $\A{=}{+}I$ manifold (to unity), but not the codimension of the $\A{=}{-}I$ manifold [cf.\ \fig{fig:dgn} and \q{proprashba}].
+(For a fixed orbit in class I-1 or II-2, both $\A=\pm I$ have the same codimension.) } as has been modelled in Sec.\ \ref{sec:singleparameterrashba}-\ref{sec:rotsymmbreakdown}.
 
@@
 In the present context, this restriction is void because $\delta\var{=}0$, hence we \textit{also} allow for symmetries that invert the sign of $\calm$.
+Therefore, the symmetry constrained codimension for exactly-degenerate bands falls into ten classes, with  $\calm$ preserving symmetries presented in \tab{table:codimension-nearlydegen} and $\calm$ inverting symmetries presented in \tab{table:codimension-exactlydegen}.
 
@@
 
+It is instructive to adopt a geometric perspective on eigenvalue degeneracies.
+While a generic $\text{SU}(2)$ matrix ${\cal \bar{A}}$ is uniformly distributed over $S^3$ [cf.\ \q{s3}],  we have found in \s{sec:introducecodimension}  band-conservation symmetry restricts the distribution to  $S^1$.
+Generally in the presence of symmetry, we are  motivated to adopt \textit{symmetric coordinates} [$\{r_1,\ldots,r_{d}\}{:}{=}\br$] that independently parametrize the symmetry-constrained $\text{SU}(2)$ matrix;\footnote{Symmetric coordinates are generally not relatable -- by a non-singular coordinate transformation -- to the canonical coordinates [\q{s3}] of asymmetric special unitaries.} such symmetry constraints have been exemplified in \q{eq:sigmazconstraint} for the case of rotational symmetry, and will be elaborated (for all other symmetries) in \app{app:codimension}.
+${\cal \bar{A}}(\br){=}{\pm}I$ then defines a set of submanifolds in $\br$-space which we refer to as \textit{degeneracy manifolds}.
+The \textit{codimension} of the degeneracy manifold  is defined as $d$ minus the dimension of said manifold; alternatively stated, the codimension is the number of independently-tunable parameters (in $\br$) needed to attain a degeneracy.
+
 For a symmetry $g$ which acts on spacetime as $\br \rightarrow \check{g} \br$ and $t\rightarrow (-1)^{s(g)}t$, 

### 2019-05-16 paper.tex
Updates from Overleaf

@@
 Since unitary matrices are exponentiated Hamiltonians (multiplied by $i$), the eigenvalue-degeneracies of the two-by-two unitary propagator $\A$ [cf.
-\q{eq:prop}] are also attainable by tuning three parameters (in the absence of symmetry).\textbf{[Fritz Haake, chaos]} We briefly review how this  result is attained; the elementary argument that will be presented here will be nontrivially generalized to other symmetry classes of orbits in the subsequent sections.
+\q{eq:prop}] are also attainable by tuning three parameters (in the absence of symmetry)\cite{haake2010quantum}.
+We briefly review how this  result is attained; the elementary argument that will be presented here will be nontrivially generalized to other symmetry classes of orbits in the subsequent sections.
 

### 2019-05-17 paper.tex
Updates from Overleaf

@@
 \includegraphics[width=1.0\columnwidth]{LL.png}
-\caption{A schematic illustration of Landau level dispersion (solid lines) with respect to $B$ for nearly-degenerate orbits.
-For better illustration, we have exaggerated the change of $\delta\lambda$ with respect to $B$ and $E$.
+\caption{A schematic illustration of Landau level dispersion (solid lines) with respect to $B$ for nearly-degenerate orbits in 2DEG with Rashba and Dresselhaus spin orbit coupling [cf.
+Eq.
+(\ref{hamRD})].
+For better illustration, the parameters have been chosen such that the change of $\delta\lambda$ with respect to $B$ and $E$ is exaggerated.
 $\delta\lambda$ is plotted in the colored background.
-Landau level quasidegeneracies occur at $\delta\lambda\equiv 0$ ({indicated by red dashed lines}).\label{fig:LL}}
+Landau level quasidegeneracies occur at $\delta\lambda=0$ (indicated by red dashed lines) and $\delta\lambda=2\pi$ is never reached [cf.
+Sec.
+\ref{sec:singleparameterrashba}].
+Parameters: $m=0.076m_0$, $\alpha=7.6\times 10^6$cm/s, $\beta=4.6\times 10^6$cm/s.\label{fig:LL}}
 \end{figure}
